### 2022-02-13 paper/formular.tex
1. add report to git 2. note from paper S.Holzer.Adaptive_Neighborhood_Selection_for_Real_Time_Surface_Normal.pdf

RGB image will be stored as gray value Scene using following equation:
\[ gray: \frac{r+2g+b}{4}  \]

Capture Depth:
\[   \]

\subsection{Normal from k neighbors}

Given a point $ p $ locating on plane $ \Pi $, calculate the normal $ n $ of plane $ \Pi $.

First, find the nearest $ k $ neighbors $ p_1,p_2,...,p_k $ of point $ p $ using KNN-algorithms. The plane $ \Pi $ containing point $ p $ can be fitted using the neighbors of point $ p $. Then the normal is available immediately.

Assume all the neighbors of point $ p $ are in plane $ \Pi = ax+by+cz+d=0 $. Since we only need calculate the normal, thus with out loss of generation, we can set displacement $ d = 0 $. Then the normal $  \bn = (a,b,c)^T  $.

Since all the neighbors of point $ p $ are located on plane $ \Pi $, thus we have 
\[ 
P_{k \times 3} \cdot  \bn_{3 \times 1} = \left(
\begin{matrix}
0 \\
0\\
0
\end{matrix}  \right) \]
In order to avoid trivial solution, one more constraint should be added
\[ \|  \bn_{3 \times 1} \|_2^2 = 1  \], which also let the normal to be a unit vector.
In order to calculate a valid normal, 3 points are required at least. For the sake of robust, more points can be used to reduce the measuring error. In this case, the equation system is over-determined, which can be modeled as following optimization problem
\begin{equation}
	\begin{array}{rrclcl}
		\displaystyle \min & \multicolumn{3}{l}{\| P  \bn \|^2} \\
		\\
		\textrm{s.t.} & \| \bn \|^2 & = & 1 
	\end{array}
\end{equation}
Let the decomposition of $ P=U\Sigma V^T $, The solution i.e. normal is the last column of $ V $.

### 2022-02-13 paper/related_work.tex
1. add report to git 2. note from paper S.Holzer.Adaptive_Neighborhood_Selection_for_Real_Time_Surface_Normal.pdf

In order to estimate normals of an object surface.

In 2012, Holzer et al. \cite{Holzer.S} presented a read-time method, which is able to run algorithm in a high frame speed. They smooth the depth data in order to handle the noise of depth image. The speed is accelerated via integral image. The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.

In 2021, Zhou et al.  \cite{zhou2021fast}

### 2022-02-19 help_funs/mu.py
add normalized convolution network

@@ -1,4 +1,10 @@
+import cv2 as cv
 import numpy as np
+import torch
+
+
+def bi_interpolation(lower_left, lower_right, upper_left, upper_right, x, y):
+    return lower_left * (1 - x) * (1 - y) + lower_right * x * (1 - y) + upper_left * (1 - x) * y + upper_right * x * y
 
 
 def normal_point_to_view_point(normal, point, view_point):
@@ -73,3 +79,83 @@ def normal2RGB(normals, mask):
                 normals[i, j] = (normals[i, j] * 255).astype(np.int32)
 
     return normals
+
+
+def copy_make_border(img, patch_width):
+    """
+    This function applies cv.copyMakeBorder to extend the image by patch_width/2
+    in top, bottom, left and right part of the image
+    Patches/windows centered at the border of the image need additional padding of size patch_width/2
+    """
+    offset = np.int32(patch_width / 2.0)
+    return cv.copyMakeBorder(img,
+                             top=offset, bottom=offset,
+                             left=offset, right=offset,
+                             borderType=cv.BORDER_REFLECT)
+
+
+def get_valid_pixels_idx(img):
+    return np.sum(img, axis=2) != 0
+
+
+def lightVisualization():
+    points = []
+    for px in range(-5, 6):
+        for py in range(-5, 6):
+            for pz in range(-5, 6):
+                p = np.array([px, py, pz]).astype(np.float32) / 10
+                if np.linalg.norm(p) > 0:
+                    points.append(p / np.linalg.norm(p))
+    return points
+
+
+def cameraVisualization():
+    points = []
+    for p in range(-50, 51):
+        ps = float(p) / 100.0
+        points.append([ps, 0.5, 0.5])
+        points.append([ps, -0.5, 0.5])
+        points.append([ps, 0.5, -0.5])
+        points.append([ps, -0.5, -0.5])
+        points.append([0.5, ps, 0.5])
+        points.append([-0.5, ps, 0.5])
+        points.append([0.5, ps, -0.5])
+        points.append([-0.5, ps, -0.5])
+        points.append([0.5, 0.5, ps])
+        points.append([0.5, -0.5, ps])
[…]

### 2022-02-19 help_funs/ply_generator.py

@@ -1,0 +1,48 @@
+import numpy as np
+import torch
+import json
+
+from improved_normal_inference.help_funs.file_io import writePLY, load_8bitImage, load_24bitNormal, load_scaled16bitImage, \
+    get_file_name, get_output_file_name
+from improved_normal_inference.help_funs.mu import lightVisualization, cameraVisualization, depth2vertex
+
+
+def generate_ply(file_idx, normal, data_type, param=0):
+    image_file, ply_file, json_file, depth_file, normal_file = get_file_name(file_idx, data_type)
+
+    f = open(json_file)
+    data = json.load(f)
+    f.close()
+
+    data['R'] = np.identity(3)
+    data['t'] = np.zeros(3)
+
+    image = load_8bitImage(image_file)
+    depth = load_scaled16bitImage(depth_file, data['minDepth'], data['maxDepth'])
+    vertex = depth2vertex(torch.tensor(depth).permute(2, 0, 1),
+                          torch.tensor(data['K']),
+                          torch.tensor(data['R']).float(),
+                          torch.tensor(data['t']).float())
+
+    mask = np.sum(np.abs(normal), axis=2) != 0
+    cameraPoints = cameraVisualization()
+    for i in range(len(cameraPoints)):
+        cameraPoints[i] = np.array(data['R']).transpose() @ cameraPoints[i] / 4 - np.array(
+            data['R']).transpose() @ np.array(data['t'])
+    lightPoints = lightVisualization()
+    for i in range(len(lightPoints)):
+        lightPoints[i] = lightPoints[i] / 8 + np.array(data['lightPos'])
+
+    writePLY(vertex, normal, image, mask, ply_file,
+             cameraPoints=cameraPoints,
+             lightPoints=lightPoints)
+    print(f"Saved {file_idx}-th ply file {ply_file}...")
+
+
+if __name__ == '__main__':
+    file_idx = 0
+    data_type = "synthetic_basic"
+
+    image_file, ply_file, json_file, depth_file, normal_file = get_file_name(file_idx, data_type)
+    normal = load_24bitNormal(normal_file)
+    generate_ply(file_idx, normal, data_type=data_type)

### 2022-02-19 knn_normal.py

@@ -4,18 +4,15 @@ import cv2 as cv
 import numpy as np
 import torch
 
+import improved_normal_inference.help_funs.file_io
+import improved_normal_inference.help_funs.mu
 from improved_normal_inference.help_funs import file_io, mu
-from improved_normal_inference.help_funs.file_io import copy_make_border
-from improved_normal_inference.help_funs.mu import normal2RGB
-from ply_generator import generate_ply
-
-k_min, k_max = 2, 3
-data_type = "synthetic_basic"
+from improved_normal_inference.help_funs.mu import normal2RGB, copy_make_border
+from improved_normal_inference.help_funs.ply_generator import generate_ply
 
 
 # data_type = "synthetic_captured"
 # data_type = "real"
-
 
 def compute_normal(vertex, mask, k):
     normals = np.zeros(shape=vertex.shape)
@@ -60,10 +57,10 @@ def knn_normal(file_idx, k_min=1, k_max=3):
         data['t'] = np.zeros(3)
 
         # calculate vertex from depth map
-        vertex = file_io.depth2vertex(torch.tensor(depth_padded).permute(2, 0, 1),
-                                      torch.tensor(data['K']),
-                                      torch.tensor(data['R']).float(),
-                                      torch.tensor(data['t']).float())
+        vertex = improved_normal_inference.help_funs.mu.depth2vertex(torch.tensor(depth_padded).permute(2, 0, 1),
+                                                                     torch.tensor(data['K']),
+                                                                     torch.tensor(data['R']).float(),
+                                                                     torch.tensor(data['t']).float())
         mask = np.sum(np.abs(depth_padded), axis=2) != 0
 
         # compute normals from neighbors
@@ -71,7 +68,7 @@ def knn_normal(file_idx, k_min=1, k_max=3):
         normals_rgb = normal2RGB(normals, mask)
         # generate point clouds, save calculated normal image and ground truth image
         generate_ply(file_idx, normals, data_type=data_type, param=k_idx)
-        file_io.write_np2img(normals_rgb, file_io.get_output_file_name(file_idx, "normal", "knn", data_type, k_idx))
+        improved_normal_inference.help_funs.file_io.write_np2img(normals_rgb, file_io.get_output_file_name(file_idx, "normal", "knn", data_type, k_idx))
[…]

### 2022-02-19 pncnn/workspace/synthetic/pncnn/network.py

@@ -1,0 +1,35 @@
+########################################
+__author__ = "Abdelrahman Eldesokey"
+__license__ = "GNU GPLv3"
+__version__ = "0.1"
+__maintainer__ = "Abdelrahman Eldesokey"
+__email__ = "abdo.eldesokey@gmail.com"
+########################################
+
+import torch
+import torch.nn as nn
+
+from improved_normal_inference.pncnn.common.unet import UNetSP
+from improved_normal_inference.pncnn.common.nconv import NConvUNet
+
+
+class CNN(nn.Module):
+    def __init__(self):
+        super().__init__() 
+        self.__name__ = 'pncnn'
+
+        # input confidence estimation network
+        self.conf_estimator = UNetSP(1, 1)
+        self.nconv = NConvUNet(1, 1)
+        self.var_estimator = UNetSP(1, 1)
+
+    def forward(self, x0):  
+
+        c0 = self.conf_estimator(x0) #  estimate the input confidence
+        xout, cout = self.nconv(x0, c0) # estimated value of depth
+        cout = self.var_estimator(cout) #
+        out = torch.cat((xout, cout, c0), 1)
+        return out
+        
+       
+

### 2022-05-08 help_funs/mu.py
modify ng, change ReLU to LeakyReLU, add one more layer in upsampling update latex

@@ -1,9 +1,7 @@
-import math
-import itertools
 import cv2 as cv
 import numpy as np
 import torch
-import torch.nn.functional as F
+import json
 import matplotlib.pyplot as plt
 
 
@@ -643,3 +641,35 @@ def filter_bg(normal_img):
         normal_img[bg_mask] = 0
 
     return normal_img
+
+
+def visual_input(depth, data, output_name):
+    data['R'] = np.identity(3)
+    data['t'] = np.zeros(3)
+    vertex = depth2vertex(torch.tensor(depth).permute(2, 0, 1),
+                          torch.tensor(data['K']),
+                          torch.tensor(data['R']).float(),
+                          torch.tensor(data['t']).float())
+    mask = vertex.sum(axis=2) == 0
+    # move all the vertex as close to original point as possible, and noramlized all the vertex
+    range_0 = vertex[:, :, :1][~mask].max() - vertex[:, :, :1][~mask].min()
+    range_1 = vertex[:, :, 1:2][~mask].max() - vertex[:, :, 1:2][~mask].min()
+    range_2 = vertex[:, :, 2:3][~mask].max() - vertex[:, :, 2:3][~mask].min()
+
+    vertex[:, :, :1][~mask] = (vertex[:, :, :1][~mask] - vertex[:, :, :1][~mask].min()) / range_0
+    vertex[:, :, 1:2][~mask] = (vertex[:, :, 1:2][~mask] - vertex[:, :, 1:2][~mask].min()) / range_1
+    vertex[:, :, 2:3][~mask] = (vertex[:, :, 2:3][~mask] - vertex[:, :, 2:3][~mask].min()) / range_2
+
+    vectors = vertex
+    vectors[mask] = 0
+
+    input_torch = torch.from_numpy(vectors.astype(np.float32))  # (depth, dtype=torch.float)
+    input_torch = input_torch.permute(2, 0, 1)
+    input_torch = input_torch.unsqueeze(0)
+    input = tenor2numpy(input_torch[:1, :3, :, :])
+    x0_normalized_8bit = normalize2_8bit(input)
+    x0_normalized_8bit = image_resize(x0_normalized_8bit, width=512, height=512)
+
+    output = cv.cvtColor(x0_normalized_8bit, cv.COLOR_RGB2BGR)
+    output_name = str(f"{output_name}.png")
+    cv.imwrite(output_name, output)

### 2022-05-08 help_funs/worksheet.py

@@ -1,0 +1,17 @@
+import mu
+import file_io
+import json
+
+data_file = "D:\\TUK\\improved_normal_inference\\paper\\pic\\00440.data0.json"
+depth_file = "D:\\TUK\\improved_normal_inference\\paper\\pic\\00440.depth0_noise.png"
+
+f = open(data_file)
+data = json.load(f)
+f.close()
+
+depth = file_io.load_scaled16bitImage(depth_file,
+                                      data['minDepth'],
+                                      data['maxDepth'])
+
+output_name = "00440.vertex"
+mu.visual_input(depth, data, output_name)

### 2022-05-09 paper/introduction.tex
add noise net model update paper

%% add noise image
\begin{figure}[!h]
	\centering
	\begin{tikzpicture}
		\node[inner sep=0pt] (depthmap) at (0,0)
		{\includegraphics[width=.5\textwidth]{./pic/00028.normal0.png}};
	\end{tikzpicture}
\end{figure}

### 2022-05-09 common/UNet.py

@@ -1,0 +1,89 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+
+
+class UNet(nn.Module):
+    def __init__(self, in_ch, out_ch):
+        super().__init__()
+        self.__name__ = 'unet'
+        kernel_down = (3, 3)
+        kernel_up = (3, 3)
+        padding_down = (1, 1)
+        padding_up = (1, 1)
+        stride = (1, 1)
+        stride_2 = (2, 2)
+
+        dilate1 = (2, 2)
+        dilate2 = (4, 4)
+        dilate3 = (8, 8)
+        dilate4 = (16, 16)
+
+        self.active_f = nn.Sigmoid()
+
+        self.epsilon = 1e-20
+        channel_size_1 = 32
+        channel_size_2 = 64
+        # https://homepages.inf.ed.ac.uk/rbf/CVonline/LOCAL_COPIES/PIRODDI1/NormConv/node2.html#:~:text=The%20idea%20of%20normalized%20convolution,them%20is%20equal%20to%20zero.
+
+        self.dconv1 = nn.Conv2d(in_ch, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv2 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv3 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv4 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
+
+        self.dilated1 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down, dilate1)
+        self.dilated2 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down, dilate2)
+        self.dilated3 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down, dilate3)
+        self.dilated4 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down, dilate4)
+
+        self.uconv1 = nn.Conv2d(channel_size_2, channel_size_1, kernel_up, stride, padding_up)
+        self.uconv2 = nn.Conv2d(channel_size_2, channel_size_1, kernel_up, stride, padding_up)
[…]

### 2022-05-09 help_funs/data_preprocess.py

@@ -12,11 +12,11 @@ import config
 from help_funs import file_io, mu
 
 
-def noisy_1channel(img):
+def noisy_1channel(img, noise_templete):
     img = img.reshape(512, 512)
     h, w = img.shape
     noise = np.random.randint(2, size=(h, w))
-    noise_img = img * noise
+    noise_img = img * noise * noise_templete
     return noise_img
 
 
@@ -30,18 +30,22 @@ def noisy(img):
 
 
 def noisy_a_folder(folder_path, output_path):
+    # get all the normal files from 'Real' dataset
+    normal_files = np.array(sorted(glob.glob(str(config.real_data / "*normal?.png"), recursive=True)))
+
     if not os.path.exists(output_path):
         os.makedirs(output_path)
-    for idx in range(500):
+    for idx in range(1000):
         image_file, ply_file, json_file, depth_gt_file, _, normal_file = file_io.get_file_name(idx, folder_path)
         if path.exists(image_file):
             f = open(json_file)
             data = json.load(f)
             # normal_gt = cv.imread(normal_file)
             depth = file_io.load_scaled16bitImage(depth_gt_file, data['minDepth'], data['maxDepth'])
-
+            random_real_normal = file_io.load_24bitNormal(np.random.choice(normal_files)).astype(np.float32)
+            noise_templete = random_real_normal.sum(axis=2) != 0
             # add noise
-            noise_depth = noisy_1channel(depth)
+            noise_depth = noisy_1channel(depth, noise_templete)
 
             # save files to the new folders
             file_io.save_scaled16bitImage(noise_depth,
@@ -165,77 +169,103 @@ def convert2training_tensor(path, k, output_type='normal'):
         print(f'File {item} converted to tensor.')
 
 
-def convert2training_tensor2(path, k, input_size=1000):
+def convert2training_tensor_noise(path):
+    k = 0
+    output_type = 'noise'
     if not os.path.exists(str(path)):
         raise FileNotFoundError
     if not os.path.exists(str(path / "tensor")):
         os.makedirs(str(path / "tensor"))
 
-    depth_files = np.array(sorted(glob.glob(str(path / "*depth0.png"), recursive=True)))
-    gt_files = np.array(sorted(glob.glob(str(path / "*normal0.png"), recursive=True)))
[…]

### 2022-05-09 main.py

@@ -1,12 +1,11 @@
 import config
-from help_funs.data_preprocess import noisy_a_folder, convert2training_tensor, convert2training_tensor2
+from help_funs.data_preprocess import noisy_a_folder, convert2training_tensor
 from workspace import train
 from pncnn.utils import args_parser
 
 import workspace.nnn.network as nnn
 import workspace.nnn24.network as nnn24
 import workspace.nnnn.network as nnnn
-import workspace.nnnx.network as nnnx
 import workspace.ng.network as ng
 
 
@@ -14,18 +13,17 @@ def main():
     args = args_parser.args_parser()
     if args.noise:
         for folder in ["selval", "test", "train"]:
+            # add noise
             original_folder = config.synthetic_data / folder
             if args.machine == "remote":
-                noisy_folder = config.synthetic_data_noise_dfki / folder
+                dataset_folder = config.synthetic_data_noise_dfki / folder
             elif args.machine == 'local':
-                noisy_folder = config.synthetic_data_noise / folder
+                dataset_folder = config.synthetic_data_noise / folder
             else:
                 raise ValueError
-            noisy_a_folder(original_folder, noisy_folder)
-            if args.exp == "nnnx":
-                convert2training_tensor2(noisy_folder, 3)
-            else:
-                convert2training_tensor(noisy_folder, args.neighbor, output_type=args.output_type)
+            noisy_a_folder(original_folder, dataset_folder)
+            # convert to tensor
+            convert2training_tensor(dataset_folder, args.neighbor, output_type=args.output_type)
 
     # config experiments
     exp_path = config.ws_path / args.exp
@@ -35,8 +33,6 @@ def main():
         model = nnn24.CNN()
     elif args.exp == "nnnn":
         model = nnnn.CNN()
-    elif args.exp == "nnnx":
-        model = nnnx.CNN()
     elif args.exp == "ng":
         model = ng.CNN()
     else:

### 2022-05-09 workspace/noise_net/network.py

@@ -1,0 +1,20 @@
+import sys
+from os.path import dirname
+
+sys.path.append(dirname(__file__))
+
+import torch
+import torch.nn as nn
+from common.UNet import UNet
+from help_funs import mu
+
+
+class CNN(nn.Module):
+    def __init__(self):
+        super().__init__()
+        self.__name__ = 'noise_net'
+        self.noise_net = UNet(1, 1)
+
+    def forward(self, x0):
+        xout = self.noise_net(x0)
+        return xout

### 2022-05-16 paper/related_work.tex
add normalized convolution network
update paper
update paper 1. add related works

@@
 
+In 2018, Yu et al. \cite{gconv} presented a CNN based method with guided
+
+In 2019, Ben-Shabat et al. \cite{Ben-Shabat_2019_CVPR} presented a CNN based method.
+
 In 2021, Zhou et al.  \cite{zhou2021fast}
+
+\section{Sparse Input processing}
+%% gconv, nconv, median filter...
+The depth-map captured by active sensors are usually full with missing pixels and holes. Thus a preprocessing for the depth map is necessary before it is fed into a neural network.
+
+Generally, it can be solved as image inpainting problems.\cite{inpainting1},\cite{inpainting2}.
+Recently, some deep learning based method for image inpainting achieved quite good performance for the hole mending task.
+Notably, in 2016, Oord et al. \cite{gated_activation} proposed a gated activation unit for a CNN model,
+\[\textbf{y} = \tanh (W_{k,f} * \textbf{x}) \odot \sigma (W_{k,g} * \textbf{x})\]
+to substitute the standard activation layer, where $ \sigma $ is the sigmoid function, which constricts the output value of second part between $ [0,1] $.
+The function is inspired by Long Short-Term Memory (LSTM) \cite{lstm} and Rated Recurrent Unit (GRU).\cite{gru} It is originally used for learning complex interactions as LSTM gates does.
+In 2018, Yu et al.
+\cite{gconv} employed same function for free-form image inpainting, which can be used to learn mask automatically from image it self.
+
+Different to aforementioned approaches, Knutsson et al. in 2005 introduced normalized convolution \cite{nconv} dealing with missing sample case for convolution operation. 
+In 2018, Eldesokey et al.
+\cite{ncnn} applied normalized convolution in CNN as normalized convolution layer that takes both sparse depth map and a binary confidence map as input to perform scene depth completion.
+In 2020, Eldesokey et al. \cite{pncnn} focus on modeling the uncertainty of depth data instead of assuming binary input confidence.
+
+\section{Normal Inference}

### 2022-05-17 paper/introduction.tex
update paper 1. add related works
1. add model: ng + resnet 2. update paper

@@
+%%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%
+
+%% standard method for normal inference is insufficient, input is sparse, not robust enough
+Standard methods compute normals from point cloud using neighboring information in image space or use Shape from Shading.
+However, the point clouds captured by sensors like Kinect or similar RGB-D, LiDAR sensors are only semi-dense.
+As shown in Figure \ref{fig:standard_normal_inference}.
+If map these normals to mesh, that is not good at all.
+Standard methods dependents on chosen neighbor size, if too small, it has larger noise sensitive, if too large, the output will too smooth and not crispy.
+Errors may occur in regions with inter-reflections, where we have errors in the 3D measurement.
+
 %% add noise image
@@
 	\begin{tikzpicture}
+
 		\node[inner sep=0pt] (depthmap) at (0,0)
-		{\includegraphics[width=.5\textwidth]{./pic/00028.normal0.png}};
+		{\includegraphics[width=.3\textwidth]{./pic/00028.depth0.png}};
+
+		\path [line] (3,0) -- node [text width=1.5cm,midway,above ] {SVD/PCA} (5,0);
+
+		\node[inner sep=0pt] (normal) at (8,0)
+		{\includegraphics[width=.3\textwidth]{./pic/00028.normal0.png}};
 	\end{tikzpicture}
+\caption{Left: Depth Map, Right: Semi-dense Normal Map}
+\label{fig:standard_normal_inference}
 \end{figure}
+
+%% there exists space for improvment 
+Although the depth image is incomplete, the depth sensor usually able to capture grayscale texture image, which are typically fully dense due to their passive nature.
+Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, etc.
+Thus the normal can be inferenced better using the given image information and depth map.
+
+%%%%%%%%%%%%%%%%%%% talk about the chanllege of this task %%%%%%%%%%%%%%%%%%
+Both depth and grayscale image are initially relevant to the machine learning algorithms.
+Based grayscale image and corresponding semi-dense depth map, a CNN model can be designed to inference the normal map, which gives more density and robust comparing to standard algorithm.
+However, the missing pixels in depth map can be distributed around the whole image, some of the region leaves complete empty pixels.
+This situation imposes further processing for the missing regions and some other challenges on the machine learning methods.
+In this thesis, we found a solution for the problems mentioned above.
+
+%% improved normal inference figure
+\begin{figure}[!h]
+	\centering
+	\begin{tikzpicture}
+
+		\node[inner sep=0pt] (image) at (0,0)
+		{\includegraphics[width=.2\textwidth]{./pic/00028.image0.png}};
+
+		\node[text width=1cm] at (2,0) {$ + $};
+
+		\node[inner sep=0pt] (depthmap) at (3.3,0)
+		{\includegraphics[width=.2\textwidth]{./pic/00028.depth0.png}};
+		\node[text width=1cm] at (8,0) {$ ? $};
+
+		\path [line] (5,0) -- node [text width=1cm,midway,above ] {CNN} (6,0);
+
+	\end{tikzpicture}
+	\caption{Left: Grayscale Image, Middle: Depth Map}
+	\label{fig:improved_normal_inference}
+\end{figure}

### 2022-05-17 paper/related_work.tex
1. add model: ng + resnet 2. update paper

@@
-In order to estimate normals of an object surface.
+\section{Sparse Input processing}
+
+%% methods deal with sparse input, like nconv, gconv ...
+The depth map is supposed to be dense.
+Therefore, how to accept sparse depth map as input in CNNs is one of the most important problem.
+Some trivial solutions like median filters are good enough, if the missing pixels are sparse enough, however, for the case of huge missing holes in the depth map, it produces just a paltry result.
+Thus a reasonable guess is required for missing areas.
+Generally, it can be solved as image inpainting problems,\cite{inpainting1},\cite{inpainting2}.
+
+%% Deep learning based approaches
+Some deep learning based method for image inpainting also achieved quite good performance for the hole mending task. 
+%% talk about gconv
+Notably, in 2016, Oord et al. \cite{gated_activation} proposed a gated activation unit for a CNN model,
+\[\textbf{y} = \tanh (W_{k,f} * \textbf{x}) \odot \sigma (W_{k,g} * \textbf{x})\]
+to substitute the standard activation layer, where $ \sigma $ is the sigmoid function, which constricts the output value of second part between $ [0,1] $.
+The function is inspired by Long Short-Term Memory (LSTM) \cite{lstm} and Rated Recurrent Unit (GRU).\cite{gru} It is originally used for learning complex interactions as LSTM gates does.
+In 2018, Yu et al.
+\cite{gconv} employed same function for free-form image inpainting, which can be used to learn mask automatically from image it self.
+
+%% talk about nconv
+Different to aforementioned approaches, Knutsson et al.
+in 2005 introduced normalized convolution \cite{nconv} dealing with missing sample case for convolution operation, which aims to reconstruct the missing pixels from the sparse output sensed by cameras, which particularly considered the confidence of each interpolated pixels, since it provides the trustworthiness of the predicted value.
+The higher the reliability of the value inference, the better the model shape reconstruction.
+
+In 2018, Eldesokey et al.
+\cite{ncnn} applied normalized convolution in CNN as normalized convolution layer that takes both sparse depth map and a binary confidence map as input to perform scene depth completion.
+In 2020, Eldesokey et al. \cite{pncnn} focus on modeling the uncertainty of depth data instead of assuming binary input confidence.
+
+\section{Normal Inference}
+
+%% normal estimation method introduction
+Ideally, the normal of each pixel in the depth map can be calculated based on its neighbor pixels constructing a over-determined function systems and solving by algebra methods\cite{geometry_based_solution}.
+This approach gives a quick but coarse normal inference.
+It also can be predict directly by feeding the image directly into a CNN \cite{Eigen}, in this case, no depth map is required.
+GeoNet\cite{GeoNet} integrates both ideas to refine the coarse normal map with another CNN predicted normal map. 
+%% traditional methods
 
@@
 
-In 2018, Yu et al. \cite{gconv} presented a CNN based method with guided
+In 2018, Yu et al. \cite{gconv} presented a CNN based method with gated convolutional layer.
+
+In 2018, Hua et al. \cite{guided} presented an approach integrating color image and certainty map into the network to enhance the performance of depth map density.
 
@@
 
-\section{Sparse Input processing}
-%% gconv, nconv, median filter...
-The depth-map captured by active sensors are usually full with missing pixels and holes. Thus a preprocessing for the depth map is necessary before it is fed into a neural network.
+%% CNN based methods
+The deep convolutional neural network is typically used for image classification, which achieved great success in last several years. \cite{yolov3}, \cite{efficientDet}.
 
-Generally, it can be solved as image inpainting problems.\cite{inpainting1},\cite{inpainting2}.
-Recently, some deep learning based method for image inpainting achieved quite good performance for the hole mending task.
-Notably, in 2016, Oord et al. \cite{gated_activation} proposed a gated activation unit for a CNN model,
-\[\textbf{y} = \tanh (W_{k,f} * \textbf{x}) \odot \sigma (W_{k,g} * \textbf{x})\]
-to substitute the standard activation layer, where $ \sigma $ is the sigmoid function, which constricts the output value of second part between $ [0,1] $.
-The function is inspired by Long Short-Term Memory (LSTM) \cite{lstm} and Rated Recurrent Unit (GRU).\cite{gru} It is originally used for learning complex interactions as LSTM gates does.
-In 2018, Yu et al.
-\cite{gconv} employed same function for free-form image inpainting, which can be used to learn mask automatically from image it self.
+%% talk about the reason we need new type of network architecture
+These kinds of network architecture takes a single image as input which usually employed for classification problems.
+The image is usually convoluted with convolutional layer and downsampling with pooling layers.
+The outputs of the network consists of a single value to represent the ID of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.
 
-Different to aforementioned approaches, Knutsson et al. in 2005 introduced normalized convolution \cite{nconv} dealing with missing sample case for convolution operation. 
-In 2018, Eldesokey et al.
-\cite{ncnn} applied normalized convolution in CNN as normalized convolution layer that takes both sparse depth map and a binary confidence map as input to perform scene depth completion.
-In 2020, Eldesokey et al. \cite{pncnn} focus on modeling the uncertainty of depth data instead of assuming binary input confidence.
+However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted.
+In this case, the traditional network architecture is not suitable anymore.
 
-\section{Normal Inference}
+%% talk about image upsampling, unet
+Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations.
+The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers to upsampling layers, thus in the end of the second half, the output is back to the input size.
+The proposed network can successfully assigned each pixel a class for segmentation tasks.
+Under this symmetric network, an input image is downsampled 3 times and upsampled 3 times.
+Output image has exactly the same size as input image.
+The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{./ref/u-net-illustration-correct-scale2}
+	\caption{U-net architecture (example for 32x32 pixels in the lowest resolution).
+Each blue box corresponds to a multi-channel feature map.
+The number of channels is denoted on top of the box.
+The x-y-size is provided at the lower left edge of the box.
+White boxes represent copied feature maps.
+The arrows denote the different operations.
+	}
+	\label{fig:u-net}
+\end{figure}
+
+%% guided scene completion

### 2022-05-17 main.py

@@ -7,6 +7,7 @@ import workspace.nnn.network as nnn
 import workspace.nnn24.network as nnn24
 import workspace.nnnn.network as nnnn
 import workspace.ng.network as ng
+import workspace.resng.network as resng
 
 
 def main():
@@ -35,6 +36,8 @@ def main():
         model = nnnn.CNN()
     elif args.exp == "ng":
         model = ng.CNN()
+    elif args.exp == "resng":
+        model = resng.CNN()
     else:
         raise ValueError("Unknown exp path")
     if args.machine == 'local':

### 2022-05-17 workspace/eval.py

@@ -68,7 +68,7 @@ def eval(v, model_path, k, output_type='rgb', img=None):
     normal, normal_img, eval_point_counter, total_time = evaluate_epoch(model, input_tensor, start_epoch, device,
                                                                         output_type)
 
-    normal_img = mu.filter_bg(normal_img)
+    normal_img = mu.filter_gray_color(normal_img)
     normal_img = normal_img.astype(np.float32)
     normal_img = mu.normalize2_8bit(normal_img)
 

### 2022-05-17 paper/introduction.tex
1.add parameter cout to resng/args.json 2. update paper 3. ignore update of args.json

@@
 
+%% CNN based methods
+The deep convolutional neural network is typically used for image classification, which achieved great success in last several years. \cite{yolov3}, \cite{efficientDet}. 
+%% talk about the reason we need new type of network architecture
+These kinds of network architecture takes a single image as input which usually employed for classification problems.
+The image is usually convoluted with convolutional layer and downsampling with pooling layers.
+The outputs of the network consists of a single value to represent the ID of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.
+
+However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted.
+In this case, the traditional network architecture is not suitable anymore.
+
 %% improved normal inference figure

### 2022-05-17 paper/related_work.tex
1.add parameter cout to resng/args.json 2. update paper 3. ignore update of args.json

@@
 
+Guided method \cite{guided} requires addition information like RGB image or the certainty map of depth map, and fuse them together to predict the dense depth map.
+
 \section{Normal Inference}
@@
 %% normal estimation method introduction
-Ideally, the normal of each pixel in the depth map can be calculated based on its neighbor pixels constructing a over-determined function systems and solving by algebra methods\cite{geometry_based_solution}.
-This approach gives a quick but coarse normal inference.
-It also can be predict directly by feeding the image directly into a CNN \cite{Eigen}, in this case, no depth map is required.
-GeoNet\cite{GeoNet} integrates both ideas to refine the coarse normal map with another CNN predicted normal map. 
-%% traditional methods
+Usually, we based on point cloud, depth map or RGB/Grayscale image of the objects or scenes to inference the normals.
 
-In 2012, Holzer et al.
-\cite{Holzer.S} presented a read-time method, which is able to run algorithm in a high frame speed.
+Traditional methods evaluate normals based on neighbor information of point cloud or depth map.
+In 2012, Holzer et al. \cite{Holzer.S} proposed method to calculate normal from covariance matrices. 
+This method use integral image as input, which is able to run algorithm in a high frame speed.
 They smooth the depth data in order to handle the noise of depth image.
-The speed is accelerated via integral image.
 The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.
-
-In 2018, Yu et al. \cite{gconv} presented a CNN based method with gated convolutional layer.
-
-In 2018, Hua et al. \cite{guided} presented an approach integrating color image and certainty map into the network to enhance the performance of depth map density.
-
-In 2019, Ben-Shabat et al. \cite{Ben-Shabat_2019_CVPR} presented a CNN based method.
-
-In 2021, Zhou et al.  \cite{zhou2021fast}
+In 2013, Fouhey et al.
+\cite{geometry_based_solution} proposed a method constructing a over-determined function systems to predict normals and solving it
+by algebra methods. Similarly, this approach gives a quick but coarse normal inference.
 
 %% CNN based methods
-The deep convolutional neural network is typically used for image classification, which achieved great success in last several years. \cite{yolov3}, \cite{efficientDet}.
+Recently, CNN based methods improve the performance of image processing to a brand new stage.
+In 2014, Eigen et al.\cite{Eigen} proposed a method predicting depth map directly from RGB image using CNN.
+In this case, no depth map is required.
+In 2016, Laina et al.
+\cite{img2depth} proposed a deeper network based on ResNet \cite{resnet} with a well designed upsamling part.
+%% guided scene completion
+In 2018, Qi et al. proposed GeoNet\cite{GeoNet}, it integrates both algebra method and also CNN method to inference depthmap based on \cite{img2depth} \cite{geometry_based_solution}.
 
-%% talk about the reason we need new type of network architecture
-These kinds of network architecture takes a single image as input which usually employed for classification problems.
-The image is usually convoluted with convolutional layer and downsampling with pooling layers.
-The outputs of the network consists of a single value to represent the ID of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.
-
-However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted.
-In this case, the traditional network architecture is not suitable anymore.
-
+%% upsampling 
+It is worth to noticed that, the output of normal inference CNN model is not one or severl labels but an entire image or normal map with same size. 
 %% talk about image upsampling, unet
 Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations.
-The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers to upsampling layers, thus in the end of the second half, the output is back to the input size.
+The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size.
 The proposed network can successfully assigned each pixel a class for segmentation tasks.
@@
 
-%% guided scene completion
+%% unstructured point cloud 
+In some case, the input is unstructured point cloud which can not be fed into a CNN entirely.
+Thus, a challenge task connect to the deep learning is the input format.
+Since different point clouds have different sizes.
+In 2018, Ben-Shabat et al.
+\cite{Ben-Shabat_2019_CVPR} presented Nesti-Net.
+It predicts the normal point by point with the help of neighbor points.
+It fixed the distance of considering neighbors to provide an unified input for CNN.
+In 2021, Zhou et al.
+\cite{zhou2021fast} presents a method considering overlapping of different patches (a group of neighboring points) as input to evaluate normals.

### 2022-05-18 paper/discussion.tex
fix a bug in data_preprocess

\section{Dataset Normalization}
%% How to represent input tensor, to make it fast converse

The vertices have been normalized before feed them into the model.

The depth range of each scene is shown in Figure \ref{fig:data_range}.

Z axis in range [4,6]
Y axis in range [-1,1]
Y axis in range [-1,1]

\begin{figure}
	\centering
	{\includegraphics[width=0.45\textwidth]{./pic/Data_Extreme.png}}
	{\includegraphics[width=0.45\textwidth]{./pic/Data_Range.png}}
	\label{fig:data_range}
	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
\end{figure}

Normalize the point cloud to a unit size.

The average range and extreme value is shown in Table \ref{tab:data_range}. Choose the biggest range as a scale factor to normalize the point cloud. Use Min value to move the point clouds close to original point as much as possible.

\begin{table}[t]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		Axis & Range & Min & Max\\
		\hline
		X & 1.48 & -0.75 & 0.73\\
		Y & \textbf{1.56} & -0.76 & 0.80\\
		Z & 1.47 & 6.53 & 8.00\\
		\hline
	\end{tabular}
	\caption{This is a table.}
	\label{tab:data_range}
\end{table}

### 2022-05-18 create_dataset.py

@@ -1,4 +1,3 @@
-
 import argparse
 
 import config
@@ -9,6 +8,9 @@ parser = argparse.ArgumentParser(description='Eval')
 # Machine selection
 parser.add_argument('--machine', type=str, default="local", choices=['local', 'remote'],
                     help="loading dataset from local or dfki machine")
+parser.add_argument('--max_k', type=int, default=2,
+                    help="loading dataset from local or dfki machine")
+
 args = parser.parse_args()
 
 for folder in ["train", "test"]:
@@ -21,6 +23,6 @@ for folder in ["train", "test"]:
     else:
         raise ValueError
     noisy_a_folder(original_folder, dataset_folder)
-    for k in range(3):
+    for k in range(args.max_k):
         print(f"K = {k}, {folder}")
         convert2training_tensor(dataset_folder, k=k, output_type="normal_noise")

### 2022-05-18 help_funs/worksheet.py

@@ -2,16 +2,94 @@ import mu
 import file_io
 import json
 
-data_file = "D:\\TUK\\improved_normal_inference\\paper\\pic\\00440.data0.json"
-depth_file = "D:\\TUK\\improved_normal_inference\\paper\\pic\\00440.depth0_noise.png"
+import os
+from pathlib import Path
+import json
+import numpy as np
+import torch
+import cv2 as cv
+import glob
+import shutil
 
-f = open(data_file)
-data = json.load(f)
-f.close()
+import config
+from help_funs import file_io, mu, chart
+from pncnn.utils import args_parser
 
-depth = file_io.load_scaled16bitImage(depth_file,
-                                      data['minDepth'],
-                                      data['maxDepth'])
 
-output_name = "00440.vertex"
-mu.visual_input(depth, data, output_name)
+##################
+
+def save_input():
+    data_file = "D:\\TUK\\improved_normal_inference\\paper\\pic\\00440.data0.json"
+    depth_file = "D:\\TUK\\improved_normal_inference\\paper\\pic\\00440.depth0_noise.png"
+
+    f = open(data_file)
+    data = json.load(f)
+    f.close()
+
+    depth = file_io.load_scaled16bitImage(depth_file,
+                                          data['minDepth'],
+                                          data['maxDepth'])
+
+    output_name = "00440.vertex"
+    mu.visual_input(depth, data, output_name)
+
+
+def save_data_range():
+    data_path = config.synthetic_data / "train"
+
+    if not os.path.exists(str(data_path)):
+        raise FileNotFoundError
+
+    depth_files = np.array(sorted(glob.glob(str(data_path / "*depth0.png"), recursive=True)))[:100]
+    data_files = np.array(sorted(glob.glob(str(data_path / "*data0.json"), recursive=True)))[:100]
+
+    data_extreme = np.zeros((6, depth_files.shape[0]))
+    data_range = np.zeros((3, depth_files.shape[0]))
+    for item in range(len(data_files)):
+        f = open(data_files[item])
+        data = json.load(f)
+        f.close()
+
+        depth = file_io.load_scaled16bitImage(depth_files[item],
+                                              data['minDepth'],
+                                              data['maxDepth'])
+
+        data['R'] = np.identity(3)
[…]

### 2022-05-22 help_funs/data_preprocess.py
update dataset normalization

@@ -167,9 +167,10 @@ def convert2training_tensor(path, k, output_type='normal'):
     data_files = np.array(sorted(glob.glob(str(path / "*data0.json"), recursive=True)))
     img_files = np.array(sorted(glob.glob(str(path / "*image0.png"), recursive=True)))
     for item in range(len(data_files)):
-        if os.path.exists(str(path / "tensor" / f"{str(item).zfill(5)}_input_{k}_{output_type}.pt")):
+        if os.path.exists(str(path / "tensor" / f"{str(item).zfill(5)}_{k}_{output_type}.pth.tar")):
             continue
 
+        # input vertex
         f = open(data_files[item])
         data = json.load(f)
         f.close()
@@ -187,46 +188,42 @@ def convert2training_tensor(path, k, output_type='normal'):
                                  torch.tensor(data['R']).float(),
                                  torch.tensor(data['t']).float())
         mask = vertex.sum(axis=2) == 0
-        # move all the vertex as close to original point as possible, and noramlized all the vertex
 
+        # move all the vertex as close to original point as possible, and noramlized all the vertex
         x_range = vertex[:, :, 0][~mask].max() - vertex[:, :, 0][~mask].min()
         y_range = vertex[:, :, 1][~mask].max() - vertex[:, :, 1][~mask].min()
         z_range = vertex[:, :, 2][~mask].max() - vertex[:, :, 2][~mask].min()
+        zzz = np.argmax(np.array([x_range, y_range, z_range]))
+        scale_factors = [x_range, y_range, z_range]
 
-        scale_factor = max(x_range, y_range, z_range)
+        vertex[:, :, :1][~mask] = (vertex[:, :, :1][~mask] - vertex[:, :, 0][~mask].min()) / scale_factors[0]
+        vertex[:, :, 1:2][~mask] = (vertex[:, :, 1:2][~mask] - vertex[:, :, 1][~mask].min()) / scale_factors[0]
+        vertex[:, :, 2:3][~mask] = (vertex[:, :, 2:3][~mask] - vertex[:, :, 2][~mask].min()) / scale_factors[0]
 
-        v_min, v_max = vertex[~mask].min(), vertex[~mask].max()
-
-        vertex[:, :, :1][~mask] = (vertex[:, :, :1][~mask] - vertex[:, :, 0][~mask].min()) / scale_factor
[…]

### 2022-05-23 paper/discussion.tex
update dataset normalization
add DeGaRes model

@@
 
-The vertices have been normalized before feed them into the model.
-
-The depth range of each scene is shown in Figure \ref{fig:data_range}.
-
-Z axis in range [4,6]
-Y axis in range [-1,1]
-Y axis in range [-1,1]
-
-\begin{figure}
+The vertices have been normalized before feed them into the model. The depth range of each scene is shown in Figure \ref{fig:data_range}.
+The sizes of each training object are various, whereas it should be as an invariant value for the training model.
+Thus the normalization is required before feed training objects into the models.
+Figure \ref{fig:data_range} shows the fluctuation of extreme values and their ranges in 100 random training items.
+Table \ref{tab:data_range} gives the corresponding average values.
+\begin{figure}[!h]
 	\centering
@@
 
-Normalize the point cloud to a unit size.
-
-The average range and extreme value is shown in Table \ref{tab:data_range}.
-Choose the biggest range as a scale factor to normalize the point cloud.
-Use Min value to move the point clouds close to original point as much as possible.
-
-\begin{table}[t]
+\begin{table}[!h]
 	\centering
@@
 		X & 1.48 & -0.75 & 0.73\\
-		Y & \textbf{1.56} & -0.76 & 0.80\\
+		Y & 1.56 & -0.76 & 0.80\\
 		Z & 1.47 & 6.53 & 8.00\\
@@
 	\end{tabular}
-	\caption{This is a table.}
+	\caption{The ranges and extreme values of each axis.
+The extreme min and max values of both X axis and Y axis are close to $ -0.75 $ and $ 0.75 $ separately.
+The case for Z axis is $ 6.5 $ and $ 8.0 $ separately.
+However, the range of three axes are relatively similar, around 1.5.
+	}
 	\label{tab:data_range}
 \end{table}
+
+For the normalization, first we translate the point to the original point as much as possible, then choose the range value of one axis as a scale factor, normalize it to a unit object.
+
+\begin{equation}\label{eq:normalization}
+	U^a = (V^a - V^a_{min}) / s  \quad  \text{for } a \text{ in }  X,Y,Z \text{ axis}
+\end{equation}
+where $ V^a_{min} $ denote the minimum value appeared in axis $ a $, $ s $ is the range of an axis, which can be any one of X, Y, or Z axis.

### 2022-05-23 common/ResNormalGuided.py

@@ -85,7 +85,6 @@ class NormalGuided(nn.Module):
 
 
     def forward(self, x1, x_img_1, cin):
-        self.resnet50(x_img_1)
 
         x1 = self.dconv1(x1)
         x1 = self.dconv2(x1)

### 2022-05-23 eval_visual.py

@@ -27,7 +27,7 @@ def preprocessing():
 
     # load data file names
     if args.data == "synthetic":
-        path = config.synthetic_data_noise / "test_visual"
+        path = config.synthetic_data_noise / "test"
     elif args.data == "real":
         path = config.real_data  # key tests 103, 166, 189,9
     else:
@@ -36,7 +36,7 @@ def preprocessing():
     all_names = [os.path.basename(path) for path in sorted(glob.glob(str(path / f"*.image?.png"), recursive=True))]
     all_names = np.array(all_names)
     eval_indices = [int(name.split(".")[0]) for name in all_names]
-    eval_indices = eval_indices
+    eval_indices = eval_indices[:5]
 
     # load test model names
     models = {
@@ -148,18 +148,19 @@ def model_eval(model_path, test_0_tensor, test_1_tensor, gt, name):
 def main():
     models, eval_idx, dataset_path, folder_path, eval_res, eval_date, eval_time = preprocessing()
 
-    test_0_input = np.array(
-        sorted(glob.glob(str(dataset_path / "tensor" / f"*_input_0_normal_noise.pt"), recursive=True)))
-    test_1_input = np.array(
-        sorted(glob.glob(str(dataset_path / "tensor" / f"*_input_1_normal_noise.pt"), recursive=True)))
-    # test_0_input = np.array(sorted(glob.glob(str(dataset_path / "tensor" / f"*_input_0_normal_noise.pt"), recursive=True)))
-    test_gt = np.array(sorted(glob.glob(str(dataset_path / "tensor" / f"*_gt_0_normal_noise.pt"), recursive=True)))
+    test_0_data = np.array(
+        sorted(glob.glob(str(dataset_path / "tensor" / f"*_0_normal_noise.pth.tar"), recursive=True)))
+    test_1_data = np.array(
+        sorted(glob.glob(str(dataset_path / "tensor" / f"*_1_normal_noise.pth.tar"), recursive=True)))
 
     for i, data_idx in enumerate(eval_idx):
         # read data
-        test_0_tensor = torch.load(test_0_input[i]).unsqueeze(0)
-        test_1_tensor = torch.load(test_1_input[i]).unsqueeze(0)
-        gt_tensor = torch.load(test_gt[i]).unsqueeze(0)
+        test_0 = torch.load(test_0_data[i])
+        test_1 = torch.load(test_1_data[i])
+
[…]

### 2022-05-23 main.py

@@ -9,23 +9,11 @@ import workspace.nnnn.network as nnnn
 import workspace.ng.network as ng
 import workspace.resng.network as resng
 import workspace.nconv.network as nconv
+import workspace.degares.network as degares
 
 
 def main():
     args = args_parser.args_parser()
-    if args.noise:
-        for folder in ["train", "test"]:
-            # add noise
-            original_folder = config.synthetic_data / folder
-            if args.machine == "remote":
-                dataset_folder = config.synthetic_data_noise_dfki / folder
-            elif args.machine == 'local':
-                dataset_folder = config.synthetic_data_noise / folder
-            else:
-                raise ValueError
-            noisy_a_folder(original_folder, dataset_folder)
-            # convert to tensor
-            convert2training_tensor(dataset_folder, args.neighbor, output_type=args.output_type)
 
     # config experiments
     exp_path = config.ws_path / args.exp
@@ -41,8 +29,11 @@ def main():
         model = resng.CNN()
     elif args.exp == "nconv":
         model = nconv.CNN()
+    elif args.exp == "degares":
+        model = degares.CNN()
     else:
         raise ValueError("Unknown exp path")
+
     if args.machine == 'local':
         dataset_path = config.synthetic_data_noise
     elif args.machine == 'remote':

### 2022-05-23 workspace/deepfit/normal_estimation_utils.py

@@ -1,433 +1,0 @@
-# normal_estimation_utils.py normal estimation and 3DmFV utility functions
-# Author:Itzik Ben Sabat sitzikbs[at]gmail.com
-# If you use this code,see LICENSE.txt file and cite our work
-
-from sklearn.mixture import GaussianMixture
-from sklearn.preprocessing import normalize
-import os
-import pickle
-import numpy as np
-import torch
-
-from workspace.deepfit import provider
-
-
-def get_gmm(points, n_gaussians, NUM_POINT, type='grid', variance=0.05, n_scales=3, D=3):
-    """
-    Compute weights, means and covariances for a gmm with two possible types 'grid' (2D/3D) and 'learned'
-    Input:
-         points: num_points_per_model*nummodels X 3 - xyz coordinates
-         n_gaussians: scalar of number of gaussians /  number of subdivisions for grid type
-         NUM_POINT: number of points per model
-         type: 'grid' / 'leared' toggle between gmm methods
-         variance: gaussian variance for grid type gmm
-    Return:
-         gmm: gmm: instance of sklearn GaussianMixture (GMM) object Gauassian mixture model
-    """
-    if type == 'grid':
-        #Generate gaussians on a grid - supports only axis equal subdivisions
-        if n_gaussians >= 32:
-            print('Warning: You have set a very large number of subdivisions.')
-        if not(isinstance(n_gaussians, list)):
-            if D == 2:
-                gmm = get_2d_grid_gmm(subdivisions=[n_gaussians, n_gaussians], variance=variance)
-            elif  D == 3 :
-                gmm = get_3d_grid_gmm(subdivisions=[n_gaussians, n_gaussians, n_gaussians], variance=variance)
-            else:
-                ValueError('Wrong dimension. This supports either D=2 or D=3')
-
-    elif type == 'learn':
-        #learn the gmm from given data and save to gmm.p file, if already learned then load it from existing gmm.p file for speed
-        if isinstance(n_gaussians, list):
-            raise  ValueError('Wrong number of gaussians: non-grid value must be a scalar')
-        print("Computing GMM from data - this may take a while...")
[…]

### 2022-05-23 workspace/deepfit/train_n_est.py

@@ -1,597 +1,0 @@
-# train_n_est.py train a DeepFit model
-# Author:Itzik Ben Sabat sitzikbs[at]gmail.com
-# If you use this code,see LICENSE.txt file and cite our work
-
-from __future__ import print_function
-
-import argparse
-import os
-import sys
-import random
-import math
-import shutil
-import numpy as np
-import torch
-import torch.nn.parallel
-import torch.optim as optim
-import torch.optim.lr_scheduler as lr_scheduler
-import torch.utils.data
-# from tensorboardX import SummaryWriter # https://github.com/lanpa/tensorboard-pytorch
-from pathlib import Path
-
-from help_funs import chart
-
-BASE_DIR = os.path.dirname(os.path.abspath(__file__))
-BASE_DIR_PATH = Path(BASE_DIR)
-sys.path.append(BASE_DIR)
-sys.path.append(os.path.join(BASE_DIR_PATH, 'models'))
-sys.path.append(os.path.join(BASE_DIR, 'utils'))
-import normal_estimation_utils
-import DeepFit
-
-# from dataset import PointcloudPatchDataset, RandomPointcloudPatchSampler, SequentialShapeRandomPointcloudPatchSampler, SequentialPointcloudPatchSampler
-import utils
-import config
-
-
-def parse_arguments():
-    parser = argparse.ArgumentParser()
-
-    # naming / file handling
-    parser.add_argument('--name', type=str, default='DeepFit_no_noise', help='training run name')
-    parser.add_argument('--arch', type=str, default='simple', help='arcitecture name:  "simple" | "3dmfv"')
-    parser.add_argument('--desc', type=str, default='My training run for single-scale normal estimation.',
-                        help='description')
-    parser.add_argument('--indir', type=str, default='/home/sitzikbs/Datasets/pcpnet/',
-                        help='input folder (point clouds)')
-    parser.add_argument('--logdir', type=str, default=str(config.ws_path / "deepfit" / "log"),
-                        help='training log folder')
-    parser.add_argument('--trainset', type=str, default="synthetic_data_noise", help='training set file name')
-    parser.add_argument('--train_on', type=str, default="full", help='choose training size')
-    parser.add_argument('--testset', type=str, default='selval', help='test set file name')
-    parser.add_argument('--saveinterval', type=int, default='10', help='save model each n epochs')
-    parser.add_argument('--refine', action="store_true",
-                        help='flag to refine the model, path determined by outri and model name')
[…]

### 2022-05-23 workspace/eval.py

@@ -19,29 +19,7 @@ from workspace.svd import eval as svd
 from torch.utils.data import Dataset, DataLoader
 import glob
 
-
-class SyntheticDepthDataset(Dataset):
-
-    def __init__(self, data_path, k, output_type):
-        self.input = np.array(
-            sorted(
-                glob.glob(str(data_path / "tensor" / f"*_input_{k}_{output_type}.pt"), recursive=True)))
-        self.gt = np.array(
-            sorted(glob.glob(str(data_path / "tensor" / f"*_gt_{k}_{output_type}.pt"), recursive=True)))
-
-        assert (len(self.gt) == len(self.input))
-
-    def __len__(self):
-        return len(self.input)
-
-    def __getitem__(self, item):
-        if item < 0 or item >= self.__len__():
-            return None
-
-        input_tensor = torch.load(self.input[item])
-        gt_tensor = torch.load(self.gt[item])
-
-        return input_tensor, gt_tensor
+from workspace.train import SyntheticDepthDataset
 
 
 def eval(dataset_path, name, model_path, gpu=0):
@@ -50,7 +28,7 @@ def eval(dataset_path, name, model_path, gpu=0):
     # SVD model
     if model_path is None:
         # load dataset
-        dataset = SyntheticDepthDataset(dataset_path, 1, "normal_noise")
+        dataset = SyntheticDepthDataset(dataset_path, 1, "normal_noise", setname='test')
         data_loader = DataLoader(dataset, shuffle=True, batch_size=1, num_workers=1)
         loss_list, time_list = svd.eval(data_loader, 2)
         return loss_list, time_list
@@ -70,7 +48,7 @@ def eval(dataset_path, name, model_path, gpu=0):
     print("ok.")
     print("load dataset...", end="")
     # load dataset
-    dataset = SyntheticDepthDataset(dataset_path, args.neighbor, "normal_noise")
+    dataset = SyntheticDepthDataset(dataset_path, args.neighbor, "normal_noise", setname='test')
     data_loader = DataLoader(dataset,
                              shuffle=True,
                              batch_size=1,
@@ -81,7 +59,7 @@ def eval(dataset_path, name, model_path, gpu=0):
     loss_list = np.zeros(data_loader.dataset.__len__())
     time_list = np.zeros(data_loader.dataset.__len__())
 
-    for i, (input, target) in enumerate(data_loader):
+    for i, (input, target, scale_factor) in enumerate(data_loader):
         with torch.no_grad():
[…]

### 2022-05-23 workspace/nnnx/utils.py

@@ -1,211 +1,0 @@
-import os, sys
-from os.path import dirname
-
-sys.path.append(dirname(__file__))
-
-import json
-import glob
-import numpy as np
-import shutil
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-from torch.utils.data import DataLoader, Dataset
-from torch.optim import SGD, Adam, lr_scheduler
-
-import config
-from help_funs import file_io, mu
-from workspace.nnnx import network, candidate_normals
-
-
-class L2Loss(nn.Module):
-    def __init__(self):
-        super().__init__()
-
-    def forward(self, outputs, target, *args):
-        return F.mse_loss(outputs, target)
-
-
-class NeuralNetworkModel():
-    def __init__(self, args, start_epoch=0):
-        self.args = args
-        self.start_epoch = start_epoch
-        self.device = torch.device("cpu" if self.args.cpu else f"cuda:{self.args.gpu}")
-        self.exp_dir = config.ws_path / self.args.exp
-        self.train_loader, self.val_loader = create_dataloader(self.args, eval_mode=False)
-        self.model = network.CNN().to(self.device)
-        self.parameters = filter(lambda p: p.requires_grad, self.model.parameters())
-        self.optimizer = self.init_optimizer()
-        self.loss = self.init_loss()
-        self.losses = []
-        self.criterion = nn.CrossEntropyLoss()
-        self.init_lr_decayer()
-        self.print_info(args)
-
-    def init_loss(self):
-        self.loss = L2Loss()
-        self.loss.to(self.device)
-        return self.loss
-
-    def init_lr_decayer(self):
-        milestones = [int(x) for x in self.args.lr_scheduler.split(",")]
-        self.lr_decayer = lr_scheduler.MultiStepLR(self.optimizer, milestones=milestones,
-                                                   gamma=self.args.lr_decay_factor)
-
-    def init_optimizer(self):
-        if self.args.optimizer.lower() == 'sgd':
-            optimizer = SGD(self.parameters,
-                            lr=self.args.lr,
-                            momentum=self.args.momentum,
-                            weight_decay=self.args.weight_decay)
-        elif self.args.optimizer.lower() == 'adam':
-            optimizer = Adam(self.parameters,
-                             lr=self.args.lr,
-                             weight_decay=self.args.weight_decay,
-                             amsgrad=True)
[…]

### 2022-05-23 workspace/pncnn/network.py

@@ -1,55 +1,0 @@
-########################################
-__author__ = "Abdelrahman Eldesokey"
-__license__ = "GNU GPLv3"
-__version__ = "0.1"
-__maintainer__ = "Abdelrahman Eldesokey"
-__email__ = "abdo.eldesokey@gmail.com"
-
-########################################
-import sys
-from os.path import dirname
-
-import cv2
-
-sys.path.append(dirname(__file__))
-
-import torch
-import torch.nn as nn
-
-from pncnn.common.unet import UNetSP
-from pncnn.common.nconv import NConvUNet
-from help_funs import mu
-
-
-class CNN(nn.Module):
-    def __init__(self):
-        super().__init__()
-        self.__name__ = 'pncnn'
-
-        # input confidence estimation network
-        # self.conf_estimator = UNetSP(1, 1)
-        self.nconv = NConvUNet(3, 3)
-        self.var_estimator = UNetSP(3, 3)
-        # self.var_estimator = UNetSP(3, 3)
-
-    def forward(self, x0, cpu=False):
-        # x0: vertex array
-        # c0: confidence of each element in x0
-
-        # c0 = self.conf_estimator(x0) #  estimate the input confidence
-        c0 = mu.binary(x0)
-        xout, cout = self.nconv(x0, c0, cpu)  # estimated value of depth
-
-        # conv layer with kernal 1
-        cout = self.var_estimator(cout)  #
-        out = torch.cat((xout, cout, c0), 1)
-
-        x0_normalized_8bit = mu.normalize2_8bit(mu.tenor2numpy(x0))
-        mu.addText(x0_normalized_8bit, "Input")
-        c0_normalized_8bit = mu.normalize2_8bit(mu.tenor2numpy(c0))
-        mu.addText(c0_normalized_8bit, "Input Confidence")
-        _, normal_knn_8bit = mu.vertex2normal(mu.tenor2numpy(x0), k_idx=5)
-        mu.addText(normal_knn_8bit, "normal = knn(Input)")
-        output_img = cv2.hconcat([x0_normalized_8bit, c0_normalized_8bit, normal_knn_8bit])
-
-        return out, output_img

### 2022-05-23 workspace/train.py

@@ -75,6 +75,37 @@ class AngleLoss(nn.Module):
         return loss  # +  F.mse_loss(outputs, target)  # + angle_loss.mul(args.angle_loss_weight)
 
 
+class AngleDetailLoss(nn.Module):
+    def __init__(self):
+        super().__init__()
+
+    def forward(self, outputs, target, args):
+        # add penalty to the extreme values, i.e. out of range [-1,1]
+        mask_too_high = torch.gt(outputs, 1).bool().detach()
+        mask_too_low = torch.lt(outputs, -1).bool().detach()
+        outputs[mask_too_high] = outputs[mask_too_high] * args.penalty
+        outputs[mask_too_low] = outputs[mask_too_low] * args.penalty
+
+        # mask of normals
+        mask = torch.sum(torch.abs(target[:, :3, :, :]), dim=1) > 0
+        mask = mask.unsqueeze(1).repeat(1, 3, 1, 1)
+        outputs_smooth = outputs[:, :3, :, :]
+        outputs_sharp = outputs[:, 3:6, :, :]
+        mask_sharp = outputs[:, 6:, :, :].bool()
+        mask_smooth = (~mask_sharp) * mask
+
+        axis = args.epoch % 3
+        outputs_smooth[mask_sharp] = 0
+        outputs_sharp[mask_smooth] = 0
+
+        outputs_merged = outputs_sharp + outputs_smooth
+        # smooth loss and sharp loss
+        axis_diff = (outputs_merged - target)[:, axis, :, :][mask[:, 0, :, :]]
+        loss = torch.sum(axis_diff ** 2) / (axis_diff.size(0))
+
+        return loss
+
+
 class L1Loss(nn.Module):
     def __init__(self):
         super().__init__()
@@ -111,7 +142,8 @@ loss_dict = {
     'masked_l1': MaskedL1Loss(),
     'masked_l2': MaskedL2Loss(),
     'weighted_l2': WeightedL2Loss(),
-    'angle': AngleLoss()
+    'angle': AngleLoss(),
+    'angle_detail': AngleDetailLoss(),
 }
 
 
@@ -119,10 +151,10 @@ loss_dict = {
 class SyntheticDepthDataset(Dataset):
 
     def __init__(self, data_path, k, output_type, setname='train'):
-        if setname in ['train']:
+        if setname in ['train', 'test']:
             self.training_case = np.array(
                 sorted(
[…]

### 2022-05-23 eval_visual.py
update degares model

@@ -30,27 +30,29 @@ def preprocessing():
         path = config.synthetic_data_noise / "test"
     elif args.data == "real":
         path = config.real_data  # key tests 103, 166, 189,9
+    elif args.data == "paper":
+        path = config.paper_pic
     else:
         raise ValueError
     # test dataset indices
     all_names = [os.path.basename(path) for path in sorted(glob.glob(str(path / f"*.image?.png"), recursive=True))]
     all_names = np.array(all_names)
-    eval_indices = [int(name.split(".")[0]) for name in all_names]
-    eval_indices = eval_indices[:5]
+    # eval_indices = [int(name.split(".")[0]) for name in all_names]
+    eval_indices = [49]
 
     # load test model names
     models = {
         # "SVD": None,
         # "Neigh_9999": config.ws_path / "nnn24" / "trained_model" / "full_normal_2999" / "checkpoint-9999.pth.tar",
-        "NNNN": config.ws_path / "nnnn" / "trained_model" / "checkpoint.pth.tar",
-        "NG": config.ws_path / "ng" / "trained_model" / "checkpoint.pth.tar",
+        # "NNNN": config.ws_path / "nnnn" / "trained_model" / "checkpoint.pth.tar",
+        # "NG": config.ws_path / "ng" / "trained_model" / "checkpoint.pth.tar",
         "NG+": config.ws_path / "resng" / "trained_model" / "checkpoint.pth.tar",
     }
     eval_res = np.zeros((len(models), len(eval_indices)))
 
     eval_time = datetime.datetime.now().strftime("%H_%M_%S")
     eval_date = datetime.datetime.today().date()
-    folder_path = config.ws_path / "eval_output" / f"{eval_date}_{eval_time}"
+    folder_path = config.paper_pic / f"{eval_date}_{eval_time}"
     if not os.path.exists(str(folder_path)):
         os.mkdir(str(folder_path))
 
@@ -155,8 +157,8 @@ def main():
 
     for i, data_idx in enumerate(eval_idx):
         # read data
-        test_0 = torch.load(test_0_data[i])
-        test_1 = torch.load(test_1_data[i])
+        test_0 = torch.load(test_0_data[data_idx])
+        test_1 = torch.load(test_1_data[data_idx])
 
         test_0_tensor = test_0['input_tensor'].unsqueeze(0)
         test_1_tensor = test_1['input_tensor'].unsqueeze(0)
[…]

### 2022-05-23 workspace/train.py

@@ -457,12 +457,10 @@ def draw_output(x0, xout, cout, target, exp_path, loss, epoch, i, output_type, p
 
     # gt normal
     target = target.numpy()
-    if output_type == 'normal' or output_type == 'normal_noise':
-        target = mu.normal2RGB(target)
+    target_img = mu.normal2RGB(target)
     mask = target.sum(axis=2) == 0
-    target_ranges = mu.addHist(target)
-    target = cv.normalize(target, None, 0, 255, cv.NORM_MINMAX, dtype=cv.CV_8U)
-    normal_gt_8bit = target
+    target_ranges = mu.addHist(target_img)
+    normal_gt_8bit = cv.normalize(target_img, None, 0, 255, cv.NORM_MINMAX, dtype=cv.CV_8U)
     mu.addText(normal_gt_8bit, "gt")
     mu.addText(normal_gt_8bit, str(target_ranges), pos="upper_right", font_size=0.5)
     output_list.append(normal_gt_8bit)

### 2022-05-30 create_dataset.py
add albedo gated model

@@ -1,4 +1,6 @@
 import argparse
+import os
+import shutil
 
 import config
 from help_funs.data_preprocess import noisy_a_folder, convert2training_tensor
@@ -12,8 +14,11 @@ parser.add_argument('--data', type=str, default="synthetic", choices=['synthetic
                     help="choose dataset")
 parser.add_argument('--max_k', type=str, default="0,1",
                     help="loading dataset from local or dfki machine")
+parser.add_argument('--clear', type=str, default="false",
+                    help="flag that is used to clear old dataset")
 
 args = parser.parse_args()
+
 if args.data == "synthetic":
     for folder in ["train", "test"]:
         original_folder = config.synthetic_data / folder
@@ -24,13 +29,16 @@ if args.data == "synthetic":
         else:
             raise ValueError
         noisy_a_folder(original_folder, dataset_folder)
+        if args.clear == "true":
+            shutil.rmtree(str(dataset_folder / "tensor"))
         for k in args.max_k.split(','):
-            print(f"K = {k}, {folder}")
+            print(f"K = {k}, {dataset_folder}")
             convert2training_tensor(dataset_folder, k=int(k), output_type="normal_noise")
+
 elif args.data == "real":
-    original_folder = config.real_data
+    dataset_folder = config.real_data
     for k in args.max_k.split(','):
-        print(f"K = {k}, {original_folder}")
-        convert2training_tensor(original_folder, k=int(k), output_type="normal_noise")
+        print(f"K = {k}, {dataset_folder}")
+        convert2training_tensor(dataset_folder, k=int(k), output_type="normal_noise")
 else:
     raise ValueError

### 2022-05-30 help_funs/chart.py

@@ -134,7 +134,7 @@ def draw_output(x0, xout, cout, c0, target, exp_path, loss, epoch, i, prefix):
     # xout = out[:, :3, :, :]
     # cout = out[:, 3:6, :, :]
 
-    x0_normalized_8bit = mu.normalize2_8bit(mu.tenor2numpy(x0[:1, :, :, :]))
+    x0_normalized_8bit = mu.normalize2_32bit(mu.tenor2numpy(x0[:1, :, :, :]))
     mu.addText(x0_normalized_8bit, "Input(Vertex)")
 
     normal_gt_8bit = mu.normal2RGB(mu.tenor2numpy(target[:1, :, :, :]))

### 2022-05-30 main.py

@@ -10,6 +10,7 @@ import workspace.ng.network as ng
 import workspace.resng.network as resng
 import workspace.nconv.network as nconv
 import workspace.degares.network as degares
+import workspace.ag.network as ag
 
 
 def main():
@@ -17,6 +18,7 @@ def main():
 
     # config experiments
     exp_path = config.ws_path / args.exp
+
     if args.exp == "nnn":
         model = nnn.CNN()
     elif args.exp == "nnn24":
@@ -31,6 +33,8 @@ def main():
         model = nconv.CNN()
     elif args.exp == "degares":
         model = degares.CNN()
+    elif args.exp == "ag":
+        model = ag.CNN()
     else:
         raise ValueError("Unknown exp path")
 

### 2022-05-30 workspace/train.py

@@ -76,6 +76,41 @@ class AngleLoss(nn.Module):
         return loss  # +  F.mse_loss(outputs, target)  # + angle_loss.mul(args.angle_loss_weight)
 
 
+class AngleAlbedoLoss(nn.Module):
+    def __init__(self):
+        super().__init__()
+
+    def forward(self, outputs, target, args):
+        normal_out = outputs[:, :3, :, :]
+        albedo_out = outputs[:, 3:4, :, :]
+        img_out = outputs[:, 4, :, :]
+
+        normals_target = target[:, :3, :, :]
+        img = target[:, 3, :, :]
+        mask_too_high = torch.gt(normal_out, 1).bool().detach()
+        mask_too_low = torch.lt(normal_out, -1).bool().detach()
+        normal_out[mask_too_high] = normal_out[mask_too_high] * args.penalty
+        normal_out[mask_too_low] = normal_out[mask_too_low] * args.penalty
+
+        # val_pixels = (~torch.prod(target == 0, 1).bool()).unsqueeze(1)
+        # angle_loss = mu.angle_between_2d_tensor(outputs, target, mask=val_pixels).sum() / val_pixels.sum()
+        # mask of non-zero positions
+        mask = torch.sum(torch.abs(normals_target[:, :3, :, :]), dim=1) > 0
+        # mask = mask.unsqueeze(1).repeat(1, 3, 1, 1).float()
+
+        axis = args.epoch % 3
+        axis_diff = (normal_out - normals_target)[:, axis, :, :][mask]
+        loss = torch.sum(axis_diff ** 2) / (axis_diff.size(0))
+
+        img_diff = (img - img_out)[mask]
+        img_diff[torch.isnan(img_diff)] = 0
+
+        albedo_loss = torch.sum(img_diff ** 2 / img_diff.size(0))
+        # print(f"\t axis: {axis}\t axis_loss: {loss:.5f}")
+
+        return albedo_loss + loss  # +  F.mse_loss(outputs, target)  # + angle_loss.mul(args.angle_loss_weight)
+
+
 class AngleDetailLoss(nn.Module):
     def __init__(self):
         super().__init__()
@@ -149,6 +184,7 @@ loss_dict = {
     'weighted_l2': WeightedL2Loss(),
     'angle': AngleLoss(),
     'angle_detail': AngleDetailLoss(),
+    'angleAlbedo': AngleAlbedoLoss(),
 }
 
 
[…]

### 2022-06-03 paper/introduction.tex
convert ag model backward

@@
+%% intro
+Surface normal inference from a single view deals with the task of object surface orientation estimation. It has many practical applications, such as augmented reality and robotics.
+
 %%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%
@@
 Standard methods compute normals from point cloud using neighboring information in image space or use Shape from Shading.
-However, the point clouds captured by sensors like Kinect or similar RGB-D, LiDAR sensors are only semi-dense.
-As shown in Figure \ref{fig:standard_normal_inference}.
-If map these normals to mesh, that is not good at all.
-Standard methods dependents on chosen neighbor size, if too small, it has larger noise sensitive, if too large, the output will too smooth and not crispy.
-Errors may occur in regions with inter-reflections, where we have errors in the 3D measurement.
+However, the point clouds data provided by Kinect or similar RGB-D, LiDAR sensors are only semi-dense.
+As shown in Figure \ref{fig:depth_map_with_noise}.
+If map these normals to polygon mesh, that is not good at all.
 
@@
 	\begin{tikzpicture}
+		\node[inner sep=0pt] (depthmap) at (0,0)
+		{\includegraphics[width=.5\textwidth]{./pic/00028.depth0.png}};
+	\end{tikzpicture}
+	\caption{A depth map captured via infrared sensors. The missing pixels distributed almost all of the image.}
+	\label{fig:depth_map_with_noise}
+\end{figure}
 
-		\node[inner sep=0pt] (depthmap) at (0,0)
-		{\includegraphics[width=.3\textwidth]{./pic/00028.depth0.png}};
+Standard methods derives normal from each point and its neighborhoods' positions.
+It dependents on chosen neighbor size.
+There are two main drawbacks.
+First, if neighbor size is too small, it has larger noise sensitive, if it is too large, the output will too smooth and not crispy.
+Second, it is not robust with noise.
+Errors may occur in regions with inter-reflections, where we have errors in the 3D measurement.
+On the other side, it is also weak with missing pixel handling, which is a common issue in depth maps.
 
-		\path [line] (3,0) -- node [text width=1.5cm,midway,above ] {SVD/PCA} (5,0);
-
+%% add noise image
+\begin{figure}[!h]
+	\centering
+	\begin{tikzpicture}	
 		\node[inner sep=0pt] (normal) at (8,0)
-		{\includegraphics[width=.3\textwidth]{./pic/00028.normal0.png}};
+		{\includegraphics[width=.5\textwidth]{./pic/00028.normal0.png}};
 	\end{tikzpicture}
-\caption{Left: Depth Map, Right: Semi-dense Normal Map}
+	\caption{Semi-dense Normal Map calculated from depth map using standard method}
 	\label{fig:standard_normal_inference}
@@
 Although the depth image is incomplete, the depth sensor usually able to capture grayscale texture image, which are typically fully dense due to their passive nature.
-Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, etc.
+Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, and grayscale image .
 Thus the normal can be inferenced better using the given image information and depth map.
@@
 Based grayscale image and corresponding semi-dense depth map, a CNN model can be designed to inference the normal map, which gives more density and robust comparing to standard algorithm.
-However, the missing pixels in depth map can be distributed around the whole image, some of the region leaves complete empty pixels.
+However, the missing pixels in depth map can be distributed around the whole image, some of the image regions leave complete empty holes.
 This situation imposes further processing for the missing regions and some other challenges on the machine learning methods.
@@
 
-However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted.
+However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted, like image segmentation\cite{unet}.
 In this case, the traditional network architecture is not suitable anymore.
@@
 \end{figure}
+
+In this thesis, we proposed a novel deep learning architecture for surface normal inference.
+
+By applying our approach to the task of normal inference, a custom dataset is created from Unity using 3D models.
+The trained Normal models achieve a remarkably better prediction accuracy at a low computational cost comparing to the standard approaches for semi-dense point clouds.

### 2022-06-05 paper/introduction.tex
update paper (introduction)

@@
-%% intro
-Surface normal inference from a single view deals with the task of object surface orientation estimation. It has many practical applications, such as augmented reality and robotics.
+%%%%%%%%%%%%%%%%%%%% intro %%%%%%%%%%%%%%%%%%%%
+
+%% What is surface normal
+\section{Introduction}
+
+Normal indicates the direction of a plane.
+In 3D coordinate systems, a normal is a vector, which perpendicular to the corresponding plane.
+Since only the direction property of a normal is demanded, the length is meaningless, thus the normal can be represented as an unit vector.
+In this case, each axis in range $ [-1,1] $.
+Therefore, for a polygon, the direction of each plane can be represented by its normal.
+
+%% why surface normal is important
+
+Surface normal has many practical applications, such as augmented reality and robotics.
+In these applications, normal is an important basic property of object surface.
+Some rendering tasks such as surface reconstruction, image registration, shading, etc, they all required surface normal as one of the inputs.
+
+%% Surface normal from point cloud
+Objects are usually captured by cameras, which provided as a single view scene with RGB colors.
+Some camera can also record the depth map at the same time.
+The depth can be converted to 3D vertices from image space.
+Therefore, the object in 3D space is usually represented as a point cloud.
+In this case, normals can not be calculated precisely since the planes of each point is unknown.
 

### 2022-06-05 paper/related_work.tex
update paper (introduction)

@@
+From considering neighborhoods in the same plane then using PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last 30 years.
+
 \section{Sparse Input processing}
@@
 
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{./ref/u-net-illustration-correct-scale2}
-	\caption{U-net architecture (example for 32x32 pixels in the lowest resolution).
+%%\begin{figure}[!h]
+%%	\centering
+%%	\includegraphics[width=\textwidth]{./ref/u-net-illustration-correct-scale2}
+%%	\caption{U-net architecture (example for 32x32 pixels in the lowest resolution).
 Each blue box corresponds to a multi-channel feature map.
@@
 The arrows denote the different operations.
-	}
-	\label{fig:u-net}
-\end{figure}
+%%	}
+%%	\label{fig:u-net}
+%% \end{figure}
 

### 2022-06-07 paper/introduction.tex
update ag model and its loss

--- 2022-06-03 paper/introduction.tex
@@
-%% intro
-Surface normal inference from a single view deals with the task of object surface orientation estimation. It has many practical applications, such as augmented reality and robotics.
-
-%%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%
-
-%% standard method for normal inference is insufficient, input is sparse, not robust enough
-Standard methods compute normals from point cloud using neighboring information in image space or use Shape from Shading.
-However, the point clouds data provided by Kinect or similar RGB-D, LiDAR sensors are only semi-dense.
-As shown in Figure \ref{fig:depth_map_with_noise}.
-If map these normals to polygon mesh, that is not good at all.
-
 %% add noise image
@@
 		\node[inner sep=0pt] (depthmap) at (0,0)
-		{\includegraphics[width=.5\textwidth]{./pic/00028.depth0.png}};
+		{\includegraphics[width=.6\textwidth]{./pic/00028.depth0.png}};
 	\end{tikzpicture}
-	\caption{A depth map captured via infrared sensors. The missing pixels distributed almost all of the image.}
+	\caption{A depth map captured via infrared sensors. The dark pixels close to the camera, the light pixels away to the camera. The missing pixels distributed all of the image.}
 	\label{fig:depth_map_with_noise}
 \end{figure}
-
-Standard methods derives normal from each point and its neighborhoods' positions.
-It dependents on chosen neighbor size.
-There are two main drawbacks.
-First, if neighbor size is too small, it has larger noise sensitive, if it is too large, the output will too smooth and not crispy.
-Second, it is not robust with noise.
-Errors may occur in regions with inter-reflections, where we have errors in the 3D measurement.
-On the other side, it is also weak with missing pixel handling, which is a common issue in depth maps.
 
@@
 		\node[inner sep=0pt] (normal) at (8,0)
-		{\includegraphics[width=.5\textwidth]{./pic/00028.normal0.png}};
+		{\includegraphics[width=.6\textwidth]{./pic/00028.normal0.png}};
 	\end{tikzpicture}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% intro %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% What is surface normal
+\section{Introduction}
+In three dimension geometry, a surface normal at the point $ P $ is a vector $ n $ perpendicular to the tangent plane of the surface at point $ P $.
+The length of a normal is usually one, with a sign to represent the sides (interior or exterior).
+
+%% why surface normal is important
+Surface normal has many practical applications, such as augmented reality and robotics.
+In these applications, normal impacts on the way that objects are represented.
+Some tasks such as surface reconstruction, image registration, shading, etc, they all required surface normal as one of the inputs.
+
+%%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%
+
+%% standard method for normal inference is insufficient, input is sparse, not robust enough
+Standard methods compute normals from point cloud using neighboring information in image space or from a single grayscale image using use Shape from Shading \cite{SFS}.
+The first method bases on the assumption that the neighbors of the points are located on the same plane.
+It performs well with a well-chosen window size.
+The drawbacks are, the algorithm is highly noise sensitive.
+It is weak with handling missing pixels, which is a common issue in the input data.
+The second method depends on the correct information about light source.
+Errors may occur in regions with inter-reflections in the 3D measurement.
+
+%% CNN based methods
+Recently, deep learning based method \cite{yolov3}, \cite{efficientDet} achieved a great succeed for image processing. 
+These kinds of network architecture takes a batch of RGB/Grayscale images as input which usually employed for classification problems.
+The image is usually convoluted with convolutional layer and downsampling with pooling layers.
+The outputs of the network consists of a single value to represent the index of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.
+
+%%%%%%%%%%%%%%%%%%% talk about the chanllege of this task %%%%%%%%%%%%%%%%%%
+%% talk about the reason we need new type of network architecture
+However, in many other vision tasks, like normal map inference, the output is demanded that it has the same shape as the input.
+Instead of predicting one or several classes for the whole input matrix, the classes for each pixels are required for prediction.
+In this case, the traditional network architecture is not suitable anymore.
+
+%% talk about upsampling 
+Recently, deep learning based methods are also applied on some computer vision tasks such as image segmentation, image inpainting and depth density enhancement.
+In these methods, multiple architectures have been proposed with an upsampling section.
+In this case, the output can be designed has the same shape as input or slightly smaller.
+Nevertheless, the resolution is similar to the input image.
+Normal Inference task has similar pipeline comparing to these tasks.
+
 %% there exists space for improvment 
-Although the depth image is incomplete, the depth sensor usually able to capture grayscale texture image, which are typically fully dense due to their passive nature.
+On the other hand, the point clouds data provided by Kinect or similar RGB-D, LiDAR sensors are only semi-dense.
+A huge mount of missing pixels distribute all over the images, some of the regions leave complete empty holes.
+This situation imposes another challenge on the normal inference.
+
+The depth image is incomplete, however, the depth sensor usually able to capture grayscale texture image, which are typically fully dense due to their passive nature.
 Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, and grayscale image .
 Thus the normal can be inferenced better using the given image information and depth map.
+Based grayscale image and corresponding semi-dense depth map, a CNN model can be designed to inference the normal map, which is able to give more density and robust result comparing to standard algorithm.
 
-%%%%%%%%%%%%%%%%%%% talk about the chanllege of this task %%%%%%%%%%%%%%%%%%
-Both depth and grayscale image are initially relevant to the machine learning algorithms.
-Based grayscale image and corresponding semi-dense depth map, a CNN model can be designed to inference the normal map, which gives more density and robust comparing to standard algorithm.
-However, the missing pixels in depth map can be distributed around the whole image, some of the image regions leave complete empty holes.
-This situation imposes further processing for the missing regions and some other challenges on the machine learning methods.
-In this thesis, we found a solution for the problems mentioned above.
+%%%%%%%%%%%%%%%%%% talk about the main work in this thesis  %%%%%%%%%%%%%%%%%%
+In this thesis, we found a solution for the problems mentioned above and proposed a noval deep learning architecture for surface normal inference.A network named Albedo Gated Normal Inference Network(AlGaN) is proposed to infer normal given the corresponding depth map.
+The architecture of AlGaN involves a two-stage CNN.
+The first stage infers the normal map using point cloud as input.
+If the light source position and grayscale image can be provided further, the second stage infers the albedo altogether with the normals from first stage.
+In addition, the loss function is based on least-square-error and Lambertian reflection.
 
-%% CNN based methods
-The deep convolutional neural network is typically used for image classification, which achieved great success in last several years. \cite{yolov3}, \cite{efficientDet}. 
-%% talk about the reason we need new type of network architecture
-These kinds of network architecture takes a single image as input which usually employed for classification problems.
-The image is usually convoluted with convolutional layer and downsampling with pooling layers.
-The outputs of the network consists of a single value to represent the ID of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.
-
-However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted, like image segmentation\cite{unet}.
-In this case, the traditional network architecture is not suitable anymore.
-
-%% improved normal inference figure
-\begin{figure}[!h]
-	\centering
-	\begin{tikzpicture}
-
-		\node[inner sep=0pt] (image) at (0,0)
-		{\includegraphics[width=.2\textwidth]{./pic/00028.image0.png}};
-
-		\node[text width=1cm] at (2,0) {$ + $};
-
-		\node[inner sep=0pt] (depthmap) at (3.3,0)
-		{\includegraphics[width=.2\textwidth]{./pic/00028.depth0.png}};
-		\node[text width=1cm] at (8,0) {$ ? $};
-
-		\path [line] (5,0) -- node [text width=1cm,midway,above ] {CNN} (6,0);
-
-	\end{tikzpicture}
-	\caption{Left: Grayscale Image, Middle: Depth Map}
-	\label{fig:improved_normal_inference}
-\end{figure}
-
-In this thesis, we proposed a novel deep learning architecture for surface normal inference.
-
-By applying our approach to the task of normal inference, a custom dataset is created from Unity using 3D models.
+With the help of synthetic data in Unity, a dataset is created for CNN model training.
+It can provide accurate ground-truth for training work, which real data usually not provided.
+The results on this dataset shows that our AlGaN model performs also well on real data captured by Infrared cameras.
 The trained Normal models achieve a remarkably better prediction accuracy at a low computational cost comparing to the standard approaches for semi-dense point clouds.

### 2022-06-07 workspace/train.py

@@ -94,14 +94,14 @@ class AngleAlbedoLoss(nn.Module):
         loss = torch.sum(axis_diff ** 2) / (axis_diff.size(0))
 
         # light loss
-        light_target = target[:, 5:8, :, :]
-        light_output = outputs[:, 3:6, :, :]
-        l_diff = (light_output - light_target).permute(0, 2, 3, 1)[mask]
-        loss += torch.sum(l_diff ** 2) / (l_diff.size(0))
+        # light_target = target[:, 5:8, :, :]
+        # light_output = outputs[:, 3:6, :, :]
+        # l_diff = (light_output - light_target).permute(0, 2, 3, 1)[mask]
+        # loss += torch.sum(l_diff ** 2) / (l_diff.size(0))
 
         # N*L loss
         G_target = target[:, 3, :, :]
-        G_output = torch.sum(normal_out * light_target, dim=1)
+        G_output = outputs[:, 3, :, :]
         G_diff = (G_output - G_target)[mask]
         loss += torch.sum(G_diff ** 2) / (G_diff.size(0))
 
@@ -267,6 +267,7 @@ class TrainingModel():
         self.print_info(args)
         self.save_model()
         self.pretrained_weight = None
+        self.best_loss = 1e+20
 
     def create_dataloader(self, dataset_path):
         train_on = self.args.train_on
@@ -437,6 +438,7 @@ def train_epoch(nn_model, epoch):
                             prefix="train")
             print(f"\t loss: {loss_0th:.2e}\t axis: {epoch % 3}")
 
+    # save loss
     loss_avg = loss_total / len(nn_model.train_loader.dataset)
     nn_model.losses[epoch % 3, epoch] = loss_avg
     if nn_model.args.angle_loss:
@@ -447,6 +449,15 @@ def train_epoch(nn_model, epoch):
             angle_loss_sharp_avg = angle_loss_sharp_total / len(nn_model.train_loader.dataset)
             nn_model.angle_sharp_losses[0, epoch] = angle_loss_sharp_avg
 
+    # indicate for best model saving
+    if nn_model.best_loss > loss_avg:
+        nn_model.best_loss = loss_avg
+        print(f'best loss updated to {loss_avg}.')
+        is_best = True
+    else:
+        is_best = False
+
+    # draw line chart
     if epoch % 10 == 9:
         draw_line_chart(np.array([nn_model.losses[0]]), nn_model.output_folder,
                         log_y=True, label=0, epoch=epoch, start_epoch=nn_model.start_epoch)
[…]

### 2022-06-07 paper/introduction.tex
change loss

@@
 	\end{tikzpicture}
-	\caption{A depth map captured via infrared sensors. The dark pixels close to the camera, the light pixels away to the camera. The missing pixels distributed all of the image.}
+	\caption{A captured depth map via infrared sensors.
+Pixels that far away represent by light colors, otherwise by dark colors.
+The black dots are the depths that failed to be detected.
+The black dots distribute in all of the images.}
 	\label{fig:depth_map_with_noise}
@@
 	\end{tikzpicture}
-	\caption{Semi-dense Normal Map calculated from depth map using standard method}
+	\caption{Semi-dense Normal Map calculated from depth map using a standard method}
 	\label{fig:standard_normal_inference}
@@
 
-%% What is surface normal
 \section{Introduction}
-In three dimension geometry, a surface normal at the point $ P $ is a vector $ n $ perpendicular to the tangent plane of the surface at point $ P $.
-The length of a normal is usually one, with a sign to represent the sides (interior or exterior).
+As a popular and affordable new type of depth sensor, Kinect, had attracted a great focus to computer vision research in the last decades.
+It simultaneously captured the grayscale or RGB image and depth map with a high resolution.
+The depth map can further convert to structured point clouds with known intrinsic calibration parameters, which can use in many applications.
 
 %% why surface normal is important
-Surface normal has many practical applications, such as augmented reality and robotics.
-In these applications, normal impacts on the way that objects are represented.
-Some tasks such as surface reconstruction, image registration, shading, etc, they all required surface normal as one of the inputs.
+Surface Normal is one of the most worthy pieces of information that can inferr from point clouds, which applies in many practical applications, such as augmented reality and robotics.
+Some tasks like shading and surface reconstruction require normal as one of the inputs.
+However, due to the lack of accuracy of the sensors, the  surface normal inference from depth maps/point clouds has many challenges.
 
@@
 %% standard method for normal inference is insufficient, input is sparse, not robust enough
-Standard methods compute normals from point cloud using neighboring information in image space or from a single grayscale image using use Shape from Shading \cite{SFS}.
-The first method bases on the assumption that the neighbors of the points are located on the same plane.
-It performs well with a well-chosen window size.
-The drawbacks are, the algorithm is highly noise sensitive.
-It is weak with handling missing pixels, which is a common issue in the input data.
-The second method depends on the correct information about light source.
+Standard methods compute normals from the point cloud using neighboring information in image space or from a single grayscale image using use Shape from Shading \cite{SFS}.
+The first method assumes that the neighbors of the points locate on the same plane.
+This method performs well with a well-chosen window size.
+However, the drawbacks are that the algorithm is highly noise sensitive.
+It is weak in handling missing pixels, which is a common issue in the input data.
+The second method depends on the correct information about the light source.
 Errors may occur in regions with inter-reflections in the 3D measurement.
@@
 Recently, deep learning based method \cite{yolov3}, \cite{efficientDet} achieved a great succeed for image processing. 
-These kinds of network architecture takes a batch of RGB/Grayscale images as input which usually employed for classification problems.
-The image is usually convoluted with convolutional layer and downsampling with pooling layers.
-The outputs of the network consists of a single value to represent the index of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.
+These network architectures use a batch of RGB/Grayscale images as input and usually employ for classification problems.
+Usually, the images are convoluted with a convolutional layer and downsampling with pooling layers.
+The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.
 
 %%%%%%%%%%%%%%%%%%% talk about the chanllege of this task %%%%%%%%%%%%%%%%%%
-%% talk about the reason we need new type of network architecture
-However, in many other vision tasks, like normal map inference, the output is demanded that it has the same shape as the input.
-Instead of predicting one or several classes for the whole input matrix, the classes for each pixels are required for prediction.
+%% talk about the reason we need a new type of network architecture
+However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
+Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
 In this case, the traditional network architecture is not suitable anymore.
@@
 %% talk about upsampling 
-Recently, deep learning based methods are also applied on some computer vision tasks such as image segmentation, image inpainting and depth density enhancement.
-In these methods, multiple architectures have been proposed with an upsampling section.
-In this case, the output can be designed has the same shape as input or slightly smaller.
+Recently, deep learning-based methods are used in computer vision tasks such as image segmentation, image inpainting, and depth density enhancement.
+In these methods, multiple architectures have proposed with an upsampling section.
+In this case, the output can be designed to have the same shape as the input or slightly smaller.
 Nevertheless, the resolution is similar to the input image.
-Normal Inference task has similar pipeline comparing to these tasks.
+The normal Inference task has a similar pipeline compared to these tasks.
 
-%% there exists space for improvment 
-On the other hand, the point clouds data provided by Kinect or similar RGB-D, LiDAR sensors are only semi-dense.
-A huge mount of missing pixels distribute all over the images, some of the regions leave complete empty holes.
-This situation imposes another challenge on the normal inference.
+%% there exists space for improvement 
+On the other hand, the point cloud data provided by Kinect or similar RGB-D, and LiDAR sensors are only semi-dense.
+A huge amount of missing pixels distribute all over the images, and some of the regions leave complete empty holes.
+This situation imposes another challenge on normal inference.
 
-The depth image is incomplete, however, the depth sensor usually able to capture grayscale texture image, which are typically fully dense due to their passive nature.
-Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, and grayscale image .
-Thus the normal can be inferenced better using the given image information and depth map.
-Based grayscale image and corresponding semi-dense depth map, a CNN model can be designed to inference the normal map, which is able to give more density and robust result comparing to standard algorithm.
+The depth image is incomplete, however, the depth sensor is able to capture grayscale texture images, which are typically fully dense due to their passive nature.
+Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, and grayscale image.
+Then the normal can be inferred better using the given image information and depth map.
+Based on the grayscale image and corresponding semi-dense depth maps, a CNN model can be designed to infer the normal map, which can give more density and robust results comparing to the standard algorithm.
 
 %%%%%%%%%%%%%%%%%% talk about the main work in this thesis  %%%%%%%%%%%%%%%%%%
-In this thesis, we found a solution for the problems mentioned above and proposed a noval deep learning architecture for surface normal inference.A network named Albedo Gated Normal Inference Network(AlGaN) is proposed to infer normal given the corresponding depth map.
+In this thesis, we found a solution for the problems mentioned above and proposed a novel deep learning architecture for surface normal inference.
+A network named Albedo Gated Normal Inference Network(AlGaN) is proposed to infer normal given the corresponding depth map.
 The architecture of AlGaN involves a two-stage CNN.
 The first stage infers the normal map using point cloud as input.
-If the light source position and grayscale image can be provided further, the second stage infers the albedo altogether with the normals from first stage.
-In addition, the loss function is based on least-square-error and Lambertian reflection.
+If the light source position and grayscale image can be provided further, the second stage infers the albedo altogether with the normals from the first stage.
+In addition, the loss function is based on least-square error and Lambertian reflection.
 
 With the help of synthetic data in Unity, a dataset is created for CNN model training.
-It can provide accurate ground-truth for training work, which real data usually not provided.
-The results on this dataset shows that our AlGaN model performs also well on real data captured by Infrared cameras.
-The trained Normal models achieve a remarkably better prediction accuracy at a low computational cost comparing to the standard approaches for semi-dense point clouds.
+It can provide accurate ground truth for training work, which real data is usually not provided.
+The results of this dataset show that our AlGaN model performs also well on real data captured by Infrared cameras.
+The trained Normal models achieve a remarkably better prediction accuracy at a low computational cost compared to the standard approaches for semi-dense point clouds.

### 2022-06-19 paper/Appendices/AppendixA.tex
update paper

% Appendix A

\chapter{Dataset} % Main appendix title

\label{AppendixA} % For referencing this appendix elsewhere, use \ref{AppendixA}

\section{Dataset}

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/00.apoll.png}
		\caption{apoll}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/01.arm.png}
		\caption{arm}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/02.armadillo.png}
		\caption{armadillo}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/03.bearded-guy.png}
		\caption{bearded-guy}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/04.bronze-sculpture.png}
		\caption{bronze-sculpture}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/05.bunny.png}
		\caption{bunny}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/06.car-engine.png}
		\caption{car-engine}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/07.cat.png}
		\caption{cat}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/08.pergolesi-side-chair.png}
		\caption{side-chair}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/09.chair2.png}
		\caption{chair2}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/10.chandelier.png}
		\caption{chandelier}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/11.christmas-bear.png}
		\caption{Christmas-bear}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/12.classic-side-table.png}
		\caption{classic-side-table}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/13.coral.png}
		\caption{coral}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/14.crocodile-statue.png}
		\caption{crocodile-statue}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/15.diane.png}
		\caption{Diane}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/16.dresdner-knabe.png}
		\caption{Dresdner-knabe}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/17.fantasy-dragon.png}
		\caption{fantasy-dragon}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/18.fox-skull.png}
		\caption{fox-skull}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/19.garuda-and-vishnu.png}
		\caption{Garuda and Vishnu}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/20.giraffe-skull.png}
		\caption{giraffe-skull}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/21.green-hat.png}
		\caption{green-hat}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/22.happy-buddha.png}
		\caption{happy-budda}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/23.heart-pendant.png}
		\caption{heart-pendant}
	\end{subfigure}

	\label{fig:dataset_a}
\caption{Point clouds in training dataset A }
\end{figure}
\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/24.indonesian-statue.png}
		\caption{indonesian-statue}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/25.industrial-compressor.png}
		\caption{industrial-compressor}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/26.kylix.png}
		\caption{kylix}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/27.lobster.png}
		\caption{lobster}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/28.head.png}
		\caption{head}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/29.Lu-Yu.png}
		\caption{Lu-Yu}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/30.maitreya.png}
		\caption{Maitreya}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/31.motorbike.png}
		\caption{motorbike}
	\end{subfigure}

		\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/32.motorcycle-wheel.png}
		\caption{motorcycle-wheel}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/33.pan.png}
		\caption{Pan}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/34.plane.png}
		\caption{plane}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/35.elkins-refrigerator.png}
		\caption{elkins-refrigerator}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/36.rutherford-b-hayes-plaster.png}
		\caption{Rutherford}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/37.statue-dragonfly-tamer.png}
		\caption{statue-dragonfly-tamer}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/38.tiger.png}
		\caption{Tiger}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/39.transmission.png}
		\caption{transmission}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/40.universe.png}
		\caption{universe}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/41.vestalin.png}
		\caption{Vestalin}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/42.zebra.png}
		\caption{Zebra}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/43.elephant-zun-base.png}
		\caption{elephant-zun-base}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/44.elephant-zun-lid.png}
		\caption{elephant-zun-lid}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/45.cosmic-buddha.png}
		\caption{cosmic-budda}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/46.fangyi-base.png}
		\caption{fangyi-base}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/47.fangyi-lid.png}
		\caption{fangyi-lid}
	\end{subfigure}

	\label{fig:dataset_b}
	\caption{Point clouds in training dataset B}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/48.guang-base.png}
		\caption{guang-base}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/49.guang-lid.png}
		\caption{guang-lid}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/00.garfield.png}
		\caption{Garfield}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.Bus.png}
		\caption{bus}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/02.dragon.png}
		\caption{dragon}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu.png}
		\caption{baoshanlu}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/04.washington.png}
		\caption{Washington}
	\end{subfigure}
	\label{fig:dataset_c}
	\caption{Point clouds in training dataset C}
\end{figure}

\section{How do I change the colors of links?}

The color of links can be changed to your liking using:

{\small\verb!\hypersetup{urlcolor=red}!}, or

{\small\verb!\hypersetup{citecolor=green}!}, or

{\small\verb!\hypersetup{allcolor=blue}!}.

\noindent If you want to completely hide the links, you can use:

{\small\verb!\hypersetup{allcolors=.}!}, or even better:

{\small\verb!\hypersetup{hidelinks}!}.

\noindent If you want to have obvious links in the PDF but not the printed text, use:

{\small\verb!\hypersetup{colorlinks=false}!}.

### 2022-06-19 paper/Chapters/Chapter01.tex
update paper

--- 2022-06-07 paper/introduction.tex
@@
-%% add noise image
-\begin{figure}[!h]
-	\centering
-	\begin{tikzpicture}
-		\node[inner sep=0pt] (depthmap) at (0,0)
-		{\includegraphics[width=.6\textwidth]{./pic/00028.depth0.png}};
-	\end{tikzpicture}
-	\caption{A captured depth map via infrared sensors.
-Pixels that far away represent by light colors, otherwise by dark colors.
-The black dots are the depths that failed to be detected.
-The black dots distribute in all of the images.}
-	\label{fig:depth_map_with_noise}
-\end{figure}
+% Chapter Template
 
-%% add noise image
-\begin{figure}[!h]
-	\centering
-	\begin{tikzpicture}	
-		\node[inner sep=0pt] (normal) at (8,0)
-		{\includegraphics[width=.6\textwidth]{./pic/00028.normal0.png}};
-	\end{tikzpicture}
-	\caption{Semi-dense Normal Map calculated from depth map using a standard method}
-	\label{fig:standard_normal_inference}
-\end{figure}
+\chapter{Introduction} % Main chapter title
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% intro %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{ch:introduction} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
 
-\section{Introduction}
+%----------------------------------------------------------------------------------------
+%	SECTION 1
+%----------------------------------------------------------------------------------------
+
+\section{From 3D to 2D}
+
+\section{Kinect and Surface Normal}
+
 As a popular and affordable new type of depth sensor, Kinect, had attracted a great focus to computer vision research in the last decades.
@@
 %% why surface normal is important
-Surface Normal is one of the most worthy pieces of information that can inferr from point clouds, which applies in many practical applications, such as augmented reality and robotics.
+Surface Normal is one of the most worthy pieces of information that can infer from point clouds, which applies in many practical applications, such as augmented reality and robotics.
 Some tasks like shading and surface reconstruction require normal as one of the inputs.
 However, due to the lack of accuracy of the sensors, the  surface normal inference from depth maps/point clouds has many challenges.
+
+%-----------------------------------
+%	SUBSECTION 1
+%-----------------------------------
+\section{Standard Methods}
 
@@
 
+%-----------------------------------
+%	SUBSECTION 2
+%-----------------------------------
+
+\section{Deep Learning based Method}
 %% CNN based methods
@@
 
-%%%%%%%%%%%%%%%%%%% talk about the chanllege of this task %%%%%%%%%%%%%%%%%%
-%% talk about the reason we need a new type of network architecture
 However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
@@
 In this case, the traditional network architecture is not suitable anymore.
+
+%----------------------------------------------------------------------------------------
+%	SECTION 2
+%----------------------------------------------------------------------------------------
+
+\section{Challenges of Normal Inference}
 
@@
 
+%% add noise image
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.4\textwidth]{Figures/kinect-depth.png}
+	\decoRule
+	\caption{A captured depth map via infrared sensors. Pixels that far away represent by light colors, otherwise by dark colors. The black dots are the depths that failed to be detected.}
+\label{fig:depth-map-with-noise}
+\end{figure}
+
+%% add noise image
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.4\textwidth]{Figures/real-normal.png}
+	\decoRule
+	\caption{Semi-dense Normal Map calculated from depth map using a standard method}
+\label{fig:standard-normal-inference}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%% talk about the main work in this thesis  %%%%%%%%%%%%%%%%%%
+\section{Main Works of this thesis}
 In this thesis, we found a solution for the problems mentioned above and proposed a novel deep learning architecture for surface normal inference.

### 2022-06-19 paper/Chapters/Chapter02.tex
update paper

--- 2022-06-05 paper/related_work.tex
@@
-From considering neighborhoods in the same plane then using PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last 30 years.
+% Chapter Template
+
+\chapter{Related Work} % Main chapter title
+
+\label{ch:02} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+
+%----------------------------------------------------------------------------------------
+%	SECTION 1
+%----------------------------------------------------------------------------------------
+
+From PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last several decades.
 

### 2022-06-19 paper/Chapters/Chapter04.tex
update paper

% Chapter Template

\chapter{Dataset} % Main chapter title

\label{ch:04} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Synthetic Dataset}
For each object in the resources, a set of generated synthetic 3D scene via Unity is used for each object.  The main advantage using generated scene is the complete information of all the information in the synthetic world. The depth map can be captured in a loss-free way. The corresponding normal map can also be safely considered as ground truth. To construct the dataset, 1000 different scenes have been saved. The model pose, camera position, light position are random changed in each scene.
For each scene, following information is recorded
\begin{itemize}
	\item Depth range
	\item Light position
	\item Camera intrinsic and extrinsic matrix
	\item Depth map
	\item Grayscale image
	\item Normal Map	
\end{itemize}

\begin{itemize}
	\item Grayscale Image
\end{itemize}

In Unity, the grayscale image in acquired via RGB texture by the following equation:
\[ gray: \frac{r+2g+b}{4}  \]

\subsection{Resource}

To train a deep learning model with supervised learning scheme, a dataset should require two principles, truth-worthy ground-truth and comprehensive scenarios. The depth map captured by Kinect is not satisfied the first requirement since it is usually semi-dense with a number of missing pixels, as shown in Figure \ref{fig:depth-map-kinect}. Therefore, a more powerful sensor is required to  perfectly record every detail of the models.

\begin{figure}[!h]
	\centering
	{\includegraphics[width=0.4\textwidth]{./Figures/kinect-depth.png}}
	\label{fig:depth-map-kinect}
	\caption{Depth Map of an object captured by Kinect}
\end{figure}

\cite{data2}, \cite{data3} and \cite{data4} published a sets of point cloud dataset with high resolution detail. The model has its point position, normal direction and uv coordinates, which as be used as ground truth in the training work. In this master thesis, 50 models are selected as training dataset, 5 are selected as test dataset. Figure \ref{fig:dataset-demo} illustrates some of the point clouds. Appendix \ref{AppendixA} gives a full version of dataset models.
\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/00.apoll.png}
		\caption{apoll}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/01.arm.png}
		\caption{arm}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/02.armadillo.png}
		\caption{armadillo}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/03.bearded-guy.png}
		\caption{bearded-guy}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/04.bronze-sculpture.png}
		\caption{bronze-sculpture}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/05.bunny.png}
		\caption{bunny}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/06.car-engine.png}
		\caption{car-engine}
	\end{subfigure}
	\begin{subfigure}[b]{0.23\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/07.cat.png}
		\caption{cat}
	\end{subfigure}

	\label{fig:dataset-demo}
	\caption{Some point clouds in training dataset}
\end{figure}

\subsection{Surface Normal}
%% What is surface normal
\label{sec:surface-normal}
In three dimension geometry, a surface normal at the point $ P $ is a vector $ n $ perpendicular to the tangent plane of the surface at point $ P $. The length of a normal is usually one, with a sign to represent the sides (interior or exterior).%% add a picture to illustrate

\subsection{Point Cloud}
\label{sec:depth-map-to-point-cloud}

A depth map $ D $ is captured by a depth camera like Kinect, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint. The range of distance depends on the performance of depth camera. It can be saved as a 16-bit image, i.e. each pixel in range $0 \tilde 65535$. A depth map with knowing calibration can be further converted to a structured point cloud.

\subsection{Point Cloud calculation}

Consider a 3-dimensional Euclidean space. Use $ z $ axis denotes the depth. The $ x  $ and $ y $ axes perpendicular with each other. For a pixel $ (u,v) $ on depth map, its value $ D(u,v) $ is the $ Z $ component of the 3D point $P_C = (X,Y,Z) $ corresponding the camera origin. Based on the triangle similarity, we can get other two components $ X $ and $ Y $ as follows

\begin{dgroup*}

	\begin{dmath*}
		X = \frac{uZ}{fk_u}
	\end{dmath*}
	\begin{dmath*}
		Y = \frac{vZ}{fk_v}
	\end{dmath*}
\end{dgroup*}

where $ fk_u, fk_v $ is the focal length in pixels align $ u $ and $ v $ axes.
It can be further converted to world coordinate system based on extrinsic matrix $ R $ and $ t $, that is
\[P_W = P_CR+t \]

\subsection{Point Cloud Normalization}

\label{sec:dataset-normalization}
%% How to represent input tensor, to make it fast converse

The vertices have been normalized before feed them into the model. The depth range of each scene is shown in Figure \ref{fig:data-range}.
The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus the normalization is required before feed training objects into the models. Figure \ref{fig:data-range} shows the fluctuation of extreme values and their ranges in 100 random training items. Table \ref{tab:data-range} gives the corresponding average values.
%\begin{figure}[!h]
%	\centering
%	{\includegraphics[width=0.45\textwidth]{./pic/Data_Extreme.png}}
%	{\includegraphics[width=0.45\textwidth]{./pic/Data_Range.png}}
%	\label{fig:data_range}
%	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
%\end{figure}

\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		Axis & Range & Min & Max\\
		\hline
		X & 1.48 & -0.75 & 0.73\\
		Y & 1.56 & -0.76 & 0.80\\
		Z & 1.47 & 6.53 & 8.00\\
		\hline
	\end{tabular}
	\caption{The ranges and extreme values of each axis. The extreme min and max values of both X axis and Y axis are close to $ -0.75 $ and $ 0.75 $ separately. The case for Z axis is $ 6.5 $ and $ 8.0 $ separately. However, the range of three axes are relatively similar, around 1.5. 
	}
	\label{tab:data-range}
\end{table}

For the normalization, first we translate the point to the original point as much as possible, then choose the range value of one axis as a scale factor, normalize it to a unit object.

\begin{equation}\label{eq:normalization}
	U^a = (V^a - V^a_{min}) / s  \quad  \text{for } a \text{ in }  X,Y,Z \text{ axis}
\end{equation}
where $ V^a_{min} $ denote the minimum value appeared in axis $ a $, $ s $ is the range of an axis, which can be any one of X, Y, or Z axis.

In this thesis, the range of X is chosen as scale factor for each scene.

As discussed in \ref{sec:dataset-normalization}, the 3D vertex point cloud should be moved to origin point and normalize in range $ [0,1] $ to acquire a scale invariant feature.

\begin{dgroup*}

	\begin{dmath*}
		X_n =\frac{X-\min(X)}{s}
	\end{dmath*}
	\begin{dmath*}
		Y_n = \frac{Y-\min(Y)}{s}
	\end{dmath*}

	\begin{dmath*}
		Z_n = \frac{Z-\min(Z)}{s}
	\end{dmath*}

\end{dgroup*}

where $ s $ is a scale factor,

\begin{dmath*}
	s = \max(X)-\min(X)
\end{dmath*}
It is calculated as the range in $ X $ axis, but theoretically can be used by $ Y $ or $ Z $ axes as well.

\subsection{Noise}
\label{sec:noise}
The raw depth maps captured by Kinect usually have missing pixels. As shown in Figure \ref{fig:depth_map_kinect}.
Observing the depth map, the missing pixels distributed all around the scene. Therefore an uniformly distributed pixel-delete noise is used for noise simulation. 
It is reasonable that the noise intensities in different scenes are various. Some scenes have more missing pixels and some have less. It enables the model to not only learn scenarios with noise, but also with small minority noise or even without noise. In the noised dataset, the noise intensity is a x-percent pixel dropoff operation. For example, noise-intensity-10 means removes 10\% pixels.
Figure \ref{fig:noise-intensity} shows the visualization of depth map after adding noise.
%% add noise image
\begin{figure}[!h]
	\centering
	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
	\decoRule	
	\caption{Noise-intensity on 0, 10, 20, 30, 40, 50. Object Name: elephant-zun-lid.}
	\label{fig:noise-intensity}
\end{figure}

\subsection{Fit to PyTorch}
In order to saving the training time, the dataset is compressed in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
\begin{table}
	\caption{The structure of a single tensor in the dataset.}
	\label{tab:tensor-structure}
	\centering
	\begin{tabular}{l l}
		\toprule
		\tabhead{Name} & \tabhead{Description} \\
		\midrule
		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
		\hline
		\multirow{4}{*}{output-tensor}  & GT-Normal  \\ & GT-Normal * GT-Light-Direction \\ & Image \\ & GT-Light-Direction \\
		\hline
		Light position & light position \\
		\hline 
		\multirow{3}{*}{Camera Matrix}  & K \\  & R \\  & t \\
		\hline 
		\multirow{2}{*}{Depth Range}  & minDepth \\  & maxDepth \\
		\hline
		\bottomrule\\
	\end{tabular}
\end{table}

\section{Real Dataset}

The real dataset is the depth map and rgb image captured via Kinect...

\section{Metrics for evaluation}
Angle Loss

### 2022-06-19 paper/Chapters/Chapter05.tex
update paper

\chapter{Experiments} % Main chapter title

\label{ch:05} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

The model is trained with PyTorch 1.10.2, CUDA 10.2.89, GPU with single NVIDIA GEFORCE GTX 1080Ti.

%% nnnn exp
\section{Gated Convolution Neural Network for Normal Inference}

The first neural network that worked well for normal prediction in this master thesis is introduced in this section. It is named Gated Convolution Neural Network, or GCNN. The GCNN model is nothing but a UNet with gated convolution layers. it can predict normal map based on a point cloud. The error is around 10 degrees.

The model uses a 512x512x3 3D vertex matrix as input and the output is a 512x512x3 normal map. The architecture is based on description in \ref{sec:architecture}. The channel size is up to 32 through the whole network. For the training parameters, learning rate is 0.001, penalty is 1.4, optimizer is Adam optimizer, the loss function is penalty-l2 loss as described in \ref{sec:loss}.

The evaluation result on 90 test scenes is shown in Figure \ref{fig:scatter-gcnn}.
The GCNN based method has angle error between 5 to 15 degrees in both type of inputs. The error trends to higher with point number decrease. It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution. Therefore the recorded surface based on the point cloud is more coarse, which also increase the difficulty of the normal inference.

\begin{figure}[h!]
	\centering
	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-no-noise.png}
	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-noised.png}
	\caption{Evaluation of average angular loss on the whole test dataset with 90 scenes. The x-axis indicates the point number, the y-axis indicates the angles. The \textbf{Left} one using point cloud without noise, the \textbf{right} one has noise.}
	\label{fig:scatter-gcnn}
\end{figure}

The evaluation visualization on synthetic dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. The error concentrate mainly on severe changed surface region, like the teeth, paw and horn of the dragon.
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_point_cloud_noise.png}
		\caption{point cloud}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_groundtruth.png}
		\caption{ground-truth}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon)}
	\label{fig:gcnn-eval-synthetic}
\end{figure}

The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
		\caption{point cloud}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
		\caption{ground-truth}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{Evaluation on Real Dataset}
	\label{fig:gcnn-eval-real}
\end{figure}

%% resng
\section{Guided Gated Convolution Neural Network for Normal Inference }

\newpage 
\section{model comparison}
This section evaluates the proposed models with the neighbor-based model and make comparison with each other.

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_groundtruth.png}
		\caption{ground-truth}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_normal_svd.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_normal_NG.png}
		\caption{guided-GCNN}
	\end{subfigure}

	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_error_SVD.png}
		\caption{Error}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_error_GCNN.png}
		\caption{Error}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_error_NG.png}
		\caption{Error}
	\end{subfigure}

	\caption{Normal Inference on different models with errors. (object: dragon)}
	\label{fig:eval-svd}
\end{figure}

### 2022-06-19 paper/Chapters/Chapter06.tex
update paper

% Chapter Template

\chapter{Conclusion} % Main chapter title

\label{ch:06} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
Gated convolution neural network...

### 2022-06-19 paper/akweury/document.tex
update paper

\documentclass[]{article}
\usepackage{amssymb}
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}

\begin{document}

\section{Guided Gated Convolution Neural Network for Normal Inference }

The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}. With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_normal_NG.png}
		\caption{g-GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_error_NG.png}
		\caption{Angle Error}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{guided-GCNN Normal Inference on Synthetic Dataset (object: dragon). GCNN result is shown on (d) and (e) as comparison.}
	\label{fig:ng-eval-synthetic}
\end{figure}

\end{document}

### 2022-06-19 paper/main.tex
update paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Masters/Doctoral Thesis 
% LaTeX Template
% Version 2.5 (27/8/17)
%
% This template was downloaded from:
% http://www.LaTeXTemplates.com
%
% Version 2.x major modifications by:
% Vel (vel@latextemplates.com)
%
% This template is based on a template by:
% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
%
% Template license:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

%\usepackage[utf8]{inputenc} % Required for inputting international characters
%\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{amssymb}
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}
%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=3.8cm, % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	THESIS INFORMATION
%----------------------------------------------------------------------------------------

\thesistitle{Improved Normal Inference from Calibrated Illuminated RGBD Images} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Dr. Didier \textsc{Stricker}}

 % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Jingyuan  \textsc{Sha}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Computer Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{https://www.uni-kl.de/}{Technische Universität Kaiserslautern}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{https://www.informatik.uni-kl.de/}{German Research Center for Artificial Intelligence}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{https://av.dfki.de/}{Augmented Vision}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{Faculty Name}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
%\hypersetup{colorlinks=false}
\hypersetup{hidelinks}
}

\begin{document}

\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages

\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}
\begin{center}
\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Master Thesis}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{https://linkedin.com/in/jingyuan-sha-5b8b43208}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{https://av.dfki.de/members/stricker/}{\supname}\\
\href{https://av.dfki.de/members/fetzer/}{M. Sc. Torben \textsc{Fetzer}}
 % Supervisor name - remove the \href bracket to remove the link  
\end{flushright}
\end{minipage}\\[3cm]

\vfill

\groupname\\\deptname\\ % Research group name and department name
\includegraphics{Figures/TUK_LOGO_RGB}\\[2cm] % Research group name and department name

\vfill

{\large \today}\\[4cm] % Date
%\includegraphics{Logo} % University/department logo - uncomment to place it

\vfill
\end{center}
\end{titlepage}

%----------------------------------------------------------------------------------------
%	DECLARATION PAGE
%----------------------------------------------------------------------------------------

\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

\cleardoublepage

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak

\hfill Dave Barry

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
\end{acknowledgements}

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

\tableofcontents % Prints the main table of contents

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)

\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\

\end{abbreviations}

%----------------------------------------------------------------------------------------
%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
%----------------------------------------------------------------------------------------

\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it

Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
%Constant Name & $Symbol$ & $Constant Value$ with units\\

\end{constants}

%----------------------------------------------------------------------------------------
%	SYMBOLS
%----------------------------------------------------------------------------------------

\begin{symbols}{lll} % Include a list of Symbols (a three column table)

$a$ & distance & \si{\meter} \\
$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
%Symbol & Name & Unit \\

\addlinespace % Gap to separate the Roman symbols from the Greek

$\omega$ & angular frequency & \si{\radian} \\

\end{symbols}

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedicatory{To ...}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter % Begin numeric (1,2,3...) page numbering

\pagestyle{thesis} % Return the page headers back to the "thesis" style

% Include the chapters of the thesis as separate files from the Chapters folder
% Uncomment the lines as you write the chapters

\include{Chapters/Chapter01}
\include{Chapters/Chapter02} 
\include{Chapters/Chapter03}
\include{Chapters/Chapter04} 
\include{Chapters/Chapter05} 
\include{Chapters/Chapter06}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\appendix % Cue to tell LaTeX that the following "chapters" are Appendices

% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\printbibliography[heading=bibintoc]

%----------------------------------------------------------------------------------------

\end{document}

### 2022-06-19 eval_visual.py

@@ -197,9 +197,11 @@ def start2(models_path_dict):
         #                                        mu.visual_vertex(vertex_0, "Input(Vertex)"),
         #                                        gt_img], [], []
         # cv.imwrite(str(folder_path / f"fancy_eval_{i}_error_gt.png"), black_img)
+        mu.save_array(gt, str(folder_path / f"fancy_eval_{i}_normal_gt"))
+
         cv.imwrite(str(folder_path / f"fancy_eval_{i}_img.png"), img)
         cv.imwrite(str(folder_path / f"fancy_eval_{i}_groundtruth.png"),
-                   cv.cvtColor(mu.visual_normal(gt, "GT"), cv.COLOR_RGB2BGR), )
+                   cv.cvtColor(mu.visual_normal(gt, "", histogram=False), cv.COLOR_RGB2BGR), )
         cv.imwrite(str(folder_path / f"fancy_eval_{i}_point_cloud_noise.png"),
                    mu.visual_vertex(vertex_0, ""))
         # evaluate CNN models
@@ -240,9 +242,9 @@ def start2(models_path_dict):
                     raise ValueError
 
             normal[mask] = 0
-
+            mu.save_array(normal, str(folder_path / f"fancy_eval_{i}_normal_{name}"))
             cv.imwrite(str(folder_path / f"fancy_eval_{i}_normal_{name}.png"),
-                       cv.cvtColor(mu.visual_normal(normal, name), cv.COLOR_RGB2BGR))
+                       cv.cvtColor(mu.visual_normal(normal, "", histogram=False), cv.COLOR_RGB2BGR))
 
             # visual normal
             # output_list.append(mu.visual_normal(normal, name))
@@ -276,8 +278,8 @@ if __name__ == '__main__':
 
     models = {
         "SVD": None,
-        # "NG": config.ws_path / "ng" / "trained_model" / "checkpoint-2800.pth.tar",  # image guided
-        "AG": config.ws_path / "ag" / "trained_model" / "checkpoint-365.pth.tar",  # with light direction
+        "NG": config.ws_path / "ng" / "trained_model" / "checkpoint-2800.pth.tar",  # image guided
+        # "AG": config.ws_path / "ag" / "trained_model" / "checkpoint-365.pth.tar",  # with light direction
         # "NG+": config.ws_path / "resng" / "trained_model" / "checkpoint.pth.tar",
[…]

### 2022-06-19 help_funs/mu.py

@@ -570,6 +570,7 @@ def addHist(img):
         histr, histr_x = np.histogram(img[:, :, i], bins=np.arange(hist_min, hist_max + 1))
         histr = np.delete(histr, np.where(histr == histr.max()), axis=0)
 
+        # plot histogram on the image
         thick = 2
         histr = histr / max(histr.max(), 100)
         for i in range(histr.shape[0]):
@@ -579,6 +580,36 @@ def addHist(img):
             max(0, i * width - thick):min(w - 1, i * width + thick)] = col
     plt.close('all')
     return color_ranges
+
+
+def rgb_diff(img1, img2):
+    diff = np.zeros(shape=(3, 256))
+    h, w = img1.shape[:2]
+    color = ([255, 0, 0], [0, 255, 0], [0, 0, 255])
+    for i, col in enumerate(color):
+        histr1, histr_x1 = np.histogram(img1[:, :, i], bins=256, range=(0, 255))
+        histr2, histr_x2 = np.histogram(img2[:, :, i], bins=256, range=(0, 255))
+
+        histr1[0] = 0
+        histr2[0] = 0
+
+        diff[i, :] = histr1 - histr2
+    return diff
+
+
+def normal_diff(img1, img2):
+    diff = np.zeros(shape=(3, 256))
+    h, w = img1.shape[:2]
+    color = ([255, 0, 0], [0, 255, 0], [0, 0, 255])
+    for i, col in enumerate(color):
+        histr1, histr_x1 = np.histogram(img1[:, :, i], bins=256, range=(0, 255))
+        histr2, histr_x2 = np.histogram(img2[:, :, i], bins=256, range=(0, 255))
+
+        histr1[0] = 0
+        histr2[0] = 0
+
+        diff[i, :] = histr1 - histr2
+    return diff
 
 
 def pure_color_img(color, size):
@@ -1025,3 +1056,7 @@ def visual_albedo(rho, name):
 
     addText(img, f"{name}(albedo)", font_size=0.8)
     return img
+
+
+def save_array(arr, save_path):
+    np.save(save_path, arr)

### 2022-06-20 paper/Chapters/Chapter05.tex
add new model: fgcnn

@@
 
+The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}.
+With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_normal_NG.png}
+		\caption{g-GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_error_NG.png}
+		\caption{Angle Error}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
+		\caption{Angle Error}
+	\end{subfigure}
+	\caption{guided-GCNN Normal Inference on Synthetic Dataset (object: dragon). GCNN result is shown on (d) and (e) as comparison.}
+	\label{fig:ng-eval-synthetic}
+\end{figure}
+
 \newpage 

### 2022-06-20 paper/akweury/document.tex
add new model: fgcnn

@@
 
-The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}.
-With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.
+From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
+It separates the interval \left[ -1,1 \right], which is exactly the range of normal vector, to 256 sections.
+Then it counts the number of points locates in each section for 3 axes.
+The 3 axes are fitted quit well in most of interval but other than \left[ -0.25,0.25 \right] for x and y axes and  interval close to $ -1 $ for z axis.
+Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
 
+It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
 \begin{figure}[h!]
 	\centering
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_normal_NG.png}
-		\caption{g-GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_error_NG.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\caption{guided-GCNN Normal Inference on Synthetic Dataset (object: dragon). GCNN result is shown on (d) and (e) as comparison.}
-	\label{fig:ng-eval-synthetic}
+	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff/normal-histo-diff.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
 \end{figure}

### 2022-06-20 help_funs/mu.py

@@ -597,19 +597,30 @@ def rgb_diff(img1, img2):
     return diff
 
 
+def normal_histo(normal):
+    mask = np.sum(normal, axis=2) == 0
+    histo = np.zeros(shape=(3, 100))
+    hist_x = None
+    for i in range(3):
+        histr1, hist_x = np.histogram(normal[:, :, i][~mask], bins=100, range=(-2, 2))
+        histo[i, :] = histr1
+    return histo, hist_x
+
+
 def normal_diff(img1, img2):
     diff = np.zeros(shape=(3, 256))
     h, w = img1.shape[:2]
     color = ([255, 0, 0], [0, 255, 0], [0, 0, 255])
+    hist_x = None
     for i, col in enumerate(color):
-        histr1, histr_x1 = np.histogram(img1[:, :, i], bins=256, range=(0, 255))
-        histr2, histr_x2 = np.histogram(img2[:, :, i], bins=256, range=(0, 255))
+        histr1, hist_x = np.histogram(img1[:, :, i], bins=256, range=(-1, 1))
+        histr2, hist_x = np.histogram(img2[:, :, i], bins=256, range=(-1, 1))
 
         histr1[0] = 0
         histr2[0] = 0
 
         diff[i, :] = histr1 - histr2
-    return diff
+    return diff, hist_x
 
 
 def pure_color_img(color, size):
@@ -718,6 +729,10 @@ def show_images(array, title):
     cv.imshow(title, array)
     cv.waitKey(0)
     cv.destroyAllWindows()
+
+
+def show_normal(normal, title="Normal"):
+    show_images(cv.cvtColor(visual_normal(normal, ""), cv.COLOR_RGB2BGR), title)
 
 
 def show_grid(grid, title):

### 2022-06-20 help_funs/worksheet.py

@@ -1,37 +1,26 @@
 import shutil
 
-import cv2 as cv
 import numpy as np
 import torch
 
 import config
-from help_funs import file_io, mu, chart
+from help_funs import mu, chart
 
 
-def test_torch():
-    # depth_file = str(config.ws_path / "a.png")
-    data_file = str(config.synthetic_data / "train" / '00102.normal0.png')
-    normal = file_io.load_24bitNormal(data_file).astype(np.float32)
-    data_tensor = torch.from_numpy(normal).permute(2, 0, 1)
-    img, img_extended = mu.hpf_torch(data_tensor)
-    cv.imwrite(str(config.ws_path / f"aa.png"), img.numpy())
+def gau_histo(gt_normal, sigma):
+    gt_normal = torch.from_numpy(gt_normal)
+    mask = gt_normal != 0
+    min = -2
+    max = 2
+    bins = 100
+    delta = float(max - min) / float(bins)
+    centers = min + delta * (torch.arange(bins).float() + 0.5)
 
-
-#
-#
-# def test_png():
-#     depth_file = str(
-#         config.ws_path / "degares" / "output" / "output_2022-05-24_15_14_04" / "train_epoch_199_0_loss_0.16585270.png")
-#     img = mu.hpf(depth_file)
-#     cv.imwrite(str(config.ws_path / "degares" / "output" / "output_2022-05-24_15_14_04" / f"aa.png"), img)
-
-
-def print_cuda_info():
-    print(f"Cuda is available: {torch.cuda.is_available()}")
-    print(f"Device count: {torch.cuda.device_count()}")
-    print(f"Current Device: {torch.cuda.current_device()}")
-    print(f"Device Name: {torch.cuda.get_device_name(torch.cuda.current_device())}")
-
+    output_histo = gt_normal[mask].unsqueeze(0) - centers.unsqueeze(1)
+    output_histo = torch.exp(-0.5 * (output_histo / sigma) ** 2) / (sigma * np.sqrt(np.pi * 2)) * delta
+    output_histo = output_histo.sum(dim=-1)
+    output_histo = (output_histo - output_histo.min()) / (output_histo.max() - output_histo.min())  # normalization
+    return output_histo
 
 if __name__ == '__main__':
     # test_torch()
@@ -40,11 +29,20 @@ if __name__ == '__main__':
 
[…]

### 2022-06-20 main.py

@@ -4,7 +4,7 @@ import workspace.degares.network as degares
 import workspace.ncnn.network as ncnn
 import workspace.ng.network as ng
 import workspace.sconv.network as nnn
-import workspace.nnn24.network as nnn24
+import workspace.fugrc.network as fugrc
 import workspace.nnnn.network as nnnn
 import workspace.resng.network as resng
 from pncnn.utils import args_parser
@@ -29,7 +29,8 @@ def main():
         model = resng.CNN()
     elif args.exp == "degares":
         model = degares.CNN()
-
+    elif args.exp == "fugrc":
+        model = fugrc.CNN(args.num_channels)
     elif args.exp == "ncnn":
         model = ncnn.CNN(args.num_channels)
     elif args.exp == "ag":

### 2022-06-20 paper/Chapters/Chapter04.tex
fix bugs in training evaluation

@@
 \section{Synthetic Dataset}
-For each object in the resources, a set of generated synthetic 3D scene via Unity is used for each object.
-The main advantage using generated scene is the complete information of all the information in the synthetic world.
-The depth map can be captured in a loss-free way.
-The corresponding normal map can also be safely considered as ground truth.
-To construct the dataset, 1000 different scenes have been saved.
-The model pose, camera position, light position are random changed in each scene.
-For each scene, following information is recorded
-\begin{itemize}
-	\item Depth range
-	\item Light position
-	\item Camera intrinsic and extrinsic matrix
-	\item Depth map
-	\item Grayscale image
-	\item Normal Map	
-\end{itemize}
-
-\begin{itemize}
-	\item Grayscale Image
-\end{itemize}
-
-In Unity, the grayscale image in acquired via RGB texture by the following equation:
-\[ gray: \frac{r+2g+b}{4}  \]
+To train a deep learning model with supervised learning scheme, a dataset should require two principles, truth-worthy ground-truth and comprehensive scenarios.
+The depth map captured by Kinect is not satisfied the first requirement since it is usually semi-dense with a number of missing pixels, as shown in Figure \ref{fig:kinect-depth}.
+Therefore, a more elaborate depth map is required for the training work.
+In this thesis, a dataset called ``synthetic50" is created for the training works.
 
 \subsection{Resource}
+\cite{data1}, \cite{data2}, \cite{data3} and \cite{data4} published a set of point cloud dataset on the internet for computer vision task research.
+These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing.
+Each objects has been scanned for hundreds of times for an exhaustive completion for the origin objects, which is up to millions points.
+(\cite{data1}).
+The dense point clouds makes the normal inference task trivial since the neighbor based method performs good enough for these kind of task.
+Some of the point cloud even equipped with pre-computed normal map based on more advanced methods.
+They all provides the accurate ground-truth for the supervised learning method.
 
-To train a deep learning model with supervised learning scheme, a dataset should require two principles, truth-worthy ground-truth and comprehensive scenarios.
-The depth map captured by Kinect is not satisfied the first requirement since it is usually semi-dense with a number of missing pixels, as shown in Figure \ref{fig:depth-map-kinect}.
-Therefore, a more powerful sensor is required to  perfectly record every detail of the models.
-
-\begin{figure}[!h]
-	\centering
-	{\includegraphics[width=0.4\textwidth]{./Figures/kinect-depth.png}}
-	\label{fig:depth-map-kinect}
-	\caption{Depth Map of an object captured by Kinect}
-\end{figure}
-
-\cite{data2}, \cite{data3} and \cite{data4} published a sets of point cloud dataset with high resolution detail.
-The model has its point position, normal direction and uv coordinates, which as be used as ground truth in the training work.
-In this master thesis, 50 models are selected as training dataset, 5 are selected as test dataset.
+In this thesis, 50 point clouds scanned on real objects have been used for training work and 5 point clouds have been used for test work.
 Figure \ref{fig:dataset-demo} illustrates some of the point clouds.
 Appendix \ref{AppendixA} gives a full version of dataset models.
+
 \begin{figure}[!h]
@@
 	\label{fig:dataset-demo}
-	\caption{Some point clouds in training dataset}
+	\caption{Point clouds scanned by high resolution scanners}
 \end{figure}
 
-\subsection{Surface Normal}
+\subsection{Data Files}
+In order to fit the using scenario of Kinect as much as possible, a set of synthetic 3D scenes of each object is captured via Unity, which is a game engine using for 3D games creation.
+It can place the point cloud in a virtual   The main advantage using generated scene is the complete information of all the information in the synthetic world.
+The depth map can be captured in a loss-free way.
+The corresponding normal map can also be safely considered as ground truth.
+To construct the dataset, 1000 different scenes have been saved.
+The model pose, camera position, light position are random changed in each scene.
+For each scene, following information is recorded
+\begin{itemize}
+	\item Depth range
+	\item Light position
+	\item Camera intrinsic and extrinsic matrix
+	\item Depth map
+	\item Grayscale image
+	\item Normal Map	
+\end{itemize}
+
+\begin{itemize}
+	\item Grayscale Image
+\end{itemize}
+
+In Unity, the grayscale image in acquired via RGB texture by the following equation:
+\[ gray: \frac{r+2g+b}{4}  \]
+
 %% What is surface normal

### 2022-06-20 help_funs/mu.py

@@ -715,7 +715,7 @@ def tenor2numpy(tensor):
     elif tensor.size() == (1, 1, 512, 512):
         return tensor.permute(2, 3, 1, 0).sum(dim=3).detach().numpy()
     else:
-        print("Unsupported input tensor size.")
+        raise ValueError("Unsupported input tensor size.")
 
 
 def show_tensor(tensor, title):

### 2022-06-20 workspace/train.py

@@ -778,10 +778,7 @@ def draw_output(exp_name, x0, xout, target, exp_path, epoch, i, train_idx, outpu
     output_list = []
 
     # input normal
-    if output_type == "noise":
-        input = mu.tenor2numpy(x0[:1, :1, :, :])
-    else:
-        input = mu.tenor2numpy(x0[:1, :3, :, :])
+    input = x0[:1, :3, :, :].permute(2, 3, 1, 0).squeeze(-1).detach().numpy()
     x0_normalized_8bit = mu.normalize2_32bit(input)
     x0_normalized_8bit = mu.image_resize(x0_normalized_8bit, width=512, height=512)
     mu.addText(x0_normalized_8bit, "Input(Vertex)")

### 2022-06-20 paper/Chapters/Chapter04.tex
update nnnn args

@@
 Therefore, a more elaborate depth map is required for the training work.
-In this thesis, a dataset called ``synthetic50" is created for the training works.
+In this thesis, a dataset called ``synthetic50-5" is created for the training works.
 
@@
 
-In this thesis, 50 point clouds scanned on real objects have been used for training work and 5 point clouds have been used for test work.
-Figure \ref{fig:dataset-demo} illustrates some of the point clouds.
+The ``synthetic50-5", is a datset with 50 point clouds as training set and 5 point clouds as test set.
+The dataset is created base on the work of this thesis and using for normal inference task.
+Figure \ref{fig:dataset-demo} gives the illustrations of some objects.
 Appendix \ref{AppendixA} gives a full version of dataset models.
@@
 \subsection{Data Files}
-In order to fit the using scenario of Kinect as much as possible, a set of synthetic 3D scenes of each object is captured via Unity, which is a game engine using for 3D games creation.
-It can place the point cloud in a virtual   The main advantage using generated scene is the complete information of all the information in the synthetic world.
+In order to fit the using scenario of Kinect as much as possible, the dataset consists of the generated synthetic 3D scenes via Unity, which is a game engine using for 3D games creation.
+
+In the synthetic scenes from engine, the object is placed on a cylinder platform, which is lighted by a directional light nearby.
+A camera focus on the platform and captured the scene.
+The layout in the game engine is shown in Figure \ref{fig:unity-workplace}.
+In order to simulate more scenarios, the positions of the camera and directional light are randomly changed in each new scene.
+For 50 training objects, 1000 scenes are generated and each scene is saved in 3 kinds of resolutions $ 512\times512\times3 $, $ 256\times256\times3 $ and $ 128\times128\times3 $.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=.8\textwidth]{./Figures/unity-workplace.PNG}
+	\caption{The layout of synthetic scenes generation in Unity.}
+	\label{fig:unity-workplace}
+\end{figure}
+
+The main advantage using generated scene is the availability of complete information.
 The depth map can be captured in a loss-free way.
 The corresponding normal map can also be safely considered as ground truth.
-To construct the dataset, 1000 different scenes have been saved.
-The model pose, camera position, light position are random changed in each scene.
+And the scale of the dataset is easy to control.
+
 For each scene, following information is recorded
@@
 \end{itemize}
-
-\begin{itemize}
-	\item Grayscale Image
-\end{itemize}
-
-In Unity, the grayscale image in acquired via RGB texture by the following equation:
+where the grayscale image in acquired via RGB texture by the following equation:
 \[ gray: \frac{r+2g+b}{4}  \]
-
-%% What is surface normal
-\label{sec:surface-normal}
-In three dimension geometry, a surface normal at the point $ P $ is a vector $ n $ perpendicular to the tangent plane of the surface at point $ P $.
-The length of a normal is usually one, with a sign to represent the sides (interior or exterior).%% add a picture to illustrate
 

### 2022-06-21 paper/Chapters/Chapter04.tex
update conv layer

@@
 
-\subsection{Data Files}
+\subsection{Synthesize Scenes using Unity}
 In order to fit the using scenario of Kinect as much as possible, the dataset consists of the generated synthetic 3D scenes via Unity, which is a game engine using for 3D games creation.
@@
 For each scene, following information is recorded
-\begin{itemize}
-	\item Depth range
-	\item Light position
-	\item Camera intrinsic and extrinsic matrix
-	\item Depth map
-	\item Grayscale image
-	\item Normal Map	
-\end{itemize}
-where the grayscale image in acquired via RGB texture by the following equation:
+\begin{table}
+	\caption{The information saved for each scene in ``synthetic50-5".}
+	\label{tab:data-files}
+	\centering
+	\begin{tabular}{l l}
+		\toprule
+		\tabhead{Data} & \tabhead{Size} \\
+		\midrule
+		Depth map & $ 512\times512\times3 $ \\
+		\hline 
+		Depth range  & $ 2\times1 $ \\  
+		\hline
+		Grayscale Image	& $ 512\times512\times1 $ \\  
+		\hline 
+		Normal Map &  $ 512\times512\times3 $  \\
+		\hline 
+		Light Position &  $ 3\times1 $  \\
+		\hline
+		Camera Intrinsic Matrix &  $ 3\times 3 $  \\
+		\hline 
+		Camera Extrinsic Matrix &  $ 3\times 4 $  \\
+		\hline 
+		\bottomrule\\
+	\end{tabular}
+\end{table}
+
+A depth map $ D $ is captured by a depth camera in Unity, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
+It can be saved as a 16-bit grayscale image, i.e.
+each pixel in range $0 - 65535$.
+The grayscale image can be used as guided normal inference task and also as a readable scene for human.
+The gray-color is converted from RGB color based on following equation
 \[ gray: \frac{r+2g+b}{4}  \]
+The normal map is the tangent surface normal, which is saved in 32-bit RGB color image. The surface normal and its corresponding RGB color can be converted based on following equation:
+\[  \]
+If consider the relation between Lambertian reflection and normal direction, the light source can be used to calculate the reflect direction of each point.
+The camera intrinsic and extrinsic matrix helps point cloud calculation.
 
-\subsection{Point Cloud}
+It is necessary to point out again that ``synthetic50-5" aiming to rebuild the using scenarios of Kinect, where all types of the generated data files shown in Table \ref{tab:data-files} are also the same format of the Kinect data.
+
+\subsection{Convert to Point Cloud}
 \label{sec:depth-map-to-point-cloud}
-
-A depth map $ D $ is captured by a depth camera like Kinect, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
-The range of distance depends on the performance of depth camera.
-It can be saved as a 16-bit image, i.e.
-each pixel in range $0 \tilde 65535$.
-A depth map with knowing calibration can be further converted to a structured point cloud.
+The depth map can be converted to 3D vertex point cloud as the input of the normal inference model.
 

### 2022-06-21 paper/Chapters/Chapter04.tex
update fgcnn

@@
 \[ gray: \frac{r+2g+b}{4}  \]
-The normal map is the tangent surface normal, which is saved in 32-bit RGB color image. The surface normal and its corresponding RGB color can be converted based on following equation:
-\[  \]
+The normal map is the tangent surface normal, which is saved in 32-bit RGB color image.
+The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on following equation:
+\begin{dgroup*}
+	\begin{dmath*}
+		n_x = \frac{R}{255} * 2 - 1
+	\end{dmath*}
+	\begin{dmath*}
+		n_y = \frac{G}{255}*2 - 1
+	\end{dmath*} 
+	\begin{dmath*}
+		n_z = 1-\frac{B}{255} * 2
+	\end{dmath*}
+\end{dgroup*}
 If consider the relation between Lambertian reflection and normal direction, the light source can be used to calculate the reflect direction of each point.
@@
 
-\subsection{Point Cloud calculation}
+\begin{figure}[h!]
+	\centering
+	\begin{tikzpicture} 
+		% reference lines
+		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
+		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
+		\draw[thick,dashed]	(0,6) -- (10,6); % top
+		% camera 
+		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
+		% world point 
+		\filldraw[black] (7,6) circle (2pt) node[anchor=north west]{Point};
+		% image point
+		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
+		% similiar triangles
+		\draw[thick] (5,0) -- (5,6); % AB
+		\draw[thick] (5,0) -- (7,6); % AC
+		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
+		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
+		% measure arrows
+		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
+		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
+	\end{tikzpicture}	
+	\caption{Convert depth to point in camera coordinate system}
+	\label{fig:depth-triangulation}
+\end{figure}
 
@@
 The $ x  $ and $ y $ axes perpendicular with each other.
-For a pixel $ (u,v) $ on depth map, its value $ D(u,v) $ is the $ Z $ component of the 3D point $P_C = (X,Y,Z) $ corresponding the camera origin.
-Based on the triangle similarity, we can get other two components $ X $ and $ Y $ as follows
-
+For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ in camera coordinate system.
+The $ X $ and $ Y $ can be calculated based on the triangle similarity
 \begin{dgroup*}
@@
 where $ fk_u, fk_v $ is the focal length in pixels align $ u $ and $ v $ axes.
-It can be further converted to world coordinate system based on extrinsic matrix $ R $ and $ t $, that is
+Converted a point from camera coordinate system to world coordinate system, using extrinsic matrix $ R $ and $ t $
 \[P_W = P_CR+t \]
@@
 Table \ref{tab:data-range} gives the corresponding average values.
-%\begin{figure}[!h]
-%	\centering
-%	{\includegraphics[width=0.45\textwidth]{./pic/Data_Extreme.png}}
-%	{\includegraphics[width=0.45\textwidth]{./pic/Data_Range.png}}
-%	\label{fig:data_range}
-%	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
-%\end{figure}
+\begin{figure}[!h]
+	\centering
+	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
+	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
+	\label{fig:data_range}
+	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
+\end{figure}
 
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		Axis & Range & Min & Max\\
-		\hline
-		X & 1.48 & -0.75 & 0.73\\
-		Y & 1.56 & -0.76 & 0.80\\
-		Z & 1.47 & 6.53 & 8.00\\
-		\hline
-	\end{tabular}
+\begin{table}[h!]
 	\caption{The ranges and extreme values of each axis.
@@
 	\label{tab:data-range}
+	\centering
+	\begin{tabular}{c c c c}
+		\toprule
+		\tabhead{Axis} & \tabhead{Range} & \tabhead{Min} & \tabhead{Max}\\
+		\midrule
+		X & 1.48 & -0.75 & 0.73\\
+		Y & 1.56 & -0.76 & 0.80\\
+		Z & 1.47 & 6.53 & 8.00\\
+		\bottomrule\\
+	\end{tabular}
 \end{table}

### 2022-06-21 paper/Chapters/Chapter05.tex
update fgcnn

@@
 
+\section{Guided Gated Convolution Neural Network for Normal Inference }
+
+From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
+It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
+Then it counts the number of points locates in each section for 3 axes.
+The 3 axes are fitted quit well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
+Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
+
+It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
+\end{figure}
+
 \newpage 

### 2022-06-21 paper/akweury/document.tex
update fgcnn

--- 2022-06-19 paper/akweury/document.tex
@@
 
-\section{Guided Gated Convolution Neural Network for Normal Inference }
-
-The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}.
-With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.
-
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_normal_NG.png}
-		\caption{g-GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_error_NG.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\caption{guided-GCNN Normal Inference on Synthetic Dataset (object: dragon). GCNN result is shown on (d) and (e) as comparison.}
-	\label{fig:ng-eval-synthetic}
-\end{figure}
-
 \end{document}

### 2022-06-21 common/FGCNN.py

@@ -21,8 +21,8 @@ class FGCNN(nn.Module):
         # self.epsilon = 1e-20
         channel_size_1 = channel_num
         channel_size_2 = channel_num * 2
-        channel_size_3 = channel_num * 4
-        channel_size_4 = channel_num * 8
+        channel_size_3 = channel_num * 2
+        channel_size_4 = channel_num * 2
         # https://homepages.inf.ed.ac.uk/rbf/CVonline/LOCAL_COPIES/PIRODDI1/NormConv/node2.html#:~:text=The%20idea%20of%20normalized%20convolution,them%20is%20equal%20to%20zero.
 
         # intro

### 2022-06-21 paper/Chapters/Chapter04.tex
update fgcnn

@@
 \subsection{Point Cloud Normalization}
-
 \label{sec:dataset-normalization}
 %% How to represent input tensor, to make it fast converse
+The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus the normalization is required before feed training objects into the models.
+The range of each axis is shown in Figure \ref{fig:data-range}.  Table \ref{tab:data-range} gives a quantitative measurement of corresponding average values.
 
-The vertices have been normalized before feed them into the model. The depth range of each scene is shown in Figure \ref{fig:data-range}.
-The sizes of each training object are various, whereas it should be as an invariant value for the training model.
-Thus the normalization is required before feed training objects into the models.
-Figure \ref{fig:data-range} shows the fluctuation of extreme values and their ranges in 100 random training items.
-Table \ref{tab:data-range} gives the corresponding average values.
-\begin{figure}[!h]
-	\centering
-	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
-	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
-	\label{fig:data_range}
-	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
-\end{figure}
-
-\begin{table}[h!]
-	\caption{The ranges and extreme values of each axis.
-The extreme min and max values of both X axis and Y axis are close to $ -0.75 $ and $ 0.75 $ separately.
-The case for Z axis is $ 6.5 $ and $ 8.0 $ separately.
-However, the range of three axes are relatively similar, around 1.5.
-	}
-	\label{tab:data-range}
-	\centering
-	\begin{tabular}{c c c c}
-		\toprule
-		\tabhead{Axis} & \tabhead{Range} & \tabhead{Min} & \tabhead{Max}\\
-		\midrule
-		X & 1.48 & -0.75 & 0.73\\
-		Y & 1.56 & -0.76 & 0.80\\
-		Z & 1.47 & 6.53 & 8.00\\
-		\bottomrule\\
-	\end{tabular}
-\end{table}
-
-For the normalization, first we translate the point to the original point as much as possible, then choose the range value of one axis as a scale factor, normalize it to a unit object.
-
-\begin{equation}\label{eq:normalization}
-	U^a = (V^a - V^a_{min}) / s  \quad  \text{for } a \text{ in }  X,Y,Z \text{ axis}
-\end{equation}
-where $ V^a_{min} $ denote the minimum value appeared in axis $ a $, $ s $ is the range of an axis, which can be any one of X, Y, or Z axis.
-
-In this thesis, the range of X is chosen as scale factor for each scene.
-
-As discussed in \ref{sec:dataset-normalization}, the 3D vertex point cloud should be moved to origin point and normalize in range $ [0,1] $ to acquire a scale invariant feature.
-
+The normalization has been performed as follows.
+First translate the points to the original point as close as possible, then choose the range value of one axis as a scale factor, normalize the points to unit vectors.
+The equation is shown as follows
 \begin{dgroup*}
@@
 	\end{dmath*}
-
 \end{dgroup*}
@@
 
+\begin{figure}[!h]
+	\centering
+	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
+	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
+	\label{fig:data_range}
+	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
+\end{figure}
+
+\begin{table}[h!]
+	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. 
+	}
+	\label{tab:data-range}
+	\centering
+	\begin{tabular}{c c c c}
+		\toprule
+		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
+		\midrule
+		X & 1.48 & -0.75 & 0.73\\
+		Y & 1.56 & -0.76 & 0.80\\
+		Z & 1.47 & 6.53 & 8.00\\
+		\bottomrule\\
+	\end{tabular}
+\end{table}
+
 \subsection{Noise}
 \label{sec:noise}
-The raw depth maps captured by Kinect usually have missing pixels. As shown in Figure \ref{fig:depth_map_kinect}.
-Observing the depth map, the missing pixels distributed all around the scene. Therefore an uniformly distributed pixel-delete noise is used for noise simulation. 
-It is reasonable that the noise intensities in different scenes are various.
-Some scenes have more missing pixels and some have less.
-It enables the model to not only learn scenarios with noise, but also with small minority noise or even without noise.
-In the noised dataset, the noise intensity is a x-percent pixel dropoff operation.
-For example, noise-intensity-10 means removes 10\% pixels.
-Figure \ref{fig:noise-intensity} shows the visualization of depth map after adding noise.
+The raw depth maps captured by Kinect usually have missing pixels. Therefore, the ``synthetic50-5" dataset adds a similar properties.
+As shown in Figure \ref{fig:depth_map_kinect}.
+the depth map has missing pixels distributed all around the scene.
+Correspondingly, an uniformly distributed pixel-delete noise is used for noise simulation.
+Furthermore, a parameter $ \mu $ is used to control the intensity of noise, it denotes the $ \mu $-percent pixel dropoff.
+For example, $ \mu-10 $ means removes 10\% pixels randomly.
+For each scene, the noising operation based on a random $ \mu $ in a range $ \left[0, 50\right] $, therefore some scenes have more missing pixels and some have less.
+The random noise intensity also enables the model to learn scenarios not only with noise, but also with minor noise or even without noise.
+Figure \ref{fig:noise-intensity} shows the noise effect on different $ \mu $.
 %% add noise image
@@
 	\decoRule	
-	\caption{Noise-intensity on 0, 10, 20, 30, 40, 50. Object Name: elephant-zun-lid.}
+	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
 	\label{fig:noise-intensity}
@@
 		\toprule
-		\tabhead{Name} & \tabhead{Description} \\
+		\tabhead{Name} & \tabhead{Content} \\
 		\midrule
@@
 		\hline
-		\multirow{4}{*}{output-tensor}  & GT-Normal  \\ & GT-Normal * GT-Light-Direction \\ & Image \\ & GT-Light-Direction \\
+		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
 		\hline
@@
 		\hline 
-		\multirow{3}{*}{Camera Matrix}  & K \\  & R \\  & t \\
+		Camera Matrix  & K,R,t\\
 		\hline 
-		\multirow{2}{*}{Depth Range}  & minDepth \\  & maxDepth \\
-		\hline
+		Depth Range  & minDepth, maxDepth\\
 		\bottomrule\\
@@
 The real dataset is the depth map and rgb image captured via Kinect...
-
-\section{Metrics for evaluation}
-Angle Loss

### 2022-06-22 help_funs/mu.py
add model hfm

@@ -1058,8 +1058,8 @@ def visual_vertex(vertex, name):
     return vertex_8bit
 
 
-def visual_img(img, name, upper_right=None):
-    addText(img, f"{name}", font_size=0.8)
+def visual_img(img, name, upper_right=None, font_scale=0.8):
+    addText(img, f"{name}", font_size=font_scale)
     if upper_right is not None:
         addText(img, f"angle error: {upper_right}", pos="upper_right", font_size=0.65)
     return img

### 2022-06-22 workspace/eval.py

@@ -28,7 +28,7 @@ def eval(dataset_path, name, model_path, gpu=0, data_type="normal_noise"):
     # SVD model
     if model_path is None:
         # load dataset
-        dataset = SyntheticDepthDataset(dataset_path, 0, data_type, setname="val")
+        dataset = SyntheticDepthDataset(dataset_path, 0, data_type, setname="test")
         data_loader = DataLoader(dataset, shuffle=False, batch_size=1, num_workers=1)
         loss_list, time_list, size_list = svd.eval(data_loader, 2)
         return loss_list, time_list, size_list
@@ -48,7 +48,7 @@ def eval(dataset_path, name, model_path, gpu=0, data_type="normal_noise"):
     if dataset_path == config.real_data:
         dataset = SyntheticDepthDataset(dataset_path, 0, data_type, setname=None)
     else:
-        dataset = SyntheticDepthDataset(dataset_path, 0, data_type, setname="val")
+        dataset = SyntheticDepthDataset(dataset_path, 0, data_type, setname="test")
     data_loader = DataLoader(dataset,
                              shuffle=True,
                              batch_size=1,

### 2022-06-22 workspace/hfm/network.py

@@ -1,0 +1,32 @@
+import sys
+from os.path import dirname
+
+sys.path.append(dirname(__file__))
+
+import torch.nn as nn
+from common.HFMNet import fconv_ms, map_conv
+import torch
+import numpy as np
+
+
+class CNN(nn.Module):
+    def __init__(self):
+        super().__init__()
+        self.__name__ = 'hfm'
+
+        # input confidence estimation network
+        self.net3_3 = fconv_ms(input_channel1=1, input_channel2=3, output_channel=3, track_running_static=True)
+        self.conf_net = map_conv(input_channel=4, output_channel=1, track_running_static=True)
+        # self.net3_3 = NormalizedNNN(3, 3, channel_num)
+
+    def forward(self, x0):
+        # x0: vertex array
+        vertex = x0[:, :3, :, :]
+        img = x0[:, 3:4, :, :]
+
+        mask = torch.sum(torch.abs(vertex[:, :3, :, :]), dim=1) > 0
+        conf_net_input = torch.cat((vertex, mask[:, np.newaxis, :, :]), dim=1)
+        vertex_conf = self.conf_net(conf_net_input)
+        output_f, output_f1, output_f2, output_f3, output_d = self.net3_3(img, vertex, vertex_conf)
+
+        return output_f

### 2022-06-23 paper/Chapters/Chapter05.tex
add model hfm
update resng

@@
 \label{ch:05} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
+The experiments are performed on two normal inference tasks: normal inference based on depth image and guided normal inference based on RGB-D image.
+Prior works for normal estimation using very deep networks.
+For a single object surface normal detection as stated in this thesis, the given methods has a similar performance but only with $ 1/10 $ size.
 
@@
 %% nnnn exp
-\section{Gated Convolution Neural Network for Normal Inference}
+\section{Surface Normal Inference based on Depth Map}
+The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $.
+A network named Gated Convolution Neural Network (GCNN) is trained and is compared with similar approaches.
 
-The first neural network that worked well for normal prediction in this master thesis is introduced in this section.
-It is named Gated Convolution Neural Network, or GCNN.
-The GCNN model is nothing but a UNet with gated convolution layers.
-it can predict normal map based on a point cloud.
-The error is around 10 degrees.
+\subsection{Compared Approaches}
 
-The model uses a 512x512x3 3D vertex matrix as input and the output is a 512x512x3 normal map.
-The architecture is based on description in \ref{sec:architecture}.
-The channel size is up to 32 through the whole network.
-For the training parameters, learning rate is 0.001, penalty is 1.4, optimizer is Adam optimizer, the loss function is penalty-l2 loss as described in \ref{sec:loss}.
+\subsection{Training Details}
+The network (see \ref{gcnn}) is trained on stated dataset in Chapter \ref{ch:04}.
+It has two versions, the L-size $ 512\times512\times3 $ and the  S-size $ 128\times128\times3 $.
+For the L-size model, it uses batch size 8 for 3500 iterations.
+For the S-size model, it uses batch size 32 for 6000 iterations.
+Both sizes use Adam optimizer \cite{adam} with a learning rate of $ 1\times10^{-3} $, penalty-l2 loss(see \ref{sec:loss}).
+The output is directly the tangent normal in range $ \left[-1,1\right] $.
+The output and input has the same shape.
 
-The evaluation result on 90 test scenes is shown in Figure \ref{fig:scatter-gcnn}.
-The GCNN based method has angle error between 5 to 15 degrees in both type of inputs.
-The error trends to higher with point number decrease.
-It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution.
-Therefore the recorded surface based on the point cloud is more coarse, which also increase the difficulty of the normal inference.
+\subsection{Qualitative Evaluation}
 
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-no-noise.png}
-	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-noised.png}
-	\caption{Evaluation of average angular loss on the whole test dataset with 90 scenes.
-The x-axis indicates the point number, the y-axis indicates the angles.
-The \textbf{Left} one using point cloud without noise, the \textbf{right} one has noise.}
-	\label{fig:scatter-gcnn}
-\end{figure}
+The evaluation visualization on dataset ``synthetic50-5" (see \ref{ch:04}) dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}.
+It compares the results with method xxx, for both smooth and highly detailed cases.
+In all the cases, the angle errors are very close.
+The test-cases are based on test point cloud in ``synthetic50-5".
 
-The evaluation visualization on synthetic dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}.
-The error concentrate mainly on severe changed surface region, like the teeth, paw and horn of the dragon.
+The model is supposed to used on any image size since it has no fully-connected layers (dense layers). Two size of models are based on exactly the same architecture.
+
+%% a detailed analyis of this figure
+It is
+
 \begin{figure}[h!]
@@
 \end{figure}
+
+\subsection{Quantitative Evaluation }
+
+The evaluation result on test scenes is shown in Figure \ref{fig:scatter-gcnn}.
+The GCNN based method has angle error between 5 to 15 degrees in both type of inputs.
+The error trends to higher with point number decrease.
+It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution.
+Therefore the recorded surface based on the point cloud is more coarse, which also increase the difficulty of the normal inference.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-no-noise.png}
+	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-noised.png}
+	\caption{Evaluation of average angular loss on the whole test dataset with 90 scenes.
+The x-axis indicates the point number, the y-axis indicates the angles.
+The \textbf{Left} one using point cloud without noise, the \textbf{right} one has noise.}
+	\label{fig:scatter-gcnn}
+\end{figure}
+
+\subsection{Speed}
 

### 2022-06-26 paper/Chapters/Chapter01.tex
fix bugs in training evaluation
update ag model

@@
 
-%----------------------------------------------------------------------------------------
-%	SECTION 1
-%----------------------------------------------------------------------------------------
-
-\section{From 3D to 2D}
-
-\section{Kinect and Surface Normal}
-
-As a popular and affordable new type of depth sensor, Kinect, had attracted a great focus to computer vision research in the last decades.
-It simultaneously captured the grayscale or RGB image and depth map with a high resolution.
-The depth map can further convert to structured point clouds with known intrinsic calibration parameters, which can use in many applications.
-
-%% why surface normal is important
-Surface Normal is one of the most worthy pieces of information that can infer from point clouds, which applies in many practical applications, such as augmented reality and robotics.
-Some tasks like shading and surface reconstruction require normal as one of the inputs.
-However, due to the lack of accuracy of the sensors, the  surface normal inference from depth maps/point clouds has many challenges.
-
-%-----------------------------------
-%	SUBSECTION 1
-%-----------------------------------
-\section{Standard Methods}
-
-%%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%
-
-%% standard method for normal inference is insufficient, input is sparse, not robust enough
-Standard methods compute normals from the point cloud using neighboring information in image space or from a single grayscale image using use Shape from Shading \cite{SFS}.
-The first method assumes that the neighbors of the points locate on the same plane.
-This method performs well with a well-chosen window size.
-However, the drawbacks are that the algorithm is highly noise sensitive.
-It is weak in handling missing pixels, which is a common issue in the input data.
-The second method depends on the correct information about the light source.
-Errors may occur in regions with inter-reflections in the 3D measurement.
-
-%-----------------------------------
-%	SUBSECTION 2
-%-----------------------------------
-
-\section{Deep Learning based Method}
-%% CNN based methods
-Recently, deep learning based method \cite{yolov3}, \cite{efficientDet} achieved a great succeed for image processing. 
-These network architectures use a batch of RGB/Grayscale images as input and usually employ for classification problems.
-Usually, the images are convoluted with a convolutional layer and downsampling with pooling layers.
-The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.
-
-However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
-Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
-In this case, the traditional network architecture is not suitable anymore.
-
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-
-\section{Challenges of Normal Inference}
-
-%% talk about upsampling 
+Surface normal is an important property of a surface with many applications, like surface reconstruction, shadings generation and other visual effects.
+The quality of the surface normal is directly impact the performances of the techniques mentioned above.
+However, especially in the task of real-world object digitalization, the surface is usually hardly to be mathematically described in equations due to the elaborate details on the objects.
+Instead, it is common to use a group of points to describe the object surface, which is a memory economical solution and also can be easier measured by 3D scanners.
+The working principle of scanners are various due to the application scenarios, which consequently produce different point cloud structure.
+For the scanners without positions recording, the point cloud acquired after scanning is unstructured.
+In this case, every 3D point can be captured by different capture position, and neighbors are not defined by capture time, which increase the difficulty and computation for the neighbor based normal inference approaches.
+Furthermore, since the lack of inherent structure, the normal can hardly be inferred by the parallel approaches.
+To acquire the structured point cloud, a depth camera can be used for data collection.
+It captures the RGB-D images for the object, which includes the standard RGB image with depth information of each pixel.
+After camera calibration, the corresponding point cloud can be calculated based on the depth map and camera matrix.
+The advantages are, a structured point cloud is mapped directly based on the same capture position from a 2D depth map, the neighbor information of each point is identical to the corresponding pixel in the 2D depth map, which reduced a huge computational works.
+Besides, base on the RGB image, which has the same indices with depth map, the normal inference task can also utilize the relationship between surface normal and light reflection to further rectify the inferred normal map with knowing light source.
+Furthermore, the structured point cloud has the same shape with the standard RGB images, which can be used for deep learning based approaches.
+Unfortunately, the depth maps captured by the sensors are only semi-dense, which is mainly caused by optical noises and the reflections in dark and shinny areas.
+Consequently, it raises the challenges to the accuracy of normal inference tasks.
 Recently, deep learning-based methods are used in computer vision tasks such as image segmentation, image inpainting, and depth density enhancement.
-In these methods, multiple architectures have proposed with an upsampling section.
-In this case, the output can be designed to have the same shape as the input or slightly smaller.
-Nevertheless, the resolution is similar to the input image.
-The normal Inference task has a similar pipeline compared to these tasks.
-
-%% there exists space for improvement 
-On the other hand, the point cloud data provided by Kinect or similar RGB-D, and LiDAR sensors are only semi-dense.
-A huge amount of missing pixels distribute all over the images, and some of the regions leave complete empty holes.
-This situation imposes another challenge on normal inference.
-
-The depth image is incomplete, however, the depth sensor is able to capture grayscale texture images, which are typically fully dense due to their passive nature.
-Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, and grayscale image.
+The output of the model is usually has the same shape as the input but with different content, which is by comparison similar to the normal inference task.
+The deep learning based method has many advantages, first, it deals well with semi-dense input, which is a common issue for the depth map.
+Second, the network of deep learning model handles the structured point cloud as a single input and infer the corresponding normal all together, which is very time economical comparing to the approaches like neighbor based methods.
+Furthermore, if the texture image acquiring from the camera is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations among light direction, normal direction, and grayscale image.
 Then the normal can be inferred better using the given image information and depth map.
-Based on the grayscale image and corresponding semi-dense depth maps, a CNN model can be designed to infer the normal map, which can give more density and robust results comparing to the standard algorithm.
-
-%% add noise image
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.4\textwidth]{Figures/kinect-depth.png}
-	\decoRule
-	\caption{A captured depth map via infrared sensors. Pixels that far away represent by light colors, otherwise by dark colors. The black dots are the depths that failed to be detected.}
-\label{fig:depth-map-with-noise}
-\end{figure}
-
-%% add noise image
-
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.4\textwidth]{Figures/real-normal.png}
-	\decoRule
-	\caption{Semi-dense Normal Map calculated from depth map using a standard method}
-\label{fig:standard-normal-inference}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%% talk about the main work in this thesis  %%%%%%%%%%%%%%%%%%
-\section{Main Works of this thesis}
-In this thesis, we found a solution for the problems mentioned above and proposed a novel deep learning architecture for surface normal inference.
-A network named Albedo Gated Normal Inference Network(AlGaN) is proposed to infer normal given the corresponding depth map.
-The architecture of AlGaN involves a two-stage CNN.
-The first stage infers the normal map using point cloud as input.
-If the light source position and grayscale image can be provided further, the second stage infers the albedo altogether with the normals from the first stage.
-In addition, the loss function is based on least-square error and Lambertian reflection.
-
-With the help of synthetic data in Unity, a dataset is created for CNN model training.
+Based on the grayscale image and corresponding semi-dense depth maps, a multi-staged model can be designed to infer the normal map, which can give more density and robust results comparing to the standard algorithm.
+In this work, we apply the deep learning based approach for surface normal inference, which is based on the calibrated illuminated RGB-D image.
+A network named gated convolution neural network (GCNN) is proposed for normal inference, which is robust to the semi-dense input.
+With the help of synthetic data in Unity, a dataset is also created for CNN model training.
 It can provide accurate ground truth for training work, which real data is usually not provided.
-The results of this dataset show that our AlGaN model performs also well on real data captured by Infrared cameras.
-The trained Normal models achieve a remarkably better prediction accuracy at a low computational cost compared to the standard approaches for semi-dense point clouds.
+The trained model is performed well both in synthetic dataset as well as the real dataset captured from RGB-D cameras and achieve a remarkably better prediction accuracy at a low computational cost compared to the standard approaches for semi-dense point clouds.
+The structure of the thesis is as follows, Chapter 1 is the introduction of the whole work.
+Chapter 2 briefly discusses the related work about normal inference.
+Chapter 3 is the main approaches of this work.
+Chapter 4 introduces the created dataset for the training work.
+Chapter 5 is the description of the experiments and the evaluation of the models.
+Chapter 6 is the conclusion of the whole thesis.

### 2022-06-26 paper/Chapters/Chapter02.tex
update ag model

@@
 %	SECTION 1
+%----------------------------------------------------------------------------------------
+%-----------------------------------
+%	SUBSECTION 1
+%-----------------------------------
+\section{Standard Methods}
+
+%%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%
+
+%% standard method for normal inference is insufficient, input is sparse, not robust enough
+Standard methods compute normals from the point cloud using neighboring information in image space or from a single grayscale image using use Shape from Shading \cite{SFS}.
+The first method assumes that the neighbors of the points locate on the same plane.
+This method performs well with a well-chosen window size.
+However, the drawbacks are that the algorithm is highly noise sensitive.
+It is weak in handling missing pixels, which is a common issue in the input data.
+The second method depends on the correct information about the light source.
+Errors may occur in regions with inter-reflections in the 3D measurement.
+
+%-----------------------------------
+%	SUBSECTION 2
+%-----------------------------------
+
+\section{Deep Learning based Method}
+%% CNN based methods
+Recently, deep learning based method \cite{yolov3}, \cite{efficientDet} achieved a great succeed for image processing. 
+These network architectures use a batch of RGB/Grayscale images as input and usually employ for classification problems.
+Usually, the images are convoluted with a convolutional layer and downsampling with pooling layers.
+The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.
+
+However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
+Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
+In this case, the traditional network architecture is not suitable anymore.
+
+%----------------------------------------------------------------------------------------
+%	SECTION 2
 %----------------------------------------------------------------------------------------

### 2022-06-26 workspace/train.py

@@ -16,7 +16,6 @@ import matplotlib.pyplot as plt
 import numpy as np
 import torch
 import torch.nn.functional as F
-import torchvision
 from torch import nn
 from torch.optim import SGD, Adam, lr_scheduler
 from torch.utils.data import DataLoader
@@ -96,7 +95,7 @@ class WeightedL2Loss(nn.Module):
         return F.mse_loss(outputs, target)
 
 
-class AngleLoss(nn.Module):
+class NormalL2Loss(nn.Module):
     def __init__(self):
         super().__init__()
 
@@ -120,6 +119,18 @@ class AngleLoss(nn.Module):
         # print(f"\t axis: {axis}\t axis_loss: {loss:.5f}")
 
         return loss  # +  F.mse_loss(outputs, target)  # + angle_loss.mul(args.angle_loss_weight)
+
+
+class GL2Loss(nn.Module):
+    def __init__(self):
+        super().__init__()
+
+    def forward(self, outputs, target, args):
+        mask = torch.abs(target) > 0
+        G_diff = (outputs - target)[mask]
+        loss = torch.sum(G_diff ** 2) / G_diff.size(0)
+
+        return loss
 
 
 class AngleHistoLoss(nn.Module):
@@ -171,14 +182,15 @@ class AngleHistoLoss(nn.Module):
 class AngleLightLoss(nn.Module):
     def __init__(self):
         super().__init__()
+        self.normal_loss = NormalL2Loss()
+        self.g_loss = GL2Loss()
 
     def forward(self, outputs, target, args):
-        mask = torch.sum(torch.abs(target[:, :3, :, :]), dim=1) > 0
+        normal_loss = self.normal_loss(outputs[:, :3, :, :], target[:, :3, :, :], args)
+        G = torch.sum(outputs[:, :3, :, :] * target[:, 5:8, :, :], dim=1)  # N * L
+        g_loss = self.g_loss(G, target[:, 3, :, :], args)
 
-        N_diff = (outputs[:, :3, :, :] - target[:, :3, :, :]).permute(0, 2, 3, 1)[mask]
-        l_diff = (outputs[:, 3:6, :, :] - target[:, 5:8, :, :]).permute(0, 2, 3, 1)[mask]
-        loss = torch.sum(N_diff ** 2) / N_diff.size(0)
-        loss += torch.sum(l_diff ** 2) / l_diff.size(0)
[…]

### 2022-06-27 paper/Chapters/Chapter01.tex
update fugrc, 5 times downsampling

@@
 Surface normal is an important property of a surface with many applications, like surface reconstruction, shadings generation and other visual effects.
-The quality of the surface normal is directly impact the performances of the techniques mentioned above.
-However, especially in the task of real-world object digitalization, the surface is usually hardly to be mathematically described in equations due to the elaborate details on the objects.
-Instead, it is common to use a group of points to describe the object surface, which is a memory economical solution and also can be easier measured by 3D scanners.
-The working principle of scanners are various due to the application scenarios, which consequently produce different point cloud structure.
+However, the calculation of surface normal in many tasks is not as straightforward as simply the cross-product of two plane vectors.
+Especially in the task of real-world object digitalization, the surface is usually hardly to be mathematically described in equations due to the elaborate details on the objects.
+Instead, it is common to use a group of points to describe the object surface, which is a memory economical solution to save the fine detail of the objects and also can be easier measured by 3D scanners.
+Therefore the task is converted to the normal inference based on the surface point, and the most of the case, the result surface normal is merely an approximation.
+
+\begin{figure}[h!]
+	\centering
+	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud.png}};
+	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud-zoom-in.png}};
+	\caption{Left: A part of the point cloud of the dragon model. Right: The zoom in of the left point cloud.}
+	\label{fig:point-cloud}
+\end{figure}
+
+Apart from this, due to the application scenarios, the working principle of scanners are various, which consequently produce point cloud structures in different forms.
 For the scanners without positions recording, the point cloud acquired after scanning is unstructured.
-In this case, every 3D point can be captured by different capture position, and neighbors are not defined by capture time, which increase the difficulty and computation for the neighbor based normal inference approaches.
+In this case, every 3D point can be captured by different capture position, and neighbors are not defined by capture time.
+It increases the difficulty and computation for the neighbor based normal inference approaches.
 Furthermore, since the lack of inherent structure, the normal can hardly be inferred by the parallel approaches.
-To acquire the structured point cloud, a depth camera can be used for data collection.
+
+However, for the scanner with calibrated camera, a structured point cloud can be captured.
+One example is the depth camera.
 It captures the RGB-D images for the object, which includes the standard RGB image with depth information of each pixel.
-After camera calibration, the corresponding point cloud can be calculated based on the depth map and camera matrix.
-The advantages are, a structured point cloud is mapped directly based on the same capture position from a 2D depth map, the neighbor information of each point is identical to the corresponding pixel in the 2D depth map, which reduced a huge computational works.
-Besides, base on the RGB image, which has the same indices with depth map, the normal inference task can also utilize the relationship between surface normal and light reflection to further rectify the inferred normal map with knowing light source.
-Furthermore, the structured point cloud has the same shape with the standard RGB images, which can be used for deep learning based approaches.
-Unfortunately, the depth maps captured by the sensors are only semi-dense, which is mainly caused by optical noises and the reflections in dark and shinny areas.
-Consequently, it raises the challenges to the accuracy of normal inference tasks.
-Recently, deep learning-based methods are used in computer vision tasks such as image segmentation, image inpainting, and depth density enhancement.
-The output of the model is usually has the same shape as the input but with different content, which is by comparison similar to the normal inference task.
-The deep learning based method has many advantages, first, it deals well with semi-dense input, which is a common issue for the depth map.
-Second, the network of deep learning model handles the structured point cloud as a single input and infer the corresponding normal all together, which is very time economical comparing to the approaches like neighbor based methods.
-Furthermore, if the texture image acquiring from the camera is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations among light direction, normal direction, and grayscale image.
-Then the normal can be inferred better using the given image information and depth map.
-Based on the grayscale image and corresponding semi-dense depth maps, a multi-staged model can be designed to infer the normal map, which can give more density and robust results comparing to the standard algorithm.
-In this work, we apply the deep learning based approach for surface normal inference, which is based on the calibrated illuminated RGB-D image.
-A network named gated convolution neural network (GCNN) is proposed for normal inference, which is robust to the semi-dense input.
-With the help of synthetic data in Unity, a dataset is also created for CNN model training.
-It can provide accurate ground truth for training work, which real data is usually not provided.
-The trained model is performed well both in synthetic dataset as well as the real dataset captured from RGB-D cameras and achieve a remarkably better prediction accuracy at a low computational cost compared to the standard approaches for semi-dense point clouds.
+After camera calibration, a corresponding point cloud can be calculated based on the depth map and camera matrix.
+It gives the advantage that a structured point cloud is mapped directly based on the same capture position from a 2D depth map, the neighbor information of each point is identical to the corresponding pixel in the 2D depth map.
+It provides a better view for the normal inference task since the neighbor information can be considered as an important reference.
+Besides the point cloud, which is one piece of information can be used for normal reference, the RGB image also leaves the trace of surface normal.
+If assume object surface is diffuse and the light coming from a knowing direction , the brightness of the object surface is proportional to the surface normal, which is known as Lambertian surface.
+It indicates the normal inference task can also utilize the relationship between surface normal and light reflection to further rectify the inferred normal map with knowing light source.
+Therefore, the illuminated calibrated RGB-D image provides as a good input for normal inference tasks.
+Unfortunately, in the actual situation, the depth maps captured by the sensors are only semi-dense, which is mainly caused by optical noises and the reflections in dark and shinny areas.
+Consequently, it disrupts the robustness of the normal inference methods.
+Median filters can be used for the sparse missing pixels, however, for the case of huge missing holes in the depth map, it produces just a paltry result.
+Thus a reasonable guess is required for missing areas.
+
+Deep learning based methods provides multiple possible solutions for the challenges mentioned above.
+First, to deal with the noised input, deep learning based methods already have the solution for the similar tasks like image inpainting and depth density enhancement, which base on the noised image as input to predict the clean and fully dense output with or without original meanings.
+Therefore, it can be a help for noise in the depth map.
+Besides, the network of deep learning model can also handle the structured point cloud as a single input and infer the corresponding normal all together, which is very time economical comparing to the approaches like neighbor based methods.
+In addition, the multi-stages training architectures provide a way to consider both depth map and texture image as the input to predict the surface normals, which not only consider the point cloud but also the add the lambertian reflection as a further constraint.
+
+In this work, we focus on the normal inference based on a semi-dense depth map with RGB image using deep learning based approaches.
+Specifically, the missing pixels in the depth map is filled up by the gated convolution and propagate in a customized UNet with skipping connections.
+The output of the training model is directly the surface normal corresponding the input depth map.
+The grayscale image is used to further improve the estimation accuracy.
+For the training work, a dataset named “synthetic50-5” is created including 55 high resolution point clouds from internet, as shown in Appendix A.
+The point clouds provide with the high accurate normals, which can be used as the ground truth of the training work.
+Most of the models have elaborate details with high curvatures but also contain smooth surfaces.
+The trained model is evaluated on both synthetic dataset as well as the real dataset captured from RGB-D cameras.
+A series of metrics have been used for qualitative evaluation.
+The model is shown to achieve a remarkably better prediction accuracy at a low computational cost compared to the standard approaches for semi-dense point clouds.
+
 The structure of the thesis is as follows, Chapter 1 is the introduction of the whole work.

### 2022-06-27 paper/Chapters/Chapter02.tex
update fugrc, 5 times downsampling

@@
 
-%----------------------------------------------------------------------------------------
-%	SECTION 1
-%----------------------------------------------------------------------------------------
-%-----------------------------------
-%	SUBSECTION 1
-%-----------------------------------
+Guided method \cite{guided} requires addition information like RGB image for the inference.
+
+%% denoising
+The depth map captured by depth sensors are usually with full of missing pixels and holes.
+\cite{depth-inpainting-distribution} proposed a depth hole filling method using the depth distributions of neighboring regions.
+
+\cite{nconv} introduced normalized convolution dealing with missing or uncertain data for convolution operation.
+It uses a binary mask to distinguish missing data and integrate it into the convolution operation.
+\cite{ncnn} applied it and use normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
+\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
+However, the relevant papers are only using 1 channel data as model input, which didn't discussed the case for the multiple-channel data as input.
+
+\cite{gated_activation} proposed a gated activation unit to model more complex interactions comparing to standard CNN layers, which mainly inspired by the multiplicative units exist in Long Short-Term Memory proposed by \cite{lstm} and Rated Recurrent Unit (GRU) proposed by \cite{gru}.
+\cite{gconv} employed the same gated unit solving for the free-form image inpainting task. The proposed network use 3 channel RGB images as input and estimate the missing pixels.
+
+%% method for structured point cloud
+
+%% CNN based methods
+
+estimate the surface normal based on improve the performance of image processing to a brand new stage. 
+In 2014, Eigen et al.\cite{Eigen} proposed a method predicting depth map directly from RGB image using CNN.
+In this case, no depth map is required.
+In 2016, Laina et al.
+\cite{img2depth} proposed a deeper network based on ResNet \cite{resnet} with a well designed upsamling part.
+%% guided scene completion
+
+\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
+
+\cite{GeoNet} uses ResNet proposed by \cite{resnet} to infer the surface normal from RGB image, and further refine it with the help of depth map based on the methods proposed by \cite{geometry_based_solution}  further refine the a  GeoNet to infer depth and surface normal in one unified system,  method proposed by \cite{img2depth}.
+
+%% upsampling 
+It is worth to noticed that, the output of normal inference CNN model is not one or severl labels but an entire image or normal map with same size. 
+%% talk about image upsampling, unet
+Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations.
+The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size.
+The proposed network can successfully assigned each pixel a class for segmentation tasks.
+Under this symmetric network, an input image is downsampled 3 times and upsampled 3 times.
+Output image has exactly the same size as input image.
+The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.
+
+%% unstructured point cloud
+For the unstructured point cloud, the neighbor information of each point is usually unknown.
+K-nearest neighbor is a common algorithm for neighbor searching.
+With knowing this information, the neighbor based approaches can be used as a second step.
+However, KNN-method merely based on the Euclidean distance in the 3D space.
+Therefore, the points of the other surfaces but in a close distance will also be considered as neighbors.
+\cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation.
+\cite{unstructed-pc-patch-stitching} presents a pipeline for calculating the normals of multiple points in parallel.
+
 \section{Standard Methods}
 
-%%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%
-
-%% standard method for normal inference is insufficient, input is sparse, not robust enough
 Standard methods compute normals from the point cloud using neighboring information in image space or from a single grayscale image using use Shape from Shading \cite{SFS}.
@@
 %% CNN based methods
-Recently, deep learning based method \cite{yolov3}, \cite{efficientDet} achieved a great succeed for image processing. 
-These network architectures use a batch of RGB/Grayscale images as input and usually employ for classification problems.
-Usually, the images are convoluted with a convolutional layer and downsampling with pooling layers.
+
+Recently, deep learning based method achieved a great succeed for image processing.
+\cite{yolov3} proposed  \cite{efficientDet} These network architectures use a batch of RGB/Grayscale images as input and are employed for classification problems.
+Usually, the images are convoluted with a convolution layer and downsampling with pooling layers.
 The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.
-
 However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
@@
 
-%----------------------------------------------------------------------------------------
-%	SECTION 2
-%----------------------------------------------------------------------------------------
-
 From PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last several decades.
-
-\section{Sparse Input processing}
-
-%% methods deal with sparse input, like nconv, gconv ...
-The depth map is supposed to be dense.
-Therefore, how to accept sparse depth map as input in CNNs is one of the most important problem.
-Some trivial solutions like median filters are good enough, if the missing pixels are sparse enough, however, for the case of huge missing holes in the depth map, it produces just a paltry result.
-Thus a reasonable guess is required for missing areas.
-Generally, it can be solved as image inpainting problems,\cite{inpainting1},\cite{inpainting2}.
-
-%% Deep learning based approaches
-Some deep learning based method for image inpainting also achieved quite good performance for the hole mending task. 
-%% talk about gconv
-Notably, in 2016, Oord et al. \cite{gated_activation} proposed a gated activation unit for a CNN model,
-\[\textbf{y} = \tanh (W_{k,f} * \textbf{x}) \odot \sigma (W_{k,g} * \textbf{x})\]
-to substitute the standard activation layer, where $ \sigma $ is the sigmoid function, which constricts the output value of second part between $ [0,1] $.
-The function is inspired by Long Short-Term Memory (LSTM) \cite{lstm} and Rated Recurrent Unit (GRU).\cite{gru} It is originally used for learning complex interactions as LSTM gates does.
-In 2018, Yu et al.
-\cite{gconv} employed same function for free-form image inpainting, which can be used to learn mask automatically from image it self.
-
-%% talk about nconv
-Different to aforementioned approaches, Knutsson et al.
-in 2005 introduced normalized convolution \cite{nconv} dealing with missing sample case for convolution operation, which aims to reconstruct the missing pixels from the sparse output sensed by cameras, which particularly considered the confidence of each interpolated pixels, since it provides the trustworthiness of the predicted value.
-The higher the reliability of the value inference, the better the model shape reconstruction.
-
-In 2018, Eldesokey et al.
-\cite{ncnn} applied normalized convolution in CNN as normalized convolution layer that takes both sparse depth map and a binary confidence map as input to perform scene depth completion.
-In 2020, Eldesokey et al. \cite{pncnn} focus on modeling the uncertainty of depth data instead of assuming binary input confidence.
-
-Guided method \cite{guided} requires addition information like RGB image or the certainty map of depth map, and fuse them together to predict the dense depth map.
 
@@
 by algebra methods. Similarly, this approach gives a quick but coarse normal inference.
-
-%% CNN based methods
-Recently, CNN based methods improve the performance of image processing to a brand new stage.
-In 2014, Eigen et al.\cite{Eigen} proposed a method predicting depth map directly from RGB image using CNN.
-In this case, no depth map is required.
-In 2016, Laina et al.
-\cite{img2depth} proposed a deeper network based on ResNet \cite{resnet} with a well designed upsamling part.
-%% guided scene completion
-In 2018, Qi et al. proposed GeoNet\cite{GeoNet}, it integrates both algebra method and also CNN method to inference depthmap based on \cite{img2depth} \cite{geometry_based_solution}.
-
-%% upsampling 
-It is worth to noticed that, the output of normal inference CNN model is not one or severl labels but an entire image or normal map with same size. 
-%% talk about image upsampling, unet
-Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations.
-The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size.
-The proposed network can successfully assigned each pixel a class for segmentation tasks.
-Under this symmetric network, an input image is downsampled 3 times and upsampled 3 times.
-Output image has exactly the same size as input image.
-The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.
-
-%%\begin{figure}[!h]
-%%	\centering
-%%	\includegraphics[width=\textwidth]{./ref/u-net-illustration-correct-scale2}
-%%	\caption{U-net architecture (example for 32x32 pixels in the lowest resolution).
-Each blue box corresponds to a multi-channel feature map.
-The number of channels is denoted on top of the box.
-The x-y-size is provided at the lower left edge of the box.
-White boxes represent copied feature maps.
-The arrows denote the different operations.
-	%%	}
-%%	\label{fig:u-net}
-%% \end{figure}
-
-%% unstructured point cloud 
-In some case, the input is unstructured point cloud which can not be fed into a CNN entirely.
-Thus, a challenge task connect to the deep learning is the input format.
-Since different point clouds have different sizes.
-In 2018, Ben-Shabat et al.
-\cite{Ben-Shabat_2019_CVPR} presented Nesti-Net.
-It predicts the normal point by point with the help of neighbor points.
-It fixed the distance of considering neighbors to provide an unified input for CNN.
-In 2021, Zhou et al.
-\cite{zhou2021fast} presents a method considering overlapping of different patches (a group of neighboring points) as input to evaluate normals.

### 2022-06-28 paper/Chapters/Chapter02.tex
update dataset synthetic256

@@
 
-Guided method \cite{guided} requires addition information like RGB image for the inference.
+\section{Deep Learning based Method}
+%% CNN based methods
 
+Recently, deep learning based method achieved a great succeed for image processing.
+\cite{yolov3} proposed  \cite{efficientDet} These network architectures use a batch of RGB/Grayscale images as input and are employed for classification problems.
+Usually, the images are convoluted with a convolution layer and downsampling with pooling layers.
+The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.
+However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
+Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
+In this case, the traditional network architecture is not suitable anymore.
+
+From PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last several decades.
+
+\section{Noise Handling}
 %% denoising
@@
 
+%% normal estimation method introduction
+\section{Surface normal inference}
+\textbf{RGB based}  
+\cite{Eigen} predicted depth map directly from RGB image. 
+\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
+\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.
+
+\textbf{Point Cloud Based} 
+\cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix.
+They also smooth the depth data in order to handle the noise of depth image.
+The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.
+
+\textbf{RGB-D based}
+Guided method \cite{guided} requires addition information like RGB image for the inference.
+
 %% method for structured point cloud
-
-%% CNN based methods
-
-estimate the surface normal based on improve the performance of image processing to a brand new stage. 
-In 2014, Eigen et al.\cite{Eigen} proposed a method predicting depth map directly from RGB image using CNN.
-In this case, no depth map is required.
-In 2016, Laina et al.
-\cite{img2depth} proposed a deeper network based on ResNet \cite{resnet} with a well designed upsamling part.
-%% guided scene completion
-
-\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
-
-\cite{GeoNet} uses ResNet proposed by \cite{resnet} to infer the surface normal from RGB image, and further refine it with the help of depth map based on the methods proposed by \cite{geometry_based_solution}  further refine the a  GeoNet to infer depth and surface normal in one unified system,  method proposed by \cite{img2depth}.
+%% image based
 
@@
 Errors may occur in regions with inter-reflections in the 3D measurement.
-
-%-----------------------------------
-%	SUBSECTION 2
-%-----------------------------------
-
-\section{Deep Learning based Method}
-%% CNN based methods
-
-Recently, deep learning based method achieved a great succeed for image processing.
-\cite{yolov3} proposed  \cite{efficientDet} These network architectures use a batch of RGB/Grayscale images as input and are employed for classification problems.
-Usually, the images are convoluted with a convolution layer and downsampling with pooling layers.
-The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.
-However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
-Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
-In this case, the traditional network architecture is not suitable anymore.
-
-From PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last several decades.
-
-\section{Normal Inference}
-
-%% normal estimation method introduction
-Usually, we based on point cloud, depth map or RGB/Grayscale image of the objects or scenes to inference the normals.
-
-Traditional methods evaluate normals based on neighbor information of point cloud or depth map.
-In 2012, Holzer et al. \cite{Holzer.S} proposed method to calculate normal from covariance matrices. 
-This method use integral image as input, which is able to run algorithm in a high frame speed.
-They smooth the depth data in order to handle the noise of depth image.
-The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.
-In 2013, Fouhey et al.
-\cite{geometry_based_solution} proposed a method constructing a over-determined function systems to predict normals and solving it
-by algebra methods. Similarly, this approach gives a quick but coarse normal inference.

### 2022-06-28 paper/Chapters/Chapter02.tex
fix a bug

@@
 \label{ch:02} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
-
-\section{Deep Learning based Method}
-%% CNN based methods
 
@@
 In this case, the traditional network architecture is not suitable anymore.
-
-From PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last several decades.
 
@@
 \textbf{RGB based}
+
+or from a single grayscale image using use Shape from Shading \cite{SFS}.
+The second method depends on the correct information about the light source.
+Errors may occur in regions with inter-reflections in the 3D measurement.
+
 \cite{Eigen} predicted depth map directly from RGB image. 
@@
 \textbf{Point Cloud Based} 
+The relevant methods derive the surface normals based on spatial relationship, which utilizes the neighbor information for estimation.
+These methods performs well with a well-chosen window size.
+However, the drawbacks are that the algorithm is highly noise sensitive.
+It is weak in handling missing pixels, which is a common issue in the input data.
+The earlier methods usually use optimized methods.
 \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix.
@@
 The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.
+\cite{optimized-methods} did a comparison among the optimization-based methods.
+
+\textbf{Unstructured point cloud}
+For the unstructured point cloud, the neighbor information of each point is usually unknown.
+K-nearest neighbor is a common algorithm for neighbor searching.
+With knowing this information, the neighbor based approaches can be used as a second step.
+However, KNN-method merely based on the Euclidean distance in the 3D space.
+Therefore, the points of the other surfaces but in a close distance will also be considered as neighbors.
+\cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation.
+\cite{unstructed-pc-patch-stitching} presents a pipeline for calculating the normals of multiple points in parallel.
 
 \textbf{RGB-D based}
-Guided method \cite{guided} requires addition information like RGB image for the inference.
-
-%% method for structured point cloud
-%% image based
 
@@
 The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.
-
-%% unstructured point cloud
-For the unstructured point cloud, the neighbor information of each point is usually unknown.
-K-nearest neighbor is a common algorithm for neighbor searching.
-With knowing this information, the neighbor based approaches can be used as a second step.
-However, KNN-method merely based on the Euclidean distance in the 3D space.
-Therefore, the points of the other surfaces but in a close distance will also be considered as neighbors.
-\cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation.
-\cite{unstructed-pc-patch-stitching} presents a pipeline for calculating the normals of multiple points in parallel.
-
-\section{Standard Methods}
-
-Standard methods compute normals from the point cloud using neighboring information in image space or from a single grayscale image using use Shape from Shading \cite{SFS}.
-The first method assumes that the neighbors of the points locate on the same plane.
-This method performs well with a well-chosen window size.
-However, the drawbacks are that the algorithm is highly noise sensitive.
-It is weak in handling missing pixels, which is a common issue in the input data.
-The second method depends on the correct information about the light source.
-Errors may occur in regions with inter-reflections in the 3D measurement.

### 2022-06-28 paper/Chapters/Chapter02.tex
update ng

@@
 
-Recently, deep learning based method achieved a great succeed for image processing.
-\cite{yolov3} proposed  \cite{efficientDet} These network architectures use a batch of RGB/Grayscale images as input and are employed for classification problems.
-Usually, the images are convoluted with a convolution layer and downsampling with pooling layers.
-The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.
-However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
-Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
-In this case, the traditional network architecture is not suitable anymore.
+Due to the different of data structures, the point clouds can be grouped into types, structured point cloud based and unstructured point cloud based.
+The first case contains the neighbor information of each point together with a depth map or RGB image, the second case does not contain any neighbor information which has to be further calculated.
 
-\section{Noise Handling}
-%% denoising
-The depth map captured by depth sensors are usually with full of missing pixels and holes.
-\cite{depth-inpainting-distribution} proposed a depth hole filling method using the depth distributions of neighboring regions.
-
-\cite{nconv} introduced normalized convolution dealing with missing or uncertain data for convolution operation.
-It uses a binary mask to distinguish missing data and integrate it into the convolution operation.
-\cite{ncnn} applied it and use normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
-\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
-However, the relevant papers are only using 1 channel data as model input, which didn't discussed the case for the multiple-channel data as input.
-
-\cite{gated_activation} proposed a gated activation unit to model more complex interactions comparing to standard CNN layers, which mainly inspired by the multiplicative units exist in Long Short-Term Memory proposed by \cite{lstm} and Rated Recurrent Unit (GRU) proposed by \cite{gru}.
-\cite{gconv} employed the same gated unit solving for the free-form image inpainting task. The proposed network use 3 channel RGB images as input and estimate the missing pixels.
-
-%% normal estimation method introduction
-\section{Surface normal inference}
-\textbf{RGB based}
-
-or from a single grayscale image using use Shape from Shading \cite{SFS}.
-The second method depends on the correct information about the light source.
-Errors may occur in regions with inter-reflections in the 3D measurement.
-
-\cite{Eigen} predicted depth map directly from RGB image. 
-\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
-\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.
-
-\textbf{Point Cloud Based} 
+\paragraph{ Structured Point Cloud Based}
 The relevant methods derive the surface normals based on spatial relationship, which utilizes the neighbor information for estimation.
@@
 
-\textbf{Unstructured point cloud}
+\paragraph{Unstructured Point Cloud Based}
 For the unstructured point cloud, the neighbor information of each point is usually unknown.
-K-nearest neighbor is a common algorithm for neighbor searching.
+K-nearest neighbor (KNN) is a common algorithm for neighbor searching.
 With knowing this information, the neighbor based approaches can be used as a second step.
@@
 Therefore, the points of the other surfaces but in a close distance will also be considered as neighbors.
-\cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation.
-\cite{unstructed-pc-patch-stitching} presents a pipeline for calculating the normals of multiple points in parallel.
+To ease this problem, \cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation.
+To calculate the normals of multiple points in parallel \cite{unstructed-pc-patch-stitching} processes a series of overlapping patches for normal estimation.
 
-\textbf{RGB-D based}
+Deep learning based methods take single RGB image or RGB-D image as the input for normal estimation.
+It has a strong relationship with the depth inference tasks, two benchmarks are highly used in these area.
+(\cite{nyu} and \cite{kitti-depth}) Based on the input of training model, the methods can be roughly divided as follows:
 
-%% upsampling 
-It is worth to noticed that, the output of normal inference CNN model is not one or severl labels but an entire image or normal map with same size. 
-%% talk about image upsampling, unet
-Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations.
-The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size.
-The proposed network can successfully assigned each pixel a class for segmentation tasks.
-Under this symmetric network, an input image is downsampled 3 times and upsampled 3 times.
-Output image has exactly the same size as input image.
-The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.
+\paragraph{Depth Based}
+Depth map contains the spatial information of the object surface, which is very important for the normal inference task.
+However, the depth map captured by depth sensors are usually with missing pixels and holes on dark, shinny or transparent regions.(\cite{nyu}).
+To overcome the missing pixels,
+\cite{depth-inpainting-distribution} proposed a depth hole filling method using the depth distributions of neighboring regions.
+\cite{nconv} introduced normalized convolution dealing with missing or uncertain data for convolution operation.
+It uses a binary mask to distinguish missing data and integrate it into the convolution operation.
+\cite{ncnn} applied it and use normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
+\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
+However, the relevant papers are only using 1 channel data as model input, which didn't discussed the case for the multiple-channel data as input, such as RGB image, or structured point cloud.
+\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.
+
+\paragraph{RGB based} RGB based methods predict the depth map diretly from single RGB image.
+\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively.
+\cite{img2depth} employed Residual Network for the feature extraction and further designed a upsampling part which replace the fully-connected layer with the unpolling layers.
+\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
+\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.
+\cite{binsformer} proposed a method achieved state of art in NYUv2 Dataset (\cite{nyu}), which adaptively generate information to predict depth maps based on RGB image.
+
+\paragraph{RGB-D based}
+\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input.
+The RGB image and depth map are in the separate branches and imply a fusion module in four sections of the network to concatenate two branches.
+It also considers the confidence of the values in depth map.

### 2022-06-28 eval.py

@@ -89,12 +89,12 @@ if __name__ == '__main__':
         # "fugrc": config.ws_path / "fugrc" / "trained_model" / "128" / "checkpoint-608.pth.tar",
         # "fugrc2": config.ws_path / "fugrc" / "trained_model" / "128" / "checkpoint-1058.pth.tar",
         # loss 13, on training
-        # "SVD": None,
+        "SVD": None,
         # "NNNN": config.ws_path / "nnnn" / "trained_model" / "128" / "checkpoint.pth.tar",  # fast, loss 14
         # "HFM": config.ws_path / "hfm" / "trained_model" / "128" / "checkpoint-288.pth.tar",  # image guided
-        "AG": config.ws_path / "ag" / "trained_model" / "128" / "checkpoint.pth.tar",
+        # "AG": config.ws_path / "ag" / "trained_model" / "128" / "checkpoint.pth.tar",
         # "ResNG": config.ws_path / "resng" / "trained_model" / "128" / "checkpoint.pth.tar",
-        "GCNN5": config.ws_path / "resng" / "trained_model" / "128" / "checkpoint.pth.tar",
+        "GCNN": config.ws_path / "resng" / "trained_model" / "128" / "checkpoint.pth.tar",
     }
     test_folder = config.synthetic_data_noise_local / "synthetic128"
 

### 2022-06-29 eval.py
update datasets

@@ -92,10 +92,10 @@ if __name__ == '__main__':
         "SVD": None,
         # "NNNN": config.ws_path / "nnnn" / "trained_model" / "128" / "checkpoint.pth.tar",  # fast, loss 14
         # "HFM": config.ws_path / "hfm" / "trained_model" / "128" / "checkpoint-288.pth.tar",  # image guided
-        # "AG": config.ws_path / "ag" / "trained_model" / "128" / "checkpoint.pth.tar",
+        "AG": config.ws_path / "ag" / "trained_model" / "128" / "checkpoint.pth.tar",
         "NG": config.ws_path / "ng" / "trained_model" / "128" / "checkpoint.pth.tar",
         "GCNN": config.ws_path / "resng" / "trained_model" / "128" / "checkpoint.pth.tar",
     }
-    test_folder = config.synthetic_data_noise_local / "synthetic128"
+    test_folder = config.synthetic_data_noise_local / "synthetic256"
 
     main(models, test_folder, args)

### 2022-06-29 help_funs/data_preprocess.py

@@ -4,7 +4,7 @@ import shutil
 
 import numpy as np
 import torch
-
+import glob
 import config
 from help_funs import file_io
 
@@ -55,17 +55,21 @@ def noisy_a_folder(folder_path, output_path):
 
     if not os.path.exists(output_path):
         os.makedirs(output_path)
-    for idx in range(10000):
-        if os.path.exists(str(output_path / (str(idx).zfill(5) + ".depth0_noise.png"))):
+
+    gt_files = np.array(sorted(glob.glob(str(folder_path / "*normal0*.png"), recursive=True)))
+    depth_files = np.array(sorted(glob.glob(str(folder_path / "*depth0*.png"), recursive=True)))
+    data_files = np.array(sorted(glob.glob(str(folder_path / "*data0*.json"), recursive=True)))
+    img_files = np.array(sorted(glob.glob(str(folder_path / "*image0*.png"), recursive=True)))
+    for idx in range(len(img_files)):
+        if os.path.exists(str(output_path / (str(idx).zfill(5) + ".depth0.png"))):
             continue
-        image_file, ply_file, json_file, depth_gt_file, _, normal_file = file_io.get_file_name(idx, folder_path)
-        if os.path.exists(image_file):
-            f = open(json_file)
+        if os.path.exists(img_files[idx]):
+            f = open(data_files[idx])
             data = json.load(f)
-            depth = file_io.load_scaled16bitImage(depth_gt_file, data['minDepth'], data['maxDepth'])
+            depth = file_io.load_scaled16bitImage(depth_files[idx], data['minDepth'], data['maxDepth'])
 
             # get noise mask
-            img = np.expand_dims(file_io.load_16bitImage(image_file), axis=2)
+            img = np.expand_dims(file_io.load_16bitImage(img_files[idx]), axis=2)
             # img[img < 20] = 0
             depth, noise_factor = noisy_1channel(depth)
 
@@ -79,9 +83,9 @@ def noisy_a_folder(folder_path, output_path):
                 json.dump(data, f)
 
             # file_io.save_16bitImage(img_noise, str(output_path / (str(idx).zfill(5) + ".image0_noise.png")))
-            shutil.copyfile(depth_gt_file, str(output_path / (str(idx).zfill(5) + ".depth0.png")))
-            shutil.copyfile(image_file, str(output_path / (str(idx).zfill(5) + ".image0.png")))
[…]

### 2022-07-02 create_dataset.py
update dataset

@@ -71,13 +71,14 @@ def convert2training_tensor(path, k, output_type='normal'):
         # data['R'], data['t'] = np.identity(3), np.zeros(3)
         vertex = mu.depth2vertex(torch.tensor(depth).permute(2, 0, 1),
                                  torch.tensor(data['K']),
-                                 torch.tensor(data['R']).float(),
-                                 torch.tensor(data['t']).float())
+                                 torch.tensor(np.identity(3)).float(),
+                                 torch.tensor(np.zeros(3)).float())
         vertex_gt = mu.depth2vertex(torch.tensor(depth_gt).permute(2, 0, 1),
                                     torch.tensor(data['K']),
-                                    torch.tensor(data['R']).float(),
-                                    torch.tensor(data['t']).float())
-
+                                    torch.tensor(np.identity(3)).float(),
+                                    torch.tensor(np.zeros(3)).float())
+        vertex[mask] = 0
+        vertex_gt[mask_gt] = 0
         vertex_norm, scale_factors, shift_vector = vectex_normalization(vertex, mask)
 
         vertex_gt, scale_factors, shift_vector = vectex_normalization(vertex_gt, mask_gt)
@@ -89,6 +90,10 @@ def convert2training_tensor(path, k, output_type='normal'):
 
         # light
         # light_pos = (data['lightPos'] - shift_vector) / scale_factors
+        light_pos = np.array(data['lightPos']) + (
+                    (np.array(data['R']).transpose(0, 1)) @ (np.array(data['t'])).reshape(3, 1)).reshape(3)
+
+        lig_pos_norm = torch.from_numpy((light_pos - shift_vector) / scale_factors)
         light_direction = mu.vertex2light_direction(vertex, data['lightPos'])
         light_direction_gt = mu.vertex2light_direction(vertex_gt, data['lightPos'])
         light_direction_gt[mask_gt] = 0
@@ -122,7 +127,7 @@ def convert2training_tensor(path, k, output_type='normal'):
         training_case = {'input_tensor': input_tensor,
                          'gt_tensor': gt_tensor,
                          'scale_factors': scale_factors,
-                         'light_source': data['lightPos'],
+                         'light_source': lig_pos_norm,
                          'K': data['K'],
                          'R': data['R'],
                          't': data['t'],
@@ -134,7 +139,7 @@ def convert2training_tensor(path, k, output_type='normal'):
 
 
[…]

### 2022-07-02 eval_visual.py

@@ -47,7 +47,7 @@ def preprocessing(models):
     elif args.data == "synthetic_noise_dfki":
         path = config.synthetic_data_noise_dfki / args.datasize / "test" / "tensor"
     elif args.data == "synthetic":
-        path = config.synthetic_data / "test" / "tensor"  # key tests 103, 166, 189,9
+        path = config.synthetic_data / args.datasize / "test" / "tensor"  # key tests 103, 166, 189,9
     elif args.data == "real":
         path = config.real_data / "tensor"  # key tests 103, 166, 189,9
     elif args.data == "paper":
@@ -176,7 +176,9 @@ def start(models_path_dict):
 def start2(models_path_dict):
     models, dataset_path, folder_path, eval_res, eval_date, eval_time, all_names, datasize = preprocessing(
         models_path_dict)
-    if datasize == "synthetic128":
+    if datasize == "synthetic64":
+        font_scale = 0.8
+    elif datasize == "synthetic128":
         font_scale = 0.8
     elif datasize == "synthetic256":
         font_scale = 0.7
@@ -223,7 +225,7 @@ def start2(models_path_dict):
             # load model
             if name == "SVD":
                 print(f'- model {name} evaluation...')
-                normal, gpu_time = svd.eval_single(vertex_0, ~mask, np.array([0, 0.8, 7.5]), farthest_neighbour=2)
+                normal, gpu_time = svd.eval_single(vertex_0, ~mask, np.array([0, 0, -7]), farthest_neighbour=2)
             else:
                 checkpoint = torch.load(model)
                 args = checkpoint['args']
@@ -267,7 +269,7 @@ def start2(models_path_dict):
         # save files
         # mu.save_array(gt, str(folder_path / f"fancy_eval_{i}_normal_gt"))
 
-        cv.imwrite(str(folder_path / f"fancy_eval_{i}_img.png"), img)
+        cv.imwrite(str(folder_path / f"fancy_eval_{i}_img.png"), mu.visual_img(img, "", font_scale=font_scale))
         cv.imwrite(str(folder_path / f"fancy_eval_{i}_groundtruth.png"),
                    cv.cvtColor(mu.visual_normal(gt, "", histogram=False), cv.COLOR_RGB2BGR), )
         cv.imwrite(str(folder_path / f"fancy_eval_{i}_point_cloud_noise.png"),
@@ -292,10 +294,10 @@ if __name__ == '__main__':
[…]

### 2022-07-04 paper/Chapters/Chapter05.tex
update ag
update dataset light position

@@
 It is
-
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_point_cloud_noise.png}
-		\caption{point cloud}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_groundtruth.png}
-		\caption{ground-truth}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon)}
-	\label{fig:gcnn-eval-synthetic}
-\end{figure}
 
@@
 
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_normal_NG.png}
-		\caption{g-GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_error_NG.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\caption{guided-GCNN Normal Inference on Synthetic Dataset (object: dragon). GCNN result is shown on (d) and (e) as comparison.}
-	\label{fig:ng-eval-synthetic}
-\end{figure}
-
 \section{Guided Gated Convolution Neural Network for Normal Inference }
@@
 This section evaluates the proposed models with the neighbor-based model and make comparison with each other.
-
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_groundtruth.png}
-		\caption{ground-truth}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_normal_svd.png}
-		\caption{SVD}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_normal_GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_normal_NG.png}
-		\caption{guided-GCNN}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.3\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_error_SVD.png}
-		\caption{Error}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.3\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_error_GCNN.png}
-		\caption{Error}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.3\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_3_error_NG.png}
-		\caption{Error}
-	\end{subfigure}
-
-	\caption{Normal Inference on different models with errors. (object: dragon)}
-	\label{fig:eval-svd}
-\end{figure}

### 2022-07-07 paper/Chapters/Chapter05.tex
update evaluation

@@
 The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $.
-A network named Gated Convolution Neural Network (GCNN) is trained and is compared with similar approaches.
-
-\subsection{Compared Approaches}
-
-\subsection{Training Details}
-The network (see \ref{gcnn}) is trained on stated dataset in Chapter \ref{ch:04}.
-It has two versions, the L-size $ 512\times512\times3 $ and the  S-size $ 128\times128\times3 $.
-For the L-size model, it uses batch size 8 for 3500 iterations.
-For the S-size model, it uses batch size 32 for 6000 iterations.
-Both sizes use Adam optimizer \cite{adam} with a learning rate of $ 1\times10^{-3} $, penalty-l2 loss(see \ref{sec:loss}).
+A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches.
+We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training.
+All the depth maps add simulated noise as introduced in \ref{sec:noise}.
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss(see \ref{sec:loss}).
 The output is directly the tangent normal in range $ \left[-1,1\right] $.
@@
 
-The evaluation visualization on dataset ``synthetic50-5" (see \ref{ch:04}) dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}.
-It compares the results with method xxx, for both smooth and highly detailed cases.
-In all the cases, the angle errors are very close.
-The test-cases are based on test point cloud in ``synthetic50-5".
-
-The model is supposed to used on any image size since it has no fully-connected layers (dense layers). Two size of models are based on exactly the same architecture.
+The visual evaluation on model GCNN shown in Figure \ref{fig:gcnn-eval-synthetic-full}.
 
@@
 
+The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}.
+Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
+\begin{figure}[th]
+	\centering
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
+		\caption{GT}
+	\end{subfigure}
+		\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+		\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
+	\caption{}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
+		\caption{}
+	\end{subfigure}
+	\caption{Zoom in of dragon object evaluation.}
+	\label{fig:gcnn-eval-synthetic-zoom-in}
+\end{figure}
+
 The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
-\begin{figure}[h!]
+\begin{figure}[th]
 	\centering

### 2022-07-07 eval_visual.py

@@ -337,13 +337,13 @@ if __name__ == '__main__':
     # load test model names
 
     models = {
-        # "SVD": None,
+        "SVD": None,
         # "GCNN-64": config.ws_path / "resng" / "trained_model" / "64" / "checkpoint.pth.tar",  # image guided
         "GCNN3-32-512": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32.pth.tar",
         # "GCNN3-32-512-2": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32-2.pth.tar",
         # "GCNN3-64-512": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-64.pth.tar",
 
-        "AG": config.ws_path / "ag" / "trained_model" / "512" / "checkpoint.pth.tar",  # with light direction
+        # "AG": config.ws_path / "ag" / "trained_model" / "512" / "checkpoint.pth.tar",  # with light direction
         # "GCNN": config.ws_path / "nnnn" / "trained_model" / "512" / "checkpoint.pth.tar",
         # "FUGRC": config.ws_path / "fugrc" / "trained_model" / "128" / "checkpoint-608.pth.tar",
 

### 2022-07-07 paper/Chapters/Chapter05.tex
update ag model

@@
 All the depth maps add simulated noise as introduced in \ref{sec:noise}.
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss(see \ref{sec:loss}).
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss.
 The output is directly the tangent normal in range $ \left[-1,1\right] $.
@@
 
-The visual evaluation on model GCNN shown in Figure \ref{fig:gcnn-eval-synthetic-full}.
+The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. As shown in the picture, GCNN model 
+Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_point_cloud_noise.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_groundtruth.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_GCNN3-32-512.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_SVD.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_GCNN3-32-512.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_SVD.png}
+	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon) From left to right: Input vertex map, ground-truth, GCNN normal map, SVD normal map, GCNN error map, SVD error map}
+	\label{fig:gcnn-eval-synthetic}
+\end{figure}
 
-%% a detailed analyis of this figure
-It is
-
-The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}.
-Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
 \begin{figure}[th]

### 2022-07-07 create_dataset.py

@@ -108,9 +108,9 @@ def convert2training_tensor(path, k, output_type='normal'):
         albedo = img / (G + 1e-20)
 
         # mu.show_images(img, "img")
-        # albedo_img = np.uint8(albedo)
-        # albedo_img = cv.normalize(albedo_img, None, 0, 255, cv.NORM_MINMAX, dtype=cv.CV_8U)
-        # mu.show_images(albedo_img, "a")
+        albedo_img = np.uint8(albedo)
+        albedo_img = cv.normalize(albedo_img, None, 0, 255, cv.NORM_MINMAX, dtype=cv.CV_8U)
+        mu.show_images(albedo_img, "a")
 
         target = np.c_[
             gt_normal,  # 0,1,2

### 2022-07-07 eval.py

@@ -89,13 +89,13 @@ if __name__ == '__main__':
         # "fugrc": config.ws_path / "fugrc" / "trained_model" / "128" / "checkpoint-608.pth.tar",
         # "fugrc2": config.ws_path / "fugrc" / "trained_model" / "128" / "checkpoint-1058.pth.tar",
         # loss 13, on training
-        "SVD": None,
+        # "SVD": None,
         # "NNNN": config.ws_path / "nnnn" / "trained_model" / "128" / "checkpoint.pth.tar",  # fast, loss 14
         # "HFM": config.ws_path / "hfm" / "trained_model" / "128" / "checkpoint-288.pth.tar",  # image guided
-        "AG": config.ws_path / "ag" / "trained_model" / "128" / "checkpoint.pth.tar",
-        "NG": config.ws_path / "ng" / "trained_model" / "128" / "checkpoint.pth.tar",
-        "GCNN": config.ws_path / "resng" / "trained_model" / "128" / "checkpoint.pth.tar",
+        "AG": config.ws_path / "ag" / "trained_model" / "512" / "checkpoint.pth.tar",
+        # "NG": config.ws_path / "ng" / "trained_model" / "128" / "checkpoint.pth.tar",
+        "GCNN": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32.pth.tar",
     }
-    test_folder = config.synthetic_data_noise_local / "synthetic256"
+    test_folder = config.synthetic_data_noise_local / "synthetic512"
 
     main(models, test_folder, args)

### 2022-07-07 eval_visual.py

@@ -343,7 +343,7 @@ if __name__ == '__main__':
         # "GCNN3-32-512-2": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32-2.pth.tar",
         # "GCNN3-64-512": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-64.pth.tar",
 
-        # "AG": config.ws_path / "ag" / "trained_model" / "512" / "checkpoint.pth.tar",  # with light direction
+        "AG": config.ws_path / "ag" / "trained_model" / "512" / "checkpoint.pth.tar",  # with light direction
         # "GCNN": config.ws_path / "nnnn" / "trained_model" / "512" / "checkpoint.pth.tar",
         # "FUGRC": config.ws_path / "fugrc" / "trained_model" / "128" / "checkpoint-608.pth.tar",
 

### 2022-07-11 paper/akweury/document.tex
update paper

@@
 
+Intrinsic image model was introduced by \cite{intrinsic-image}.
+It represents that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
+\[ I =R  \odot S\]
+The equation can be further decomposed based on different surface models.
+If assume the object surfaces are Lambertian surfaces, i.e.
+the diffuse surfaces, the equation can be decomposed further as follows
+\[ I = \rho  \odot (L_0 \textbf{L} \cdot  \textbf{N}) \]
+where $ \rho $ is the reflectance of diffuse surface, also know as albedo, $ L_0 $ is the radiance of  incoming light, i.e.
+irradiance, $ \textbf{L} $ is the direction of incoming light as unit vector map and $ \textbf{N} $ is the surface normal also as unit vector map.
+
+The decomposition gives a constraint of the normal map with given other information, which can be considered further in the deep learning model.
+The image $ I $ is given in the RGB-D image, the light map $ \textbf{L} $ can be calculated based on the light source and the vertex map.
+
+L->L0L
+
+\newpage 
+ As shown in Figure \ref{fig:lambertian-surface}, 
+\begin{figure}[th]
+	\centering
+	\begin{tikzpicture} 
+		% reference lines
+		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
+		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
+		\draw[thick, ->] (-1,3) -- (2,0) node[midway, left] {$ \textbf{s} $}; %% source direction
+		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
+		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
+		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
+	\end{tikzpicture}	
+	\caption{Lambertian Surface}
+	\label{fig:lambertian-surface}
+\end{figure}
+According to the Lambertian reflectance model, the relationship between image and the surface model is 
+\[ I = \rho (\textbf{N} \cdot \textbf{L}) \]
+
+where $ I $ is the total power , $ \rho $ is the albedo,  $ N $ is the normal map and $ L $ is the incoming light direction.
+
 \end{document}

### 2022-07-11 paper/akweury/document.tex
update albedoGated model

@@
 \usepackage{breqn}
-
+\usepackage{bm}
 \usepackage{graphicx}
@@
 The image $ I $ is given in the RGB-D image, the light map $ \textbf{L} $ can be calculated based on the light source and the vertex map.
+Since the brightness $ L_0 $ of the image is not take into account when we calculate the surface normal, it is save to remove it in the equation.
+Using the predicted surface normal map $  \bm{\hat{N}} $, then the calculated albedo $ \hat\rho $ is as follows
+\[ \hat\rho = \frac{I}{\textbf{L} \cdot  \bm{\hat{N}} }  \]
+The accuracy of $ \hat\rho $ is related to the accuracy of $  \bm{\hat{N}} $. The normal
 
-L->L0L
+V -> N
+don't known albedo
+L, N
+
+N->rho
 

### 2022-07-11 main_noise.py

@@ -3,7 +3,7 @@ from help_funs.data_preprocess import convert2training_tensor_noise
 from workspace import train
 from pncnn.utils import args_parser
 
-import workspace.noise_net.network as noiseNet
+import workspace.albedoGated.network as noiseNet
 
 
 def main():
@@ -20,7 +20,7 @@ def main():
 
     # config experiments
     exp_path = config.ws_path / args.exp
-    if args.exp == "noise_net":
+    if args.exp == "albedoGated":
         model = noiseNet.CNN()
     else:
         raise ValueError("Unknown exp path")

### 2022-07-15 paper/akweury/document.tex
update ag model

--- 2022-07-11 paper/akweury/document.tex
@@
 
+\section{Guided normal inference using GCNN}
+
+\subsection{Shape from shading}
 Intrinsic image model was introduced by \cite{intrinsic-image}.
@@
 where $ \rho $ is the reflectance of diffuse surface, also know as albedo, $ L_0 $ is the radiance of  incoming light, i.e.
-irradiance, $ \textbf{L} $ is the direction of incoming light as unit vector map and $ \textbf{N} $ is the surface normal also as unit vector map.
+irradiance, $ \textbf{L} $ is the opposite direction of incoming light as unit vector map and $ \textbf{N} $ is the surface normal also as unit vector map, as shown in Figure \ref{fig:lambertian-surface}
 
-The decomposition gives a constraint of the normal map with given other information, which can be considered further in the deep learning model.
-The image $ I $ is given in the RGB-D image, the light map $ \textbf{L} $ can be calculated based on the light source and the vertex map.
-
-L->L0L
-
-\newpage 
- As shown in Figure \ref{fig:lambertian-surface}, 
 \begin{figure}[th]
@@
 \end{figure}
-According to the Lambertian reflectance model, the relationship between image and the surface model is 
-\[ I = \rho (\textbf{N} \cdot \textbf{L}) \]
 
-where $ I $ is the total power , $ \rho $ is the albedo,  $ N $ is the normal map and $ L $ is the incoming light direction.
+The equation can be further rearranged as follows
+\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
+The shape from shading method employed the equation mentioned above to predict the both surface albedo and the normal.
+More specifically, a set of $ k $ image for the same scene have been captured based on different light projections.
+Then, for each pixel $ (x,y) $ in the image, an equation system can be set up
+
+\[ 
+\begin{pmatrix}
+	L_1^T \\
+	L_2^T \\
+	\cdots \\
+	L_k^T
+\end{pmatrix} g(x,y) = 
+\begin{pmatrix}
+	I_1(x,y) \\
+	I_2(x,y) \\
+	\cdots \\
+	I_3(x,y)
+\end{pmatrix}
+\]
+for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
+The equation can be solved based on least square methods. 
+Since normal $ N(x,y) $ is unit vector, thus we have
+
+\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]
+
+Then the normal can be obtained as follow
+
+\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]
+
+In another word, the surface normal including the albedo can be obtained directly based on images and light directions.
+
+\subsection{Light and image guided normal inference using GCNN}
+
+The decomposition gives a constraint of the normal map with given other information, which can be considered further in the deep learning model.
+The image $ I $ is given in the RGB-D image, the light map $ \textbf{L} $ can be calculated based on the light source and the vertex map.
+
+Inspired by the Shape from shading approach mentioned above, a new approach is proposed in this thesis for normal prediction.
+The structure is shown in Figure \ref{fig:albedo-gated-archi}.
+The model takes image $ \textbf{I} $, Light direction $ \textbf{L} $ and 3D vertex $ \textbf{V} $ as input.
+Each input has its own branch based on UNet architecture with four times fusion in the upsampling part.
+
+\subsection{Light Map}
+The incoming light direction of each point can be represented as a matrix with same size as normal map or vertex map, where each pixel corresponding with each other.
+
+%% calc the light direction matrix
+\paragraph{Calculation}
+The incoming light direction can be calculated based on the position of light source and points.
+As shown in Figure \ref{fig:lambertian-surface-principle}, the incoming light direction of the surface point is a vector point from light source to the surface point, therefor it can be calculated as follows
+
+\begin{equation}\label{light-direction}
+	\begin{array}{ll}
+		L&= \frac{V-S}{\|V-S\|_2}\\ 
+	\end{array}
+\end{equation}
+where $ S $ is the light source position and $ V $ is the vertices, both $ S $ and  $ V $ are with respect to the camera space.
+The light direction map $ L $ is normalized since only the direction of the light is considered.
+
+\paragraph{Inpainting}
+Due to the exist noise in the vertex map, the getting light map is also semi-dense.
+
+stores for every pixel the direction of incoming light.
+find a mapping H, such that $ l_{in} = H(v, l_{s}) $ for pixel $ v $, $ l_s $ is the position of light source, $ l_{in} $ is direction of incoming light of pixel $ v $.
+Iterate all the pixels, we get the light direction map $ L $.
 

### 2022-07-15 workspace/train.py

@@ -337,7 +337,7 @@ def train_epoch(nn_model, epoch):
             albedo_gt = mu.albedo(target[:, 4:5, :, :], mask, target[:, 3:4, :, :], nn_model.args.albedo_threshold)
 
             # print("albedo maxmin: " + str(albedo_target.max()) + str(albedo_target.min()))
-            nn_model.albedo_loss = loss_utils.weighted_log_l1_loss(out[:, 3:4, :, :], albedo_gt,
+            nn_model.albedo_loss = loss_utils.weighted_log_l1_loss(out[:, 6:7, :, :], albedo_gt,
                                                                    nn_model.args.penalty,
                                                                    0, 1)
 
@@ -393,7 +393,7 @@ def train_epoch(nn_model, epoch):
         plot_loss_per_axis(light_loss_total, nn_model, epoch, title="light_loss")
     if nn_model.args.albedo_loss:
         nn_model.losses[9, epoch] = albedo_loss_total / len(nn_model.train_loader.dataset)
-        draw_line_chart(np.array([nn_model.losses[6]]), nn_model.output_folder,
+        draw_line_chart(np.array([nn_model.losses[9]]), nn_model.output_folder,
                         log_y=True, label="albedo", epoch=epoch, start_epoch=0, title="albedo_loss", cla_leg=True)
 
     # indicate for best model saving
@@ -587,6 +587,8 @@ def draw_output(exp_name, input, xout, target, exp_path, epoch, i, train_idx, pr
     x_out_normal = xout[0, :3, :, :].permute(1, 2, 0).to('cpu').numpy()
     x_out_light = xout[0, :3, :, :].permute(1, 2, 0).to('cpu').numpy()
     g_out = xout[0, 3:6, :, :].permute(1, 2, 0).to('cpu').numpy()
+    rho_out = xout[0, 6:7, :, :].permute(1, 2, 0).to('cpu').numpy()
+
     mask = gt.sum(axis=2) == 0
     # input
     output_list.append(mu.visual_vertex(vertex_0, "input(vertex)"))
@@ -600,6 +602,21 @@ def draw_output(exp_name, input, xout, target, exp_path, epoch, i, train_idx, pr
         output_list.append(mu.visual_light(x_out_light, "pred"))
         output_list.append(mu.visual_light(light_gt, "gt"))
         output_list.append(mu.visual_diff(light_gt, x_out_light, "angle"))
[…]

### 2022-07-15 paper/akweury/document.tex
update albedogated model

--- 2022-07-11 paper/akweury/document.tex
@@
 \usepackage{tikz-network}
+\usetikzlibrary{calc,patterns,angles,quotes}
 \usepackage{breqn}
-
+\usepackage{bm}
 \usepackage{graphicx}
@@
 \usepackage{multirow}
+\usepackage{graphicx}
 \usetikzlibrary{fit}
@@
 
+\section{Guided normal inference using GCNN}
+
+\subsection{Intrinsic image decomposition}
 Intrinsic image model was introduced by \cite{intrinsic-image}.
-It represents that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
+It interprets that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
 \[ I =R  \odot S\]
+It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
+%% insert a image for decompositions
+\begin{figure}[th]
+	\centering
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
+	\decoRule	
+	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
+	\label{fig:intrinsic-image}
+\end{figure}
+
 The equation can be further decomposed based on different surface models.
 If assume the object surfaces are Lambertian surfaces, i.e.
-the diffuse surfaces, the equation can be decomposed further as follows
-\[ I = \rho  \odot (L_0 \textbf{L} \cdot  \textbf{N}) \]
-where $ \rho $ is the reflectance of diffuse surface, also know as albedo, $ L_0 $ is the radiance of  incoming light, i.e.
-irradiance, $ \textbf{L} $ is the direction of incoming light as unit vector map and $ \textbf{N} $ is the surface normal also as unit vector map.
+the surface which reflect light in all directions, the shading image can be decomposed as the product of the  radiance of  incoming light $ L_0 $, the cosine of the angle of incidence, which is the dot product of the surface normal $ N $ and the light source direction $ L $.
+\[ I = \rho  \odot ( L_0 \textbf{L} \cdot  \textbf{N}) \]
+note that the surface normal $ N $ and light direction $ L $ are unit vectors thus they have only two degrees of freedom.
 
-The decomposition gives a constraint of the normal map with given other information, which can be considered further in the deep learning model.
-The image $ I $ is given in the RGB-D image, the light map $ \textbf{L} $ can be calculated based on the light source and the vertex map.
-
-L->L0L
-
-\newpage 
- As shown in Figure \ref{fig:lambertian-surface}, 
 \begin{figure}[th]
@@
 		% reference lines
+		\coordinate (light) at (-1,3);
+		\coordinate (p) at (2,0);
+		\coordinate (normal) at (2,3);
 		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
 		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
-		\draw[thick, ->] (-1,3) -- (2,0) node[midway, left] {$ \textbf{s} $}; %% source direction
+		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
+		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
 		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
@@
 	\end{tikzpicture}
-	\caption{Lambertian Surface}
+	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
 	\label{fig:lambertian-surface}
 \end{figure}
-According to the Lambertian reflectance model, the relationship between image and the surface model is 
-\[ I = \rho (\textbf{N} \cdot \textbf{L}) \]
 
-where $ I $ is the total power , $ \rho $ is the albedo,  $ N $ is the normal map and $ L $ is the incoming light direction.
+The equation can be further rearranged as follows
+\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
+The shape from shading method employed the equation mentioned above to predict the both surface albedo $ \rho $ and the normal $ \textbf{N} $ with knowning light source direction $ \textbf{L} $.
+More specifically, a set of $ k $ image for the same scene have been captured based on different light projections.
+Then, for each pixel $ (x,y) $ in the image, an equation system can be set up
+
+\[ 
+\begin{pmatrix}
+	L_1^T \\
+	L_2^T \\
+	\cdots \\
+	L_k^T
+\end{pmatrix} g(x,y) = 
+\begin{pmatrix}
+	I_1(x,y) \\
+	I_2(x,y) \\
+	\cdots \\
+	I_3(x,y)
+\end{pmatrix}
+\]
+for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
+The equation can be solved based on least square methods. 
+Since normal $ N(x,y) $ is unit vector, thus we have
+
+\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]
+
+Then the normal can be obtained as follow
+
+\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]
+
+In another word, the surface normal including the albedo can be obtained directly based on images and light directions.
+
+\subsection{Light Map}
+The light map $ L $ can be derived from vertex map and the light source position.
+As shown in Figure \ref{fig:lambertian-surface}, the incoming light direction is a vector point from light source to the surface point, therefor it can be calculated as follows
+\begin{equation}\label{light-direction}
+	\begin{array}{ll}
+		L(x,y)&= \frac{V(x,y)-(s_x,s_y)}{\|V(x,y)-(s_x,s_y)\|_2}\\ 
+	\end{array}
+\end{equation}
+where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space.
+The light direction map $ L $ is normalized since only the direction of the light is considered.
+The light map is a matrix corresponding the light direction of whole image where each pixel corresponding with each other, thus it has the same size as the vertex map.
+
+It is important to note that due to the exist noise in the vertex map, the getting light map is only semi-dense, as shown in Figure \ref{fig:light-input}.
+
+\begin{figure}[th]
+	\centering
+	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
+	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_light_input.png}}
+	\decoRule	
+	\caption{The light map calculated from vertex map and the light source}
+	\label{fig:light-input}
+\end{figure}
+
+In order to ease this issue, a light inpainting model has been trained based on the GCNN network. It takes the semi-dense light map as input and predict the fully dense light map.
+
+\begin{figure}[th]
+	\centering
+	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
+	\begin{tikzpicture}
+		%% -------------------------------------- parameters ------------------------------------------------
+		\pgfmathsetmacro{\vdist}{0.4}
+
+		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
+		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3
+
+		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
+		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}
+
+		%% 	d_in							3x512x512
+		%%	dconv1: 	d_in-->x1 			32x512x512
+		\pgfmathsetmacro{\disttimes}{1}	%% width 32
+		\pgfmathsetmacro{\yshift}{1}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
+		\pgfmathsetmacro{\yschift}{-1}
+
+		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
+
+		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};
+
+		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
+		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);
+
+		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
+		\pgfmathsetmacro{\yschift}{-1}
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
+\end{tikzpicture}
+
+\caption{Light Net for light inpainting based on GCNN architecture.}
+\label{fig:light-net-archi}
+\end{figure}
+
+\subsection{Light and image guided normal inference using GCNN}
+Based on above implementations, we propose a Triple Gated Convolutional Neural Network (TriGNet) to perform guided normal inference.
+The structure is shown in Figure \ref{fig:albedo-gated-archi}.
+As shown in the name, the network is constructed based on three GCNN architectures: Image GCNN, Light GCNN, and Vertex GCNN.
 

### 2022-07-15 create_dataset.py

@@ -113,6 +113,7 @@ def convert2training_tensor(path, k, output_type='normal'):
         # albedo_img = cv.normalize(albedo_img, None, 0, 255, cv.NORM_MINMAX, dtype=cv.CV_8U)
         # mu.show_images(albedo_img, "a")
 
+        ###################  target  ####################
         target = np.c_[
             gt_normal,  # 0,1,2
             np.sum(gt_normal * light_direction_gt, axis=-1, keepdims=True),  # 3
@@ -120,9 +121,11 @@ def convert2training_tensor(path, k, output_type='normal'):
             light_direction_gt  # 5,6,7
         ]
 
-        # case of resng, ng
+        ################### input #######################
         vertex_norm[mask] = 0
-        vectors = np.c_[vertex_norm, np.expand_dims(img, axis=2), light_direction]
+        vectors = np.c_[vertex_norm,  # 0,1,2
+                        np.expand_dims(img, axis=2),  # 3
+                        light_direction]  # 4,5,6
 
         # convert to tensor
         input_tensor = torch.from_numpy(vectors.astype(np.float32)).permute(2, 0, 1)

### 2022-07-17 paper/akweury/document.tex
update an loss

@@
-\documentclass[]{article}
+\documentclass[border=15pt, multi, tikz]{article}
 \usepackage{amssymb}
@@
 \usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
-
+\usepackage{import}
 \usepackage{tikz}
@@
 \usetikzlibrary {positioning}
-
+\subimport{./layers/}{init}
 \newcommand{\bn}{\textbf{n}}
 \newcommand{\tabhead}[1]{\textbf{#1}}
+
+\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
+\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
+\def\PoolColor{rgb:red,1;black,0.3}
+\def\DcnvColor{rgb:blue,5;green,2.5;white,5}
+\def\SoftmaxColor{rgb:magenta,5;black,7}
+\def\SumColor{rgb:blue,5;green,15}
+\def\poolsep{1}
 
@@
 	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
-	\decoRule	
 	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
@@
 	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_light_input.png}}
-	\decoRule	
 	\caption{The light map calculated from vertex map and the light source}
@@
 
-In order to ease this issue, a light inpainting model has been trained based on the GCNN network. It takes the semi-dense light map as input and predict the fully dense light map.
+In order to ease this issue, a light inpainting model has been trained based on the GCNN network with the identity architecture but the input and output, which takes the semi-dense light map as input and predict the fully dense light map as output.
 
@@
 \end{tikzpicture}
-
 \caption{Light Net for light inpainting based on GCNN architecture.}
@@
 \subsection{Light and image guided normal inference using GCNN}
-Based on above implementations, we propose a Triple Gated Convolutional Neural Network (TriGNet) to perform guided normal inference.
+Based on above implementations, we propose a Three branches Gated Convolutional Neural Network (TriGNet) to perform guided normal inference.
 The structure is shown in Figure \ref{fig:albedo-gated-archi}.
-As shown in the name, the network is constructed based on three GCNN architectures: Image GCNN, Light GCNN, and Vertex GCNN.
+As shown in the name, the network utilizes the GCNN architecture three times to accomplish the task.
+
+\begin{figure}[th]
+	\centering 
+	\begin{tikzpicture}
+		\tikzstyle{connection}=[ultra thick,every node/.style={sloped,allow upside down},draw=\edgecolor,opacity=0.6]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Draw Layer Blocks
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% conv1_1,conv1_2,%pool1
+\pic[shift={(0,0,0)}] at (0,0,0) {RightBandedBox={name=cr1,%
+		xlabel={{"64","64"}},zlabel=I,fill=\ConvColor,bandfill=\ConvReluColor,%
+		height=40,width={2,2},depth=40}};
+\pic[shift={(\poolsep,0,0)}] at (cr1-east) {Box={name=p1,%
+		fill=\PoolColor,opacity=0.5,height=30,width=1,depth=30}};
+% conv2_1,conv2_2,pool2
+\pic[shift={(1,0,0)}] at (p1-east) {RightBandedBox={name=cr2,%
+		xlabel={{"64","64"}},zlabel=I/2,fill=\ConvColor,bandfill=\ConvReluColor,%
+		height=30,width={3,3},depth=30}};
+\pic[shift={(\poolsep,0,0)}] at (cr2-east) {Box={name=p2,%
+		fill=\PoolColor,opacity=0.5,height=23,width=1,depth=23}};
+% conv3_1,conv3_2,pool3
+\pic[shift={(1,0,0)}] at (p2-east) {RightBandedBox={name=cr3,%
+		xlabel={{"256","256","256"}},zlabel=I/4,fill=\ConvColor,bandfill=\ConvReluColor,%
+		height=23,width={4,4,4},depth=23}};
+\pic[shift={(\poolsep,0,0)}] at (cr3-east) {Box={name=p3,%
+		fill=\PoolColor,opacity=0.5,height=14,width=1,depth=14}};
+% conv4_1,conv4_2,conv4_3,pool4
+\pic[shift={(1,0,0)}] at (p3-east) {RightBandedBox={name=cr4,%
+		xlabel={{"512","512","512"}},zlabel=I/8,fill=\ConvColor,bandfill=\ConvReluColor,%
+		height=14,width={7,7,7},depth=14}};
+\pic[shift={(\poolsep,0,0)}] at (cr4-east) {Box={name=p4,%
+		fill=\PoolColor,opacity=0.5,height=8,width=1,depth=8}};
+% conv5_1,conv5_2,conv5_3,pool5
+\pic[shift={(1,0,0)}] at (p4-east) {RightBandedBox={name=cr5,%
+		xlabel={{"512","512","512"}},fill=\ConvColor,bandfill=\ConvReluColor,%
+		height=8,width={7,7,7},depth=8}};
+%% fc8 -> cr8 (score32)
+\pic[shift={(0,0,0)}] at (cr5-east) {Box={name=score16,%
+		xlabel={{"K","dummy"}},fill=\ConvColor,%
+		height=8,width=2,depth=8,zlabel=I/16}};
+
+%% Upsampling Deconv Layer
+%% Dcnv16    
+\pic[shift={(2.5,0,0)}] at (score16-east) {Box={name=d16,%
+		xlabel={{"","dummy"}},fill=\DcnvColor,opacity=0.7,height=40,width=0.5,depth=40}};
+%% Dcnv8    
+\pic[shift={(.25,0,0)}] at (d16-east) {Box={name=d8,%
+		xlabel={{"","dummy"}},fill=\DcnvColor,opacity=0.7,height=40,width=0.5,depth=40}};
+%% Dcnv4    
+\pic[shift={(.25,0,0)}] at (d8-east) {Box={name=d4,%
+		xlabel={{"","dummy"}},fill=\DcnvColor,opacity=0.7,height=40,width=0.5,depth=40}};
+%% Dcnv2    
+\pic[shift={(.25,0,0)}] at (d4-east) {Box={name=d2,%
+		xlabel={{"","dummy"}},fill=,opacity=0.01,height=40,width=0.5,depth=40}};
+
+%% Dcnv envelope    
+\pic[shift={(-0.2,0,0)}] at (d16-west) {Box={name=env,caption=concatenation of deconvolved feature maps,%
+		xlabel={{"","dummy"}},fill=,opacity=0.2,height=42,width={8},depth=42}};
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\def\skipshift{6.5}
+%%Joining with previous streams (fcn-16)
+%% score16
+\pic[shift={(0,0,3+\skipshift)}] at (cr5-anchor) {Box={name=score8,%
+		xlabel={{"K","dummy"}},fill=\ConvColor,height=14,width=2,depth=14,zlabel=I/8}};
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%Joining with previous streams (fcn-8)
+%% score8
+\pic[shift={(0,0,8+\skipshift)}] at (cr4-east) {Box={name=score4,%
+		xlabel={{"K","dummy"}},fill=\ConvColor,height=23,width=2,depth=23,zlabel=I/4}};
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%Joining with previous streams (fcn-4)
+%% score4
+\pic[shift={(1,0,13+\skipshift)}] at (cr3-east) {Box={name=score2,%
+		xlabel={{"K","dummy"}},fill=\ConvColor,height=30,width=2,depth=30,zlabel=I/2}}; 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%Joining with previous streams (fcn-2)
+%% score2
+\pic[shift={(0.3,0,22+\skipshift)}] at (p2-east) {Box={name=score,%
+		xlabel={{"K","dummy"}},fill=\ConvColor,height=40,width=2,depth=40,zlabel=I}};
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Final convolution
+
+\pic[shift={(3,0,0)}] at (d2-east) {Box={name=output,%
+		xlabel={{"K","dummy"}},fill=\ConvColor,height=40,width=2,depth=40,zlabel=I}};
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Draw connections
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\draw [connection]  (cr1-east)    -- node {\midarrow} (p1-west);
+\draw [connection]  (p1-east)    -- node {\midarrow} (cr2-west);
+\draw [connection]  (cr2-east)    -- node {\midarrow} (p2-west);
+\draw [connection]  (p2-east)    -- node {\midarrow} (cr3-west);
+\draw [connection]  (cr3-east)    -- node {\midarrow} (p3-west);
+\draw [connection]  (p3-east)    -- node {\midarrow} (cr4-west);
+\draw [connection]  (cr4-east)    -- node {\midarrow} (p4-west);
+\draw [connection]  (p4-east)    -- node {\midarrow} (cr5-west);
+\draw [connection]  (score16-east)    -- node {\midarrow} (d16-west);
+%
+\path (cr4-east) -- (p4-west) coordinate[pos=0.4] (after4) ;
+\draw (d16-near)++(0,0,-1+\skipshift) coordinate (d16h);
+\draw [connection]  (after4)    -- node {\midarrow} ++(0,0,3+\skipshift) -- node {\midarrow} (score8-west);
+\draw [connection]  (score8-east) -- node{\midarrow} (d16h) -- node{\midarrow}(d16-near);
+%
+\path (cr3-east) -- (p3-west) coordinate[pos=0.4] (after3) ;
+\draw (d8-near)++(0,0,4+\skipshift) coordinate (d8h);
+\draw [connection]  (after3)    -- node {\midarrow} ++(0,0,8+\skipshift) -- node {\midarrow} (score4-west);
+\draw [connection]  (score4-east) -- node{\midarrow} (d8h) -- node{\midarrow}(d8-near);
+%
+\path (cr2-east) -- (p2-west) coordinate[pos=0.4] (after2) ;
+\draw (d4-near)++(0,0,9+\skipshift) coordinate (d4h);
+\draw [connection]  (after2)    -- node {\midarrow} ++(0,0,13+\skipshift) -- node {\midarrow} (score2-west);
+\draw [connection]  (score2-east) -- node{\midarrow} (d4h) -- node{\midarrow}(d4-near);
+%
+\path (cr1-east) -- (p1-west) coordinate[pos=0.4] (after1) ;
+\draw (d2-near)++(0,0,18+\skipshift) coordinate (d2h);
+\draw [connection]  (after1)    -- node {\midarrow} ++(0,0,22+\skipshift) -- node {\midarrow} (score-west);
+\draw [connection]  (score-east) -- node{\midarrow} (d2h) -- node{\midarrow}(d2-near);
+
+\draw [connection]  (d2-east)    -- node {\midarrow} (output-west);
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\end{tikzpicture}
+	\caption{TriGNet Architecture}
+	\label{fig:trig-net-archi}
+\end{figure}
 

### 2022-07-17 paper/akweury/document.tex
upload an2 model

--- 2022-07-15 paper/akweury/document.tex
@@
 \usepackage{graphicx}
+\usepackage{rotating}
 \usetikzlibrary{fit}
@@
 \subsection{Light Map}
+\label{sec:lightmap}
 The light map $ L $ can be derived from vertex map and the light source position.
@@
 \subsection{Light and image guided normal inference using GCNN}
-Based on above implementations, we propose a Triple Gated Convolutional Neural Network (TriGNet) to perform guided normal inference.
+Based on above implementations, we propose a Three branches Gated Convolutional Neural Network (TriGNet) to perform guided normal inference.
 The structure is shown in Figure \ref{fig:albedo-gated-archi}.
-As shown in the name, the network is constructed based on three GCNN architectures: Image GCNN, Light GCNN, and Vertex GCNN.
+As mentioned in the name, the network utilizes the GCNN architecture three times to accomplish the task.
+The first branch (shown above) takes a light map introduced in \ref{sec:lightmap} as the input, the structure is the same as GCNN architecture except that the last two standard convolution layers, the skip connections are kept to connect the 3 down/up samplings.
+The second branch (shown below) takes image as the input, the structure is the same as the first branch other than the input image is 1 channel but not 3 channels. 
+The third branch takes the 3D vertex map as the input.
+The structure is based on GCNN architecture.
+However, in order to merge the other two branches, the vertex branch equips 4 times fusions in the up sampling part.
+Specifically, the first fusion locates immediately after the last gconv layer of the last down sampling, the second fusion after the second gconv layer of first up sampling, the third fusion after the second gconv layer of second up sampling, the fourth fusion after the second gconv layer of the third up sampling.
+Each fusion follows by an interpolation layer, a gconv layer to reduce the channel back to 32, a skip connection concatenate layer and another gconv layer to reduce the channel back to 32.
+After the fourth fusion, a gconv layer used for channel reduction, 2 standard conv layer for output prediction.
+
+\begin{sidewaysfigure}[th]
+	\centering
+	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
+	\caption{The architecture of TriGNet}
+	\label{fig:albedo-gated-archi}
+\end{sidewaysfigure}
 

### 2022-07-17 workspace/train.py
upload an2 model

@@ -137,12 +137,14 @@ class TrainingModel():
         train_on = self.args.train_on
 
         train_dataset = SyntheticDepthDataset(dataset_path, setname='train')
-        test_dataset = SyntheticDepthDataset(dataset_path, setname='train')
+        # test_dataset = SyntheticDepthDataset(dataset_path, setname='selval')
+        test_dataset = train_dataset
         # Select the desired number of images from the training set
         if train_on != 'full':
             import random
             training_idxs = np.array(random.sample(range(0, len(train_dataset)), int(train_on)))
             train_dataset.training_case = train_dataset.training_case[training_idxs]
+            test_dataset.training_case = test_dataset.training_case[5]
         print("test case number: " + str(test_dataset.training_case.shape))
         # test_dataset.training_case = test_dataset.training_case[:3]
         train_data_loader = DataLoader(train_dataset,

### 2022-07-18 paper/akweury/document.tex
upload an2 model
change loss

--- 2022-07-15 paper/akweury/document.tex
@@
 \usetikzlibrary {positioning}
-
+\subimport{./layers/}{init}
 \newcommand{\bn}{\textbf{n}}
@@
 
+\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
+\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
+\def\PoolColor{rgb:red,1;black,0.3}
+\def\DcnvColor{rgb:blue,5;green,2.5;white,5}
+\def\SoftmaxColor{rgb:magenta,5;black,7}
+\def\SumColor{rgb:blue,5;green,15}
+\def\poolsep{1}
+
 \begin{document}
 
-\section{Guided normal inference using GCNN}
+\section{Guided Gated Convolution Neural Network for Normal Inference }
 
-\subsection{Intrinsic image decomposition}
-Intrinsic image model was introduced by \cite{intrinsic-image}.
-It interprets that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
-\[ I =R  \odot S\]
-It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
-%% insert a image for decompositions
-\begin{figure}[th]
-	\centering
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
-	\decoRule	
-	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
-	\label{fig:intrinsic-image}
-\end{figure}
+\subsection{Light Net Evaluation}
 
-The equation can be further decomposed based on different surface models.
-If assume the object surfaces are Lambertian surfaces, i.e.
-the surface which reflect light in all directions, the shading image can be decomposed as the product of the  radiance of  incoming light $ L_0 $, the cosine of the angle of incidence, which is the dot product of the surface normal $ N $ and the light source direction $ L $.
-\[ I = \rho  \odot ( L_0 \textbf{L} \cdot  \textbf{N}) \]
-note that the surface normal $ N $ and light direction $ L $ are unit vectors thus they have only two degrees of freedom.
+We evaluate the light net on the test dataset for light inpainting task.
+A qualitative evaluation of light net is shown in Figure \ref{fig:eval-light}.
+The average angular error are lower than $ 0.3 $ degree on all of test cases.
+In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.
+Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases.
+The loss is mainly below
 
@@
 	\centering
-	\begin{tikzpicture} 
-		% reference lines
-		\coordinate (light) at (-1,3);
-		\coordinate (p) at (2,0);
-		\coordinate (normal) at (2,3);
-		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
-		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
-		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
-		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
-		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
-		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
-		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
-	\end{tikzpicture}
-	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
-	\label{fig:lambertian-surface}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
+
+	\caption{Qualitative evaluation of light net on Sphere, bus and Washington statue.
+From left to right, grayscale image, semi-dense light map(input), full-dense light map(output), full-dense light map(ground-truth), error map.}
+	\label{fig:eval-light}
 \end{figure}
-
-The equation can be further rearranged as follows
-\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
-The shape from shading method employed the equation mentioned above to predict the both surface albedo $ \rho $ and the normal $ \textbf{N} $ with knowning light source direction $ \textbf{L} $.
-More specifically, a set of $ k $ image for the same scene have been captured based on different light projections.
-Then, for each pixel $ (x,y) $ in the image, an equation system can be set up
-
-\[ 
-\begin{pmatrix}
-	L_1^T \\
-	L_2^T \\
-	\cdots \\
-	L_k^T
-\end{pmatrix} g(x,y) = 
-\begin{pmatrix}
-	I_1(x,y) \\
-	I_2(x,y) \\
-	\cdots \\
-	I_3(x,y)
-\end{pmatrix}
-\]
-for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
-The equation can be solved based on least square methods. 
-Since normal $ N(x,y) $ is unit vector, thus we have
-
-\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]
-
-Then the normal can be obtained as follow
-
-\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]
-
-In another word, the surface normal including the albedo can be obtained directly based on images and light directions.
-
-\subsection{Light Map}
-The light map $ L $ can be derived from vertex map and the light source position.
-As shown in Figure \ref{fig:lambertian-surface}, the incoming light direction is a vector point from light source to the surface point, therefor it can be calculated as follows
-\begin{equation}\label{light-direction}
-	\begin{array}{ll}
-		L(x,y)&= \frac{V(x,y)-(s_x,s_y)}{\|V(x,y)-(s_x,s_y)\|_2}\\ 
-	\end{array}
-\end{equation}
-where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space.
-The light direction map $ L $ is normalized since only the direction of the light is considered.
-The light map is a matrix corresponding the light direction of whole image where each pixel corresponding with each other, thus it has the same size as the vertex map.
-
-It is important to note that due to the exist noise in the vertex map, the getting light map is only semi-dense, as shown in Figure \ref{fig:light-input}.
 
@@
 	\centering
-	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
-	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_light_input.png}}
-	\decoRule	
-	\caption{The light map calculated from vertex map and the light source}
-	\label{fig:light-input}
+	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
+	\caption{The evaluation on 100 test cases of Light Net.}
+	\label{fig:scatter-light}
 \end{figure}
 
-In order to ease this issue, a light inpainting model has been trained based on the GCNN network. It takes the semi-dense light map as input and predict the fully dense light map.
+\begin{table}[th]
 
+	\centering
+	\begin{tabular}{l l l}
+		\toprule
+		\tabhead{Model} & \tabhead{Angle Error /degree} & \tabhead{Time /ms}\\
+		\midrule
+		LightNet  & 0.17  & 4.72 \\ 
+		\hline
+		GCNN  & 9999 & 9999 \\
+		\hline
+		Trignet  & 9999 & 9999 \\
+		\hline
+		Trignet  & 9999 & 9999 \\
+		\bottomrule\\
+	\end{tabular}
+	\caption{The error of models. The angle error is the average angle error of all valid pixels in the test case. The time unit is millisecond.}
+	\label{tab:model-error}
+\end{table}
+
+\subsection{comparison}
+From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
+It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
+Then it counts the number of points locates in each section for 3 axes.
+The 3 axes are fitted quit well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
+Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
+
+It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
 \begin{figure}[th]
 	\centering
-	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
-	\begin{tikzpicture}
-		%% -------------------------------------- parameters ------------------------------------------------
-		\pgfmathsetmacro{\vdist}{0.4}
-
-		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
-		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3
-
-		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
-		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}
-
-		%% 	d_in							3x512x512
-		%%	dconv1: 	d_in-->x1 			32x512x512
-		\pgfmathsetmacro{\disttimes}{1}	%% width 32
-		\pgfmathsetmacro{\yshift}{1}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
-		\pgfmathsetmacro{\yschift}{-1}
-
-		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
-
-		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};
-
-		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
-		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);
-
-		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
-		\pgfmathsetmacro{\yschift}{-1}
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
-\end{tikzpicture}
-
-\caption{Light Net for light inpainting based on GCNN architecture.}
-\label{fig:light-net-archi}
+	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
 \end{figure}
 
-\subsection{Light and image guided normal inference using GCNN}
-Based on above implementations, we propose a Triple Gated Convolutional Neural Network (TriGNet) to perform guided normal inference.
-The structure is shown in Figure \ref{fig:albedo-gated-archi}.
-As shown in the name, the network is constructed based on three GCNN architectures: Image GCNN, Light GCNN, and Vertex GCNN.
-
 \end{document}

### 2022-07-18 paper/main.tex
update ag
change loss

@@
 \usepackage{amssymb}
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles \left( APA)
 
@@
 \usepackage{multirow}
+\usepackage{pdfpages}
+\usepackage{rotating}
 \usetikzlibrary{fit}
+\usetikzlibrary{calc,patterns,angles,quotes}
 \usetikzlibrary {arrows.meta,graphs,shapes.misc}
@@
 
+\subimport{./layers/}{init}
+
 \newcommand{\bn}{\textbf{n}}
 \newcommand{\tabhead}[1]{\textbf{#1}}
+
+\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
+\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
+\def\PoolColor{rgb:red,1;black,0.3}
+\def\DcnvColor{rgb:blue,5;green,2.5;white,5}
+\def\SoftmaxColor{rgb:magenta,5;black,7}
+\def\SumColor{rgb:blue,5;green,15}
+\def\poolsep{1}
+
 %----------------------------------------------------------------------------------------

### 2022-07-19 paper/akweury/document.tex
update new model and new dataset

@@
 
-We evaluate the light net on the test dataset for light inpainting task.
+We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.
+
 A qualitative evaluation of light net is shown in Figure \ref{fig:eval-light}.
@@
 In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.
-Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases.
-The loss is mainly below
 
@@
 
+Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases.
+The average pixel-wise angular error is 0.17 degree as shown in Table \ref{tab:model-error}.
+An regression line has been added in the plot to analysis the tendency of the errors.
+The angular error slightly goes up when valid point number in the scene increase.
+It is make sense since the valid pixels are usually connected and concentrate in a single patch, the less of the area of the patch, which corresponding the number of the valid points, the less variation of the light direction among the pixels, thus better the evaluation.
+
 \begin{figure}[th]
@@
 
+\subsection{Trignet Net Evaluation}
+
+The qualitative evaluation of Trignet uses the model trained based on masked L2 loss.
+
+\subsubsection{title}
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
+
+	\caption{Qualitative evaluation of Trignet net on Sphere, bus and Washington statue.
+From left to right, semi 3D vertex map, full-dense normal map(output), full-dense normal map(ground-truth), error map.}
+	\label{fig:eval-trignet}
+\end{figure}
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
+	\caption{The evaluation on 100 test cases of Trignet.}
+	\label{fig:scatter-trignet}
+\end{figure}
+
+\subsection{comparison}
+From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
+It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
+Then it counts the number of points locates in each section for 3 axes.
+The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
+Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
+
+It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
+\end{figure}
+
 \begin{table}[th]
@@
 		\toprule
-		\tabhead{Model} & \tabhead{Angle Error /degree} & \tabhead{Time /ms}\\
+		\tabhead{Model} & \tabhead{L2} & \tabhead{Time /ms}\\
 		\midrule
@@
 
-\subsection{comparison}
-From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
-It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
-Then it counts the number of points locates in each section for 3 axes.
-The 3 axes are fitted quit well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
-Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
-
-It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
-	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
-The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
-(The chart is based on the "dragon" scene showing above)}
-	\label{fig:normal-histo-diff}
-\end{figure}
-
 \end{document}

### 2022-07-19 common/VI5Net.py

@@ -1,0 +1,150 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+
+from common.Layers import GConv
+
+
+class VI5Net(nn.Module):
+    def __init__(self, in_ch, out_ch, channel_num):
+        super().__init__()
+
+        kernel_down = (3, 3)
+        kernel_up = (3, 3)
+        padding_down = (1, 1)
+        padding_up = (1, 1)
+        stride = (1, 1)
+        stride_2 = (2, 2)
+
+        channel_size_1 = channel_num
+        channel_size_2 = channel_num * 2
+        channel_size_3 = channel_num * 2
+        # https://homepages.inf.ed.ac.uk/rbf/CVonline/LOCAL_COPIES/PIRODDI1/NormConv/node2.html#:~:text=The%20idea%20of%20normalized%20convolution,them%20is%20equal%20to%20zero.
+        self.dconv1 = GConv(in_ch, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv2 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv4 = GConv(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
+
+        # self.l_dconv1 = GConv(in_ch, channel_size_1, kernel_down, stride, padding_down)
+        # self.l_dconv2 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        # self.l_dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        # self.l_dconv4 = GConv(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
+
+        self.i_dconv1 = GConv(1, channel_size_1, kernel_down, stride, padding_down)
+        self.i_dconv2 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.i_dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
[…]

### 2022-07-19 eval_visual.py

@@ -50,7 +50,7 @@ def preprocessing(models):
     elif args.data == "synthetic":
         path = config.synthetic_data / args.datasize / "selval" / "tensor"  # key tests 103, 166, 189,9
     elif args.data == "real":
-        path = config.real_data / "tensor"  # key tests 103, 166, 189,9
+        path = config.real_data / "selval" / "tensor"  # key tests 103, 166, 189,9
     elif args.data == "paper":
         path = config.paper_pic
     else:
@@ -425,10 +425,12 @@ if __name__ == '__main__':
 
     models = {
         # "SVD": None,
-        "light": config.ws_path / "light" / "trained_model" / "512" / "checkpoint.pth.tar",  # image guided
+        # "light": config.ws_path / "light" / "trained_model" / "512" / "checkpoint.pth.tar",  # image guided
         # "albedoGated": config.ws_path / "albedoGated" / "trained_model" / "512" / "checkpoint.pth.tar",
         # "an": config.ws_path / "an" / "trained_model" / "512" / "checkpoint.pth.tar",
-        # "GCNN3-32-512": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32.pth.tar",
+        "TrignetBerhu": config.ws_path / "an2" / "trained_model" / "512" / "checkpoint-berhu.pth.tar",
+        "TrignetL2": config.ws_path / "an2" / "trained_model" / "512" / "checkpoint-l2.pth.tar",
+        "GCNN3-32-512": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32.pth.tar",
         # "GCNN3-32-512-2": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32-2.pth.tar",
         # "GCNN3-64-512": config.ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-64.pth.tar",
 

### 2022-07-19 workspace/vi5/network.py

@@ -1,0 +1,64 @@
+import sys
+from os.path import dirname
+
+sys.path.append(dirname(__file__))
+import torch
+import torch.nn as nn
+from common.ResNormalGuided import NormalGuided
+from common.AlbedoGatedNNN import GNet
+import config
+from help_funs import mu
+
+
+# from common.NormalizedNNN import NormalizedNNN
+
+class CNN(nn.Module):
+    def __init__(self, channel_num):
+        super().__init__()
+        # self.__name__ = 'albedoGated'
+        self.channel_num = channel_num
+        # self.light_net = NormalGuided(3, 3, channel_num)
+        self.g_net = GNet(3, 3, channel_num)
+        # self.remove_grad()
+
+    def remove_grad(self):
+        for param in self.light_net.parameters():
+            param.requires_grad = False
+
+    def init_net(self):
+        light_source_net = NormalGuided(3, 3, self.channel_num)
+        light_checkpoint = torch.load(config.light_3_32)
+
+        light_source_net.load_state_dict(light_checkpoint['model'].light3_3.state_dict())
+        light_source_net_dict = light_source_net.state_dict()
+        light_net_dict = self.g_net.state_dict()
+
+        light_source_net_dict = mu.change_light_dict_name(light_source_net_dict, light_net_dict, "l_")
+
+        light_source_net_dict = {k: v for k, v in light_source_net_dict.items() if
+                                 k in light_net_dict and v.size() == light_net_dict[k].size()}
+
+        light_net_dict.update(light_source_net_dict)
+        self.g_net.load_state_dict(light_net_dict)
+
+        normal_source_net = NormalGuided(3, 3, self.channel_num)
+        normal_checkpoint = torch.load(config.gcnn_3_32)
+        normal_source_net.load_state_dict(normal_checkpoint['model'].nconv3_3.state_dict())
+        normal_source_net_dict = normal_source_net.state_dict()
+        normal_net_dict = self.g_net.state_dict()
+        normal_source_net_dict = {k: v for k, v in normal_source_net_dict.items() if
+                                  k in normal_net_dict and v.size() == normal_net_dict[k].size()}
+        normal_net_dict.update(normal_source_net_dict)
+        self.g_net.load_state_dict(normal_net_dict)
+
+    def forward(self, x):
+        # x0: vertex array
+        x_vertex = x[:, :3, :, :]
+        x_img = x[:, 3:4, :, :]
[…]

### 2022-07-23 paper/Chapters/Chapter05.tex
change loss
update vil args

@@
 
-%% resng
 \section{Guided Gated Convolution Neural Network for Normal Inference }
 
-The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}.
-With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.
+\subsection{Light Net Evaluation}
 
-\section{Guided Gated Convolution Neural Network for Normal Inference }
+We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.
 
+A qualitative evaluation of light net is shown in Figure \ref{fig:eval-light}.
+The average angular error are lower than $ 0.3 $ degree on all of test cases.
+In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
+
+	\caption{Qualitative evaluation of light net on Sphere, bus and Washington statue.
+From left to right, grayscale image, semi-dense light map(input), full-dense light map(output), full-dense light map(ground-truth), error map.}
+	\label{fig:eval-light}
+\end{figure}
+
+Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases.
+The average pixel-wise angular error is 0.17 degree as shown in Table \ref{tab:model-error}.
+An regression line has been added in the plot to analysis the tendency of the errors.
+The angular error slightly goes up when valid point number in the scene increase.
+It is make sense since the valid pixels are usually connected and concentrate in a single patch, the less of the area of the patch, which corresponding the number of the valid points, the less variation of the light direction among the pixels, thus better the evaluation.
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
+	\caption{The evaluation on 100 test cases of Light Net.}
+	\label{fig:scatter-light}
+\end{figure}
+
+\subsection{Vertex-Image-Light Net (VIL Net) Evaluation}
+
+The qualitative evaluation of VIL net uses the model trained based on masked L2 loss.
+
+\subsubsection{title}
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
+
+	\caption{Qualitative evaluation of Trignet net on Sphere, bus and Washington statue.
+From left to right, semi 3D vertex map, full-dense normal map(output), full-dense normal map(ground-truth), error map.}
+	\label{fig:eval-trignet}
+\end{figure}
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
+	\caption{The evaluation on 100 test cases of Trignet.}
+	\label{fig:scatter-trignet}
+\end{figure}
+
+\subsection{comparison}
 From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
@@
 Then it counts the number of points locates in each section for 3 axes.
-The 3 axes are fitted quit well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
+The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
 Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
@@
 It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
-\begin{figure}[h!]
+\begin{figure}[th]
 	\centering
@@
 
-\newpage 
-\section{model comparison}
-This section evaluates the proposed models with the neighbor-based model and make comparison with each other.
+\begin{table}[th]
+
+	\centering
+	\begin{tabular}{l l l l l l l l }
+		\toprule
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.} & over-perform\\
+		\midrule
+		LightNet  & 0.17  & 4.72 & &  & & & \\ 
+		\hline
+		GCNN  & 10.57 & 5.25 & 8 & 200,1600 & 0.5 & 0 & - \\
+		\hline
+		an3 & 10.46 & 64.86 & 8 & 3,12,1000  & 0.5 & 1 & yes\\
+		\hline
+		an3 & 10.81 & 65.34 & 8 & 10,1000  & 0.5 & 1 & no(yes) \\
+		\hline
+		VIL-1 & 10.50 & 31.57 & 8 & 10,1000 & 0.5 & 1 & yes \\
+		\hline
+		VIL-1 & 10.82 & 32.61 & 8 & 3,12,1000 & 0.5 & 1 & no(yes) \\
+		\hline
+		VIL-3  & 10.79 & 54.76 & 8 & 100,1000 & 0.1 & 3 & no(yes) \\
+		\hline
+		VIL-10  & 11.10 & 132.32 & 8 & 100,1000 & 0.1 &10 & no(yes)\\
+		\bottomrule\\
+	\end{tabular}
+	\caption{The error of models.
+The angle error is the average angle error of all valid pixels in the test case.
+The time unit is millisecond.
+bz is the batch size, lr-schedule is learning rate schedule.
+lr-df is learning rate decay factor, l/i.
+Nr is the number of light-image maps used for each scene}
+	\label{tab:model-error}
+\end{table}
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=\linewidth]{./Figures/regression-comparison.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
+\end{figure}

### 2022-07-23 paper/akweury/document.tex
update args
update vil args

--- 2022-07-18 paper/akweury/document.tex
@@
 
-\section{Guided Gated Convolution Neural Network for Normal Inference }
+\subsection{VIL Net}
+Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net). 
+The structure is shown in Figure \ref{fig:albedo-gated-archi}. As mentioned in the name, the network utilizes vertex map, light map and image map to accomplish the normal inference task.
 
-\subsection{Light Net Evaluation}
+The network can be consider in two parts.
+The first part is the image and light map feature encoder, which is identify to the downsampling part of the GCNN architecture.
+It takes the concatenated image and light map as input, thus the input has 4 channels.
+Then the network down sampling three times to predict the feature map of the image and light map.
+The output of this part is the output of third gated convolution layer in the third down-sampling.
+The second part is basically identify to the original GCNN architecture, but before the start of upsampling part, 2 extra layers are added.
+First, a concatenate layer is added to fuse the vertex feature and the image and light map feature getting from encoder.
+Second, a gated convolution layer is added to reduce the channels fit to the following architecture.
+The rest part of the network is identify to the original GCNN.
 
-We evaluate the light net on the test dataset for light inpainting task.
-A qualitative evaluation of light net is shown in Figure \ref{fig:eval-light}.
-The average angular error are lower than $ 0.3 $ degree on all of test cases.
-In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.
-Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases.
-The loss is mainly below
+The network concatenate the image and the light together
 
-\begin{figure}[th]
+\subsection{An3 Net}
+The first branch (shown above) takes a light map introduced in \ref{sec:lightmap} as the input, the structure is the same as GCNN architecture except that the last two standard convolution layers, the skip connections are kept to connect the 3 down/up samplings.
+The second branch (shown below) takes image as the input, the structure is the same as the first branch other than the input image is 1 channel but not 3 channels. 
+The third branch takes the 3D vertex map as the input.
+The structure is based on GCNN architecture.
+However, in order to merge the other two branches, the vertex branch equips 4 times fusions in the up sampling part.
+Specifically, the first fusion locates immediately after the last gconv layer of the last down sampling, the second fusion after the second gconv layer of first up sampling, the third fusion after the second gconv layer of second up sampling, the fourth fusion after the second gconv layer of the third up sampling.
+Each fusion follows by an interpolation layer, a gconv layer to reduce the channel back to 32, a skip connection concatenate layer and another gconv layer to reduce the channel back to 32.
+After the fourth fusion, a gconv layer used for channel reduction, 2 standard conv layer for output prediction.
+
+\begin{sidewaysfigure}[th]
 	\centering
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
+	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
+	\caption{The architecture of TriGNet}
+	\label{fig:albedo-gated-archi}
+\end{sidewaysfigure}
 
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
-
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
-
-	\caption{Qualitative evaluation of light net on Sphere, bus and Washington statue.
-From left to right, grayscale image, semi-dense light map(input), full-dense light map(output), full-dense light map(ground-truth), error map.}
-	\label{fig:eval-light}
-\end{figure}
-
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
-	\caption{The evaluation on 100 test cases of Light Net.}
-	\label{fig:scatter-light}
-\end{figure}
-
-\begin{table}[th]
-
-	\centering
-	\begin{tabular}{l l l}
-		\toprule
-		\tabhead{Model} & \tabhead{Angle Error /degree} & \tabhead{Time /ms}\\
-		\midrule
-		LightNet  & 0.17  & 4.72 \\ 
-		\hline
-		GCNN  & 9999 & 9999 \\
-		\hline
-		Trignet  & 9999 & 9999 \\
-		\hline
-		Trignet  & 9999 & 9999 \\
-		\bottomrule\\
-	\end{tabular}
-	\caption{The error of models. The angle error is the average angle error of all valid pixels in the test case. The time unit is millisecond.}
-	\label{tab:model-error}
-\end{table}
-
-\subsection{comparison}
-From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
-It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
-Then it counts the number of points locates in each section for 3 axes.
-The 3 axes are fitted quit well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
-Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
-
-It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
-	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
-The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
-(The chart is based on the "dragon" scene showing above)}
-	\label{fig:normal-histo-diff}
-\end{figure}
+\subsection{Loss Function}
+For the case of normal output, the loss function is the same as Mask-L2 loss as introduced in \ref{par:maskl2}.
+For the case of the product of albedo and normal, the loss function utilized a scaled Mask-L2 loss, which gives the range of inliers between $ [0,255] $.
 

### 2022-07-23 paper/akweury/document.tex
fix a bug

@@
 
-The network concatenate the image and the light together
+With the help of an extra image-light encoder, the network gained more information of the object surface, which is supposed to predict the surface normal more accurate.
+In this scenario, the output is still the surface normal, thus the training loss can be the same as GCNN model.
 

### 2022-07-23 workspace/train.py

@@ -688,7 +688,7 @@ def main(args, exp_dir, network, train_dataset):
         if epoch % nn_model.args.print_freq == nn_model.args.print_freq - 1:
             test_epoch(nn_model, epoch)
 
-        if np.isnan(np.sum(loss[:3, epoch])) or loss > 1e+4:
+        if np.isnan(np.sum(loss[:3, epoch])) or np.sum(loss[:3, epoch]) > 1e+4:
             break
 
 

### 2022-07-23 paper/akweury/document.tex
add evaluation dataset

@@
 The network can be consider in two parts.
-The first part is the image and light map feature encoder, which is identify to the downsampling part of the GCNN architecture.
-It takes the concatenated image and light map as input, thus the input has 4 channels.
-Then the network down sampling three times to predict the feature map of the image and light map.
-The output of this part is the output of third gated convolution layer in the third down-sampling.
-The second part is basically identify to the original GCNN architecture, but before the start of upsampling part, 2 extra layers are added.
+The first part extracts the feature map encoders.
+It deals with two kinds of input, the vertex map $ X_1 \in \mathbb{R}^{w\times h\times3}$ and the concatenation of light and image map $ X_2 \in \mathbb{R}^{w\times h\times4} $.
+The network extracts the geometry features $ X_v $ from vertex map $ X_1 $ (represented as a regression function v)
+\[ v: X_1 \rightarrow X_v \]
+meanwhile, the network extracts the photometric features $ X_l $ from image and the light map $ X_2 $ (represented as a regression function $ l $)
+\[ l: X_2 \rightarrow X_l \]
+where the two encoders have the same network architecture based on GCNN model.The second part is basically identify to the original GCNN architecture, but before the start of upsampling part, 2 extra layers are added.
 First, a concatenate layer is added to fuse the vertex feature and the image and light map feature getting from encoder.
-Second, a gated convolution layer is added to reduce the channels fit to the following architecture.
-The rest part of the network is identify to the original GCNN.
+Second, a fused feature map is predicted from all the feature maps base on a single gated convolution layer. (represented as a regression function $ m $)
+\[ m: [X_v X_l] \rightarrow X_f \]
+Then the network interpolates the feature maps $ X_f $ using 3 times upsamling with gated convolution layers.
+Meanwhile, the skip connections from UNet have been kept.
+Thus the feature maps $ X_{df_1, df_2, ...} $ of each down-sampling time in the regression model $ v $ are considered in the upsamling part.
+\[ n: X_f, X_{df_1, df_2, ...} \rightarrow N \]
 

### 2022-07-23 paper/main.tex
add evaluation dataset

@@
 
-\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
+\begin{notations}{ll} % Include a list of abbreviations (a table of two columns)
 
-\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
-\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\
+\textbf{I} & Grayscale Image Matrix (Height $ \times $ Width $ \times $ 1)\\
+\textbf{L} & Light Map Matrix (Height $ \times $ Width $ \times $ 3)\\
+\textbf{N} & Normal Map Matrix (Height $ \times $ Width $ \times $ 3)\\
+\textbf{V} & Vertex Map Matrix (Height $ \times $ Width $ \times $ 3)\\
 
-\end{abbreviations}
+\textbf{X} & Input Matrix (Height $ \times $ Width $ \times $ Channels)\\
+\textbf{Y} & Output Matrix (Height $ \times $ Width $ \times $ Channels)\\
+
+\textbf{w} & Width of Matrix\\
+\textbf{h} & Height of Matrix\\
+
+\end{notations}
 
@@
 
-\begin{symbols}{lll} % Include a list of Symbols (a three column table)
+\begin{operations}{ll} % Include a list of Symbols (a three column table)
 
-$a$ & distance & \si{\meter} \\
-$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
+$[A B]$ & concatenation between A and B \\
+$\oplus$ & element-wise multiplication \\
+$\cdot$ & dot product \\
 %Symbol & Name & Unit \\
@@
 
-\end{symbols}
+\end{operations}
 

### 2022-07-23 eval.py

@@ -87,17 +87,19 @@ if __name__ == '__main__':
 
     models = {
 
-        # "an3-3-12-1000": config.paper_exp / "an3" / "checkpoint-l1-3-12-1000.pth.tar",
+        # "an3-3-12-1000": config.paper_exp / "an3" / "checkpoint-l1-3-12-1000-3.pth.tar",
+        # "an3-3-12-1000": config.paper_exp / "an3" / "checkpoint-l1-3-12-1000-2.pth.tar",
         # "an3-10-1000": config.paper_exp / "an3" / "checkpoint-l1-10-1000.pth.tar",
 
+        # "vil-10-1000": config.paper_exp / "vil10" / "checkpoint-l1-10-1000.pth.tar",
         # "vil-10-1000": config.paper_exp / "vil10" / "checkpoint-l1-10-1000.pth.tar",
         # "vil-3-12-1000": config.paper_exp / "vil10" / "checkpoint-l1-3-12-1000.pth.tar",
 
         # "vil3-100-1000": config.paper_exp / "vil10" / "checkpoint-l3-100-1000.pth.tar",
         # "vil10-100-1000": config.paper_exp / "vil10" / "checkpoint-l10-100-1000.pth.tar",
 
-        "GCNN-b8": config.paper_exp / "gcnn" / "checkpoint-b8.pth.tar",
-        "GCNN-3-12-1000": config.paper_exp / "gcnn" / "checkpoint-3-12-1000.pth.tar",
+        "GCNN-b8": config.paper_exp / "gcnn" / "checkpoint-1662.pth.tar",
+        # "GCNN-3-12-1000": config.paper_exp / "gcnn" / "checkpoint-3-12-1000.pth.tar",
         # "GCNN-b32": config.paper_exp / "gcnn" / "checkpoint-b32.pth.tar",
         # "SVD": None,
 

### 2022-07-24 paper/akweury/document.tex
fix a bug

@@
 
+The normal inference task estimate the surface normal of a 3D object.
+There are two main approach to solve the task.
+Geometry based approach estimate the surface normal of an object based on the geometry principle.
+Point cloud is a common surface geometry information which samples the surface point position in 3D space.
+Another approach is photometric stereo based approach, which utilizes a set of images under different illumination conditions.
+In this chapter, geometry and photometric stereo based approach are introduced separately, then a deep learning based approach using geometry information is proposed.
+In the end, as the main work of the thesis, another deep learning method is proposed based on both geometry and photometric stereo information.
+
+\section{Geometry based normal estimation}
+
+\subsection{Approach}
+The geometry based normal estimation uses point cloud of the object surface as input.
+Given a structured point cloud $ V^{W\times H\times 3} $ to estimate the normal map  $ N^{W\times H \times 3} $, where each normal  $ \textbf{n}^{3\times 1} $ at point $ \textbf{v}^{3\times 1} \in N $ is a unit vector with its direction point outward of the surface and perpendicular to the tangent plane of the surface at point $ \textbf{p}^{3\times 1} $.
+
+The idea behind the neighbor based method is to fit a plane $ \Pi $ using the $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of the point $ \textbf{p} $, calculate the normal  $ \tilde{\textbf{n}} $ of the plane.
+
+It is under the assumption that the point and its neighbors are located in the same plane.
+This is usually not hold for the most of the surface, but if $ k $ in a suitable scale and point cloud is dense enough, it is enough to get an accurate and sharp result.
+As shown in Figure \ref{fig:svd-normal}.
+
+Specifically, it is not necessary to find the exact plane equation to solve the normal. Instead, the normal can be derived based on an equation system. 
+The normal $ \tilde{\textbf{n}} $ of plane $ \Pi $ is perpendicular to all the vector on the plane $ \Pi $, we can construct $ k $ vectors on plane $ \Pi $ use  $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of point $ \textbf{p} $.
+For the simplicity, we can choose $ \textbf{p}_1 $ as the base point, then $ k-1 $ vectors can be construct as follows
+\begin{equation}
+	\begin{array}{rr}
+		\displaystyle \textbf{v}_i = \textbf{p}_1 - \textbf{p}_i & \text{for}\ i= 2,...,k \\
+	\end{array}
+\end{equation}
+and each of them satisfied $ \textbf{v}_i \cdot \tilde{\textbf{n}} = 0$. Then, the equation system can be constructed as 
+\begin{equation}{\label{eq:normal-overdetermined-equation}}
+	A \cdot \textbf{n} = 0
+\end{equation}
+where $ A \in \mathbb{R}^{(k-1)\times 3} $ is the vector matrix vertically stacked by $ \textbf{v}_1, ..., \textbf{v}_{k-1} $.
+In order to avoid trivial solution, one more constraint should be added
+\[ \|  \bn_{3 \times 1} \|_2^2 = 1  \]
+which also let the normal to be a unit vector.
+
+To calculate a valid normal, at least 3 points are required to construct, i.e.
+$ k>=3 $.
+For the sake of robust, more points can be used to reduce the measuring error.
+For the case $ k>3 $, since the surface vectors are actually not in the same plane, the equation system is likely over-determined .
+Then the equation system mentioned above can be converted to follow optimization problem
+\begin{equation}
+	\begin{array}{rrclcl}
+		\displaystyle \min & \multicolumn{3}{l}{\| A  \bn \|^2} \\
+		\\
+		\textrm{s.t.} & \| \bn \|^2 & = & 1 
+	\end{array}
+\end{equation}
+which can be solved by singular value decomposition(SVD). Let the decomposition of 
+\[ A=U\Sigma V^T \]
+The solution i.e. normal is the last column of $ V $.
+
+At last, all the normals should point ot view point $ \textbf{s} $, thus the direction of a normal should be inverted if 
+\begin{equation}\label{eq:normal-invertion}
+	\textbf{n} \cdot (\textbf{p}  - \textbf{s}) > 0
+\end{equation}
+
+Repeat the procedure for all the points in the point cloud to get the entire normal map.
+
+\subsection{Evaluation}
+The neighbor based method can predict the normal map in a good way when the given point cloud is dense, as shown in Figure \ref{fig:svd-normal}.
+It can successfully predict the smooth surface of the dragon object, especially the flakes and the tails of the dragon.
+
+However, it failed in the areas such as hindleg, horn and the mouth, which consists mainly by sharp edges.
+This is because the neighbors points in these area do not hold the assumption of coplanarity well, the normals of these neighbors can be very different.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
+	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
+	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}
+
+	\label{fig:svd-normal}
+	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5 \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
+\end{figure}
+The neighbor based method is depended on a well-chosen parameter $ k $.
+Figure \ref{fig:svd-k-eval} shows the evaluation on different $ k $ values.
+When $ k=1 $, the average error of the whole image is the lowest one, most of the normals are close to the ground-truth but the outline edges, which are the areas that surface normal changed extremely sever.
+For the case $ k=2 $, the sharp edges are more smooth and cause more error, like the eyes area of the dragon.
+Compare to the first case, the outline edge error goes better.
+Most of the edge errors are reduced when $ k=2 $, since more neighbor points join the evaluation and it reduces the effect of outliers.
+However, for the area of horn outline, hindleg outline, the error goes worse.
+In this case, most of the neighbors of these points are outliers and thus failed this approach.
+$ k=3 $ and $ k=4 $ further increase the angle errors based on $ k=2 $.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
+	\label{fig:svd-k-eval}
+	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
+\end{figure}
+
+The performance of neighbor based method is good enough for a well chosen $ k $, and it can be further improved by simply use different $ k $ for different area prediction.
+However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor selection and also reduce the number of possible neighbors of each point for a fixed $ k $.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
+	\label{fig:svd-noise}
+	\caption{Evaluation of neighbor based method on a noised dragon model}
+\end{figure}
+
+% ---------------------- gated convolution neural network ------------------------
+\section{Gated Convolution neural network for surface normal estimation}
+\label{gcnn}
+
+Recently, deep learning based method achieved a great succeed for image processing.
+( \cite{yolov3}, \cite{efficientDet}) These network architectures use a batch of RGB / Grayscale images as input and are employed for classification problems.
+Usually, the images are convoluted with a convolution layer and downsampling with pooling layers.
+The outputs of the network consist of a single value to represent the index of the corresponding class (\cite{efficientDet}) or with a set of values to represent the position of bounding boxes.(\cite{yolov3}).
+However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
+Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
+In this case, the traditional network architecture is not suitable anymore.
+
+%% upsampling 
+It is worth to noticed that, the output of normal inference CNN model is not one or several labels but an entire image or normal map with same size. 
+%% talk about image upsampling, unet
+Recently,\cite{unet} proposed an architecture called UNet for biomedical image segmentations.
+The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size.
+The proposed network can successfully assigned each pixel a class for segmentation tasks.
+Under this symmetric network, an input image is downsampled 4 times and upsampled 4 times.
+Output image has exactly the same size as input image.
+The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.8\textwidth]{./Figures/u-net-illustration-correct-scale2.pdf}
+	\label{fig:u-net}
+	\caption{The structure of UNet. \cite{unet}}
+\end{figure}
+
+The UNet is based on standard convolution layers to construct the network. This is reasonable for image processing task with full-dense input, since no missing pixels exist. 
+However, for the input of noised point cloud, the valid and invalid pixels will be treated equally if we still perform standard convolution layers.
+Since the aim of the network is not learning the pattern of noise, but the noise with eternally changing patterns will confuse the network, and it fails the normal inference, a mask is required to distinguish two kinds of pixels.
+
+% why we need a mask
+\cite{pncnn0} use binary mask to indicate valid pixels, and further use normalized convolution to predict the output. The normalized convolution is shown as follows
+
+\begin{equation}
+	\begin{array}{rrclcl}
+		O(x,y) = 
+		\begin{cases}
+			\dfrac{\Sigma_i^k\Sigma_j^k W(i,j) \cdot I(x-i,y-j) \cdot M(x-i,y-j)}{\Sigma_i^k\Sigma_j^k W(i,j) \cdot M(x-i,y-j)}, & \text{if}\ \sum_{i}^k\sum_{j}^k M(i,j)>0 \\
+			0, & \text{otherwise}
+		\end{cases}
+	\end{array}
+\end{equation}
+
+where $ k $ is the kernel size, $ (x,y) $ is the position in input, $ (i,j) $ is the displacement in kenel, $ M $ is the corresponding mask.
+A binary mask uses 1 to indicate valid pixels and 0 otherwise.
+$ \odot $ denotes element-wise multiplication.
+
+Normalized convolution layer added the weight to the mask. However, a initialization for the mask is still required, and the propagation of the mask remain a tricky task.
+
+\subsection{Gated Convolution}
+
+% introduce gconv
+\cite{gated_activation} proposed a gated activation unit to model more complex interactions comparing to standard CNN layers, which mainly inspired by the multiplicative units exist in Long Short-Term Memory proposed by \cite{lstm} and Rated Recurrent Unit (GRU) proposed by \cite{gru}.
+\cite{gconv} employed the same gated unit solving for the free-form image inpainting task. The proposed network use 3 channel RGB images as input and estimate the missing pixels.
+
+The structure is shown in Figure \ref{fig:gconvLayer}.
+Instead of using a mask as input to indicate valid pixels, it employs a standard convolution layers to learn this mask directly from data.
+The valid pixels are then activated by a Sigmoid function.
+Then it imply element-wise multiplication with the feature map.
+Formally, the gated convolution is described as follows, the layer with input size $ (N, C_{in}, H, W) $ and output size $ (N, C_{out}, H_{out}, W_{out}) $:
+\begin{equation}\label{gconv}
+	o(N_i, C_{o_j}) = \sigma(\sum_{k=0}^{C_{in}-1}w_g(C_{o_j}, k) \star i(N_i,k) + b_g(C_{o_j})) * 
+	\phi (\sum_{k=0}^{C_{in}-1}w_f(C_{o_j}, k) \star i(N_i,k) + b_f(C_{o_j}))
+\end{equation}
+where $ \phi $ is LeakyReLU function, $ \sigma $ is sigmoid function, thus the output values are in range $ [0,1] $, $ \star $ is the valid 2D cross-correlation operator, $ N $ is batch size, $ C $ denotes a number of channels, $ H $ is a height of input planes in pixels, and $ W $ is width in pixels, $ w(C_{o_j},k) $ denotes the weight of $ j $-th output channel corresponding $ k $-th input channel, $ i(N_i, k) $denotes the input of $ i $-th batch corresponding $ k $-th input channel, $ b(C_{o_j}) $ denotes the bias of $ j $-th output channel.
+
+% Gated Convolution Layer
+\begin{figure}[th]
+	\centering
+	\begin{tikzpicture}
+		\tikzstyle{rect} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!20]
+		\tikzstyle{arrow} = [thick,->,>=stealth]
+		\node (output) [rect] {Output};
+		\node (oplus) [below of=output, yshift=-.2cm] {$\Huge\oplus $};
+		\node (LeakyReLU) [rect,below of=oplus, yshift=-0.4cm] {Feature};
+		\node (sigmoid) [rect, below of=oplus, yshift=-0.4cm, xshift=-4cm] {Mask};
+
+		\node (conv1) [rect,below of=sigmoid, yshift=-1cm] {Mask};
+		\node (conv2) [rect,below of=LeakyReLU, yshift=-1cm] {Feature};
+		\node (input) [below of=oplus] at (0,-7) {\includegraphics[width=.25\textwidth]{./Figures/train-input.png}};
+
+		\draw [arrow] (oplus) -- (output);
+		\draw [arrow] (sigmoid) |- (oplus);
+		\draw [arrow] (LeakyReLU) -- (oplus);
+		\draw [arrow] (conv2) --  node [text width=2.5cm, midway, right=1em]{LeakyReLU} (LeakyReLU);
+		\draw [arrow] (conv1) --  node [text width=2.5cm, midway, right=1em]{Sigmoid} (sigmoid);
+		\draw [arrow] (input) -|  node [text width=2.5cm, midway, below=1em]{Conv2D} (conv1);
+		\draw [arrow] (input) -- node [text width=2.5cm, midway, right=1em]{Conv2D} (conv2);
+	\end{tikzpicture}
+	\caption{Gated Convolution Layer, where $ \oplus $ denotes element-wise multiplication.}
+	\label{fig:gconvLayer}
+\end{figure}
+
+%\section{Canny Edge Detection for Detail Enhancement}
+%The inaccuracy part is usually concentrate in the coarse surface or drastic changed surface parts of the object.
+The corresponding part can be extracted separately via edge detector algorithms, like Canny Edge detector.
+Feed the edges to a special net for normal prediction might improve the accuracy further.
+
+\subsection{Architecture}
+\label{sec:architecture}
+Based on the implementation mentioned above, the architecture roughly follows on UNet proposed by \cite{unet}, as shown in Figure \ref{fig:gcnn-archi}.
+
+Instead of using pooling layers for down/up samplings, gated convolution layer with stride $ (1,1) $ is used.
+The gated convolution using Sigmoid function for gating layer and LeakyReLU function for feature layer.
+All the layers are gated convolution layer with the exception of last two layers, which instead uses standard convolution layer to scale the output in range $\left[-1, 1\right]$.
+Other than the last two layers which use $ 1\times 1 $ kernels, all the gated convolution layer use $ 3\times 3 $ kernels with $ 1\times1 $ padding.
+
+The input is 3D vertex with size $ 512\times512\times3 $, and output is $ 512\times512\times3 $ normal map, which has the same resolution.
+There are 3 times downsamplings, each scale with 3 gated convolution layers, the third layer has stride 2.
+The upsampling part interpolate the feature maps 3 times with 1 gated convolution layer in each scale.
+
+It keeps the skip connection in UNet to remain the fine detail features.
+
+% GCNN Architecture
+\begin{figure}[!h]
+	\centering
+	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
+	\begin{tikzpicture}
+		%% -------------------------------------- parameters ------------------------------------------------
+		\pgfmathsetmacro{\vdist}{0.4}
+
+		\pgfmathsetmacro{\boxsizea}{3}	%% width 512
+		\pgfmathsetmacro{\boxsizeb}{1.5}	%% width 256
+		\pgfmathsetmacro{\boxsizec}{1}	%% width 128
+		\pgfmathsetmacro{\boxsized}{0.7}	%% width 64
+
+		\pgfmathsetmacro{\boxwidthd}{0.1}	%% width 1
+		\pgfmathsetmacro{\boxwidtha}{0.2}	%% width 3
+		\pgfmathsetmacro{\boxwidthb}{\boxwidtha*1.3}	%% width 32
+		\pgfmathsetmacro{\boxwidthc}{\boxwidtha*3}		%% width 64
+
+		\pgfmathsetmacro{\convwshift}{9}
+		\pgfmathsetmacro{\preprocessingshift}{4}
+		\pgfmathsetmacro{\labelshift}{1.5}
+		\pgfmathsetmacro{\gconvwshift}{0}
+
+		\pgfmathsetmacro{\secrowshift}{-6}
+
+		\pgfmathsetmacro{\convrowstart}{4}
+		\pgfmathsetmacro{\secondrowstart}{4}
+
+		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
+		\definecolor{gconvcolor}{rgb}{0.5,0.7,0.7}
+		\definecolor{convcolor}{rgb}{0.5,0.7,0.3}
+		\definecolor{gconvdilatedcolor}{rgb}{0.6,0,0.3}
+
+		%% ---------------------------------- preprocessing --------------------------------------------
+		%%  img_in 1x512x512
+		\pgfmathsetmacro{\disttimes}{3.5}
+		\pgfmathsetmacro{\yschift}{\preprocessingshift}
+		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
+		{\includegraphics[width=.15\textwidth]{./Figures/train-input.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {3D Vertex};
+
+		\draw [-stealth](1.45,\yschift-1.8) -- (1.45,\yschift-2.6);
+
+		\draw [-stealth]  (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);
+
+		\pgfmathsetmacro{\disttimes}{10}
+		\pgfmathsetmacro{\yschift}{\preprocessingshift}
+		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
+		{\includegraphics[width=.15\textwidth]{./Figures/train-depth-noise}};
+		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {Add Noise};
+
+		\draw [-stealth] (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);
+
+		\pgfmathsetmacro{\disttimes}{16.5}
+		\pgfmathsetmacro{\yschift}{\preprocessingshift}
+		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
+		{\includegraphics[width=.15\textwidth]{./Figures/train-depth.png}};
+		\node[text width=2cm] at (\vdist*\disttimes+0.2,\yschift-1.5) {Depth Map};
+
+		%% ----------------------------------- output normal map -------------------------------------
+		\pgfmathsetmacro{\disttimes}{25}
+		\pgfmathsetmacro{\yschift}{\preprocessingshift}
+		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
+		{\includegraphics[width=.15\textwidth]{./Figures/train-normal-gt.png}};
+		\node[text width=2.5cm] at (\vdist*\disttimes,\yschift-1.5) {Normal Map};
+
+		\draw [-stealth] (\vdist*\disttimes+0.2,\yschift-2.7) -- (\vdist*\disttimes+0.2,\yschift-1.8);
+
+		%% ------------------------------------------- vertex input ----------------------------------------------
+		%% 	d_in							3x512x512
+		%%	dconv1: 	d_in-->x1 			32x512x512
+		\pgfmathsetmacro{\disttimes}{1}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift}
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%%	dconv2:		x1-->x1				32x512x512
+		\pgfmathsetmacro{\disttimes}{2}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift}
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%%	dconv3:		x1-->x1				32x512x512
+		\pgfmathsetmacro{\disttimes}{3}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift}
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\draw (\vdist*\disttimes-0.2,\yschift-3.2) -- (\vdist*\disttimes-0.2,\yschift-4);
+		\draw (\vdist*\disttimes-0.2,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-4);
+		\draw [-stealth] (\vdist*\disttimes+6.5,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-3.2);
+
+		%% downsample 1
+		%%	dconv4:		x1-->x2				32x256x256
+		\pgfmathsetmacro{\disttimes}{4}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%%	dconv2:		x2-->x2				32x256x256
+		\pgfmathsetmacro{\disttimes}{5}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%%	dconv3:		x2-->x2				32x256x256
+		\pgfmathsetmacro{\disttimes}{6}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\draw (\vdist*\disttimes-0.1,\yschift-1.6) -- (\vdist*\disttimes-0.1,\yschift-2.7);
+		\draw (\vdist*\disttimes-0.1,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-2.7);
+		\draw [-stealth] (\vdist*\disttimes+4.2,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-1.7);
+
+		%% downsample 2
+		%%	dconv4:		x2-->x3				32x128x128
+		\pgfmathsetmacro{\disttimes}{7}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%%	dconv2:		x3-->x3				32x128x128
+		\pgfmathsetmacro{\disttimes}{8}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%%	dconv3:		x3-->x3				32x128x128
+		\pgfmathsetmacro{\disttimes}{9}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\draw (\vdist*\disttimes-0.1,\yschift-1.2) -- (\vdist*\disttimes-0.1,\yschift-1.8);
+		\draw (\vdist*\disttimes-0.1,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.8);
+		\draw [-stealth] (\vdist*\disttimes+1.8,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.2);
+
+		%% downsample 3
+		%%	dconv4:		x3-->x4				32x64x64
+		\pgfmathsetmacro{\disttimes}{10}
+		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-1}
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%%	dconv2:		x4-->x4				32x64x64
+		\pgfmathsetmacro{\disttimes}{11}
+		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%%	dconv3:		x4-->x4				32x64x64
+		\pgfmathsetmacro{\disttimes}{12}
+		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%		%% dilated
+		%		%%	dilated1:	x4-->x4				32x64x64
+		%		\pgfmathsetmacro{\disttimes}{13}
+		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%		%%	dilated2:	x4-->x4				32x64x64
+		%		\pgfmathsetmacro{\disttimes}{14}
+		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%		%%	dilated3:	x4-->x4				32x64x64
+		%		\pgfmathsetmacro{\disttimes}{15}
+		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%		%%	dilated4:	x4-->x4				32x64x64
+		%		\pgfmathsetmacro{\disttimes}{16}
+		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%		
+		%		
+		%		
+		%		
+		%		%%	dconv2:		x4-->x4				32x64x64
+		%		\pgfmathsetmacro{\disttimes}{17}
+		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%		%%	dconv3:		x4-->x4				32x64x64
+		%		\pgfmathsetmacro{\disttimes}{18}
+		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
+		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
+		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% ----------------------------------- upsampling -------------------------------------
+
+		%% upsample 1
+		%% interpolate	x4-->x3_us			64x128x128
+		\pgfmathsetmacro{\disttimes}{13}
+		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% concatenate x3_us
+		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% uconv1		x3_us-->x3			32x128x128
+		\pgfmathsetmacro{\disttimes}{15}
+		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% upsample 2
+		%% interpolate	x3-->x2_us			32x256x256
+		\pgfmathsetmacro{\disttimes}{16}
+		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.6}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%% concatenated x2
+		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.6}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% uconv2 		x2,x2_us-->x2		32x256x256
+		\pgfmathsetmacro{\disttimes}{18}
+		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift-0.6}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% upsample 3
+		%% interpolate	x2-->x1_us			32x512x512
+		\pgfmathsetmacro{\disttimes}{19}
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+		%% concatenated x1 and x1_us
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% uconv3		x1,x1_us-->x1		32x512x512
+		\pgfmathsetmacro{\disttimes}{21}
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
+		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% conv1		x1-->xout			3x512x512
+		\pgfmathsetmacro{\disttimes}{22}
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 3
+		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% conv2		xout-->xout			3x512x512
+		\pgfmathsetmacro{\disttimes}{23}
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthd}	%% width 3
+		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
+		\node[text width=1cm] at (\vdist*\disttimes+0.5,\yschift-3.3) {3};
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		%% ------------------------------------- label ----------------------------------------------		
+		\pgfmathsetmacro{\disttimes}{10}
+		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthc}	%% width 3
+		\pgfmathsetmacro{\yschift}{\labelshift}	%% width 32
+		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1) {Conv2d};
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\pgfmathsetmacro{\disttimes}{15}
+		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidthc}	%% width 3
+		\pgfmathsetmacro{\yschift}{\labelshift}	%% width 32
+		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1) {Gated};
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+	\end{tikzpicture}
+
+	\caption{Basic Normal Neural Network model based on Gated Convolution layer and UNet architecture. }
+	\label{fig:gcnn-archi}
+\end{figure}
+
+\subsection{Loss Function}
+
+\paragraph{L1 Loss}
+L1 loss, also known as absolute error loss, which calculates the absolute difference between the prediction and the ground truth. It leads to the median of the observations.
+
+\[ L_1(\tilde y - y) = |\tilde y - y | \]
+
+\paragraph{L2 Loss}
+The standard loss function for optimization in regression problems is the L2 loss, also known as squared error loss, which minimize the squared difference between a prediction and the actual value.
+It leads to the mean of the observations.
+\[ L_2(\tilde y - y) = \|\tilde y - y \|_2^2 \]
+
+\paragraph{Masked L2 Loss with penalty for outliers(mask-l2)}
+\label{par:maskl2}
+The background pixels of the input data are not considered in the normal inference task, they are saved as black pixels in the input data.
+These pixels should not considered in the loss function, i.e.
+invalid pixels.
+Therefore, a valid mask is required to distinguish the background and the main object.
+Specifically, using a matrix with the same width and height as the output, for each pixel, 0 is invalid, 1 is valid.
+Furthermore, depends on the specific task, the output should be constraint in a range.
+For normal output, the range is $ [-1,1] $.
+Thus for the outliers out of this range, a outlier mask can be applied to give them a penalty.
+
+\begin{equation}\label{gcnn-loss}
+	\begin{array}{ll}
+		l(x,y)&= L  = \{l_1, ..., l_N\}^T\\ 
+		l_{n\in N} &= \| mask_{obj} \odot mask_{ol} \odot ( {\tilde y}_n - y_n) \|_2^2 + 	\| mask_{obj} \odot mask_{nol} \odot ( {\tilde y}_n - y_n) \|_2^2 \\
+	\end{array}
+\end{equation}
+
+where $ x $ is input, $ y $ is target, $ N $ is the batch size.$ mask_{obj} $ is the mask of the object, i.e.
+1 means it is an pixel on the object, 0 is an pixel on the background.
+$ mask_{ol} $ is the mask for the outliers, i.e.
+1 means outliers, 0 means non outlier, $ mask_{nol} $ is exactly the inverse of $ mask_{ol} $.
+$ p $ is the penalty of the outliers, it is set as 1.4.
+
+\paragraph{Reversed Huber Loss}
+
+\cite{berhu-loss} proposed Reversed Huber loss to combine both L1 and L2 loss. L1 loss is for small values whereas L2 for large values
+\begin{equation}\label{berhu-loss}
+	\begin{array}{ll}
+		\mathcal{B}(y)= \begin{cases}
+			|y| & |y| \le c \\
+			\dfrac{y^2 + c^2}{2d} & |x| > c\\
+		\end{cases}
+	\end{array}
+\end{equation}
+where $ c=0.2\max (|\tilde y - y|) $.
+
+\newpage
+
+\section{Guided normal inference using GCNN}
+
+\subsection{Intrinsic image decomposition}
+Intrinsic image model was introduced by \cite{intrinsic-image}.
+It interprets that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
+\[ I =R  \odot S\]
+It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
+%% insert a image for decompositions
+\begin{figure}[th]
+	\centering
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
+	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
+	\label{fig:intrinsic-image}
+\end{figure}
+
+The equation can be further decomposed based on different surface models.
+If assume the object surfaces are Lambertian surfaces, i.e.
+the surface which reflect light in all directions, the shading image can be decomposed as the product of the  radiance of  incoming light $ L_0 $, the cosine of the angle of incidence, which is the dot product of the surface normal $ N $ and the light source direction $ L $.
+\[ I = \rho  \odot ( L_0 \textbf{L} \cdot  \textbf{N}) \]
+note that the surface normal $ N $ and light direction $ L $ are unit vectors thus they have only two degrees of freedom.
+
+\begin{figure}[th]
+	\centering
+	\begin{tikzpicture} 
+		% reference lines
+		\coordinate (light) at (-1,3);
+		\coordinate (p) at (2,0);
+		\coordinate (normal) at (2,3);
+		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
+		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
+		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
+		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
+		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
+		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
+		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
+	\end{tikzpicture}
+	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
+	\label{fig:lambertian-surface}
+\end{figure}
+
+The equation can be further rearranged as follows
+\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
+The shape from shading method employed the equation mentioned above to predict the both surface albedo $ \rho $ and the normal $ \textbf{N} $ with knowning light source direction $ \textbf{L} $.
+More specifically, a set of $ k $ image for the same scene have been captured based on different light projections.
+Then, for each pixel $ (x,y) $ in the image, an equation system can be set up
+
+\[ 
+\begin{pmatrix}
+	L_1^T \\
+	L_2^T \\
+	\cdots \\
+	L_k^T
+\end{pmatrix} g(x,y) = 
+\begin{pmatrix}
+	I_1(x,y) \\
+	I_2(x,y) \\
+	\cdots \\
+	I_3(x,y)
+\end{pmatrix}
+\]
+for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
+The equation can be solved based on least square methods. 
+Since normal $ N(x,y) $ is unit vector, thus we have
+
+\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]
+
+Then the normal can be obtained as follow
+
+\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]
+
+In another word, the surface normal including the albedo can be obtained directly based on images and light directions.
+
+\subsection{Light Map}
+\label{sec:lightmap}
+The light map $ L $ can be derived from vertex map and the light source position.
+As shown in Figure \ref{fig:lambertian-surface}, the incoming light direction is a vector point from light source to the surface point, therefor it can be calculated as follows
+\begin{equation}\label{light-direction}
+	\begin{array}{ll}
+		L(x,y)&= \dfrac{V(x,y)-(s_x,s_y)}{\|V(x,y)-(s_x,s_y)\|_2}\\ 
+	\end{array}
+\end{equation}
+where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space.
+The light direction map $ L $ is normalized since only the direction of the light is considered.
+The light map is a matrix corresponding the light direction of whole image where each pixel corresponding with each other, thus it has the same size as the vertex map.
+
+It is important to note that due to the exist noise in the vertex map, the getting light map is only semi-dense, as shown in Figure \ref{fig:light-input}.
+
+\begin{figure}[th]
+	\centering
+	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
+	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_light_input.png}}
+	\caption{The light map calculated from vertex map and the light source}
+	\label{fig:light-input}
+\end{figure}
+
+In order to ease this issue, a light inpainting model has been trained based on the GCNN network with the identity architecture but the input and output, which takes the semi-dense light map as input and predict the fully dense light map as output.
+
+\begin{figure}[th]
+	\centering
+	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
+	\begin{tikzpicture}
+		%% -------------------------------------- parameters ------------------------------------------------
+		\pgfmathsetmacro{\vdist}{0.4}
+
+		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
+		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3
+
+		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
+		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}
+
+		%% 	d_in							3x512x512
+		%%	dconv1: 	d_in-->x1 			32x512x512
+		\pgfmathsetmacro{\disttimes}{1}	%% width 32
+		\pgfmathsetmacro{\yshift}{1}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
+		\pgfmathsetmacro{\yschift}{-1}
+
+		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
+
+		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};
+
+		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
+		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);
+
+		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
+		\pgfmathsetmacro{\yschift}{-1}
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
+	\end{tikzpicture}
+	\caption{Light Net for light inpainting based on GCNN architecture.}
+	\label{fig:light-net-archi}
+\end{figure}
+
 \subsection{VIL Net}
 Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net). 
-The structure is shown in Figure \ref{fig:albedo-gated-archi}. As mentioned in the name, the network utilizes vertex map, light map and image map to accomplish the normal inference task.
+The structure is based on GCNN model which use downsampling two times as shown in Figure \ref{fig:albedo-gated-archi}.
+As mentioned in the name, the network utilizes vertex map, light map and image map to accomplish the normal inference task.
 
 The network can be consider in two parts.
-The first part extracts the feature map encoders.
-It deals with two kinds of input, the vertex map $ X_1 \in \mathbb{R}^{w\times h\times3}$ and the concatenation of light and image map $ X_2 \in \mathbb{R}^{w\times h\times4} $.
+The first part extracts the feature maps.
+It deals with two kinds of input, the vertex map $ X_1 \in \mathbb{R}^{w\times h\times3}$, and the concatenation of light and image map $ X_2 \in \mathbb{R}^{w\times h\times4} $.
 The network extracts the geometry features $ X_v $ from vertex map $ X_1 $ (represented as a regression function v)
 \[ v: X_1 \rightarrow X_v \]
-meanwhile, the network extracts the photometric features $ X_l $ from image and the light map $ X_2 $ (represented as a regression function $ l $)
+and the photometric features $ X_l $ from image and the light map $ X_2 $ (represented as a regression function $ l $)
 \[ l: X_2 \rightarrow X_l \]
-where the two encoders have the same network architecture based on GCNN model.The second part is basically identify to the original GCNN architecture, but before the start of upsampling part, 2 extra layers are added.
-First, a concatenate layer is added to fuse the vertex feature and the image and light map feature getting from encoder.
+where the two encoders have the same network architecture based on the downsampling part of GCNN model.
+After the feature extraction, 2 extra layers are added.
+First, a concatenate layer is added to fuse the vertex feature, and the image and light map feature getting from encoder.
 Second, a fused feature map is predicted from all the feature maps base on a single gated convolution layer. (represented as a regression function $ m $)
 \[ m: [X_v X_l] \rightarrow X_f \]
-Then the network interpolates the feature maps $ X_f $ using 3 times upsamling with gated convolution layers.
+Then the network interpolates the feature maps $ X_f $ 3 times using interpolation and gated convolution layers to inference the normal map $ N $.
 Meanwhile, the skip connections from UNet have been kept.

### 2022-07-24 paper/Chapters/Chapter05.tex
update an2 (Trignet)

@@
 The model is trained with PyTorch 1.10.2, CUDA 10.2.89, GPU with single NVIDIA GEFORCE GTX 1080Ti.
+
+\section{GCNN model evaluation}
+
+In order to ease this issue, a light inpainting model has been trained based on the GCNN network with the identity architecture but the input and output, which takes the semi-dense light map as input and predict the fully dense light map as output.
+
+\begin{figure}[th]
+	\centering
+	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
+	\begin{tikzpicture}
+		%% -------------------------------------- parameters ------------------------------------------------
+		\pgfmathsetmacro{\vdist}{0.4}
+
+		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
+		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3
+
+		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
+		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}
+
+		%% 	d_in							3x512x512
+		%%	dconv1: 	d_in-->x1 			32x512x512
+		\pgfmathsetmacro{\disttimes}{1}	%% width 32
+		\pgfmathsetmacro{\yshift}{1}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
+		\pgfmathsetmacro{\yschift}{-1}
+
+		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
+
+		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};
+
+		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
+		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);
+
+		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
+		\pgfmathsetmacro{\yschift}{-1}
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
+	\end{tikzpicture}
+	\caption{Light Net for light inpainting based on GCNN architecture.}
+	\label{fig:light-net-archi}
+\end{figure}
 

### 2022-07-24 paper/akweury/document.tex
update an2 (Trignet)

@@
 \usepackage{bm}
+\usepackage{float}
 \usepackage{graphicx}
@@
 
-The performance of neighbor based method is good enough for a well chosen $ k $, and it can be further improved by simply use different $ k $ for different area prediction.
-However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor selection and also reduce the number of possible neighbors of each point for a fixed $ k $.
+The performance of neighbor based method is good enough for a well chosen $ k $.
+However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
 \begin{figure}[th]
@@
 % ---------------------- gated convolution neural network ------------------------
+
+\section{Photometric Stereo}
+Photometric stereo was initially introduced by \cite{photometric-stereo}, which estimates the surface normal of the object by observing the object in the same position but under different illuminated scenes.
+It based on the fact that the light reflected by a surface is dependent on the surface normal and the light direction.
+
+\subsection{Approaches}
+Given an image $ I $, it can be decomposed in to two parts, the reflectance $ R $ and the shading $ S $,
+\[ I = R\oplus S\]
+where $ \oplus $ denotes the element-wise product.
+This decomposition of the image is based on the intrinsic image model, which proposed by  \cite{intrinsic-image}.
+It interprets the observed image into reflectance image and the shading image.
+As shown in Figure \ref{fig:intrinsic-image}
+%% insert a image for decompositions
+\begin{figure}[th]
+	\centering
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
+	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
+	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
+	\label{fig:intrinsic-image}
+\end{figure}
+
+The equation can be further decomposed based on different surface models.
+If assume the object surfaces are Lambertian surfaces, i.e.
+the surface which reflect light in all directions, the shading image can be decomposed as the product of the  radiance of  incoming light $ L_0 $, the cosine of the angle of incidence, which is the dot product of the surface normal $ N $ and the light source direction $ L $.
+\[ I = \rho  \odot ( L_0 \textbf{L} \cdot  \textbf{N}) \]
+note that the surface normal $ N $ and light direction $ L $ are unit vectors thus they have only two degrees of freedom.
+
+\begin{figure}[th]
+	\centering
+	\begin{tikzpicture} 
+		% reference lines
+		\coordinate (light) at (-1,3);
+		\coordinate (p) at (2,0);
+		\coordinate (normal) at (2,3);
+		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
+		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
+		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
+		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
+		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
+		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
+		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
+	\end{tikzpicture}
+	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
+	\label{fig:lambertian-surface}
+\end{figure}
+
+The equation can be further rearranged as follows
+\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
+The shape from shading method employed the equation mentioned above to predict the both surface albedo $ \rho $ and the normal $ \textbf{N} $ with knowning light source direction $ \textbf{L} $.
+More specifically, a set of $ k $ image for the same scene have been captured based on different light projections.
+Then, for each pixel $ (x,y) $ in the image, an equation system can be set up
+
+\[ 
+\begin{pmatrix}
+	L_1^T \\
+	L_2^T \\
+	\cdots \\
+	L_k^T
+\end{pmatrix} g(x,y) = 
+\begin{pmatrix}
+	I_1(x,y) \\
+	I_2(x,y) \\
+	\cdots \\
+	I_3(x,y)
+\end{pmatrix}
+\]
+for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
+The equation can be solved based on least square methods. 
+Since normal $ N(x,y) $ is unit vector, thus we have
+
+\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]
+
+Then the normal can be obtained as follow
+
+\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]
+
+In another word, the surface normal including the albedo can be obtained directly based on a set of images and light directions.
+
 \section{Gated Convolution neural network for surface normal estimation}
-\label{gcnn}
+\label{sec:gcnn}
 
@@
 
-Instead of using pooling layers for down/up samplings, gated convolution layer with stride $ (1,1) $ is used.
-The gated convolution using Sigmoid function for gating layer and LeakyReLU function for feature layer.
-All the layers are gated convolution layer with the exception of last two layers, which instead uses standard convolution layer to scale the output in range $\left[-1, 1\right]$.
-Other than the last two layers which use $ 1\times 1 $ kernels, all the gated convolution layer use $ 3\times 3 $ kernels with $ 1\times1 $ padding.
+\begin{sidewaysfigure}[th]
+	\centering
+	\includegraphics[width=1\textwidth]{Figures/gcnn}
+	\caption{The architecture of Gated convolution neural network (GCNN) based on Gated convolution and UNet Architecture.}
+	\label{fig:gcnn-archi}
+\end{sidewaysfigure}
+In order to describe the network in a common way, the parameters of the network are represented by letters.
+The network is constructed by a downsampling part and a upsampling part.
+In the downsampling part, the input is the $ X \in \mathbb{R}^{w\times w\times ch}$.
+The input matrix goes through 3 downsampling layer blocks, each block has two gated convolution layers with stride (1,1) and an extra gated convolution layers with stride (2,2) as a downsampling operation.
+The total three times downsamplings extract the geometry features $ X_v $ from input matrix $ X $ (represented as a regression function $ f $)
+\[ f: X \rightarrow X_f \]
+After the feature extraction, the network upsampling the feature map 3 times to get the output matrix $ Y $.
+Each upsampling consists of an interpolation operation uses nearest neighboring interpolations for resolution upsamling, then a concatenate layer that concatenate the interpolated result and the corresponding high resolution feature map  $ X_{df_1, df_2, ...} $  from the downsampling part.
+This is also called skip connection.
+In the last, a gated convolution layer is utilized to reduce the channel size to fit the next upsampling block.
+After the three times upsampling, two standard convolution layer is added in the last without activation function to predict the surface normal.
+The whole upsampling branch can be represented as a regression function $ n $,
+\[ n: X_v, X_{df_1, df_2, ...} \rightarrow N \]
+All the convolution layers in the network use same kernel size $ 3\times 3 $.
 
-The input is 3D vertex with size $ 512\times512\times3 $, and output is $ 512\times512\times3 $ normal map, which has the same resolution.
-There are 3 times downsamplings, each scale with 3 gated convolution layers, the third layer has stride 2.
-The upsampling part interpolate the feature maps 3 times with 1 gated convolution layer in each scale.
-
-It keeps the skip connection in UNet to remain the fine detail features.
-
-% GCNN Architecture
-\begin{figure}[!h]
-	\centering
-	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
-	\begin{tikzpicture}
-		%% -------------------------------------- parameters ------------------------------------------------
-		\pgfmathsetmacro{\vdist}{0.4}
-
-		\pgfmathsetmacro{\boxsizea}{3}	%% width 512
-		\pgfmathsetmacro{\boxsizeb}{1.5}	%% width 256
-		\pgfmathsetmacro{\boxsizec}{1}	%% width 128
-		\pgfmathsetmacro{\boxsized}{0.7}	%% width 64
-
-		\pgfmathsetmacro{\boxwidthd}{0.1}	%% width 1
-		\pgfmathsetmacro{\boxwidtha}{0.2}	%% width 3
-		\pgfmathsetmacro{\boxwidthb}{\boxwidtha*1.3}	%% width 32
-		\pgfmathsetmacro{\boxwidthc}{\boxwidtha*3}		%% width 64
-
-		\pgfmathsetmacro{\convwshift}{9}
-		\pgfmathsetmacro{\preprocessingshift}{4}
-		\pgfmathsetmacro{\labelshift}{1.5}
-		\pgfmathsetmacro{\gconvwshift}{0}
-
-		\pgfmathsetmacro{\secrowshift}{-6}
-
-		\pgfmathsetmacro{\convrowstart}{4}
-		\pgfmathsetmacro{\secondrowstart}{4}
-
-		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
-		\definecolor{gconvcolor}{rgb}{0.5,0.7,0.7}
-		\definecolor{convcolor}{rgb}{0.5,0.7,0.3}
-		\definecolor{gconvdilatedcolor}{rgb}{0.6,0,0.3}
-
-		%% ---------------------------------- preprocessing --------------------------------------------
-		%%  img_in 1x512x512
-		\pgfmathsetmacro{\disttimes}{3.5}
-		\pgfmathsetmacro{\yschift}{\preprocessingshift}
-		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
-		{\includegraphics[width=.15\textwidth]{./Figures/train-input.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {3D Vertex};
-
-		\draw [-stealth](1.45,\yschift-1.8) -- (1.45,\yschift-2.6);
-
-		\draw [-stealth]  (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);
-
-		\pgfmathsetmacro{\disttimes}{10}
-		\pgfmathsetmacro{\yschift}{\preprocessingshift}
-		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
-		{\includegraphics[width=.15\textwidth]{./Figures/train-depth-noise}};
-		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {Add Noise};
-
-		\draw [-stealth] (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);
-
-		\pgfmathsetmacro{\disttimes}{16.5}
-		\pgfmathsetmacro{\yschift}{\preprocessingshift}
-		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
-		{\includegraphics[width=.15\textwidth]{./Figures/train-depth.png}};
-		\node[text width=2cm] at (\vdist*\disttimes+0.2,\yschift-1.5) {Depth Map};
-
-		%% ----------------------------------- output normal map -------------------------------------
-		\pgfmathsetmacro{\disttimes}{25}
-		\pgfmathsetmacro{\yschift}{\preprocessingshift}
-		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
-		{\includegraphics[width=.15\textwidth]{./Figures/train-normal-gt.png}};
-		\node[text width=2.5cm] at (\vdist*\disttimes,\yschift-1.5) {Normal Map};
-
-		\draw [-stealth] (\vdist*\disttimes+0.2,\yschift-2.7) -- (\vdist*\disttimes+0.2,\yschift-1.8);
-
-		%% ------------------------------------------- vertex input ----------------------------------------------
-		%% 	d_in							3x512x512
-		%%	dconv1: 	d_in-->x1 			32x512x512
-		\pgfmathsetmacro{\disttimes}{1}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift}
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%%	dconv2:		x1-->x1				32x512x512
-		\pgfmathsetmacro{\disttimes}{2}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift}
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%%	dconv3:		x1-->x1				32x512x512
-		\pgfmathsetmacro{\disttimes}{3}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift}
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		\draw (\vdist*\disttimes-0.2,\yschift-3.2) -- (\vdist*\disttimes-0.2,\yschift-4);
-		\draw (\vdist*\disttimes-0.2,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-4);
-		\draw [-stealth] (\vdist*\disttimes+6.5,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-3.2);
-
-		%% downsample 1
-		%%	dconv4:		x1-->x2				32x256x256
-		\pgfmathsetmacro{\disttimes}{4}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%%	dconv2:		x2-->x2				32x256x256
-		\pgfmathsetmacro{\disttimes}{5}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%%	dconv3:		x2-->x2				32x256x256
-		\pgfmathsetmacro{\disttimes}{6}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		\draw (\vdist*\disttimes-0.1,\yschift-1.6) -- (\vdist*\disttimes-0.1,\yschift-2.7);
-		\draw (\vdist*\disttimes-0.1,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-2.7);
-		\draw [-stealth] (\vdist*\disttimes+4.2,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-1.7);
-
-		%% downsample 2
-		%%	dconv4:		x2-->x3				32x128x128
-		\pgfmathsetmacro{\disttimes}{7}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%%	dconv2:		x3-->x3				32x128x128
-		\pgfmathsetmacro{\disttimes}{8}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%%	dconv3:		x3-->x3				32x128x128
-		\pgfmathsetmacro{\disttimes}{9}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		\draw (\vdist*\disttimes-0.1,\yschift-1.2) -- (\vdist*\disttimes-0.1,\yschift-1.8);
-		\draw (\vdist*\disttimes-0.1,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.8);
-		\draw [-stealth] (\vdist*\disttimes+1.8,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.2);
-
-		%% downsample 3
-		%%	dconv4:		x3-->x4				32x64x64
-		\pgfmathsetmacro{\disttimes}{10}
-		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-1}
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%%	dconv2:		x4-->x4				32x64x64
-		\pgfmathsetmacro{\disttimes}{11}
-		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%%	dconv3:		x4-->x4				32x64x64
-		\pgfmathsetmacro{\disttimes}{12}
-		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%		%% dilated
-		%		%%	dilated1:	x4-->x4				32x64x64
-		%		\pgfmathsetmacro{\disttimes}{13}
-		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%		%%	dilated2:	x4-->x4				32x64x64
-		%		\pgfmathsetmacro{\disttimes}{14}
-		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%		%%	dilated3:	x4-->x4				32x64x64
-		%		\pgfmathsetmacro{\disttimes}{15}
-		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%		%%	dilated4:	x4-->x4				32x64x64
-		%		\pgfmathsetmacro{\disttimes}{16}
-		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%		
-		%		
-		%		
-		%		
-		%		%%	dconv2:		x4-->x4				32x64x64
-		%		\pgfmathsetmacro{\disttimes}{17}
-		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%		%%	dconv3:		x4-->x4				32x64x64
-		%		\pgfmathsetmacro{\disttimes}{18}
-		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
-		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
-		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		%		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% ----------------------------------- upsampling -------------------------------------
-
-		%% upsample 1
-		%% interpolate	x4-->x3_us			64x128x128
-		\pgfmathsetmacro{\disttimes}{13}
-		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% concatenate x3_us
-		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% uconv1		x3_us-->x3			32x128x128
-		\pgfmathsetmacro{\disttimes}{15}
-		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.9}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% upsample 2
-		%% interpolate	x3-->x2_us			32x256x256
-		\pgfmathsetmacro{\disttimes}{16}
-		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.6}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%% concatenated x2
-		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.6}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% uconv2 		x2,x2_us-->x2		32x256x256
-		\pgfmathsetmacro{\disttimes}{18}
-		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift-0.6}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% upsample 3
-		%% interpolate	x2-->x1_us			32x512x512
-		\pgfmathsetmacro{\disttimes}{19}
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-		%% concatenated x1 and x1_us
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes+\boxwidth,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% uconv3		x1,x1_us-->x1		32x512x512
-		\pgfmathsetmacro{\disttimes}{21}
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
-		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% conv1		x1-->xout			3x512x512
-		\pgfmathsetmacro{\disttimes}{22}
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 3
-		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% conv2		xout-->xout			3x512x512
-		\pgfmathsetmacro{\disttimes}{23}
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthd}	%% width 3
-		\pgfmathsetmacro{\yschift}{\gconvwshift}	%% width 32
-		\node[text width=1cm] at (\vdist*\disttimes+0.5,\yschift-3.3) {3};
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		%% ------------------------------------- label ----------------------------------------------		
-		\pgfmathsetmacro{\disttimes}{10}
-		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthc}	%% width 3
-		\pgfmathsetmacro{\yschift}{\labelshift}	%% width 32
-		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1) {Conv2d};
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=convcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		\pgfmathsetmacro{\disttimes}{15}
-		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidthc}	%% width 3
-		\pgfmathsetmacro{\yschift}{\labelshift}	%% width 32
-		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1) {Gated};
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-	\end{tikzpicture}
-
-	\caption{Basic Normal Neural Network model based on Gated Convolution layer and UNet architecture. }
-	\label{fig:gcnn-archi}
-\end{figure}
+One of the key feature of the network is the output has the same size as the input.
+This is achieved by the (1,1) padding and the same channel number in the convolution layers.
+Thus the surface normal can be achieved 1-1 estimation.
+Another key point of the network is the robustness of the noise.
+The network takes semi-dense matrix as input then predicts the fully-dense matrix as output.
+The last feature is the multi-purpose using scenarios.
+In the description, no specific input type has been indicated.
+In this thesis, two application scenarios have been verified.
+The first is the missing-pixel estimation but with out the transformation of the style of the input matrix, which takes the semi-dense matrix as input and simply fill the missing pixels in the output.
+The second is the missing pixel estimation with style-transferred of the matrix.
+In this case, the network takes the semi-dense matrix as input, the output matrix is fully-dense but each pixel has the different meaning as the input.
+Actually, the first scenario can be consider as the specially case of the second scenario which the style of output and the input remain the same.
+The network is test in Chapter \ref{ch:05}, which is shown the good performance on noise filtering task and also the normal surface estimation task.
 
@@
 
-\newpage
-
 \section{Guided normal inference using GCNN}
-
-\subsection{Intrinsic image decomposition}
-Intrinsic image model was introduced by \cite{intrinsic-image}.
-It interprets that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
-\[ I =R  \odot S\]
-It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
-%% insert a image for decompositions
-\begin{figure}[th]
-	\centering
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
-	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
-	\label{fig:intrinsic-image}
-\end{figure}
-
-The equation can be further decomposed based on different surface models.
-If assume the object surfaces are Lambertian surfaces, i.e.
-the surface which reflect light in all directions, the shading image can be decomposed as the product of the  radiance of  incoming light $ L_0 $, the cosine of the angle of incidence, which is the dot product of the surface normal $ N $ and the light source direction $ L $.
-\[ I = \rho  \odot ( L_0 \textbf{L} \cdot  \textbf{N}) \]
-note that the surface normal $ N $ and light direction $ L $ are unit vectors thus they have only two degrees of freedom.
-
-\begin{figure}[th]
-	\centering
-	\begin{tikzpicture} 
-		% reference lines
-		\coordinate (light) at (-1,3);
-		\coordinate (p) at (2,0);
-		\coordinate (normal) at (2,3);
-		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
-		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
-		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
-		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
-		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
-		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
-		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
-	\end{tikzpicture}
-	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
-	\label{fig:lambertian-surface}
-\end{figure}
-
-The equation can be further rearranged as follows
-\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
-The shape from shading method employed the equation mentioned above to predict the both surface albedo $ \rho $ and the normal $ \textbf{N} $ with knowning light source direction $ \textbf{L} $.
-More specifically, a set of $ k $ image for the same scene have been captured based on different light projections.
-Then, for each pixel $ (x,y) $ in the image, an equation system can be set up
-
-\[ 
-\begin{pmatrix}
-	L_1^T \\
-	L_2^T \\
-	\cdots \\
-	L_k^T
-\end{pmatrix} g(x,y) = 
-\begin{pmatrix}
-	I_1(x,y) \\
-	I_2(x,y) \\
-	\cdots \\
-	I_3(x,y)
-\end{pmatrix}
-\]
-for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
-The equation can be solved based on least square methods. 
-Since normal $ N(x,y) $ is unit vector, thus we have
-
-\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]
-
-Then the normal can be obtained as follow
-
-\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]
-
-In another word, the surface normal including the albedo can be obtained directly based on images and light directions.
+The guided normal inference takes the light direction and the image into consideration.
+It is under the assumption that the scene image $ I $ is captured by a calibrated camera, i.e.
+knowing the intrinsic $ K $ and extrinsic camera matrix $ [R|t] $, and a the light position $ (s_x, s_y, s_z) $ of the single light source.
+The geometry based approach inference the surface normal from the point cloud, whereas the photometric stereo inference the surface normal from a set of calibrated illuminated images.
+The idea behind this chapter is that improve the geometry based approach with the help of one calibrated illuminated image.
+Since the calibrated illuminated image contains the information about the surface feature, it is supposed to help the geometry approach in a proper way.
+Based on this idea, two networks are proposed in this section.
 
@@
 \label{sec:lightmap}
-The light map $ L $ can be derived from vertex map and the light source position.
+The light map $ L $ can be derived from vertex map $ V $ and the light source position $ s $.
 As shown in Figure \ref{fig:lambertian-surface}, the incoming light direction is a vector point from light source to the surface point, therefor it can be calculated as follows
@@
 \end{equation}
-where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space.
-The light direction map $ L $ is normalized since only the direction of the light is considered.
-The light map is a matrix corresponding the light direction of whole image where each pixel corresponding with each other, thus it has the same size as the vertex map.
-
-It is important to note that due to the exist noise in the vertex map, the getting light map is only semi-dense, as shown in Figure \ref{fig:light-input}.
-
-\begin{figure}[th]
+\begin{figure}[H]
 	\centering
-	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
-	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_light_input.png}}
+	{\includegraphics[width=.25\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
+	{\includegraphics[width=.25\textwidth]{./Figures/intrinsic_image_light_input.png}}
 	\caption{The light map calculated from vertex map and the light source}
@@
 \end{figure}
-
-In order to ease this issue, a light inpainting model has been trained based on the GCNN network with the identity architecture but the input and output, which takes the semi-dense light map as input and predict the fully dense light map as output.
-
-\begin{figure}[th]
-	\centering
-	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
-	\begin{tikzpicture}
-		%% -------------------------------------- parameters ------------------------------------------------
-		\pgfmathsetmacro{\vdist}{0.4}
-
-		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
-		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3
-
-		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
-		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}
-
-		%% 	d_in							3x512x512
-		%%	dconv1: 	d_in-->x1 			32x512x512
-		\pgfmathsetmacro{\disttimes}{1}	%% width 32
-		\pgfmathsetmacro{\yshift}{1}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
-		\pgfmathsetmacro{\yschift}{-1}
-
-		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
-
-		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};
-
-		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
-		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);
-
-		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
-		\pgfmathsetmacro{\yschift}{-1}
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
-	\end{tikzpicture}
-	\caption{Light Net for light inpainting based on GCNN architecture.}
-	\label{fig:light-net-archi}
-\end{figure}
+where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space.
+The light direction map $ L $ is normalized since only the direction of the light is considered.
+Using the equation above for all the pixels in the point cloud can obtain the corresponding light map, which is a matrix with same size as point clouds.
+However, it is important to note that due to the exist noise in the vertex map, the getting light map is only semi-dense, as shown in Figure \ref{fig:light-input}.
 
@@
 Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net).
-The structure is based on GCNN model which use downsampling two times as shown in Figure \ref{fig:albedo-gated-archi}.
-As mentioned in the name, the network utilizes vertex map, light map and image map to accomplish the normal inference task.
+The structure is basically derived from GCNN model as mentioned in \ref{sec:gcnn}, which is shown in Figure
+\ref{fig:VIL-Net}.
+
+As mentioned in the name, the \textbf{VIL}-Net utilizes \textbf{V}ertex map, \textbf{L}ight map and \textbf{I}mage map to accomplish the normal inference task.
 
 The network can be consider in two parts.
-The first part extracts the feature maps.
+The first part extracts the feature maps from the input data.
 It deals with two kinds of input, the vertex map $ X_1 \in \mathbb{R}^{w\times h\times3}$, and the concatenation of light and image map $ X_2 \in \mathbb{R}^{w\times h\times4} $.
@@
 where the two encoders have the same network architecture based on the downsampling part of GCNN model.
-After the feature extraction, 2 extra layers are added.
-First, a concatenate layer is added to fuse the vertex feature, and the image and light map feature getting from encoder.
-Second, a fused feature map is predicted from all the feature maps base on a single gated convolution layer. (represented as a regression function $ m $)
+After the feature extraction, 2 extra layers are added: 1, a concatenate layer is added to fuse the vertex feature, and the image and light map feature getting from the encoder.
+2, a fused feature map is predicted from all the feature maps base on a single gated convolution layer. (represented as a regression function $ m $)
 \[ m: [X_v X_l] \rightarrow X_f \]
 Then the network interpolates the feature maps $ X_f $ 3 times using interpolation and gated convolution layers to inference the normal map $ N $.
-Meanwhile, the skip connections from UNet have been kept.
-Thus the feature maps $ X_{df_1, df_2, ...} $ of each down-sampling time in the regression model $ v $ are considered in the upsamling part.
+Meanwhile, the skip connections fuse the high resolution features $ X_{df_1, df_2, ...} $ from the downsampling part during the upsamplings.
+The upsampling is represented as a regression function $ n $:
 \[ n: X_f, X_{df_1, df_2, ...} \rightarrow N \]
@@
 In this scenario, the output is still the surface normal, thus the training loss can be the same as GCNN model.
+
+\begin{sidewaysfigure}[th]
+	\centering
+	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
+	\caption{The architecture of TriGNet}
+	\label{fig:VIL-Net}
+\end{sidewaysfigure}
 
@@
 
-\begin{sidewaysfigure}[th]
-	\centering
-	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
-	\caption{The architecture of TriGNet}
-	\label{fig:albedo-gated-archi}
-\end{sidewaysfigure}
-
-\subsection{Loss Function}
-For the case of normal output, the loss function is the same as Mask-L2 loss as introduced in \ref{par:maskl2}.
-For the case of the product of albedo and normal, the loss function utilized a scaled Mask-L2 loss, which gives the range of inliers between $ [0,255] $.
-
 \end{document}

### 2022-07-24 eval.py

@@ -86,21 +86,15 @@ if __name__ == '__main__':
     args = parser.parse_args()
 
     models = {
+        # test
+        "an3-8-1000": config.paper_exp / "an3" / "checkpoint-8-1000-236.pth.tar",
+        "vil-8-1000": config.paper_exp / "vil10" / "checkpoint-8-1000-239.pth.tar",
+        "GCNN-8-1000": config.paper_exp / "gcnn" / "checkpoint-8-1000-243.pth.tar",
 
-        # "an3-3-12-1000": config.paper_exp / "an3" / "checkpoint-l1-3-12-1000-3.pth.tar",
-        # "an3-3-12-1000": config.paper_exp / "an3" / "checkpoint-l1-3-12-1000-2.pth.tar",
-        # "an3-10-1000": config.paper_exp / "an3" / "checkpoint-l1-10-1000.pth.tar",
-
-        "vil-10-1000": config.paper_exp / "vil10" / "checkpoint-10-1000.pth.tar",
-        "vil-3-12-1000": config.paper_exp / "vil10" / "checkpoint-3-12-1000.pth.tar",
-
-        "vil3": config.paper_exp / "vil10" / "checkpoint-3-12-1000-l3.pth.tar",
-        "vil10": config.paper_exp / "vil10" / "checkpoint-10-1000-l10.pth.tar",
-
-        # "GCNN-b8": config.paper_exp / "gcnn" / "checkpoint-1662.pth.tar",
-
+        # record
+        # "an3-3-12-1000": config.paper_exp / "an3" / "checkpoint-l1-3-12-1000.pth.tar",
+        # "vil-10-1000": config.paper_exp / "vil10" / "checkpoint-10-1000.pth.tar",
         # "GCNN-3-12-1000": config.paper_exp / "gcnn" / "checkpoint-3-12-1000.pth.tar",
-        # "GCNN-b32": config.paper_exp / "gcnn" / "checkpoint-b32.pth.tar",
         # "SVD": None,
 
     }

### 2022-07-25 paper/akweury/document.tex
update an (Trignet-CNN)

@@
 	\centering
-	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
-	\caption{The architecture of TriGNet}
+	\includegraphics[width=1\textwidth]{Figures/vil-net} % Research group name and department name
+	\caption{The architecture of VIL-Net}
 	\label{fig:VIL-Net}
@@
 
-\subsection{An3 Net}
+\subsection{TriG-Net}
+
+Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net).
+The structure is basically derived from GCNN model as mentioned in \ref{sec:gcnn}, which is shown in Figure
+\ref{fig:VIL-Net}.
+
+As mentioned in the name, the \textbf{VIL}-Net utilizes \textbf{V}ertex map, \textbf{L}ight map and \textbf{I}mage map to accomplish the normal inference task.
+
+The network can be consider in two parts.
+The first part extracts the feature maps from the input data.
+It deals with two kinds of input, the vertex map $ X_1 \in \mathbb{R}^{w\times h\times3}$, and the concatenation of light and image map $ X_2 \in \mathbb{R}^{w\times h\times4} $.
+The network extracts the geometry features $ X_v $ from vertex map $ X_1 $ (represented as a regression function v)
+\[ v: X_1 \rightarrow X_v \]
+and the photometric features $ X_l $ from image and the light map $ X_2 $ (represented as a regression function $ l $)
+\[ l: X_2 \rightarrow X_l \]
+where the two encoders have the same network architecture based on the downsampling part of GCNN model.
+After the feature extraction, 2 extra layers are added: 1, a concatenate layer is added to fuse the vertex feature, and the image and light map feature getting from the encoder.
+2, a fused feature map is predicted from all the feature maps base on a single gated convolution layer. (represented as a regression function $ m $)
+\[ m: [X_v X_l] \rightarrow X_f \]
+Then the network interpolates the feature maps $ X_f $ 3 times using interpolation and gated convolution layers to inference the normal map $ N $.
+Meanwhile, the skip connections fuse the high resolution features $ X_{df_1, df_2, ...} $ from the downsampling part during the upsamplings.
+The upsampling is represented as a regression function $ n $:
+\[ n: X_f, X_{df_1, df_2, ...} \rightarrow N \]
+
+With the help of an extra image-light encoder, the network gained more information of the object surface, which is supposed to predict the surface normal more accurate.
+In this scenario, the output is still the surface normal, thus the training loss can be the same as GCNN model.
+
 The first branch (shown above) takes a light map introduced in \ref{sec:lightmap} as the input, the structure is the same as GCNN architecture except that the last two standard convolution layers, the skip connections are kept to connect the 3 down/up samplings.
@@
 
+\begin{sidewaysfigure}[th]
+	\centering
+	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
+	\caption{The architecture of Trig-Net}
+	\label{fig:VIL-Net}
+\end{sidewaysfigure}
+
 \end{document}

### 2022-07-25 common/AlbedoGatedNNN.py

@@ -168,6 +168,7 @@ class GNet(nn.Module):
         return xout
 
 
+#
 class GNet2(nn.Module):
     def __init__(self, in_ch, out_ch, channel_num):
         super().__init__()
@@ -193,25 +194,25 @@ class GNet2(nn.Module):
         self.l_dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
         self.l_dconv4 = GConv(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
 
-        self.i_dconv1 = GConv(1, channel_size_1, kernel_down, stride, padding_down)
-        self.i_dconv2 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
-        self.i_dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
-        self.i_dconv4 = GConv(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
+        self.i_dconv1 = nn.Conv2d(1, channel_size_1, kernel_down, stride, padding_down)
+        self.i_dconv2 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.i_dconv3 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.i_dconv4 = nn.Conv2d(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
 
-        self.uconv1_1 = GConv(channel_size_3, channel_size_1, kernel_up, stride, padding_up)
-        self.uconv1 = GConv(channel_size_2, channel_size_1, kernel_up, stride, padding_up)
-        self.uconv2_1 = GConv(channel_size_3, channel_size_1, kernel_up, stride, padding_up)
-        self.uconv2 = GConv(channel_size_2, channel_size_1, kernel_up, stride, padding_up)
         self.uconv3_1 = GConv(channel_size_3, channel_size_1, kernel_up, stride, padding_up)
         self.uconv3 = GConv(channel_size_2, channel_size_1, kernel_up, stride, padding_up)
+        self.uconv4_1 = GConv(channel_size_3, channel_size_1, kernel_up, stride, padding_up)
[…]

### 2022-07-25 workspace/train.py

@@ -306,11 +306,7 @@ def train_epoch(nn_model, epoch, eval_loss_best):
         # Compute the loss
 
         if nn_model.args.normal_loss:
-            if nn_model.args.exp == "an":
-                a = out.detach().clone()
-                normal_out = a / (torch.linalg.norm(a, dim=1, keepdim=True, ord=2) + 1e-20)
-            else:
-                normal_out = out[:, :3, :, :]
+            normal_out = out[:, :3, :, :]
 
             nn_model.normal_loss = loss_utils.weighted_unit_vector_loss(normal_out,
                                                                         target[:, :3, :, :],
@@ -324,11 +320,7 @@ def train_epoch(nn_model, epoch, eval_loss_best):
             loss_total += normal_loss_total
 
         if nn_model.args.normal_huber_loss:
-            if nn_model.args.exp == "an":
-                a = out.detach().clone()
-                normal_out = a / (torch.linalg.norm(a, dim=1, keepdim=True, ord=2) + 1e-20)
-            else:
-                normal_out = out[:, :3, :, :]
+            normal_out = out[:, :3, :, :]
 
             nn_model.normal_loss = loss_utils.weighted_unit_vector_huber_loss(normal_out,
                                                                               target[:, :3, :, :],
@@ -567,7 +559,7 @@ def draw_output(exp_name, input, xout, target, exp_path, epoch, i, train_idx, pr
         output_list.append(mu.visual_light(x_out_light, "pred"))
         # output_list.append(mu.visual_light(light_gt, "gt"))
         output_list.append(mu.visual_diff(light_gt, x_out_light, "angle"))
-    elif exp_name in ["vi5", "resng", "i5", "an2", "nnnn", "vil10", "an3"]:
+    elif exp_name in ["vi5", "resng", "i5", "an2", "nnnn", "vil10", "an3", "an"]:
         x_out_normal[mask] = 0
         x_out_normal[x_out_normal > 1] = 1
         x_out_normal[x_out_normal < -1] = -1
@@ -594,7 +586,7 @@ def draw_output(exp_name, input, xout, target, exp_path, epoch, i, train_idx, pr
         x_out_normal[mask] = 0
         output_list.append(mu.visual_normal(x_out_normal, "pred"))
         output_list.append(mu.visual_diff(gt, x_out_normal, "angle"))
-    elif exp_name == "an":
+    elif exp_name == "an4":
         # g
[…]

### 2022-07-25 paper/akweury/document.tex
update an (Trignet-CNN)

@@
 
-Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net).
-The structure is basically derived from GCNN model as mentioned in \ref{sec:gcnn}, which is shown in Figure
-\ref{fig:VIL-Net}.
+We propose a light and image guided network called Triple-pipe-gated-Network (Trip-Net), which employs the GCNN architecture three times to accomplish the normal inference task.
+The architecture is shown in Figure \ref{fig:Trig-Net}.
+
+The network has three pipes combined with one main pipe and two side pipes.
+Each pipe deals with different task.
+The main pipe deals with the geometry information, which takes the vertex map as the input and used to predict the surface normal.
+The light map is a side pipe which take light map as input and extract the light feature then forward the features to the main pipe as a supplementary information for the main pipe.
+The image pipe takes the image as the input and extracts the image features then forward the features to the main pipe as well.
+The supplementary pipes provide the illumination information which helps the main pipe to refine the inferred normals.
+\subsubsection{Side-Pipe(Light)}
+The task of light pipe in the network is to predict the light feature from the phtometric information using the light direction in the scene, which is calculated from the point cloud and the light position.
+The light map also inherits the noise from the point cloud, which lead to a semi-dense input map.
+Therefore this side pipe utilizes gated convolution layers for feature map extraction.
+The input vertex map is downsampled three times in this part.
+Each downsampling utilizes three gated layers, the first two layers have stride (1,1) and the third one has stride (2,2) to reduce the feature scale.
+In the upsampling part, the network also has three times upsampling as a symmetric design.
+In each upsampling, it first uses nearest neighbor interpolation algorithms to expend the feature map size.
+Then it concatenates the corresponding feature map from the downsampling part.
+In the last, the feature map goes through a gated convolution layer to reduce the channel size.
+In the upsampling part,
 
@@
 	\caption{The architecture of Trig-Net}
-	\label{fig:VIL-Net}
+	\label{fig:Trig-Net}
 \end{sidewaysfigure}

### 2022-07-25 paper/akweury/document.tex
update light

--- 2022-07-24 paper/akweury/document.tex
@@
 
-The normal inference task estimate the surface normal of a 3D object.
-There are two main approach to solve the task.
-Geometry based approach estimate the surface normal of an object based on the geometry principle.
-Point cloud is a common surface geometry information which samples the surface point position in 3D space.
-Another approach is photometric stereo based approach, which utilizes a set of images under different illumination conditions.
-In this chapter, geometry and photometric stereo based approach are introduced separately, then a deep learning based approach using geometry information is proposed.
-In the end, as the main work of the thesis, another deep learning method is proposed based on both geometry and photometric stereo information.
+The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
+The input matrix has $ 128\times 128 $ height and width.
+Each vertex map has dimension $ 128\times 128\times3 $, light map has $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.
+The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
 
-\section{Geometry based normal estimation}
+\section{GCNN model evaluation}
+The GCNN model is the base model of the whole thesis. In this section, we first discuss the noise filter performance of the model and then evaluate the performance on normal inference.
 
-\subsection{Approach}
-The geometry based normal estimation uses point cloud of the object surface as input.
-Given a structured point cloud $ V^{W\times H\times 3} $ to estimate the normal map  $ N^{W\times H \times 3} $, where each normal  $ \textbf{n}^{3\times 1} $ at point $ \textbf{v}^{3\times 1} \in N $ is a unit vector with its direction point outward of the surface and perpendicular to the tangent plane of the surface at point $ \textbf{p}^{3\times 1} $.
-
-The idea behind the neighbor based method is to fit a plane $ \Pi $ using the $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of the point $ \textbf{p} $, calculate the normal  $ \tilde{\textbf{n}} $ of the plane.
-
-It is under the assumption that the point and its neighbors are located in the same plane.
-This is usually not hold for the most of the surface, but if $ k $ in a suitable scale and point cloud is dense enough, it is enough to get an accurate and sharp result.
-As shown in Figure \ref{fig:svd-normal}.
-
-Specifically, it is not necessary to find the exact plane equation to solve the normal. Instead, the normal can be derived based on an equation system. 
-The normal $ \tilde{\textbf{n}} $ of plane $ \Pi $ is perpendicular to all the vector on the plane $ \Pi $, we can construct $ k $ vectors on plane $ \Pi $ use  $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of point $ \textbf{p} $.
-For the simplicity, we can choose $ \textbf{p}_1 $ as the base point, then $ k-1 $ vectors can be construct as follows
-\begin{equation}
-	\begin{array}{rr}
-		\displaystyle \textbf{v}_i = \textbf{p}_1 - \textbf{p}_i & \text{for}\ i= 2,...,k \\
-	\end{array}
-\end{equation}
-and each of them satisfied $ \textbf{v}_i \cdot \tilde{\textbf{n}} = 0$. Then, the equation system can be constructed as 
-\begin{equation}{\label{eq:normal-overdetermined-equation}}
-	A \cdot \textbf{n} = 0
-\end{equation}
-where $ A \in \mathbb{R}^{(k-1)\times 3} $ is the vector matrix vertically stacked by $ \textbf{v}_1, ..., \textbf{v}_{k-1} $.
-In order to avoid trivial solution, one more constraint should be added
-\[ \|  \bn_{3 \times 1} \|_2^2 = 1  \]
-which also let the normal to be a unit vector.
-
-To calculate a valid normal, at least 3 points are required to construct, i.e.
-$ k>=3 $.
-For the sake of robust, more points can be used to reduce the measuring error.
-For the case $ k>3 $, since the surface vectors are actually not in the same plane, the equation system is likely over-determined .
-Then the equation system mentioned above can be converted to follow optimization problem
-\begin{equation}
-	\begin{array}{rrclcl}
-		\displaystyle \min & \multicolumn{3}{l}{\| A  \bn \|^2} \\
-		\\
-		\textrm{s.t.} & \| \bn \|^2 & = & 1 
-	\end{array}
-\end{equation}
-which can be solved by singular value decomposition(SVD). Let the decomposition of 
-\[ A=U\Sigma V^T \]
-The solution i.e. normal is the last column of $ V $.
-
-At last, all the normals should point ot view point $ \textbf{s} $, thus the direction of a normal should be inverted if 
-\begin{equation}\label{eq:normal-invertion}
-	\textbf{n} \cdot (\textbf{p}  - \textbf{s}) > 0
-\end{equation}
-
-Repeat the procedure for all the points in the point cloud to get the entire normal map.
-
-\subsection{Evaluation}
-The neighbor based method can predict the normal map in a good way when the given point cloud is dense, as shown in Figure \ref{fig:svd-normal}.
-It can successfully predict the smooth surface of the dragon object, especially the flakes and the tails of the dragon.
-
-However, it failed in the areas such as hindleg, horn and the mouth, which consists mainly by sharp edges.
-This is because the neighbors points in these area do not hold the assumption of coplanarity well, the normals of these neighbors can be very different.
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
-	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
-	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}
-
-	\label{fig:svd-normal}
-	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5 \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
-\end{figure}
-The neighbor based method is depended on a well-chosen parameter $ k $.
-Figure \ref{fig:svd-k-eval} shows the evaluation on different $ k $ values.
-When $ k=1 $, the average error of the whole image is the lowest one, most of the normals are close to the ground-truth but the outline edges, which are the areas that surface normal changed extremely sever.
-For the case $ k=2 $, the sharp edges are more smooth and cause more error, like the eyes area of the dragon.
-Compare to the first case, the outline edge error goes better.
-Most of the edge errors are reduced when $ k=2 $, since more neighbor points join the evaluation and it reduces the effect of outliers.
-However, for the area of horn outline, hindleg outline, the error goes worse.
-In this case, most of the neighbors of these points are outliers and thus failed this approach.
-$ k=3 $ and $ k=4 $ further increase the angle errors based on $ k=2 $.
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
-	\label{fig:svd-k-eval}
-	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
-\end{figure}
-
-The performance of neighbor based method is good enough for a well chosen $ k $.
-However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
-	\label{fig:svd-noise}
-	\caption{Evaluation of neighbor based method on a noised dragon model}
-\end{figure}
-
-% ---------------------- gated convolution neural network ------------------------
-
-\section{Photometric Stereo}
-Photometric stereo was initially introduced by \cite{photometric-stereo}, which estimates the surface normal of the object by observing the object in the same position but under different illuminated scenes.
-It based on the fact that the light reflected by a surface is dependent on the surface normal and the light direction.
-
-\subsection{Approaches}
-Given an image $ I $, it can be decomposed in to two parts, the reflectance $ R $ and the shading $ S $,
-\[ I = R\oplus S\]
-where $ \oplus $ denotes the element-wise product.
-This decomposition of the image is based on the intrinsic image model, which proposed by  \cite{intrinsic-image}.
-It interprets the observed image into reflectance image and the shading image.
-As shown in Figure \ref{fig:intrinsic-image}
-%% insert a image for decompositions
-\begin{figure}[th]
-	\centering
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
-	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
-	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
-	\label{fig:intrinsic-image}
-\end{figure}
-
-The equation can be further decomposed based on different surface models.
-If assume the object surfaces are Lambertian surfaces, i.e.
-the surface which reflect light in all directions, the shading image can be decomposed as the product of the  radiance of  incoming light $ L_0 $, the cosine of the angle of incidence, which is the dot product of the surface normal $ N $ and the light source direction $ L $.
-\[ I = \rho  \odot ( L_0 \textbf{L} \cdot  \textbf{N}) \]
-note that the surface normal $ N $ and light direction $ L $ are unit vectors thus they have only two degrees of freedom.
+\subsection{Noise Filter Result}
 
@@
 	\centering
+	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
 	\begin{tikzpicture}
-		% reference lines
-		\coordinate (light) at (-1,3);
-		\coordinate (p) at (2,0);
-		\coordinate (normal) at (2,3);
-		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
-		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
-		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
-		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
-		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
-		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
-		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
+		%% -------------------------------------- parameters ------------------------------------------------
+		\pgfmathsetmacro{\vdist}{0.4}
+
+		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
+		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3
+
+		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
+		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}
+
+		%% 	d_in							3x512x512
+		%%	dconv1: 	d_in-->x1 			32x512x512
+		\pgfmathsetmacro{\disttimes}{1}	%% width 32
+		\pgfmathsetmacro{\yshift}{1}	%% width 32
+		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
+		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
+		\pgfmathsetmacro{\yschift}{-1}
+
+		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
+
+		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
+		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};
+
+		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
+		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);
+
+		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
+		\pgfmathsetmacro{\yschift}{-1}
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
+		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
+
+		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
 	\end{tikzpicture}
-	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
-	\label{fig:lambertian-surface}
+	\caption{Light Net for light inpainting based on GCNN architecture.}
+	\label{fig:light-net-archi}
 \end{figure}
 
-The equation can be further rearranged as follows
-\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
-The shape from shading method employed the equation mentioned above to predict the both surface albedo $ \rho $ and the normal $ \textbf{N} $ with knowning light source direction $ \textbf{L} $.
-More specifically, a set of $ k $ image for the same scene have been captured based on different light projections.
-Then, for each pixel $ (x,y) $ in the image, an equation system can be set up
+%% nnnn exp
+\section{Surface Normal Inference based on Depth Map}
+The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $.
+A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches.
+We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training.
+All the depth maps add simulated noise as introduced in \ref{sec:noise}.
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss.
+The output is directly the tangent normal in range $ \left[-1,1\right] $.
+The output and input has the same shape.
 
-\[ 
-\begin{pmatrix}
-	L_1^T \\
-	L_2^T \\
-	\cdots \\
-	L_k^T
-\end{pmatrix} g(x,y) = 
-\begin{pmatrix}
-	I_1(x,y) \\
-	I_2(x,y) \\
-	\cdots \\
-	I_3(x,y)
-\end{pmatrix}
-\]
-for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
-The equation can be solved based on least square methods. 
-Since normal $ N(x,y) $ is unit vector, thus we have
+\subsection{Qualitative Evaluation}
 
-\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]
-
-Then the normal can be obtained as follow
-
-\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]
-
-In another word, the surface normal including the albedo can be obtained directly based on a set of images and light directions.
-
-\section{Gated Convolution neural network for surface normal estimation}
-\label{sec:gcnn}
-
-Recently, deep learning based method achieved a great succeed for image processing.
-( \cite{yolov3}, \cite{efficientDet}) These network architectures use a batch of RGB / Grayscale images as input and are employed for classification problems.
-Usually, the images are convoluted with a convolution layer and downsampling with pooling layers.
-The outputs of the network consist of a single value to represent the index of the corresponding class (\cite{efficientDet}) or with a set of values to represent the position of bounding boxes.(\cite{yolov3}).
-However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input.
-Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction.
-In this case, the traditional network architecture is not suitable anymore.
-
-%% upsampling 
-It is worth to noticed that, the output of normal inference CNN model is not one or several labels but an entire image or normal map with same size. 
-%% talk about image upsampling, unet
-Recently,\cite{unet} proposed an architecture called UNet for biomedical image segmentations.
-The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size.
-The proposed network can successfully assigned each pixel a class for segmentation tasks.
-Under this symmetric network, an input image is downsampled 4 times and upsampled 4 times.
-Output image has exactly the same size as input image.
-The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.
+The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. As shown in the picture, GCNN model 
+Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_point_cloud_noise.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_groundtruth.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_GCNN3-32-512.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_SVD.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_GCNN3-32-512.png}
+	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_SVD.png}
+	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon) From left to right: Input vertex map, ground-truth, GCNN normal map, SVD normal map, GCNN error map, SVD error map}
+	\label{fig:gcnn-eval-synthetic}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=.8\textwidth]{./Figures/u-net-illustration-correct-scale2.pdf}
-	\label{fig:u-net}
-	\caption{The structure of UNet. \cite{unet}}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.15\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
+		\caption{}
+	\end{subfigure}
+	\caption{Zoom in of dragon object evaluation.}
+	\label{fig:gcnn-eval-synthetic-zoom-in}
 \end{figure}
 
-The UNet is based on standard convolution layers to construct the network. This is reasonable for image processing task with full-dense input, since no missing pixels exist. 
-However, for the input of noised point cloud, the valid and invalid pixels will be treated equally if we still perform standard convolution layers.
-Since the aim of the network is not learning the pattern of noise, but the noise with eternally changing patterns will confuse the network, and it fails the normal inference, a mask is required to distinguish two kinds of pixels.
-
-% why we need a mask
-\cite{pncnn0} use binary mask to indicate valid pixels, and further use normalized convolution to predict the output. The normalized convolution is shown as follows
-
-\begin{equation}
-	\begin{array}{rrclcl}
-		O(x,y) = 
-		\begin{cases}
-			\dfrac{\Sigma_i^k\Sigma_j^k W(i,j) \cdot I(x-i,y-j) \cdot M(x-i,y-j)}{\Sigma_i^k\Sigma_j^k W(i,j) \cdot M(x-i,y-j)}, & \text{if}\ \sum_{i}^k\sum_{j}^k M(i,j)>0 \\
-			0, & \text{otherwise}
-		\end{cases}
-	\end{array}
-\end{equation}
-
-where $ k $ is the kernel size, $ (x,y) $ is the position in input, $ (i,j) $ is the displacement in kenel, $ M $ is the corresponding mask.
-A binary mask uses 1 to indicate valid pixels and 0 otherwise.
-$ \odot $ denotes element-wise multiplication.
-
-Normalized convolution layer added the weight to the mask. However, a initialization for the mask is still required, and the propagation of the mask remain a tricky task.
-
-\subsection{Gated Convolution}
-
-% introduce gconv
-\cite{gated_activation} proposed a gated activation unit to model more complex interactions comparing to standard CNN layers, which mainly inspired by the multiplicative units exist in Long Short-Term Memory proposed by \cite{lstm} and Rated Recurrent Unit (GRU) proposed by \cite{gru}.
-\cite{gconv} employed the same gated unit solving for the free-form image inpainting task. The proposed network use 3 channel RGB images as input and estimate the missing pixels.
-
-The structure is shown in Figure \ref{fig:gconvLayer}.
-Instead of using a mask as input to indicate valid pixels, it employs a standard convolution layers to learn this mask directly from data.
-The valid pixels are then activated by a Sigmoid function.
-Then it imply element-wise multiplication with the feature map.
-Formally, the gated convolution is described as follows, the layer with input size $ (N, C_{in}, H, W) $ and output size $ (N, C_{out}, H_{out}, W_{out}) $:
-\begin{equation}\label{gconv}
-	o(N_i, C_{o_j}) = \sigma(\sum_{k=0}^{C_{in}-1}w_g(C_{o_j}, k) \star i(N_i,k) + b_g(C_{o_j})) * 
-	\phi (\sum_{k=0}^{C_{in}-1}w_f(C_{o_j}, k) \star i(N_i,k) + b_f(C_{o_j}))
-\end{equation}
-where $ \phi $ is LeakyReLU function, $ \sigma $ is sigmoid function, thus the output values are in range $ [0,1] $, $ \star $ is the valid 2D cross-correlation operator, $ N $ is batch size, $ C $ denotes a number of channels, $ H $ is a height of input planes in pixels, and $ W $ is width in pixels, $ w(C_{o_j},k) $ denotes the weight of $ j $-th output channel corresponding $ k $-th input channel, $ i(N_i, k) $denotes the input of $ i $-th batch corresponding $ k $-th input channel, $ b(C_{o_j}) $ denotes the bias of $ j $-th output channel.
-
-% Gated Convolution Layer
+The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
 \begin{figure}[th]
 	\centering
-	\begin{tikzpicture}
-		\tikzstyle{rect} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!20]
-		\tikzstyle{arrow} = [thick,->,>=stealth]
-		\node (output) [rect] {Output};
-		\node (oplus) [below of=output, yshift=-.2cm] {$\Huge\oplus $};
-		\node (LeakyReLU) [rect,below of=oplus, yshift=-0.4cm] {Feature};
-		\node (sigmoid) [rect, below of=oplus, yshift=-0.4cm, xshift=-4cm] {Mask};
-
-		\node (conv1) [rect,below of=sigmoid, yshift=-1cm] {Mask};
-		\node (conv2) [rect,below of=LeakyReLU, yshift=-1cm] {Feature};
-		\node (input) [below of=oplus] at (0,-7) {\includegraphics[width=.25\textwidth]{./Figures/train-input.png}};
-
-		\draw [arrow] (oplus) -- (output);
-		\draw [arrow] (sigmoid) |- (oplus);
-		\draw [arrow] (LeakyReLU) -- (oplus);
-		\draw [arrow] (conv2) --  node [text width=2.5cm, midway, right=1em]{LeakyReLU} (LeakyReLU);
-		\draw [arrow] (conv1) --  node [text width=2.5cm, midway, right=1em]{Sigmoid} (sigmoid);
-		\draw [arrow] (input) -|  node [text width=2.5cm, midway, below=1em]{Conv2D} (conv1);
-		\draw [arrow] (input) -- node [text width=2.5cm, midway, right=1em]{Conv2D} (conv2);
-	\end{tikzpicture}
-	\caption{Gated Convolution Layer, where $ \oplus $ denotes element-wise multiplication.}
-	\label{fig:gconvLayer}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
+		\caption{point cloud}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
+		\caption{ground-truth}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
+		\caption{Angle Error}
+	\end{subfigure}
+	\caption{Evaluation on Real Dataset}
+	\label{fig:gcnn-eval-real}
 \end{figure}
 
-%\section{Canny Edge Detection for Detail Enhancement}
-%The inaccuracy part is usually concentrate in the coarse surface or drastic changed surface parts of the object.
-The corresponding part can be extracted separately via edge detector algorithms, like Canny Edge detector.
-Feed the edges to a special net for normal prediction might improve the accuracy further.
+\subsection{Quantitative Evaluation }
 
-\subsection{Architecture}
-\label{sec:architecture}
-Based on the implementation mentioned above, the architecture roughly follows on UNet proposed by \cite{unet}, as shown in Figure \ref{fig:gcnn-archi}.
+The evaluation result on test scenes is shown in Figure \ref{fig:scatter-gcnn}.
+The GCNN based method has angle error between 5 to 15 degrees in both type of inputs.
+The error trends to higher with point number decrease.
+It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution.
+Therefore the recorded surface based on the point cloud is more coarse, which also increase the difficulty of the normal inference.
 
-\begin{sidewaysfigure}[th]
+\begin{figure}[h!]
 	\centering
-	\includegraphics[width=1\textwidth]{Figures/gcnn}
-	\caption{The architecture of Gated convolution neural network (GCNN) based on Gated convolution and UNet Architecture.}
-	\label{fig:gcnn-archi}
-\end{sidewaysfigure}
-In order to describe the network in a common way, the parameters of the network are represented by letters.
-The network is constructed by a downsampling part and a upsampling part.
-In the downsampling part, the input is the $ X \in \mathbb{R}^{w\times w\times ch}$.
-The input matrix goes through 3 downsampling layer blocks, each block has two gated convolution layers with stride (1,1) and an extra gated convolution layers with stride (2,2) as a downsampling operation.
-The total three times downsamplings extract the geometry features $ X_v $ from input matrix $ X $ (represented as a regression function $ f $)
-\[ f: X \rightarrow X_f \]
-After the feature extraction, the network upsampling the feature map 3 times to get the output matrix $ Y $.
-Each upsampling consists of an interpolation operation uses nearest neighboring interpolations for resolution upsamling, then a concatenate layer that concatenate the interpolated result and the corresponding high resolution feature map  $ X_{df_1, df_2, ...} $  from the downsampling part.
-This is also called skip connection.
-In the last, a gated convolution layer is utilized to reduce the channel size to fit the next upsampling block.
-After the three times upsampling, two standard convolution layer is added in the last without activation function to predict the surface normal.
-The whole upsampling branch can be represented as a regression function $ n $,
-\[ n: X_v, X_{df_1, df_2, ...} \rightarrow N \]
-All the convolution layers in the network use same kernel size $ 3\times 3 $.
+	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-no-noise.png}
+	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-noised.png}
+	\caption{Evaluation of average angular loss on the whole test dataset with 90 scenes.
+The x-axis indicates the point number, the y-axis indicates the angles.
+The \textbf{Left} one using point cloud without noise, the \textbf{right} one has noise.}
+	\label{fig:scatter-gcnn}
+\end{figure}
 
-One of the key feature of the network is the output has the same size as the input.
-This is achieved by the (1,1) padding and the same channel number in the convolution layers.
-Thus the surface normal can be achieved 1-1 estimation.
-Another key point of the network is the robustness of the noise.
-The network takes semi-dense matrix as input then predicts the fully-dense matrix as output.
-The last feature is the multi-purpose using scenarios.
-In the description, no specific input type has been indicated.
-In this thesis, two application scenarios have been verified.
-The first is the missing-pixel estimation but with out the transformation of the style of the input matrix, which takes the semi-dense matrix as input and simply fill the missing pixels in the output.
-The second is the missing pixel estimation with style-transferred of the matrix.
-In this case, the network takes the semi-dense matrix as input, the output matrix is fully-dense but each pixel has the different meaning as the input.
-Actually, the first scenario can be consider as the specially case of the second scenario which the style of output and the input remain the same.
-The network is test in Chapter \ref{ch:05}, which is shown the good performance on noise filtering task and also the normal surface estimation task.
+\subsection{Speed}
 
-\subsection{Loss Function}
+\section{Guided Gated Convolution Neural Network for Normal Inference }
 
-\paragraph{L1 Loss}
-L1 loss, also known as absolute error loss, which calculates the absolute difference between the prediction and the ground truth. It leads to the median of the observations.
+\subsection{Light Net Evaluation}
 
-\[ L_1(\tilde y - y) = |\tilde y - y | \]
+We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.
 
-\paragraph{L2 Loss}
-The standard loss function for optimization in regression problems is the L2 loss, also known as squared error loss, which minimize the squared difference between a prediction and the actual value.
-It leads to the mean of the observations.
-\[ L_2(\tilde y - y) = \|\tilde y - y \|_2^2 \]
+A qualitative evaluation of light net is shown in Figure \ref{fig:eval-light}.
+The average angular error are lower than $ 0.3 $ degree on all of test cases.
+In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.
 
-\paragraph{Masked L2 Loss with penalty for outliers(mask-l2)}
-\label{par:maskl2}
-The background pixels of the input data are not considered in the normal inference task, they are saved as black pixels in the input data.
-These pixels should not considered in the loss function, i.e.
-invalid pixels.
-Therefore, a valid mask is required to distinguish the background and the main object.
-Specifically, using a matrix with the same width and height as the output, for each pixel, 0 is invalid, 1 is valid.
-Furthermore, depends on the specific task, the output should be constraint in a range.
-For normal output, the range is $ [-1,1] $.
-Thus for the outliers out of this range, a outlier mask can be applied to give them a penalty.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
 
-\begin{equation}\label{gcnn-loss}
-	\begin{array}{ll}
-		l(x,y)&= L  = \{l_1, ..., l_N\}^T\\ 
-		l_{n\in N} &= \| mask_{obj} \odot mask_{ol} \odot ( {\tilde y}_n - y_n) \|_2^2 + 	\| mask_{obj} \odot mask_{nol} \odot ( {\tilde y}_n - y_n) \|_2^2 \\
-	\end{array}
-\end{equation}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
 
-where $ x $ is input, $ y $ is target, $ N $ is the batch size.$ mask_{obj} $ is the mask of the object, i.e.
-1 means it is an pixel on the object, 0 is an pixel on the background.
-$ mask_{ol} $ is the mask for the outliers, i.e.
-1 means outliers, 0 means non outlier, $ mask_{nol} $ is exactly the inverse of $ mask_{ol} $.
-$ p $ is the penalty of the outliers, it is set as 1.4.
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
 
-\paragraph{Reversed Huber Loss}
+	\caption{Qualitative evaluation of light net on Sphere, bus and Washington statue.
+From left to right, grayscale image, semi-dense light map(input), full-dense light map(output), full-dense light map(ground-truth), error map.}
+	\label{fig:eval-light}
+\end{figure}
 
-\cite{berhu-loss} proposed Reversed Huber loss to combine both L1 and L2 loss. L1 loss is for small values whereas L2 for large values
-\begin{equation}\label{berhu-loss}
-	\begin{array}{ll}
-		\mathcal{B}(y)= \begin{cases}
-			|y| & |y| \le c \\
-			\dfrac{y^2 + c^2}{2d} & |x| > c\\
-		\end{cases}
-	\end{array}
-\end{equation}
-where $ c=0.2\max (|\tilde y - y|) $.
+Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases.
+The average pixel-wise angular error is 0.17 degree as shown in Table \ref{tab:model-error}.
+An regression line has been added in the plot to analysis the tendency of the errors.
+The angular error slightly goes up when valid point number in the scene increase.
+It is make sense since the valid pixels are usually connected and concentrate in a single patch, the less of the area of the patch, which corresponding the number of the valid points, the less variation of the light direction among the pixels, thus better the evaluation.
 
-\section{Guided normal inference using GCNN}
-The guided normal inference takes the light direction and the image into consideration.
-It is under the assumption that the scene image $ I $ is captured by a calibrated camera, i.e.
-knowing the intrinsic $ K $ and extrinsic camera matrix $ [R|t] $, and a the light position $ (s_x, s_y, s_z) $ of the single light source.
-The geometry based approach inference the surface normal from the point cloud, whereas the photometric stereo inference the surface normal from a set of calibrated illuminated images.
-The idea behind this chapter is that improve the geometry based approach with the help of one calibrated illuminated image.
-Since the calibrated illuminated image contains the information about the surface feature, it is supposed to help the geometry approach in a proper way.
-Based on this idea, two networks are proposed in this section.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
+	\caption{The evaluation on 100 test cases of Light Net.}
+	\label{fig:scatter-light}
+\end{figure}
 
-\subsection{Light Map}
-\label{sec:lightmap}
-The light map $ L $ can be derived from vertex map $ V $ and the light source position $ s $.
-As shown in Figure \ref{fig:lambertian-surface}, the incoming light direction is a vector point from light source to the surface point, therefor it can be calculated as follows
-\begin{equation}\label{light-direction}
-	\begin{array}{ll}
-		L(x,y)&= \dfrac{V(x,y)-(s_x,s_y)}{\|V(x,y)-(s_x,s_y)\|_2}\\ 
-	\end{array}
-\end{equation}
-\begin{figure}[H]
+\subsection{Vertex-Image-Light Net (VIL Net) Evaluation}
+
+The qualitative evaluation of VIL net uses the model trained based on masked L2 loss.
+
+\subsubsection{title}
+
+\begin{figure}[th]
 	\centering
-	{\includegraphics[width=.25\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
-	{\includegraphics[width=.25\textwidth]{./Figures/intrinsic_image_light_input.png}}
-	\caption{The light map calculated from vertex map and the light source}
-	\label{fig:light-input}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
+
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
+
+	\caption{Qualitative evaluation of Trignet net on Sphere, bus and Washington statue.
+From left to right, semi 3D vertex map, full-dense normal map(output), full-dense normal map(ground-truth), error map.}
+	\label{fig:eval-trignet}
 \end{figure}
-where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space.
-The light direction map $ L $ is normalized since only the direction of the light is considered.
-Using the equation above for all the pixels in the point cloud can obtain the corresponding light map, which is a matrix with same size as point clouds.
-However, it is important to note that due to the exist noise in the vertex map, the getting light map is only semi-dense, as shown in Figure \ref{fig:light-input}.
 
-\subsection{VIL Net}
-Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net).
-The structure is basically derived from GCNN model as mentioned in \ref{sec:gcnn}, which is shown in Figure
-\ref{fig:VIL-Net}.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
+	\caption{The evaluation on 100 test cases of Trignet.}
+	\label{fig:scatter-trignet}
+\end{figure}
 
-As mentioned in the name, the \textbf{VIL}-Net utilizes \textbf{V}ertex map, \textbf{L}ight map and \textbf{I}mage map to accomplish the normal inference task.
+\subsection{comparison}
+From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
+It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
+Then it counts the number of points locates in each section for 3 axes.
+The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
+Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
 
-The network can be consider in two parts.
-The first part extracts the feature maps from the input data.
-It deals with two kinds of input, the vertex map $ X_1 \in \mathbb{R}^{w\times h\times3}$, and the concatenation of light and image map $ X_2 \in \mathbb{R}^{w\times h\times4} $.
-The network extracts the geometry features $ X_v $ from vertex map $ X_1 $ (represented as a regression function v)
-\[ v: X_1 \rightarrow X_v \]
-and the photometric features $ X_l $ from image and the light map $ X_2 $ (represented as a regression function $ l $)
-\[ l: X_2 \rightarrow X_l \]
-where the two encoders have the same network architecture based on the downsampling part of GCNN model.
-After the feature extraction, 2 extra layers are added: 1, a concatenate layer is added to fuse the vertex feature, and the image and light map feature getting from the encoder.
-2, a fused feature map is predicted from all the feature maps base on a single gated convolution layer. (represented as a regression function $ m $)
-\[ m: [X_v X_l] \rightarrow X_f \]
-Then the network interpolates the feature maps $ X_f $ 3 times using interpolation and gated convolution layers to inference the normal map $ N $.
-Meanwhile, the skip connections fuse the high resolution features $ X_{df_1, df_2, ...} $ from the downsampling part during the upsamplings.
-The upsampling is represented as a regression function $ n $:
-\[ n: X_f, X_{df_1, df_2, ...} \rightarrow N \]
+It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
+\end{figure}
 
-With the help of an extra image-light encoder, the network gained more information of the object surface, which is supposed to predict the surface normal more accurate.
-In this scenario, the output is still the surface normal, thus the training loss can be the same as GCNN model.
+\begin{table}[th]
 
-\begin{sidewaysfigure}[th]
 	\centering
-	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
-	\caption{The architecture of TriGNet}
-	\label{fig:VIL-Net}
-\end{sidewaysfigure}
+	\begin{tabular}{l l l l l l l l }
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.} & over-perform\\
+		LightNet  & 0.17  & 4.72 & &  & & & \\ 
+		\hline
+		GCNN  & 10.57 & 5.25 & 8 & 200,1600 & 0.5 & 0 & - \\
+		\hline
+		an3 & 10.46 & 64.86 & 8 & 3,12,1000  & 0.5 & 1 & yes\\
+		\hline
+		an3 & 10.81 & 65.34 & 8 & 10,1000  & 0.5 & 1 & no(yes) \\
+		\hline
+		VIL-1 & 10.50 & 31.57 & 8 & 10,1000 & 0.5 & 1 & yes \\
+		\hline
+		VIL-1 & 10.82 & 32.61 & 8 & 3,12,1000 & 0.5 & 1 & no(yes) \\
+		\hline
+		VIL-3  & 10.79 & 54.76 & 8 & 100,1000 & 0.1 & 3 & no(yes) \\
+		\hline
+		VIL-10  & 11.10 & 132.32 & 8 & 100,1000 & 0.1 &10 & no(yes)\\
+	\end{tabular}
+	\caption{The error of models.
+The angle error is the average angle error of all valid pixels in the test case.
+The time unit is millisecond.
+bz is the batch size, lr-schedule is learning rate schedule.
+lr-df is learning rate decay factor, l/i.
+Nr is the number of light-image maps used for each scene}
+	\label{tab:model-error}
+\end{table}
 
-\subsection{An3 Net}
-The first branch (shown above) takes a light map introduced in \ref{sec:lightmap} as the input, the structure is the same as GCNN architecture except that the last two standard convolution layers, the skip connections are kept to connect the 3 down/up samplings.
-The second branch (shown below) takes image as the input, the structure is the same as the first branch other than the input image is 1 channel but not 3 channels. 
-The third branch takes the 3D vertex map as the input.
-The structure is based on GCNN architecture.
-However, in order to merge the other two branches, the vertex branch equips 4 times fusions in the up sampling part.
-Specifically, the first fusion locates immediately after the last gconv layer of the last down sampling, the second fusion after the second gconv layer of first up sampling, the third fusion after the second gconv layer of second up sampling, the fourth fusion after the second gconv layer of the third up sampling.
-Each fusion follows by an interpolation layer, a gconv layer to reduce the channel back to 32, a skip connection concatenate layer and another gconv layer to reduce the channel back to 32.
-After the fourth fusion, a gconv layer used for channel reduction, 2 standard conv layer for output prediction.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=\linewidth]{./Figures/regression-comparison.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
+\end{figure}
 

### 2022-07-25 paper/main.tex
update an2 (Trignet)
update light

@@
 \usepackage{import}
+\usepackage{float}
 \usepackage{tikz}
@@
 
-\begin{notations}{ll} % Include a list of abbreviations (a table of two columns)
+\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
 
@@
 
-\end{notations}
-
-%----------------------------------------------------------------------------------------
-%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
-%----------------------------------------------------------------------------------------
-
-\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
-
-% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
-
-Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
-%Constant Name & $Symbol$ & $Constant Value$ with units\\
-
-\end{constants}
+\end{abbreviations}
 
@@
 
-\begin{operations}{ll} % Include a list of Symbols (a three column table)
+\begin{symbols}{ll} % Include a list of Symbols (a three column table)
 
@@
 
-\addlinespace % Gap to separate the Roman symbols from the Greek
-
-$\omega$ & angular frequency & \si{\radian} \\
-
-\end{operations}
+\end{symbols}
 

### 2022-07-25 common/ResNormalGuided.py

@@ -30,7 +30,7 @@ class GConv(_ConvNd):
 class NormalGuided(nn.Module):
     def __init__(self, in_ch, out_ch, c_num):
         super().__init__()
-        # self.__name__ = 'resng'
+        # self.__name__ = 'vertex'
         kernel_down = (3, 3)
         kernel_up = (3, 3)
         padding_down = (1, 1)

### 2022-07-25 common/StandardNNN.py

@@ -15,7 +15,6 @@ output: normal  (3,512,512)
 class NormalNN(nn.Module):
     def __init__(self, in_ch, out_ch, ch_size):
         super().__init__()
-        self.__name__ = 'NormalNN'
         kernel_down = (3, 3)
         kernel_up = (3, 3)
         padding_down = (1, 1)
@@ -39,8 +38,8 @@ class NormalNN(nn.Module):
         self.uconv2 = Conv(channel_size_2, channel_size_1, kernel_up, stride, padding_up, active_function="LeakyReLU")
         self.uconv3 = Conv(channel_size_2, channel_size_1, kernel_up, stride, padding_up, active_function="LeakyReLU")
 
-        self.conv1 = Conv(channel_size_1, out_ch, (1, 1), (1, 1), (0, 0), active_function="LeakyReLU")
-        self.conv2 = Conv(out_ch, out_ch, (1, 1), (1, 1), (0, 0))
+        self.conv1 = nn.Conv2d(channel_size_1, out_ch, (1, 1), (1, 1), (0, 0))
+        self.conv2 = nn.Conv2d(out_ch, out_ch, (1, 1), (1, 1), (0, 0))
 
     def forward(self, x0):
         x1 = self.dconv1(x0)

### 2022-07-25 config.py

@@ -35,9 +35,9 @@ gcnn_model_64 = ws_path / "nnnn" / "trained_model" / "64" / "checkpoint.pth.tar"
 gcnn_model_128 = ws_path / "nnnn" / "trained_model" / "128" / "checkpoint.pth.tar"
 gcnn_model_256 = ws_path / "nnnn" / "trained_model" / "256" / "checkpoint.pth.tar"
 gcnn_model_512 = ws_path / "nnnn" / "trained_model" / "512" / "checkpoint.pth.tar"
-gcnn_3_32 = ws_path / "resng" / "trained_model" / "512" / "checkpoint-3-32.pth.tar"
+gcnn_3_32 = ws_path / "vertex" / "trained_model" / "512" / "checkpoint-3-32.pth.tar"
 
-resng_model_64 = ws_path / "resng" / "trained_model" / "64" / "checkpoint.pth.tar"
-resng_model_128 = ws_path / "resng" / "trained_model" / "128" / "checkpoint.pth.tar"
-resng_model_256 = ws_path / "resng" / "trained_model" / "256" / "checkpoint.pth.tar"
-resng_model_512 = ws_path / "resng" / "trained_model" / "512" / "checkpoint.pth.tar"
+resng_model_64 = ws_path / "vertex" / "trained_model" / "64" / "checkpoint.pth.tar"
+resng_model_128 = ws_path / "vertex" / "trained_model" / "128" / "checkpoint.pth.tar"
+resng_model_256 = ws_path / "vertex" / "trained_model" / "256" / "checkpoint.pth.tar"
+resng_model_512 = ws_path / "vertex" / "trained_model" / "512" / "checkpoint.pth.tar"

### 2022-07-25 paper/akweury/document.tex
update nnnn

@@
 \section{GCNN model evaluation}
-The GCNN model is the base model of the whole thesis. In this section, we first discuss the noise filter performance of the model and then evaluate the performance on normal inference.
+The GCNN model is the base model of the whole thesis.
+In this section, we first evaluate the inpainting performance of the model based on light map input.
+Then we use the same model for normal inference task.
 
-\subsection{Noise Filter Result}
+\subsection{Light Inpainting}
+The light inpainting task in this section in order to evaluate the noise inpainting performance of GCNN model.
+It takes semi-dense light map as input to predict the fully dense light map, as shown in Figure \ref{fig:light-net-archi}.
 
@@
 		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
+		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light_input.png}};
 		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
@@
 		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};
+		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light.png}};
+		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {fully-dense Light Map};
 
@@
 
-		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
+		\node[text width=3.5cm] at (\vdist*\disttimes+0.3,\yschift-1) {GCNN};
 	\end{tikzpicture}
-	\caption{Light Net for light inpainting based on GCNN architecture.}
+	\caption{Light map inpainting based on GCNN architecture.}
 	\label{fig:light-net-archi}
 \end{figure}
+
+The network is trained on 3000 light maps in the "synthetic-50-5" dataset with initial learning rate 0.001, learning schedule 8,1000 with decay factor 0.5, the batch size is 8, the feature map channel is 128 in all of the gated convolution layers.
+The result is shown in Table \ref{tab:light-inpainting}
+
+\begin{table}[th]
+
+	\centering
+	\begin{tabular}{l l l l l l l l }
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.} & over-perform\\
+		LightNet  & 0.17  & 4.72 & &  & & & \\ 
+		\hline
+		GCNN  & 10.57 & 5.25 & 8 & 200,1600 & 0.5 & 0 & - \\
+		\hline
+		an3 & 10.46 & 64.86 & 8 & 3,12,1000  & 0.5 & 1 & yes\\
+		\hline
+		an3 & 10.81 & 65.34 & 8 & 10,1000  & 0.5 & 1 & no(yes) \\
+		\hline
+		VIL-1 & 10.50 & 31.57 & 8 & 10,1000 & 0.5 & 1 & yes \\
+		\hline
+		VIL-1 & 10.82 & 32.61 & 8 & 3,12,1000 & 0.5 & 1 & no(yes) \\
+		\hline
+		VIL-3  & 10.79 & 54.76 & 8 & 100,1000 & 0.1 & 3 & no(yes) \\
+		\hline
+		VIL-10  & 11.10 & 132.32 & 8 & 100,1000 & 0.1 &10 & no(yes)\\
+	\end{tabular}
+	\caption{The error of models.
+The angle error is the average angle error of all valid pixels in the test case.
+The time unit is millisecond.
+bz is the batch size, lr-schedule is learning rate schedule.
+lr-df is learning rate decay factor, l/i.
+Nr is the number of light-image maps used for each scene}
+	\label{tab:light-inpainting}
+\end{table}
 

### 2022-07-25 help_funs/worksheet.py

@@ -26,9 +26,9 @@ def gau_histo(gt_normal, sigma):
 
 def load_a_training_tensor():
     test_0_data = np.array(
-        sorted(glob.glob(str(config.synthetic_data_noise_local / "synthetic512" / "selval" / "tensor" /
+        sorted(glob.glob(str(config.synthetic_data_noise_local / "synthetic128" / "selval" / "tensor" /
                              f"*_0_*"), recursive=True)))
-    test_0 = torch.load(test_0_data[1])
+    test_0 = torch.load(test_0_data[0])  # 0, 3, 5
     test_0_tensor = test_0['input_tensor'].unsqueeze(0)
     gt_tensor = test_0['gt_tensor'].unsqueeze(0)
     return test_0_tensor, gt_tensor
@@ -68,41 +68,44 @@ def visual_albedo_histo(albedo_gt):
 if __name__ == '__main__':
     training_tensor, gt_tensor = load_a_training_tensor()
     vertex = training_tensor[:, :3, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
-    light_input = training_tensor[:, 4:7, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
-    light_gt = gt_tensor[:, 5:8, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
+    light_input = training_tensor[:, 13:16, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
+    light_gt = gt_tensor[:, 13:16, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
     normal_gt = gt_tensor[:, :3, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
     img_gt = gt_tensor[:, 4:5, :, :].permute(2, 3, 1, 0).squeeze(-1).squeeze(-1).numpy()
-    g_gt = gt_tensor[:, 3:4, :, :].permute(2, 3, 1, 0).squeeze(-1).squeeze(-1).numpy()
+    # g_gt = gt_tensor[:, 3:4, :, :].permute(2, 3, 1, 0).squeeze(-1).squeeze(-1).numpy()
 
     img_gt_norm = img_gt / 255
-    albedo_gt = img_gt_norm / (g_gt + 1e-20)
+    # albedo_gt = img_gt_norm / (g_gt + 1e-20)
 
     # tranculation
     tranculate_threshold = 1
 
[…]

### 2022-07-25 paper/akweury/document.tex
update eval

@@
 The network is trained on 3000 light maps in the "synthetic-50-5" dataset with initial learning rate 0.001, learning schedule 8,1000 with decay factor 0.5, the batch size is 8, the feature map channel is 128 in all of the gated convolution layers.
-The result is shown in Table \ref{tab:light-inpainting}
-
+The result is shown in Table \ref{tab:light-inpainting} In order to show the performance of the model in a better way, we use two extra model as the comparison.
+The first one is GCNN-NOC, where NOC means "no skip connection", the second one is CNN, which has the same architecture as the GCNN but only use standard convolution layers in the network.
+%% TODO: add the experiment result and analysis.
 \begin{table}[th]
@@
 	\centering
-	\begin{tabular}{l l l l l l l l }
-		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.} & over-perform\\
-		LightNet  & 0.17  & 4.72 & &  & & & \\ 
+	\begin{tabular}{l l l l l l }
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
+		GCNN  & 0.17  & 4.72 & 8 & 8,1000 & 0.5\\ 
 		\hline
-		GCNN  & 10.57 & 5.25 & 8 & 200,1600 & 0.5 & 0 & - \\
+		GCNN-NOC  &  &  & 8 & 8,1000 & 0.5\\
 		\hline
-		an3 & 10.46 & 64.86 & 8 & 3,12,1000  & 0.5 & 1 & yes\\
-		\hline
-		an3 & 10.81 & 65.34 & 8 & 10,1000  & 0.5 & 1 & no(yes) \\
-		\hline
-		VIL-1 & 10.50 & 31.57 & 8 & 10,1000 & 0.5 & 1 & yes \\
-		\hline
-		VIL-1 & 10.82 & 32.61 & 8 & 3,12,1000 & 0.5 & 1 & no(yes) \\
-		\hline
-		VIL-3  & 10.79 & 54.76 & 8 & 100,1000 & 0.1 & 3 & no(yes) \\
-		\hline
-		VIL-10  & 11.10 & 132.32 & 8 & 100,1000 & 0.1 &10 & no(yes)\\
+		CNN & & & & 8,1000 & 0.5\\
 	\end{tabular}
-	\caption{The error of models.
+	\caption{The inpainting performance of the GCNN model for light map inpainting.
 The angle error is the average angle error of all valid pixels in the test case.
-The time unit is millisecond.
-bz is the batch size, lr-schedule is learning rate schedule.
-lr-df is learning rate decay factor, l/i.
-Nr is the number of light-image maps used for each scene}
+bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}
 	\label{tab:light-inpainting}
@@
 
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_img.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_input.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_gt.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light.png}
+	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light.png}
+	\caption{GCNN Normal Inference for light map inpainting based on dragon object.
+From left to right, grayscale image, semi-dense light map(input), ground-truth light map, predicted light map, the angle error of the predicted light map.}
+	\label{fig:gcnn-eval-synthetic}
+\end{figure}
+
+\newpage
 %% nnnn exp
-\section{Surface Normal Inference based on Depth Map}
-The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $.
-A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches.
-We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training.
-All the depth maps add simulated noise as introduced in \ref{sec:noise}.
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss.
-The output is directly the tangent normal in range $ \left[-1,1\right] $.
-The output and input has the same shape.
+\subsection{Surface Normal Inference based on GCNN}
 
-\subsection{Qualitative Evaluation}
-
-The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. As shown in the picture, GCNN model 
-Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
 \begin{figure}[th]
@@
 
+We evaluate the performance of the normal inference task based on a single GCNN architecture.
+The model is trained on 3000 images from "synthetic50-5" dataset.
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
+
+The model takes a single vertex map as input and predict the corresponding normal map in the output.
+A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval-synthetic} and Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the neighbor based approach based on SVD optimization is considered as a base line.
+The GCNN based approach has apparently better performance than SVD based approach, which get rid of the trace of the noise in the input vertex map.
+Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
+ As shown in the figure, the area of beard of the dragon and its neck are on the different surface, which can be easily seen on GCNN result, whereas the SVD based approach is confused and get a very randomly surface normal.
+
 The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
@@
 
-\subsection{Quantitative Evaluation }
-
-The evaluation result on test scenes is shown in Figure \ref{fig:scatter-gcnn}.
+We evaluate the GCNN model on 100 test images as a quantitative evaluation.
+The result is shown in Figure \ref{fig:scatter-gcnn}.
 The GCNN based method has angle error between 5 to 15 degrees in both type of inputs.
-The error trends to higher with point number decrease.
+The error trends to higher when point number decreases.
 It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution.
@@
 
-\subsection{Speed}
-
+\newpage
 \section{Guided Gated Convolution Neural Network for Normal Inference }

### 2022-07-25 help_funs/chart.py

@@ -54,6 +54,8 @@ def scatter_chart(data_x, data_y, path, title=None, x_scale=None, y_scale=None, 
                   x_label=None, y_label=None, show=False, log_y=False, cla_leg=False):
     if data_x.shape[1] <= 1:
         return
+
+    plt.figure(figsize=(10, 6))
     for i, row in enumerate(data_x):
         b, a = np.polyfit(data_x[i], data_y[i], deg=1)
         plt.scatter(data_x[i], data_y[i], label=labels[i])
@@ -72,7 +74,8 @@ def scatter_chart(data_x, data_y, path, title=None, x_scale=None, y_scale=None, 
         plt.yscale('log')
 
     plt.legend()
-    plt.figure(figsize=(10, 10 * 0.618))
+
+    # plt.figure(figsize=(1000, 1000 * 0.618))
     if not os.path.exists(str(path)):
         os.mkdir(path)
     plt.savefig(

### 2022-07-26 paper/akweury/document.tex
update eval and light model

@@
 The first one is GCNN-NOC, where NOC means "no skip connection", the second one is CNN, which has the same architecture as the GCNN but only use standard convolution layers in the network.
+All the models are tested on a laptop with a single NVIDIA GeForce 940MX, 2GB memory.
 %% TODO: add the experiment result and analysis.
@@
 		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
-		GCNN  & 0.17  & 4.72 & 8 & 8,1000 & 0.5\\ 
+		U-GCNN  & 0.59  & 14.45 & 8 & 8,1000 & 0.5\\ 
 		\hline
-		GCNN-NOC  &  &  & 8 & 8,1000 & 0.5\\
+		U-GCNN-NOC & 1.31 & 16.14 & 8 & 8,1000 & 0.5\\
 		\hline
-		CNN & & & & 8,1000 & 0.5\\
+		U-CNN & 4.10 & 10.52 & 8 & 8,1000 & 0.5\\
 	\end{tabular}
-	\caption{The inpainting performance of the GCNN model for light map inpainting.
+	\caption{The performance of the GCNN model for light map inpainting.
 The angle error is the average angle error of all valid pixels in the test case.

### 2022-07-26 paper/akweury/document.tex
update paper

@@
 \documentclass[border=15pt, multi, tikz]{article}
-\usepackage{amssymb}
 \usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
@@
 Each vertex map has dimension $ 128\times 128\times3 $, light map has $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
 The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
@@
 It takes semi-dense light map as input to predict the fully dense light map, as shown in Figure \ref{fig:light-net-archi}.
+The network is trained on 3000 light maps in the "synthetic-50-5" dataset with initial learning rate 0.001, learning schedule 8,1000 with decay factor 0.5, the batch size is 8, the feature map channel is 128 in all of the gated convolution layers.
+All the models are tested on a laptop with a single NVIDIA GeForce 940MX, 2GB memory.
 
+%% light eval model structure
 \begin{figure}[th]
@@
 
-The network is trained on 3000 light maps in the "synthetic-50-5" dataset with initial learning rate 0.001, learning schedule 8,1000 with decay factor 0.5, the batch size is 8, the feature map channel is 128 in all of the gated convolution layers.
-The result is shown in Table \ref{tab:light-inpainting} In order to show the performance of the model in a better way, we use two extra model as the comparison.
+The result is shown in Table \ref{tab:light-inpainting}.
+Besides the GCNN model, we use two extra model as the comparisons.
 The first one is GCNN-NOC, where NOC means "no skip connection", the second one is CNN, which has the same architecture as the GCNN but only use standard convolution layers in the network.
-All the models are tested on a laptop with a single NVIDIA GeForce 940MX, 2GB memory.
-%% TODO: add the experiment result and analysis.
-\begin{table}[th]
+The GCNN architecture achieves the average angle error lower than 1 degree.
+As a comparison, U-CNN model has 4 degrees error, which shows the relative weakness of noise filter competence.
+Besides, the skip connection also booster the performance, since the no skip connection version still has error greater than 1 degree.
+The both two models for the inpainting task reveals the superiority of GCNN architecture.
+Figure \ref{fig:light-scatter} and \ref{fig:light-eval} gives a quantitative and qualitative evaluation.
+
+%% light eval table
+\begin{table}[H]
 
@@
 
-\begin{figure}[th]
+%% light eval visualization
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light.png}
-	\caption{GCNN Normal Inference for light map inpainting based on dragon object.
-From left to right, grayscale image, semi-dense light map(input), ground-truth light map, predicted light map, the angle error of the predicted light map.}
-	\label{fig:gcnn-eval-synthetic}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_img.png}
+		\caption{gray-scale image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_input.png}
+		\caption{Vertex(Input)}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_gt.png}
+		\caption{ground-truth}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light-cnn.png}
+	\caption{U-CNN}
+\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light-noc.png}
+	\caption{U-GCNN-NOC}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light.png}
+	\caption{U-GCNN Error}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light-cnn.png}
+	\caption{U-CNN Error}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light-noc.png}
+	\caption{U-NOC Error}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+	\node[text width=0.1\textwidth] at (10,-1) {90};
+	\node[inner sep=0pt] (input) at (8,-1)
+	{\includegraphics[width=.2\textwidth]{./Figures/colorscale_hot-vertical.jpg}};
+	\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{GCNN Normal Inference for light map inpainting based on dragon object. The degree error map is shown in last row. The average error is shown in the upper right corner in the error map.}
+	\label{fig:light-eval}
 \end{figure}
 
-\newpage
-%% nnnn exp
-\subsection{Surface Normal Inference based on GCNN}
-
-\begin{figure}[th]
+%% light eval scatter
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_point_cloud_noise.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_groundtruth.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_GCNN3-32-512.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_SVD.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_GCNN3-32-512.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_SVD.png}
-	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon) From left to right: Input vertex map, ground-truth, GCNN normal map, SVD normal map, GCNN error map, SVD error map}
-	\label{fig:gcnn-eval-synthetic}
+	\includegraphics[width=0.9\linewidth]{./Figures/gcnn-light/scatter-light.png}
+	\caption{GCNN for light map inpainting on 100 scenes.
+The evaluated models are corresponding to the table \ref{tab:light-inpainting}, the line in the figure is the corresponding regression line of each model.}
+	\label{fig:light-scatter}
 \end{figure}
 
-\begin{figure}[th]
+%% nnnn exp
+\subsection{Surface Normal Inference}
+
+We evaluate geometry based approach for surface normal estimation using a pure GCNN architecture.
+The input of the model is 3D vertex map whereas the output is directly the corresponding tangent surface normal map in range $ [-1,1] $.
+The training parameters are as same as light inpainting task mentioned above.
+
+A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval-synthetic} and Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, theb SVD approach is considered as a base line.
+The GCNN based approach has apparently better performance than SVD based approach, which completely get rid of the trace of the noise in the input vertex map.
+Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the right leg area of the Washington statue object to give a closer comparison with the ground-truth.
+As shown in the figure, the GCNN method successfully predict the surface connection area between the lower hem of the gown and the stone chair, whereas the no skip version is blurry in the same area.
+The two surface is still distinguishable but the sharp details has been lost.
+The CNN version has the skip connection thus gives a better detail than NOC version.
+However, if we compare the error map of U-GCNN and U-CNN in figure \ref{fig:gcnn-eval-synthetic}, the basement of the stone chair that Washington sit is actually a smooth flat stage, the U-GCNN shows an accurate predict, but the same area in U-CNN has an average higher error.
+The whole basement surface has a overall higher error.
+It holds also for the other smooth areas like the side of the stone chair, the gown and the upper body of the statue.
+It is because the noise of the input still disturb the CNN model and take the input noise into account for normal estimation which deviate to the correct surface normal.
+When we look back to the U-GCNN based method, we can found that the surface normal has better performance in the smooth area compare to the CNN approach and a sharp detail compare to the no skip connection version.
+
+%% gcnn-eval
+\begin{figure}[H]
 	\centering
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
-		\caption{Input}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_groundtruth.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_img.png}
 		\caption{GT}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-GCNN.png}
+		\caption{U-GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-CNN.png}
+		\caption{U-CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-NOC.png}
+		\caption{U-NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_SVD.png}
+	\caption{SVD}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{Surface Normal Inference based GCNN model on "Washington´´ object. The first row shows the estimated surface normal. The second row is the degree error map.}
+	\label{fig:gcnn-eval}
+\end{figure}
+
+%% fig:gcnn-eval-synthetic-zoom-in
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-GCNN.png}
 		\caption{GCNN}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-NOC.png}
+		\caption{NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-CNN.png}
+		\caption{CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_SVD.png}
 	\caption{SVD}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
-		\caption{}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
-		\caption{}
-	\end{subfigure}
-	\caption{Zoom in of dragon object evaluation.}
+
+	\caption{Zoom in of the center region of Washington object. The first row is surface normal, the second row is the corresponding errors.}
 	\label{fig:gcnn-eval-synthetic-zoom-in}
@@
 
-We evaluate the performance of the normal inference task based on a single GCNN architecture.
-The model is trained on 3000 images from "synthetic50-5" dataset.
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
-
-The model takes a single vertex map as input and predict the corresponding normal map in the output.
-A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval-synthetic} and Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the neighbor based approach based on SVD optimization is considered as a base line.
-The GCNN based approach has apparently better performance than SVD based approach, which get rid of the trace of the noise in the input vertex map.
-Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
- As shown in the figure, the area of beard of the dragon and its neck are on the different surface, which can be easily seen on GCNN result, whereas the SVD based approach is confused and get a very randomly surface normal.
-
 The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
+%% fig:gcnn-eval-real
 \begin{figure}[th]
@@
 
-We evaluate the GCNN model on 100 test images as a quantitative evaluation.
+We evaluate the U-GCNN model on 100 test images as a quantitative evaluation.
 The result is shown in Figure \ref{fig:scatter-gcnn}.
-The GCNN based method has angle error between 5 to 15 degrees in both type of inputs.
-The error trends to higher when point number decreases.
-It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution.
-Therefore the recorded surface based on the point cloud is more coarse, which also increase the difficulty of the normal inference.
+The GCNN based method has average angle error around 10 degrees, whereas the no skip connection version has error above 12 degrees and the CNN version has error above 15 degrees.
 
+%% scatter_gcnn
 \begin{figure}[h!]
 	\centering
-	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-no-noise.png}
-	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-noised.png}
-	\caption{Evaluation of average angular loss on the whole test dataset with 90 scenes.
+	\includegraphics[width=.8\textwidth]{./Figures/gcnn-synthetic/gcnn-scatter.png}
+	\caption{Evaluation of average angular loss on the whole test dataset with 100 scenes.
 The x-axis indicates the point number, the y-axis indicates the angles.
-The \textbf{Left} one using point cloud without noise, the \textbf{right} one has noise.}
+The lines show in the picture are the regression line of each model.}
 	\label{fig:scatter-gcnn}
@@
 \newpage
-\section{Guided Gated Convolution Neural Network for Normal Inference }
+\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }
 

### 2022-07-26 eval.py

@@ -91,12 +91,13 @@ if __name__ == '__main__':
         # "an-8-1000": config.paper_exp / "an" / "checkpoint-526.pth.tar",
         # "vil10-8-1000": config.paper_exp / "vil10" / "checkpoint-10-8-1000-489.pth.tar",
 
+        "light-gcnn": config.paper_exp / "light" / "checkpoint-gcnn-348.pth.tar",
         # "light-gcnn": config.paper_exp / "light" / "checkpoint-640.pth.tar",
         # "light-noc": config.paper_exp / "light" / "checkpoint-noc-499.pth.tar",
         # "light-cnn": config.paper_exp / "light" / "checkpoint-cnn-599.pth.tar",
 
-        # "gcnn-cnn": config.paper_exp / "gcnn" / "checkpoint-cnn-473.pth.tar",
-        # "gcnn-noc": config.paper_exp / "gcnn" / "checkpoint-noc-619.pth.tar",
+        # "gcnn-cnn": config.paper_exp / "gcnn" / "checkpoint-cnn-858.pth.tar",
+        # "gcnn-noc": config.paper_exp / "gcnn" / "checkpoint-noc-955.pth.tar",
         # "gcnn-gcnn": config.paper_exp / "gcnn" / "checkpoint-gcnn-1099.pth.tar",
 
         # record

### 2022-07-27 paper/akweury/document.tex
update an2

@@
 
-\subsection{Light Net Evaluation}
-
 We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.
@@
 In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.
-
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
-
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
-
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
-
-	\caption{Qualitative evaluation of light net on Sphere, bus and Washington statue.
-From left to right, grayscale image, semi-dense light map(input), full-dense light map(output), full-dense light map(ground-truth), error map.}
-	\label{fig:eval-light}
-\end{figure}
 
@@
 
-\begin{figure}[th]
+%% gcnn-eval
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
-	\caption{The evaluation on 100 test cases of Light Net.}
-	\label{fig:scatter-light}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-GCNN.png}
+		\caption{U-GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-CNN.png}
+		\caption{U-CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-NOC.png}
+		\caption{U-NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{Surface Normal Inference based GCNN model on "Washington´´ object. The first row shows the estimated surface normal. The second row is the degree error map.}
+	\label{fig:gcnn-eval}
 \end{figure}
 
-\subsection{Vertex-Image-Light Net (VIL Net) Evaluation}
+%% fig:gcnn-eval-synthetic-zoom-in
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_SVD.png}
+	\end{subfigure}
 
-The qualitative evaluation of VIL net uses the model trained based on masked L2 loss.
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-NOC.png}
+		\caption{NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-CNN.png}
+		\caption{CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
 
-\subsubsection{title}
-
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}
-
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}
-
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
-	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}
-
-	\caption{Qualitative evaluation of Trignet net on Sphere, bus and Washington statue.
-From left to right, semi 3D vertex map, full-dense normal map(output), full-dense normal map(ground-truth), error map.}
-	\label{fig:eval-trignet}
-\end{figure}
-
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
-	\caption{The evaluation on 100 test cases of Trignet.}
-	\label{fig:scatter-trignet}
+	\caption{Zoom in of the center region of Washington object. The first row is surface normal, the second row is the corresponding errors.}
+	\label{fig:gcnn-eval-synthetic-zoom-in}
 \end{figure}

### 2022-07-27 common/AlbedoGatedNNN.py

@@ -168,6 +168,433 @@ class GNet(nn.Module):
         return xout
 
 
+class GNetF3F(nn.Module):
+    # 3 times fusion (First three fusions are kept)
+    def __init__(self, in_ch, out_ch, channel_num):
+        super().__init__()
+        # self.__name__ = 'gnet'
+        kernel_down = (3, 3)
+        kernel_up = (3, 3)
+        padding_down = (1, 1)
+        padding_up = (1, 1)
+        stride = (1, 1)
+        stride_2 = (2, 2)
+
+        channel_size_1 = channel_num
+        channel_size_2 = channel_num * 2
+        channel_size_3 = channel_num * 3
+        # https://homepages.inf.ed.ac.uk/rbf/CVonline/LOCAL_COPIES/PIRODDI1/NormConv/node2.html#:~:text=The%20idea%20of%20normalized%20convolution,them%20is%20equal%20to%20zero.
+        self.dconv1 = GConv(in_ch, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv2 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.dconv4 = GConv(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
+
+        self.l_dconv1 = GConv(in_ch, channel_size_1, kernel_down, stride, padding_down)
+        self.l_dconv2 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.l_dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.l_dconv4 = GConv(channel_size_1, channel_size_1, kernel_down, stride_2, padding_down)
+
+        self.i_dconv1 = GConv(1, channel_size_1, kernel_down, stride, padding_down)
+        self.i_dconv2 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
+        self.i_dconv3 = GConv(channel_size_1, channel_size_1, kernel_down, stride, padding_down)
[…]

### 2022-07-27 paper/akweury/document.tex
update eval

@@
 
+For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net that introduced in \ref{sec:trip-net}. 
+The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
+As a comparison, we create a similar model, which keeps the vertex and light pipes same but replace the image pipe with standard convolution layers (corresponding "AN" model in the figures and tables).
+
+The quantitative evaluation is shown in figure \ref{fig:trip-scatter}.
 We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.

### 2022-07-30 paper/akweury/document.tex
update an2

--- 2022-07-27 paper/akweury/document.tex
@@
 The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
-The input matrix has $ 128\times 128 $ height and width.
-Each vertex map has dimension $ 128\times 128\times3 $, light map has $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.
+The screen size is $ 128\times 128 $ in height and width.
+The corresponding vertex matrix has dimension $ 128\times 128\times3 $, light map has dimension $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.
 The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
@@
 The GCNN model is the base model of the whole thesis.
-In this section, we first evaluate the inpainting performance of the model based on light map input.
-Then we use the same model for normal inference task.
+The architecture is described in \ref{sec:gcnn}.
+We use a single GCNN to estimate the surface normal based on geometry information.
+It uses vertex map as input to estimate the corresponding tangent surface normal map.
+%% gcnn-eval
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
+		\caption{CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
+		\caption{NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{Surface Normal Inference based GCNN model on "Dragon´´ object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\label{fig:gcnn-eval}
+\end{figure}
+
+A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
+SVD approach is considered as the baseline shown in last column.
+As shown in the figure, learning based methods performs better than SVD in terms of angle error.
+The SVD approach is failed to deal with semi-dense input since there exists many points that missing neighbors.
+The GCNN model is especially good at noise input due to the gated convolution layer design.
+As a further detailed comparison, \ref{fig:gcnn-eval-synthetic-zoom-in} gives a closer visualization on the same object.
+
+%% fig:gcnn-eval-synthetic-zoom-in
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-NOC.png}
+		\caption{NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-CNN.png}
+		\caption{CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+
+	\caption{Zoom in of the center region of Dragon object.
+The first row is surface normal, the second row is the corresponding errors.
+NOC model has no skip connnection, CNN model replace gated convolution layer to standard convolution layer.}
+	\label{fig:gcnn-eval-synthetic-zoom-in}
+\end{figure}
+As shown in figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the GCNN method gives a sharper edge prediction on the horn area of the dragon object, as well as the scales, whereas the no skip version (NOC) is blurry in the same area.
+
+The CNN version has the skip connection thus gives a better detail than NOC model.
+However, if we compare the error map of GCNN and CNN in figure \ref{fig:gcnn-eval}, the CNN has less accurate in the smooth area than GCNN model.
+Like the dragon body, CNN model has a overall higher error than GCNN.
+It is because the noise of the input still disturb the CNN model and it takes the input noise into account for normal estimation which deviate to the correct surface normal.
+When we look back to the GCNN based method, we can found that the surface normal has better performance in the smooth area compare to the CNN approach and a sharp detail compare to the no skip connection version.
+
+Table \ref{tab:gcnn-eval} gives a quantitative evaluation for GCNN model. It bases on 100 different test scenes in the "synthetic-50-5´´ dataset with angle metrics for evaluation.
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l }
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
+		SVD(baseline)  & 41.14  & 320.40 & 8 & 8,1000 & 0.5\\ 
+		\hline
+		GCNN  & 10.64  & 10.44 & 8 & 8,1000 & 0.5\\ 
+		\hline
+		GCNN-NOC & 13.61 & 5.38 & 8 & 8,1000 & 0.5\\
+		\hline
+		CNN & 15.35 & 4.15 & 8 & 8,1000 & 0.5\\
+	\end{tabular}
+	\caption{The performance of the GCNN model for geometry information based normal inference.
+The angle error is the average angle error of all valid pixels in the test case.
+bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}
+	\label{tab:gcnn-eval}
+\end{table}
+
+\newpage
+\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }
+
+For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
+The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
+As a comparison, we placed GCNN result in the last column.
+The training settings for all the models are exact the same to ensure fairness.
+As shown in the figure, TripNet uses illuminated calibrated RGBD image has a better performance than GCNN model.
+The dragon scales are sharper in TripNet result.
+Figure \ref{fig:tripnet-eval-synthetic-zoom-in} gives a closer visualization.
+%% TripNet-eval
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
+		\caption{TripNet}
+	\end{subfigure}
+\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
+	\caption{GCNN}
+\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{TripNet qualitative evaluation. Surface Normal Inference on ``Dragon" object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\label{fig:trip-eval}
+\end{figure}
+
+%% tripNet zoom in eval
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_an2-8-1000.png}
+	\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+
+	\caption{Zoom in of the center region of Dragon object. The first row is surface normal, the second row is the corresponding errors.}
+	\label{fig:tripnet-eval-synthetic-zoom-in}
+\end{figure}
+
+\subsection{comparison}
+From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
+It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
+Then it counts the number of points locates in each section for 3 axes.
+The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
+Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
+
+It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
+\end{figure}
+
+\begin{table}[th]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.}\\
+		SVD  & 41.14  & 320.40 & - & - & - & 0 \\ 
+		\hline
+		GCNN  & 10.64 & 10.44 & 8 & 8,1000 & 0.5 & 0 \\
+		\hline
+		TripNet-CNN & 10.46 & 28.74 & 8 & 8,1000  & 0.5 & 1 \\
+		\hline
+		TripNet-F1B & \textbf{9.26} & 43.79 & 8 & 8,1000  & 0.5 & 1 \\
+		\hline
+		TripNet & \textbf{9.17} & 43.79 & 8 & 8,1000  & 0.5 & 1 \\
+	\end{tabular}
+	\caption{A quantitative evaluation on proposed approaches.
+The angle error is the average angle error of all valid pixels in the test case.
+The time unit is millisecond.
+bz is the batch size, lr-schedule is learning rate schedule.
+lr-df is learning rate decay factor, l/i.
+Nr is the number of light-image maps used for each scene}
+	\label{tab:model-error}
+\end{table}
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=\linewidth]{./Figures/regression-comparison.png}
+	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
+The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
+(The chart is based on the "dragon" scene showing above)}
+	\label{fig:normal-histo-diff}
+\end{figure}
 
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_img.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
 		\caption{gray-scale image}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-			\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_input.png}
-		\caption{Vertex(Input)}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_input.png}
+		\caption{Light Direction}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_gt.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_gt.png}
 		\caption{ground-truth}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-gcnn.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light-cnn.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-cnn.png}
 		\caption{U-CNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_light-noc.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-noc.png}
 		\caption{U-GCNN-NOC}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-gcnn.png}
 		\caption{U-GCNN Error}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light-cnn.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-cnn.png}
 		\caption{U-CNN Error}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-light/fancy_eval_1_light_error_light-noc.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-noc.png}
 		\caption{U-NOC Error}
@@
 	\label{fig:light-scatter}
-\end{figure}
-
-%% nnnn exp
-\subsection{Surface Normal Inference}
-
-We evaluate geometry based approach for surface normal estimation using a pure GCNN architecture.
-The input of the model is 3D vertex map whereas the output is directly the corresponding tangent surface normal map in range $ [-1,1] $.
-The training parameters are as same as light inpainting task mentioned above.
-
-A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval-synthetic} and Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, theb SVD approach is considered as a base line.
-The GCNN based approach has apparently better performance than SVD based approach, which completely get rid of the trace of the noise in the input vertex map.
-Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the right leg area of the Washington statue object to give a closer comparison with the ground-truth.
-As shown in the figure, the GCNN method successfully predict the surface connection area between the lower hem of the gown and the stone chair, whereas the no skip version is blurry in the same area.
-The two surface is still distinguishable but the sharp details has been lost.
-The CNN version has the skip connection thus gives a better detail than NOC version.
-However, if we compare the error map of U-GCNN and U-CNN in figure \ref{fig:gcnn-eval-synthetic}, the basement of the stone chair that Washington sit is actually a smooth flat stage, the U-GCNN shows an accurate predict, but the same area in U-CNN has an average higher error.
-The whole basement surface has a overall higher error.
-It holds also for the other smooth areas like the side of the stone chair, the gown and the upper body of the statue.
-It is because the noise of the input still disturb the CNN model and take the input noise into account for normal estimation which deviate to the correct surface normal.
-When we look back to the U-GCNN based method, we can found that the surface normal has better performance in the smooth area compare to the CNN approach and a sharp detail compare to the no skip connection version.
-
-%% gcnn-eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-CNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-GCNN.png}
-		\caption{U-GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-CNN.png}
-		\caption{U-CNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-NOC.png}
-		\caption{U-NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_SVD.png}
-	\caption{SVD}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Surface Normal Inference based GCNN model on "Washington´´ object. The first row shows the estimated surface normal. The second row is the degree error map.}
-	\label{fig:gcnn-eval}
-\end{figure}
-
-%% fig:gcnn-eval-synthetic-zoom-in
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-CNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-NOC.png}
-		\caption{NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-CNN.png}
-		\caption{CNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_SVD.png}
-	\caption{SVD}
-	\end{subfigure}
-
-	\caption{Zoom in of the center region of Washington object. The first row is surface normal, the second row is the corresponding errors.}
-	\label{fig:gcnn-eval-synthetic-zoom-in}
 \end{figure}
@@
 
-\newpage
-\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }
-
-We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.
-
-A qualitative evaluation of light net is shown in Figure \ref{fig:eval-light}.
-The average angular error are lower than $ 0.3 $ degree on all of test cases.
-In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.
-
-Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases.
-The average pixel-wise angular error is 0.17 degree as shown in Table \ref{tab:model-error}.
-An regression line has been added in the plot to analysis the tendency of the errors.
-The angular error slightly goes up when valid point number in the scene increase.
-It is make sense since the valid pixels are usually connected and concentrate in a single patch, the less of the area of the patch, which corresponding the number of the valid points, the less variation of the light direction among the pixels, thus better the evaluation.
-
-%% gcnn-eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-CNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-GCNN.png}
-		\caption{U-GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-CNN.png}
-		\caption{U-CNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_GCNN-NOC.png}
-		\caption{U-NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_5_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Surface Normal Inference based GCNN model on "Washington´´ object. The first row shows the estimated surface normal. The second row is the degree error map.}
-	\label{fig:gcnn-eval}
-\end{figure}
-
-%% fig:gcnn-eval-synthetic-zoom-in
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_GCNN-CNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-NOC.png}
-		\caption{NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_GCNN-CNN.png}
-		\caption{CNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_5_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-
-	\caption{Zoom in of the center region of Washington object. The first row is surface normal, the second row is the corresponding errors.}
-	\label{fig:gcnn-eval-synthetic-zoom-in}
-\end{figure}
-
-\subsection{comparison}
-From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
-It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
-Then it counts the number of points locates in each section for 3 axes.
-The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
-Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
-
-It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
-	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
-The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
-(The chart is based on the "dragon" scene showing above)}
-	\label{fig:normal-histo-diff}
-\end{figure}
-
-\begin{table}[th]
-
-	\centering
-	\begin{tabular}{l l l l l l l l }
-		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.} & over-perform\\
-		LightNet  & 0.17  & 4.72 & &  & & & \\ 
-		\hline
-		GCNN  & 10.57 & 5.25 & 8 & 200,1600 & 0.5 & 0 & - \\
-		\hline
-		an3 & 10.46 & 64.86 & 8 & 3,12,1000  & 0.5 & 1 & yes\\
-		\hline
-		an3 & 10.81 & 65.34 & 8 & 10,1000  & 0.5 & 1 & no(yes) \\
-		\hline
-		VIL-1 & 10.50 & 31.57 & 8 & 10,1000 & 0.5 & 1 & yes \\
-		\hline
-		VIL-1 & 10.82 & 32.61 & 8 & 3,12,1000 & 0.5 & 1 & no(yes) \\
-		\hline
-		VIL-3  & 10.79 & 54.76 & 8 & 100,1000 & 0.1 & 3 & no(yes) \\
-		\hline
-		VIL-10  & 11.10 & 132.32 & 8 & 100,1000 & 0.1 &10 & no(yes)\\
-	\end{tabular}
-	\caption{The error of models.
-The angle error is the average angle error of all valid pixels in the test case.
-The time unit is millisecond.
-bz is the batch size, lr-schedule is learning rate schedule.
-lr-df is learning rate decay factor, l/i.
-Nr is the number of light-image maps used for each scene}
-	\label{tab:model-error}
-\end{table}
-
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=\linewidth]{./Figures/regression-comparison.png}
-	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
-The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
-(The chart is based on the "dragon" scene showing above)}
-	\label{fig:normal-histo-diff}
-\end{figure}
-
 \end{document}

### 2022-07-30 paper/Chapters/Chapter05.tex
update an (Trignet-CNN)
update dataset

--- 2022-07-07 paper/Chapters/Chapter05.tex
@@
 
-\label{ch:05} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
-The experiments are performed on two normal inference tasks: normal inference based on depth image and guided normal inference based on RGB-D image.
-Prior works for normal estimation using very deep networks.
-For a single object surface normal detection as stated in this thesis, the given methods has a similar performance but only with $ 1/10 $ size.
+The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
+The screen size is $ 128\times 128 $ in height and width.
+The corresponding vertex matrix has dimension $ 128\times 128\times3 $, light map has dimension $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
+The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
 
-The model is trained with PyTorch 1.10.2, CUDA 10.2.89, GPU with single NVIDIA GEFORCE GTX 1080Ti.
+\section{GCNN model evaluation}
+The GCNN model is the base model of the whole thesis.
+The architecture is described in \ref{sec:gcnn}.
+We use a single GCNN to estimate the surface normal based on geometry information.
+It uses vertex map as input to estimate the corresponding tangent surface normal map.
+%% gcnn-eval
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_SVD.png}
+	\end{subfigure}
 
-%% nnnn exp
-\section{Surface Normal Inference based on Depth Map}
-The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $.
-A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches.
-We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training.
-All the depth maps add simulated noise as introduced in \ref{sec:noise}.
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss.
-The output is directly the tangent normal in range $ \left[-1,1\right] $.
-The output and input has the same shape.
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
+		\caption{CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
+		\caption{NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
 
-\subsection{Qualitative Evaluation}
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
 
-The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. As shown in the picture, GCNN model 
-Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_point_cloud_noise.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_groundtruth.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_GCNN3-32-512.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_SVD.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_GCNN3-32-512.png}
-	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_SVD.png}
-	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon) From left to right: Input vertex map, ground-truth, GCNN normal map, SVD normal map, GCNN error map, SVD error map}
-	\label{fig:gcnn-eval-synthetic}
+	\caption{Surface Normal Inference based GCNN model on "Dragon´´ object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\label{fig:gcnn-eval}
 \end{figure}
 
-\begin{figure}[th]
+A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
+SVD approach is considered as the baseline shown in last column.
+As shown in the figure, learning based methods performs better than SVD in terms of angle error.
+The SVD approach is failed to deal with semi-dense input since there exists many points that missing neighbors.
+The GCNN model is especially good at noise input due to the gated convolution layer design.
+As a further detailed comparison, \ref{fig:gcnn-eval-synthetic-zoom-in} gives a closer visualization on the same object.
+
+%% fig:gcnn-eval-synthetic-zoom-in
+\begin{figure}[H]
 	\centering
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
-		\caption{Input}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-CNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
 		\caption{GT}
 	\end{subfigure}
-		\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
 		\caption{GCNN}
 	\end{subfigure}
-		\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-NOC.png}
+		\caption{NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-CNN.png}
+		\caption{CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_SVD.png}
 		\caption{SVD}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
-	\caption{}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.15\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
-		\caption{}
-	\end{subfigure}
-	\caption{Zoom in of dragon object evaluation.}
+
+	\caption{Zoom in of the center region of Dragon object.
+The first row is surface normal, the second row is the corresponding errors.
+NOC model has no skip connnection, CNN model replace gated convolution layer to standard convolution layer.}
 	\label{fig:gcnn-eval-synthetic-zoom-in}
 \end{figure}
+As shown in figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the GCNN method gives a sharper edge prediction on the horn area of the dragon object, as well as the scales, whereas the no skip version (NOC) is blurry in the same area.
 
-The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
+The CNN version has the skip connection thus gives a better detail than NOC model.
+However, if we compare the error map of GCNN and CNN in figure \ref{fig:gcnn-eval}, the CNN has less accurate in the smooth area than GCNN model.
+Like the dragon body, CNN model has a overall higher error than GCNN.
+It is because the noise of the input still disturb the CNN model and it takes the input noise into account for normal estimation which deviate to the correct surface normal.
+When we look back to the GCNN based method, we can found that the surface normal has better performance in the smooth area compare to the CNN approach and a sharp detail compare to the no skip connection version.
+
+Table \ref{tab:gcnn-eval} gives a quantitative evaluation for GCNN model. It bases on 100 different test scenes in the "synthetic-50-5´´ dataset with angle metrics for evaluation.
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l }
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
+		SVD(baseline)  & 41.14  & 320.40 & 8 & 8,1000 & 0.5\\ 
+		\hline
+		GCNN  & 10.64  & 10.44 & 8 & 8,1000 & 0.5\\ 
+		\hline
+		GCNN-NOC & 13.61 & 5.38 & 8 & 8,1000 & 0.5\\
+		\hline
+		CNN & 15.35 & 4.15 & 8 & 8,1000 & 0.5\\
+	\end{tabular}
+	\caption{The performance of the GCNN model for geometry information based normal inference.
+The angle error is the average angle error of all valid pixels in the test case.
+bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}
+	\label{tab:gcnn-eval}
+\end{table}
+
+\newpage
+\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }
+
+For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
+The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
+As a comparison, we placed GCNN result in the last column.
+The training settings for all the models are exact the same to ensure fairness.
+As shown in the figure, TripNet uses illuminated calibrated RGBD image has a better performance than GCNN model.
+The dragon scales are sharper in TripNet result.
+Figure \ref{fig:tripnet-eval-synthetic-zoom-in} gives a closer visualization.
+%% TripNet-eval
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
+		\caption{TripNet}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{TripNet qualitative evaluation. Surface Normal Inference on ``Dragon" object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\label{fig:trip-eval}
+\end{figure}
+
+%% tripNet zoom in eval
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_an2-8-1000.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+
+	\caption{Zoom in of the center region of Dragon object. The first row is surface normal, the second row is the corresponding errors.}
+	\label{fig:tripnet-eval-synthetic-zoom-in}
+\end{figure}
+
+\begin{table}[th]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.}\\
+		SVD  & 41.14  & 320.40 & - & - & - & 0 \\ 
+		\hline
+		GCNN  & 10.64 & 10.44 & 8 & 8,1000 & 0.5 & 0 \\
+		\hline
+		TripNet-CNN & 10.46 & 28.74 & 8 & 8,1000  & 0.5 & 1 \\
+		\hline
+		TripNet-F1B & 9.22 &44.59 & 8 & 8,1000  & 0.5 & 1 \\
+		\hline
+		TripNet & \textbf{9.17} & 43.79 & 8 & 8,1000  & 0.5 & 1 \\
+	\end{tabular}
+	\caption{A quantitative evaluation on proposed approaches.
+The angle error is the average angle error of all valid pixels in the test case.
+The time unit is in millisecond.
+bz is the batch size, lr-schedule is learning rate schedule.
+lr-df is learning rate decay factor, l/i.
+Nr is the number of light-image maps used for each scene}
+	\label{tab:model-error}
+\end{table}
+
+\subsection{Comparison}
+
+%% Final-Visual
 \begin{figure}[th]
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
-		\caption{point cloud}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
-		\caption{ground-truth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_an2-8-1000.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_img.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_img.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
+		\caption{TripNet}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
-		\caption{Angle Error}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_SVD.png}
+		\caption{SVD}
 	\end{subfigure}
-	\caption{Evaluation on Real Dataset}
-	\label{fig:gcnn-eval-real}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
+	\label{fig:final-eval}
 \end{figure}
 
-\subsection{Quantitative Evaluation }
+%% Final-Visual-Zoom-In
+\begin{figure}[th]
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
+	\end{subfigure}
 
-The evaluation result on test scenes is shown in Figure \ref{fig:scatter-gcnn}.
-The GCNN based method has angle error between 5 to 15 degrees in both type of inputs.
-The error trends to higher with point number decrease.
-It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution.
-Therefore the recorded surface based on the point cloud is more coarse, which also increase the difficulty of the normal inference.
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_img.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_SVD.png}
+	\end{subfigure}
 
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-no-noise.png}
-	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-noised.png}
-	\caption{Evaluation of average angular loss on the whole test dataset with 90 scenes.
-The x-axis indicates the point number, the y-axis indicates the angles.
-The \textbf{Left} one using point cloud without noise, the \textbf{right} one has noise.}
-	\label{fig:scatter-gcnn}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_img.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+
+	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
+	\label{fig:tripnet-eval-synthetic-zoom-in}
 \end{figure}
-
-\subsection{Speed}
-
-%% resng
-\section{Guided Gated Convolution Neural Network for Normal Inference }
-
-The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}.
-With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.
-
-\section{Guided Gated Convolution Neural Network for Normal Inference }
-
-From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
-It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
-Then it counts the number of points locates in each section for 3 axes.
-The 3 axes are fitted quit well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
-Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
-
-It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
-	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
-The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
-(The chart is based on the "dragon" scene showing above)}
-	\label{fig:normal-histo-diff}
-\end{figure}
-
-\newpage 
-\section{model comparison}
-This section evaluates the proposed models with the neighbor-based model and make comparison with each other.

### 2022-07-30 paper/akweury/document.tex
update dataset

@@
 
+\section{Training Details}
+
 The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
-The screen size is $ 128\times 128 $ in height and width.
-The corresponding vertex matrix has dimension $ 128\times 128\times3 $, light map has dimension $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.
+Each scene has a depth map with dimension $ 128\times 128 \times $ in height, width and channel, an image with dimension $ 128\times 128 \times 1 $.
+The depth map is converted to 3D vertex map as introduced in Chapter \ref{ch:04}.
+The light map is calculated based on vertex map and the known light position.
+We create a tensor in PyTorch that includes vertex map, image and the light direction for each scene and considered it as one training case.
+Thus 3000 scenes has corresponding 3000 training cases.
+Each scene has a corresponding ground-truth normal map for loss calculation and the evaluation.
+
+The training processes are evaluated in every 100 epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
+Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
+
+\begin{figure}[H]
+	\centering
+
+		\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.normal0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.normal0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.normal0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.normal0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.image0.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
+		\caption{CNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
+		\caption{NOC}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
+		\caption{SVD}
+	\end{subfigure}	
+	\caption{Surface Normal Inference based GCNN model on "Dragon´´ object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\label{fig:gcnn-eval}
+\end{figure}
+
 The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5. 
@@
 
-\subsection{comparison}
-From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
-It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
-Then it counts the number of points locates in each section for 3 axes.
-The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
-Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
-
-It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
-	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
-The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
-(The chart is based on the "dragon" scene showing above)}
-	\label{fig:normal-histo-diff}
-\end{figure}
-
 \begin{table}[th]
@@
 		\hline
-		TripNet-F1B & \textbf{9.26} & 43.79 & 8 & 8,1000  & 0.5 & 1 \\
+		TripNet-F1B & 9.22 &44.59 & 8 & 8,1000  & 0.5 & 1 \\
 		\hline
@@
 The angle error is the average angle error of all valid pixels in the test case.
-The time unit is millisecond.
+The time unit is in millisecond.
 bz is the batch size, lr-schedule is learning rate schedule.
@@
 
-\begin{figure}[th]
+\subsection{Comparison}
+
+\newpage
+%% Final-Visual
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=\linewidth]{./Figures/regression-comparison.png}
-	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively.
-The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis.
-(The chart is based on the "dragon" scene showing above)}
-	\label{fig:normal-histo-diff}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_img.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_SVD.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_SVD.png}
+\end{subfigure}
+
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_img.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_SVD.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_SVD.png}
+\end{subfigure}
+
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_img.png}
+	\caption{GT}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
+	\caption{TripNet}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
+	\caption{GCNN}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_SVD.png}
+	\caption{SVD}
+\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
+	\label{fig:final-eval}
 \end{figure}
+
+%% Final-Visual-Zoom-In
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_img.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_SVD.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_SVD.png}
+\end{subfigure}
+
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_img.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_SVD.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_an2-8-1000.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_SVD.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+		\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+
+	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
+	\label{fig:tripnet-eval-synthetic-zoom-in}
+\end{figure}
+
+From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
+It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
+Then it counts the number of points locates in each section for 3 axes.
+The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
+Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
+
+It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
 

### 2022-07-30 create_dataset_multi_lights.py

@@ -16,7 +16,7 @@ parser = argparse.ArgumentParser(description='Eval')
 # Machine selection
 parser.add_argument('--machine', type=str, default="local", choices=['local', 'remote'],
                     help="loading dataset from local or dfki machine")
-parser.add_argument('--data', type=str, default="synthetic128",
+parser.add_argument('--data', type=str, default="synthetic512",
                     help="choose dataset")
 parser.add_argument('--max_k', type=str, default="0",
                     help="loading dataset from local or dfki machine")
@@ -29,8 +29,8 @@ args = parser.parse_args()
 
 
 def convert2training_tensor(path, k, output_type='normal'):
-    width = 128
-    light_num = 10
+    width = 512
+    light_num = 1
     if not os.path.exists(str(path)):
         raise FileNotFoundError
     if not os.path.exists(str(path / "tensor")):
@@ -102,9 +102,9 @@ def convert2training_tensor(path, k, output_type='normal'):
         # light
         # light_pos = (data['lightPos'] - shift_vector) / scale_factors
 
-        light_direction_gt_array = np.zeros((width, width, 30))
-        light_direction_array = np.zeros((width, width, 30))
-        img_array = np.zeros((width, width, 10))
+        light_direction_gt_array = np.zeros((width, width, 3 * light_num))
+        light_direction_array = np.zeros((width, width, 3 * light_num))
+        img_array = np.zeros((width, width, 1 * light_num))
         img_file_prefix = data_files[item].split(".")[0] + ".image"
         for i in range(light_num):
             img_file = img_file_prefix + str(i) + ".png"

### 2022-07-30 paper/akweury/document.tex
update an2 model

@@
 	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.depth0_noise.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
-		\caption{GT}
+		\caption{Baoshanlu}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.image0.png}
-		\caption{GCNN}
+		\caption{Vase}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
-		\caption{CNN}
+		\caption{Garfield}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
-		\caption{NOC}
+		\caption{Dragon}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
-		\caption{SVD}
+		\caption{Bus}
 	\end{subfigure}	
-	\caption{Surface Normal Inference based GCNN model on "Dragon´´ object. The first row shows the estimated surface normal. The second row is the angle error map.}
-	\label{fig:gcnn-eval}
+	\caption{Some of the test scenes during the training. From top to bottom, normal map, depth map, noised depth map, grayscale image.}
+	\label{fig:test-scene}
 \end{figure}

### 2022-07-30 paper/akweury/document.tex
update an2 model

@@
 
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5. 
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
 The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
+It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
+We terminate the training when the evaluation on the test dataset converged.
 
-\section{GCNN model evaluation}
+\section{GCNN model evaluation based on Geometry Information}
 The GCNN model is the base model of the whole thesis.

### 2022-07-30 paper/akweury/document.tex
update nnnn model

@@
 It uses vertex map as input to estimate the corresponding tangent surface normal map.
+
+In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
+We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN".
+It is used to verify the performance the gated convolution layers.
+As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
+Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
+Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same.
+Is is designed to show the validation of skip connections.
+Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss.
+The GCNN approach achieves a lower loss from start to the end of the training.
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.8\textwidth]{./Figures/gcnn_loss_compare.png}
+	\caption{The training history of GCNN model. The line chart records the training BerHu loss of the model GCNN, NOC and CNN.}
+	\label{fig:gcnn-training-history}
+\end{figure}
+
 %% gcnn-eval

### 2022-07-30 help_funs/visual_loss_from_multi_model.py

@@ -6,10 +6,14 @@ from help_funs import chart
 
 models = {
     # "GCNN-1534": config.ws_path / "nnnn" / "trained_model" / "128" / "checkpoint-c32.pth.tar",
-    "vil10-100-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l10-100-1000.pth.tar",
-    "vil3-100-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l3-100-1000.pth.tar",
-    "vil-3-12-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l1-3-12-1000.pth.tar",
-    "vil-10-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l1-10-1000.pth.tar",
+    # "vil10-100-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l10-100-1000.pth.tar",
+    # "vil3-100-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l3-100-1000.pth.tar",
+    # "vil-3-12-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l1-3-12-1000.pth.tar",
+    # "vil-10-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l1-10-1000.pth.tar",
+
+    "GCNN": config.paper_exp / "gcnn" / "checkpoint-gcnn-1099.pth.tar",  # GCNN
+    "NOC": config.paper_exp / "gcnn" / "checkpoint-noc-807.pth.tar",
+    "CNN": config.paper_exp / "gcnn" / "checkpoint-cnn-695.pth.tar",
 
 }
 
@@ -22,5 +26,8 @@ for model_idx, (name, model) in enumerate(models.items()):
     batch_size = args.batch_size
     loss = checkpoint['losses'] / batch_size
     normal_loss_avg = np.sum(loss[:3], axis=0, keepdims=True) / 3
+    for idx in range(normal_loss_avg.shape[1]):
+        if normal_loss_avg[0, idx] == 0:
+            normal_loss_avg[0, idx] = normal_loss_avg[0, idx - 1]
     chart.line_chart(np.array(normal_loss_avg), output_folder, labels=[name], title="Loss Comparison",
-                     y_label="L2 Loss", log_y=True)
+                     y_label="L2 Loss", log_y=False)

### 2022-07-30 paper/akweury/document.tex
update nnnn model

@@
 
-\section{GCNN model evaluation based on Geometry Information}
+\section{GCNN model based on Geometry Information}
 The GCNN model is the base model of the whole thesis.
+The architecture is described in \ref{sec:gcnn}.
+We use a single GCNN to estimate the surface normal based on geometry information.
+It uses vertex map as input to estimate the corresponding tangent surface normal map.
+
+In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
+We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN".
+It is used to verify the performance the gated convolution layers.
+As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
+Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
+Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same.
+Is is designed to show the validation of skip connections.
+Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss.
+The GCNN approach achieves a lower loss from start to the end of the training.
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.8\textwidth]{./Figures/gcnn_loss_compare.png}
+	\caption{The training history of GCNN model. The line chart records the training BerHu loss of the model GCNN, NOC and CNN.}
+	\label{fig:gcnn-training-history}
+\end{figure}
+
+\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
+The Trip-Net model is the base model of the whole thesis.
 The architecture is described in \ref{sec:gcnn}.

### 2022-07-30 paper/akweury/document.tex
update nnnn model

@@
 \section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
-The Trip-Net model is the base model of the whole thesis.
-The architecture is described in \ref{sec:gcnn}.
-We use a single GCNN to estimate the surface normal based on geometry information.
-It uses vertex map as input to estimate the corresponding tangent surface normal map.
+The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train.
+It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
+For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of Trip-Net architecture.
+Since the Trip-Net is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the simplification.
+A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
+We evaluate the fusion times from 1 to 4.
+Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.
 
-In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
-We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN".
-It is used to verify the performance the gated convolution layers.
-As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
-Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
-Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same.
-Is is designed to show the validation of skip connections.
-Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss.
-The GCNN approach achieves a lower loss from start to the end of the training.
+As shown in the loss figure, ... (discussion about the figure)
 
@@
 	\includegraphics[width=.8\textwidth]{./Figures/gcnn_loss_compare.png}
-	\caption{The training history of GCNN model. The line chart records the training BerHu loss of the model GCNN, NOC and CNN.}
-	\label{fig:gcnn-training-history}
+	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
+	\label{fig:trip-net-training-history}
 \end{figure}
+
+\section{Evaluation}
 

### 2022-07-30 help_funs/visual_loss_from_multi_model.py

@@ -6,10 +6,6 @@ from help_funs import chart
 
 models = {
     # "GCNN-1534": config.ws_path / "nnnn" / "trained_model" / "128" / "checkpoint-c32.pth.tar",
-    # "vil10-100-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l10-100-1000.pth.tar",
-    # "vil3-100-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l3-100-1000.pth.tar",
-    # "vil-3-12-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l1-3-12-1000.pth.tar",
-    # "vil-10-1000": config.ws_path / "vil10" / "trained_model" / "128" / "checkpoint-l1-10-1000.pth.tar",
 
     "GCNN": config.paper_exp / "gcnn" / "checkpoint-gcnn-1099.pth.tar",  # GCNN
     # "NOC": config.paper_exp / "gcnn" / "checkpoint-noc-807.pth.tar",

### 2022-07-30 paper/akweury/document.tex
update nnnn model

@@
 For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of Trip-Net architecture.
-Since the Trip-Net is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the simplification.
+Since the Trip-Net is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
 A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
@@
 	\centering
-	\includegraphics[width=.8\textwidth]{./Figures/gcnn_loss_compare.png}
+	\includegraphics[width=.8\textwidth]{./Figures/trip_net_loss.png}
 	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}

### 2022-07-30 config.py

@@ -26,6 +26,9 @@ synthetic_data_noise_dfki = Path("/netscratch/sha/data_synthetic_noise")
 real_data = dataset / "data_real"
 real_data_dfki = Path("/netscratch/sha/data_real")
 
+# model path
+model_dfki = Path("/netscratch/sha/models")
+
 # pretrained model
 
 light_c64 = paper_exp / "light" / "checkpoint-640.pth.tar"

### 2022-07-30 help_funs/visual_loss_from_multi_model.py

@@ -11,7 +11,9 @@ models = {
     # "NOC": config.paper_exp / "gcnn" / "checkpoint-noc-807.pth.tar",
     # "CNN": config.paper_exp / "gcnn" / "checkpoint-cnn-695.pth.tar",
     "Trip-Net": config.paper_exp / "an2" / "checkpoint-8-1000-655.pth.tar",  # Trip Net
-    "Trip-Net-F1B": config.paper_exp / "an2" / "checkpoint-f1b-798.pth.tar",  # Trip Net
+    "Trip-Net-F1F": config.paper_exp / "an2" / "checkpoint-f1b-798.pth.tar",  # Trip Net
+    "Trip-Net-F2F": config.paper_exp / "an2" / "checkpoint-f1b-798.pth.tar",  # Trip Net
+    "Trip-Net-F3F": config.paper_exp / "an2" / "checkpoint-f1b-798.pth.tar",  # Trip Net
     "Trip-Net-C": config.paper_exp / "an" / "checkpoint-818.pth.tar",
 
 }

### 2022-07-30 workspace/train.py

@@ -22,7 +22,7 @@ from torch.utils.data import Dataset
 
 from help_funs import mu
 from workspace import loss_utils
-
+import config
 date_now = datetime.datetime.today().date()
 time_now = datetime.datetime.now().strftime("%H_%M_%S")
 mse_criterion = torch.nn.MSELoss(reduction='mean')
@@ -161,7 +161,10 @@ class TrainingModel():
         return train_data_loader, test_data_loader
 
     def init_output_folder(self):
-        folder_path = self.exp_dir / f"output_{date_now}_{time_now}"
+        if self.args.machine == "remote":
+            folder_path = config.model_dfki / f"output_{date_now}_{time_now}"
+        else:
+            folder_path = self.exp_dir / f"output_{date_now}_{time_now}"
         if not os.path.exists(str(folder_path)):
             os.mkdir(str(folder_path))
         return folder_path

### 2022-07-30 paper/akweury/document.tex
update an2

@@
 We evaluate the fusion times from 1 to 4.
-Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.
+We set learning rate=$ 1e-3 $.
+It goes well with GCNN model but lead to loss explosion in Trip-Net.
+Thus we set a learning rate schedule with decay step at epoch 8.
+The decay factor is $ 0.5$.
+The batch size is chosen 8.
 
-As shown in the loss figure, ... (discussion about the figure)
+Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss. As shown in the loss figure, ... (discussion about the figure)
 
@@
 \section{Evaluation}
+We evaluate the trained models on ``synthetic-50-5".
+5 different objects are included with 100 scenes in total.
+The test objects do not exist in the training dataset.
+The dataset is evaluated based on angle metrics.
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l }
+		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
+		Baoshanlu  & 38.53  &11.09 & 13.59 & 15.55 & 9.82\\ 
+		\hline
+		Bus & 32.61  & 7.82 & 8.98 & 11.95 & 7.35\\ 
+		\hline
+		Dragon &45.04& 10.61 & 15.31 & 16.05 & 7.35\\
+		\hline
+		Garfield & 42.15& 10.22 & 12.52 & 14.47 & 9.15\\
+		\hline
+		Washington &47.36 & 13.47 & 17.65 & 18.78 & 12.18\\
+	\end{tabular}
+	\caption{The performance of the GCNN model for geometry information based normal inference.
+The angle error is the average angle error of all valid pixels in the test case.
+bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}
+	\label{tab:gcnn-eval}
+\end{table}
 

### 2022-07-31 paper/akweury/document.tex
update an

@@
 	\centering
-	\begin{tabular}{l l l l l l }
-		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
-		Baoshanlu  & 38.53  &11.09 & 13.59 & 15.55 & 9.82\\ 
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
+		Baoshanlu  		& 20 & 38.53  &11.09 & 13.59 & 15.55 & 9.82\\ 
 		\hline
-		Bus & 32.61  & 7.82 & 8.98 & 11.95 & 7.35\\ 
+		Bus 			& 20 & 32.61  & 7.82 & 8.98 & 11.95 & 7.35\\ 
 		\hline
-		Dragon &45.04& 10.61 & 15.31 & 16.05 & 7.35\\
+		Dragon  		& 20 & 45.04& 10.61 & 15.31 & 16.05 & 7.35\\
 		\hline
-		Garfield & 42.15& 10.22 & 12.52 & 14.47 & 9.15\\
+		Garfield 		& 20 & 42.15& 10.22 & 12.52 & 14.47 & 9.15\\
 		\hline
-		Washington &47.36 & 13.47 & 17.65 & 18.78 & 12.18\\
+		Washington 		& 20 & 47.36 & 13.47 & 17.65 & 18.78 & 12.18\\
 	\end{tabular}
-	\caption{The performance of the GCNN model for geometry information based normal inference.
-The angle error is the average angle error of all valid pixels in the test case.
-bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}
-	\label{tab:gcnn-eval}
+	\caption{Average Angle Error of the evaluation dataset.}	
+	\label{tab:gcnn-eval-mean}
+\end{table}
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
+		Baoshanlu  		& 20 & 38.53  &8.86 & 13.59 & 15.55 & 9.82\\ 
+		\hline
+		Bus 			& 20 & 32.61  & 4.44 & 4.44 & 11.95 & 7.35\\ 
+		\hline
+		Dragon	 		& 20 & 45.04 & 7.62 & 7.62 & 16.05 & 7.35\\
+		\hline
+		Garfield 		& 20 & 42.15 & 6.40 & 6.40 & 14.47 & 9.15\\
+		\hline
+		Washington 		& 20 & 47.36 & 7.64 & 17.65 & 18.78 & 12.18\\
+	\end{tabular}
+	\caption{Median Angle Error of the evaluation dataset.}	
+	\label{tab:gcnn-eval-median}
+\end{table}
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
+		Baoshanlu  		& 20 & 0.56  & 0.25 & 13.59 & 15.55 & 9.82\\ 
+		\hline
+		Bus 			& 20 & 32.61  & 0.56 & 8.98 & 11.95 & 7.35\\ 
+		\hline
+		Dragon 			& 20 & 45.04& 0.31 & 15.31 & 16.05 & 7.35\\
+		\hline
+		Garfield 		& 20 & 42.15& 0.41 & 12.52 & 14.47 & 9.15\\
+		\hline
+		Washington 		& 20 & 47.36 & 0.38 & 17.65 & 18.78 & 12.18\\
+	\end{tabular}
+	\caption{5 Average Angle Error of the evaluation dataset.}	
+	\label{tab:gcnn-eval-d5}
+\end{table}
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
+		Baoshanlu  	& 20 & 0.81 & 0.62 & 13.59 & 15.55 & 9.82\\ 
+		\hline
+		Bus 		& 20 & 32.61 & 0.81 & 8.98 & 11.95 & 7.35\\ 
+		\hline
+		Dragon 		& 20 & 45.04 & 0.69 & 15.31 & 16.05 & 7.35\\
+		\hline
+		Garfield 	& 20 & 42.15 & 0.72 & 12.52 & 14.47 & 9.15\\
+		\hline
+		Washington 	& 20 & 47.36 & 0.62 & 17.65 & 18.78 & 12.18\\
+	\end{tabular}
+	\caption{11.5 Average Angle Error of the evaluation dataset.}	
+	\label{tab:gcnn-eval-d11}
+\end{table}
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
+		Baoshanlu  & 20 & 0.90  &	0.90 & 13.59 & 15.55 & 9.82\\ 
+		\hline
+		Bus & 20 & 32.61  &			0.93 & 8.98 & 11.95 & 7.35\\ 
+		\hline
+		Dragon & 20 & 45.04& 		0.90 & 15.31 & 16.05 & 7.35\\
+		\hline
+		Garfield & 20 & 42.15& 		0.90 & 12.52 & 14.47 & 9.15\\
+		\hline
+		Washington & 20 & 47.36 &	0.81 & 17.65 & 18.78 & 12.18\\
+	\end{tabular}
+	\caption{22.5 Average Angle Error of the evaluation dataset.}	
+	\label{tab:gcnn-eval-d22}
+\end{table}
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
+		Baoshanlu  & 20 & 0.96  &0.96 & 13.59 & 15.55 & 9.82\\ 
+		\hline
+		Bus & 20 & 32.61  & 0.96 & 8.98 & 11.95 & 7.35\\ 
+		\hline
+		Dragon & 20 & 45.04& 0.95 & 15.31 & 16.05 & 7.35\\
+		\hline
+		Garfield & 20 & 42.15& 0.94 & 12.52 & 14.47 & 9.15\\
+		\hline
+		Washington & 20 & 47.36 &0.88 & 17.65 & 18.78 & 12.18\\
+	\end{tabular}
+	\caption{30 Angle Error of the evaluation dataset.}	
+	\label{tab:gcnn-eval-d30}
 \end{table}

### 2022-07-31 help_funs/mu.py

@@ -50,9 +50,29 @@ def radian_between_tensor(v1, v2):
 def avg_angle_between_tensor(v1, v2):
     radian_diff = radian_between_tensor(v1, v2)
     deg_diff = torch.rad2deg(radian_diff)
+    deg_diff[deg_diff > 90] = 180 - deg_diff[deg_diff > 90]
+
+    deg_diff_5 = deg_diff > 5
+    deg_diff_5 = deg_diff_5.sum() / deg_diff.count_nonzero()
+
+    deg_diff_11d25 = deg_diff > 11.25
+    deg_diff_11d25 = deg_diff_11d25.sum() / deg_diff.count_nonzero()
+
+    deg_diff_22d5 = deg_diff > 22.5
+    deg_diff_22d5 = deg_diff_22d5.sum() / deg_diff.count_nonzero()
+
+    deg_diff_30 = deg_diff > 30
+    deg_diff_30 = deg_diff_30.sum() / deg_diff.count_nonzero()
+
     avg_angle = deg_diff.sum() / deg_diff.size()[0]
-    avg_angle[avg_angle > 90] = 180 - avg_angle[avg_angle > 90]
-    return avg_angle
+    median_angle = deg_diff.median()
+
+    return avg_angle.to("cpu").detach().numpy(), \
+           median_angle.to("cpu").detach().numpy(), \
+           deg_diff_5.to("cpu").detach().numpy(), \
+           deg_diff_11d25.to("cpu").detach().numpy(), \
+           deg_diff_22d5.to("cpu").detach().numpy(), \
+           deg_diff_30.to("cpu").detach().numpy()
 
 
 def vertex2light_direction(vertex_map, light_sorce):

### 2022-07-31 workspace/eval.py

@@ -30,8 +30,9 @@ def eval(dataset_path, name, model_path, gpu=0, data_type="normal_noise"):
         # load dataset
         dataset = SyntheticDepthDataset(dataset_path, 0, data_type, setname="individual")
         data_loader = DataLoader(dataset, shuffle=False, batch_size=1, num_workers=1)
-        loss_list, time_list, size_list = svd.eval(data_loader, 2)
-        return loss_list, time_list, size_list
+        loss_list, time_list, size_list, median_loss_list, d5_list, d11_list, d22_list, d30_list = svd.eval(data_loader,
+                                                                                                            2)
+        return loss_list, time_list, size_list, median_loss_list, d5_list, d11_list, d22_list, d30_list
 
     # load model
     checkpoint = torch.load(model_path)
@@ -57,8 +58,14 @@ def eval(dataset_path, name, model_path, gpu=0, data_type="normal_noise"):
     print(f'ok, {data_loader.dataset.__len__()} items.')
 
     loss_list = np.zeros(data_loader.dataset.__len__())
+    median_loss_list = np.zeros(data_loader.dataset.__len__())
     time_list = np.zeros(data_loader.dataset.__len__())
     size_list = np.zeros(data_loader.dataset.__len__())
+
+    d5_list = np.zeros(data_loader.dataset.__len__())
+    d11_list = np.zeros(data_loader.dataset.__len__())
+    d22_list = np.zeros(data_loader.dataset.__len__())
+    d30_list = np.zeros(data_loader.dataset.__len__())
 
     for i, (input, target, scale_factor) in enumerate(data_loader):
         with torch.no_grad():
@@ -91,15 +98,21 @@ def eval(dataset_path, name, model_path, gpu=0, data_type="normal_noise"):
 
                 normal = out[:, :3, :, :].permute(0, 2, 3, 1).squeeze(0)
                 normal_target = target[:, :3, :, :].permute(0, 2, 3, 1).squeeze(0)
-                diff = mu.avg_angle_between_tensor(normal[mask], normal_target[mask]).to("cpu").detach().numpy()
+                diff, median_err, deg_diff_5, deg_diff_11d25, deg_diff_22d5, deg_diff_30 = mu.avg_angle_between_tensor(
+                    normal[mask], normal_target[mask])
 
             loss_list[i] = diff
             time_list[i] = gpu_time * 1000
 
+            median_loss_list[i] = median_err
[…]

### 2022-07-31 paper/akweury/document.tex
update evaluation

--- 2022-07-30 paper/akweury/document.tex
@@
 
-The training processes are evaluated in every 100 epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
-Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
-
 \begin{figure}[H]
@@
 
-		\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.normal0.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.normal0.png}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0.png}
 \end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0_noise.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.image0.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.normal0.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
 	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.normal0.png}
 \end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
 	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.normal0.png}
 \end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
+	\caption{Depth Map}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
+	\caption{Add noise}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
+	\caption{Image}
+\end{subfigure}
+\begin{subfigure}[b]{0.20\linewidth}
 	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
+	\caption{Normal}
 \end{subfigure}
 
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.depth0_noise.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
-		\caption{Baoshanlu}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.image0.png}
-		\caption{Vase}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
-		\caption{Garfield}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
-		\caption{Dragon}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
-		\caption{Bus}
-	\end{subfigure}	
-	\caption{Some of the test scenes during the training. From top to bottom, normal map, depth map, noised depth map, grayscale image.}
+	\caption{Some of the test scenes during the training. From top to bottom, baoshanlu, Washington, Garfield, Dragon, Bus}
 	\label{fig:test-scene}
 \end{figure}
+
+The training processes are evaluated in every epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
+Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
+Note that the position of objects are not placed naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
 
@@
 	\centering
-	\includegraphics[width=.8\textwidth]{./Figures/gcnn_loss_compare.png}
-	\caption{The training history of GCNN model. The line chart records the training BerHu loss of the model GCNN, NOC and CNN.}
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
+	\caption{The training history of GCNN model.
+The line chart records the training BerHu loss of the model GCNN, NOC and CNN.
+The left shows the training loss history whereas the right one shows the evaluation loss history.}
 	\label{fig:gcnn-training-history}
@@
 It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
-For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of Trip-Net architecture.
-Since the Trip-Net is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
-A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
+For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
+Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
+A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $F, where $ x $ denotes the fusion times.
 We evaluate the fusion times from 1 to 4.
+For the learning rate.
+we set $ 1e-3 $.
+It goes well with GCNN model but lead to loss explosion in Trip-Net.
+Thus we set a learning rate schedule with an extra decay step at epoch 8.
+The decay factor is $ 0.5$.
+The batch size is chosen as 8.
+
 Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.
-
-As shown in the loss figure, ... (discussion about the figure)
+As shown in the loss figure, all of the four models has a reasonable learning rate.
+Trip-Net with four times fusion converges faster than others and also achieve a lower loss.
+Trip-Net-F3F converges slower than Trip-Net but achieved to a similar evaluation loss.
+The evaluation loss in Trip-Net-F1F and Trip-Net-F2F are relative higher than 3 or 4 times fusions model.
 
@@
 	\centering
-	\includegraphics[width=.8\textwidth]{./Figures/trip_net_loss.png}
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
 	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
@@
 
+However, the sacrifice of accuracy gives a relatively lighter model.
+Since we remove the fusions between different pipes, the corresponding upsampling layers in the image and light pipes can also be removed.
+The model can be trained faster and the size is reduced as well.
+Table \ref{tab:trip-net-size-compare} gives a comparison of the size and training time among different models.
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB} & \tabhead{Time /h}\\
+		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106  &  9.82\\ 
+		\hline
+		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 &  7.35\\ 
+		\hline
+		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 &  7.35\\
+		\hline
+		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
+		\hline
+		GCNN 					& 32 & 32 & 0 & 0 & 46 & 2.18\\
+	\end{tabular}
+	\caption{Model information.
+Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
+Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
+}
+	\label{tab:gcnn-eval-mean}
+\end{table}
+
 \section{Evaluation}
+We evaluate the trained models on ``synthetic-50-5".
+5 objects are considered in the test dataset.
+They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $.
+Each object has 20 scenes with total 100 scenes for 5 objects.
+The test objects do not exist in the training dataset.
+We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified.
+$ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $.
+$ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.
+
+Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis.
+When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
+When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
+
+Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation.
+Note that the input vertex map is only semi-dense.
+One of the benefit of GCNN architecture is the robust to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
+
+\paragraph{Average Angle Error Metric}
+The metric calculate the average angle error for each point between the inferred normal and ground-truth normal. 
+\paragraph{Median Angle Error Metric}
+The metric calculate the median angle error of all the point in the normal map.
+\paragraph{5 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 5 degrees comparing to ground-truth.
+\paragraph{11.5 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 11.5 degrees comparing to ground-truth.
+\paragraph{22.5 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 22.5 degrees comparing to ground-truth.
+\paragraph{30 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 30 degrees comparing to ground-truth.
+
+%% mean metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & & & & 9.82 \\ 
+		\hline
+		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & & & & 7.32\\ 
+		\hline
+		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & & & & 7.35 \\
+		\hline
+		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & & & & 9.15 \\
+		\hline
+		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & & & & 12.13\\
+	\end{tabular}
+	\caption{Average Angle Error of the evaluation dataset.}	
+	\label{tab:eval-mean}
+\end{table}
+
+%% median metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & & & & 7.62 \\ 
+		\hline
+		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & & & & 4.01 \\ 
+		\hline
+		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & & & & 5.06 \\
+		\hline
+		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & & & & 5.81\\
+		\hline
+		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& & & & 6.76\\
+	\end{tabular}
+	\caption{Median Angle Error of the evaluation dataset.}	
+	\label{tab:eval-median}
+\end{table}
+
+%% 5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l |l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & & & & 0.31\\ 
+		\hline
+		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & & & & 0.59 \\ 
+		\hline
+		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & & & & 0.50\\
+		\hline
+		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & & & & 0.45\\
+		\hline
+		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & & & & 0.41\\
+	\end{tabular}
+	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
+	\label{tab:eval-5d}
+\end{table}
+
+%% 11.5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 & & & & 0.69\\ 
+		\hline
+		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & & & & 0.83 \\ 
+		\hline
+		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & & & & 0.82\\
+		\hline
+		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 & & & & 0.75\\
+		\hline
+		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & & & & 0.66\\
+	\end{tabular}
+	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
+	\label{tab:eval-11d}
+\end{table}
+
+%% 22.5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & & & & 0.92\\ 
+		\hline
+		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & & & & 0.94\\ 
+		\hline
+		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & & & & 0.95\\
+		\hline
+		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & & & & 0.91\\
+		\hline
+		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & & & & 0.84\\
+	\end{tabular}
+	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
+	\label{tab:eval-22d}
+\end{table}
+
+%% 30 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & & & & 0.97 \\ 
+		\hline
+		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & & & & 0.96 \\ 
+		\hline
+		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & & & & 0.98 \\
+		\hline
+		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & & & & 0.95 \\
+		\hline
+		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & & & & 0.90\\
+	\end{tabular}
+	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
+	\label{tab:eval-30d}
+\end{table}
 
@@
 	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
+		\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
 		\caption{GT}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
+		\caption{Predict}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
-		\caption{TripNet}
-	\end{subfigure}
-\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-	\caption{GCNN}
+	\caption{Error}
 \end{subfigure}
@@
 
-	\caption{TripNet qualitative evaluation. Surface Normal Inference on ``Dragon" object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\caption{Normal inference based on Trip-Net. Test image resolution $ 128\times128 $}
 	\label{fig:trip-eval}

### 2022-07-31 eval.py

@@ -18,7 +18,7 @@ def get_args():
     parser = argparse.ArgumentParser(description='Eval')
 
     # Mode selection
-    parser.add_argument('--data', type=str, default='synthetic128', help="choose evaluate dataset")
+    parser.add_argument('--data', type=str, default='synthetic512', help="choose evaluate dataset")
     parser.add_argument('--gpu', type=int, default=0, help="choose GPU index")
     parser.add_argument('--data-type', type=str, default="normal_noise", help="choose data type")
     parser.add_argument('--machine', type=str, default="local", choices=['local', 'remote'],
@@ -96,15 +96,19 @@ if __name__ == '__main__':
                         help="loading dataset from local or dfki machine")
     args = parser.parse_args()
 
-    # test_folder = config.synthetic_data_noise_local / "synthetic128"
-    test_folder = config.real_data
+    test_folder = config.synthetic_data_noise_local / "synthetic512"
+    # test_folder = config.real_data
     models = {
         # test
         # "light-gcnn": config.paper_exp / "light" / "checkpoint-640.pth.tar",
         # "light-noc": config.paper_exp / "light" / "checkpoint-noc-499.pth.tar",
         # "light-cnn": config.paper_exp / "light" / "checkpoint-cnn-599.pth.tar",
 
-        "SVD": None,
+        # "SVD": None,
+
+        "GCNN-512": config.ws_path / "nnnn" / "output_2022-07-30_16_43_11" / "checkpoint-138.pth.tar",  # GCNN
+        # "GCNN-512": config.ws_path / "nnnn" / "output_2022-07-30_16_43_11" / "model_best.pth.tar",  # GCNN
+        "Trip-Net-512": config.ws_path / "an2" / "output_2022-07-30_16_35_38" / "checkpoint-32.pth.tar",  # GCNN
 
         # "GCNN-GCNN": config.paper_exp / "gcnn" / "checkpoint-gcnn-1099.pth.tar",  # GCNN
         # "GCNN-NOC": config.paper_exp / "gcnn" / "checkpoint-noc-807.pth.tar",

### 2022-07-31 eval_single_obj.py

@@ -56,13 +56,13 @@ def main(models, test_folder, args, name):
         loss_list, time_list, size_list, median_loss_list, d5_list, d11_list, d22_list, d30_list = eval.eval(
             test_folder, name, model, gpu=args.gpu, data_type=args.data_type)
 
-        loss_avg[name] = np.array(loss_list).sum() / np.array(loss_list).shape[0]
-        time_avg[name] = np.array(time_list)[5:].sum() / np.array(time_list)[5:].shape[0]
-        median_avg[name] = np.array(median_loss_list).sum() / np.array(median_loss_list).shape[0]
-        d5_avg[name] = np.array(d5_list).sum() / np.array(d5_list).shape[0]
-        d11_avg[name] = np.array(d11_list).sum() / np.array(d11_list).shape[0]
-        d22_avg[name] = np.array(d22_list).sum() / np.array(d22_list).shape[0]
-        d30_avg[name] = np.array(d30_list).sum() / np.array(d30_list).shape[0]
+        loss_avg[name] = ("%.2f" % (np.array(loss_list).sum() / np.array(loss_list).shape[0]))
+        time_avg[name] = ("%.2f" % (np.array(time_list)[5:].sum() / np.array(time_list)[5:].shape[0]))
+        median_avg[name] = ("%.2f" % (np.array(median_loss_list).sum() / np.array(median_loss_list).shape[0]))
+        d5_avg[name] = ("%.2f" % (1 - np.array(d5_list).sum() / np.array(d5_list).shape[0]))
+        d11_avg[name] = ("%.2f" % (1 - np.array(d11_list).sum() / np.array(d11_list).shape[0]))
+        d22_avg[name] = ("%.2f" % (1 - np.array(d22_list).sum() / np.array(d22_list).shape[0]))
+        d30_avg[name] = ("%.2f" % (1 - np.array(d30_list).sum() / np.array(d30_list).shape[0]))
         losses.append(loss_list)
         times.append(time_list[5:])
         sizes.append(size_list)
@@ -82,7 +82,7 @@ def main(models, test_folder, args, name):
                   # 'times': times,
                   'test_folder': str(test_folder),
                   }
-    print(f"{name}: {str(loss_avg.values())}")
+    print(f"mean: {str(loss_avg.values())}")
     print(f"median: {str(median_avg.values())}")
[…]

### 2022-07-31 eval_zoom_in.py

@@ -1,0 +1,201 @@
+"""
+input: an image, the incomplete depth map of the image
+output: predicted normal map
+"""
+import argparse
+import datetime
+import glob
+import os
+
+import cv2 as cv
+import numpy as np
+import torch
+
+import config
+from help_funs import mu
+from workspace.svd import eval as svd
+
+
+############ EVALUATION FUNCTION ############
+def evaluate_epoch(args, model, input_tensor, device):
+    model.eval()  # Swith to evaluate mode
+    with torch.no_grad():
+        input_tensor = input_tensor.to(device)
+        torch.cuda.synchronize()
+        # Forward Pass
+        output = model(input_tensor)
+        # store the predicted normal
+        output = output[0, :].permute(1, 2, 0)
+        output = output.to('cpu').numpy()
+        output[output > 1] = 1
+        output[output < -1] = -1
+    return output[:, :, :3]
+
+
+def preprocessing(models):
+    parser = argparse.ArgumentParser(description='Eval')
+
+    # Mode selection
+    parser.add_argument('--data', type=str, default='synthetic_noise', help="choose evaluate dataset")
+    parser.add_argument('--datasize', type=str, default='synthetic128', help="choose evaluate dataset size")
+
+    parser.add_argument('--machine', type=str, default="local", choices=['local', 'remote'],
+                        help="loading dataset from local or dfki machine")
+    args = parser.parse_args()
+
+    # load data file names
+    if args.data == "synthetic_noise":
+        path = config.synthetic_data_noise_local / args.datasize / "selval" / "tensor"
+    elif args.data == "synthetic_noise_dfki":
+        path = config.synthetic_data_noise_dfki / args.datasize / "test" / "tensor"
+    elif args.data == "synthetic":
+        path = config.synthetic_data / "test" / "tensor"  # key tests 103, 166, 189,9
+    elif args.data == "real":
+        path = config.real_data / "tensor"  # key tests 103, 166, 189,9
+    elif args.data == "paper":
+        path = config.paper_pic
+    else:
+        raise ValueError
+    # test dataset indices
[…]

### 2022-07-31 workspace/train.py

@@ -20,9 +20,10 @@ from torch.optim import SGD, Adam, lr_scheduler
 from torch.utils.data import DataLoader
 from torch.utils.data import Dataset
 
+import config
 from help_funs import mu
 from workspace import loss_utils
-import config
+
 date_now = datetime.datetime.today().date()
 time_now = datetime.datetime.now().strftime("%H_%M_%S")
 mse_criterion = torch.nn.MSELoss(reduction='mean')
@@ -747,10 +748,6 @@ def main(args, exp_dir, network, train_dataset):
         # Save checkpoint in case evaluation crashed
         nn_model.save_checkpoint(is_best, epoch)
 
-        if epoch > 10:
-            if np.isnan(np.sum(loss[:3, epoch])):
-                print("loss is nan.")
-                break
         if np.sum(loss[:3, epoch]) > 1e+4:
             print("loss is greater than 1e+4.")
             break

### 2022-07-31 paper/Chapters/Chapter05.tex
update eval

@@
 
+\section{Training Details}
+
 The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
-The screen size is $ 128\times 128 $ in height and width.
-The corresponding vertex matrix has dimension $ 128\times 128\times3 $, light map has dimension $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
+Each scene has a depth map with dimension $ 128\times 128 \times $ in height, width and channel, an image with dimension $ 128\times 128 \times 1 $.
+The depth map is converted to 3D vertex map as introduced in Chapter \ref{ch:04}.
+The light map is calculated based on vertex map and the known light position.
+We create a tensor in PyTorch that includes vertex map, image and the light direction for each scene and considered it as one training case.
+Thus 3000 scenes has corresponding 3000 training cases.
+Each scene has a corresponding ground-truth normal map for loss calculation and the evaluation.
+
+\begin{figure}[H]
+	\centering
+
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.normal0.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.image0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.normal0.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.normal0.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.normal0.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
+		\caption{Depth Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
+		\caption{Add noise}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
+		\caption{Normal}
+	\end{subfigure}
+
+	\caption{Some of the test scenes during the training. From top to bottom, baoshanlu, Washington, Garfield, Dragon, Bus}
+	\label{fig:test-scene}
+\end{figure}
+
+The training processes are evaluated in every epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
+Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
+Note that the position of objects are not placed naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
+
+The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
 The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
+It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
+We terminate the training when the evaluation on the test dataset converged.
 
-\section{GCNN model evaluation}
+\section{GCNN model based on Geometry Information}
 The GCNN model is the base model of the whole thesis.
@@
 It uses vertex map as input to estimate the corresponding tangent surface normal map.
-%% gcnn-eval
+
+In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
+We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN".
+It is used to verify the performance the gated convolution layers.
+As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
+Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
+Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same.
+Is is designed to show the validation of skip connections.
+Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss.
+The GCNN approach achieves a lower loss from start to the end of the training.
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
+	\caption{The training history of GCNN model.
+The line chart records the training BerHu loss of the model GCNN, NOC and CNN.
+The left shows the training loss history whereas the right one shows the evaluation loss history.}
+	\label{fig:gcnn-training-history}
+\end{figure}
+
+\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
+The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train.
+It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
+For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
+Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
+A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $F, where $ x $ denotes the fusion times.
+We evaluate the fusion times from 1 to 4.
+For the learning rate.
+we set $ 1e-3 $.
+It goes well with GCNN model but lead to loss explosion in Trip-Net.
+Thus we set a learning rate schedule with an extra decay step at epoch 8.
+The decay factor is $ 0.5$.
+The batch size is chosen as 8.
+
+Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.
+As shown in the loss figure, all of the four models has a reasonable learning rate.
+Trip-Net with four times fusion converges faster than others and also achieve a lower loss.
+Trip-Net-F3F converges slower than Trip-Net but achieved to a similar evaluation loss.
+The evaluation loss in Trip-Net-F1F and Trip-Net-F2F are relative higher than 3 or 4 times fusions model.
+
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
+	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
+	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
+	\label{fig:trip-net-training-history}
+\end{figure}
+
+However, the sacrifice of accuracy gives a relatively lighter model.
+Since we remove the fusions between different pipes, the corresponding upsampling layers in the image and light pipes can also be removed.
+The model can be trained faster and the size is reduced as well.
+Table \ref{tab:trip-net-size-compare} gives a comparison of the size and training time among different models.
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l l }
+		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB} & \tabhead{Time /h}\\
+		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106  &  9.82\\ 
+		\hline
+		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 &  7.35\\ 
+		\hline
+		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 &  7.35\\
+		\hline
+		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
+		\hline
+		GCNN 					& 32 & 32 & 0 & 0 & 46 & 2.18\\
+	\end{tabular}
+	\caption{Model information.
+Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
+Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
+}
+	\label{tab:gcnn-eval-mean}
+\end{table}
+
+\section{Evaluation}
+
+Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation.
+Note that the input vertex map is only semi-dense.
+One of the benefit of GCNN architecture is the robust to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
+
+\paragraph{Average Angle Error Metric}
+The metric calculate the average angle error for each point between the inferred normal and ground-truth normal. 
+\paragraph{Median Angle Error Metric}
+The metric calculate the median angle error of all the point in the normal map.
+\paragraph{5 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 5 degrees comparing to ground-truth.
+\paragraph{11.5 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 11.5 degrees comparing to ground-truth.
+\paragraph{22.5 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 22.5 degrees comparing to ground-truth.
+\paragraph{30 Degree Error Metric}
+The metric calculate the percentage of the predicted normals that has error less than 30 degrees comparing to ground-truth.
+
+We evaluate the trained models on ``synthetic-50-5".
+5 objects are considered in the test dataset.
+They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $.
+Each object has 20 scenes with total 100 scenes for 5 objects.
+The test objects do not exist in the training dataset.
+We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified.
+$ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $.
+$ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.
+
+Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis.
+When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
+When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
+
+%% mean metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & & & & 9.82 \\ 
+		\hline
+		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & & & & 7.32\\ 
+		\hline
+		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & & & & 7.35 \\
+		\hline
+		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & & & & 9.15 \\
+		\hline
+		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & & & & 12.13\\
+	\end{tabular}
+	\caption{Average Angle Error of the evaluation dataset.}	
+	\label{tab:eval-mean}
+\end{table}
+
+%% median metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & & & & 7.62 \\ 
+		\hline
+		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & & & & 4.01 \\ 
+		\hline
+		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & & & & 5.06 \\
+		\hline
+		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & & & & 5.81\\
+		\hline
+		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& & & & 6.76\\
+	\end{tabular}
+	\caption{Median Angle Error of the evaluation dataset.}	
+	\label{tab:eval-median}
+\end{table}
+
+%% 5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l |l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & & & & 0.31\\ 
+		\hline
+		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & & & & 0.59 \\ 
+		\hline
+		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & & & & 0.50\\
+		\hline
+		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & & & & 0.45\\
+		\hline
+		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & & & & 0.41\\
+	\end{tabular}
+	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
+	\label{tab:eval-5d}
+\end{table}
+
+%% 11.5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 & & & & 0.69\\ 
+		\hline
+		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & & & & 0.83 \\ 
+		\hline
+		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & & & & 0.82\\
+		\hline
+		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 & & & & 0.75\\
+		\hline
+		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & & & & 0.66\\
+	\end{tabular}
+	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
+	\label{tab:eval-11d}
+\end{table}
+
+%% 22.5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & & & & 0.92\\ 
+		\hline
+		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & & & & 0.94\\ 
+		\hline
+		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & & & & 0.95\\
+		\hline
+		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & & & & 0.91\\
+		\hline
+		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & & & & 0.84\\
+	\end{tabular}
+	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
+	\label{tab:eval-22d}
+\end{table}
+
+%% 30 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l | l | l l l | l l l l }
+		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & & & & 0.97 \\ 
+		\hline
+		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & & & & 0.96 \\ 
+		\hline
+		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & & & & 0.98 \\
+		\hline
+		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & & & & 0.95 \\
+		\hline
+		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & & & & 0.90\\
+	\end{tabular}
+	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
+	\label{tab:eval-30d}
+\end{table}
+
+\section{Visualization evaluation on GCNN model}
+A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
+As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object.
+The image has an overall good performance on the whole object.
+A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
+In the same case, NOC model as shown in Figure  \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
+CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
+Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).
+
+%% GCNN-eval
 \begin{figure}[H]
 	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
 		\caption{GT}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+		\caption{Predict}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
-		\caption{CNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
-		\caption{NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_SVD.png}
-		\caption{SVD}
+		\caption{Error}
 	\end{subfigure}
@@
 
-	\caption{Surface Normal Inference based GCNN model on "Dragon´´ object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\caption{Normal inference based on GCNN. Test image has resolution $ 128\times128 $}
 	\label{fig:gcnn-eval}
@@
 
-A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
-SVD approach is considered as the baseline shown in last column.
-As shown in the figure, learning based methods performs better than SVD in terms of angle error.
-The SVD approach is failed to deal with semi-dense input since there exists many points that missing neighbors.
-The GCNN model is especially good at noise input due to the gated convolution layer design.
-As a further detailed comparison, \ref{fig:gcnn-eval-synthetic-zoom-in} gives a closer visualization on the same object.
-
-%% fig:gcnn-eval-synthetic-zoom-in
+%% GCNN zoom in eval
 \begin{figure}[H]
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-NOC.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-CNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_normal.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_error.png}
+		\caption{Scale}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_error.png}
+		\caption{Head}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_error.png}
+		\caption{Foreleg}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_error.png}
+		\caption{Hindleg}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_error.png}
+		\caption{Tail}
+	\end{subfigure}
+
+	\caption{Zoom in of some regions of Dragon object.
+The first row is surface normal, the second row is the corresponding errors.
+Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
+	\label{fig:gcnn-eval-synthetic-zoom-in}
+\end{figure}
+
+%% compare to other models
+
+%% GCNN zoom in eval
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
 		\caption{GT}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
 		\caption{GCNN}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-NOC.png}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
 		\caption{NOC}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-CNN.png}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
 		\caption{CNN}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
 
-	\caption{Zoom in of the center region of Dragon object.
-The first row is surface normal, the second row is the corresponding errors.
-NOC model has no skip connnection, CNN model replace gated convolution layer to standard convolution layer.}
-	\label{fig:gcnn-eval-synthetic-zoom-in}
+	\caption{Comparison of GCNN model with no skip connection version(NOC) and standard convolution layer only version (CNN). The second row is the corresponding mean average degree error.}
+	\label{fig:gcnn-eval-multi-model}
 \end{figure}
-As shown in figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the GCNN method gives a sharper edge prediction on the horn area of the dragon object, as well as the scales, whereas the no skip version (NOC) is blurry in the same area.
-
-The CNN version has the skip connection thus gives a better detail than NOC model.
-However, if we compare the error map of GCNN and CNN in figure \ref{fig:gcnn-eval}, the CNN has less accurate in the smooth area than GCNN model.
-Like the dragon body, CNN model has a overall higher error than GCNN.
-It is because the noise of the input still disturb the CNN model and it takes the input noise into account for normal estimation which deviate to the correct surface normal.
-When we look back to the GCNN based method, we can found that the surface normal has better performance in the smooth area compare to the CNN approach and a sharp detail compare to the no skip connection version.
-
-Table \ref{tab:gcnn-eval} gives a quantitative evaluation for GCNN model. It bases on 100 different test scenes in the "synthetic-50-5´´ dataset with angle metrics for evaluation.
-
-\begin{table}[H]
-
-	\centering
-	\begin{tabular}{l l l l l l }
-		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
-		SVD(baseline)  & 41.14  & 320.40 & 8 & 8,1000 & 0.5\\ 
-		\hline
-		GCNN  & 10.64  & 10.44 & 8 & 8,1000 & 0.5\\ 
-		\hline
-		GCNN-NOC & 13.61 & 5.38 & 8 & 8,1000 & 0.5\\
-		\hline
-		CNN & 15.35 & 4.15 & 8 & 8,1000 & 0.5\\
-	\end{tabular}
-	\caption{The performance of the GCNN model for geometry information based normal inference.
-The angle error is the average angle error of all valid pixels in the test case.
-bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}
-	\label{tab:gcnn-eval}
-\end{table}
 
@@
 The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
-As a comparison, we placed GCNN result in the last column.
-The training settings for all the models are exact the same to ensure fairness.
-As shown in the figure, TripNet uses illuminated calibrated RGBD image has a better performance than GCNN model.
-The dragon scales are sharper in TripNet result.
-Figure \ref{fig:tripnet-eval-synthetic-zoom-in} gives a closer visualization.
+In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same.
+We also use the same input as we did in GCNN evaluation.
+The error of Trip-Net is 6 degree whereas the GCNN is 9.
+
+As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and close to the ground-truth.
+The head region gives a sharper edge prediction.
+All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
+
 %% TripNet-eval
@@
 	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
 		\caption{GT}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
+		\caption{Predict}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
-		\caption{TripNet}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-		\caption{GCNN}
+		\caption{Error}
 	\end{subfigure}
@@
 
-	\caption{TripNet qualitative evaluation. Surface Normal Inference on ``Dragon" object. The first row shows the estimated surface normal. The second row is the angle error map.}
+	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
 	\label{fig:trip-eval}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_normal.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
-		\caption{GT}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_error.png}
+		\caption{Scale}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_an2-8-1000.png}
-		\caption{Trip-Net}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_error.png}
+		\caption{Head}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
-		\caption{GCNN}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
+		\caption{Foreleg}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_error.png}
+		\caption{Hindleg}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_error.png}
+		\caption{Tail}
 	\end{subfigure}
 
-	\caption{Zoom in of the center region of Dragon object. The first row is surface normal, the second row is the corresponding errors.}
+	\caption{Zoom in of some regions of Dragon object.
+The first row is surface normal, the second row is the corresponding errors.
+Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
 	\label{fig:tripnet-eval-synthetic-zoom-in}
@@
 
-\begin{table}[th]
-
-	\centering
-	\begin{tabular}{l l l l l l l }
-		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.}\\
-		SVD  & 41.14  & 320.40 & - & - & - & 0 \\ 
-		\hline
-		GCNN  & 10.64 & 10.44 & 8 & 8,1000 & 0.5 & 0 \\
-		\hline
-		TripNet-CNN & 10.46 & 28.74 & 8 & 8,1000  & 0.5 & 1 \\
-		\hline
-		TripNet-F1B & 9.22 &44.59 & 8 & 8,1000  & 0.5 & 1 \\
-		\hline
-		TripNet & \textbf{9.17} & 43.79 & 8 & 8,1000  & 0.5 & 1 \\
-	\end{tabular}
-	\caption{A quantitative evaluation on proposed approaches.
-The angle error is the average angle error of all valid pixels in the test case.
-The time unit is in millisecond.
-bz is the batch size, lr-schedule is learning rate schedule.
-lr-df is learning rate decay factor, l/i.
-Nr is the number of light-image maps used for each scene}
-	\label{tab:model-error}
-\end{table}
-
-\subsection{Comparison}
-
+\section{More Comparison}
+Figure \ref{fig:final-eval} gives more visualization on model SVD, GCNN and Trip-Net. Figure \ref{fig:final-eval-zoom-in} is the corresponding zoom-in visualization.
+\newpage
 %% Final-Visual
-\begin{figure}[th]
+\begin{figure}
 	\centering
@@
 %% Final-Visual-Zoom-In
-\begin{figure}[th]
+\begin{figure}
 	\centering
@@
 	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
-	\label{fig:tripnet-eval-synthetic-zoom-in}
+	\label{fig:final-eval-zoom-in}
 \end{figure}

### 2022-07-31 paper/akweury/document.tex
update eval

@@
 \section{Evaluation}
-We evaluate the trained models on ``synthetic-50-5".
-5 objects are considered in the test dataset.
-They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $.
-Each object has 20 scenes with total 100 scenes for 5 objects.
-The test objects do not exist in the training dataset.
-We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified.
-$ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $.
-$ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.
-
-Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis.
-When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
-When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
 
@@
 The metric calculate the percentage of the predicted normals that has error less than 30 degrees comparing to ground-truth.
+
+We evaluate the trained models on ``synthetic-50-5".
+5 objects are considered in the test dataset.
+They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $.
+Each object has 20 scenes with total 100 scenes for 5 objects.
+The test objects do not exist in the training dataset.
+We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified.
+$ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $.
+$ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.
+
+Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis.
+When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
+When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
 
@@
 
-%% gcnn-eval
+\section{Visualization evaluation on GCNN model}
+A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
+As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object.
+The image has an overall good performance on the whole object.
+A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
+In the same case, NOC model as shown in Figure  \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
+CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
+Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).
+
+%% GCNN-eval
 \begin{figure}[H]
 	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
 		\caption{GT}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+		\caption{Predict}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
-		\caption{CNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
-		\caption{NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_SVD.png}
-		\caption{SVD}
+		\caption{Error}
 	\end{subfigure}
@@
 
-	\caption{Normal inference based on Trip-Net. Test image resolution $ 128\times128 $}
+	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
 	\label{fig:trip-eval}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_normal.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
+	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_normal.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
-		\caption{GT}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_error.png}
+		\caption{Scale}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_an2-8-1000.png}
-	\caption{Trip-Net}
+	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_error.png}
+	\caption{Head}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
-		\caption{GCNN}
+	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
+	\caption{Foreleg}
+\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_error.png}
+	\caption{Hindleg}
+\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_error.png}
+		\caption{Tail}
 	\end{subfigure}
 
-	\caption{Zoom in of the center region of Dragon object. The first row is surface normal, the second row is the corresponding errors.}
+	\caption{Zoom in of some regions of Dragon object.
+The first row is surface normal, the second row is the corresponding errors.
+Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
 	\label{fig:tripnet-eval-synthetic-zoom-in}
@@
 
-\begin{table}[th]
-
-	\centering
-	\begin{tabular}{l l l l l l l }
-		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.}\\
-		SVD  & 41.14  & 320.40 & - & - & - & 0 \\ 
-		\hline
-		GCNN  & 10.64 & 10.44 & 8 & 8,1000 & 0.5 & 0 \\
-		\hline
-		TripNet-CNN & 10.46 & 28.74 & 8 & 8,1000  & 0.5 & 1 \\
-		\hline
-		TripNet-F1B & 9.22 &44.59 & 8 & 8,1000  & 0.5 & 1 \\
-		\hline
-		TripNet & \textbf{9.17} & 43.79 & 8 & 8,1000  & 0.5 & 1 \\
-	\end{tabular}
-	\caption{A quantitative evaluation on proposed approaches.
-The angle error is the average angle error of all valid pixels in the test case.
-The time unit is in millisecond.
-bz is the batch size, lr-schedule is learning rate schedule.
-lr-df is learning rate decay factor, l/i.
-Nr is the number of light-image maps used for each scene}
-	\label{tab:model-error}
-\end{table}
-
-\subsection{Comparison}
-
+\section{More Comparison}
+Figure \ref{fig:final-eval} gives more visualization on model SVD, GCNN and Trip-Net. Figure \ref{fig:final-eval-zoom-in} is the corresponding zoom-in visualization.
 \newpage
 %% Final-Visual
-\begin{figure}[H]
+\begin{figure}
 	\centering
@@
 %% Final-Visual-Zoom-In
-\begin{figure}[H]
+\begin{figure}
 	\centering
@@
 	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
-	\label{fig:tripnet-eval-synthetic-zoom-in}
-\end{figure}
-
-From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension.
-It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections.
-Then it counts the number of points locates in each section for 3 axes.
-The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis.
-Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.
-
-It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
-
-\subsection{Light Inpainting}
-The light inpainting task in this section in order to evaluate the noise inpainting performance of GCNN model.
-It takes semi-dense light map as input to predict the fully dense light map, as shown in Figure \ref{fig:light-net-archi}.
-The network is trained on 3000 light maps in the "synthetic-50-5" dataset with initial learning rate 0.001, learning schedule 8,1000 with decay factor 0.5, the batch size is 8, the feature map channel is 128 in all of the gated convolution layers.
-All the models are tested on a laptop with a single NVIDIA GeForce 940MX, 2GB memory.
-
-%% light eval model structure
-\begin{figure}[th]
-	\centering
-	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
-	\begin{tikzpicture}
-		%% -------------------------------------- parameters ------------------------------------------------
-		\pgfmathsetmacro{\vdist}{0.4}
-
-		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
-		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3
-
-		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
-		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}
-
-		%% 	d_in							3x512x512
-		%%	dconv1: 	d_in-->x1 			32x512x512
-		\pgfmathsetmacro{\disttimes}{1}	%% width 32
-		\pgfmathsetmacro{\yshift}{1}	%% width 32
-		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
-		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
-		\pgfmathsetmacro{\yschift}{-1}
-
-		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light_input.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};
-
-		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
-		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light.png}};
-		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {fully-dense Light Map};
-
-		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
-		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);
-
-		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
-		\pgfmathsetmacro{\yschift}{-1}
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
-		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
-
-		\node[text width=3.5cm] at (\vdist*\disttimes+0.3,\yschift-1) {GCNN};
-	\end{tikzpicture}
-	\caption{Light map inpainting based on GCNN architecture.}
-	\label{fig:light-net-archi}
-\end{figure}
-
-The result is shown in Table \ref{tab:light-inpainting}.
-Besides the GCNN model, we use two extra model as the comparisons.
-The first one is GCNN-NOC, where NOC means "no skip connection", the second one is CNN, which has the same architecture as the GCNN but only use standard convolution layers in the network.
-The GCNN architecture achieves the average angle error lower than 1 degree.
-As a comparison, U-CNN model has 4 degrees error, which shows the relative weakness of noise filter competence.
-Besides, the skip connection also booster the performance, since the no skip connection version still has error greater than 1 degree.
-The both two models for the inpainting task reveals the superiority of GCNN architecture.
-Figure \ref{fig:light-scatter} and \ref{fig:light-eval} gives a quantitative and qualitative evaluation.
-
-%% light eval table
-\begin{table}[H]
-
-	\centering
-	\begin{tabular}{l l l l l l }
-		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
-		U-GCNN  & 0.59  & 14.45 & 8 & 8,1000 & 0.5\\ 
-		\hline
-		U-GCNN-NOC & 1.31 & 16.14 & 8 & 8,1000 & 0.5\\
-		\hline
-		U-CNN & 4.10 & 10.52 & 8 & 8,1000 & 0.5\\
-	\end{tabular}
-	\caption{The performance of the GCNN model for light map inpainting.
-The angle error is the average angle error of all valid pixels in the test case.
-bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}
-	\label{tab:light-inpainting}
-\end{table}
-
-%% light eval visualization
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
-		\caption{gray-scale image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_input.png}
-		\caption{Light Direction}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_gt.png}
-		\caption{ground-truth}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-gcnn.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-cnn.png}
-		\caption{U-CNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-noc.png}
-		\caption{U-GCNN-NOC}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-gcnn.png}
-		\caption{U-GCNN Error}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-cnn.png}
-		\caption{U-CNN Error}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-noc.png}
-		\caption{U-NOC Error}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_hot-vertical.jpg}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{GCNN Normal Inference for light map inpainting based on dragon object. The degree error map is shown in last row. The average error is shown in the upper right corner in the error map.}
-	\label{fig:light-eval}
-\end{figure}
-
-%% light eval scatter
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.9\linewidth]{./Figures/gcnn-light/scatter-light.png}
-	\caption{GCNN for light map inpainting on 100 scenes.
-The evaluated models are corresponding to the table \ref{tab:light-inpainting}, the line in the figure is the corresponding regression line of each model.}
-	\label{fig:light-scatter}
-\end{figure}
-
-The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
-%% fig:gcnn-eval-real
-\begin{figure}[th]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
-		\caption{point cloud}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
-		\caption{ground-truth}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
-		\caption{Angle Error}
-	\end{subfigure}
-	\caption{Evaluation on Real Dataset}
-	\label{fig:gcnn-eval-real}
-\end{figure}
-
-We evaluate the U-GCNN model on 100 test images as a quantitative evaluation.
-The result is shown in Figure \ref{fig:scatter-gcnn}.
-The GCNN based method has average angle error around 10 degrees, whereas the no skip connection version has error above 12 degrees and the CNN version has error above 15 degrees.
-
-%% scatter_gcnn
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=.8\textwidth]{./Figures/gcnn-synthetic/gcnn-scatter.png}
-	\caption{Evaluation of average angular loss on the whole test dataset with 100 scenes.
-The x-axis indicates the point number, the y-axis indicates the angles.
-The lines show in the picture are the regression line of each model.}
-	\label{fig:scatter-gcnn}
+	\label{fig:final-eval-zoom-in}
 \end{figure}

### 2022-08-01 paper/akweury/document.tex
update an_real

@@
 
-\section{Training Details}
+ In this thesis, we require two kinds of input data for model training. 
+ First we need geometry information of the object surface. This can be collected by a depth camera, which records the Z-axis distance of the object surface point to the camera position. 
+ Second we need illuminated information of the object surface, which considers as a help-information of the geometry based model to further improve the inference accuracy.
+This kind of information is collected by a light scanner, which usually has known intrinsic and extrinsic camera matrix, so that we can convert the point between camera coordinate system and the world coordinate system.
+Besides, an extra spot light will be placed in a known position to illuminate the object surface.
+Then, the light scanner can capture the scene as a grayscale/RGB image, save the camera matrix and light position.
+So we can based on the light position and the depth map acquired from depth camera to calculate light direction and further use image to estimate the surface normal.
 
-The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
-Each scene has a depth map with dimension $ 128\times 128 \times $ in height, width and channel, an image with dimension $ 128\times 128 \times 1 $.
-The depth map is converted to 3D vertex map as introduced in Chapter \ref{ch:04}.
-The light map is calculated based on vertex map and the known light position.
-We create a tensor in PyTorch that includes vertex map, image and the light direction for each scene and considered it as one training case.
-Thus 3000 scenes has corresponding 3000 training cases.
-Each scene has a corresponding ground-truth normal map for loss calculation and the evaluation.
+ In order to acquire these data, we can use a light scanner to scan the objects in laboratory.
+However, the scanner is failed to scan dark, shinny and transparent region, which leaves a plenty of missing pixels and holes in the depth map.
+Thus the corresponding surface points are incomplete for the object.
+It leads to the missing ground-truth in the normal map.
+Second, to train a deep learning based model usually require a huge dataset, especially for the network without backbone.
+To create a single depth map dataset for this thesis would be too much of work and resource requirement.
+A proper way for getting huge depth map data with illumination information can be considered using a game engine, which can simulate any number of data that we required.
 
-\begin{figure}[H]
+ In this thesis, we use Unity game engine for data generation.
+Based on a $ C\# $ script, we can set on a similar configuration in the laboratory.
+Then create a mount of data based on the collected object models.
+The dataset that we created for this thesis is called \textit{synthetic-50-5}, since it has 50 different object models for training and 5 object models for testing.
+
+\section{Resource}
+The object model we used are coming from internet.
+\cite{data1}, \cite{data2}, \cite{data3} and \cite{data4} published a set of point cloud dataset for computer vision research.
+These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing.
+Each objects has been scanned for hundreds of times with an exhaustive completion for the origin objects, which is up to millions points.
+(\cite{data1}).
+The dense point clouds makes the normal inference task trivial since the neighbor based method performs good enough for these kind of task.
+Some of the point cloud even equipped with pre-computed normal map based on more advanced methods.
+They all provides the accurate ground-truth for the supervised learning method.
+
+The \textit{synthetic50-5} is a datset with 50 point clouds as training set and 5 point clouds as test set.
+When we create the dataset, we tried to make the object types as many as possible to give a robust and wide range covered training scenarios.
+The category of the models include figure, animal, statue, toy, furniture, antique, car model, which include the smooth surface model like \textit{arm, bus, bunny, cat, zebra} and also the model with highly elaborate details, like \textit{Washington, Car-Engine, Armadillo}.
+The dataset is created base on the work of this thesis and using for normal inference task.
+Figure \ref{fig:dataset-demo} gives the illustrations of some objects.
+Appendix \ref{AppendixA} gives a full version of dataset models.
+
+\begin{figure}[!h]
 	\centering
-
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/00.apoll.png}
+		\caption{apoll}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/01.arm.png}
+		\caption{arm}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/02.armadillo.png}
+		\caption{armadillo}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.normal0.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/03.bearded-guy.png}
+		\caption{bearded-guy}
 	\end{subfigure}
 
-	\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/04.bronze-sculpture.png}
+		\caption{sculpture}
 	\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0_noise.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/05.bunny.png}
+		\caption{bunny}
 	\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.image0.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/06.car-engine.png}
+		\caption{car-engine}
 	\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.normal0.png}
+	\begin{subfigure}[b]{0.23\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/07.cat.png}
+		\caption{cat}
 	\end{subfigure}
 
-	\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.normal0.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.normal0.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
-	\caption{Depth Map}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
-	\caption{Add noise}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
-	\caption{Image}
-\end{subfigure}
-\begin{subfigure}[b]{0.20\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
-	\caption{Normal}
-\end{subfigure}
-
-	\caption{Some of the test scenes during the training. From top to bottom, baoshanlu, Washington, Garfield, Dragon, Bus}
-	\label{fig:test-scene}
+	\label{fig:dataset-demo}
+	\caption{Point clouds scanned by high resolution scanners}
 \end{figure}
 
-The training processes are evaluated in every epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
-Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
-Note that the position of objects are not placed naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
+\section{Synthesize Scenes using Unity}
+In order to fit the using scenario of Kinect as much as possible, the dataset consists of the generated synthetic 3D scenes via Unity, which is a game engine using for 3D games creation.
 
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
-The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
-It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
-We terminate the training when the evaluation on the test dataset converged.
+In the synthetic scenes from engine, the object is placed on a cylinder platform, which is lighted by a directional light nearby.
+A camera focus on the platform and captured the scene.
+The layout in the game engine is shown in Figure \ref{fig:unity-workplace}.
+In order to simulate more scenarios, the positions of the camera and directional light are randomly changed in each new scene.
+For 50 training objects, 1000 scenes are generated and each scene is saved in 3 kinds of resolutions $ 512\times512\times3 $, $ 256\times256\times3 $ and $ 128\times128\times3 $.
 
-\section{GCNN model based on Geometry Information}
-The GCNN model is the base model of the whole thesis.
-The architecture is described in \ref{sec:gcnn}.
-We use a single GCNN to estimate the surface normal based on geometry information.
-It uses vertex map as input to estimate the corresponding tangent surface normal map.
-
-In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
-We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN".
-It is used to verify the performance the gated convolution layers.
-As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
-Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
-Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same.
-Is is designed to show the validation of skip connections.
-Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss.
-The GCNN approach achieves a lower loss from start to the end of the training.
-
-\begin{figure}[th]
+\begin{figure}[h!]
 	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
-	\caption{The training history of GCNN model.
-The line chart records the training BerHu loss of the model GCNN, NOC and CNN.
-The left shows the training loss history whereas the right one shows the evaluation loss history.}
-	\label{fig:gcnn-training-history}
+	\includegraphics[width=.8\textwidth]{./Figures/unity-workplace.PNG}
+	\caption{The layout of synthetic scenes generation in Unity.}
+	\label{fig:unity-workplace}
 \end{figure}
 
-\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
-The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train.
-It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
-For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
-Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
-A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $F, where $ x $ denotes the fusion times.
-We evaluate the fusion times from 1 to 4.
-For the learning rate.
-we set $ 1e-3 $.
-It goes well with GCNN model but lead to loss explosion in Trip-Net.
-Thus we set a learning rate schedule with an extra decay step at epoch 8.
-The decay factor is $ 0.5$.
-The batch size is chosen as 8.
+The main advantage using generated scene is the availability of complete information.
+The depth map can be captured in a loss-free way.
+The corresponding normal map can also be safely considered as ground truth.
+And the scale of the dataset is easy to control.
 
-Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.
-As shown in the loss figure, all of the four models has a reasonable learning rate.
-Trip-Net with four times fusion converges faster than others and also achieve a lower loss.
-Trip-Net-F3F converges slower than Trip-Net but achieved to a similar evaluation loss.
-The evaluation loss in Trip-Net-F1F and Trip-Net-F2F are relative higher than 3 or 4 times fusions model.
+For each scene, following information is recorded
+\begin{table}
+	\caption{The information saved for each scene in ``synthetic50-5".}
+	\label{tab:data-files}
+	\centering
+	\begin{tabular}{l l}
+		\tabhead{Data} & \tabhead{Size} \\
+		Depth map & $ 512\times512\times3 $ \\
+		\hline 
+		Depth range  & $ 2\times1 $ \\  
+		\hline
+		Grayscale Image	& $ 512\times512\times1 $ \\  
+		\hline 
+		Normal Map &  $ 512\times512\times3 $  \\
+		\hline 
+		Light Position &  $ 3\times1 $  \\
+		\hline
+		Camera Intrinsic Matrix &  $ 3\times 3 $  \\
+		\hline 
+		Camera Extrinsic Matrix &  $ 3\times 4 $  \\
+		\hline 
+	\end{tabular}
+\end{table}
 
-\begin{figure}[th]
+A depth map $ D $ is captured by a depth camera in Unity, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
+It can be saved as a 16-bit grayscale image, i.e.
+each pixel in range $0 - 65535$.
+The grayscale image can be used as guided normal inference task and also as a readable scene for human.
+The gray-color is converted from RGB color based on following equation
+\[ gray: \frac{r+2g+b}{4}  \]
+The normal map is the tangent surface normal, which is saved in 32-bit RGB color image.
+The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on following equation:
+\begin{dgroup*}
+	\begin{dmath*}
+		n_x = \frac{R}{255} * 2 - 1
+	\end{dmath*}
+	\begin{dmath*}
+		n_y = \frac{G}{255}*2 - 1
+	\end{dmath*} 
+	\begin{dmath*}
+		n_z = 1-\frac{B}{255} * 2
+	\end{dmath*}
+\end{dgroup*}
+If consider the relation between Lambertian reflection and normal direction, the light source can be used to calculate the reflect direction of each point.
+The camera intrinsic and extrinsic matrix helps point cloud calculation.
+
+It is necessary to point out again that ``synthetic50-5" aiming to rebuild the using scenarios of Kinect, where all types of the generated data files shown in Table \ref{tab:data-files} are also the same format of the Kinect data.
+
+\subsection{Convert to Point Cloud}
+\label{sec:depth-map-to-point-cloud}
+The depth map can be converted to 3D vertex point cloud as the input of the normal inference model.
+
+\begin{figure}[h!]
 	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
-	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
-	\label{fig:trip-net-training-history}
+	\begin{tikzpicture} 
+		% reference lines
+		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
+		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
+		\draw[thick,dashed]	(0,6) -- (10,6); % top
+		% camera 
+		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
+		% world point 
+		\filldraw[black] (7,6) circle (2pt) node[anchor=north west]{Point};
+		% image point
+		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
+		% similiar triangles
+		\draw[thick] (5,0) -- (5,6); % AB
+		\draw[thick] (5,0) -- (7,6); % AC
+		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
+		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
+		% measure arrows
+		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
+		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
+	\end{tikzpicture}	
+	\caption{Convert depth to point in camera coordinate system}
+	\label{fig:depth-triangulation}
 \end{figure}
 
-However, the sacrifice of accuracy gives a relatively lighter model.
-Since we remove the fusions between different pipes, the corresponding upsampling layers in the image and light pipes can also be removed.
-The model can be trained faster and the size is reduced as well.
-Table \ref{tab:trip-net-size-compare} gives a comparison of the size and training time among different models.
+Consider a 3-dimensional Euclidean space.
+Use $ z $ axis denotes the depth.
+The $ x  $ and $ y $ axes perpendicular with each other.
+For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ in camera coordinate system.
+The $ X $ and $ Y $ can be calculated based on the triangle similarity
+\begin{dgroup*}
 
-\begin{table}[H]
+	\begin{dmath*}
+		X = \frac{uZ}{fk_u}
+	\end{dmath*}
+	\begin{dmath*}
+		Y = \frac{vZ}{fk_v}
+	\end{dmath*}
+\end{dgroup*}
 
+where $ fk_u, fk_v $ is the focal length in pixels align $ u $ and $ v $ axes.
+Converted a point from camera coordinate system to world coordinate system, using extrinsic matrix $ R $ and $ t $
+\[P_W = P_CR+t \]
+
+\subsection{Point Cloud Normalization}
+\label{sec:dataset-normalization}
+%% How to represent input tensor, to make it fast converse
+The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus the normalization is required before feed training objects into the models.
+The range of each axis is shown in Figure \ref{fig:data-range}.  Table \ref{tab:data-range} gives a quantitative measurement of corresponding average values.
+
+The normalization has been performed as follows.
+First translate the points to the original point as close as possible, then choose the range value of one axis as a scale factor, normalize the points to unit vectors.
+The equation is shown as follows
+\begin{dgroup*}
+
+	\begin{dmath*}
+		X_n =\frac{X-\min(X)}{s}
+	\end{dmath*}
+	\begin{dmath*}
+		Y_n = \frac{Y-\min(Y)}{s}
+	\end{dmath*}
+
+	\begin{dmath*}
+		Z_n = \frac{Z-\min(Z)}{s}
+	\end{dmath*}
+\end{dgroup*}
+
+where $ s $ is a scale factor,
+
+\begin{dmath*}
+	s = \max(X)-\min(X)
+\end{dmath*}
+It is calculated as the range in $ X $ axis, but theoretically can be used by $ Y $ or $ Z $ axes as well.
+
+\begin{figure}[!h]
 	\centering
-	\begin{tabular}{l l l l l l l }
-		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB} & \tabhead{Time /h}\\
-		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106  &  9.82\\ 
-		\hline
-		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 &  7.35\\ 
-		\hline
-		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 &  7.35\\
-		\hline
-		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
-		\hline
-		GCNN 					& 32 & 32 & 0 & 0 & 46 & 2.18\\
+	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
+	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
+	\label{fig:data_range}
+	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
+\end{figure}
+
+\begin{table}[h!]
+	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. 
+	}
+	\label{tab:data-range}
+	\centering
+	\begin{tabular}{c c c c}
+		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
+		X & 1.48 & -0.75 & 0.73\\
+		Y & 1.56 & -0.76 & 0.80\\
+		Z & 1.47 & 6.53 & 8.00\\
+
 	\end{tabular}
-	\caption{Model information.
-Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
-Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
-}
-	\label{tab:gcnn-eval-mean}
 \end{table}
 
-\section{Evaluation}
+\subsection{Noise}
+\label{sec:noise}
+The raw depth maps captured by Kinect usually have missing pixels. Therefore, the ``synthetic50-5" dataset adds a similar properties.
+As shown in Figure \ref{fig:depth_map_kinect}.
+the depth map has missing pixels distributed all around the scene.
+Correspondingly, an uniformly distributed pixel-delete noise is used for noise simulation.
+Furthermore, a parameter $ \mu $ is used to control the intensity of noise, it denotes the $ \mu $-percent pixel dropoff.
+For example, $ \mu-10 $ means removes 10\% pixels randomly.
+For each scene, the noising operation based on a random $ \mu $ in a range $ \left[0, 50\right] $, therefore some scenes have more missing pixels and some have less.
+The random noise intensity also enables the model to learn scenarios not only with noise, but also with minor noise or even without noise.
+Figure \ref{fig:noise-intensity} shows the noise effect on different $ \mu $.
+%% add noise image
+\begin{figure}[!h]
+	\centering
+	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
+	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
+	\label{fig:noise-intensity}
+\end{figure}
 
-Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation.
-Note that the input vertex map is only semi-dense.
-One of the benefit of GCNN architecture is the robust to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
-
-\paragraph{Average Angle Error Metric}
-The metric calculate the average angle error for each point between the inferred normal and ground-truth normal. 
-\paragraph{Median Angle Error Metric}
-The metric calculate the median angle error of all the point in the normal map.
-\paragraph{5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 5 degrees comparing to ground-truth.
-\paragraph{11.5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 11.5 degrees comparing to ground-truth.
-\paragraph{22.5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 22.5 degrees comparing to ground-truth.
-\paragraph{30 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 30 degrees comparing to ground-truth.
-
-We evaluate the trained models on ``synthetic-50-5".
-5 objects are considered in the test dataset.
-They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $.
-Each object has 20 scenes with total 100 scenes for 5 objects.
-The test objects do not exist in the training dataset.
-We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified.
-$ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $.
-$ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.
-
-Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis.
-When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
-When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
-
-%% mean metric
-\begin{table}[H]
+\subsection{Fit to PyTorch}
+In order to saving the training time, the dataset is compressed in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
+\begin{table}
+	\caption{The structure of a single tensor in the dataset.}
+	\label{tab:tensor-structure}
 	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & & & & 9.82 \\ 
+	\begin{tabular}{l l}
+		\tabhead{Name} & \tabhead{Content} \\
+		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
 		\hline
-		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & & & & 7.32\\ 
+		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
 		\hline
-		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & & & & 7.35 \\
+		Light position & light position \\
 		\hline 
-		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & & & & 9.15 \\
+		Camera Matrix  & K,R,t\\
 		\hline 
-		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & & & & 12.13\\
+		Depth Range  & minDepth, maxDepth\\
 	\end{tabular}
-	\caption{Average Angle Error of the evaluation dataset.}	
-	\label{tab:eval-mean}
 \end{table}
 
-%% median metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & & & & 7.62 \\ 
-		\hline
-		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & & & & 4.01 \\ 
-		\hline
-		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & & & & 5.06 \\
-		\hline
-		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & & & & 5.81\\
-		\hline
-		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& & & & 6.76\\
-	\end{tabular}
-	\caption{Median Angle Error of the evaluation dataset.}	
-	\label{tab:eval-median}
-\end{table}
-
-%% 5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l |l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & & & & 0.31\\ 
-		\hline
-		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & & & & 0.59 \\ 
-		\hline
-		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & & & & 0.50\\
-		\hline
-		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & & & & 0.45\\
-		\hline
-		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & & & & 0.41\\
-	\end{tabular}
-	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
-	\label{tab:eval-5d}
-\end{table}
-
-%% 11.5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 & & & & 0.69\\ 
-		\hline
-		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & & & & 0.83 \\ 
-		\hline
-		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & & & & 0.82\\
-		\hline
-		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 & & & & 0.75\\
-		\hline
-		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & & & & 0.66\\
-	\end{tabular}
-	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
-	\label{tab:eval-11d}
-\end{table}
-
-%% 22.5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & & & & 0.92\\ 
-		\hline
-		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & & & & 0.94\\ 
-		\hline
-		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & & & & 0.95\\
-		\hline
-		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & & & & 0.91\\
-		\hline
-		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & & & & 0.84\\
-	\end{tabular}
-	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
-	\label{tab:eval-22d}
-\end{table}
-
-%% 30 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & & & & 0.97 \\ 
-		\hline
-		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & & & & 0.96 \\ 
-		\hline
-		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & & & & 0.98 \\
-		\hline
-		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & & & & 0.95 \\
-		\hline
-		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & & & & 0.90\\
-	\end{tabular}
-	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
-	\label{tab:eval-30d}
-\end{table}
-
-\section{Visualization evaluation on GCNN model}
-A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
-As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object.
-The image has an overall good performance on the whole object.
-A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
-In the same case, NOC model as shown in Figure  \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
-CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
-Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).
-
-%% GCNN-eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
-		\caption{Image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-		\caption{Predict}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-		\caption{Error}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Normal inference based on GCNN. Test image has resolution $ 128\times128 $}
-	\label{fig:gcnn-eval}
-\end{figure}
-
-%% GCNN zoom in eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_normal.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_error.png}
-		\caption{Scale}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_error.png}
-		\caption{Head}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_error.png}
-		\caption{Foreleg}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_error.png}
-		\caption{Hindleg}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_error.png}
-		\caption{Tail}
-	\end{subfigure}
-
-	\caption{Zoom in of some regions of Dragon object.
-The first row is surface normal, the second row is the corresponding errors.
-Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
-	\label{fig:gcnn-eval-synthetic-zoom-in}
-\end{figure}
-
-%% compare to other models
-
-%% GCNN zoom in eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
-		\caption{NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
-		\caption{CNN}
-	\end{subfigure}
-
-	\caption{Comparison of GCNN model with no skip connection version(NOC) and standard convolution layer only version (CNN). The second row is the corresponding mean average degree error.}
-	\label{fig:gcnn-eval-multi-model}
-\end{figure}
-
-\newpage
-\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }
-
-For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
-The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
-In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same.
-We also use the same input as we did in GCNN evaluation.
-The error of Trip-Net is 6 degree whereas the GCNN is 9.
-
-As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and close to the ground-truth.
-The head region gives a sharper edge prediction.
-All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
-
-%% TripNet-eval
-\begin{figure}[H]
-	\centering
-		\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
-		\caption{Image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
-		\caption{Predict}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
-	\caption{Error}
-\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
-	\label{fig:trip-eval}
-\end{figure}
-
-%% tripNet zoom in eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_normal.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_error.png}
-		\caption{Scale}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_error.png}
-	\caption{Head}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
-	\caption{Foreleg}
-\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_error.png}
-	\caption{Hindleg}
-\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_error.png}
-		\caption{Tail}
-	\end{subfigure}
-
-	\caption{Zoom in of some regions of Dragon object.
-The first row is surface normal, the second row is the corresponding errors.
-Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
-	\label{fig:tripnet-eval-synthetic-zoom-in}
-\end{figure}
-
-\section{More Comparison}
-Figure \ref{fig:final-eval} gives more visualization on model SVD, GCNN and Trip-Net. Figure \ref{fig:final-eval-zoom-in} is the corresponding zoom-in visualization.
-\newpage
-%% Final-Visual
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_img.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_SVD.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_SVD.png}
-\end{subfigure}
-
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_img.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_SVD.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_SVD.png}
-\end{subfigure}
-
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_img.png}
-	\caption{GT}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
-	\caption{TripNet}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
-	\caption{GCNN}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_SVD.png}
-	\caption{SVD}
-\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
-	\label{fig:final-eval}
-\end{figure}
-
-%% Final-Visual-Zoom-In
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_img.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_SVD.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_SVD.png}
-\end{subfigure}
-
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_img.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_SVD.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_an2-8-1000.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
-\end{subfigure}
-\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_SVD.png}
-\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-		\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-
-	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
-	\label{fig:final-eval-zoom-in}
-\end{figure}
-
 \end{document}

### 2022-08-01 paper/Chapters/Chapter04.tex
update evaluation
update eval

@@
 
-\section{Synthetic Dataset}
-To train a deep learning model with supervised learning scheme, a dataset should require two principles, truth-worthy ground-truth and comprehensive scenarios.
-The depth map captured by Kinect is not satisfied the first requirement since it is usually semi-dense with a number of missing pixels, as shown in Figure \ref{fig:kinect-depth}.
-Therefore, a more elaborate depth map is required for the training work.
-In this thesis, a dataset called ``synthetic50-5" is created for the training works.
+ In this thesis, we require two kinds of input data for model training. 
+First we need geometry information of the object surface. This can be collected by a depth camera, which records the Z-axis distance of the object surface point to the camera position. 
+Second we need illuminated information of the object surface, which considers as a help-information of the geometry based model to further improve the inference accuracy.
+This kind of information is collected by a light scanner, which usually has known intrinsic and extrinsic camera matrix, so that we can convert the point between camera coordinate system and the world coordinate system.
+Besides, an extra spot light will be placed in a known position to illuminate the object surface.
+Then, the light scanner can capture the scene as a grayscale/RGB image, save the camera matrix and light position.
+So we can based on the light position and the depth map acquired from depth camera to calculate light direction and further use image to estimate the surface normal.
 
-\subsection{Resource}
-\cite{data1}, \cite{data2}, \cite{data3} and \cite{data4} published a set of point cloud dataset on the internet for computer vision task research.
+In order to acquire these data, we can use a light scanner to scan the objects in laboratory.
+However, the scanner is failed to scan dark, shinny and transparent region, which leaves a plenty of missing pixels and holes in the depth map.
+Thus the corresponding surface points are incomplete for the object.
+It leads to the missing ground-truth in the normal map.
+Second, to train a deep learning based model usually require a huge dataset, especially for the network without backbone.
+To create a single depth map dataset for this thesis would be too much of work and resource requirement.
+A proper way for getting huge depth map data with illumination information can be considered using a game engine, which can simulate any number of data that we required.
+
+In this thesis, we use Unity game engine for data generation.
+Based on a $ C\# $ script, we can set on a similar configuration in the laboratory.
+Then create a mount of data based on the collected object models.
+The dataset that we created for this thesis is called \textit{synthetic-50-5}, since it has 50 different object models for training and 5 object models for testing.
+
+\section{Resource}
+The object model we used are searched from internet.
+\cite{data1}, \cite{data2}, \cite{data3} and \cite{data4} published a set of point cloud dataset for computer vision research.
 These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing.
-Each objects has been scanned for hundreds of times for an exhaustive completion for the origin objects, which is up to millions points.
+Each objects has been scanned for hundreds of times with an exhaustive completion for the origin objects, which is up to millions points.
 (\cite{data1}).
@@
 
-The ``synthetic50-5", is a datset with 50 point clouds as training set and 5 point clouds as test set.
+The \textit{synthetic50-5} is a datset we generated in this thesis with 50 point clouds as training set and 5 point clouds as test set.
+When we create the dataset, we tried to make the object types as many as possible to give a robust and wide range covered training scenarios.
+The category of the models include figure, animal, statue, toy, furniture, antique, car model, which include the smooth surface model like \textit{arm, bus, bunny, cat, zebra} and also the model with highly elaborate details, like \textit{Washington, Car-Engine, Armadillo}.
 The dataset is created base on the work of this thesis and using for normal inference task.
@@
 	\centering
-	\begin{subfigure}[b]{0.23\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/train-dataset/00.apoll.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/train-dataset/01.arm.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/train-dataset/02.armadillo.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/train-dataset/03.bearded-guy.png}
@@
 
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/04.bronze-sculpture.png}
-		\caption{bronze-sculpture}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/08.pergolesi-side-chair_texture.png}
+		\caption{chair}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/05.bunny.png}
-		\caption{bunny}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/42.zebra_texture.png}
+		\caption{zebra}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/06.car-engine.png}
-		\caption{car-engine}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.bus_texture.png}
+		\caption{bus}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/07.cat.png}
-		\caption{cat}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu_texture.png}
+		\caption{baoshanlu}
 	\end{subfigure}
@@
 
-\subsection{Synthesize Scenes using Unity}
-In order to fit the using scenario of Kinect as much as possible, the dataset consists of the generated synthetic 3D scenes via Unity, which is a game engine using for 3D games creation.
+Besides, some of the objects also has its own texture, as shown in the second row of Figure \ref{fig:dataset-demo}.
+This is specially prepared for illuminated approach since they will take the image as account to evaluate the surface normal.
+The object surface gives a different reflectence with different surface texture, which further impact the model performance.
 
-In the synthetic scenes from engine, the object is placed on a cylinder platform, which is lighted by a directional light nearby.
-A camera focus on the platform and captured the scene.
-The layout in the game engine is shown in Figure \ref{fig:unity-workplace}.
-In order to simulate more scenarios, the positions of the camera and directional light are randomly changed in each new scene.
-For 50 training objects, 1000 scenes are generated and each scene is saved in 3 kinds of resolutions $ 512\times512\times3 $, $ 256\times256\times3 $ and $ 128\times128\times3 $.
+\definecolor{direction-light-color}{RGB}{255,244,214}
+\newcommand{\col}[1]{%
+	\textcolor{#1}{\vrule width 0.5cm}}
+\section{Synthesize Scenes using Unity}
+In order to simulate the the data collection scenario close to the real life in the laboratory as much as possible.
+We placed a flat cylinder called $ stage $ in the center in the 3D space as a platform to place objects.
+The stage is fixed in a determined position, which is not moved when the scene is captured.
+A directional light with RGB color FFF4D6 \col{direction-light-color}  placed in a top-view direction around 25 meters away to provide as ambient light, which also has a fixed position.
+A RGB-D camera is placed in a top-view direction around 10m away from the stage.
+The camera is the sensor to capture the depth map and the grayscale image, which is random moved after a new scene.
+The moving range of the camera has 0.1m in both directions of X, Y, and Z axis and 1 degree random changed Euler angle.
+A point light placed around 5 meters away as the illumination light, which is also randomly moved after a new scene.
+The moving range is 0.3m in both directions of X, Y, and Z axis and 1 degree random in Euler angle.
+
+During the data collection, the object is randomly selected and placed on the stage.
+The object has a random upto 30 degrees rotation align $ roll $-axis, 30-degrees rotation align $ pitch $-axis and 180-degrees align $ yaw $-axis.
+Thus the camera has the opportunity to capture every direction of the object and consequently abundant the dataset.
+The layout in the Unity game engine is shown in Figure \ref{fig:unity-workplace}.
+We generate 3000 scenes with resolution $ 128\times128\times3 $ and 5000 scenes with resolution $ 512\times512\times3 $.
 
@@
 	\centering
-	\includegraphics[width=.8\textwidth]{./Figures/unity-workplace.PNG}
+	\includegraphics[width=.99\textwidth]{./Figures/unity-workplace.PNG}
 	\caption{The layout of synthetic scenes generation in Unity.}
@@
 
-The main advantage using generated scene is the availability of complete information.
+The main advantage using generated scenes is the availability of complete information.
 The depth map can be captured in a loss-free way.
@@
 And the scale of the dataset is easy to control.
-
-For each scene, following information is recorded
+Table \ref{tab:data-files} gives more dataset information.
 \begin{table}
@@
 	\begin{tabular}{l l}
-		\toprule
 		\tabhead{Data} & \tabhead{Size} \\
-		\midrule
-		Depth map & $ 512\times512\times3 $ \\
+		Depth map & Width$ \times $Height$ \times $ 1 \\
 		\hline 
-		Depth range  & $ 2\times1 $ \\  
+		Depth range  & MinDepth, MaxDepth \\  
 		\hline
-		Grayscale Image	& $ 512\times512\times1 $ \\  
+		Grayscale Image	&  Width$ \times $Height$ \times $ 1 \\  
 		\hline 
-		Normal Map &  $ 512\times512\times3 $  \\
+		Normal Map &   Width$ \times $Height$ \times $ 3  \\
 		\hline 
@@
 		\hline 
-		\bottomrule\\
 	\end{tabular}
@@
 
-A depth map $ D $ is captured by a depth camera in Unity, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
+One important detail that we must care about is the camera exposure.
+Or we have to control the light radiance on the object surface.
+As shown in figure \ref{fig:camera_exposure}, too less exposure on the object neutralizes the illumination information, which only left ambient light effect.
+Too much exposure makes the surface texture hard to recognize.
+When we did the experiments, we found that a suitable light setting is essential to the illuminated based approach.
+A too much or too less light effects won't improve the illuminated based approach.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{./Figures/wrong_exposure_2.png}
+		\caption{Too dim}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{./Figures/right_exposure.png}
+		\caption{Just Right}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{./Figures/wrong_exposure.png}
+		\caption{Too bright}
+	\end{subfigure}
+	\caption{Different exposure to the objects.}
+	\label{fig:camera_exposure}
+\end{figure}
+
+\section{Data preprocessing}
+The raw data captured from Unity required further preprocessing before feed them into the training models. 
+A depth map is captured by a depth camera in Unity, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
 It can be saved as a 16-bit grayscale image, i.e.
 each pixel in range $0 - 65535$.
+
 The grayscale image can be used as guided normal inference task and also as a readable scene for human.
-The gray-color is converted from RGB color based on following equation
+Since the image captured by camera is RGB format, we need to convert it to gray-color for our models.
+It based on following equation
 \[ gray: \frac{r+2g+b}{4}  \]
+
 The normal map is the tangent surface normal, which is saved in 32-bit RGB color image.
@@
 \end{dgroup*}
+
 If consider the relation between Lambertian reflection and normal direction, the light source can be used to calculate the reflect direction of each point.
+
 The camera intrinsic and extrinsic matrix helps point cloud calculation.
-
-It is necessary to point out again that ``synthetic50-5" aiming to rebuild the using scenarios of Kinect, where all types of the generated data files shown in Table \ref{tab:data-files} are also the same format of the Kinect data.
 
@@
 Use $ z $ axis denotes the depth.
-The $ x  $ and $ y $ axes perpendicular with each other.
-For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ in camera coordinate system.
+The $ x  $ and $ y $ axis perpendicular with each other.
+For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ with respect to camera coordinate system.
 The $ X $ and $ Y $ can be calculated based on the triangle similarity
@@
 The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus the normalization is required before feed training objects into the models.
-The range of each axis is shown in Figure \ref{fig:data-range}.  Table \ref{tab:data-range} gives a quantitative measurement of corresponding average values.
+The data fluctuation in each axis is shown in Figure \ref{fig:data-range}.  Table \ref{tab:data-range} gives a quantitative measurement of corresponding average values.
 
@@
 	\centering
-	\begin{tabular}{c c c c}
-		\toprule
+	\begin{tabular}{c | c c c}
+		\hline 
 		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
-		\midrule
+		\hline 
 		X & 1.48 & -0.75 & 0.73\\
+		\hline 
 		Y & 1.56 & -0.76 & 0.80\\
+		\hline 
 		Z & 1.47 & 6.53 & 8.00\\
-		\bottomrule\\
+		\hline
+
 	\end{tabular}
@@
 \label{sec:noise}
-The raw depth maps captured by Kinect usually have missing pixels. Therefore, the ``synthetic50-5" dataset adds a similar properties.
-As shown in Figure \ref{fig:depth_map_kinect}.
-the depth map has missing pixels distributed all around the scene.
-Correspondingly, an uniformly distributed pixel-delete noise is used for noise simulation.
-Furthermore, a parameter $ \mu $ is used to control the intensity of noise, it denotes the $ \mu $-percent pixel dropoff.
-For example, $ \mu-10 $ means removes 10\% pixels randomly.
-For each scene, the noising operation based on a random $ \mu $ in a range $ \left[0, 50\right] $, therefore some scenes have more missing pixels and some have less.
+The raw depth maps captured by light scanner usually have missing pixels.
+In order to fit well with real-data, the synthetic data has been added uniform distributed noise, which is randomly remove the valid pixels in the maps.
+The simulated noise is distributed evenly around the whole map with a specific noise intensity.
+A parameter $ \mu $ is used to control the intensity of noise, it denotes the $ \mu $-percent pixel dropoff.
+For example, $ \mu-10 $ removes 10\% pixels randomly.
+For each scene, the noising operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used.
+Some scenes have more missing pixels and some have less.
 The random noise intensity also enables the model to learn scenarios not only with noise, but also with minor noise or even without noise.
-Figure \ref{fig:noise-intensity} shows the noise effect on different $ \mu $.
+Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
 %% add noise image
@@
 	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
-	\decoRule	
 	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
@@
 In order to saving the training time, the dataset is compressed in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
-\begin{table}
+\begin{table}[H]
 	\caption{The structure of a single tensor in the dataset.}
@@
 	\centering
-	\begin{tabular}{l l}
-		\toprule
+	\begin{tabular}{l | l}
 		\tabhead{Name} & \tabhead{Content} \\
-		\midrule
 		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
@@
 		Depth Range  & minDepth, maxDepth\\
-		\bottomrule\\
 	\end{tabular}
 \end{table}
-
-\section{Real Dataset}
-
-The real dataset is the depth map and rgb image captured via Kinect...

### 2022-08-01 paper/akweury/document.tex
update eval

@@
 \usepackage{rotating}
+\usepackage{booktabs}
 \usetikzlibrary{fit}
@@
 \section{Resource}
-The object model we used are coming from internet.
+The object model we used are searched from internet.
 \cite{data1}, \cite{data2}, \cite{data3} and \cite{data4} published a set of point cloud dataset for computer vision research.
@@
 
-The \textit{synthetic50-5} is a datset with 50 point clouds as training set and 5 point clouds as test set.
+The \textit{synthetic50-5} is a datset we generated in this thesis with 50 point clouds as training set and 5 point clouds as test set.
 When we create the dataset, we tried to make the object types as many as possible to give a robust and wide range covered training scenarios.
@@
 
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/04.bronze-sculpture.png}
-		\caption{sculpture}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/08.pergolesi-side-chair_texture.png}
+		\caption{chair}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/05.bunny.png}
-		\caption{bunny}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/train-dataset/42.zebra_texture.png}
+		\caption{zebra}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/06.car-engine.png}
-		\caption{car-engine}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.bus_texture.png}
+		\caption{bus}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.23\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/train-dataset/07.cat.png}
-		\caption{cat}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu_texture.png}
+		\caption{baoshanlu}
 	\end{subfigure}
@@
 
+Besides, some of the objects also has its own texture, as shown in the second row of Figure \ref{fig:dataset-demo}.
+This is specially prepared for illuminated approach since they will take the image as account to evaluate the surface normal.
+The object surface gives a different reflectence with different surface texture, which further impact the model performance.
+
+\definecolor{direction-light-color}{RGB}{255,244,214}
+\newcommand{\col}[1]{%
+	\textcolor{#1}{\vrule width 0.5cm}}
 \section{Synthesize Scenes using Unity}
-In order to fit the using scenario of Kinect as much as possible, the dataset consists of the generated synthetic 3D scenes via Unity, which is a game engine using for 3D games creation.
+In order to simulate the the data collection scenario close to the real life in the laboratory as much as possible.
+We placed a flat cylinder called $ stage $ in the center in the 3D space as a platform to place objects.
+The stage is fixed in a determined position, which is not moved when the scene is captured.
+A directional light with RGB color FFF4D6 \col{direction-light-color}  placed in a top-view direction around 25 meters away to provide as ambient light, which also has a fixed position.
+A RGB-D camera is placed in a top-view direction around 10m away from the stage.
+The camera is the sensor to capture the depth map and the grayscale image, which is random moved after a new scene.
+The moving range of the camera has 0.1m in both directions of X, Y, and Z axis and 1 degree random changed Euler angle.
+A point light placed around 5 meters away as the illumination light, which is also randomly moved after a new scene.
+The moving range is 0.3m in both directions of X, Y, and Z axis and 1 degree random in Euler angle.
 
-In the synthetic scenes from engine, the object is placed on a cylinder platform, which is lighted by a directional light nearby.
-A camera focus on the platform and captured the scene.
-The layout in the game engine is shown in Figure \ref{fig:unity-workplace}.
-In order to simulate more scenarios, the positions of the camera and directional light are randomly changed in each new scene.
-For 50 training objects, 1000 scenes are generated and each scene is saved in 3 kinds of resolutions $ 512\times512\times3 $, $ 256\times256\times3 $ and $ 128\times128\times3 $.
+During the data collection, the object is randomly selected and placed on the stage.
+The object has a random upto 30 degrees rotation align $ roll $-axis, 30-degrees rotation align $ pitch $-axis and 180-degrees align $ yaw $-axis.
+Thus the camera has the opportunity to capture every direction of the object and consequently abundant the dataset.
+The layout in the Unity game engine is shown in Figure \ref{fig:unity-workplace}.
+We generate 3000 scenes with resolution $ 128\times128\times3 $ and 5000 scenes with resolution $ 512\times512\times3 $.
 
@@
 		\tabhead{Data} & \tabhead{Size} \\
-		Depth map & $ 512\times512\times3 $ \\
+		Depth map & Width$ \times $Height$ \times $ 1 \\
 		\hline 
-		Depth range  & $ 2\times1 $ \\  
+		Depth range  & MinDepth, MaxDepth \\  
 		\hline
-		Grayscale Image	& $ 512\times512\times1 $ \\  
+		Grayscale Image	&  Width$ \times $Height$ \times $ 1 \\  
 		\hline 
-		Normal Map &  $ 512\times512\times3 $  \\
+		Normal Map &   Width$ \times $Height$ \times $ 3  \\
 		\hline 
@@
 
-A depth map $ D $ is captured by a depth camera in Unity, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
+One important detail that we must care about is the camera exposure.
+Or we have to control the light radiance on the object surface.
+As shown in figure \ref{fig:camera_exposure}, too less exposure on the object neutralizes the illumination information, which only left ambient light effect.
+Too much exposure makes the surface texture hard to recognize.
+When we did the experiments, we found that a suitable light setting is essential to the illuminated based approach.
+A too much or too less light effects won't improve the illuminated based approach.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{./Figures/wrong_exposure_2.png}
+		\caption{Too dim}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+	\includegraphics[width=\textwidth]{./Figures/right_exposure.png}
+	\caption{Just Right}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+	\includegraphics[width=\textwidth]{./Figures/wrong_exposure.png}
+	\caption{Too bright}
+	\end{subfigure}
+	\caption{Different exposure to the objects.}
+	\label{fig:camera_exposure}
+\end{figure}
+
+\section{Data preprocessing}
+The raw data captured from Unity required further preprocessing before feed them into the training models. 
+A depth map is captured by a depth camera in Unity, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
 It can be saved as a 16-bit grayscale image, i.e.
 each pixel in range $0 - 65535$.
+
 The grayscale image can be used as guided normal inference task and also as a readable scene for human.
-The gray-color is converted from RGB color based on following equation
+Since the image captured by camera is RGB format, we need to convert it to gray-color for our models.
+It based on following equation
 \[ gray: \frac{r+2g+b}{4}  \]
+
 The normal map is the tangent surface normal, which is saved in 32-bit RGB color image.
@@
 	\centering
-	\begin{tabular}{c c c c}
+	\begin{tabular}{c | c c c}
+		\hline 
 		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
+		\hline 
 		X & 1.48 & -0.75 & 0.73\\
+		\hline 
 		Y & 1.56 & -0.76 & 0.80\\
+		\hline 
 		Z & 1.47 & 6.53 & 8.00\\
+		\hline
 
@@
 	\centering
-	\begin{tabular}{l l}
+	\begin{tabular}{l | l}
 		\tabhead{Name} & \tabhead{Content} \\

### 2022-08-01 paper/akweury/document.tex
update eval

--- 2022-07-31 paper/akweury/document.tex
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & & & & 9.82 \\ 
+		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & & 9.82 \\ 
 		\hline
-		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & & & & 7.32\\ 
+		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & & 7.32\\ 
 		\hline
-		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & & & & 7.35 \\
+		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & & 7.35 \\
 		\hline
-		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & & & & 9.15 \\
+		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & & 9.15 \\
 		\hline
-		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & & & & 12.13\\
+		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & & 12.13\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & & & & 7.62 \\ 
+		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & & 7.62 \\ 
 		\hline
-		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & & & & 4.01 \\ 
+		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & & 4.01 \\ 
 		\hline
-		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & & & & 5.06 \\
+		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & & 5.06 \\
 		\hline
-		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & & & & 5.81\\
+		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & & 5.81\\
 		\hline
-		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& & & & 6.76\\
+		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & & 6.76\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & & & & 0.31\\ 
+		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & & 0.31\\ 
 		\hline
-		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & & & & 0.59 \\ 
+		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & & 0.59 \\ 
 		\hline
-		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & & & & 0.50\\
+		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & & 0.50\\
 		\hline
-		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & & & & 0.45\\
+		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & & 0.45\\
 		\hline
-		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & & & & 0.41\\
+		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & & 0.41\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 & & & & 0.69\\ 
+		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & & 0.69\\ 
 		\hline
-		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & & & & 0.83 \\ 
+		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & & 0.83 \\ 
 		\hline
-		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & & & & 0.82\\
+		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & & 0.82\\
 		\hline
-		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 & & & & 0.75\\
+		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & & 0.75\\
 		\hline
-		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & & & & 0.66\\
+		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & & 0.66\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & & & & 0.92\\ 
+		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & & 0.92\\ 
 		\hline
-		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & & & & 0.94\\ 
+		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & & 0.94\\ 
 		\hline
-		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & & & & 0.95\\
+		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & & 0.95\\
 		\hline
-		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & & & & 0.91\\
+		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & & 0.91\\
 		\hline
-		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & & & & 0.84\\
+		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & & 0.84\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & & & & 0.97 \\ 
+		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & & 0.97 \\ 
 		\hline
-		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & & & & 0.96 \\ 
+		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & & 0.96 \\ 
 		\hline
-		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & & & & 0.98 \\
+		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & & 0.98 \\
 		\hline
-		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & & & & 0.95 \\
+		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & & 0.95 \\
 		\hline
-		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & & & & 0.90\\
+		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & & 0.90\\
 	\end{tabular}
@@
 \newpage
-\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }
+\section{Visualized evaluation on Trip-Net models }
 
@@
 Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
+	\label{fig:tripnet-eval-synthetic-zoom-in}
+\end{figure}
+
+%% F1-F4 eval
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f1.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f2.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f4.png}
+	\end{subfigure}
+
+		\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f1.png}
+		\caption{F1}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f2.png}
+		\caption{F2}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
+		\caption{F3}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f4.png}
+		\caption{F4}
+	\end{subfigure}
+
+	\caption{Comparison between different fusion times for Trip-Net. The first row is surface normal, the second row is the corresponding errors. The number in ``F$ x $" represents the fusion times. }
 	\label{fig:tripnet-eval-synthetic-zoom-in}
@@
 
+\section{Trining on higher resolution}
+We also prepared the dataset with resolution $ 512\times 512 $ for model evaluation.
+Higher resolution gives more information about the surface feature using the same model compare to lower resolution.
+The benefit is, if we extract a fixed sized patch from the normal map, say $ 32 \times 32 $, it might correspond a hindleg area of the dragon object in $ 128\times 128 $ resolution but maybe only a toe in $ 512\times 512 $ resolution.
+Therefore if we still use the same kernel size in the network for the same dataset, the higher the resolution it has, the less area it will cover.
+This is a good thing.
+Because then we only need to use these $ 32\times 32 $ points to calculate a toe in $ 512\times512 $ resolution image.
+But in $ 128\times128 $ resolution image, we use the same area $ 32\times32 $ to calculate the whole hindleg.
+In another word, we can also say that the higher resolution ``smooth" the object surface.
+Thus the higher resolution helps the model to calculate a more accurate normal map.
+
+We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution.
+Figure \ref{fig:high_resolution_eval} gives a comparison among SVD, GCNN and Trip-Net models.
+
 \end{document}

### 2022-08-01 eval_visual.py

@@ -37,7 +37,8 @@ def preprocessing(models):
     parser.add_argument('--data', type=str, default='synthetic_noise', help="choose evaluate dataset")
     parser.add_argument('--datasize', type=str, default='synthetic128', help="choose evaluate dataset size")
     parser.add_argument('--combine', type=str, default='true', help="combine the output images in one")
-
+    parser.add_argument('--gpu', type=int, default=0, help="choose GPU index")
+    parser.add_argument('--data_type', type=str, default="normal_noise", help="choose data type")
     parser.add_argument('--machine', type=str, default="local", choices=['local', 'remote'],
                         help="loading dataset from local or dfki machine")
     args = parser.parse_args()
@@ -440,24 +441,31 @@ def start2(models_path_dict):
 if __name__ == '__main__':
     # load test model names
 
+    # models = {
+    #     # "light-gcnn": config.paper_exp / "light" / "checkpoint-640.pth.tar",
+    #     # "light-noc": config.paper_exp / "light" / "checkpoint-noc-499.pth.tar",
+    #     # "light-cnn": config.paper_exp / "light" / "checkpoint-cnn-599.pth.tar",
+    #     #
+    #     # "SVD": None,
+    #     #
+    #     # "GCNN-GCNN": config.paper_exp / "gcnn" / "checkpoint-gcnn-1099.pth.tar",  # GCNN
+    #     # "GCNN-NOC": config.paper_exp / "gcnn" / "checkpoint-noc-807.pth.tar",
+    #     # "GCNN-CNN": config.paper_exp / "gcnn" / "checkpoint-cnn-695.pth.tar",
+    #     #
+    #     # "an2-8-1000": config.paper_exp / "an2" / "checkpoint-8-1000-655.pth.tar",  # Trip Net
+    #     # "f1": config.ws_path / "an2" / "an2_gnet-f1f_2022-07-30_22_33_05" / "checkpoint-655.pth.tar",
+    #     # "f2": config.ws_path / "an2" / "an2_gnet-f2f_2022-07-30_22_33_53" / "checkpoint-662.pth.tar",
+    #     "f3": config.ws_path / "an2" / "an2_gnet-f3f_2022-07-30_22_34_22" / "checkpoint-168.pth.tar",
[…]

### 2022-08-01 help_funs/visual_loss_from_multi_model.py

@@ -1,6 +1,6 @@
 import numpy as np
 import torch
-
+import matplotlib.pyplot as plt
 import config
 from help_funs import chart
 
@@ -8,16 +8,21 @@ models = {
 
     # "NOC": config.ws_path / "nnnn" / "output_2022-07-30_20_39_43" / "checkpoint-459.pth.tar",
     # "CNN": config.ws_path / "nnnn" / "output_2022-07-30_20_41_10" / "checkpoint-461.pth.tar",
-    # "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-07-30_22_33_05" / "checkpoint-647.pth.tar",  # Trip Net
-    # "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-07-30_22_33_53" / "checkpoint-610.pth.tar",  # Trip Net
+    "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-07-30_22_33_05" / "checkpoint-647.pth.tar",  # Trip Net
+    "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-07-30_22_33_53" / "checkpoint-610.pth.tar",  # Trip Net
     # "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-07-30_22_34_22" / "checkpoint-299.pth.tar",  # Trip Net
     # "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-07-30_22_32_25" / "checkpoint-452.pth.tar",  # Trip Net
-    "An_Real": config.ws_path / "an2" / "an_real_gnet-f4_2022-08-01_10_06_35" / "checkpoint-4.pth.tar",  # Trip Net
+    #
+    "CNN": config.ws_path / "nnnn" / "output_2022-07-30_20_41_10" / "checkpoint-1414.pth.tar",  # Trip Net
+    "NOC": config.ws_path / "nnnn" / "output_2022-07-30_20_39_43" / "checkpoint-1415.pth.tar",  # Trip Net
+    # "GCNN": config.ws_path / "nnnn" / "nnnn_gcnn_2022-07-31_10_39_24" / "checkpoint-883.pth.tar",  # Trip Net
+
+    # "An_Real": config.ws_path / "an2" / "an_real_gnet-f4_2022-08-01_10_06_35" / "checkpoint-4.pth.tar",  # Trip Net
 
 }
 
[…]

### 2022-08-01 paper/akweury/document.tex
update eval

@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f3.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f3.png}
 		\caption{F3}
@@
 
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_SVD.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_GCNN-512-269.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_Trip-Net-512.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_GCNN-512-269.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_Trip-Net-512.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+
+	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
+	\label{fig:high_resolution_eval}
+\end{figure}
+
+%% 5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l l l }
+		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
+		Mean  					& 20 & 5.43 & \\ 
+		\hline
+		Median					& 20 & 3.53 & \\ 
+		\hline
+		$ 5^\circ $ 			& 20 & 0.67 & \\
+		\hline
+		$ 11.5^\circ $ 			& 20 & 0.89 & \\
+		\hline
+		$ 22.5^\circ $ 			& 20 & 0.97 & \\
+		\hline
+		$ 30^\circ $ 			& 20 & 0.98 & \\
+	\end{tabular}
+	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
+	\label{tab:high_resolution_eval}
+\end{table}
+
 \end{document}

### 2022-08-01 workspace/train.py

@@ -448,15 +448,7 @@ def train_epoch(nn_model, epoch, eval_loss_best):
         draw_line_chart(np.array([nn_model.losses[9]]), nn_model.output_folder,
                         log_y=True, label="albedo", epoch=epoch, start_epoch=0, title="albedo_loss", cla_leg=True)
 
-    # indicate for best model saving
-    if nn_model.best_loss > loss_total:
-        nn_model.best_loss = loss_total
-        print(f'best loss updated to {float(loss_total / len(nn_model.train_loader.dataset)):.8e}')
-        is_best = True
-    else:
-        is_best = False
-
-    return is_best, nn_model.losses
+    return False, nn_model.losses
 
 
 def test_epoch(nn_model, epoch):
@@ -494,13 +486,13 @@ def test_epoch(nn_model, epoch):
                 loss_total += normal_loss_total
 
             if nn_model.args.normal_huber_loss:
-                normal_out = out[:, :3, :, :]
-
-                nn_model.normal_loss_eval = loss_utils.weighted_unit_vector_huber_loss(normal_out,
-                                                                                       target[:, :3, :, :],
-                                                                                       nn_model.args.penalty,
-                                                                                       epoch,
-                                                                                       nn_model.args.loss_type)
+                normal_out = out[:, :3, :, :].permute(1, 2, 0).to('cpu').numpy()
+                gt = target[:, :3, :, :].permute(2, 3, 1, 0).to("cpu").squeeze(-1).numpy()
+                mask = gt.sum(axis=2) == 0
+                normal_out[mask] = 0
+                normal_out[normal_out > 1] = 1
+                normal_out[normal_out < -1] = -1
+                _, nn_model.normal_loss_eval = mu.eval_img_angle(gt, normal_out)
 
                 loss += nn_model.normal_loss_eval
                 # for plot purpose
@@ -740,6 +732,11 @@ def main(args, exp_dir, network, train_dataset):
                 draw_line_chart(nn_model.losses_eval, nn_model.output_folder,
                                 log_y=True, label="eval_loss", epoch=epoch, start_epoch=0, title="eval_loss",
                                 cla_leg=True)
+            if eval_loss_best < eval_loss:
+                stop_factor += 1
+                if stop_factor > 2:
+                    print("two times error up. stop training")
+                    break
 
             if eval_loss < eval_loss_best:
                 eval_loss_best = eval_loss

### 2022-08-02 paper/akweury/document.tex
update eval

@@
 	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_normal_SVD.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_normal_GCNN-512.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_Trip-Net-512.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_error_GCNN-512.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_Trip-Net-512.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+
+	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
+	\label{fig:high_resolution_eval}
+\end{figure}
+
+%% 5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l l l }
+		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
+		Mean  					& 8.88 & 5.43 & \\ 
+		\hline
+		Median					& 3.66 & 3.53 & \\ 
+		\hline
+		$ 5^\circ $ 			& 0.63 & 0.67 & \\
+		\hline
+		$ 11.5^\circ $ 			& 0.79 & 0.89 & \\
+		\hline
+		$ 22.5^\circ $ 			& 0.89 & 0.97 & \\
+		\hline
+		$ 30^\circ $ 			& 0.92 & 0.98 & \\
+	\end{tabular}
+	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
+	\label{tab:high_resolution_eval}
+\end{table}
+
+\section{Training on Real-Dataset}
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_groundtruth.png}
@@
 
-%% 5 degree metric
 \begin{table}[H]
@@
 		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
-		Mean  					& 20 & 5.43 & \\ 
+		Mean  					& 8.20 & 8.90 & 8.80\\ 
 		\hline
-		Median					& 20 & 3.53 & \\ 
+		Median					& 4.87 & 5.82 & 5.66 \\ 
 		\hline
-		$ 5^\circ $ 			& 20 & 0.67 & \\
+		$ 5^\circ $ 			& 0.51 & 0.43 & 0.44 \\
 		\hline
-		$ 11.5^\circ $ 			& 20 & 0.89 & \\
+		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.78 \\
 		\hline
-		$ 22.5^\circ $ 			& 20 & 0.97 & \\
+		$ 22.5^\circ $ 			& 0.93 & 0.93 & 0.93 \\
 		\hline
-		$ 30^\circ $ 			& 20 & 0.98 & \\
+		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96\\
 	\end{tabular}

### 2022-08-02 paper/akweury/document.tex
update eval

@@
 
-The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
-Each scene has a depth map with dimension $ 128\times 128 \times $ in height, width and channel, an image with dimension $ 128\times 128 \times 1 $.
+The models are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
+Each scene has a depth map with dimension $ 128\times 128 $ in height and width, an image with dimension $ 128\times 128 \times 1 $.
 The depth map is converted to 3D vertex map as introduced in Chapter \ref{ch:04}.
@@
 
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.normal0.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0_noise.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.image0.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.normal0.png}
@@
 
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.normal0.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.normal0.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
@@
 
-The training processes are evaluated in every epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
+The training processes are evaluated in every epochs with 29 evaluation scenes that models never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
 Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
-Note that the position of objects are not placed naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
+Note that the position of objects are not placed always naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
 
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
+For the training parameters, we set the training pipeline with batch size $ 8 $, we found that a higher batch size will reduce the final performance.
+Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
 The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
@@
 
-In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
-We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN".
+In order to verify the applicability of the skip connection and the gated convolution layers, we trained two extra models as a comparison.
+The first model, we replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same, and give it a name ``CNN".
 It is used to verify the performance the gated convolution layers.
@@
 Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
-Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same.
-Is is designed to show the validation of skip connections.
-Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss.
-The GCNN approach achieves a lower loss from start to the end of the training.
+Another model called ``NOC" is designed to verify the skip connection, which simply removes the skip connections in the network but keeps other settings same.
+Is is designed to show to which content will skip connection help the model performance.
+
+We use Reversed Huber Loss as loss function during the training, since we found it gives a better final error compare to L2 loss.
+The model is evaluated after every epoch training and calculate the angle error on the test dataset.
+The training history is shown in Figure \ref{fig:gcnn-training-history}.
+We can see that all of these three models can learn the normal inference task where the model ``NOC" has the highest error, which is the effect of the missing of skip connection.
+The ``CNN" model has the skip connection but use standard convolution layer has a better performance.
+The GCNN model use the skip connection and the gated convolution layer further reduce the error.
 
@@
 	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
+	\includegraphics[width=\textwidth]{./Figures/gcnn_training_loss.png}
+
+	\includegraphics[width=\textwidth]{./Figures/gcnn_eval_loss.png}
 	\caption{The training history of GCNN model.

### 2022-08-02 help_funs/visual_loss_from_multi_model.py

@@ -1,15 +1,16 @@
+import matplotlib.pyplot as plt
 import numpy as np
 import torch
-import matplotlib.pyplot as plt
+
 import config
 from help_funs import chart
 
 models = {
 
-    "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-01_22_55_21" / "checkpoint-298.pth.tar",  # Trip Net
-    "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-02_11_46_55" / "checkpoint-27.pth.tar",  # Trip Net
-    "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-01_22_32_35" / "checkpoint-296.pth.tar",  # Trip Net
-    "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-01_22_31_37" / "checkpoint-234.pth.tar",  # Trip Net
+    # "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-01_22_55_21" / "checkpoint-298.pth.tar",  # Trip Net
+    # "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-02_11_46_55" / "checkpoint-27.pth.tar",  # Trip Net
+    # "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-01_22_32_35" / "checkpoint-296.pth.tar",  # Trip Net
+    # "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-01_22_31_37" / "checkpoint-234.pth.tar",  # Trip Net
     #
     "CNN": config.ws_path / "nnnn" / "nnnn_cnn_2022-08-01_22_55_17" / "checkpoint-456.pth.tar",  # Trip Net
     "NOC": config.ws_path / "nnnn" / "nnnn_gcnn_noc_2022-08-01_22_55_21" / "checkpoint-435.pth.tar",  # Trip Net
@@ -18,7 +19,8 @@ models = {
 }
 
 output_folder = config.paper_exp
-plt.figure(figsize=(20, 6))
+plt.rcParams.update({'font.size': 30})
+plt.figure(figsize=(30, 10))
 plt.grid(True)
 
 for model_idx, (name, model) in enumerate(models.items()):
[…]

### 2022-08-02 paper/akweury/document.tex
update an2

@@
 
-In order to verify the applicability of the skip connection and the gated convolution layers, we trained two extra models as a comparison.
-The first model, we replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same, and give it a name ``CNN".
-It is used to verify the performance the gated convolution layers.
-As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
-Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
-Another model called ``NOC" is designed to verify the skip connection, which simply removes the skip connections in the network but keeps other settings same.
-Is is designed to show to which content will skip connection help the model performance.
-
-We use Reversed Huber Loss as loss function during the training, since we found it gives a better final error compare to L2 loss.
-The model is evaluated after every epoch training and calculate the angle error on the test dataset.
-The training history is shown in Figure \ref{fig:gcnn-training-history}.
-We can see that all of these three models can learn the normal inference task where the model ``NOC" has the highest error, which is the effect of the missing of skip connection.
-The ``CNN" model has the skip connection but use standard convolution layer has a better performance.
-The GCNN model use the skip connection and the gated convolution layer further reduce the error.
-
-\begin{figure}[th]
+\begin{figure}[H]
 	\centering
@@
 
+In order to verify the applicability of the skip connection and the gated convolution layers, we trained two extra models as a comparison.
+The first model, we replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same, and give it a name ``CNN".
+It is used to verify the performance the gated convolution layers.
+As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
+Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
+Another model called ``NOC" is designed to verify the skip connection, which simply removes the skip connections in the network but keeps other settings same.
+Is is designed to show to which content will skip connection help the model performance.
+We use Reversed Huber Loss as loss function during the training, since we found it gives a better final error compare to L2 loss.
+The model is evaluated after every epoch training and calculate the angle error on the test dataset.
+The training history is shown in Figure \ref{fig:gcnn-training-history}.
+
+%% TODO
+waiting for the experiment, then describe the chart...
+
+\begin{table}[H]
+
+	\centering
+	\begin{tabular}{l l l l l l }
+		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB}\\
+		\hline
+		CNN 					& 17 & 32 & 0 & 0 & 25.5 \\
+		\hline
+		NOC 					& 32 & 32 & 0 & 0 & 30.6 \\
+		\hline
+		GCNN 					& 32 & 32 & 0 & 0 & 45.8 \\
+	\end{tabular}
+	\caption{GCNN Model information.
+Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
+Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
+}
+	\label{tab:gcnn-eval-mean}
+\end{table}
+
 \section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
@@
 It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
-For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
+When we train this model, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
  Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
-A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $F, where $ x $ denotes the fusion times.
+A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
 We evaluate the fusion times from 1 to 4.
@@
 
-Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.
-As shown in the loss figure, all of the four models has a reasonable learning rate.
-Trip-Net with four times fusion converges faster than others and also achieve a lower loss.
-Trip-Net-F3F converges slower than Trip-Net but achieved to a similar evaluation loss.
-The evaluation loss in Trip-Net-F1F and Trip-Net-F2F are relative higher than 3 or 4 times fusions model.
+Figure \ref{fig:trip-net-training-history} shows the training history of Trip-Net models on BerHu Loss. As shown in the loss figure, all of the four models has a reasonable learning rate. 
+From the chart we can see that, trip-Net with four times fusion converges obviously faster than fewer fusion times model.
+However, model F3 with 3 times fusion converge slower than F4 but in the end it achieves a similar evaluation loss with F4.
+The F1 and F2 models are relatively weaker than the other two models.
 
-\begin{figure}[th]
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
+	\includegraphics[width=\textwidth]{./Figures/trip_net_training_loss.png}
+	\includegraphics[width=\textwidth]{./Figures/trip_net_eval_loss.png}
 	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
@@
 		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
-		\hline
-		GCNN 					& 32 & 32 & 0 & 0 & 46 & 2.18\\
 	\end{tabular}
-	\caption{Model information.
+	\caption{Trip-Net Model information.
 Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
@@
 }
-	\label{tab:gcnn-eval-mean}
+	\label{tab:trip-net-size-compare}
 \end{table}
 
-\section{Evaluation}
+\section{Quantitative Evaluation}
 

### 2022-08-02 paper/akweury/document.tex
update eval
update an2

@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_groundtruth.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_normal_GCNN-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_Trip-Net-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_img.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_error_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
 		\caption{SVD}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_error_GCNN-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_Trip-Net-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
 		\caption{Trip-Net}
@@
 \end{figure}
-
 %% 5 degree metric
@@
 		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
-		Mean  					& 8.88 & 5.43 & \\ 
+		Mean  					& 8.88 & 5.82 & 5.33 \\ 
 		\hline
-		Median					& 3.66 & 3.53 & \\ 
+		Median					& 3.66 & 3.98 & 3.67 \\ 
 		\hline
-		$ 5^\circ $ 			& 0.63 & 0.67 & \\
+		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
 		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.89 & \\
+		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
 		\hline
-		$ 22.5^\circ $ 			& 0.89 & 0.97 & \\
+		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
 		\hline
-		$ 30^\circ $ 			& 0.92 & 0.98 & \\
+		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
 	\end{tabular}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_groundtruth.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_GCNN-512-269.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_Trip-Net-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_img.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
 		\caption{SVD}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_GCNN-512-269.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
 		\caption{GCNN}

### 2022-08-02 eval_single_obj.py

@@ -110,14 +110,14 @@ if __name__ == '__main__':
             if args.data == "synthetic":
                 test_folder = config.synthetic_data_noise_pc2103 / "synthetic512" / "test" / "tensor"
             else:
-                test_folder = config.real_data_dfki / "test"
+                test_folder = config.real_data_pc2103 / "test"
             models = {
-                # "Trip-Net-512": config.model_dfki / "checkpoint-32.pth.tar",  # GCNN
-                # "Trip-Net-512-36": config.ws_path / "an2" / "checkpoint-36.pth.tar",  # GCNN
-                "Trip-Net-512-41": config.ws_path / "an2" / "checkpoint-41.pth.tar",  # GCNN
-                # "Trip-Net-512-32": config.ws_path / "an2" / "checkpoint-32.pth.tar",  # GCNN
-                "SVD": None,
-                "NNNN-512": config.ws_path / "nnnn" / "checkpoint-226.pth.tar",  # GCNN
+                "An2-real-train": config.ws_path / "an2_real" / "checkpoint-train-82.pth.tar",
+                "An2-real-resume": config.ws_path / "an2_real" / "checkpoint-resume-444.pth.tar",
+
+                # "SVD": None,
+                # "NNNN-512": config.ws_path / "nnnn" / "checkpoint-226.pth.tar",  # GCNN
+                # "Trip-Net-512-41": config.ws_path / "an2" / "checkpoint-41.pth.tar",  # GCNN
 
             }
         else:

### 2022-08-02 paper/akweury/document.tex
update eval

@@
 	\centering
+
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
+		\caption{GT}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
+	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
+	\caption{SVD}
 \end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
+		\caption{GCNN}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
+		\caption{Trip-Net}
 	\end{subfigure}
@@
 		\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_img.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_img.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_SVD.png}
 		\caption{SVD}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_NNNN-512.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_Trip-Net-512.png}
 		\caption{Trip-Net}
@@
 		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
-		Mean  					& 8.20 & 8.90 & 8.80\\ 
+		Mean  					& 8.20 & 8.90 & 8.30\\ 
 		\hline
-		Median					& 4.87 & 5.82 & 5.66 \\ 
+		Median					& 4.87 & 5.82 & 5.14 \\ 
 		\hline
-		$ 5^\circ $ 			& 0.51 & 0.43 & 0.44 \\
+		$ 5^\circ $ 			& 0.51 & 0.43 & 0.49 \\
 		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.78 \\
+		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.80 \\
 		\hline

### 2022-08-02 eval_visual.py

@@ -214,7 +214,7 @@ def start2(models_path_dict):
         light_input = test_0_tensor[:, 13:16, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
         vertex_0 = test_0_tensor[:, :3, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
 
-        img_0 = test_0_tensor[:, 3:4, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
+        img_0 = gt_tensor[:, 3:4, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
 
         mask = gt.sum(axis=2) == 0
         # mask_input = vertex_0.sum(axis=2) == 0
@@ -463,8 +463,8 @@ if __name__ == '__main__':
         # "f2": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-02_01_06_20" / "model_best.pth.tar",
 
         # "Trip-Net-512-36": config.ws_path / "an2" / "checkpoint-36.pth.tar",  # GCNN
-        "Trip-Net-512": config.ws_path / "an2" / "checkpoint-41.pth.tar",  # GCNN
-        "An2-real-train": config.ws_path / "an_real" / "checkpoint-train-82.pth.tar",
+        # "Trip-Net-512": config.ws_path / "an2" / "checkpoint-41.pth.tar",  # GCNN
+        # "An2-real-train": config.ws_path / "an_real" / "checkpoint-train-82.pth.tar",
         "An2-real-resume": config.ws_path / "an_real" / "checkpoint-resume-444.pth.tar",
         "SVD": None,
         "NNNN-512": config.ws_path / "nnnn" / "checkpoint-226.pth.tar",  # GCNN

### 2022-08-02 paper/akweury/document.tex
update an2

@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & & 9.82 \\ 
+		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & 9.77 & 9.80 \\ 
 		\hline
-		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & & 7.32\\ 
+		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & 7.30 & 7.62\\ 
 		\hline
-		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & & 7.35 \\
+		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 & 7.79 \\
 		\hline
-		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & & 9.15 \\
+		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 & 9.39 \\
 		\hline
-		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & & 12.13\\
+		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 & 12.60\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & & 7.62 \\ 
+		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 & 7.50 \\ 
 		\hline
-		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & & 4.01 \\ 
+		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & 3.65 & 4.47 \\ 
 		\hline
-		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & & 5.06 \\
+		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 & 5.52 \\
 		\hline
-		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & & 5.81\\
+		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & 6.04 \\
 		\hline
-		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & & 6.76\\
+		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & 7.03 & 7.25\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & & 0.31\\ 
+		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & 0.33 & 0.32\\ 
 		\hline
-		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & & 0.59 \\ 
+		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & 0.63 & 0.55 \\ 
 		\hline
-		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & & 0.50\\
+		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 & 0.46\\
 		\hline
-		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & & 0.45\\
+		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & 0.43\\
 		\hline
-		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & & 0.41\\
+		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & 0.40 & 0.37\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & & 0.69\\ 
+		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & 0.69 & 0.69\\ 
 		\hline
-		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & & 0.83 \\ 
+		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & 0.83 & 0.83 \\ 
 		\hline
-		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & & 0.82\\
+		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & 0.81\\
 		\hline
-		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & & 0.75\\
+		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 & 0.75\\
 		\hline
-		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & & 0.66\\
+		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & 0.65\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & & 0.92\\ 
+		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & 0.92 & 0.92\\ 
 		\hline
-		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & & 0.94\\ 
+		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & 0.94\\ 
 		\hline
-		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & & 0.95\\
+		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & 0.95\\
 		\hline
-		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & & 0.91\\
+		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & 0.91 & 0.91\\
 		\hline
-		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & & 0.84\\
+		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & 0.83 & 0.83\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & & 0.97 \\ 
+		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & 0.97 & 0.97 \\ 
 		\hline
-		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & & 0.96 \\ 
+		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & 0.96 & 0.96 \\ 
 		\hline
-		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & & 0.98 \\
+		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & 0.98 \\
 		\hline
-		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & & 0.95 \\
+		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & 0.95 \\
 		\hline
-		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & & 0.90\\
+		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & 0.89 & 0.89\\
 	\end{tabular}
@@
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
+\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/00008.image0.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
+	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_SVD.png}
 	\caption{SVD}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
+	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_NNNN-512.png}
 	\caption{GCNN}
@@
 \begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
+	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_An2-real-resume.png}
 	\caption{Trip-Net}
 \end{subfigure}	
-
-		\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_img.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_NNNN-512.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_Trip-Net-512.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-
-	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
+	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ real dataset. The first row is surface normal, the second row is the corresponding errors. }
 	\label{fig:high_resolution_eval}
@@
 	\end{tabular}
-	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
+	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes in real dataset.}	
 	\label{tab:high_resolution_eval}

### 2022-08-03 paper/akweury/document.tex
update eval

@@
 
-The training processes are evaluated in every epochs with 29 evaluation scenes that models never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
+The training processes are evaluated in every epochs with 100 evaluation scenes that models never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
 Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
@@
 Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
-The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
+The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTXA 6000.
 It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
@@
 
-\section{GCNN model based on Geometry Information}
-The GCNN model is the base model of the whole thesis.
+GCNN model is the base model of the whole thesis.
 The architecture is described in \ref{sec:gcnn}.
@@
 It uses vertex map as input to estimate the corresponding tangent surface normal map.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{./Figures/gcnn_training_loss.png}
-
-	\includegraphics[width=\textwidth]{./Figures/gcnn_eval_loss.png}
-	\caption{The training history of GCNN model.
-The line chart records the training BerHu loss of the model GCNN, NOC and CNN.
-The left shows the training loss history whereas the right one shows the evaluation loss history.}
-	\label{fig:gcnn-training-history}
-\end{figure}
-
 In order to verify the applicability of the skip connection and the gated convolution layers, we trained two extra models as a comparison.
@@
 We use Reversed Huber Loss as loss function during the training, since we found it gives a better final error compare to L2 loss.
-The model is evaluated after every epoch training and calculate the angle error on the test dataset.
-The training history is shown in Figure \ref{fig:gcnn-training-history}.
-
-%% TODO
-waiting for the experiment, then describe the chart...
 
@@
 
-\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
 The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train.
@@
 
-Figure \ref{fig:trip-net-training-history} shows the training history of Trip-Net models on BerHu Loss. As shown in the loss figure, all of the four models has a reasonable learning rate. 
-From the chart we can see that, trip-Net with four times fusion converges obviously faster than fewer fusion times model.
-However, model F3 with 3 times fusion converge slower than F4 but in the end it achieves a similar evaluation loss with F4.
+We also found that, trip-Net with four times fusion converges obviously faster than fewer fusion times model.
+However, model F3 with 3 times fusion converge slower than F4 but in the end it achieves a similar evaluation loss with F4(see Qualitative evaluation).
 The F1 and F2 models are relatively weaker than the other two models.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{./Figures/trip_net_training_loss.png}
-	\includegraphics[width=\textwidth]{./Figures/trip_net_eval_loss.png}
-	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
-	\label{fig:trip-net-training-history}
-\end{figure}
 
@@
 	\centering
-	\begin{tabular}{l l l l l l l }
-		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB} & \tabhead{Time /h}\\
-		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106  &  9.82\\ 
+	\begin{tabular}{l l l l l l }
+		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB}\\
+		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106\\ 
 		\hline
-		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 &  7.35\\ 
+		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 \\ 
 		\hline
-		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 &  7.35\\
+		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 \\
 		\hline
-		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
+		Trip-Net 				& 100 & 40 & 30 & 30 & 198\\
 	\end{tabular}
@@
 \section{Quantitative Evaluation}
-
+We evaluated our models on synthetic dataset with resolution $ 128\times 128 $. 
 Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation.
@@
 
-Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis.
 When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
 When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
+
+From the table we can see that all the learning based approaches achieves a better result than SVD approach.
+In the 30 degrees error metric, GCNN based approach achieves 95 \% accuracy whereas Trip-Net is even higher, some of the models like $ dragon $ achieves 98\%.
+The best performance is around 90\%, 75 \%, 45 \% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metric respectively.
+Another notable result is the close performance of F3 and F4 models, where they achieves a very comparable performance.
+We also found that during the training, F4 model converges faster than F3, but F3 in the end achieves a similar loss with model F4.
+However, based on the$ 30^\circ $, $ 22.5^\circ $, $ 11.5^\circ $ metrics, we can still see that F4 model gives a more stable performance with less high error normals.
+This is reasonable since the last fusion in the original resolution provides more high resolution information to the model.
 
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & 9.77 & 9.80 \\ 
+		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 &\textbf{ 9.77 }& 9.80 \\ 
 		\hline
-		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & 7.30 & 7.62\\ 
+		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & \textbf{7.30} & 7.62\\ 
 		\hline
-		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 & 7.79 \\
+		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 &\textbf{ 7.79} \\
 		\hline
-		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 & 9.39 \\
+		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 &\textbf{ 9.39} \\
 		\hline
-		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 & 12.60\\
+		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 &\textbf{ 12.60}\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 & 7.50 \\ 
+		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 &\textbf{ 7.50} \\ 
 		\hline
-		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & 3.65 & 4.47 \\ 
+		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & \textbf{3.65 }& 4.47 \\ 
 		\hline
-		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 & 5.52 \\
+		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 &\textbf{ 5.52} \\
 		\hline
-		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & 6.04 \\
+		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & \textbf{6.04 }\\
 		\hline
-		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & 7.03 & 7.25\\
+		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 &\textbf{ 7.03 }& 7.25\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & 0.33 & 0.32\\ 
+		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 &\textbf{ 0.33 }& 0.32\\ 
 		\hline
-		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & 0.63 & 0.55 \\ 
+		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & \textbf{0.63 }& 0.55 \\ 
 		\hline
-		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 & 0.46\\
+		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 &\textbf{ 0.46}\\
 		\hline
-		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & 0.43\\
+		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & \textbf{0.43}\\
 		\hline
-		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & 0.40 & 0.37\\
+		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & \textbf{0.40 }& 0.37\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & 0.69 & 0.69\\ 
+		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 &\textbf{ 0.69 }& \textbf{0.69}\\ 
 		\hline
-		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & 0.83 & 0.83 \\ 
+		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & \textbf{0.83 }&\textbf{ 0.83 }\\ 
 		\hline
-		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & 0.81\\
+		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & \textbf{0.81}\\
 		\hline
-		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 & 0.75\\
+		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 &\textbf{ 0.75}\\
 		\hline
-		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & 0.65\\
+		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & \textbf{0.65}\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & 0.92 & 0.92\\ 
+		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 &\textbf{ 0.92} &\textbf{ 0.92}\\ 
 		\hline
-		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & 0.94\\ 
+		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & \textbf{0.94}\\ 
 		\hline
-		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & 0.95\\
+		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & \textbf{0.95}\\
 		\hline
-		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & 0.91 & 0.91\\
+		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 &\textbf{ 0.91} &\textbf{ 0.91}\\
 		\hline
-		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & 0.83 & 0.83\\
+		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & \textbf{0.83} &\textbf{ 0.83}\\
 	\end{tabular}
@@
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & 0.97 & 0.97 \\ 
+		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 &\textbf{ 0.97 }&\textbf{ 0.97} \\ 
 		\hline
-		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & 0.96 & 0.96 \\ 
+		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & \textbf{0.96} &\textbf{ 0.96} &\textbf{ 0.96 }\\ 
 		\hline
-		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & 0.98 \\
+		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & \textbf{0.98} \\
 		\hline
-		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & 0.95 \\
+		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & \textbf{0.95 }\\
 		\hline
-		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & 0.89 & 0.89\\
+		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & \textbf{0.89} & \textbf{0.89}\\
 	\end{tabular}
@@
 A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
-In the same case, NOC model as shown in Figure  \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
+In the same case, NOC model as shown in Figure.
+\ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
 CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
 Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).
+
+Figure \ref{fig:gcnn-eval-more} shows more evaluation on GCNN model.
+Although we can get a good result from GCNN model but from model ``Washington" we still can see it lacks the sharpness in the detail area like the face and clothes area.
 
@@
 
+%% gcnn-Visual-more
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_input.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
+\end{subfigure}
+\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
+\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+		\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_point_cloud_noise.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
+		\caption{Error}
+	\end{subfigure}
+
+		\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-CNN.png}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
+	\label{fig:gcnn-eval-more}
+\end{figure}
+
 \newpage
@@
 For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}.
+The Trip-Net uses illuminated information align with the geometry information achieves a sharper and more accurate result compare to the GCNN model.
 The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
@@
 
-As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and close to the ground-truth.
+As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and also close to the ground-truth.
 The head region gives a sharper edge prediction.
 All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
+It seems that the illumination helps the model to learn sharper features in the network.
 
@@
 
-\section{More Comparison}
-Figure \ref{fig:final-eval} gives more visualization on model SVD, GCNN and Trip-Net. Figure \ref{fig:final-eval-zoom-in} is the corresponding zoom-in visualization.
-\newpage
-%% Final-Visual
-\begin{figure}
+%% trip-net-Visual-more
+\begin{figure}[H]
 	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_an2-8-1000.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_img.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_input.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
 	\end{subfigure}
 
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_point_cloud_noise.png}
+	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_img.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_input.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_an2-8-1000.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_point_cloud_noise.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
+		\caption{GT}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
+		\caption{GCNN}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
+		\caption{Error}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_img.png}
-		\caption{GT}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_input.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
-		\caption{TripNet}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
-		\caption{GCNN}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_an2-8-1000.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_SVD.png}
-		\caption{SVD}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
 	\end{subfigure}
@@
 	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
-	\label{fig:final-eval}
-\end{figure}
-
-%% Final-Visual-Zoom-In
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_img.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_img.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-
-	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
-	\label{fig:final-eval-zoom-in}
+	\label{fig:gcnn-eval-more}
 \end{figure}
@@
 The benefit is, if we extract a fixed sized patch from the normal map, say $ 32 \times 32 $, it might correspond a hindleg area of the dragon object in $ 128\times 128 $ resolution but maybe only a toe in $ 512\times 512 $ resolution.
-Therefore if we still use the same kernel size in the network for the same dataset, the higher the resolution it has, the less area it will cover.
+Therefore if we still use the same kernel size in the network for the same dataset, (like we did with $ 3\times 3 $) the higher the resolution it has, the less area it will cover.
+Thus the surface will more smooth and easy to calculate the surface normal.
 This is a good thing.
-Because then we only need to use these $ 32\times 32 $ points to calculate a toe in $ 512\times512 $ resolution image.
-But in $ 128\times128 $ resolution image, we use the same area $ 32\times32 $ to calculate the whole hindleg.
+Because then we might only need to use these $ 32\times 32 $ points to calculate a toe in $ 512\times512 $ resolution image.
+But in $ 128\times128 $ resolution image, the same area $ 32\times32 $ might corresponding to entire  hindleg of the dragon object.
 In another word, we can also say that the higher resolution ``smooth" the object surface.
@@
 
+Since our model is fully convolution network, the architecture keeps exactly same on the high resolution dataset.
 We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution.
-Figure \ref{fig:high_resolution_eval} gives a comparison among SVD, GCNN and Trip-Net models.
+The training on high resolution network takes longer time but achieves a lower angle error.
 
-\begin{figure}[H]
+%% 5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l l l l }
+		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
+		Mean  					& 8.88 & 5.82 & 5.33 \\ 
+		\hline
+		Median					& 3.66 & 3.98 & 3.67 \\ 
+		\hline
+		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
+		\hline
+		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
+		\hline
+		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
+		\hline
+		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
+	\end{tabular}
+	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
+	\label{tab:high_resolution_eval}
+\end{table}
+
+A quantitative evaluation is shown in table \ref{tab:high_resolution_eval}.
+It follows the same performance rank compare to lower resolution, which is GCNN better than SVD approach and Trip-Net slightly better than GCNN.
+The accuracy is 99 \% in the $ 30^\circ $ metric for Trip-Net and $ 5^\circ $ mean error.
+A qualitative evaluation is shown in figure \ref{fig:trip-eval-high-resolution}, this is a figure object with both smooth area (the belly and arm) and highly detailed area with sharp surface (the uneven surface of stone table).
+Our models gives an average degree area at $ 5^\circ $.
+A comparison with other models is shown in figure \ref{fig:trip-eval-compare}.
+
+Another remarkable result is the SVD approach, which also gives a good result ($ 8.88^\circ $ in mean degree metric).
+Like we discussed, the surface are relative more smooth if we keep the same window size for normal inference.
+In the high resolution scenes, although the percentage of missing pixels in a fixed windows are remain the same compare to small resolution scenes, but the remain valid pixels are mainly on a relatively flat plane thus they are good enough for an accurate normal inference.
+Consequently, we can see from the error map in Figure \ref{fig:high_resolution_eval}, the sharp edges of the dragon, like the horns and the hindlegs, the SVD approach still has high errors.
+
+%% high resolution trip-net visualization
+\begin{figure}[th]
+	\centering
+	\begin{subfigure}[b]{0.48\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_normal_Trip-Net-512.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.48\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_groundtruth.png}
+	\caption{GT}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_point_cloud_noise.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_error_Trip-Net-512.png}
+		\caption{Error}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+
+	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
+	\label{fig:trip-eval-high-resolution}
+\end{figure}
+
+%& trip-net evaluation with other models
+
+\begin{figure}[th]
 	\centering
@@
 	\end{subfigure}
-
 	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
-	\label{fig:high_resolution_eval}
+	\label{fig:trip-eval-compare}
 \end{figure}
-%% 5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l l l }
-		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
-		Mean  					& 8.88 & 5.82 & 5.33 \\ 
-		\hline
-		Median					& 3.66 & 3.98 & 3.67 \\ 
-		\hline
-		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
-		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
-		\hline
-		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
-		\hline
-		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
-	\end{tabular}
-	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
-	\label{tab:high_resolution_eval}
-\end{table}
 
 \section{Training on Real-Dataset}
+We also applied our model on a small dataset that captured by a light scanner in our laboratory in order to see the applicability of our approaches.
+For the geometry information based approach, we use the GCNN model that trained on high resolution synthetic dataset directly, since it only require the depth map as input, the scenarios of two dataset are the same.
+For the illuminated calibrated RGB-D image based approach, the model has to be refined based on the real-dataset, since the light intensity, camera matrix are different.
+We refined the Trip-Net based on a pre-trained GCNN model with the same settings in previous experiments, and observe the results.
+As shown in Figure \ref{fig:real_eval}
 
-\begin{figure}[H]
+\begin{figure}[th]
 	\centering
@@
 	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ real dataset. The first row is surface normal, the second row is the corresponding errors. }
-	\label{fig:high_resolution_eval}
+	\label{fig:real_eval}
 \end{figure}

### 2022-08-03 eval_single_obj.py

@@ -92,8 +92,8 @@ if __name__ == '__main__':
     for folder_name in ["baoshanlu", "bus", "dragon", "garfield", "washington"]:
         if args.machine == "local":
             # test_folder = config.real_data / "test"
-            test_folder = config.synthetic_data_noise_local / "synthetic128" / "seperate" / folder_name
-            # test_folder = config.dataset / "data_synthetic_noise" / "synthetic128" / "tensor"
+            # test_folder = config.synthetic_data_noise_local / "synthetic128" / "seperate" / folder_name
+            test_folder = config.dataset / "data_synthetic_noise" / "synthetic128" / "tensor"
             # test_folder = config.synthetic_data_noise_local / "synthetic512" / "test"
             models = {
                 # "SVD": None,
@@ -101,10 +101,10 @@ if __name__ == '__main__':
                 # "NOC": config.ws_path / "nnnn" / "nnnn_gcnn_noc_2022-08-01_22_55_21" / "checkpoint-435.pth.tar",
                 # "GCNN": config.ws_path / "nnnn" / "nnnn_gcnn_2022-08-01_21_50_45" / "checkpoint-460.pth.tar",
 
-                "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-03_00_01_56" / "checkpoint-150.pth.tar",
-                "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-03_00_01_07" / "checkpoint-150.pth.tar",
-                "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-02_23_59_25" / "checkpoint-150.pth.tar",
-                "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-02_23_58_31" / "checkpoint-100.pth.tar",
+                # "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-03_00_01_56" / "checkpoint-150.pth.tar",
+                # "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-03_00_01_07" / "checkpoint-150.pth.tar",
+                # "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-02_23_59_25" / "checkpoint-150.pth.tar",
[…]

### 2022-08-03 help_funs/visual_loss_from_multi_model.py

@@ -9,12 +9,12 @@ models = {
 
     # "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-03_00_01_56" / "checkpoint-150.pth.tar",
     # "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-03_00_01_07" / "checkpoint-150.pth.tar",
-    "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-02_23_59_25" / "checkpoint-150.pth.tar",
-    "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-02_23_58_31" / "checkpoint-100.pth.tar",
+    # "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-02_23_59_25" / "checkpoint-150.pth.tar",
+    # "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-02_23_58_31" / "checkpoint-100.pth.tar",
     #
-    "CNN": config.ws_path / "nnnn" / "nnnn_cnn_2022-08-03_00_15_34" / "checkpoint-200.pth.tar",
-    "NOC": config.ws_path / "nnnn" / "nnnn_gcnn_noc_2022-08-03_00_07_32" / "checkpoint-200.pth.tar",
-    "GCNN": config.ws_path / "nnnn" / "nnnn_gcnn_2022-08-03_00_02_37" / "checkpoint-200.pth.tar",
+    # "CNN": config.ws_path / "nnnn" / "nnnn_cnn_2022-08-03_00_15_34" / "checkpoint-200.pth.tar",
+    # "NOC": config.ws_path / "nnnn" / "nnnn_gcnn_noc_2022-08-03_00_07_32" / "checkpoint-200.pth.tar",
+    "GCNN": config.ws_path / "nnnn" / "nnnn_gcnn_2022-07-31_10_39_24" / "checkpoint-992.pth.tar",
 
 }
 
@@ -28,15 +28,15 @@ for model_idx, (name, model) in enumerate(models.items()):
     args = checkpoint['args']
     start_epoch = checkpoint['epoch']
     batch_size = args.batch_size
+
     # loss = checkpoint['losses']
     # normal_loss_avg = np.sum(loss[:3], axis=0, keepdims=True) / 3
 
-    loss = checkpoint['eval_losses']
[…]

### 2022-08-03 paper/Chapters/Chapter05.tex
update paper

@@
 	\end{subfigure}
-
+	\decoRule
 	\caption{Some of the test scenes during the training. From top to bottom, baoshanlu, Washington, Garfield, Dragon, Bus}
@@
 
-The training processes are evaluated in every epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
+The training processes are evaluated in every epochs with 100 evaluation scenes that models never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
 Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
-Note that the position of objects are not placed naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
+Note that the position of objects are not placed always naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
 
-The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
-The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
+For the training parameters, we set the training pipeline with batch size $ 8 $, we found that a higher batch size will reduce the final performance.
+Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
+The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTXA 6000.
 It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
@@
 It uses vertex map as input to estimate the corresponding tangent surface normal map.
-
-In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
-We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN".
+In order to verify the applicability of the skip connection and the gated convolution layers, we trained two extra models as a comparison.
+The first model, we replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same, and give it a name ``CNN".
 It is used to verify the performance the gated convolution layers.
@@
 Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
-Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same.
-Is is designed to show the validation of skip connections.
-Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss.
-The GCNN approach achieves a lower loss from start to the end of the training.
+Another model called ``NOC" is designed to verify the skip connection, which simply removes the skip connections in the network but keeps other settings same.
+Is is designed to show to which content will skip connection help the model performance.
+We use Reversed Huber Loss as loss function during the training, since we found it gives a better final error compare to L2 loss.
 
-\begin{figure}[th]
+\begin{table}[H]
+
 	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
-	\caption{The training history of GCNN model.
-The line chart records the training BerHu loss of the model GCNN, NOC and CNN.
-The left shows the training loss history whereas the right one shows the evaluation loss history.}
-	\label{fig:gcnn-training-history}
-\end{figure}
+	\begin{tabular}{l | l l l l l }
+		\toprule
+		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB}\\
+		\midrule
+		\hline
+		CNN 					& 17 & 32 & 0 & 0 & 25.5 \\
+		\hline
+		NOC 					& 32 & 32 & 0 & 0 & 30.6 \\
+		\hline
+		GCNN 					& 32 & 32 & 0 & 0 & 45.8 \\
+		\bottomrule
+	\end{tabular}
+	\caption{GCNN Model information.
+Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
+Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
+}
+	\label{tab:gcnn-eval-mean}
+\end{table}
 
-\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
 The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train.
 It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
-For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
+When we train this model, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
 Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
-A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $F, where $ x $ denotes the fusion times.
+A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
 We evaluate the fusion times from 1 to 4.
@@
 
-Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.
-As shown in the loss figure, all of the four models has a reasonable learning rate.
-Trip-Net with four times fusion converges faster than others and also achieve a lower loss.
-Trip-Net-F3F converges slower than Trip-Net but achieved to a similar evaluation loss.
-The evaluation loss in Trip-Net-F1F and Trip-Net-F2F are relative higher than 3 or 4 times fusions model.
-
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
-	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
-	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
-	\label{fig:trip-net-training-history}
-\end{figure}
+We also found that, trip-Net with four times fusion converges obviously faster than fewer fusion times model.
+However, model F3 with 3 times fusion converge slower than F4 but in the end it achieves a similar evaluation loss with F4(see Qualitative evaluation).
+The F1 and F2 models are relatively weaker than the other two models.
 
@@
 	\centering
-	\begin{tabular}{l l l l l l l }
-		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB} & \tabhead{Time /h}\\
-		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106  &  9.82\\ 
+	\begin{tabular}{l | l l l l l }
+		\toprule
+		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB}\\
+		\midrule
+		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106\\ 
 		\hline
-		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 &  7.35\\ 
+		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 \\ 
 		\hline
-		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 &  7.35\\
+		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 \\
 		\hline
-		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
-		\hline
-		GCNN 					& 32 & 32 & 0 & 0 & 46 & 2.18\\
+		Trip-Net 				& 100 & 40 & 30 & 30 & 198\\
+		\bottomrule
 	\end{tabular}
-	\caption{Model information.
+	\caption{Trip-Net Model information.
 Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
@@
 }
-	\label{tab:gcnn-eval-mean}
+	\label{tab:trip-net-size-compare}
 \end{table}
 
-\section{Evaluation}
-
+\section{Quantitative Evaluation}
+We evaluated our models on synthetic dataset with resolution $ 128\times 128 $. 
 Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation.
@@
 	\begin{tabular}{l l | l | l l l | l l l l }
+		\toprule
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & & & & 9.82 \\ 
+		\midrule
+		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 &\textbf{ 9.77 }& 9.80 \\ 
 		\hline
-		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & & & & 7.32\\ 
+		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & \textbf{7.30} & 7.62\\ 
 		\hline
-		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & & & & 7.35 \\
+		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 &\textbf{ 7.79} \\
 		\hline
-		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & & & & 9.15 \\
+		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 &\textbf{ 9.39} \\
 		\hline
-		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & & & & 12.13\\
+		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 &\textbf{ 12.60}\\
+		\bottomrule
 	\end{tabular}
@@
 	\begin{tabular}{l l | l | l l l | l l l l }
+		\toprule
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & & & & 7.62 \\ 
+		\midrule
+		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 &\textbf{ 7.50} \\ 
 		\hline
-		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & & & & 4.01 \\ 
+		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & \textbf{3.65 }& 4.47 \\ 
 		\hline
-		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & & & & 5.06 \\
+		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 &\textbf{ 5.52} \\
 		\hline
-		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & & & & 5.81\\
+		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & \textbf{6.04 }\\
 		\hline
-		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& & & & 6.76\\
+		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 &\textbf{ 7.03 }& 7.25\\
+		\bottomrule
 	\end{tabular}
@@
 	\begin{tabular}{l l | l | l l l |l l l l }
+		\toprule
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & & & & 0.31\\ 
+		\midrule
+		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 &\textbf{ 0.33 }& 0.32\\ 
 		\hline
-		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & & & & 0.59 \\ 
+		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & \textbf{0.63 }& 0.55 \\ 
 		\hline
-		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & & & & 0.50\\
+		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 &\textbf{ 0.46}\\
 		\hline
-		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & & & & 0.45\\
+		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & \textbf{0.43}\\
 		\hline
-		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & & & & 0.41\\
+		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & \textbf{0.40 }& 0.37\\
+		\bottomrule
 	\end{tabular}
@@
 	\begin{tabular}{l l | l | l l l | l l l l }
+		\toprule
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 & & & & 0.69\\ 
+		\midrule
+		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 &\textbf{ 0.69 }& \textbf{0.69}\\ 
 		\hline
-		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & & & & 0.83 \\ 
+		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & \textbf{0.83 }&\textbf{ 0.83 }\\ 
 		\hline
-		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & & & & 0.82\\
+		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & \textbf{0.81}\\
 		\hline
-		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 & & & & 0.75\\
+		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 &\textbf{ 0.75}\\
 		\hline
-		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & & & & 0.66\\
+		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & \textbf{0.65}\\
+		\bottomrule
 	\end{tabular}
@@
 	\begin{tabular}{l l | l | l l l | l l l l }
+		\toprule
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & & & & 0.92\\ 
+		\midrule
+		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 &\textbf{ 0.92} &\textbf{ 0.92}\\ 
 		\hline
-		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & & & & 0.94\\ 
+		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & \textbf{0.94}\\ 
 		\hline
-		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & & & & 0.95\\
+		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & \textbf{0.95}\\
 		\hline
-		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & & & & 0.91\\
+		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 &\textbf{ 0.91} &\textbf{ 0.91}\\
 		\hline
-		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & & & & 0.84\\
+		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & \textbf{0.83} &\textbf{ 0.83}\\
+		\bottomrule
 	\end{tabular}
@@
 	\begin{tabular}{l l | l | l l l | l l l l }
+		\toprule
 		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & & & & 0.97 \\ 
+		\midrule
+		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 &\textbf{ 0.97 }&\textbf{ 0.97} \\ 
 		\hline
-		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & & & & 0.96 \\ 
+		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & \textbf{0.96} &\textbf{ 0.96} &\textbf{ 0.96 }\\ 
 		\hline
-		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & & & & 0.98 \\
+		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & \textbf{0.98} \\
 		\hline
-		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & & & & 0.95 \\
+		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & \textbf{0.95 }\\
 		\hline
-		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & & & & 0.90\\
+		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & \textbf{0.89} & \textbf{0.89}\\
+		\bottomrule
 	\end{tabular}
@@
 
+%% svd evaluation
+\section{Visualization evaluation on SVD}
+
+The SVD approach can predict the normal map in a good way when the given point cloud is dense.
+As shown in Figure \ref{fig:svd-normal}.
+It can successfully predict the smooth surface of the dragon object, especially the flakes and the tails of the dragon.
+
+However, it failed in the areas such as hindleg, horn and the mouth, which consists mainly by sharp edges.
+This is because the neighbors points in these area do not hold the assumption of coplanarity well, the normals of these neighbors can be very different.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
+	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
+	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}
+	\decoRule
+	\label{fig:svd-normal}
+	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5 \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
+\end{figure}
+The neighbor based method is depended on a well-chosen parameter $ k $.
+Figure \ref{fig:svd-k-eval} shows the evaluation on different $ k $ values.
+When $ k=1 $, the average error of the whole image is the lowest one, most of the normals are close to the ground-truth but the outline edges, which are the areas that surface normal changed extremely sever.
+For the case $ k=2 $, the sharp edges are more smooth and cause more error, like the eyes area of the dragon.
+Compare to the first case, the outline edge error goes better.
+Most of the edge errors are reduced when $ k=2 $, since more neighbor points join the evaluation and it reduces the effect of outliers.
+However, for the area of horn outline, hindleg outline, the error goes worse.
+In this case, most of the neighbors of these points are outliers and thus failed this approach.
+$ k=3 $ and $ k=4 $ further increase the angle errors based on $ k=2 $.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
+	\decoRule
+	\label{fig:svd-k-eval}
+	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
+\end{figure}
+
+The performance of neighbor based method is good enough for a well chosen $ k $.
+However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
+	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
+	\decoRule
+	\label{fig:svd-noise}
+	\caption{Evaluation of neighbor based method on a noised dragon model}
+\end{figure}
+
+\newpage 
 \section{Visualization evaluation on GCNN model}
@@
 	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
+		\node[text width=0.1\textwidth] at (11,-1) {90};
 		\node[inner sep=0pt] (input) at (8,-1)
@@
 	\end{tikzpicture}
-
+	\decoRule
 	\caption{Normal inference based on GCNN. Test image has resolution $ 128\times128 $}
@@
 %% GCNN zoom in eval
-\begin{figure}[H]
+\begin{figure}[th]
 	\centering
@@
 
+	\decoRule
 	\caption{Zoom in of some regions of Dragon object.
@@
 
+	\decoRule
 	\caption{Comparison of GCNN model with no skip connection version(NOC) and standard convolution layer only version (CNN). The second row is the corresponding mean average degree error.}
@@
 
+%% gcnn-Visual-more
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_point_cloud_noise.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
+		\caption{Error}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-CNN.png}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
+	\label{fig:gcnn-eval-more}
+\end{figure}
+
 \newpage
-\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }
+\section{Visualized evaluation on Trip-Net models }
 
 For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}.
+The Trip-Net uses illuminated information align with the geometry information achieves a sharper and more accurate result compare to the GCNN model.
 The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
@@
 	\end{tikzpicture}
-
+	\decoRule
 	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
@@
 
-\section{More Comparison}
-Figure \ref{fig:final-eval} gives more visualization on model SVD, GCNN and Trip-Net. Figure \ref{fig:final-eval-zoom-in} is the corresponding zoom-in visualization.
-\newpage
-%% Final-Visual
-\begin{figure}
+%% F1-F4 eval
+
+\begin{figure}[H]
 	\centering
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f1.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f2.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f3.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f4.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f1.png}
+		\caption{F1}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f2.png}
+		\caption{F2}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f3.png}
+		\caption{F3}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f4.png}
+		\caption{F4}
+	\end{subfigure}
+
+	\decoRule
+	\caption{Comparison between different fusion times for Trip-Net. The first row is surface normal, the second row is the corresponding errors. The number in ``F$ x $" represents the fusion times. }
+	\label{fig:tripnet-eval-synthetic-zoom-in}
+\end{figure}
+
+%% trip-net-Visual-more
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_img.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_input.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
-		\caption{TripNet}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
-	\label{fig:final-eval}
-\end{figure}
-
-%% Final-Visual-Zoom-In
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_img.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_SVD.png}
-	\end{subfigure}
-
 	\begin{subfigure}[b]{0.24\linewidth}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_img.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_point_cloud_noise.png}
+		\caption{Input}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
+		\caption{GT}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
+		\caption{GCNN}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
+		\caption{Error}
 	\end{subfigure}
 
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_input.png}
+	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
+	\label{fig:gcnn-eval-more}
+\end{figure}
+
+\section{Trining on higher resolution}
+We also prepared the dataset with resolution $ 512\times 512 $ for model evaluation.
+Higher resolution gives more information about the surface feature using the same model compare to lower resolution.
+The benefit is, if we extract a fixed sized patch from the normal map, say $ 32 \times 32 $, it might correspond a hindleg area of the dragon object in $ 128\times 128 $ resolution but maybe only a toe in $ 512\times 512 $ resolution.
+Therefore if we still use the same kernel size in the network for the same dataset, (like we did with $ 3\times 3 $) the higher the resolution it has, the less area it will cover.
+Thus the surface will more smooth and easy to calculate the surface normal.
+This is a good thing.
+Because then we might only need to use these $ 32\times 32 $ points to calculate a toe in $ 512\times512 $ resolution image.
+But in $ 128\times128 $ resolution image, the same area $ 32\times32 $ might corresponding to entire  hindleg of the dragon object.
+In another word, we can also say that the higher resolution ``smooth" the object surface.
+Thus the higher resolution helps the model to calculate a more accurate normal map.
+
+%% high resolution trip-net visualization
+\begin{figure}[th]
+	\centering
+	\begin{subfigure}[b]{0.48\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_normal_Trip-Net-512.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.48\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_point_cloud_noise.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_11_error_Trip-Net-512.png}
+		\caption{Error}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
+	\label{fig:trip-eval-high-resolution}
+\end{figure}
+
+Since our model is fully convolution network, the architecture keeps exactly same on the high resolution dataset.
+We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution.
+The training on high resolution network takes longer time but achieves a lower angle error.
+
+%% 5 degree metric
+\begin{table}
+	\centering
+	\begin{tabular}{l | l l l }
+		\toprule
+		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
+		\midrule
+		Mean  					& 8.88 & 5.82 & 5.33 \\ 
+		\hline
+		Median					& 3.66 & 3.98 & 3.67 \\ 
+		\hline
+		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
+		\hline
+		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
+		\hline
+		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
+		\hline
+		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
+	\label{tab:high_resolution_eval}
+\end{table}
+
+A quantitative evaluation is shown in table \ref{tab:high_resolution_eval}.
+It follows the same performance rank compare to lower resolution, which is GCNN better than SVD approach and Trip-Net slightly better than GCNN.
+The accuracy is 99 \% in the $ 30^\circ $ metric for Trip-Net and $ 5^\circ $ mean error.
+A qualitative evaluation is shown in figure \ref{fig:trip-eval-high-resolution}, this is a figure object with both smooth area (the belly and arm) and highly detailed area with sharp surface (the uneven surface of stone table).
+Our models gives an average degree area at $ 5^\circ $.
+A comparison with other models is shown in figure \ref{fig:trip-eval-compare}.
+
+Another remarkable result is the SVD approach, which also gives a good result ($ 8.88^\circ $ in mean degree metric).
+Like we discussed, the surface are relative more smooth if we keep the same window size for normal inference.
+In the high resolution scenes, although the percentage of missing pixels in a fixed windows are remain the same compare to small resolution scenes, but the remain valid pixels are mainly on a relatively flat plane thus they are good enough for an accurate normal inference.
+Consequently, we can see from the error map in Figure \ref{fig:high_resolution_eval}, the sharp edges of the dragon, like the horns and the hindlegs, the SVD approach still has high errors.
+
+%& trip-net evaluation with other models
+
+\begin{figure}[th]
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_img.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
-		\caption{Trip-Net}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
+		\caption{SVD}
 	\end{subfigure}
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_SVD.png}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\decoRule
+	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
+	\label{fig:trip-eval-compare}
+\end{figure}
+
+\section{Training on Real-Dataset}
+We also applied our model on a dataset that captured by a light scanner in our laboratory in order to see the applicability of our approaches.
+For the geometry information based approach, we directly use the GCNN model that trained on synthetic dataset, since it only require the depth map as input, the scenarios of two dataset are the same.
+For the illuminated calibrated RGB-D image based approach, the model has to be refined based on the real-dataset, since the light intensity and position, camera matrix are different.
+We refined the Trip-Net based on a pre-trained GCNN model with the same settings in previous experiments, and observe the results.
+
+\begin{figure}[th]
+	\centering
+	\begin{subfigure}[b]{0.48\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_normal_An2-real-resume-616.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.48\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_point_cloud_noise.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_error_An2-real-resume.png}
+		\caption{Error}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Normal inference based on Trip-Net. Test image has resolution $ 512\times512 $}
+	\label{fig:trip-eval-real}
+\end{figure}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l | l l l }
+		\toprule
+		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
+		\midrule
+		Mean  					& 8.20 & 8.74 & \textbf{8.09}\\ 
+		\hline
+		Median					& \textbf{4.87} & 5.70 & 5.00 \\ 
+		\hline
+		$ 5^\circ $ 			& \textbf{0.51} & 0.44 & 0.50 \\
+		\hline
+		$ 11.5^\circ $ 			& 0.79 & 0.79 & \textbf{0.81} \\
+		\hline
+		$ 22.5^\circ $ 			& 0.93 & 0.93 & \textbf{0.94} \\
+		\hline
+		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes in real dataset.}	
+	\label{tab:high_resolution_eval}
+\end{table}
+
+Since in the real-dataset, we don't have a ground-truth for evaluation.
+But if we see directly from the visualization in figure \ref{fig:trip-eval-real}, we can see that Trip-Net approach has good ability to  ``mend" the missing pixels in the scenes and also gives a sharp result.
+The folds on the gowns are recognizable and even countable.
+\ref{fig:real_eval_compare} compares the Trip-Net with other approaches.
+
+But we also noted that the big holes in the base stage remains in the depth maps.
+These big holes corresponds to the shinny and dark texture area, which common exists in the depth map captured by the scanners.
+Since these big holes are related with only special feature areas and also has irregular shapes, we didn't simulate this type of noise in the synthetic dataset but only with a random binary mask.
+Thus our models failed to mend missing big holes in the estimated normal map.
+This can be a further direction of this topic, that find a way to generate high similar depth map noise to get a more robust training dataset.
+
+%% real eval comparison
+\begin{figure}[th]
+	\centering
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/00008.image0.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_SVD.png}
 		\caption{SVD}
 	\end{subfigure}	
-
-	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
-	\label{fig:final-eval-zoom-in}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_NNNN-512.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_An2-real-resume.png}
+		\caption{Trip-Net}
+	\end{subfigure}	
+	\decoRule
+	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ real dataset. The first row is surface normal, the second row is the corresponding errors. }
+	\label{fig:real_eval_compare}
 \end{figure}

### 2022-08-03 paper/akweury/document.tex
update eval
update paper

--- 2022-08-02 paper/akweury/document.tex
@@
 \usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
+
+\usepackage{amssymb}
+\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles \left( APA)
+
+\addbibresource{example.bib} % The filename of the bibliography
+
+\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
 \usepackage{import}
+\usepackage{float}
 \usepackage{tikz}
 \usepackage{tikz-network}
-\usetikzlibrary{calc,patterns,angles,quotes}
 \usepackage{breqn}
 \usepackage{bm}
-\usepackage{float}
 \usepackage{graphicx}
@@
 \usepackage{multirow}
-\usepackage{graphicx}
+\usepackage{pdfpages}
 \usepackage{rotating}
-\usepackage{booktabs}
+\usetikzlibrary{fit}
+\usetikzlibrary{calc,patterns,angles,quotes}
+\usetikzlibrary {arrows.meta,graphs,shapes.misc}
+\usetikzlibrary {positioning}
+
 \usetikzlibrary{fit}
@@
 
-\section{Training Details}
-
-The models are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
-Each scene has a depth map with dimension $ 128\times 128 $ in height and width, an image with dimension $ 128\times 128 \times 1 $.
-The depth map is converted to 3D vertex map as introduced in Chapter \ref{ch:04}.
-The light map is calculated based on vertex map and the known light position.
-We create a tensor in PyTorch that includes vertex map, image and the light direction for each scene and considered it as one training case.
-Thus 3000 scenes has corresponding 3000 training cases.
-Each scene has a corresponding ground-truth normal map for loss calculation and the evaluation.
-
-\begin{figure}[H]
+\begin{figure}[th]
 	\centering
 
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.image0.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.normal0.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
-		\caption{Depth Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
-		\caption{Add noise}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
-		\caption{Image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
-		\caption{Normal}
-	\end{subfigure}
-
-	\caption{Some of the test scenes during the training. From top to bottom, baoshanlu, Washington, Garfield, Dragon, Bus}
-	\label{fig:test-scene}
+	\begin{tikzpicture} 
+		% reference lines
+		\coordinate (light) at (-1,3);
+		\coordinate (p) at (2,0);
+		\coordinate (normal) at (2,3);
+		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
+		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
+		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
+		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
+		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
+		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
+		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
+	\end{tikzpicture}
+	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
+	\label{fig:lambertian-surface}
 \end{figure}
 
-The training processes are evaluated in every epochs with 29 evaluation scenes that models never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
-Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
-Note that the position of objects are not placed always naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
-
-For the training parameters, we set the training pipeline with batch size $ 8 $, we found that a higher batch size will reduce the final performance.
-Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
-The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.
-It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
-We terminate the training when the evaluation on the test dataset converged.
-
-\section{GCNN model based on Geometry Information}
-The GCNN model is the base model of the whole thesis.
-The architecture is described in \ref{sec:gcnn}.
-We use a single GCNN to estimate the surface normal based on geometry information.
-It uses vertex map as input to estimate the corresponding tangent surface normal map.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{./Figures/gcnn_training_loss.png}
-
-	\includegraphics[width=\textwidth]{./Figures/gcnn_eval_loss.png}
-	\caption{The training history of GCNN model.
-The line chart records the training BerHu loss of the model GCNN, NOC and CNN.
-The left shows the training loss history whereas the right one shows the evaluation loss history.}
-	\label{fig:gcnn-training-history}
-\end{figure}
-
-In order to verify the applicability of the skip connection and the gated convolution layers, we trained two extra models as a comparison.
-The first model, we replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same, and give it a name ``CNN".
-It is used to verify the performance the gated convolution layers.
-As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
-Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
-Another model called ``NOC" is designed to verify the skip connection, which simply removes the skip connections in the network but keeps other settings same.
-Is is designed to show to which content will skip connection help the model performance.
-We use Reversed Huber Loss as loss function during the training, since we found it gives a better final error compare to L2 loss.
-The model is evaluated after every epoch training and calculate the angle error on the test dataset.
-The training history is shown in Figure \ref{fig:gcnn-training-history}.
-
-%% TODO
-waiting for the experiment, then describe the chart...
-
-\begin{table}[H]
-
-	\centering
-	\begin{tabular}{l l l l l l }
-		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB}\\
-		\hline
-		CNN 					& 17 & 32 & 0 & 0 & 25.5 \\
-		\hline
-		NOC 					& 32 & 32 & 0 & 0 & 30.6 \\
-		\hline
-		GCNN 					& 32 & 32 & 0 & 0 & 45.8 \\
-	\end{tabular}
-	\caption{GCNN Model information.
-Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
-Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
-}
-	\label{tab:gcnn-eval-mean}
-\end{table}
-
-\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
-The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train.
-It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
-When we train this model, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
- Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
-A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
-We evaluate the fusion times from 1 to 4.
-For the learning rate.
-we set $ 1e-3 $.
-It goes well with GCNN model but lead to loss explosion in Trip-Net.
-Thus we set a learning rate schedule with an extra decay step at epoch 8.
-The decay factor is $ 0.5$.
-The batch size is chosen as 8.
-
-Figure \ref{fig:trip-net-training-history} shows the training history of Trip-Net models on BerHu Loss. As shown in the loss figure, all of the four models has a reasonable learning rate. 
-From the chart we can see that, trip-Net with four times fusion converges obviously faster than fewer fusion times model.
-However, model F3 with 3 times fusion converge slower than F4 but in the end it achieves a similar evaluation loss with F4.
-The F1 and F2 models are relatively weaker than the other two models.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{./Figures/trip_net_training_loss.png}
-	\includegraphics[width=\textwidth]{./Figures/trip_net_eval_loss.png}
-	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
-	\label{fig:trip-net-training-history}
-\end{figure}
-
-However, the sacrifice of accuracy gives a relatively lighter model.
-Since we remove the fusions between different pipes, the corresponding upsampling layers in the image and light pipes can also be removed.
-The model can be trained faster and the size is reduced as well.
-Table \ref{tab:trip-net-size-compare} gives a comparison of the size and training time among different models.
-
-\begin{table}[H]
-
-	\centering
-	\begin{tabular}{l l l l l l l }
-		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB} & \tabhead{Time /h}\\
-		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106  &  9.82\\ 
-		\hline
-		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 &  7.35\\ 
-		\hline
-		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 &  7.35\\
-		\hline
-		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
-	\end{tabular}
-	\caption{Trip-Net Model information.
-Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
-Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
-}
-	\label{tab:trip-net-size-compare}
-\end{table}
-
-\section{Quantitative Evaluation}
-
-Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation.
-Note that the input vertex map is only semi-dense.
-One of the benefit of GCNN architecture is the robust to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
-
-\paragraph{Average Angle Error Metric}
-The metric calculate the average angle error for each point between the inferred normal and ground-truth normal. 
-\paragraph{Median Angle Error Metric}
-The metric calculate the median angle error of all the point in the normal map.
-\paragraph{5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 5 degrees comparing to ground-truth.
-\paragraph{11.5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 11.5 degrees comparing to ground-truth.
-\paragraph{22.5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 22.5 degrees comparing to ground-truth.
-\paragraph{30 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 30 degrees comparing to ground-truth.
-
-We evaluate the trained models on ``synthetic-50-5".
-5 objects are considered in the test dataset.
-They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $.
-Each object has 20 scenes with total 100 scenes for 5 objects.
-The test objects do not exist in the training dataset.
-We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified.
-$ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $.
-$ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.
-
-Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis.
-When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
-When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
-
-%% mean metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & & 9.82 \\ 
-		\hline
-		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & & 7.32\\ 
-		\hline
-		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & & 7.35 \\
-		\hline
-		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & & 9.15 \\
-		\hline
-		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & & 12.13\\
-	\end{tabular}
-	\caption{Average Angle Error of the evaluation dataset.}	
-	\label{tab:eval-mean}
-\end{table}
-
-%% median metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & & 7.62 \\ 
-		\hline
-		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & & 4.01 \\ 
-		\hline
-		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & & 5.06 \\
-		\hline
-		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & & 5.81\\
-		\hline
-		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & & 6.76\\
-	\end{tabular}
-	\caption{Median Angle Error of the evaluation dataset.}	
-	\label{tab:eval-median}
-\end{table}
-
-%% 5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l |l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & & 0.31\\ 
-		\hline
-		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & & 0.59 \\ 
-		\hline
-		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & & 0.50\\
-		\hline
-		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & & 0.45\\
-		\hline
-		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & & 0.41\\
-	\end{tabular}
-	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
-	\label{tab:eval-5d}
-\end{table}
-
-%% 11.5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & & 0.69\\ 
-		\hline
-		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & & 0.83 \\ 
-		\hline
-		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & & 0.82\\
-		\hline
-		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & & 0.75\\
-		\hline
-		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & & 0.66\\
-	\end{tabular}
-	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
-	\label{tab:eval-11d}
-\end{table}
-
-%% 22.5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & & 0.92\\ 
-		\hline
-		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & & 0.94\\ 
-		\hline
-		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & & 0.95\\
-		\hline
-		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & & 0.91\\
-		\hline
-		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & & 0.84\\
-	\end{tabular}
-	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
-	\label{tab:eval-22d}
-\end{table}
-
-%% 30 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
-		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & & 0.97 \\ 
-		\hline
-		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & & 0.96 \\ 
-		\hline
-		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & & 0.98 \\
-		\hline
-		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & & 0.95 \\
-		\hline
-		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & & 0.90\\
-	\end{tabular}
-	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
-	\label{tab:eval-30d}
-\end{table}
-
-\section{Visualization evaluation on GCNN model}
-A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
-As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object.
-The image has an overall good performance on the whole object.
-A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
-In the same case, NOC model as shown in Figure  \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
-CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
-Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).
-
-%% GCNN-eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
-		\caption{Image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-		\caption{Predict}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-		\caption{Error}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Normal inference based on GCNN. Test image has resolution $ 128\times128 $}
-	\label{fig:gcnn-eval}
-\end{figure}
-
-%% GCNN zoom in eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_normal.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_error.png}
-		\caption{Scale}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_error.png}
-		\caption{Head}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_error.png}
-		\caption{Foreleg}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_error.png}
-		\caption{Hindleg}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_error.png}
-		\caption{Tail}
-	\end{subfigure}
-
-	\caption{Zoom in of some regions of Dragon object.
-The first row is surface normal, the second row is the corresponding errors.
-Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
-	\label{fig:gcnn-eval-synthetic-zoom-in}
-\end{figure}
-
-%% compare to other models
-
-%% GCNN zoom in eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
-		\caption{NOC}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
-		\caption{CNN}
-	\end{subfigure}
-
-	\caption{Comparison of GCNN model with no skip connection version(NOC) and standard convolution layer only version (CNN). The second row is the corresponding mean average degree error.}
-	\label{fig:gcnn-eval-multi-model}
-\end{figure}
-
-\newpage
-\section{Visualized evaluation on Trip-Net models }
-
-For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
-The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
-In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same.
-We also use the same input as we did in GCNN evaluation.
-The error of Trip-Net is 6 degree whereas the GCNN is 9.
-
-As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and close to the ground-truth.
-The head region gives a sharper edge prediction.
-All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
-
-%% TripNet-eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
-		\caption{Image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
-		\caption{Predict}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
-		\caption{Error}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
-	\label{fig:trip-eval}
-\end{figure}
-
-%% tripNet zoom in eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_normal.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_error.png}
-		\caption{Scale}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_error.png}
-		\caption{Head}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
-		\caption{Foreleg}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_error.png}
-		\caption{Hindleg}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_error.png}
-		\caption{Tail}
-	\end{subfigure}
-
-	\caption{Zoom in of some regions of Dragon object.
-The first row is surface normal, the second row is the corresponding errors.
-Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
-	\label{fig:tripnet-eval-synthetic-zoom-in}
-\end{figure}
-
-%% F1-F4 eval
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f1.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f2.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f3.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f4.png}
-	\end{subfigure}
-
-		\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f1.png}
-		\caption{F1}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f2.png}
-		\caption{F2}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f3.png}
-		\caption{F3}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f4.png}
-		\caption{F4}
-	\end{subfigure}
-
-	\caption{Comparison between different fusion times for Trip-Net. The first row is surface normal, the second row is the corresponding errors. The number in ``F$ x $" represents the fusion times. }
-	\label{fig:tripnet-eval-synthetic-zoom-in}
-\end{figure}
-
-\section{More Comparison}
-Figure \ref{fig:final-eval} gives more visualization on model SVD, GCNN and Trip-Net. Figure \ref{fig:final-eval-zoom-in} is the corresponding zoom-in visualization.
-\newpage
-%% Final-Visual
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_img.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_img.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
-		\caption{TripNet}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (10,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-
-	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
-	\label{fig:final-eval}
-\end{figure}
-
-%% Final-Visual-Zoom-In
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_img.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_img.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_SVD.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-
-	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
-	\label{fig:final-eval-zoom-in}
-\end{figure}
-
-\section{Trining on higher resolution}
-We also prepared the dataset with resolution $ 512\times 512 $ for model evaluation.
-Higher resolution gives more information about the surface feature using the same model compare to lower resolution.
-The benefit is, if we extract a fixed sized patch from the normal map, say $ 32 \times 32 $, it might correspond a hindleg area of the dragon object in $ 128\times 128 $ resolution but maybe only a toe in $ 512\times 512 $ resolution.
-Therefore if we still use the same kernel size in the network for the same dataset, the higher the resolution it has, the less area it will cover.
-This is a good thing.
-Because then we only need to use these $ 32\times 32 $ points to calculate a toe in $ 512\times512 $ resolution image.
-But in $ 128\times128 $ resolution image, we use the same area $ 32\times32 $ to calculate the whole hindleg.
-In another word, we can also say that the higher resolution ``smooth" the object surface.
-Thus the higher resolution helps the model to calculate a more accurate normal map.
-
-We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution.
-Figure \ref{fig:high_resolution_eval} gives a comparison among SVD, GCNN and Trip-Net models.
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-
-	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
-	\label{fig:high_resolution_eval}
-\end{figure}
-%% 5 degree metric
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l l l }
-		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
-		Mean  					& 8.88 & 5.82 & 5.33 \\ 
-		\hline
-		Median					& 3.66 & 3.98 & 3.67 \\ 
-		\hline
-		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
-		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
-		\hline
-		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
-		\hline
-		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
-	\end{tabular}
-	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
-	\label{tab:high_resolution_eval}
-\end{table}
-
-\section{Training on Real-Dataset}
-
-\begin{figure}[H]
-	\centering
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
-	\caption{SVD}
-\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-
-		\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_img.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_NNNN-512.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_Trip-Net-512.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-
-	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
-	\label{fig:high_resolution_eval}
-\end{figure}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{l l l l }
-		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
-		Mean  					& 8.20 & 8.90 & 8.30\\ 
-		\hline
-		Median					& 4.87 & 5.82 & 5.14 \\ 
-		\hline
-		$ 5^\circ $ 			& 0.51 & 0.43 & 0.49 \\
-		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.80 \\
-		\hline
-		$ 22.5^\circ $ 			& 0.93 & 0.93 & 0.93 \\
-		\hline
-		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96\\
-	\end{tabular}
-	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
-	\label{tab:high_resolution_eval}
-\end{table}
-
 \end{document}

### 2022-08-05 paper/Chapters/Chapter05.tex
update paper

@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
 		\caption{Image}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_groundtruth.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_GCNN-GCNN.png}
 		\caption{Predict}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN.png}
 		\caption{Error}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_normal.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_error.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_22_-8_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_2_22_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_32_12_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_42_-28_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_12_-48_normal.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_22_-8_error.png}
 		\caption{Scale}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_error.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_2_22_error.png}
 		\caption{Head}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_error.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_32_12_error.png}
 		\caption{Foreleg}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_error.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_42_-28_error.png}
 		\caption{Hindleg}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_error.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_12_-48_error.png}
 		\caption{Tail}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_GCNN-NOC.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_GCNN-CNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-NOC.png}
 		\caption{NOC}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-CNN.png}
 		\caption{CNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_point_cloud_noise.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
 		\caption{Input}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_groundtruth.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_GCNN-GCNN.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_GCNN-GCNN.png}
 		\caption{Error}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_GCNN-CNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_GCNN-CNN.png}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_an2-8-1000.png}
 		\caption{Predict}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_an2-8-1000.png}
 		\caption{Error}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_normal.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_error.png}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_22_-8_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_2_22_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_32_12_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_42_-28_normal.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_12_-48_normal.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_22_-8_error.png}
 		\caption{Scale}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_error.png}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_2_22_error.png}
 		\caption{Head}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_32_12_error.png}
 		\caption{Foreleg}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_error.png}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_42_-28_error.png}
 		\caption{Hindleg}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_error.png}
+		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_12_-48_error.png}
 		\caption{Tail}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f1.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f2.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f3.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f4.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_img.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_f1.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_f2.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_f3.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_f4.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.18\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
 		\caption{GT}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f1.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f1.png}
 		\caption{F1}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f2.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f2.png}
 		\caption{F2}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f3.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f3.png}
 		\caption{F3}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f4.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f4.png}
 		\caption{F4}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_point_cloud_noise.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
 		\caption{Input}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_normal_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_an2-8-1000.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_9_error_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_an2-8-1000.png}
 		\caption{Error}
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_9_error_an2-8-1000.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_an2-8-1000.png}
 	\end{subfigure}

### 2022-08-05 paper/akweury/document.tex
update paper

@@
 \usepackage{pdfpages}
+\usepackage{pgfplots}
 \usepackage{rotating}
@@
 \begin{tikzpicture}
-		% reference lines
-		\coordinate (light) at (-1,3);
-		\coordinate (p) at (2,0);
-		\coordinate (normal) at (2,3);
-		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
-		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
-		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
-		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
-		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
-		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
-		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
+	\pgfplotsset{ticks=none}
+	\begin{axis} [axis lines=center]
+		\addplot [domain=0:1, smooth, thick, width=5mm, color=red] { x };
+		\addplot [domain=1:2, smooth, width=5mm] { x };
+		\addplot [domain=-2:-1, smooth, width=3mm] { -x };
+		\addplot [domain=-1:0, smooth, thick, width=3mm, color=red] { -x };
+		\addplot [domain=-2:-1, smooth, thick, color=red] { (x^2+1^2)/(2*1) };
+		\addplot [domain=1:2, smooth, thick, color=red] { (x^2+1^2)/(2*1) };
+	\end{axis}
 \end{tikzpicture}
-	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
-	\label{fig:lambertian-surface}
+	\caption{The shape of Berhu Loss (show in red line). }
+	\label{fig:berhu-loss-shape}
 \end{figure}
-
 \end{document}

### 2022-08-05 eval_single_obj.py

@@ -92,8 +92,8 @@ if __name__ == '__main__':
     for folder_name in ["baoshanlu", "bus", "dragon", "garfield", "washington"]:
         if args.machine == "local":
             # test_folder = config.real_data / "test"
-            # test_folder = config.synthetic_data_noise_local / "synthetic128" / "seperate" / folder_name
-            test_folder = config.dataset / "data_synthetic_noise" / "synthetic128" / "tensor"
+            test_folder = config.synthetic_data_noise_local / "synthetic128" / "seperate" / folder_name
+            # test_folder = config.dataset / "data_synthetic_noise" / "synthetic128" / "tensor"
             # test_folder = config.synthetic_data_noise_local / "synthetic512" / "test"
             models = {
                 # "SVD": None,
@@ -103,12 +103,12 @@ if __name__ == '__main__':
 
                 # "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-03_00_01_56" / "checkpoint-150.pth.tar",
                 # "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-03_00_01_07" / "checkpoint-150.pth.tar",
-                "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-01_22_32_35" / "checkpoint-1117.pth.tar",
-                "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-01_22_31_37" / "checkpoint-929.pth.tar",
-                #
-                # "CNN": config.ws_path / "nnnn" / "nnnn_cnn_2022-08-03_00_15_34" / "checkpoint-200.pth.tar",
-                # "NOC": config.ws_path / "nnnn" / "nnnn_gcnn_noc_2022-08-03_00_07_32" / "checkpoint-200.pth.tar",
-                # "GCNN": config.ws_path / "nnnn" / "nnnn_gcnn_2022-08-03_00_02_37" / "checkpoint-200.pth.tar",
+                # "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-01_22_32_35" / "checkpoint-1117.pth.tar",
+                # "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-01_22_31_37" / "checkpoint-929.pth.tar",
+
[…]

### 2022-08-05 help_funs/visual_loss_from_multi_model.py

@@ -7,14 +7,16 @@ from help_funs import chart
 
 models = {
 
-    # "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-03_00_01_56" / "checkpoint-150.pth.tar",
-    # "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-03_00_01_07" / "checkpoint-150.pth.tar",
-    # "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-02_23_59_25" / "checkpoint-150.pth.tar",
-    # "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-02_23_58_31" / "checkpoint-100.pth.tar",
+    # "Trip-Net-F1F": config.ws_path / "an2" / "an2_gnet-f1f_2022-08-03_10_01_05" / "checkpoint-450.pth.tar",
+    # "Trip-Net-F2F": config.ws_path / "an2" / "an2_gnet-f2f_2022-08-03_10_04_02" / "checkpoint-550.pth.tar",
+    # "Trip-Net-F3F": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-02_23_59_25" / "checkpoint-650.pth.tar",
+    "Trip-Net-F3F-2": config.ws_path / "an2" / "an2_gnet-f3f_2022-08-01_22_32_35" / "checkpoint-1327.pth.tar",
+    # "Trip-Net": config.ws_path / "an2" / "an2_gnet-f4_2022-08-02_23_58_31" / "checkpoint-300.pth.tar",
+    "Trip-Net-2": config.ws_path / "an2" / "an2_gnet-f4_2022-08-01_22_31_37" / "checkpoint-1116.pth.tar",
     #
-    # "CNN": config.ws_path / "nnnn" / "nnnn_cnn_2022-08-03_00_15_34" / "checkpoint-200.pth.tar",
-    # "NOC": config.ws_path / "nnnn" / "nnnn_gcnn_noc_2022-08-03_00_07_32" / "checkpoint-200.pth.tar",
-    "GCNN": config.ws_path / "nnnn" / "nnnn_gcnn_2022-07-31_10_39_24" / "checkpoint-992.pth.tar",
[…]

### 2022-08-05 workspace/nnnn/eval_feature_maps.py

@@ -20,7 +20,7 @@ datasize = args.datasize
 font_scale = 1
 
 # read data
-test_0 = torch.load(np.array(sorted(glob.glob(str(dataset_path / f"*_0_*"), recursive=True)))[3])
+test_0 = torch.load(np.array(sorted(glob.glob(str(dataset_path / f"*_0_*"), recursive=True)))[7])  # 7
 
 # unpack model
 test_0_tensor = test_0['input_tensor'].unsqueeze(0)
@@ -38,7 +38,7 @@ img_8bit = cv.normalize(np.uint8(img_gt), None, 0, 255, cv.NORM_MINMAX, dtype=cv
 img = cv.merge((img_8bit, img_8bit, img_8bit))
 normal_no_mask_img = None
 FEATURE_MAP_NUM = 128
-CV_COLOR = cv.COLORMAP_RAINBOW
+CV_COLOR = cv.COLORMAP_TURBO
 
 # evaluate CNN models
 for model_idx, (name, model) in enumerate(models.items()):
@@ -141,10 +141,23 @@ for model_idx, (name, model) in enumerate(models.items()):
         feature_map = mu.visual_vertex(feature_map, str(idx))
         feature_map_uconv3.append(cv.applyColorMap(feature_map, CV_COLOR))
 
-    feature_map_list = [
-        # feature_map_dconv1, feature_map_dconv2, feature_map_dconv3, feature_map_dconv4,
-        feature_map_uconv1, feature_map_uconv2, feature_map_uconv3
-    ]
+    from itertools import islice
+
+
+    def convert(lst, var_lst):
+        it = iter(lst)
+        return [list(islice(it, i)) for i in var_lst]
+
+
+    feature_map_list = convert(feature_map_uconv3, [16, 16, 16, 16, 16, 16, 16, 16])
+
+    # feature_map_list = [
+    #     # feature_map_dconv1, feature_map_dconv2, feature_map_dconv3, feature_map_dconv4,
+    #     # feature_map_uconv1,
+    #     # feature_map_uconv2,
+    #     feature_map_uconv3
+    # ]
+
     xout[mask] = 0
     xout[xout > 1] = 1
     xout[xout < -1] = -1

### 2022-08-05 paper/Appendices/AppendixA.tex
update dataset
update paper

@@
 \section{Dataset}
-
-\begin{figure}[!h]
+%% dataset a
+\begin{figure}
 	\centering
@@
 
+	\label{fig:dataset_a}
+\caption{Point clouds in training dataset A }
+\end{figure}
+
+%% dataset b 
+\begin{figure}
+	\centering
 	\begin{subfigure}[b]{0.23\linewidth}
@@
 
-	\label{fig:dataset_a}
-\caption{Point clouds in training dataset A }
-\end{figure}
-\begin{figure}[!h]
-	\centering
 		\begin{subfigure}[b]{0.23\linewidth}
@@
 
+	\label{fig:dataset_b}
+	\caption{Point clouds in training dataset B }
+\end{figure}
+
+%% dataset c 
+\begin{figure}
+	\centering
+
 	\begin{subfigure}[b]{0.23\linewidth}
@@
 
-	\label{fig:dataset_b}
-	\caption{Point clouds in training dataset B}
-\end{figure}
-
-\begin{figure}
-	\centering
 	\begin{subfigure}[b]{0.23\linewidth}
@@
 \end{subfigure}
+
 	\label{fig:dataset_c}
@@
 
-\section{How do I change the colors of links?}
+\section {More Visualization}
 
-The color of links can be changed to your liking using:
+%% gcnn-Visual-more
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
 
-{\small\verb!\hypersetup{urlcolor=red}!}, or
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_GCNN-GCNN.png}
+	\end{subfigure}
 
-{\small\verb!\hypersetup{citecolor=green}!}, or
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
 
-{\small\verb!\hypersetup{allcolor=blue}!}.
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_GCNN-GCNN.png}
+	\end{subfigure}
 
-\noindent If you want to completely hide the links, you can use:
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_GCNN-GCNN.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_GCNN-GCNN.png}
 
-{\small\verb!\hypersetup{allcolors=.}!}, or even better:
+	\end{subfigure}
 
-{\small\verb!\hypersetup{hidelinks}!}.
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GCNN-GCNN.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_GCNN-CNN.png}
+		\caption{Error}
+	\end{subfigure}
 
-\noindent If you want to have obvious links in the PDF but not the printed text, use:
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{GCNN models evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
+	\label{fig:gcnn-eval-more}
+\end{figure}
 
-{\small\verb!\hypersetup{colorlinks=false}!}.
+%% Trip-Net more evaluation
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_an2-8-1000.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_an2-8-1000.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
+
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
+
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_an2-8-1000.png}
+
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_an2-8-1000.png}
+
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_an2-8-1000.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_an2-8-1000.png}
+		\caption{Error}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
+	\label{fig:trip-net-eval-more}
+\end{figure}

### 2022-08-05 paper/Chapters/Chapter05.tex
update paper

@@
 
-\newpage 
 \section{Visualization evaluation on GCNN model}
@@
 CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
-Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).
+Besides, the sharp area like the hindleg and the head area of dragon object, CNN model gives a much brighter error map (which means a higher angle error).
 
@@
 	\decoRule
-	\caption{Normal inference based on GCNN. Test image has resolution $ 128\times128 $}
+	\caption{Normal inference based on GCNN. ($ 128\times128 $)}
 	\label{fig:gcnn-eval}
@@
 	\decoRule
-	\caption{Zoom in of some regions of Dragon object.
-The first row is surface normal, the second row is the corresponding errors.
-Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
+	\caption{Zoom in of some regions of Dragon object (GCNN models). Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
 	\label{fig:gcnn-eval-synthetic-zoom-in}
@@
 	\decoRule
-	\caption{Comparison of GCNN model with no skip connection version(NOC) and standard convolution layer only version (CNN). The second row is the corresponding mean average degree error.}
+	\caption{Comparison of GCNN based models.}
 	\label{fig:gcnn-eval-multi-model}
@@
 
-%% gcnn-Visual-more
-\begin{figure}
+\section{Feature Maps Discussion on GCNN architecture models}
+
+As shown in figure \ref{fig:gcnn-cnn-feature map}, we also visualize the feature maps of the last gated convolution layer in the first up-sampling part for CNN and GCNN models, which corresponding the feature maps with size $ 32\times 32 $ in width and height.
+The input data is also same dragon object that we used for normal visualization.
+For each feature map, we map the minimum value to the left-most color in the color bar and the maximum value to the right-most color in the color bar.
+We want to discuss the the different of the feature maps between CNN, NOC and GCNN models.
+
+In order to see the result clearly, we use one color for the feature map visualization and use the brightness to distinguish the scale of the vales, the white corresponds 1, the black corresponds 0, green color corresponds some value in between.
+
+From the CNN feature maps, we can see that the brightness areas are distributed all around the feature maps.
+For the GCNN feature maps, the brightness areas are usually concentrate only in few pixels.
+If we map the brightness areas to the original image, they correspond to the dense sharp edges areas, which is usually the hardest areas for normal estimation task.
+We suspect that these feature maps are the detail feature maps that extract from sharp edges.
+Based on this assumption, we can say that gated convolution layer describes the detail features in a more accurate way compare to standard convolution layer, since the brightness areas is smaller.
+Most of the GCNN feature maps usually has only one bright pixel with a few set of dim green pixels whereas CNN feature maps has more bright pixels with a lot of dim pixels all around the image.
+This accurate feature extraction provides our GCNN model a better performance on the detail area.
+
+Second, for the GCNN model,  we observed that some feature maps have no  small bright areas but bright areas distributed evenly on the whole object.
+Some of the feature maps has a overall medium value some has a value close to 1.
+Nevertheless, these feature maps are different from the detail feature maps with only few pixels with high values(brightness).
+We suspect that these features maps provides an over-view of the objects for a coarse prediction.
+So that they can cooperate with detail feature maps to sharpen the prediction.
+It also holds for NOC model, since it does not equip with skip connection, most of the feature maps are global feature maps with an evenly bright feature maps, so that the corresponding normal maps predicted by NOC model are more coarse.
+For the CNN model, there also exists global feature maps, however, they are mostly incomplete, either missing the tails or missing the paws.
+Actually, these missing areas can usually be found in the detail feature maps.
+This also explained why the CNN detail feature maps has too much brightness areas, the detail feature maps and global feature maps are mixed together.
+And this unclear feature map extractor leads to the weak performance on normal estimation.
+
+%% feature maps comparison
+\begin{figure}[H]
 	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_GCNN-GCNN.png}
+
+	\begin{subfigure}[b]{\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn.png}
+		\caption{CNN Feature Maps}
 	\end{subfigure}
 
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_GCNN-GCNN.png}
+	\begin{subfigure}[b]{\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc.png}
+		\caption{NOC Feature Maps}
 	\end{subfigure}
 
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_GCNN-GCNN.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
-		\caption{Input}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_GCNN-GCNN.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_GCNN-GCNN.png}
-		\caption{Error}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GCNN-GCNN.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_GCNN-CNN.png}
+	\begin{subfigure}[b]{\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn.png}
+	\caption{GCNN Feature Maps}
 \end{subfigure}
@@
 		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
 		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
@@
 	\decoRule
-	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
-	\label{fig:gcnn-eval-more}
+	\caption{Feature maps of GCNN architecture based models at the first up-sampling gated convolution layer.
+All 128 feature maps are visualized for each model with normalization and filtered background.}
+	\label{fig:gcnn-cnn-feature map}
 \end{figure}
@@
 The Trip-Net uses illuminated information align with the geometry information achieves a sharper and more accurate result compare to the GCNN model.
-The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
-In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same.
-We also use the same input as we did in GCNN evaluation.
-The error of Trip-Net is 6 degree whereas the GCNN is 9.
-
-As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and also close to the ground-truth.
-The head region gives a sharper edge prediction.
-All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
-It seems that the illumination helps the model to learn sharper features in the network.
 
@@
 \end{figure}
+
+The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
+In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same.
+We also use the same input as we did in GCNN evaluation.
+The error of Trip-Net is 6 degree whereas the GCNN is 9.
 
@@
 	\decoRule
-	\caption{Zoom in of some regions of Dragon object.
-The first row is surface normal, the second row is the corresponding errors.
-Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
+	\caption{Zoom in of detail regions ( $ 32\times32 $ ) of Dragon object (Trip-Net model).}
 	\label{fig:tripnet-eval-synthetic-zoom-in}
@@
 
+As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and also close to the ground-truth.
+The head region gives a sharper edge prediction.
+All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
+It seems that the illumination helps the model to learn sharper features in the network.
+
 %% F1-F4 eval
 
-\begin{figure}[H]
+\begin{figure}
 	\centering
@@
 	\decoRule
-	\caption{Comparison between different fusion times for Trip-Net. The first row is surface normal, the second row is the corresponding errors. The number in ``F$ x $" represents the fusion times. }
+	\caption{Comparison between different fusion times for Trip-Net. }
 	\label{fig:tripnet-eval-synthetic-zoom-in}
-\end{figure}
-
-%% trip-net-Visual-more
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
-		\caption{Input}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_an2-8-1000.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_an2-8-1000.png}
-		\caption{Error}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_an2-8-1000.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_an2-8-1000.png}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (11,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-	\decoRule
-	\caption{Evaluation on objects Baoshanlu, Washington statue, Bus(from top to bottom).}
-	\label{fig:gcnn-eval-more}
 \end{figure}
@@
 
+%% 5 degree metric
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l | l l l }
+		\toprule
+		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
+		\midrule
+		Mean  					& 8.88 & 5.82 & 5.33 \\ 
+		\hline
+		Median					& 3.66 & 3.98 & 3.67 \\ 
+		\hline
+		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
+		\hline
+		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
+		\hline
+		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
+		\hline
+		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
+		\bottomrule
+	\end{tabular}
+	\caption{High resolution dataset evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
+	\label{tab:high_resolution_eval}
+\end{table}
+
+Since our model is fully convolution network, the architecture keeps exactly same on the high resolution dataset.
+We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution.
+The training on high resolution network takes longer time but achieves a lower angle error.
+
+\newpage 
 %% high resolution trip-net visualization
@@
 \end{figure}
-
-Since our model is fully convolution network, the architecture keeps exactly same on the high resolution dataset.
-We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution.
-The training on high resolution network takes longer time but achieves a lower angle error.
-
-%% 5 degree metric
-\begin{table}
-	\centering
-	\begin{tabular}{l | l l l }
-		\toprule
-		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
-		\midrule
-		Mean  					& 8.88 & 5.82 & 5.33 \\ 
-		\hline
-		Median					& 3.66 & 3.98 & 3.67 \\ 
-		\hline
-		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
-		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
-		\hline
-		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
-		\hline
-		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
-	\label{tab:high_resolution_eval}
-\end{table}
 
@@
 	\decoRule
-	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
+	\caption{High resolution dataset ($ 512\times 512 $) comparison.}
 	\label{fig:trip-eval-compare}
@@
 
-\begin{figure}[th]
-	\centering
-	\begin{subfigure}[b]{0.48\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_normal_An2-real-resume-616.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.48\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_groundtruth.png}
-		\caption{GT}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_point_cloud_noise.png}
-		\caption{Input}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_img.png}
-		\caption{Image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_error_An2-real-resume.png}
-		\caption{Error}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (11,-1) {90};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
-	\end{tikzpicture}
-	\decoRule
-	\caption{Normal inference based on Trip-Net. Test image has resolution $ 512\times512 $}
-	\label{fig:trip-eval-real}
-\end{figure}
-
-\begin{table}
+\begin{table}[H]
 	\centering
@@
 
+\begin{figure}[th]
+	\centering
+	\begin{subfigure}[b]{0.30\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_normal_An2-real-resume-616.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.30\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_point_cloud_noise.png}
+		\caption{Input}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.20\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_error_An2-real-resume.png}
+		\caption{Error}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Real Dataset ($ 512\times 512 $) evaluation (Trip-Net)}
+	\label{fig:trip-eval-real}
+\end{figure}
+
 Since in the real-dataset, we don't have a ground-truth for evaluation.
@@
 
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
@@
 
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/00008.image0.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_SVD.png}
@@
 	\end{subfigure}	
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_NNNN-512.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
+	\begin{subfigure}[b]{0.2\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_An2-real-resume.png}
@@
 	\decoRule
-	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ real dataset. The first row is surface normal, the second row is the corresponding errors. }
+	\caption{Real dataset ($ 512\times 512 $) comparison.}
 	\label{fig:real_eval_compare}

### 2022-08-05 paper/Chapters/Chapter06.tex
update paper

@@
 %----------------------------------------------------------------------------------------
-Gated convolution neural network...
+In our approaches, two networks have been proposed.
+The first network called GCNN is used for geometry information based approach, which is our baseline method.
+It is especially good for the semi-dense input data which is benefited with gated convolution layer design.
+Using this network we achieved a more accurate normal inference than using standard layers network based on the same architecture.
+We also show the effectiveness of skip connection in the U-Net.
+Our network uses a fully convolution design which enables it takes any resolution images as input.
+
+The second network is called Trip-Net, which is based on the GCNN model.
+It is designed for illumination calibrated RGB-D image based approaches.
+This model utilises GCNN architecture three times in order to handle vertex map, light map and image map separately.
+We have also found that 3 to 4 times fusion times among 3 pipes in our models is the key point for the performance enhancement.
+Based on our experiments, we found that the models trained on illuminated calibrated RGB-D images achieve a  better performance than geometry information only based approach and gives more sharpness in the normal map.
+
+We also explored the performance of our models on a real dataset and compare with traditional method like SVD based approach.
+Especially, our gated convolution layer based model can fill the missing pixels in the real input data and keep an accurate normal estimation, whereas the optimization based approach like SVD is failed to do so.
+
+In our experiments we collected 55 high density point clouds from internet and used them for our dataset generation.
+Specifically, we use a RGB-D camera, an ambient light and one directional light  collect thousands of scenes.
+The scene generation is simulated by game engine Unity.
+Furthermore, we also simulated noise in our synthetic dataset by a uniform distributed drop off to fit our model adopt with semi-dense input data.
+
+However, for the large missing areas, we did not generate a similar noise in the training set, which leads to our model cannot fill the holes in the real data.
+Exploring a sensor-noise mimic algorithm to generate more reality closed data for training work can be a direction of further work.

### 2022-08-05 paper/main.tex
update paper

@@
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
+We proposed a learning based approach for surface normal estimation based on illuminated calibrated RGB-D image. 
+Different with other methods, the approach not only base on geometry information, but also takes the photometric stereo approach into account, which use calibrated illuminated image to further improve the performance.
+The two types of data gives a superior performance on normal inference task.
+One of the key points of our approach is, the proposed method require only one light source for each scene capture instead of multiple light positions, which can be very easy to configure in the practice.
+
+Our model is trained on a  gated convolution neural network called (Trip-Net).
+The gated convolution design is supposed to handle the semi-dense depth map input, which is a common artefact by the depth sensor.
+Furthermore, a dataset based on 55 point clouds called ``synthetic-50-5“ in created for training.
+We trained our model on this synthetic dataset then further applied it to real dataset.
+A qualitative and quantitative evaluation is reported in the end.
 \end{abstract}

### 2022-08-05 paper/Chapters/Chapter01.tex
update paper

--- 2022-06-26 paper/Chapters/Chapter01.tex
@@
 
-Surface normal is an important property of a surface with many applications, like surface reconstruction, shadings generation and other visual effects.
-The quality of the surface normal is directly impact the performances of the techniques mentioned above.
-However, especially in the task of real-world object digitalization, the surface is usually hardly to be mathematically described in equations due to the elaborate details on the objects.
-Instead, it is common to use a group of points to describe the object surface, which is a memory economical solution and also can be easier measured by 3D scanners.
-The working principle of scanners are various due to the application scenarios, which consequently produce different point cloud structure.
-For the scanners without positions recording, the point cloud acquired after scanning is unstructured.
-In this case, every 3D point can be captured by different capture position, and neighbors are not defined by capture time, which increase the difficulty and computation for the neighbor based normal inference approaches.
+%Surface normal is an important property of a surface with many applications, like surface reconstruction, shadings generation and other visual effects.
+However, the calculation of surface normal in many tasks is not as straightforward as simply the cross-product of two plane vectors.
+Especially in the task of real-world object digitalization, the surface is usually hardly to be mathematically described in equations due to the elaborate details on the objects.
+%
+%Instead, it is common to infer it from the object point cloud.
+The point cloud records a great number of point positions on the object surface.
+These numbers of points altogether, are called point cloud, which is a memory economical solution to describe the shape of the object surface.
+They contains the geometry information of the surface, thus can be used for surface normal inference.
+%
+
+%
+%Apart from this, due to the application scenarios, the working principle of scanners are various, which consequently produce point cloud structures in different forms.
+For the scanners without positions recording, the point cloud is unstructured.
+In this case, every 3D point can be captured by different capture position, and neighbors are not defined by capture time.
+It increases the difficulty and computation for the neighbor based normal inference approaches.
 Furthermore, since the lack of inherent structure, the normal can hardly be inferred by the parallel approaches.
-To acquire the structured point cloud, a depth camera can be used for data collection.
-It captures the RGB-D images for the object, which includes the standard RGB image with depth information of each pixel.
-After camera calibration, the corresponding point cloud can be calculated based on the depth map and camera matrix.
-The advantages are, a structured point cloud is mapped directly based on the same capture position from a 2D depth map, the neighbor information of each point is identical to the corresponding pixel in the 2D depth map, which reduced a huge computational works.
-Besides, base on the RGB image, which has the same indices with depth map, the normal inference task can also utilize the relationship between surface normal and light reflection to further rectify the inferred normal map with knowing light source.
-Furthermore, the structured point cloud has the same shape with the standard RGB images, which can be used for deep learning based approaches.
-Unfortunately, the depth maps captured by the sensors are only semi-dense, which is mainly caused by optical noises and the reflections in dark and shinny areas.
-Consequently, it raises the challenges to the accuracy of normal inference tasks.
-Recently, deep learning-based methods are used in computer vision tasks such as image segmentation, image inpainting, and depth density enhancement.
-The output of the model is usually has the same shape as the input but with different content, which is by comparison similar to the normal inference task.
-The deep learning based method has many advantages, first, it deals well with semi-dense input, which is a common issue for the depth map.
-Second, the network of deep learning model handles the structured point cloud as a single input and infer the corresponding normal all together, which is very time economical comparing to the approaches like neighbor based methods.
-Furthermore, if the texture image acquiring from the camera is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations among light direction, normal direction, and grayscale image.
-Then the normal can be inferred better using the given image information and depth map.
-Based on the grayscale image and corresponding semi-dense depth maps, a multi-staged model can be designed to infer the normal map, which can give more density and robust results comparing to the standard algorithm.
-In this work, we apply the deep learning based approach for surface normal inference, which is based on the calibrated illuminated RGB-D image.
-A network named gated convolution neural network (GCNN) is proposed for normal inference, which is robust to the semi-dense input.
-With the help of synthetic data in Unity, a dataset is also created for CNN model training.
-It can provide accurate ground truth for training work, which real data is usually not provided.
-The trained model is performed well both in synthetic dataset as well as the real dataset captured from RGB-D cameras and achieve a remarkably better prediction accuracy at a low computational cost compared to the standard approaches for semi-dense point clouds.
+%
+%Thus getting a structured point cloud from a calibrated scanner is a much more convenient choice.
+One solution is the depth camera.
+It captures the RGB-D images of the object, which includes the standard RGB image with depth information of each pixel.
+Based on the calibrated camera, it is easy to acquire the structured surface point cloud from depth map and camera matrix.
+Furthermore, the point cloud is mapped directly based on the 2D depth map with the same capture position.
+which keeps the neighbor information of each point.
+It is identical to the corresponding pixel in the 2D depth map.
+This provides a better view for the normal inference task since the neighbor information can be considered as a reference.
+%
+%Besides geometry based approach, photometric stereo based approach using a set of light sources with knowing positions to separately project lights on the object, the surface normal can be calculated from the captured images and the known light directions.
+It is different from geometry based approach since no surface position is required.
+However, it usually require many different light positions to acquire a good performance \cite{spline-net} \cite{CNN-PS}, which raise the complexity for the data collection.
+%
+%Actually, the depth camera is able to acquire both geometry information like depth map as well as the images as photometric information.
+They are usually acquired at the same time when we collect the data.
+This inspired us to utilize the both depth map and image information to infer the surface map in order to find a more practical and more accurate approach that integrate two kinds of information and consequently improved surface normal inference.
+%
+%
+%Deep learning based methods provides multiple possible solutions for the challenges mentioned above.
+First, to deal with the noised input, deep learning based methods already have the solution for the similar tasks like image inpainting and depth density enhancement, which base on the noised image as input to predict the clean and fully dense output with or without original meanings.
+Therefore, it can be a help for noise in the depth map.
+Besides, the network of deep learning model can also handle the structured point cloud as a single input and infer the corresponding normal all together, which is very time economical comparing to the approaches like neighbor based methods.
+In addition, the multi-stages training architectures provide a way to consider both depth map and texture image as the input to predict the surface normals, which not only consider the point cloud but also the add the lambertian reflection as a further constraint.
+%
+%Unfortunately, in the actual situation, the depth maps captured by the sensors are only semi-dense, which is mainly caused by.
+Consequently, it disrupts the robustness of the normal inference methods.
+Median filters can be used for the sparse missing pixels, however, for the case of huge missing holes in the depth map, it produces just a paltry result.
+Thus a reasonable guess is required for missing areas.
+%
+%
+%In this work, we focus on the normal inference based on a semi-dense depth map with RGB image using deep learning based approaches.
+Specifically, the missing pixels in the depth map is filled up by the gated convolution and propagate in a customized UNet with skipping connections.
+The output of the training model is directly the surface normal corresponding the input depth map.
+The grayscale image is used to further improve the estimation accuracy.
+%For the training work, a dataset named “synthetic50-5” is created including 55 high resolution point clouds from internet, as shown in Appendix A.
+The point clouds provide with the high accurate normals, which can be used as the ground truth of the training work.
+Most of the models have elaborate details with high curvatures but also contain smooth surfaces.
+The trained model is evaluated on both synthetic dataset as well as the real dataset captured from RGB-D cameras.
+A series of metrics have been used for qualitative evaluation.
+The model is shown to achieve a remarkably better prediction accuracy at a low computational cost compared to the standard approaches for semi-dense point clouds.
+
+%% main problem, introduce deep learning, UNet
+In 3D computer vision tasks, the \textit{point cloud} ( i.e.
+a great number of point positions on the object surface, these numbers of points altogether, are called point cloud) is a common input data to describe the object surface.
+Based on the geometry information containing in the point cloud, we can acquire the corresponding surface normal, which is an importance features in computer vision, which can be further used for  surface reconstruction, shadings generation and other visual effects.
+A common approach to acquire the surface normal from point cloud is the optimization approach which consider the neighbor points in the same plane and calculate the plane normal.
+However, for the single input data with only one shot recording, like the depth camera, the acquired point cloud is converted from depth map.
+But due to the  optical noises and the reflections in dark and shinny areas of the object surface, the depth map is usually semi-dense only.
+Thus it limited the neighbor based approach since the missing data leads to less neighbors of each points.
+However, recent advances in image inpainting areas have motivated researchers to recover the missing regions in the input data using deep neural networks and achieves a good performance.
+For example, \cite{gconv} uses a gated convolution network to inpaint a custom removed areas in the images.
+\cite{nconv} uses normalized convolution network to enhance semi-dense depth map to fully dense depth map.
+Either work takes in-complete input data and mends it to fully dense output.
+Thus a deep learning based approach can be a way to deal with the semi-dense depth map input for surface normal estimation task.
+
+\begin{figure}[h!]
+	\centering
+	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud.png}}
+	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud-zoom-in.png}}
+	\decoRule
+	\caption{Left: A piece of point cloud of the dragon object. Right: Zoom in of the point cloud.}
+	\label{fig:point-cloud}
+\end{figure}
+
+%% introduce photometric stereo
+Photometric stereo is another approach in computer vision which can be used for surface normal estimation, where the normals are inferred from appearance variations under multiple illuminations.
+The relative methods are typically solve the least square problem based on the pointwise image formation model.\cite{SFS} and based on the Bidirectional Reflectance Distribution Function (BRDF).
+While BRDF based model generally cannot account the global illumination effects and this is usually unavoidable problem due to the light interactions and difficult traced mathematically.
+
+%% papers contribution, main work
+Both directions mentioned above have been widely researched using deep learning approaches.
+However, the approach that takes both geometry and illuminated information together into account for normal estimation remains impoverishment.
+We present a deep learning based approach takes both geometry and photometric information into account for normal inference.
+For a practical reason, we consider only 1 illuminated image based on the calibrated camera and takes semi-dense point cloud as input data.
+To achieve this goal, we will mainly take the geometry information into consideration and take the photometric information as a supplementary.
+
+%% introduce the network, trip-net, dataset
+One of our challenge is to apply the semi-dense input data to the neural network in a image-wise way.
+UNet is a good network applying for computer vision task with up-sampling requirement.
+We modified it with gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data.
+Another challenge is to merge the different input data feature maps together to cooperatively improved surface normal inference task.
+We propose a $ multi-fusion $ scheme for integration on separate feature map extractors.
+We will show that this multi-fusion design can be taken advantages of combination of different input data types and improved surface normal inference performance.
+To train our network, we create a synthetic RGB-D image dataset by utilizing one light source illumination and one ambient light illumination to simulate application scenarios.
+To simulate depth maps in real world, we applied uniform distributed drop-out noise to the input data with a control parameter for noise density.
+
+%% experiments
+We trained our approach on our proposed synthetic dataset ``synthetic-50-5" and evaluate it on 6 different metrics.
+We compare our approach against the geometry information based approach based on the similar network architecture and show that our calibrated illuminated RGB-D image based approach further improved normal accuracy.
+We also applied our model on real dataset and compare with the optimization based approach.
+
 The structure of the thesis is as follows, Chapter 1 is the introduction of the whole work.

### 2022-08-05 paper/Chapters/Chapter05.tex
update paper

@@
 %% svd evaluation
-\section{Visualization evaluation on SVD}
+\section{Visual evaluation on SVD}
 
@@
 
-\section{Visualization evaluation on GCNN model}
+\section{Visual evaluation on GCNN model}
 A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
@@
 
-\section{Feature Maps Discussion on GCNN architecture models}
+\section{ Discussion about the feature maps of GCNN architecture models}
 
@@
 \newpage 
-\section{Visualized evaluation on Trip-Net models }
+\section{Visual evaluation on Trip-Net models }
 
@@
 
+Since in the real-dataset, we don't have a ground-truth for evaluation.
+But if we see directly from the visualization in figure \ref{fig:trip-eval-real}, we can see that Trip-Net approach has good ability to  ``mend" the missing pixels in the scenes and also gives a sharp result.
+The folds on the gowns are recognizable and even countable.
+\ref{fig:real_eval_compare} compares the Trip-Net with other approaches.
+
+But we also noted that the big holes in the base stage remains in the depth maps.
+These big holes corresponds to the shinny and dark texture area, which common exists in the depth map captured by the scanners.
+Since these big holes are related with only special feature areas and also has irregular shapes, we didn't simulate this type of noise in the synthetic dataset but only with a random binary mask.
+Thus our models failed to mend missing big holes in the estimated normal map.
+This can be a further direction of this topic, that find a way to generate high similar depth map noise to get a more robust training dataset.
+
 \begin{figure}[th]
@@
 \end{figure}
-
-Since in the real-dataset, we don't have a ground-truth for evaluation.
-But if we see directly from the visualization in figure \ref{fig:trip-eval-real}, we can see that Trip-Net approach has good ability to  ``mend" the missing pixels in the scenes and also gives a sharp result.
-The folds on the gowns are recognizable and even countable.
-\ref{fig:real_eval_compare} compares the Trip-Net with other approaches.
-
-But we also noted that the big holes in the base stage remains in the depth maps.
-These big holes corresponds to the shinny and dark texture area, which common exists in the depth map captured by the scanners.
-Since these big holes are related with only special feature areas and also has irregular shapes, we didn't simulate this type of noise in the synthetic dataset but only with a random binary mask.
-Thus our models failed to mend missing big holes in the estimated normal map.
-This can be a further direction of this topic, that find a way to generate high similar depth map noise to get a more robust training dataset.
 

### 2022-08-05 paper/main.tex
update paper

@@
 
-\vspace*{0.2\textheight}
+%\vspace*{0.2\textheight}
 
-\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
-
-\hfill Dave Barry
+%\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
+%
+%\hfill Dave Barry
 
@@
 
-\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
-
-\textbf{I} & Grayscale Image Matrix (Height $ \times $ Width $ \times $ 1)\\
-\textbf{L} & Light Map Matrix (Height $ \times $ Width $ \times $ 3)\\
-\textbf{N} & Normal Map Matrix (Height $ \times $ Width $ \times $ 3)\\
-\textbf{V} & Vertex Map Matrix (Height $ \times $ Width $ \times $ 3)\\
-
-\textbf{X} & Input Matrix (Height $ \times $ Width $ \times $ Channels)\\
-\textbf{Y} & Output Matrix (Height $ \times $ Width $ \times $ Channels)\\
-
-\textbf{w} & Width of Matrix\\
-\textbf{h} & Height of Matrix\\
-
-\end{abbreviations}
+%\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
+%
+%\textbf{I} & Grayscale Image Matrix (Height $ \times $ Width $ \times $ 1)\\
+%\textbf{L} & Light Map Matrix (Height $ \times $ Width $ \times $ 3)\\
+%\textbf{N} & Normal Map Matrix (Height $ \times $ Width $ \times $ 3)\\
+%\textbf{V} & Vertex Map Matrix (Height $ \times $ Width $ \times $ 3)\\
+%
+%\textbf{X} & Input Matrix (Height $ \times $ Width $ \times $ Channels)\\
+%\textbf{Y} & Output Matrix (Height $ \times $ Width $ \times $ Channels)\\
+%
+%\textbf{w} & Width of Matrix\\
+%\textbf{h} & Height of Matrix\\
+%
+%
+%
+%\end{abbreviations}
 
@@
 
-\begin{symbols}{ll} % Include a list of Symbols (a three column table)
-
-$[A B]$ & concatenation between A and B \\
-$\oplus$ & element-wise multiplication \\
-$\cdot$ & dot product \\
-%Symbol & Name & Unit \\
-
-\end{symbols}
-
 %----------------------------------------------------------------------------------------
@@
 
-\dedicatory{To ...}
+\dedicatory{To my fire}
 
@@
 \include{Appendices/AppendixA}
-%\include{Appendices/AppendixB}
+\include{Appendices/AppendixB}
 %\include{Appendices/AppendixC}

### 2022-08-06 paper/Chapters/Chapter02.tex
update paper

@@
 
-Due to the different of data structures, the point clouds can be grouped into types, structured point cloud based and unstructured point cloud based.
-The first case contains the neighbor information of each point together with a depth map or RGB image, the second case does not contain any neighbor information which has to be further calculated.
+%% depth map approach
+Surface normal inference is a widely researched topic and can be solved in multiple directions.
+Based on a structured point cloud, the surface normal can be derived from geometry information of the point cloud, which mainly utilizes the neighbor information and consider it as an optimization problem (\cite{optimized-methods} ).
+They can perform well on dense point cloud input data based on a well-chosen window size.
+However, the drawbacks are that the algorithms are highly noise sensitive.
+The point cloud is usually not fully dense and normally converted from depth map, which are usually with missing pixels and holes on dark, shinny or transparent regions (\cite{nyu}).
+The missing points destabilizes the geometry based solution.
+To ease this problem, \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix, which is used to smooth the depth data in order to handle the noise of depth image.
+\cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map.
+Some approaches use deep learning method to fill missing areas.
+\cite{nconv} introduces normalized convolution to deal with missing or uncertain depth data with an added mask on the standard convolution operation.
+\cite{ncnn} applied it and use it as normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
+\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
 
-\paragraph{ Structured Point Cloud Based}
-The relevant methods derive the surface normals based on spatial relationship, which utilizes the neighbor information for estimation.
-These methods performs well with a well-chosen window size.
-However, the drawbacks are that the algorithm is highly noise sensitive.
-It is weak in handling missing pixels, which is a common issue in the input data.
-The earlier methods usually use optimized methods.
-\cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix.
-They also smooth the depth data in order to handle the noise of depth image.
-The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.
-\cite{optimized-methods} did a comparison among the optimization-based methods.
+%% photometric approach
+Photometric stereo is another approach that infer surface normal from BRDF based surface model.
+The surface normal is related with observed intensity, the incoming light direction, the outgoing viewing direction and the light intensity.
+It required multiple light conditions to get an optimal solution.
+
+%% fusion approach
+
+%% talk about gated convolution, Unet
+
+%% in summary
 
@@
 
-\paragraph{Depth Based}
-Depth map contains the spatial information of the object surface, which is very important for the normal inference task.
-However, the depth map captured by depth sensors are usually with missing pixels and holes on dark, shinny or transparent regions.(\cite{nyu}).
-To overcome the missing pixels,
-\cite{depth-inpainting-distribution} proposed a depth hole filling method using the depth distributions of neighboring regions.
-\cite{nconv} introduced normalized convolution dealing with missing or uncertain data for convolution operation.
-It uses a binary mask to distinguish missing data and integrate it into the convolution operation.
-\cite{ncnn} applied it and use normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
-\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
-However, the relevant papers are only using 1 channel data as model input, which didn't discussed the case for the multiple-channel data as input, such as RGB image, or structured point cloud.
-\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.
-
 \paragraph{RGB based} RGB based methods predict the depth map diretly from single RGB image.
@@
 It also considers the confidence of the values in depth map.
+
+\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.

### 2022-08-06 paper/Chapters/Chapter04.tex
update paper

@@
 	\end{subfigure}
-
+	\decoRule
 	\label{fig:dataset-demo}
@@
 The layout in the Unity game engine is shown in Figure \ref{fig:unity-workplace}.
-We generate 3000 scenes with resolution $ 128\times128\times3 $ and 5000 scenes with resolution $ 512\times512\times3 $.
+We generate 3000 scenes with resolution $ 128\times128 $ and 5000 scenes with resolution $ 512\times512 $.
 
@@
 	\includegraphics[width=.99\textwidth]{./Figures/unity-workplace.PNG}
+	\decoRule
 	\caption{The layout of synthetic scenes generation in Unity.}
@@
 	\begin{tabular}{l l}
+		\toprule
 		\tabhead{Data} & \tabhead{Size} \\
+		\midrule
 		Depth map & Width$ \times $Height$ \times $ 1 \\
@@
 		\hline 
+		\bottomrule
 	\end{tabular}
@@
 	\end{subfigure}
+	\decoRule
 	\caption{Different exposure to the objects.}
@@
 It based on following equation
-\[ gray: \frac{r+2g+b}{4}  \]
+\[ gray: \frac{R+2G+B}{4}  \]
 
@@
 	\end{tikzpicture}	
+	\decoRule
 	\caption{Convert depth to point in camera coordinate system}
@@
 	\label{fig:data_range}
+	\decoRule
 	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
@@
 
-\begin{table}[h!]
-	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. 
-	}
+\begin{table}[th]
 	\label{tab:data-range}
@@
 	\begin{tabular}{c | c c c}
-		\hline 
+		\toprule
 		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
-		\hline 
+		\midrule
 		X & 1.48 & -0.75 & 0.73\\
@@
 		Z & 1.47 & 6.53 & 8.00\\
-		\hline
+		\bottomrule
 
 	\end{tabular}
+	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. }
 \end{table}
@@
 	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
+	\decoRule
 	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
@@
 	\begin{tabular}{l | l}
+		\toprule
 		\tabhead{Name} & \tabhead{Content} \\
+		\midrule
 		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
@@
 		Depth Range  & minDepth, maxDepth\\
+		\bottomrule
 	\end{tabular}

### 2022-08-06 paper/Chapters/Chapter05.tex
update paper

@@
 	\label{fig:svd-noise}
-	\caption{Evaluation of neighbor based method on a noised dragon model}
+	\caption{SVD visual evaluation on a noised dragon model ($ 128\times128 $)}
 \end{figure}
@@
 	\decoRule
-	\caption{Normal inference based on GCNN. ($ 128\times128 $)}
+	\caption{GCNN visual evaluation. Window size $ 128\times128 $}
 	\label{fig:gcnn-eval}
@@
 	\decoRule
-	\caption{Zoom in of some regions of Dragon object (GCNN models). Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
+	\caption{Zoom in of some regions of Dragon object (GCNN models). Window size $ 32\times32 $.}
 	\label{fig:gcnn-eval-synthetic-zoom-in}
@@
 	\decoRule
-	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
+	\caption{Trip-Net visual evaluation on resolution $ 128\times128 $}
 	\label{fig:trip-eval}
@@
 	\decoRule
-	\caption{Comparison between different fusion times for Trip-Net. }
+	\caption{Comparison between different fusion times on Trip-Net Architecture ($ 128\times128 $). }
 	\label{fig:tripnet-eval-synthetic-zoom-in}
@@
 	\decoRule
-	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
+	\caption{Trip-Net visual evaluation on high resolution dataset $ 512 \times 512 $.}
 	\label{fig:trip-eval-high-resolution}
@@
 	\decoRule
-	\caption{High resolution dataset ($ 512\times 512 $) comparison.}
+	\caption{Comparison on high resolution dataset ($ 512\times 512 $) .}
 	\label{fig:trip-eval-compare}

### 2022-08-06 paper/Chapters/Chapter06.tex
update paper

@@
 We also show the effectiveness of skip connection in the U-Net.
-Our network uses a fully convolution design which enables it takes any resolution images as input.
+Besides, the fully convolution design enables it to use various resolution images as input.
 
@@
 We have also found that 3 to 4 times fusion times among 3 pipes in our models is the key point for the performance enhancement.
-Based on our experiments, we found that the models trained on illuminated calibrated RGB-D images achieve a  better performance than geometry information only based approach and gives more sharpness in the normal map.
+Based on our experiments, it shows that the models trained on illuminated calibrated RGB-D images achieve a  better performance than geometry information only based approach and gives more sharpness in the normal map.
 
@@
 
-In our experiments we collected 55 high density point clouds from internet and used them for our dataset generation.
+We collected 55 high density point clouds from internet and used them for our dataset generation.
 Specifically, we use a RGB-D camera, an ambient light and one directional light  collect thousands of scenes.
@@
 Furthermore, we also simulated noise in our synthetic dataset by a uniform distributed drop off to fit our model adopt with semi-dense input data.
-
 However, for the large missing areas, we did not generate a similar noise in the training set, which leads to our model cannot fill the holes in the real data.

### 2022-08-06 paper/Chapters/Chapter02.tex
update paper

@@
-% Chapter Template
+_{}% Chapter Template
 
@@
 
-%% depth map approach
 Surface normal inference is a widely researched topic and can be solved in multiple directions.
-Based on a structured point cloud, the surface normal can be derived from geometry information of the point cloud, which mainly utilizes the neighbor information and consider it as an optimization problem (\cite{optimized-methods} ).
-They can perform well on dense point cloud input data based on a well-chosen window size.
-However, the drawbacks are that the algorithms are highly noise sensitive.
-The point cloud is usually not fully dense and normally converted from depth map, which are usually with missing pixels and holes on dark, shinny or transparent regions (\cite{nyu}).
-The missing points destabilizes the geometry based solution.
-To ease this problem, \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix, which is used to smooth the depth data in order to handle the noise of depth image.
+Traditionally, it can be inferred from a point cloud.
+There exists many optimization based approaches to pixel-wise calculate surface normal using neighbor information of each point (\cite{optimized-methods}).
+\cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix.
+These approaches perform well on dense input data based on a well-chosen window size.
+However, in many practical dataset, like  (\cite{nyu} and \cite{kitti-depth}), the geometry information is provided as depth map.
+The depth map can be used to convert to point cloud but it is usually very noisy with many missing pixels and holes on dark, shinny or transparent regions.
+It gives more challenge on neighbor based approaches since no neighbor information exists in many of such areas.
+
+In order to ease this problem, some of the approaches focus on depth map enhancement by estimating missing regions.
 \cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map.
-Some approaches use deep learning method to fill missing areas.
-\cite{nconv} introduces normalized convolution to deal with missing or uncertain depth data with an added mask on the standard convolution operation.
-\cite{ncnn} applied it and use it as normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
-\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
+\cite{ncnn} use deep learning based approach for semi-dense depth map inpainting, which mainly utilized normalized convolution proposed by \cite{nconv}.
+This approach considers a 0-1 mask to distinguish valid and invalid data points.
+\cite{pncnn} improved this approch by proposing an input confidence estimation network to replace the binary mask with a estimated confidence mask.
+\cite{depth-enhance-guided} uses normalized convolution for depth map inpainting as well and also use RGB image as the guidance.
 
-%% photometric approach
+On the other hand, some of the approaches use RGB image to estimate depth map or surface normal or use RGB-D image to estimate surface normal. 
+\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively.
+\cite{img2depth} also predicts the depth map from image, which employed Residual Network for the feature extraction and further designed a upsampling part with the unpolling layers.
+\cite{binsformer} proposed a method adaptively generate information to predict depth maps based on RGB image. 
+\cite{geometry_based_solution} uses RGB-D images to estimate surface normal.
+It proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
+\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.
+\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input.
+
+However, these approaches are mainly relies on RGB images as input for normal estimation or depth inference and applied for indoor scenarios like bedroom or office, which does not focus on fine details of the surface but only main directions of the regions like direction of floor, walls, seats etc.
+
+%% photometric stereo
 Photometric stereo is another approach that infer surface normal from BRDF based surface model.
@@
 It required multiple light conditions to get an optimal solution.
+\cite{CNN-PS} uses a CNN based approach to learn  the relationship between photometric stereo input and the surface normal under hundreds of lights which also robust to the effect of global illuminations.
+\cite{spline-net} based on a lighting interpolation network to use only  a sparse set of lights for photometric stereo task.
 
-%% fusion approach
+Our approach utilizes a single light position as illumination information and further use RGB-D image to provide geometry information observed intensity for surface normal inference, which takes multiple input data type into consideration for normal estimation, which is supposed to improve single input data type approach under the same condition.
 
-%% talk about gated convolution, Unet
-
-%% in summary
-
-\paragraph{Unstructured Point Cloud Based}
-For the unstructured point cloud, the neighbor information of each point is usually unknown.
+%For the unstructured point cloud, the neighbor information of each point is usually unknown.
 K-nearest neighbor (KNN) is a common algorithm for neighbor searching.
@@
 To calculate the normals of multiple points in parallel \cite{unstructed-pc-patch-stitching} processes a series of overlapping patches for normal estimation.
+%
+%
 
-Deep learning based methods take single RGB image or RGB-D image as the input for normal estimation.
+%% depth map approach
+
+%% photometric approach
+
+%
+%%% depth map approach
+%Surface normal inference is a widely researched topic and can be solved in multiple directions.
+Based on a structured point cloud, the surface normal can be derived from geometry information of the point cloud, which mainly utilizes the neighbor information and consider it as an optimization problem (\cite{optimized-methods} ).
+They can perform well on dense point cloud input data based on a well-chosen window size.
+However, the drawbacks are that the algorithms are highly noise sensitive.
+%The point cloud is usually not fully dense and normally converted from depth map, which are usually with missing pixels and holes on dark, shinny or transparent regions (\cite{nyu}).
+The missing points destabilizes the geometry based solution.
+To ease this problem, \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix, which is used to smooth the depth data in order to handle the noise of depth image.
+\cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map.
+%Some approaches use deep learning method to fill missing areas.
+\cite{nconv} introduces normalized convolution to deal with missing or uncertain depth data with an added mask on the standard convolution operation.
+\cite{ncnn} applied it and use it as normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
+\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
+%
+%
+%%% photometric approach
+%Photometric stereo is another approach that infer surface normal from BRDF based surface model.
+The surface normal is related with observed intensity, the incoming light direction, the outgoing viewing direction and the light intensity.
+It required multiple light conditions to get an optimal solution.
+%
+%
+%
+%
+%
+%
+%
+%%% fusion approach
+%
+%
+%%% talk about gated convolution, Unet
+%
+%%% in summary
+%
+%\paragraph{Unstructured Point Cloud Based}
+%For the unstructured point cloud, the neighbor information of each point is usually unknown.
+K-nearest neighbor (KNN) is a common algorithm for neighbor searching.
+With knowing this information, the neighbor based approaches can be used as a second step.
+However, KNN-method merely based on the Euclidean distance in the 3D space.
+Therefore, the points of the other surfaces but in a close distance will also be considered as neighbors.
+To ease this problem, \cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation.
+To calculate the normals of multiple points in parallel \cite{unstructed-pc-patch-stitching} processes a series of overlapping patches for normal estimation.
+%
+%
+%
+%Deep learning based methods take single RGB image or RGB-D image as the input for normal estimation.
 It has a strong relationship with the depth inference tasks, two benchmarks are highly used in these area.
 (\cite{nyu} and \cite{kitti-depth}) Based on the input of training model, the methods can be roughly divided as follows:
-
-\paragraph{RGB based} RGB based methods predict the depth map diretly from single RGB image.
-\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively.
+%
+%
+%
+%\paragraph{RGB based} RGB based methods predict the depth map diretly from single RGB image.
+%\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively.
 \cite{img2depth} employed Residual Network for the feature extraction and further designed a upsampling part which replace the fully-connected layer with the unpolling layers.
-\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
-\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.
+%\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
+%\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.
 \cite{binsformer} proposed a method achieved state of art in NYUv2 Dataset (\cite{nyu}), which adaptively generate information to predict depth maps based on RGB image.
-
-\paragraph{RGB-D based}
-\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input.
+%
+%\paragraph{RGB-D based}
+%\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input.
 The RGB image and depth map are in the separate branches and imply a fusion module in four sections of the network to concatenate two branches.
 It also considers the confidence of the values in depth map.
-
-\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.
+%
+%\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.

### 2022-08-07 paper/Chapters/Chapter02.tex
update paper

@@
 There exists many optimization based approaches to pixel-wise calculate surface normal using neighbor information of each point (\cite{optimized-methods}).
-\cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix.
+\cite{Holzer.S} proposed a method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix.
 These approaches perform well on dense input data based on a well-chosen window size.
-However, in many practical dataset, like  (\cite{nyu} and \cite{kitti-depth}), the geometry information is provided as depth map.
-The depth map can be used to convert to point cloud but it is usually very noisy with many missing pixels and holes on dark, shinny or transparent regions.
+However, in many practical dataset, like  (\cite{nyu} and \cite{kitti-depth}), the geometry information is provided as a depth map.
+The depth map can be used to convert to point cloud, but it is usually very noisy with many missing pixels and holes on dark, shiny or transparent regions.
 It gives more challenge on neighbor based approaches since no neighbor information exists in many of such areas.
@@
 This approach considers a 0-1 mask to distinguish valid and invalid data points.
-\cite{pncnn} improved this approch by proposing an input confidence estimation network to replace the binary mask with a estimated confidence mask.
+\cite{pncnn} improved this approach by proposing an input confidence estimation network to replace the binary mask with a estimated confidence mask.
 \cite{depth-enhance-guided} uses normalized convolution for depth map inpainting as well and also use RGB image as the guidance.
@@
 \cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively.
-\cite{img2depth} also predicts the depth map from image, which employed Residual Network for the feature extraction and further designed a upsampling part with the unpolling layers.
+\cite{img2depth} also predicts the depth map from image, which employed Residual Network for the feature extraction and further designed a up-sampling part with the un-polling layers.
 \cite{binsformer} proposed a method adaptively generate information to predict depth maps based on RGB image. 
@@
 
-However, these approaches are mainly relies on RGB images as input for normal estimation or depth inference and applied for indoor scenarios like bedroom or office, which does not focus on fine details of the surface but only main directions of the regions like direction of floor, walls, seats etc.
+However, these approaches mainly rely on RGB images as input for normal estimation or depth inference and applied for indoor scenarios like bedroom or office, which does not focus on fine details of the surface but only main directions of the regions like direction of floor, walls, seats, etc.
 

### 2022-08-07 paper/Chapters/Chapter01.tex
update paper

@@
 a great number of point positions on the object surface, these numbers of points altogether, are called point cloud) is a common input data to describe the object surface.
-Based on the geometry information containing in the point cloud, we can acquire the corresponding surface normal, which is an importance features in computer vision, which can be further used for  surface reconstruction, shadings generation and other visual effects.
-A common approach to acquire the surface normal from point cloud is the optimization approach which consider the neighbor points in the same plane and calculate the plane normal.
+Based on the geometry information containing in the point cloud, we can acquire the corresponding surface normal, which is an importance features in computer vision, and it can be further used for surface reconstruction, shadings generation and other visual effects.
+A common approach to acquire the surface normal from the point cloud is the optimization approach which consider the neighbor points in the same plane and calculate the plane normal.
 However, for the single input data with only one shot recording, like the depth camera, the acquired point cloud is converted from depth map.
-But due to the  optical noises and the reflections in dark and shinny areas of the object surface, the depth map is usually semi-dense only.
-Thus it limited the neighbor based approach since the missing data leads to less neighbors of each points.
+But due to the optical noises and the reflections in dark and shiny areas of the object surface, the depth map is usually semi-dense only.
+Thus it limited the neighbor based approach since the missing data leads to fewer neighbors of each point.
 However, recent advances in image inpainting areas have motivated researchers to recover the missing regions in the input data using deep neural networks and achieves a good performance.
 For example, \cite{gconv} uses a gated convolution network to inpaint a custom removed areas in the images.
-\cite{nconv} uses normalized convolution network to enhance semi-dense depth map to fully dense depth map.
+\cite{nconv} uses normalized convolution network to enhance the semi-dense depth map to fully dense depth map.
 Either work takes in-complete input data and mends it to fully dense output.
@@
 Photometric stereo is another approach in computer vision which can be used for surface normal estimation, where the normals are inferred from appearance variations under multiple illuminations.
-The relative methods are typically solve the least square problem based on the pointwise image formation model.\cite{SFS} and based on the Bidirectional Reflectance Distribution Function (BRDF).
-While BRDF based model generally cannot account the global illumination effects and this is usually unavoidable problem due to the light interactions and difficult traced mathematically.
+The relative methods are typically solve the least square problem based on the point-wise image formation model.\cite{SFS} and based on the Bidirectional Reflectance Distribution Function (BRDF).
+While BRDF based model generally cannot account the global illumination effects and this is usually an unavoidable problem due to the light interactions and difficult traced mathematically.
 
@@
 %% introduce the network, trip-net, dataset
-One of our challenge is to apply the semi-dense input data to the neural network in a image-wise way.
-UNet is a good network applying for computer vision task with up-sampling requirement.
-We modified it with gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data.
-Another challenge is to merge the different input data feature maps together to cooperatively improved surface normal inference task.
+One of our challenges is to apply the semi-dense input data to the neural network in an image-wise way.
+UNet is a good network applying for computer vision tasks with up-sampling requirements.
+We modified it with a gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data.
+Another challenge is to merge the different input data feature maps to cooperatively improved the surface normal inference task.
 We propose a $ multi-fusion $ scheme for integration on separate feature map extractors.
-We will show that this multi-fusion design can be taken advantages of combination of different input data types and improved surface normal inference performance.
+We will show that this multi-fusion design can be taken advantage of by a combination of different input data types and improved surface normal inference performance.
 To train our network, we create a synthetic RGB-D image dataset by utilizing one light source illumination and one ambient light illumination to simulate application scenarios.
-To simulate depth maps in real world, we applied uniform distributed drop-out noise to the input data with a control parameter for noise density.
+To simulate depth maps in the real world, we applied uniform distributed drop-out noise to the input data with a control parameter for noise density.
 
@@
 We trained our approach on our proposed synthetic dataset ``synthetic-50-5" and evaluate it on 6 different metrics.
-We compare our approach against the geometry information based approach based on the similar network architecture and show that our calibrated illuminated RGB-D image based approach further improved normal accuracy.
-We also applied our model on real dataset and compare with the optimization based approach.
+We compare our approach against the geometry information based approach based on similar network architecture and show that our calibrated illuminated RGB-D image based approach further improved normal accuracy.
+We also applied our model to a real dataset and compare it with the optimization based approach.
 
@@
 Chapter 2 briefly discusses the related work about normal inference.
-Chapter 3 is the main approaches of this work.
+Chapter 3 is the main approach of this work.
 Chapter 4 introduces the created dataset for the training work.

### 2022-08-07 paper/Chapters/Chapter04.tex
update paper

@@
 
- In this thesis, we require two kinds of input data for model training. 
-First we need geometry information of the object surface. This can be collected by a depth camera, which records the Z-axis distance of the object surface point to the camera position. 
-Second we need illuminated information of the object surface, which considers as a help-information of the geometry based model to further improve the inference accuracy.
-This kind of information is collected by a light scanner, which usually has known intrinsic and extrinsic camera matrix, so that we can convert the point between camera coordinate system and the world coordinate system.
-Besides, an extra spot light will be placed in a known position to illuminate the object surface.
-Then, the light scanner can capture the scene as a grayscale/RGB image, save the camera matrix and light position.
-So we can based on the light position and the depth map acquired from depth camera to calculate light direction and further use image to estimate the surface normal.
+ In this thesis, we require two kinds of input data to train our models. 
+First we need geometry information of the object surface.
+This can be collected by a depth camera, which records the Z-axis distance of the object surface to the camera position and it can be further converted to a point cloud.
+Second we need illuminated information of the object surface, which considers as a photometric-information of for the further accuracy improvement. 
+This kind of information requires an observed image of the object with the light directions that projected to the object surface.
 
 In order to acquire these data, we can use a light scanner to scan the objects in laboratory.
-However, the scanner is failed to scan dark, shinny and transparent region, which leaves a plenty of missing pixels and holes in the depth map.
+However, the scanner is failed to scan dark, shiny and transparent region, which leaves a plenty of missing pixels and holes in the depth map.
 Thus the corresponding surface points are incomplete for the object.
@@
 When we create the dataset, we tried to make the object types as many as possible to give a robust and wide range covered training scenarios.
-The category of the models include figure, animal, statue, toy, furniture, antique, car model, which include the smooth surface model like \textit{arm, bus, bunny, cat, zebra} and also the model with highly elaborate details, like \textit{Washington, Car-Engine, Armadillo}.
+The category of the models include figure, animal, statue, toy, furniture, antique, car model, some of them correspond the smooth surface model like \textit{arm, bus, bunny, cat, zebra} and some of the model has highly elaborate details, like \textit{Washington, Car-Engine, Armadillo}.
 The dataset is created base on the work of this thesis and using for normal inference task.
@@
 
-Besides, some of the objects also has its own texture, as shown in the second row of Figure \ref{fig:dataset-demo}.
+Besides, some of the objects also has colored texture, as shown in the second row of Figure \ref{fig:dataset-demo}.
 This is specially prepared for illuminated approach since they will take the image as account to evaluate the surface normal.
-The object surface gives a different reflectence with different surface texture, which further impact the model performance.
+The textured models are more likely to the real dataset and further gives a good robustness to our models.
 
@@
 \section{Synthesize Scenes using Unity}
-In order to simulate the the data collection scenario close to the real life in the laboratory as much as possible.
-We placed a flat cylinder called $ stage $ in the center in the 3D space as a platform to place objects.
-The stage is fixed in a determined position, which is not moved when the scene is captured.
-A directional light with RGB color FFF4D6 \col{direction-light-color}  placed in a top-view direction around 25 meters away to provide as ambient light, which also has a fixed position.
+In order to simulate the data collection scenario close to the real life in the laboratory as much as possible.
+We did following settings.
+A flat cylinder called $ stage $ is placed in the center in the 3D space as a platform to place objects.
+The stage is fixed in a determined position, which is not moved when the images are captured.
+A directional light with RGB color FFF4D6 \col{direction-light-color} is placed in a top-view direction around 25 meters away to provide as ambient light source, which also has a fixed position.
 A RGB-D camera is placed in a top-view direction around 10m away from the stage.
-The camera is the sensor to capture the depth map and the grayscale image, which is random moved after a new scene.
+The camera is the sensor to capture the depth map and the grayscale image, which is random change the places after each scene.
 The moving range of the camera has 0.1m in both directions of X, Y, and Z axis and 1 degree random changed Euler angle.
-A point light placed around 5 meters away as the illumination light, which is also randomly moved after a new scene.
+A point light placed around 5 meters away as the illumination light, which is also randomly moved after each scene.
 The moving range is 0.3m in both directions of X, Y, and Z axis and 1 degree random in Euler angle.
@@
 Or we have to control the light radiance on the object surface.
-As shown in figure \ref{fig:camera_exposure}, too less exposure on the object neutralizes the illumination information, which only left ambient light effect.
+As shown in figure \ref{fig:camera_exposure}, too less exposure will neutralize the illumination information, which only left ambient light effect.
 Too much exposure makes the surface texture hard to recognize.

### 2022-08-07 paper/Chapters/Chapter04.tex
update paper

@@
  In this thesis, we require two kinds of input data to train our models. 
-First we need geometry information of the object surface.
+First, we need to know the geometry of the object surface.
 This can be collected by a depth camera, which records the Z-axis distance of the object surface to the camera position and it can be further converted to a point cloud.
-Second we need illuminated information of the object surface, which considers as a photometric-information of for the further accuracy improvement. 
-This kind of information requires an observed image of the object with the light directions that projected to the object surface.
+Second, we need illuminated information of the object surface, which considers a photometric-information used for further improvement. 
+This kind of information requires an observed image of the object with the light directions projected onto the object surface.
 
-In order to acquire these data, we can use a light scanner to scan the objects in laboratory.
-However, the scanner is failed to scan dark, shiny and transparent region, which leaves a plenty of missing pixels and holes in the depth map.
-Thus the corresponding surface points are incomplete for the object.
-It leads to the missing ground-truth in the normal map.
-Second, to train a deep learning based model usually require a huge dataset, especially for the network without backbone.
-To create a single depth map dataset for this thesis would be too much of work and resource requirement.
-A proper way for getting huge depth map data with illumination information can be considered using a game engine, which can simulate any number of data that we required.
+In order to gain these data, we can use a light scanner to scan the objects in the laboratory.
+However, the scanner usually can not scan the dark, shiny, and transparent regions, which leaves plenty of missing pixels and holes in the depth map.
+This incomplete surface information raises the difficulty for our model training since the ground-truth corresponding to the depth map will be incomplete as well.
+Second, training a deep learning-based model usually requires a huge dataset, especially for a network without a backbone.
+To create a single depth map dataset for this thesis would be too much work and resource requirements.
+A proper way for getting huge depth map data with illumination information can be considered using a game engine, which can simulate any number of data that we require.
 
-In this thesis, we use Unity game engine for data generation.
-Based on a $ C\# $ script, we can set on a similar configuration in the laboratory.
-Then create a mount of data based on the collected object models.
-The dataset that we created for this thesis is called \textit{synthetic-50-5}, since it has 50 different object models for training and 5 object models for testing.
+In this thesis, we use the Unity game engine for data generation.
+By using a $ C\# $ script, we can set up a similar configuration in the laboratory.
+Then create a mount of data based on the collected objects.
+The dataset that we created for this thesis is called \textit{synthetic-50-5} since it has 50 different object models for training and 5 object models for testing.
 
@@
 The object model we used are searched from internet.
-\cite{data1}, \cite{data2}, \cite{data3} and \cite{data4} published a set of point cloud dataset for computer vision research.
+A set of point cloud datasets for computer vision research has been published by /cite[data1], /cite[data2], /cite[data3] and /cite[data4].
 These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing.
-Each objects has been scanned for hundreds of times with an exhaustive completion for the origin objects, which is up to millions points.
+All objects has been scanned for hundreds of times with an exhaustive completion for the origin objects, which is up to millions points.
 (\cite{data1}).
-The dense point clouds makes the normal inference task trivial since the neighbor based method performs good enough for these kind of task.
-Some of the point cloud even equipped with pre-computed normal map based on more advanced methods.
-They all provides the accurate ground-truth for the supervised learning method.
+The dense point clouds make the normal inference task trivial since the neighbor based method performs adequately for this kind of task.
+Some of the point clouds even contain pre-computed normal maps based on more advanced methods.
+They all provide the accurate ground truth for the supervised learning method.
 
-The \textit{synthetic50-5} is a datset we generated in this thesis with 50 point clouds as training set and 5 point clouds as test set.
+The \textit{synthetic50-5} is a dataset we generated in this thesis based on 50 point clouds as a training set and 5 point clouds as a test set.
 When we create the dataset, we tried to make the object types as many as possible to give a robust and wide range covered training scenarios.
-The category of the models include figure, animal, statue, toy, furniture, antique, car model, some of them correspond the smooth surface model like \textit{arm, bus, bunny, cat, zebra} and some of the model has highly elaborate details, like \textit{Washington, Car-Engine, Armadillo}.
-The dataset is created base on the work of this thesis and using for normal inference task.
-Figure \ref{fig:dataset-demo} gives the illustrations of some objects.
-Appendix \ref{AppendixA} gives a full version of dataset models.
+There are various categories of models, such as figure, animal, statue, toy, furniture, antique, and car model, some of which have relatively smooth surfaces, such as /textit[arm, bus, bunny, cat, zebra], and some of which have highly complicated details, such as \textit{Washington, Car-Engine, Armadillo}.
+We created this dataset for normal inference tasks. Figure \ref{fig:dataset-demo} gives the illustrations of some objects. Appendix \ref{AppendixA} gives a full version of dataset models.
 
@@
 \end{figure}
-
-Besides, some of the objects also has colored texture, as shown in the second row of Figure \ref{fig:dataset-demo}.
-This is specially prepared for illuminated approach since they will take the image as account to evaluate the surface normal.
-The textured models are more likely to the real dataset and further gives a good robustness to our models.
+Besides, some objects also have colored textures, as shown in the second row of Figure \ref{fig:dataset-demo}.
+This is specially prepared for the illuminated approach since they will take the image into account to evaluate the surface normal.
+By using textured models, our models become closer to the real dataset and have improved robustness, which can apply to the real dataset further.
 
@@
 \section{Synthesize Scenes using Unity}
-In order to simulate the data collection scenario close to the real life in the laboratory as much as possible.
-We did following settings.
-A flat cylinder called $ stage $ is placed in the center in the 3D space as a platform to place objects.
-The stage is fixed in a determined position, which is not moved when the images are captured.
-A directional light with RGB color FFF4D6 \col{direction-light-color} is placed in a top-view direction around 25 meters away to provide as ambient light source, which also has a fixed position.
-A RGB-D camera is placed in a top-view direction around 10m away from the stage.
-The camera is the sensor to capture the depth map and the grayscale image, which is random change the places after each scene.
-The moving range of the camera has 0.1m in both directions of X, Y, and Z axis and 1 degree random changed Euler angle.
-A point light placed around 5 meters away as the illumination light, which is also randomly moved after each scene.
-The moving range is 0.3m in both directions of X, Y, and Z axis and 1 degree random in Euler angle.
+In order to simulate the data collection scenario close to the real world as much as possible.
+We did the following settings.
+A flat cylinder called $ stage $ is placed in the center of the 3D space as a platform to place objects.
+We fixed the stage in a predetermined position, which is not changed when images are captured.
+To provide ambient light, one directional light with RGB color FFF4D6 /col[direction-light-color] is placed in a top-view direction at a distance of 25 meters, which also has a fixed location.
+An RGB-D camera is placed in a top-view direction around 10m away from the stage.
+The camera captures the depth map and the gray-scale image, which is randomly arranged after each scene.
+The moving range of the camera has 0.1m in both directions of the X, Y, and Z axis and a 1-degree random changed Euler angle.
+As an illumination light, a point light is placed around 5 meters away, which is also randomly moved after each scene.
+The moving range is 0.3m in both directions of the X, Y, and Z axis and 1 degree random in the Euler angle.
 
 During the data collection, the object is randomly selected and placed on the stage.
-The object has a random upto 30 degrees rotation align $ roll $-axis, 30-degrees rotation align $ pitch $-axis and 180-degrees align $ yaw $-axis.
+The object has a random up to 30 degrees rotation align $ roll $-axis, 30-degrees rotation aligns $ pitch $-axis, and 180-degrees rotation aligns $ yaw $-axis.
 Thus the camera has the opportunity to capture every direction of the object and consequently abundant the dataset.
@@
 \end{figure}
-
-The main advantage using generated scenes is the availability of complete information.
-The depth map can be captured in a loss-free way.
+The main advantage of generated scenes is the availability of complete information.
+We can capture the depth map in a lossless way.
 The corresponding normal map can also be safely considered as ground truth.
@@
 
-One important detail that we must care about is the camera exposure.
+One critical detail that we must care about is camera exposure.
 Or we have to control the light radiance on the object surface.
-As shown in figure \ref{fig:camera_exposure}, too less exposure will neutralize the illumination information, which only left ambient light effect.
+As shown in figure \ref{fig:camera_exposure}, too little exposure will neutralize the illumination information, resulting in an ambient light effect.
 Too much exposure makes the surface texture hard to recognize.
-When we did the experiments, we found that a suitable light setting is essential to the illuminated based approach.
-A too much or too less light effects won't improve the illuminated based approach.
+When we did the experiments, we found that a suitable light setting is essential to the illumination-based approach.
+Too much or too few light effects won't improve the illumination-based approach.
 
@@
 \section{Data preprocessing}
-The raw data captured from Unity required further preprocessing before feed them into the training models. 
-A depth map is captured by a depth camera in Unity, which is a 1 channel image that contains the information relating to the distance of the surfaces of the scene objects from a viewpoint.
-It can be saved as a 16-bit grayscale image, i.e.
-each pixel in range $0 - 65535$.
+The raw data captured from Unity required further preprocessing before feeding them into the training models. 
+A depth map is captured by a depth camera in Unity, which is a 1 channel image that contains information relating to the distance of the surfaces of the scene objects from a viewpoint.
+It can be saved as a 16-bit gray-scale image, i.e.
+each pixel in the range $0 - 65535$.
 
-The grayscale image can be used as guided normal inference task and also as a readable scene for human.
-Since the image captured by camera is RGB format, we need to convert it to gray-color for our models.
-It based on following equation
+The gray-scale image can be used as a guided normal inference task and also as a readable scene for humans.
+Since the image captured by the camera is in RGB format, we need to convert it to gray colors for our models.
+It is based on the following equation.
 \[ gray: \frac{R+2G+B}{4}  \]
 
-The normal map is the tangent surface normal, which is saved in 32-bit RGB color image.
-The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on following equation:
+The normal map is the tangent surface normal, which is saved in a 32-bit RGB color image.
+The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on the following equation:
 \begin{dgroup*}
@@
 \label{sec:depth-map-to-point-cloud}
-The depth map can be converted to 3D vertex point cloud as the input of the normal inference model.
+
+The depth map can be converted to a 3D vertex point cloud as the input of the normal inference model.
 
@@
 Consider a 3-dimensional Euclidean space.
-Use $ z $ axis denotes the depth.
-The $ x  $ and $ y $ axis perpendicular with each other.
-For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ with respect to camera coordinate system.
-The $ X $ and $ Y $ can be calculated based on the triangle similarity
+Use $ z $ axis to denote the depth.
+The $ x  $ and $ y $ axis are perpendicular to each other.
+For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ regarding camera coordinate system.
+The $ X $ and $ Y $ can be calculated based on the triangle similarity.
 \begin{dgroup*}
@@
 \end{dgroup*}
-
 where $ fk_u, fk_v $ is the focal length in pixels align $ u $ and $ v $ axes.
-Converted a point from camera coordinate system to world coordinate system, using extrinsic matrix $ R $ and $ t $
+Converted a point from camera coordinate system to the world coordinate system, using extrinsic matrix $ R $ and $ t $
 \[P_W = P_CR+t \]
@@
 %% How to represent input tensor, to make it fast converse
-The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus the normalization is required before feed training objects into the models.
-The data fluctuation in each axis is shown in Figure \ref{fig:data-range}.  Table \ref{tab:data-range} gives a quantitative measurement of corresponding average values.
+The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus normalization is required before feeding training objects into the models.
+We showed the data fluctuation in each axis in Figure \ref{fig:data-range}. Table \ref{tab:data-range} gives a quantitative evaluation of the corresponding average values.
 
 The normalization has been performed as follows.
-First translate the points to the original point as close as possible, then choose the range value of one axis as a scale factor, normalize the points to unit vectors.
+First, translate the points to the original point as close as possible, then choose the range value of one axis as a scale factor, and normalize the points to unit vectors.
 The equation is shown as follows
@@
 \end{dmath*}
-It is calculated as the range in $ X $ axis, but theoretically can be used by $ Y $ or $ Z $ axes as well.
+It is calculated as the range of the $ X $ axis, but theoretically can be used by the $ Y $ or $ Z $ axes as well.
 
@@
 \label{sec:noise}
-The raw depth maps captured by light scanner usually have missing pixels.
-In order to fit well with real-data, the synthetic data has been added uniform distributed noise, which is randomly remove the valid pixels in the maps.
-The simulated noise is distributed evenly around the whole map with a specific noise intensity.
-A parameter $ \mu $ is used to control the intensity of noise, it denotes the $ \mu $-percent pixel dropoff.
+The raw depth maps captured by light scanners usually have missing pixels.
+In order to fit well with real data, the synthetic data has been added uniform distributed noise, which randomly removes the valid pixels in the maps.
+The simulated noise is distributed evenly around the whole map with specific noise intensity.
+A parameter $ \mu $ is used to control the intensity of noise.
+It denotes the $ \mu $-percent pixel drop-off.
 For example, $ \mu-10 $ removes 10\% pixels randomly.
-For each scene, the noising operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used.
-Some scenes have more missing pixels and some have less.
-The random noise intensity also enables the model to learn scenarios not only with noise, but also with minor noise or even without noise.
+For each scene, the noise operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used.
+Some scenes have more missing pixels and some have fewer.
+The random noise intensity also enables the model to learn scenarios not only with noise but also with minor noise or even without noise.
 Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
@@
 \subsection{Fit to PyTorch}
-In order to saving the training time, the dataset is compressed in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
+In order to save training time, we compress the dataset in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
 \begin{table}[H]

### 2022-08-09 paper/Chapters/Chapter01.tex
update paper

@@
 %% main problem, introduce deep learning, UNet
-In 3D computer vision tasks, the \textit{point cloud} ( i.e.
-a great number of point positions on the object surface, these numbers of points altogether, are called point cloud) is a common input data to describe the object surface.
-Based on the geometry information containing in the point cloud, we can acquire the corresponding surface normal, which is an importance features in computer vision, and it can be further used for surface reconstruction, shadings generation and other visual effects.
-A common approach to acquire the surface normal from the point cloud is the optimization approach which consider the neighbor points in the same plane and calculate the plane normal.
-However, for the single input data with only one shot recording, like the depth camera, the acquired point cloud is converted from depth map.
-But due to the optical noises and the reflections in dark and shiny areas of the object surface, the depth map is usually semi-dense only.
-Thus it limited the neighbor based approach since the missing data leads to fewer neighbors of each point.
-However, recent advances in image inpainting areas have motivated researchers to recover the missing regions in the input data using deep neural networks and achieves a good performance.
-For example, \cite{gconv} uses a gated convolution network to inpaint a custom removed areas in the images.
-\cite{nconv} uses normalized convolution network to enhance the semi-dense depth map to fully dense depth map.
-Either work takes in-complete input data and mends it to fully dense output.
-Thus a deep learning based approach can be a way to deal with the semi-dense depth map input for surface normal estimation task.
+
+In 3D computer vision tasks, the \textit{point cloud} (i.e., an unstructured set of 3D points representing the surfaces in the scene) is a common input file to describe the object surface.
+Based on the geometry information in the point cloud, we can calculate the corresponding surface normal, which is an important feature in computer vision.
+The surface normal can be used for surface reconstruction, shading generation and other visual effects.
+The common method for determining the surface normal from the point cloud is the optimization approach, which considers the neighboring points in the same plane and calculates the surface normal.
+
+However, for single input data with only one shot, such as the data acquired by a depth camera, the point cloud is converted from a depth map and the given calibration information.
+In the case of active depth sensors, the depth map is usually only semi-dense due to optical noise and reflections in dark and shiny areas of the object surface, missing many pixels and holes.
+This limits the neighborhood-based approach because the missing data results in a smaller number of neighbors for each point.
+However, recent advances in the field of image inpainting have motivated researchers to use deep neural networks to recover the missing regions in the input data and achieve good performance.
+For example, \cite{gconv} uses a gated convolution network to recover user-defined removed regions in the images.
+\cite{nconv} uses a normalized convolution network to extend the semi-dense depth map to a fully dense depth map.
+In both cases, incomplete input data is used and converted to a fully dense output.
+Therefore, a Deep Learning based approach can be a way to deal with semi-dense depth maps for surface normal estimation tasks.
 
@@
 	\centering
-	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud.png}}
-	{\includegraphics[width=.45\textwidth]{./Figures/point-cloud-zoom-in.png}}
+	\captionsetup{width=\linewidth}
+	{\includegraphics[width=.49\textwidth]{./Figures/point-cloud.png}}
+	{\includegraphics[width=.49\textwidth]{./Figures/point-cloud-zoom-in.png}}
 	\decoRule
-	\caption{Left: A piece of point cloud of the dragon object. Right: Zoom in of the point cloud.}
+	\caption{Left: A portion of the point cloud of the \textit{dragon} object. Right: Zoom in of the point cloud.}
 	\label{fig:point-cloud}
@@
 %% introduce photometric stereo
-Photometric stereo is another approach in computer vision which can be used for surface normal estimation, where the normals are inferred from appearance variations under multiple illuminations.
-The relative methods are typically solve the least square problem based on the point-wise image formation model.\cite{SFS} and based on the Bidirectional Reflectance Distribution Function (BRDF).
-While BRDF based model generally cannot account the global illumination effects and this is usually an unavoidable problem due to the light interactions and difficult traced mathematically.
+Photometric stereo is another approach in computer vision that can be used for estimating surface normals, where the normals are derived from appearance variations under different illuminations.
+The corresponding methods are usually solved using the least squares problem, which is based on the point-wise image formation model \cite{SFS} and on the assumption of the Lambert surface.
+However, the Lambert surface generally cannot account for global illumination effects, which is an unavoidable problem due to light interactions.
 
 %% papers contribution, main work
-Both directions mentioned above have been widely researched using deep learning approaches.
-However, the approach that takes both geometry and illuminated information together into account for normal estimation remains impoverishment.
-We present a deep learning based approach takes both geometry and photometric information into account for normal inference.
-For a practical reason, we consider only 1 illuminated image based on the calibrated camera and takes semi-dense point cloud as input data.
-To achieve this goal, we will mainly take the geometry information into consideration and take the photometric information as a supplementary.
+Both of the above directions have been widely explored using deep learning approaches.
+However, the approach that considers both geometry and illuminated information for normal estimation remains insufficient.
+We present a Deep Learning based approach that considers both geometric and photometric information for normal inference.
+For practical reasons, we consider a semi-dense depth map with only one additional illuminated image based on the calibrated camera as input data to find a compromise between the two methods.
 
 %% introduce the network, trip-net, dataset
-One of our challenges is to apply the semi-dense input data to the neural network in an image-wise way.
-UNet is a good network applying for computer vision tasks with up-sampling requirements.
+One of our challenges is to apply the semi-dense input data to the neural network in an image-aware manner.
+\textit{U-Net} is a good network for computer vision tasks with up-sampling requirements.
 We modified it with a gated activation unit called \textit{gated convolution layer (gconv)} to handle semi-dense input data.
-Another challenge is to merge the different input data feature maps to cooperatively improved the surface normal inference task.
-We propose a $ multi-fusion $ scheme for integration on separate feature map extractors.
-We will show that this multi-fusion design can be taken advantage of by a combination of different input data types and improved surface normal inference performance.
-To train our network, we create a synthetic RGB-D image dataset by utilizing one light source illumination and one ambient light illumination to simulate application scenarios.
-To simulate depth maps in the real world, we applied uniform distributed drop-out noise to the input data with a control parameter for noise density.
+Another challenge is to merge the different feature maps of the input data to cooperatively improve the surface normal inference task.
+We propose a \textit{multi-fusion} scheme for integrating separate feature maps.
+We will show that this \textit{multi-fusion} design can be leveraged by combining different input data types and improving the performance of surface normal inference.
+To train our network, we create a synthetic RGB-D image dataset by using a light source and ambient light illumination to simulate application scenarios.
+To simulate depth maps in the real world, we added uniformly distributed drop-out noise to the input data, with the noise density controlled by a parameter.
 
 %% experiments
-We trained our approach on our proposed synthetic dataset ``synthetic-50-5" and evaluate it on 6 different metrics.
-We compare our approach against the geometry information based approach based on similar network architecture and show that our calibrated illuminated RGB-D image based approach further improved normal accuracy.
-We also applied our model to a real dataset and compare it with the optimization based approach.
+We trained our models on our proposed synthetic dataset \textit{synthetic-50-5} and evaluated them on 6 different metrics.
+The results show that our approach based on calibrated illuminated RGB-D images further improves the normal accuracy.
+We also applied our model to a real dataset and compared it with the optimization-based approach.
 
-The structure of the thesis is as follows, Chapter 1 is the introduction of the whole work.
-Chapter 2 briefly discusses the related work about normal inference.
-Chapter 3 is the main approach of this work.
-Chapter 4 introduces the created dataset for the training work.
-Chapter 5 is the description of the experiments and the evaluation of the models.
-Chapter 6 is the conclusion of the whole thesis.
+The structure of the paper is as follows: In Chapter 2, we briefly discuss related work on the normal inference task.
+Chapter 3 briefly introduces a traditional optimization-based approach and photometric stereo, and then proposes two learning-based approaches for surface normal estimation.
+Chapter 4 presents the dataset created for the training work and its preprocessing.
+Chapter 5 analyzes the experiments and provides both qualitative and quantitative evaluations of the models.
+Chapter 6 is the summary of the entire thesis.

### 2022-08-09 paper/Chapters/Chapter02.tex
update paper

--- 2022-08-06 paper/Chapters/Chapter02.tex
@@
 
-%% depth map approach
-Surface normal inference is a widely researched topic and can be solved in multiple directions.
-Based on a structured point cloud, the surface normal can be derived from geometry information of the point cloud, which mainly utilizes the neighbor information and consider it as an optimization problem (\cite{optimized-methods} ).
-They can perform well on dense point cloud input data based on a well-chosen window size.
-However, the drawbacks are that the algorithms are highly noise sensitive.
-The point cloud is usually not fully dense and normally converted from depth map, which are usually with missing pixels and holes on dark, shinny or transparent regions (\cite{nyu}).
-The missing points destabilizes the geometry based solution.
-To ease this problem, \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix, which is used to smooth the depth data in order to handle the noise of depth image.
-\cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map.
-Some approaches use deep learning method to fill missing areas.
-\cite{nconv} introduces normalized convolution to deal with missing or uncertain depth data with an added mask on the standard convolution operation.
-\cite{ncnn} applied it and use it as normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras.
-\cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.
+Surface normal inference is a widely researched topic and can be solved in several ways.
+Traditionally, it can be derived from a point cloud.
+There are many optimization-based approaches to computing surface normals pixel-by-pixel using neighborhood information.
+\cite{optimized-methods} gives a comparison between some of these approaches.
+\cite{Holzer.S} proposed a method of using local neighbors with an interest parameter $ p $ and derives the surface normal from the eigenvectors of the corresponding covariance matrix.
+These approaches work well for dense input data based on a well-chosen window size.
+However, in many practical datasets such as NYU Depth Dataset V2 \cite{nyu} and KITTI-Depth\cite{kitti-depth}, the point clouds are often converted from depth maps.
+But the depth maps are usually very noisy and contains many missing pixels and holes in dark, shiny, or transparent areas.
+This poses more of a challenge for neighborhood-based approaches, as neighborhood information is not available in many of these areas.
 
-%% photometric approach
-Photometric stereo is another approach that infer surface normal from BRDF based surface model.
-The surface normal is related with observed intensity, the incoming light direction, the outgoing viewing direction and the light intensity.
-It required multiple light conditions to get an optimal solution.
+To solve this problem, some approaches focus on improving the depth map by estimating missing regions.
+\cite{depth-inpainting-distribution} proposed an approach that considers the depth distributions of neighboring regions to fill the holes in the depth map.
+\cite{ncnn} uses a deep learning-based approach for painting semi-dense depth maps, which mainly uses the normalized convolution proposed by \cite{nconv}.
+This approach considers a 0-1 mask to distinguish valid and invalid data points.
+\cite{pncnn} improved this approach by proposing an input confidence estimation network to replace the binary mask with an estimated confidence mask.
+\cite{depth-enhance-guided} also uses a normalized convolution for inpainting the depth map and also uses an RGB image as a guidance.
 
-%% fusion approach
+On the other hand, some of the approaches use RGB-D images to estimate the surface normal or use RGB images to estimate the fully dense depth map.
+\cite{Eigen} proposed a two-level network for predicting the depth map based on RGB images, where the global and local features of the object are considered separately.
+\cite{img2depth} also predicts the depth map from the image, using a residual network for feature extraction and developing an up-sampling part with the un-polling layers.
+\cite{binsformer} proposed a method that adaptively generates depth map prediction information based on RGB images. 
+\cite{geometry_based_solution} uses RGB-D images to estimate surface normals.
+It proposes a method for learning discriminative and geometrically informative primitives from RGB-D images, which is then used to recover the surface normals of a scene from a single image.
+\cite{GeoNet} uses ResNet \cite{resnet} to derive a coarse surface normal from an RGB image, and refines it using a depth map based on the \cite{geometry_based_solution} method. 
+\cite{hfm} derives surface normals based on an RGB-D image using the \textit{U-Net} architecture.
 
-%% talk about gated convolution, Unet
+However, these approaches mainly rely on RGB images as input for estimating the normal or the full depth map.
+The applied scenarios are mainly indoor scenes such as bedrooms or offices, where the focus is not on the fine details of the object surface, but only on the main directions of each area, such as the directions of the floor, walls, or seats, etc as shown in Figure \ref{fig:dataset-comparison}
 
-%% in summary
+\begin{figure}[h!]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/nyu_depth_v2_img.jpg}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/nyu_depth_v2_depth.jpg}
+	\caption{}
+\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/train-image.png}
+	\caption{}
+\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/train-depth-noise.png}
+	\caption{}
+\end{subfigure}
+	\decoRule
+	\caption{(a)-(b): Output from the RGB camera (a) and depth camera (b) of a scene in \textit{NYU Depth Dataset V2} \cite{nyu}.
+(c)-(d): Output from the gray-scale camera (c) and depth camera (d) of a scene in our proposed dataset \textit{synthetic-50-5}.}
+	\label{fig:dataset-comparison}
+\end{figure}
+%% Photometric Stereo
+Photometric stereo is another approach that derives the surface normal from the BRDF-based surface model.
+The surface normal is related to the observed intensity, the direction of incident light, the direction of outgoing light, and the light intensity.
+Several light conditions are required to obtain an optimal solution.
+\cite{CNN-PS} uses a CNN-based approach to learn the relationship between photometric stereo input and the surface normal under hundreds of lighting conditions, which is also robust to the effects of global illuminations.
+\cite{spline-net} is based on an illumination interpolation network to use only a sparse set of lights for photometric stereo tasks.
 
-\paragraph{Unstructured Point Cloud Based}
-For the unstructured point cloud, the neighbor information of each point is usually unknown.
-K-nearest neighbor (KNN) is a common algorithm for neighbor searching.
-With knowing this information, the neighbor based approaches can be used as a second step.
-However, KNN-method merely based on the Euclidean distance in the 3D space.
-Therefore, the points of the other surfaces but in a close distance will also be considered as neighbors.
-To ease this problem, \cite{unstructed-pc} proposed a method based on unstructured point cloud with selecting the optimal scale around each point for normal estimation.
-To calculate the normals of multiple points in parallel \cite{unstructed-pc-patch-stitching} processes a series of overlapping patches for normal estimation.
-
-Deep learning based methods take single RGB image or RGB-D image as the input for normal estimation.
-It has a strong relationship with the depth inference tasks, two benchmarks are highly used in these area.
-(\cite{nyu} and \cite{kitti-depth}) Based on the input of training model, the methods can be roughly divided as follows:
-
-\paragraph{RGB based} RGB based methods predict the depth map diretly from single RGB image.
-\cite{Eigen} proposed a two staged network for depth map prediction based on RGB image, which consider the global features and the local features respectively.
-\cite{img2depth} employed Residual Network for the feature extraction and further designed a upsampling part which replace the fully-connected layer with the unpolling layers.
-\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.
-\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.
-\cite{binsformer} proposed a method achieved state of art in NYUv2 Dataset (\cite{nyu}), which adaptively generate information to predict depth maps based on RGB image.
-
-\paragraph{RGB-D based}
-\cite{hfm} based on UNet architecture for normal estimation using RGB-D image as input.
-The RGB image and depth map are in the separate branches and imply a fusion module in four sections of the network to concatenate two branches.
-It also considers the confidence of the values in depth map.
-
-\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.
+Our approach uses an RGB-D image but known light direction and calibrated information for surface normal inference, which considers multiple input data types into account for the estimation.

### 2022-08-09 paper/Chapters/Chapter04.tex
update paper

@@
 
-\section{Resource}
+\section{Data Resources}
 The object model we used are searched from internet.
-A set of point cloud datasets for computer vision research has been published by /cite[data1], /cite[data2], /cite[data3] and /cite[data4].
+A set of point cloud datasets for computer vision research has been published by \cite{data1}, \cite{data2}, \cite{data3} and \cite{data4}.
 These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing.
@@
 	\decoRule
+	\caption{Point clouds scanned by high resolution scanners}
 	\label{fig:dataset-demo}
-	\caption{Point clouds scanned by high resolution scanners}
 \end{figure}
@@
 	\textcolor{#1}{\vrule width 0.5cm}}
-\section{Synthesize Scenes using Unity}
+\section{Synthesizing Scenes using Unity}
 In order to simulate the data collection scenario close to the real world as much as possible.
@@
 
-\section{Data preprocessing}
+\section{Data Preprocessing}
 The raw data captured from Unity required further preprocessing before feeding them into the training models. 
-A depth map is captured by a depth camera in Unity, which is a 1 channel image that contains information relating to the distance of the surfaces of the scene objects from a viewpoint.
-It can be saved as a 16-bit gray-scale image, i.e.
-each pixel in the range $0 - 65535$.
+\paragraph{Depth Map}
+A depth map is captured by the depth camera in Unity, which is a 1 channel image that contains information relating to the Z-axis distance from object surface to the camera.
+It is saved as a 16-bit gray-scale image, i.e.
+each pixel in the range $\mathtt{0 - 65535}$.
 
-The gray-scale image can be used as a guided normal inference task and also as a readable scene for humans.
-Since the image captured by the camera is in RGB format, we need to convert it to gray colors for our models.
-It is based on the following equation.
-\[ gray: \frac{R+2G+B}{4}  \]
+The raw depth maps in real data that captured by light scanners usually have missing pixels.
+In order to fit well with real data, the synthetic data has been added uniform distributed noise, which randomly removes the valid pixels in the maps.
+The simulated noise is distributed evenly around the whole map with specific noise intensity.
+A parameter $ \mu $ is used to control the intensity of noise.
+It denotes the $ \mu $-percent pixel drop-off.
+For example, $ \mu-10 $ removes 10\% pixels randomly.
+For each scene, the noise operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used.
+Some scenes have more missing pixels and some have fewer.
+The random noise intensity also enables the model to learn scenarios not only with noise but also with minor noise or even without noise.
+Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
+%% add noise image
+\begin{figure}[!h]
+	\centering
+	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
+	\decoRule
+	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
+	\label{fig:noise-intensity}
+\end{figure}
 
-The normal map is the tangent surface normal, which is saved in a 32-bit RGB color image.
-The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on the following equation:
-\begin{dgroup*}
-	\begin{dmath*}
-		n_x = \frac{R}{255} * 2 - 1
-	\end{dmath*}
-	\begin{dmath*}
-		n_y = \frac{G}{255}*2 - 1
-	\end{dmath*} 
-	\begin{dmath*}
-		n_z = 1-\frac{B}{255} * 2
-	\end{dmath*}
-\end{dgroup*}
-
-If consider the relation between Lambertian reflection and normal direction, the light source can be used to calculate the reflect direction of each point.
-
-The camera intrinsic and extrinsic matrix helps point cloud calculation.
-
-\subsection{Convert to Point Cloud}
-\label{sec:depth-map-to-point-cloud}
-
-The depth map can be converted to a 3D vertex point cloud as the input of the normal inference model.
-
+The depth map is further converted to 3D vertex map after adding the noise.
 \begin{figure}[h!]
@@
 For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ regarding camera coordinate system.
-The $ X $ and $ Y $ can be calculated based on the triangle similarity.
+Knowing $ Z $, corresponding depth map pixel $ D(u,v) $ and the camera focal length in pixels $ fk_u, fk_v $, the other two component  $ X $ and $ Y $ in the 3D space can be calculated based on the triangle similarity.
+
 \begin{dgroup*}
@@
 \end{dgroup*}
-where $ fk_u, fk_v $ is the focal length in pixels align $ u $ and $ v $ axes.
-Converted a point from camera coordinate system to the world coordinate system, using extrinsic matrix $ R $ and $ t $
+Convert a point from camera coordinate system to the world coordinate system, using extrinsic matrix $ R $ and $ t $
 \[P_W = P_CR+t \]
 
-\subsection{Point Cloud Normalization}
-\label{sec:dataset-normalization}
 %% How to represent input tensor, to make it fast converse
-The sizes of each training object are various, whereas it should be as an invariant value for the training model. Thus normalization is required before feeding training objects into the models.
-We showed the data fluctuation in each axis in Figure \ref{fig:data-range}. Table \ref{tab:data-range} gives a quantitative evaluation of the corresponding average values.
+The sizes of each training object are various, we normalized them to an unit scale thus they has relatively similar distance to the camera.
+We showed the value fluctuation in each axis in Figure \ref{fig:data_range} before normalization. Table \ref{tab:data_range} gives a quantitative evaluation of the corresponding average values.
 
@@
 \end{dmath*}
-It is calculated as the range of the $ X $ axis, but theoretically can be used by the $ Y $ or $ Z $ axes as well.
+which is calculated as the range of the $ X $ axis, but theoretically can be used by the $ Y $ or $ Z $ axes as well.
 
@@
 	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
-	\label{fig:data_range}
 	\decoRule
 	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
+	\label{fig:data_range}
 \end{figure}
@@
 \begin{table}[th]
-	\label{tab:data-range}
+
 	\centering
@@
 		\bottomrule
-
 	\end{tabular}
 	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. }
+	\label{tab:data_range}
 \end{table}
 
-\subsection{Noise}
-\label{sec:noise}
-The raw depth maps captured by light scanners usually have missing pixels.
-In order to fit well with real data, the synthetic data has been added uniform distributed noise, which randomly removes the valid pixels in the maps.
-The simulated noise is distributed evenly around the whole map with specific noise intensity.
-A parameter $ \mu $ is used to control the intensity of noise.
-It denotes the $ \mu $-percent pixel drop-off.
-For example, $ \mu-10 $ removes 10\% pixels randomly.
-For each scene, the noise operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used.
-Some scenes have more missing pixels and some have fewer.
-The random noise intensity also enables the model to learn scenarios not only with noise but also with minor noise or even without noise.
-Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
-%% add noise image
-\begin{figure}[!h]
-	\centering
-	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
-	\decoRule
-	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
-	\label{fig:noise-intensity}
-\end{figure}
+\paragraph{Image}
+The gray-scale image can be used for photometric stereo approach and also as a readable information for humans.
+Since the image captured by the camera is in RGB format, we need to convert it to gray colors to fit our models.
+It is based on the following equation.
+\[ gray: \frac{R+2G+B}{4}  \]
 
-\subsection{Fit to PyTorch}
+\paragraph{Normal Map}
+The normal map is the tangent surface normal, which is saved in a 8-bit/channel RGB image.
+The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on the following equation:
+\begin{dgroup*}
+	\begin{dmath*}
+		n_x = \frac{R}{255} * 2 - 1
+	\end{dmath*}
+	\begin{dmath*}
+		n_y = \frac{G}{255}*2 - 1
+	\end{dmath*} 
+	\begin{dmath*}
+		n_z = 1-\frac{B}{255} * 2
+	\end{dmath*}
+\end{dgroup*}
+
 In order to save training time, we compress the dataset in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.

### 2022-08-09 paper/Chapters/Chapter05.tex
update paper

@@
 The models are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
-Each scene has a depth map with dimension $ 128\times 128 $ in height and width, an image with dimension $ 128\times 128 \times 1 $.
-The depth map is converted to 3D vertex map as introduced in Chapter \ref{ch:04}.
+Each scene has a depth map with dimension $ 128\times 128 $ in height and width, an image with dimension $ 128\times 128 $.
+The depth map is converted from 3D vertex map as introduced in Chapter \ref{ch:04}.
 The light map is calculated based on vertex map and the known light position.
 We create a tensor in PyTorch that includes vertex map, image and the light direction for each scene and considered it as one training case.
-Thus 3000 scenes has corresponding 3000 training cases.
+Thus 3000 scenes correspond 3000 training cases.
 Each scene has a corresponding ground-truth normal map for loss calculation and the evaluation.
+Figure \ref{fig:test-scene} shows some of the training cases.
+Note that the position of objects are not placed always naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
 
@@
 
-The training processes are evaluated in every epochs with 100 evaluation scenes that models never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set.
-Figure \ref{fig:test-scene} shows some of the test scenes during the training work.
-Note that the position of objects are not placed always naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
+Besides the 3000 training scenes, 100 extra scenes containing 5 different object models are as evaluation dataset during the training. They are evaluated in each epoch.
 
 For the training parameters, we set the training pipeline with batch size $ 8 $, we found that a higher batch size will reduce the final performance.
-Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5.
+Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, it will decay at epoch 8 with learning decay factor 0.5.
 The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTXA 6000.
 It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
-We terminate the training when the evaluation on the test dataset converged.
+We terminate the training when the angle error of the normal map stop decreasing.
 
@@
 The architecture is described in \ref{sec:gcnn}.
-We use a single GCNN to estimate the surface normal based on geometry information.
+We use a single GCNN to estimate the surface normal as a geometry based approach.
 It uses vertex map as input to estimate the corresponding tangent surface normal map.
@@
 The first model, we replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same, and give it a name ``CNN".
-It is used to verify the performance the gated convolution layers.
+It is used to compare the performance between gated convolution layer and standard convolution layer for our normal inference task.
 As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
@@
 Is is designed to show to which content will skip connection help the model performance.
-We use Reversed Huber Loss as loss function during the training, since we found it gives a better final error compare to L2 loss.
+We use Reversed Huber Loss as loss function during the training.
+We found it gives a better final error compare to L2 loss.
 
@@
 When we train this model, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
-Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
+We also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
 A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
 We evaluate the fusion times from 1 to 4.
-For the learning rate.
-we set $ 1e-3 $.
+For the learning rate, we set it as $ 1e-3 $.
 It goes well with GCNN model but lead to loss explosion in Trip-Net.
@@
 
-We also found that, trip-Net with four times fusion converges obviously faster than fewer fusion times model.
+During the training we found that trip-Net with four times fusion converges obviously faster than fewer fusion times model.
 However, model F3 with 3 times fusion converge slower than F4 but in the end it achieves a similar evaluation loss with F4(see Qualitative evaluation).
-The F1 and F2 models are relatively weaker than the other two models.
-
-However, the sacrifice of accuracy gives a relatively lighter model.
-Since we remove the fusions between different pipes, the corresponding upsampling layers in the image and light pipes can also be removed.
-The model can be trained faster and the size is reduced as well.
+The F1 and F2 models are relatively less accurate than the other two models, but the sacrifice of accuracy gives a relatively lighter model.
+Since they have less fusion times, the corresponding upsampling layers in the image and light pipes can also be removed.
+The model can be trained in a faster way and the size is reduced as well.
 Table \ref{tab:trip-net-size-compare} gives a comparison of the size and training time among different models.
@@
 
-\section{Quantitative Evaluation}
+\section{Quantitative Evaluation on 6 Metrics}
 We evaluated our models on synthetic dataset with resolution $ 128\times 128 $. 
@@
 Note that the input vertex map is only semi-dense.
-One of the benefit of GCNN architecture is the robust to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
+One of the benefit of GCNN architecture is the robustness to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
 
 \paragraph{Average Angle Error Metric}
-The metric calculate the average angle error for each point between the inferred normal and ground-truth normal. 
+The metric calculate the average angle error for each point between the inferred normal and ground-truth normal map. 
 \paragraph{Median Angle Error Metric}
@@
 
-We evaluate the trained models on ``synthetic-50-5".
+We evaluated our trained models on ``synthetic-50-5".
 5 objects are considered in the test dataset.
@@
 In the 30 degrees error metric, GCNN based approach achieves 95 \% accuracy whereas Trip-Net is even higher, some of the models like $ dragon $ achieves 98\%.
-The best performance is around 90\%, 75 \%, 45 \% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metric respectively.
+The best performance is around 90\%, 75 \%, 45 \% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metrics respectively.
 Another notable result is the close performance of F3 and F4 models, where they achieves a very comparable performance.
@@
 However, based on the$ 30^\circ $, $ 22.5^\circ $, $ 11.5^\circ $ metrics, we can still see that F4 model gives a more stable performance with less high error normals.
-This is reasonable since the last fusion in the original resolution provides more high resolution information to the model.
+This is reasonable since the last fusion in the original resolution provides more high resolution information to the models.
 
@@
 %% svd evaluation
-\section{Visual evaluation on SVD}
+\section{Visual Evaluation on SVD}
 
@@
 	\centering
-	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
-	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
-	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}
+	\includegraphics[width=.32\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
+	\includegraphics[width=.32\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
+	\includegraphics[width=.32\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}
 	\decoRule
+	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5. \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
 	\label{fig:svd-normal}
-	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5 \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
 \end{figure}
-The neighbor based method is depended on a well-chosen parameter $ k $.
+The SVD approach is depended on a well-chosen parameter $ k $.
 Figure \ref{fig:svd-k-eval} shows the evaluation on different $ k $ values.
@@
 	\centering
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
 	\decoRule
+	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
 	\label{fig:svd-k-eval}
-	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
-	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
+	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
 	\decoRule
+	\caption{SVD visual evaluation on a noised dragon model ($ 128\times128 $)}
 	\label{fig:svd-noise}
-	\caption{SVD visual evaluation on a noised dragon model ($ 128\times128 $)}
 \end{figure}
 
-\section{Visual evaluation on GCNN model}
+\section{Visual Evaluation on GCNN}
 A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
@@
 A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
-In the same case, NOC model as shown in Figure.
-\ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
+In the same case, NOC model as shown in Figure \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
 CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
 Besides, the sharp area like the hindleg and the head area of dragon object, CNN model gives a much brighter error map (which means a higher angle error).
+Figure \ref{fig:gcnn-eval-more} shows more evaluation on GCNN model.
 
-Figure \ref{fig:gcnn-eval-more} shows more evaluation on GCNN model.
-Although we can get a good result from GCNN model but from model ``Washington" we still can see it lacks the sharpness in the detail area like the face and clothes area.
+We can get a good result from GCNN model, but from model ``Washington" we still can see it lacks the sharpness in the detail area like the face and clothes area.
 
@@
 
-\section{ Discussion about the feature maps of GCNN architecture models}
+\section{Discussion on the Feature Maps in GCNN}
 
-As shown in figure \ref{fig:gcnn-cnn-feature map}, we also visualize the feature maps of the last gated convolution layer in the first up-sampling part for CNN and GCNN models, which corresponding the feature maps with size $ 32\times 32 $ in width and height.
+As shown in figure \ref{fig:gcnn-cnn-feature map}, we also visualize the feature maps of the last gated convolution layer in the first up-sampling part for CNN and GCNN models, which corresponding the 128 feature maps with size $ 32\times 32 $ in width and height.
 The input data is also same dragon object that we used for normal visualization.
 For each feature map, we map the minimum value to the left-most color in the color bar and the maximum value to the right-most color in the color bar.
-We want to discuss the the different of the feature maps between CNN, NOC and GCNN models.
+We want to discuss the the difference of the feature maps between CNN, NOC and GCNN models.
 
-In order to see the result clearly, we use one color for the feature map visualization and use the brightness to distinguish the scale of the vales, the white corresponds 1, the black corresponds 0, green color corresponds some value in between.
+In order to see the result clearly, we use one color for the feature map visualization and use the brightness to distinguish the scale of the values, the white corresponds 1, the black corresponds 0, and the green-hue colors corresponds some values in between.
 
-From the CNN feature maps, we can see that the brightness areas are distributed all around the feature maps.
-For the GCNN feature maps, the brightness areas are usually concentrate only in few pixels.
-If we map the brightness areas to the original image, they correspond to the dense sharp edges areas, which is usually the hardest areas for normal estimation task.
-We suspect that these feature maps are the detail feature maps that extract from sharp edges.
+From the CNN feature maps, we can see that the high value areas are usually more than one in a single feature map. Many of them have more than two bright areas. 
+ For the GCNN feature maps, the brightness areas are usually concentrate only in one area or even one point.
+If we map the brightness areas to the original image, they correspond to the dense sharp edges areas, like mouse, horn, or tail of the dragon object, which is usually the hardest areas for normal estimation task.
+We suspect that these feature maps with few bright areas or only one bright area are the detail feature maps that for sharp edges inference.
 Based on this assumption, we can say that gated convolution layer describes the detail features in a more accurate way compare to standard convolution layer, since the brightness areas is smaller.
@@
 
-Second, for the GCNN model,  we observed that some feature maps have no  small bright areas but bright areas distributed evenly on the whole object.
-Some of the feature maps has a overall medium value some has a value close to 1.
-Nevertheless, these feature maps are different from the detail feature maps with only few pixels with high values(brightness).
-We suspect that these features maps provides an over-view of the objects for a coarse prediction.
-So that they can cooperate with detail feature maps to sharpen the prediction.
-It also holds for NOC model, since it does not equip with skip connection, most of the feature maps are global feature maps with an evenly bright feature maps, so that the corresponding normal maps predicted by NOC model are more coarse.
+Second, for the GCNN model,  we observed that some feature maps have very evenly bright areas distributed on the whole object.
+They are either overall dim or overall bright.
+Nevertheless, these feature maps are different from the detail feature maps with only few pixels with high values(brightness) but most of the other pixels with relatively low values.
+We suspect that these evenly value distributed features maps are the global feature maps that provide an over-view of the objects for a coarse prediction.
+So that they can cooperate with detail feature maps and further used to sharpen the prediction.
+It also holds for NOC model, since it does not equip with skip connections, most of the feature maps are global feature maps, so that the corresponding normal maps predicted by NOC model are more coarse than the GCNN model.
 For the CNN model, there also exists global feature maps, however, they are mostly incomplete, either missing the tails or missing the paws.
 Actually, these missing areas can usually be found in the detail feature maps.
-This also explained why the CNN detail feature maps has too much brightness areas, the detail feature maps and global feature maps are mixed together.
-And this unclear feature map extractor leads to the weak performance on normal estimation.
+This also explained why the CNN detail feature maps has several bright areas in their detail feature maps.
+The detail feature maps and global feature maps are mixed together.
+And this unclear feature map extractor leads to reduce the performance on normal estimation task.
 
@@
 		\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[text width=0.1\textwidth] at (11,-1) {1};
 		\node[inner sep=0pt] (input) at (8,-1)
 		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
-		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
 	\end{tikzpicture}
@@
 \newpage 
-\section{Visual evaluation on Trip-Net models }
+\section{Visual Evaluation on Trip-Net}
 
@@
 We also use the same input as we did in GCNN evaluation.
-The error of Trip-Net is 6 degree whereas the GCNN is 9.
+The error of Trip-Net is $ 6^\circ $ whereas the GCNN is $ 9^\circ $.
 
@@
 All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
-It seems that the illumination helps the model to learn sharper features in the network.
+
+Figure \ref{fig:tripnet-fusion-eval} compares different fusion times on Trip-Net model.
+We can see that model F1 with one fusion and and F2 with two fusions did not achieve a better result compare to GCNN model, which means the illuminated information doesn't work if we only consider the lower resolution feature maps.
+F3 model with 3 times fusion and F4 model with 4 times fusion give a much better result and also beyond the GCNN model.
+These two times fusion include high resolution features in the last up-sampling and the final output-size features before the standard convolution layers.
+We can observe the dragon scale in the figures, they are much sharper in the last two images.
 
@@
 	\caption{Comparison between different fusion times on Trip-Net Architecture ($ 128\times128 $). }
-	\label{fig:tripnet-eval-synthetic-zoom-in}
+	\label{fig:tripnet-fusion-eval}
 \end{figure}
 
-\section{Trining on higher resolution}
-We also prepared the dataset with resolution $ 512\times 512 $ for model evaluation.
-Higher resolution gives more information about the surface feature using the same model compare to lower resolution.
+\section{Trining on Higher Resolution}
+We also trained our models on a higher resolution dataset with $ 512\times 512 $ in width and height for each scene.
+Higher resolution data gives more information about the surface feature using the same model compare to lower resolution.
 The benefit is, if we extract a fixed sized patch from the normal map, say $ 32 \times 32 $, it might correspond a hindleg area of the dragon object in $ 128\times 128 $ resolution but maybe only a toe in $ 512\times 512 $ resolution.
 Therefore if we still use the same kernel size in the network for the same dataset, (like we did with $ 3\times 3 $) the higher the resolution it has, the less area it will cover.
-Thus the surface will more smooth and easy to calculate the surface normal.
+Thus the surface in the same window size will more smooth and easy to be calculated the surface normal.
 This is a good thing.
@@
 But in $ 128\times128 $ resolution image, the same area $ 32\times32 $ might corresponding to entire  hindleg of the dragon object.
-In another word, we can also say that the higher resolution ``smooth" the object surface.
-Thus the higher resolution helps the model to calculate a more accurate normal map.
+In another word, we can also say that the higher resolution ``smooth" the object surface within the same size area.
+Thus the higher resolution helps the model to calculate a more accurate normal maps.
 
@@
 
-\newpage 
 %% high resolution trip-net visualization
@@
 A quantitative evaluation is shown in table \ref{tab:high_resolution_eval}.
-It follows the same performance rank compare to lower resolution, which is GCNN better than SVD approach and Trip-Net slightly better than GCNN.
-The accuracy is 99 \% in the $ 30^\circ $ metric for Trip-Net and $ 5^\circ $ mean error.
-A qualitative evaluation is shown in figure \ref{fig:trip-eval-high-resolution}, this is a figure object with both smooth area (the belly and arm) and highly detailed area with sharp surface (the uneven surface of stone table).
-Our models gives an average degree area at $ 5^\circ $.
+It follows the same performance ranking compares to lower resolution, which is GCNN better than SVD approach and Trip-Net slightly better than GCNN.
+The accuracy is 99 \% in the $ 30^\circ $ metric.
+In mean error metric, the error is  $ 5^\circ $.
+A qualitative evaluation is shown in figure \ref{fig:trip-eval-high-resolution}.
+We use a figure object with both smooth area (the belly and arm) and highly detailed area with sharp surface (the uneven surface of stone table) for evaluation.
+Our models gives an  $ 5^\circ $ in mean degree metric.
+
 A comparison with other models is shown in figure \ref{fig:trip-eval-compare}.
-
-Another remarkable result is the SVD approach, which also gives a good result ($ 8.88^\circ $ in mean degree metric).
-Like we discussed, the surface are relative more smooth if we keep the same window size for normal inference.
-In the high resolution scenes, although the percentage of missing pixels in a fixed windows are remain the same compare to small resolution scenes, but the remain valid pixels are mainly on a relatively flat plane thus they are good enough for an accurate normal inference.
-Consequently, we can see from the error map in Figure \ref{fig:high_resolution_eval}, the sharp edges of the dragon, like the horns and the hindlegs, the SVD approach still has high errors.
+Note that we use the same dragon object (but slightly moved the place since they have been captured in different time in high resolution dataset) for evaluation this time as a coherent comparison with low resolution dataset.
+The SVD based approach gives a good result ($ 8.88^\circ $ in mean degree metric).
+Like we discussed, the surface are relatively more smooth if we keep the same window size for normal inference.
+In the high resolution scenes, although the percentage of missing pixels in a fixed windows are remain the same compare to small resolution scenes, but the remain valid pixels in the same window size are on a relatively flat plane thus they are good enough for an accurate normal inference.
+However, as we expected, we can still see the high degree error in the sharp edges of the dragon object, like the horns and the hindleg areas as shown in \ref{fig:trip-eval-compare}.
 
@@
 \section{Training on Real-Dataset}
-We also applied our model on a dataset that captured by a light scanner in our laboratory in order to see the applicability of our approaches.
-For the geometry information based approach, we directly use the GCNN model that trained on synthetic dataset, since it only require the depth map as input, the scenarios of two dataset are the same.
+We also applied our model on a dataset that captured by a light scanner in our laboratory in order to see our model's applicability to the real-dataset.
+For the geometry information based approach, we directly use the GCNN model that trained on synthetic dataset since it only require the depth map as input, the scenarios of two dataset are the same.
 For the illuminated calibrated RGB-D image based approach, the model has to be refined based on the real-dataset, since the light intensity and position, camera matrix are different.
@@
 	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes in real dataset.}	
-	\label{tab:high_resolution_eval}
+	\label{tab:real_eval}
 \end{table}
@@
 The folds on the gowns are recognizable and even countable.
-\ref{fig:real_eval_compare} compares the Trip-Net with other approaches.
+Figure \ref{fig:real_eval_compare} compares the Trip-Net with other approaches.
 
-But we also noted that the big holes in the base stage remains in the depth maps.
-These big holes corresponds to the shinny and dark texture area, which common exists in the depth map captured by the scanners.
-Since these big holes are related with only special feature areas and also has irregular shapes, we didn't simulate this type of noise in the synthetic dataset but only with a random binary mask.
+But we also noted that the big holes in the base stage remains in the normal maps.
+These big holes corresponds to the shinny and dark texture area, which common exist in the depth map captured by the scanners.
+Since these big holes are related with only special feature areas and also has irregular shapes, we didn't simulate this type of noise in the synthetic dataset but only with a sparse binary mask.
 Thus our models failed to mend missing big holes in the estimated normal map.
-This can be a further direction of this topic, that find a way to generate high similar depth map noise to get a more robust training dataset.
+This can be a further work of this topic, that find a way to generate high similar depth map noise to get a more robust training dataset.
 

### 2022-08-09 paper/main.tex
update paper

@@
 \usepackage{amssymb}
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles \left( APA)
+%\usepackage[backend=bibte,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles \left( APA)
+
+\usepackage[backend=bibtex,style=numeric]{biblatex}
 
 \addbibresource{example.bib} % The filename of the bibliography
-
 \usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
@@
 \usepackage{rotating}
+\usepackage{caption}
+\captionsetup[figure]{font=normalsize,labelfont=normalsize}
+\captionsetup{justification   = raggedright,
+	singlelinecheck = false, width=\linewidth}
 \usetikzlibrary{fit}
@@
 \university{\href{https://www.uni-kl.de/}{Technische Universität Kaiserslautern}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
-\department{\href{https://www.informatik.uni-kl.de/}{German Research Center for Artificial Intelligence}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+\department{\href{https://www.informatik.uni-kl.de/}{Department of Computer Science}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
 \group{\href{https://av.dfki.de/}{Augmented Vision}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
-\faculty{\href{http://faculty.university.com}{Faculty Name}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
+\faculty{\href{https://av.dfki.de/}{Augmented Vision}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
 
@@
 \begin{flushright} \large
-\emph{Supervisor:} \\
+\emph{Supervisors:} \\
 \href{https://av.dfki.de/members/stricker/}{\supname}\\
@@
 
-\groupname\\\deptname\\ % Research group name and department name
+\groupname\\
+\deptname\\ % Research group name and department name
 \includegraphics{Figures/TUK_LOGO_RGB}\\[2cm] % Research group name and department name
@@
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-We proposed a learning based approach for surface normal estimation based on illuminated calibrated RGB-D image. 
-Different with other methods, the approach not only base on geometry information, but also takes the photometric stereo approach into account, which use calibrated illuminated image to further improve the performance.
+In this work, a learning based approach for surface normal estimation based on illuminiated calibrated RGB-D images is proposed.
+
+This approach extends the geometry based approach by techniques of photometric stereo, which uses calibrated illuminated images for normal estimation. 
 The two types of data gives a superior performance on normal inference task.
-One of the key points of our approach is, the proposed method require only one light source for each scene capture instead of multiple light positions, which can be very easy to configure in the practice.
+One of the key points of our approach is, the proposed method require only one light source for each scene capture instead of multiple light sources, which can be very easy to configure in the practice.
 
-Our model is trained on a  gated convolution neural network called (Trip-Net).
-The gated convolution design is supposed to handle the semi-dense depth map input, which is a common artefact by the depth sensor.
-Furthermore, a dataset based on 55 point clouds called ``synthetic-50-5“ in created for training.
-We trained our model on this synthetic dataset then further applied it to real dataset.
-A qualitative and quantitative evaluation is reported in the end.
+Our model is trained on a gated convolution neural network (Trip-Net).
+The gated convolution design is intended to handle the missing pixels in the depth map, which is a common defect of the depth sensor.
+We also created a dataset of 55 point clouds called \textit{Synthetic-50-5} for training.
+We trained our model on this synthetic dataset and then applied it to a real dataset.
+Finally, a qualitative and quantitative evaluation is performed.
+
 \end{abstract}
@@
 
-\begin{acknowledgements}
-\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
-The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
-\end{acknowledgements}
+%\begin{acknowledgements}
+%\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
+%The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
+%\end{acknowledgements}
 
@@
 \tableofcontents % Prints the main table of contents
-
-\listoffigures % Prints the list of figures
-
-\listoftables % Prints the list of tables
 
@@
 %----------------------------------------------------------------------------------------
-
-\dedicatory{To my fire}
+%
+%\dedicatory{To my fire}
 
@@
 %\include{Appendices/AppendixC}
-
+\listoffigures % Prints the list of figures
+\listoftables % Prints the list of tables
 %----------------------------------------------------------------------------------------

### 2022-08-09 paper/presentation/template.tex
update paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 2.0 (March 8, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	11pt, % Set the default font size, options include: 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, 20pt
	%t, % Uncomment to vertically align all slide content to the top of the slide, rather than the default centered
	%aspectratio=169, % Uncomment to set the aspect ratio to a 16:9 ratio which matches the aspect ratio of 1080p and 4K screens and projectors
]{beamer}

\graphicspath{{Images/}{./}} % Specifies where to look for included images (trailing slash required)

\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule for better rules in tables

%----------------------------------------------------------------------------------------
%	SELECT LAYOUT THEME
%----------------------------------------------------------------------------------------

% Beamer comes with a number of default layout themes which change the colors and layouts of slides. Below is a list of all themes available, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

%----------------------------------------------------------------------------------------
%	SELECT COLOR THEME
%----------------------------------------------------------------------------------------

% Beamer comes with a number of color themes that can be applied to any layout theme to change its colors. Uncomment each of these in turn to see how they change the colors of your selected layout theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{monarca}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{spruce}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%----------------------------------------------------------------------------------------
%	SELECT FONT THEME & FONTS
%----------------------------------------------------------------------------------------

% Beamer comes with several font themes to easily change the fonts used in various parts of the presentation. Review the comments beside each one to decide if you would like to use it. Note that additional options can be specified for several of these font themes, consult the beamer documentation for more information.

%\usefonttheme{default} % Typeset using the default sans serif font
%\usefonttheme{serif} % Typeset using the default serif font (make sure a sans font isn't being set as the default font if you use this option!)
%\usefonttheme{structurebold} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in bold
%\usefonttheme{structureitalicserif} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in italic serif
\usefonttheme{structuresmallcapsserif} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in small caps serif

%------------------------------------------------

%\usepackage{mathptmx} % Use the Times font for serif text
\usepackage{palatino} % Use the Palatino font for serif text

%\usepackage{helvet} % Use the Helvetica font for sans serif text
\usepackage[default]{opensans} % Use the Open Sans font for sans serif text
%\usepackage[default]{FiraSans} % Use the Fira Sans font for sans serif text
%\usepackage[default]{lato} % Use the Lato font for sans serif text

%----------------------------------------------------------------------------------------
%	SELECT INNER THEME
%----------------------------------------------------------------------------------------

% Inner themes change the styling of internal slide elements, for example: bullet points, blocks, bibliography entries, title pages, theorems, etc. Uncomment each theme in turn to see what changes it makes to your presentation.

%\useinnertheme{default}
\useinnertheme{circles}
%\useinnertheme{rectangles}
%\useinnertheme{rounded}
%\useinnertheme{inmargin}

%----------------------------------------------------------------------------------------
%	SELECT OUTER THEME
%----------------------------------------------------------------------------------------

% Outer themes change the overall layout of slides, such as: header and footer lines, sidebars and slide titles. Uncomment each theme in turn to see what changes it makes to your presentation.

%\useoutertheme{default}
\useoutertheme{infolines}
%\useoutertheme{miniframes}
%\useoutertheme{smoothbars}
%\useoutertheme{sidebar}
%\useoutertheme{split}
%\useoutertheme{shadow}
%\useoutertheme{tree}
%\useoutertheme{smoothtree}

%\setbeamertemplate{footline} % Uncomment this line to remove the footer line in all slides
\setbeamertemplate{footline}[page number] % Uncomment this line to replace the footer line in all slides with a simple slide count

\setbeamertemplate{navigation symbols}{} % Uncomment this line to remove the navigation symbols from the bottom of all slides

%----------------------------------------------------------------------------------------
%	PRESENTATION INFORMATION
%----------------------------------------------------------------------------------------

\title[Improved Normal Inference]{Improved Normal Inference from Calibrated Illuminated RGB-D Images} % The short title in the optional parameter appears at the bottom of every slide, the full title in the main parameter is only on the title page

\subtitle{Master Thesis Defense} % Presentation subtitle, remove this command if a subtitle isn't required

\author[Jingyuan Sha]{Jingyuan Sha} % Presenter name(s), the optional parameter can contain a shortened version to appear on the bottom of every slide, while the main parameter will appear on the title slide

\institute[TUK]{Technische Universität Kaiserslautern \\ \smallskip \textit{jingyuan@rhrk.uni-kl.de}} % Your institution, the optional parameter can be used for the institution shorthand and will appear on the bottom of every slide after author names, while the required parameter is used on the title slide and can include your email address or additional information on separate lines

\date[\today]{\\ \today} % Presentation date or conference/meeting name, the optional parameter can contain a shortened version to appear on the bottom of every slide, while the required parameter value is output to the title slide

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SLIDE
%----------------------------------------------------------------------------------------

\begin{frame}
	\titlepage % Output the title slide, automatically created using the text entered in the PRESENTATION INFORMATION block above
\end{frame}

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS SLIDE
%----------------------------------------------------------------------------------------

% The table of contents outputs the sections and subsections that appear in your presentation, specified with the standard \section and \subsection commands. You may either display all sections and subsections on one slide with \tableofcontents, or display each section at a time on subsequent slides with \tableofcontents[pausesections]. The latter is useful if you want to step through each section and mention what you will discuss.

\begin{frame}
	\frametitle{Presentation Overview} % Slide title, remove this command for no title

	\tableofcontents % Output the table of contents (all sections on one slide)
	%\tableofcontents[pausesections] % Output the table of contents (break sections up across separate slides)
\end{frame}

%----------------------------------------------------------------------------------------
%	Introduction SLIDE
%----------------------------------------------------------------------------------------

\section{Introduction}

\begin{frame}
	\frametitle{Surface Normal Inference}
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION BODY SLIDES
%----------------------------------------------------------------------------------------

\section{Text} % Sections are added in order to organize your presentation into discrete blocks, all sections and subsections are automatically output to the table of contents as an overview of the talk but NOT output in the presentation as separate slides

%------------------------------------------------

\begin{frame}
	\frametitle{Paragraphs of Text}

	Sed iaculis \alert{dapibus gravida}. Morbi sed tortor erat, nec interdum arcu. Sed id lorem lectus. Quisque viverra augue id sem ornare non aliquam nibh tristique. Aenean in ligula nisl. Nulla sed tellus ipsum. Donec vestibulum ligula non lorem vulputate fermentum accumsan neque mollis.

	\bigskip % Vertical whitespace

	% Quote example
	\begin{quote}
		Sed diam enim, sagittis nec condimentum sit amet, ullamcorper sit amet libero. Aliquam vel dui orci, a porta odio.\\
		--- Someone, somewhere\ldots
	\end{quote}

	\bigskip % Vertical whitespace

	Nullam id suscipit ipsum. Aenean lobortis commodo sem, ut commodo leo gravida vitae. Pellentesque vehicula ante iaculis arcu pretium rutrum eget sit amet purus. Integer ornare nulla quis neque ultrices lobortis.
\end{frame}

%------------------------------------------------

\begin{frame}
	\frametitle{Lists}
	\framesubtitle{Bullet Points and Numbered Lists} % Optional subtitle

	\begin{itemize}
		\item Lorem ipsum dolor sit amet, consectetur adipiscing elit
		\item Aliquam blandit faucibus nisi, sit amet dapibus enim tempus
		\begin{itemize}
			\item Lorem ipsum dolor sit amet, consectetur adipiscing elit
			\item Nam cursus est eget velit posuere pellentesque
		\end{itemize}
		\item Nulla commodo, erat quis gravida posuere, elit lacus lobortis est, quis porttitor odio mauris at libero
	\end{itemize}

	\bigskip % Vertical whitespace

	\begin{enumerate}
		\item Nam cursus est eget velit posuere pellentesque
		\item Vestibulum faucibus velit a augue condimentum quis convallis nulla gravida 
	\end{enumerate}
\end{frame}

%------------------------------------------------

\subsection{Blocks}

\begin{frame}
	\frametitle{Blocks of Highlighted Text}

	\begin{block}{Block Title}
		Lorem ipsum dolor sit amet, consectetur adipiscing elit. Integer lectus nisl, ultricies in feugiat rutrum, porttitor sit amet augue.
	\end{block}

	\begin{exampleblock}{Example Block Title}
		Aliquam ut tortor mauris. Sed volutpat ante purus, quis accumsan.
	\end{exampleblock}

	\begin{alertblock}{Alert Block Title}
		Pellentesque sed tellus purus. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
	\end{alertblock}

	\begin{block}{} % Block without title
		Suspendisse tincidunt sagittis gravida. Curabitur condimentum, enim sed venenatis rutrum, ipsum neque consectetur orci.
	\end{block}
\end{frame}

%------------------------------------------------

\subsection{Columns}

\begin{frame}
	\frametitle{Multiple Columns}
	\framesubtitle{Subtitle} % Optional subtitle

	\begin{columns}[c] % The "c" option specifies centered vertical alignment while the "t" option is used for top vertical alignment
		\begin{column}{0.45\textwidth} % Left column width
			\textbf{Heading}
			\begin{enumerate}
				\item Statement
				\item Explanation
				\item Example
			\end{enumerate}
		\end{column}
		\begin{column}{0.5\textwidth} % Right column width
			Lorem ipsum dolor sit amet, consectetur adipiscing elit. Integer lectus nisl, ultricies in feugiat rutrum, porttitor sit amet augue. Aliquam ut tortor mauris. Sed volutpat ante purus, quis accumsan dolor.
		\end{column}
	\end{columns}
\end{frame}

%------------------------------------------------

\section{Table and Figure Examples}

\subsection{Table}

\begin{frame}
	\frametitle{Table}
	\framesubtitle{Subtitle} % Optional subtitle

	\begin{table}
		\begin{tabular}{l l l}
			\toprule
			\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
			\midrule
			Treatment 1 & 0.0003262 & 0.562 \\
			Treatment 2 & 0.0015681 & 0.910 \\
			Treatment 3 & 0.0009271 & 0.296 \\
			\bottomrule
		\end{tabular}
		\caption{Table caption}
	\end{table}
\end{frame}

%------------------------------------------------

\subsection{Figure}

\begin{frame}
	\frametitle{Figure}

	\begin{figure}
		\includegraphics[width=0.8\linewidth]{creodocs_logo.pdf}
		\caption{Creodocs logo.}
	\end{figure}
\end{frame}

%------------------------------------------------

\section{Mathematics}

\begin{frame}
	\frametitle{Definitions \& Examples}

	\begin{definition}
		A \alert{prime number} is a number that has exactly two divisors.
	\end{definition}

	\smallskip % Vertical whitespace

	\begin{example}
		\begin{itemize}
			\item 2 is prime (two divisors: 1 and 2).
			\item 3 is prime (two divisors: 1 and 3).
			\item 4 is not prime (\alert{three} divisors: 1, 2, and 4).
		\end{itemize}
	\end{example}

	\smallskip % Vertical whitespace

	You can also use the \texttt{theorem}, \texttt{lemma}, \texttt{proof} and \texttt{corollary} environments.
\end{frame}

%------------------------------------------------

\begin{frame}
	\frametitle{Theorem, Corollary \& Proof}

	\begin{theorem}[Mass--energy equivalence]
		$E = mc^2$
	\end{theorem}

	\begin{corollary}
		$x + y = y + x$
	\end{corollary}

	\begin{proof}
		$\omega + \phi = \epsilon$
	\end{proof}
\end{frame}

%------------------------------------------------

\begin{frame}
	\frametitle{Equation}

	\begin{equation}
		\cos^3 \theta =\frac{1}{4}\cos\theta+\frac{3}{4}\cos 3\theta
	\end{equation}
\end{frame}

%------------------------------------------------

\begin{frame}[fragile] % Need to use the fragile option when verbatim is used in the slide
	\frametitle{Verbatim}

	\begin{example}[Theorem Slide Code]
		\begin{verbatim}
			\begin{frame}
				\frametitle{Theorem}
				\begin{theorem}[Mass--energy equivalence]
					$E = mc^2$
				\end{theorem}
		\end{frame}\end{verbatim} % Must be on the same line
	\end{example}
\end{frame}

%------------------------------------------------

\begin{frame}
	Slide without title.
\end{frame}

%------------------------------------------------

\section{Referencing}

\begin{frame}
	\frametitle{Citing References}

	An example of the \texttt{\textbackslash cite} command to cite within the presentation:

	\bigskip % Vertical whitespace

	This statement requires citation \cite{p1,p2}.
\end{frame}

%------------------------------------------------

\begin{frame} % Use [allowframebreaks] to allow automatic splitting across slides if the content is too long
	\frametitle{References}

	\begin{thebibliography}{99} % Beamer does not support BibTeX so references must be inserted manually as below, you may need to use multiple columns and/or reduce the font size further if you have many references
		\footnotesize % Reduce the font size in the bibliography

		\bibitem[Smith, 2022]{p1}
			John Smith (2022)
			\newblock Publication title
			\newblock \emph{Journal Name} 12(3), 45 -- 678.

		\bibitem[Kennedy, 2023]{p2}
			Annabelle Kennedy (2023)
			\newblock Publication title
			\newblock \emph{Journal Name} 12(3), 45 -- 678.
	\end{thebibliography}
\end{frame}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGMENTS SLIDE
%----------------------------------------------------------------------------------------

\begin{frame}
	\frametitle{Acknowledgements}

	\begin{columns}[t] % The "c" option specifies centered vertical alignment while the "t" option is used for top vertical alignment
		\begin{column}{0.45\textwidth} % Left column width
			\textbf{Smith Lab}
			\begin{itemize}
				\item Alice Smith
				\item Devon Brown
			\end{itemize}
			\textbf{Cook Lab}
			\begin{itemize}
				\item Margaret
				\item Jennifer
				\item Yuan
			\end{itemize}
		\end{column}		
		\begin{column}{0.5\textwidth} % Right column width
			\textbf{Funding}
			\begin{itemize}
				\item British Royal Navy
				\item Norwegian Government
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

%----------------------------------------------------------------------------------------
%	CLOSING SLIDE
%----------------------------------------------------------------------------------------

\begin{frame}[plain] % The optional argument 'plain' hides the headline and footline
	\begin{center}
		{\Huge The End}

		\bigskip\bigskip % Vertical whitespace

		{\LARGE Questions? Comments?}
	\end{center}
\end{frame}

%----------------------------------------------------------------------------------------

\end{document}

### 2022-08-10 paper/Chapters/Chapter04.tex
update paper

@@
 
- In this thesis, we require two kinds of input data to train our models. 
+In this work, we need two types of input data to train our models. 
 First, we need to know the geometry of the object surface.
-This can be collected by a depth camera, which records the Z-axis distance of the object surface to the camera position and it can be further converted to a point cloud.
-Second, we need illuminated information of the object surface, which considers a photometric-information used for further improvement. 
-This kind of information requires an observed image of the object with the light directions projected onto the object surface.
+This can be captured by a depth camera, which records the distance of the object surface from the optical center of the camera and can be converted into a point cloud.
+Second, we need information about the illumination of the object surface, which is used as photometric information for further improvements. 
+This type of information requires an observed image of the object with the light directions projected onto the object surface.
 
-In order to gain these data, we can use a light scanner to scan the objects in the laboratory.
-However, the scanner usually can not scan the dark, shiny, and transparent regions, which leaves plenty of missing pixels and holes in the depth map.
-This incomplete surface information raises the difficulty for our model training since the ground-truth corresponding to the depth map will be incomplete as well.
-Second, training a deep learning-based model usually requires a huge dataset, especially for a network without a backbone.
-To create a single depth map dataset for this thesis would be too much work and resource requirements.
-A proper way for getting huge depth map data with illumination information can be considered using a game engine, which can simulate any number of data that we require.
+To obtain this data, we can use a structured light scanner to scan the objects in the laboratory.
+However, the scanner usually cannot scan the dark, shiny, and transparent areas, resulting in many missing pixels and holes in the depth map.
+This incomplete surface information makes it difficult to train our model because the ground truth corresponding to the depth map is also incomplete.
+Second, training a deep learning-based model usually requires a large dataset, especially for a network without a backbone.
+Creating a single deep map dataset for this work would require too much work and resources.
+A suitable way to obtain huge depth map data with illumination information is to use a game engine that can simulate an arbitrary number of data.
 
-In this thesis, we use the Unity game engine for data generation.
-By using a $ C\# $ script, we can set up a similar configuration in the laboratory.
-Then create a mount of data based on the collected objects.
-The dataset that we created for this thesis is called \textit{synthetic-50-5} since it has 50 different object models for training and 5 object models for testing.
+We use the Unity game engine for data generation.
+Using a $ C\# $ script, we can set up a similar configuration in the lab.
+We then create a dataset based on the collected objects.
+The dataset we created for this work is called \textit{synthetic-50-5} because it contains 50 different object models for training and 5 object models for testing.
 
 \section{Data Resources}
-The object model we used are searched from internet.
-A set of point cloud datasets for computer vision research has been published by \cite{data1}, \cite{data2}, \cite{data3} and \cite{data4}.
-These point clouds are scanned from real objects using high resolution scanners like Cyberware 3030 MS+ and calibrated with post processing.
-All objects has been scanned for hundreds of times with an exhaustive completion for the origin objects, which is up to millions points.
-(\cite{data1}).
-The dense point clouds make the normal inference task trivial since the neighbor based method performs adequately for this kind of task.
-Some of the point clouds even contain pre-computed normal maps based on more advanced methods.
+The object models we used were collected from the Internet.
+A number of point cloud datasets for image processing research have been published by \cite{data1}, \cite{data2}, \cite{data3}, and \cite{data4}.
+Some of these point clouds were scanned from real objects using high-resolution scanners such as the Cyberware 3030 MS+ and calibrated with post-processing.
+These objects were scanned hundreds of times, fully capturing the original objects with up to millions of points\cite{data1}.
+Some of them are fully digitally synthesized.
+The dense point clouds make the normal inference task trivial, as the neighborhood-based method works adequately for this type of task.
+Some of the point clouds even contain precomputed normal maps based on more advanced methods.
 They all provide the accurate ground truth for the supervised learning method.
 
-The \textit{synthetic50-5} is a dataset we generated in this thesis based on 50 point clouds as a training set and 5 point clouds as a test set.
-When we create the dataset, we tried to make the object types as many as possible to give a robust and wide range covered training scenarios.
-There are various categories of models, such as figure, animal, statue, toy, furniture, antique, and car model, some of which have relatively smooth surfaces, such as /textit[arm, bus, bunny, cat, zebra], and some of which have highly complicated details, such as \textit{Washington, Car-Engine, Armadillo}.
-We created this dataset for normal inference tasks. Figure \ref{fig:dataset-demo} gives the illustrations of some objects. Appendix \ref{AppendixA} gives a full version of dataset models.
+The \textit{synthetic-50-5} is a dataset we created in this work based on 50 point clouds as the training set and 5 point clouds as the test set.
+In creating the dataset, we tried to use as many object types as possible to cover a robust and wide range of training scenarios.
+There are several categories of models, such as figurines, animals, statues, toys, furniture, antiques, and car models, some of which have relatively smooth surfaces, such as model \textit{arm, bus, rabbit, cat, zebra}, and some of which have very intricate details, such as model \textit{Washington, Car-Engine, Armadillo}.
+We created this dataset for normal inference tasks.
+Figure \ref{fig:dataset-demo} shows illustrations of some objects.
+Appendix \ref{AppendixA} contains a complete version of the models of the dataset.
 
@@
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{subfigure}[b]{0.24\linewidth}
@@
 	\decoRule
-	\caption{Point clouds scanned by high resolution scanners}
+	\caption{Some of the objects used for \textit{Synthetic-50-5}}
 	\label{fig:dataset-demo}
 \end{figure}
-Besides, some objects also have colored textures, as shown in the second row of Figure \ref{fig:dataset-demo}.
-This is specially prepared for the illuminated approach since they will take the image into account to evaluate the surface normal.
-By using textured models, our models become closer to the real dataset and have improved robustness, which can apply to the real dataset further.
+In addition, some objects also have colored textures, as shown in the second line of Figure \ref{fig:dataset-demo}.
+This is specifically prepared for the illuminated approach, since the image is used to evaluate the surface normals.
+By using textured models, our models get closer to the real dataset and have improved robustness that can be further applied to the real dataset.
 
@@
 \section{Synthesizing Scenes using Unity}
-In order to simulate the data collection scenario close to the real world as much as possible.
-We did the following settings.
-A flat cylinder called $ stage $ is placed in the center of the 3D space as a platform to place objects.
-We fixed the stage in a predetermined position, which is not changed when images are captured.
-To provide ambient light, one directional light with RGB color FFF4D6 /col[direction-light-color] is placed in a top-view direction at a distance of 25 meters, which also has a fixed location.
-An RGB-D camera is placed in a top-view direction around 10m away from the stage.
-The camera captures the depth map and the gray-scale image, which is randomly arranged after each scene.
-The moving range of the camera has 0.1m in both directions of the X, Y, and Z axis and a 1-degree random changed Euler angle.
-As an illumination light, a point light is placed around 5 meters away, which is also randomly moved after each scene.
-The moving range is 0.3m in both directions of the X, Y, and Z axis and 1 degree random in the Euler angle.
 
-During the data collection, the object is randomly selected and placed on the stage.
-The object has a random up to 30 degrees rotation align $ roll $-axis, 30-degrees rotation aligns $ pitch $-axis, and 180-degrees rotation aligns $ yaw $-axis.
-Thus the camera has the opportunity to capture every direction of the object and consequently abundant the dataset.
+To simulate the data acquisition scenario as realistically as possible.
+We made the following settings.
+A flat cylinder, called \textit{stage} , is placed in the center of the 3D space as a platform for placing objects.
+We fixed the \textit{stage} in a predetermined position that will not be changed when images are captured.
+A directional light with RGB color FFF4D6 \col{direction-light-color} is placed 25 m away in the top view direction as an ambient light, which also has a fixed position.
+An RGB-D camera is placed about 10 m away from the stage in the top-view direction.
+The camera captures the depth map and the grayscale image, which are randomly arranged after each scene.
+The movement range of the camera is 0.1 m in both directions of the X, Y and Z axes and a randomly changed Euler angle of $ 1^\circ $.
+A point light is placed about 5 m away as the illumination light, which is also moved randomly after each scene.
+The range of motion is 0.3 m in both directions of the X, Y and Z axes and $ 1^\circ $ randomly in the Euler angle.
+
+During data acquisition, the object is randomly selected and placed on the stage.
+The object has a random rotation of up to $ 30^\circ $ in the $roll $ axis direction, a $ 30^\circ $ rotation in the $pitch $ axis direction, and a $ 180^\circ $ degree rotation in the $yaw $ axis direction.
+This gives the camera the ability to capture most directions of the objects.
 The layout in the Unity game engine is shown in Figure \ref{fig:unity-workplace}.
@@
 	\centering
-	\includegraphics[width=.99\textwidth]{./Figures/unity-workplace.PNG}
+		\captionsetup{width=\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/unity-workplace.PNG}
 	\decoRule
-	\caption{The layout of synthetic scenes generation in Unity.}
+	\caption{The layout of synthetic scene generation in Unity.}
 	\label{fig:unity-workplace}
@@
 \begin{table}
-	\caption{The information saved for each scene in ``synthetic50-5".}
-	\label{tab:data-files}
 	\centering
@@
 	\end{tabular}
+	\caption{The information saved for each scene in \textit{synthetic-50-5}.}
+	\label{tab:data-files}
 \end{table}
 
-One critical detail that we must care about is camera exposure.
-Or we have to control the light radiance on the object surface.
-As shown in figure \ref{fig:camera_exposure}, too little exposure will neutralize the illumination information, resulting in an ambient light effect.
-Too much exposure makes the surface texture hard to recognize.
-When we did the experiments, we found that a suitable light setting is essential to the illumination-based approach.
-Too much or too few light effects won't improve the illumination-based approach.
+A critical detail we need to pay attention to is the exposure of the camera.
+Or we need to control the light emission on the object surface.
+As can be seen in Figure \ref{fig:camera_exposure}, too much exposure causes the surface texture to be difficult to see, resulting in clipping.
+In our experiments, we found that an appropriate light setting is essential for the illumination-based approach.
+Too much or too little lighting effects do not improve the illumination-based approach.
 
@@
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{subfigure}[b]{0.32\linewidth}
 		\includegraphics[width=\textwidth]{./Figures/wrong_exposure_2.png}
-		\caption{Too dim}
+		\caption{Insufficient light}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{./Figures/wrong_exposure.png}
-		\caption{Too bright}
+		\caption{Too much light}
 	\end{subfigure}
@@
 \section{Data Preprocessing}
-The raw data captured from Unity required further preprocessing before feeding them into the training models. 
+The raw data collected by Unity required further processing before it could be fed into the training models. 
 \paragraph{Depth Map}
-A depth map is captured by the depth camera in Unity, which is a 1 channel image that contains information relating to the Z-axis distance from object surface to the camera.
-It is saved as a 16-bit gray-scale image, i.e.
-each pixel in the range $\mathtt{0 - 65535}$.
+A depth map is a 1-channel image that contains information about the distance from the object surface to the camera center.
+It is stored as a 16-bit grayscale image, meaning that each pixel is in the range $\mathtt{0 - 65535}$.
 
-The raw depth maps in real data that captured by light scanners usually have missing pixels.
-In order to fit well with real data, the synthetic data has been added uniform distributed noise, which randomly removes the valid pixels in the maps.
-The simulated noise is distributed evenly around the whole map with specific noise intensity.
-A parameter $ \mu $ is used to control the intensity of noise.
-It denotes the $ \mu $-percent pixel drop-off.
-For example, $ \mu-10 $ removes 10\% pixels randomly.
-For each scene, the noise operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used.
-Some scenes have more missing pixels and some have fewer.
-The random noise intensity also enables the model to learn scenarios not only with noise but also with minor noise or even without noise.
-Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
+The raw depth maps in real data acquired by light scanners usually have missing pixels.
+To achieve a good match to the real data, a uniformly distributed noise was added to the synthetic data to randomly remove the valid pixels in the depth maps.
+The simulated noise is uniformly distributed over the entire map with a certain noise intensity.
+A parameter $ \mu $ is used to control the intensity of the noise.
+It specifies the $ \mu $ pixel drop in percent.
+For example, at $ \mu-10 $, 10\% of the pixels are randomly removed.
+For each scene, the noise operation is based on a random $ \mu $ in a range $ \left[0, 50\right] $.
+In some scenes there are more missing pixels, in others less.
+The random noise intensity also allows the model to learn scenarios not only with noise, but also with low noise or even no noise.
+Figure \ref{fig:noise-intensity} shows the noise effect at different $ \mu $.
+
 %% add noise image
@@
 	\centering
-	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
+	\captionsetup{width=\linewidth}
+	{\includegraphics[width=\textwidth]{./Figures/add_noise_depth.png}}
 	\decoRule
-	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
+	\caption{From left to right: Noise-intensity on $ \mu-0$, $\mu-10$, $\mu-20$, $\mu-30$, $\mu-40$, $\mu-50$. Object Name: \textit{elephant-zun-lid}.}
 	\label{fig:noise-intensity}
@@
 
-The depth map is further converted to 3D vertex map after adding the noise.
-\begin{figure}[h!]
-	\centering
-	\begin{tikzpicture} 
-		% reference lines
-		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
-		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
-		\draw[thick,dashed]	(0,6) -- (10,6); % top
-		% camera 
-		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
-		% world point 
-		\filldraw[black] (7,6) circle (2pt) node[anchor=north west]{Point};
-		% image point
-		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
-		% similiar triangles
-		\draw[thick] (5,0) -- (5,6); % AB
-		\draw[thick] (5,0) -- (7,6); % AC
-		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
-		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
-		% measure arrows
-		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
-		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
-	\end{tikzpicture}	
-	\decoRule
-	\caption{Convert depth to point in camera coordinate system}
-	\label{fig:depth-triangulation}
-\end{figure}
+%\begin{figure}[h!]
+%	\centering
+%	\begin{tikzpicture} 
+%		% reference lines
+%		\node[inner sep=10pt] (input) at (0,0)
+%		{\includegraphics[width=\linewidth]{./Figures/ply_config.png}};
+%		
+%		%		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
+%		%		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
+%		%		\draw[thick,dashed]	(0,6) -- (10,6); % top
+%		% camera 
+%		%		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
+%		% world point 
+%		%		\filldraw[black] (2,2) circle (2pt) node[anchor=north west]{Point};
+%		% image point
+%		%		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
+%		% similiar triangles
+%		%		\draw[thick] (0,0) -- (2,6); % AB
+%		%		\draw[thick] (5,0) -- (7,6); % AC
+%		%		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
+%		%		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
+%		%		% measure arrows
+%		%		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
+%		%		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
+%	\end{tikzpicture}	
+%	\caption{Data Collection configuration}
+%	\label{fig:depth-triangulation}
+%\end{figure}
+The depth map is converted to a 3D vertex map after adding the noise.
+Consider a 3-dimensional Euclidean space.
+The $ X $ and $ Y $ axes are perpendicular to each other align with the direction of width and height of the depth map separately.
+The $ Z $ axis is point inward (i.e., from view point to the depth map).
+The depth provided in the depth map is the distance from camera center to the object surface.
+Thus, in order to find the corresponding 3D vertex map $ \textbf{V}_C $ with respect to the camera coordinate system, we only need to multiple the depth matrix $ \textbf{Depth} $ with the point direction matrix $ \textbf{Dir} $.
 
-Consider a 3-dimensional Euclidean space.
-Use $ z $ axis to denote the depth.
-The $ x  $ and $ y $ axis are perpendicular to each other.
-For a pixel $ (u,v) $ on depth map, its depth $ D(u,v) $ is the $ Z $ component of the corresponding point $P_C = (X,Y,Z) $ regarding camera coordinate system.
-Knowing $ Z $, corresponding depth map pixel $ D(u,v) $ and the camera focal length in pixels $ fk_u, fk_v $, the other two component  $ X $ and $ Y $ in the 3D space can be calculated based on the triangle similarity.
+\begin{dgroup*}
+	\begin{dmath*}
+		\textbf{V}_C = \textbf{Depth} \odot \textbf{Dir}
+	\end{dmath*}
+\end{dgroup*}
+
+For the direction $ \textbf{Dir}(x,y,z) $ of a point $ \textbf{V}(x,y,z) $, it's X and Y components can be mapped from the corresponding pixel position $ (u,v) $ on the depth map, whereas the Z component is the focal length $ fk $ in pixels.
+Then we have to further normalize it to an unit vector.
 
@@
 	\begin{dmath*}
-		X = \frac{uZ}{fk_u}
+		\textbf{Dir}(x, y, z) = \dfrac{(u, v, fk)}{\|(u, v, fk) \|^2_2}
 	\end{dmath*}
-	\begin{dmath*}
-		Y = \frac{vZ}{fk_v}
-	\end{dmath*}
+
 \end{dgroup*}
-Convert a point from camera coordinate system to the world coordinate system, using extrinsic matrix $ R $ and $ t $
-\[P_W = P_CR+t \]
+Conversion of a point from the camera coordinate system to the world coordinate system using the extrinsic matrix $ R $ and $ t $
+\[\textbf{V}_W = \textbf{V}_C R+t \]
 
 %% How to represent input tensor, to make it fast converse
-The sizes of each training object are various, we normalized them to an unit scale thus they has relatively similar distance to the camera.
-We showed the value fluctuation in each axis in Figure \ref{fig:data_range} before normalization. Table \ref{tab:data_range} gives a quantitative evaluation of the corresponding average values.
+The sizes of the individual training objects are different. We normalized them to a unit scale so that they have a relatively similar distance from the camera.
+In Figure \ref{fig:data_range} we have plotted the variations in value in each axis before normalization.
+Table \ref{tab:data_range} gives a quantitative evaluation of the corresponding average values.
 
-The normalization has been performed as follows.
-First, translate the points to the original point as close as possible, then choose the range value of one axis as a scale factor, and normalize the points to unit vectors.
-The equation is shown as follows
+The normalization was performed as follows.
+First, the points are translated to the original point as much as possible, then the range value of an axis is chosen as the scaling factor, and the points are normalized to unit vectors.
+The equation is represented as follows
+
 \begin{dgroup*}
-
 	\begin{dmath*}
@@
 	\end{dmath*}
-\end{dgroup*}
-
-where $ s $ is a scale factor,
-
 	\begin{dmath*}
@@
 	\end{dmath*}
-which is calculated as the range of the $ X $ axis, but theoretically can be used by the $ Y $ or $ Z $ axes as well.
+\end{dgroup*}
+where $ s $ is a scaling factor calculated as the range of the $ X $ axis, but theoretically it can also be the range of $ Y $ or $ Z $ axis.
 
@@
 	\centering
-	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
-	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
+	\captionsetup{width=\linewidth}
+	{\includegraphics[width=0.49\textwidth]{./Figures/Data_Extreme.png}}
+	{\includegraphics[width=0.49\textwidth]{./Figures/Data_Range.png}}
 	\decoRule
@@
 \paragraph{Image}
-The gray-scale image can be used for photometric stereo approach and also as a readable information for humans.
-Since the image captured by the camera is in RGB format, we need to convert it to gray colors to fit our models.
-It is based on the following equation.
+
+The grayscale image can be used for the photometric stereo method and also as readable information for humans.
+Since the image captured by the camera is in RGB format, we need to convert it to grayscale to fit our models.
+This is done using the following equation.
 \[ gray: \frac{R+2G+B}{4}  \]
@@
 \paragraph{Normal Map}
-The normal map is the tangent surface normal, which is saved in a 8-bit/channel RGB image.
-The surface normal $ (n_x, n_y, n_z) $ and its corresponding RGB color $ (R,G,B) $ can be converted based on the following equation:
+The normal map is the tangential surface normal stored in an 8-bit/channel RGB image.
+The surface normal $ (n_x, n_y, n_z) $ and the corresponding RGB color $ (R,G,B) $ can be converted using the following equation:
+
 \begin{dgroup*}
 	\begin{dmath*}
-		n_x = \frac{R}{255} * 2 - 1
+		n_x = \frac{R}{255} \cdot 2 - 1
 	\end{dmath*}
 	\begin{dmath*}
-		n_y = \frac{G}{255}*2 - 1
+		n_y = \frac{G}{255} \cdot 2 - 1
 	\end{dmath*} 
 	\begin{dmath*}
-		n_z = 1-\frac{B}{255} * 2
+		n_z = 1-\frac{B}{255} \cdot 2
 	\end{dmath*}
@@
 
-In order to save training time, we compress the dataset in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
-\begin{table}[H]
-	\caption{The structure of a single tensor in the dataset.}
-	\label{tab:tensor-structure}
-	\centering
-	\begin{tabular}{l | l}
-		\toprule
-		\tabhead{Name} & \tabhead{Content} \\
-		\midrule
-		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
-		\hline
-		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
-		\hline
-		Light position & light position \\
-		\hline 
-		Camera Matrix  & K,R,t\\
-		\hline 
-		Depth Range  & minDepth, maxDepth\\
-		\bottomrule
-	\end{tabular}
-\end{table}
+%In order to save training time, we compress the dataset in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
+%\begin{table}[H]
+%	\centering
+%	\captionsetup{width=\linewidth}
+%	\begin{tabular}{l | l}
+%		\toprule
+%		\tabhead{Name} & \tabhead{Content} \\
+%		\midrule
+%		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
+%		\hline
+%		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
+%		\hline
+%		Light position & light position \\
+%		\hline 
+%		Camera Matrix  & K,R,t\\
+%		\hline 
+%		Depth Range  & minDepth, maxDepth\\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{The structure of a single tensor in the dataset.}
+%	\label{tab:tensor-structure}
+%\end{table}

### 2022-08-10 paper/akweury/document.tex
update paper

@@
 
+\usepackage{tikz-3dplot}
+\usetikzlibrary{calc}
+\newcommand{\DrawPlane}[3][]{\draw[#1] 
+	(-1*\PlaneScale,{\PlaneScale*cos(#2)},{\PlaneScale*sin(#2)})
+	-- ++  (2*\PlaneScale,0,0)
+	-- ++ (0,{sqrt(3)*\PlaneScale*cos(#3)},{sqrt(3)*\PlaneScale*sin(#3)})
+	-- ++  (-2*\PlaneScale,0,0) -- cycle;}
+\newcommand{\DrawSinglePlane}[2][]{\ifcase#2
+	\or
+	\DrawPlane[fill=blue,#1]{210}{240} %left bottom 
+	\or
+	\DrawPlane[fill=red,#1]{-30}{-60} % right bottom
+	\or
+	\DrawPlane[fill=purple,#1]{210}{180} % bottom left
+	\or
+	\DrawPlane[fill=purple,#1]{210}{0} % bottom middle
+	\or
+	\DrawPlane[fill=purple,#1]{-30}{0} % bottom right
+	\or
+	\DrawPlane[fill=blue,#1]{90}{240} % left top
+	\or
+	\DrawPlane[fill=red,#1]{90}{-60} % right middle
+	\or
+	\DrawPlane[fill=red,#1]{90}{120} % right top
+	\or
+	\DrawPlane[fill=blue,#1]{90}{60} % left top
+	\fi
+}
+
 \usetikzlibrary{fit}
@@
 \begin{document}
+\begin{figure}[h!]
+	\centering
+	\tdplotsetmaincoords{70}{110}
+	\begin{tikzpicture} [scale=3]	
+		% reference lines
+%		\node[inner sep=10pt] (input) at (0,0)
+%		{\includegraphics[width=\linewidth]{./Figures/ply_config.png}};
 
-\begin{figure}[th]
-	\centering
+\filldraw[
+draw=red,%
+fill=red!20,%
+opacity=0.5,
+]  (1,1,1)
+-- (1,-1,1)
+-- (-1,-1,1)
+-- (-1,1,1)
+-- cycle;
+\draw[thick,->] (0,0,0) -- (2,0,0) node[anchor=north east]{$x$};
 
-\begin{tikzpicture}
-	\pgfplotsset{ticks=none}
-	\begin{axis} [axis lines=center]
-		\addplot [domain=0:1, smooth, thick, width=5mm, color=red] { x };
-		\addplot [domain=1:2, smooth, width=5mm] { x };
-		\addplot [domain=-2:-1, smooth, width=3mm] { -x };
-		\addplot [domain=-1:0, smooth, thick, width=3mm, color=red] { -x };
-		\addplot [domain=-2:-1, smooth, thick, color=red] { (x^2+1^2)/(2*1) };
-		\addplot [domain=1:2, smooth, thick, color=red] { (x^2+1^2)/(2*1) };
-	\end{axis}
+\draw[thick,->] (0,0,0) -- (0,-2,0) node[anchor=north west]{$y$};
+\draw[thick,->] (0,0,0) -- (0,0,-2) node[anchor=south]{$z$};
+%		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
+%		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
+%		\draw[thick,dashed]	(0,6) -- (10,6); % top
+		% camera 
+%		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
+		% world point 
+%		\filldraw[black] (2,2) circle (2pt) node[anchor=north west]{Point};
+		% image point
+%		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
+		% similiar triangles
+%		\draw[thick] (0,0) -- (2,6); % AB
+%		\draw[thick] (5,0) -- (7,6); % AC
+%		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
+%		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
+%		% measure arrows
+%		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
+%		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
 	\end{tikzpicture}	
-	\caption{The shape of Berhu Loss (show in red line). }
-	\label{fig:berhu-loss-shape}
+	\caption{Data Collection configuration}
+	\label{fig:depth-triangulation}
 \end{figure}
+
 \end{document}

### 2022-08-11 paper/Chapters/Chapter05.tex
update paper

@@
 
-The models are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes.
+The models are trained on the dataset \textit{synthetic-50-5} with 3000 scenes mentioned in chapter \ref{ch:04}.
 Each scene has a depth map with dimension $ 128\times 128 $ in height and width, an image with dimension $ 128\times 128 $.
-The depth map is converted from 3D vertex map as introduced in Chapter \ref{ch:04}.
-The light map is calculated based on vertex map and the known light position.
-We create a tensor in PyTorch that includes vertex map, image and the light direction for each scene and considered it as one training case.
-Thus 3000 scenes correspond 3000 training cases.
-Each scene has a corresponding ground-truth normal map for loss calculation and the evaluation.
+The depth map is converted from the 3D vertex map as introduced in chapter \ref{ch:04}.
+The light map is computed from the vertex map and the known light position.
+We create a tensor in PyTorch containing the vertex map, image, and light direction for each scene and consider it as a training case.
+Thus, 3000 scenes correspond to 3000 training cases.
+For each scene, there is a corresponding ground truth normal map for loss calculation and evaluation.
 Figure \ref{fig:test-scene} shows some of the training cases.
-Note that the position of objects are not placed always naturally on the stage but with a random rotation in X, Y, Z axes, respectively.
+Note that the position of the objects is not always placed naturally on the stage, but with a random rotation in the X, Y and Z axes.
 
+% test scene
 \begin{figure}[H]
 	\centering
-
+	\captionsetup{width=\linewidth}
 	\begin{subfigure}[b]{0.24\linewidth}
@@
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
-		\caption{Add noise}
+		\caption{Added noise}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
-		\caption{Normal}
+		\caption{Normal Map}
 	\end{subfigure}
 	\decoRule
-	\caption{Some of the test scenes during the training. From top to bottom, baoshanlu, Washington, Garfield, Dragon, Bus}
+	\caption{Some of the evaluation scenes during the training. The objects from top to bottom rows: \textit{ Washington}, \textit{Bus}}
 	\label{fig:test-scene}
@@
 
-Besides the 3000 training scenes, 100 extra scenes containing 5 different object models are as evaluation dataset during the training. They are evaluated in each epoch.
+Besides the 3000 training scenes, 100 additional scenes with 5 different object models are used as evaluation dataset during the training. They are evaluated in each epoch.
 
-For the training parameters, we set the training pipeline with batch size $ 8 $, we found that a higher batch size will reduce the final performance.
-Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, it will decay at epoch 8 with learning decay factor 0.5.
-The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTXA 6000.
-It takes 14 hours to train GCNN and 35 hours to train the Trip-Net.
-We terminate the training when the angle error of the normal map stop decreasing.
+For the training parameters, we set the training pipeline with a batch size of 8, since we found that a higher batch size decreases the final performance.
+Adam Optimizer (\cite{adam}), learning rate starting at $ 1\times10^{-3} $, it will decrease at epoch 8 with learning decay factor 0.5.
+The model is trained using PyTorch 1.10.0a0, CUDA 11.4.1, GPU with an NVIDIA GEFORCE RTXA 6000.
+It takes 14 hours to train the GCNN and 35 hours to train the Trip-Net.
+We stop training when the angular error of the normal map stops decreasing.
 
-GCNN model is the base model of the whole thesis.
+The \textit{GCNN} is the base model of the whole work.
 The architecture is described in \ref{sec:gcnn}.
-We use a single GCNN to estimate the surface normal as a geometry based approach.
-It uses vertex map as input to estimate the corresponding tangent surface normal map.
-In order to verify the applicability of the skip connection and the gated convolution layers, we trained two extra models as a comparison.
-The first model, we replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same, and give it a name ``CNN".
-It is used to compare the performance between gated convolution layer and standard convolution layer for our normal inference task.
-As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input.
-Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN".
-Another model called ``NOC" is designed to verify the skip connection, which simply removes the skip connections in the network but keeps other settings same.
-Is is designed to show to which content will skip connection help the model performance.
-We use Reversed Huber Loss as loss function during the training.
-We found it gives a better final error compare to L2 loss.
+We use a single \textit{GCNN} to estimate surface normals as a geometry-based approach.
+It uses a vertex map as input.
+To verify the applicability of the skip-connection and gated-convolution layers, we trained two additional models for comparison.
+In the first model, we replace all gated layers with default convolutional layers in the network, but keep all other settings and give it the name \textit{CNN}.
+It is used to compare the performance between the gated layer and the default convolutional layer for our normal inference task.
+As mentioned in \ref{ch:03}, the gated layer is designed to process noisy input.
+Since the entire vertex map in the dataset was noisy, the \textit{GCNN} should outperform \textit{CNN}.
+Another model called \textit{NOC} is used to check skip connections, which simply removes the skip connections in the network but leaves the other settings unchanged.
+Its purpose is to show to what extent the performance of the model is improved by skipping connections.
+We use Reversed Huber Loss as a loss function during training.
+We have found that it gives a better final error compared to L2 loss.
 
 \begin{table}[H]
-
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{tabular}{l | l l l l l }
@@
 		\hline
-		CNN 					& 17 & 32 & 0 & 0 & 25.5 \\
+		CNN 					& 17 & 32 & - & - & 25.5 \\
 		\hline
-		NOC 					& 32 & 32 & 0 & 0 & 30.6 \\
+		NOC 					& 32 & 32 & - & - & 30.6 \\
 		\hline
-		GCNN 					& 32 & 32 & 0 & 0 & 45.8 \\
+		GCNN 					& 32 & 32 & - & - & 45.8 \\
 		\bottomrule
 	\end{tabular}
-	\caption{GCNN Model information.
-Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively.
-Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2.
-}
+	\caption{GCNN model information.
+The V-P, L-P, and I-P columns indicate the number of convolutional layers in the vertex pipe, light pipe, and image pipe, respectively.
+Note that a gated convolution layer consists of 2 standard layers and is therefore counted as 2.}
 	\label{tab:gcnn-eval-mean}
@@
 
-The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train.
+The trip-net model uses a triple GCNN architecture with 4 times fusions, which is more difficult to train.
 It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
-When we train this model, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture.
-We also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification.
-A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times.
-We evaluate the fusion times from 1 to 4.
-For the learning rate, we set it as $ 1e-3 $.
-It goes well with GCNN model but lead to loss explosion in Trip-Net.
-Thus we set a learning rate schedule with an extra decay step at epoch 8.
+When we train this model, we take the GCNN model as the baseline to observe the advantages of the illuminated information with the trip-net architecture.
+We also examined the optimal fusion times of the Trip-Net to determine a possible simplification of the model.
+A set of similar models was trained with the same settings but different fusion times, denoted Trip-Net-F$ x $, where $ x $ denotes the fusion times.
+We score the fusion times from 1 to 4.
+For the learning rate, we initially set $ 1e-3 $.
+This fits the GCNN model well, but leads to a loss explosion in the trip-net.
+Therefore, we set a learning rate schedule with an additional decay step at epoch 8.
 The decay factor is $ 0.5$.
-The batch size is chosen as 8.
+The batch size is set to 8.
 
-During the training we found that trip-Net with four times fusion converges obviously faster than fewer fusion times model.
-However, model F3 with 3 times fusion converge slower than F4 but in the end it achieves a similar evaluation loss with F4(see Qualitative evaluation).
-The F1 and F2 models are relatively less accurate than the other two models, but the sacrifice of accuracy gives a relatively lighter model.
-Since they have less fusion times, the corresponding upsampling layers in the image and light pipes can also be removed.
-The model can be trained in a faster way and the size is reduced as well.
-Table \ref{tab:trip-net-size-compare} gives a comparison of the size and training time among different models.
+During training, we found that the trip-net with 4 fusions converges significantly faster than models with fewer fusion times.
+However, model F3 with three times fusion converges slower than F4, but ends up with a similar loss of score as F4 (see Qualitative Evaluation).
+Models F1 and F2 are relatively less accurate than the other two models, but the sacrifice of accuracy results in a relatively lighter model.
+Since they have fewer fusion times, the corresponding upsampling layers in the image and light pipes can also be removed.
+The model can be trained faster, and the size is also smaller.
+Table \ref{tab:trip-net-size-compare} contains a comparison of the size of different models.
 
 \begin{table}[H]
-
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{tabular}{l | l l l l l }
@@
 One of the benefit of GCNN architecture is the robustness to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
+We use $\tilde{\textbf{N}}$ denotes the estimated normal map, $ \textbf{N} $ denotes the ground-truth normal map, $ P $ denotes the \textit{set} of valid points, \textit{ValidNum} denotes the number of valid points.
+\textit{abs} is a function to calculate the absolute value of the given value, \textit{median} is a function calculate the median value of a given set.
 
-\paragraph{Average Angle Error Metric}
-The metric calculate the average angle error for each point between the inferred normal and ground-truth normal map. 
-\paragraph{Median Angle Error Metric}
-The metric calculate the median angle error of all the point in the normal map.
+\paragraph{Average Angle Error Metric (AAE)}
+The metric calculates the average angle error for each point between the inferred normal and ground-truth normal map. 
+%% https://www.cuemath.com/geometry/angle-between-vectors/
+\[ 
+AAE = \frac
+{1}
+{ValidNum} \cdot \sum_{i\in P}  \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) 
+\]
+
+\paragraph{Median Angle Error Metric (MED)}
+The metric calculates the median angle error of all of the points in the normal map.
+\[ 
+MED = 
+\text{Median}   \left( \Bigg\{ i \in P \Bigg |  \text{abs}\left(\arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \right)   \Bigg\}\right)
+\]
+
 \paragraph{5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 5 degrees comparing to ground-truth.
+The metric calculates the percentage of the predicted normals that has error less than $ 5^\circ $ comparing to ground-truth.
+It first calculates the number of normals that have error less than $ 5^\circ $
+\[
+D_5 = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 5 \right)
+\]
+Then it calculate the percentage of the normals that error less than $ 5^\circ $.
+\[ 
+E_5 = \frac{D_5}{ValidNum}\times 100\%
+\]
+
 \paragraph{11.5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 11.5 degrees comparing to ground-truth.
+The metric calculates the percentage of the predicted normals that has error less than $ 11.5^\circ $ comparing to ground-truth.
+It first calculates the number of normals that have error less than $ 11.5^\circ $.
+
+\[
+D_{11.5} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 11.5 \right)
+\]
+Then it calculate the percentage of the normals that error less than $ 11.5^\circ $.
+\[ 
+E_{11.5} = \frac{D_{11.5}}{ValidNum}\times 100\%
+\]
+
 \paragraph{22.5 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 22.5 degrees comparing to ground-truth.
+The metric calculates the percentage of the predicted normals that has error less than $ 22.5^\circ $ comparing to ground-truth.
+It first calculates the number of normals that have error less than $ 22.5^\circ $.
+
+\[
+D_{22.5} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 22.5 \right)
+\]
+Then it calculate the percentage of the normals that error less than $ 22.5^\circ $.
+\[ 
+E_{22.5} = \frac{D_{22.5}}{ValidNum}\times 100\%
+\]
+
 \paragraph{30 Degree Error Metric}
-The metric calculate the percentage of the predicted normals that has error less than 30 degrees comparing to ground-truth.
+The metric calculates the percentage of the predicted normals that has error less than $ 30^\circ $ comparing to ground-truth.
+It first calculates the number of normals that have error less than $ 30^\circ $.
 
-We evaluated our trained models on ``synthetic-50-5".
+\[
+D_{30} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 30 \right)
+\]
+Then it calculate the percentage of the normals that error less than $ 30^\circ $.
+\[ 
+E_{30} = \frac{D_{30}}{ValidNum}\times 100\%
+\]
+
+We evaluated our trained models on \textit{synthetic-50-5}.
 5 objects are considered in the test dataset.
-They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $.
+They are: \textit{Baoshanlu}, \textit{Bus},  \textit{Dragon}, \textit{Garfield} , and \textit{Washington}.
 Each object has 20 scenes with total 100 scenes for 5 objects.
 The test objects do not exist in the training dataset.
-We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified.
-$ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $.
-$ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.
+We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each model are simplified.
+\textit{SVD}  model use SVD optimization method, \textit{NOC} model is the no skip connection version of \textit{GCNN}, \textit{CNN} is the CNN version of \textit{GCNN}.
+\textit{F1}, \textit{F2}, \textit{F3}, \textit{F4} means the fusion times in the Trip-Net.
 
-When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model.
-When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.
+When evaluating the \textit{GCNN} models, we take \textit{SVD} model with an optimal neighbor size as baseline.
+\textit{NOC} and \textit{CNN} are used to verify the performance of \textit{GCNN} model.
+When evaluate the \textit{F1}-\textit{F4} models, we can take \textit{GCNN} model as baseline.
 
 From the table we can see that all the learning based approaches achieves a better result than SVD approach.
-In the 30 degrees error metric, GCNN based approach achieves 95 \% accuracy whereas Trip-Net is even higher, some of the models like $ dragon $ achieves 98\%.
+In the 30 degrees error metric, GCNN based approach achieves 95 \% accuracy whereas Trip-Net is even higher, some of the models like \textit{dragon} achieves 98\%.
 The best performance is around 90\%, 75 \%, 45 \% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metrics respectively.
@@
 We also found that during the training, F4 model converges faster than F3, but F3 in the end achieves a similar loss with model F4.
-However, based on the$ 30^\circ $, $ 22.5^\circ $, $ 11.5^\circ $ metrics, we can still see that F4 model gives a more stable performance with less high error normals.
+However, based on the $ 30^\circ $, $ 22.5^\circ $, $ 11.5^\circ $ metrics, we can still see that F4 model gives a more stable performance with less high error normals.
 This is reasonable since the last fusion in the original resolution provides more high resolution information to the models.
@@
 	\end{tabular}
-	\caption{Average Angle Error of the evaluation dataset.}	
+	\caption{Average Angle Error of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
 	\label{tab:eval-mean}
@@
 	\end{tabular}
-	\caption{Median Angle Error of the evaluation dataset.}	
+	\caption{Median Angle Error of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
 	\label{tab:eval-median}
@@
 	\end{tabular}
-	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
+	\caption{Percent of error less than 5 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
 	\label{tab:eval-5d}
@@
 	\end{tabular}
-	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
+	\caption{Percent of error less than 11.5 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
 	\label{tab:eval-11d}
@@
 	\end{tabular}
-	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
+	\caption{Percent of error less than 22.5 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
 	\label{tab:eval-22d}
@@
 	\end{tabular}
-	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
+	\caption{Percent of error less than 30 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
 	\label{tab:eval-30d}

### 2022-08-11 paper/Chapters/Chapter05.tex
update paper

@@
 
-The trip-net model uses a triple GCNN architecture with 4 times fusions, which is more difficult to train.
+The trip-net model uses a triple GCNN architecture with 4 fusions, which is more difficult to train.
 It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map.
@@
 \section{Quantitative Evaluation on 6 Metrics}
-We evaluated our models on synthetic dataset with resolution $ 128\times 128 $. 
-Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation.
-Note that the input vertex map is only semi-dense.
-One of the benefit of GCNN architecture is the robustness to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.
-We use $\tilde{\textbf{N}}$ denotes the estimated normal map, $ \textbf{N} $ denotes the ground-truth normal map, $ P $ denotes the \textit{set} of valid points, \textit{ValidNum} denotes the number of valid points.
-\textit{abs} is a function to calculate the absolute value of the given value, \textit{median} is a function calculate the median value of a given set.
+We evaluated our models on a synthetic dataset with a resolution of $ 128 by $ 128. 
+Based on the metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for the evaluation.
+Note that the vertex map input is only semi-dense.
+One of the advantages of the GCNN architecture is that it is robust to noisy input, so all points, including missing points in the input vertex map, are considered in the evaluation.
+We use $\tilde{\textbf{N}}$ for the estimated normal map, $ \textbf{N} $ for the ground-truth normal map, $ P $ for the \textit{set} of valid points, \textit{ValidNum} for the number of valid points.
+\textit{abs} is a function to calculate the absolute value of the given values, \textit{median} is a function to calculate the median value of a given \textit{set}.
 
 \paragraph{Average Angle Error Metric (AAE)}
-The metric calculates the average angle error for each point between the inferred normal and ground-truth normal map. 
+The metric calculates the average absolute angular error for each point between the inferred normal and the ground-truth normal map.
 %% https://www.cuemath.com/geometry/angle-between-vectors/
@@
 {1}
-{ValidNum} \cdot \sum_{i\in P}  \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) 
+{ValidNum} \cdot \sum_{i\in P}  \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| 
 \]
@@
 \paragraph{Median Angle Error Metric (MED)}
-The metric calculates the median angle error of all of the points in the normal map.
+The metric calculates the median of the absolute angular error of all points in the normal map.
+
 \[ 
 MED = 
-\text{Median}   \left( \Bigg\{ i \in P \Bigg |  \text{abs}\left(\arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \right)   \Bigg\}\right)
+\text{Median}   \left( \Bigg\{ \left|\arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \right| \text{for}\ i \in P   \Bigg\}\right)
 \]
 
-\paragraph{5 Degree Error Metric}
-The metric calculates the percentage of the predicted normals that has error less than $ 5^\circ $ comparing to ground-truth.
-It first calculates the number of normals that have error less than $ 5^\circ $
+\paragraph{5 Degree Error Metric ($ E_5 $)}
+The metric calculates the percentage of predicted normals that have an error less than $ 5^\circ $ compared to ground truth.
+First, the number of normals that have an error less than $ 5^\circ $ ($ D_5 $) is calculated.
 \[
@@
 \]
-Then it calculate the percentage of the normals that error less than $ 5^\circ $.
+Then the percentage of normals that have error less than $ 5^\circ $ ($ E_5 $) is calculated.
 \[ 
@@
 
-\paragraph{11.5 Degree Error Metric}
-The metric calculates the percentage of the predicted normals that has error less than $ 11.5^\circ $ comparing to ground-truth.
-It first calculates the number of normals that have error less than $ 11.5^\circ $.
+\paragraph{11.5 Degree Error Metric ($ E_{11.5} $)}
+The metric calculates the percentage of predicted normals that have an error less than $ 11.5^\circ $ compared to ground truth.
+First, the number of normals that have an error less than $ 11.5^\circ $ ($ D_{11.5} $) is calculated.
 
@@
 \]
-Then it calculate the percentage of the normals that error less than $ 11.5^\circ $.
+Then the percentage of normals that have error less than $ 11.5^\circ $ ($ E_{11.5} $) is calculated.
 \[ 
@@
 
-\paragraph{22.5 Degree Error Metric}
-The metric calculates the percentage of the predicted normals that has error less than $ 22.5^\circ $ comparing to ground-truth.
-It first calculates the number of normals that have error less than $ 22.5^\circ $.
+\paragraph{22.5 Degree Error Metric ($ E_{22.5} $)}
+The metric calculates the percentage of predicted normals that have an error less than $ 22.5^\circ $ compared to ground truth.
+First, the number of normals that have an error less than $ 22.5^\circ $ ($ D_{22.5} $) is calculated.
 
@@
 \]
-Then it calculate the percentage of the normals that error less than $ 22.5^\circ $.
+Then the percentage of normals that have error less than $ 22.5^\circ $ ($ E_{22.5} $) is calculated.
 \[ 
@@
 
-\paragraph{30 Degree Error Metric}
-The metric calculates the percentage of the predicted normals that has error less than $ 30^\circ $ comparing to ground-truth.
-It first calculates the number of normals that have error less than $ 30^\circ $.
+\paragraph{30 Degree Error Metric ($ E_{30} $)} 
+The metric calculates the percentage of predicted normals that have an error less than $ 30^\circ $ compared to ground truth.
+First, the number of normals that have an error less than $ 30^\circ $ ($ D_{30} $) is calculated.
 
@@
 \]
-Then it calculate the percentage of the normals that error less than $ 30^\circ $.
+Then the percentage of normals that have error less than $ 30^\circ $ ($ E_{30} $) is calculated.
 \[ 
@@
 We evaluated our trained models on \textit{synthetic-50-5}.
-5 objects are considered in the test dataset.
-They are: \textit{Baoshanlu}, \textit{Bus},  \textit{Dragon}, \textit{Garfield} , and \textit{Washington}.
-Each object has 20 scenes with total 100 scenes for 5 objects.
-The test objects do not exist in the training dataset.
-We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each model are simplified.
-\textit{SVD}  model use SVD optimization method, \textit{NOC} model is the no skip connection version of \textit{GCNN}, \textit{CNN} is the CNN version of \textit{GCNN}.
-\textit{F1}, \textit{F2}, \textit{F3}, \textit{F4} means the fusion times in the Trip-Net.
-
-When evaluating the \textit{GCNN} models, we take \textit{SVD} model with an optimal neighbor size as baseline.
+In the test dataset, 5 objects are considered.
+They are: \textit{Baoshanlu}, \textit{Bus}, \textit{Dragon}, \textit{Garfield} and \textit{Washington}.
+Each object has 20 scenes with a total of 100 scenes for 5 objects.
+The test objects are not present in the training dataset.
+We evaluate all the presented models on the test dataset, to fit them into a table, the names of each model are simplified.
+The model \textit{SVD} uses the SVD optimization method, the model \textit{NOC} is the no-skip connection version of \textit{GCNN}, \textit{CNN} is the CNN version of \textit{GCNN}.
+\textit{F1}, \textit{F2}, \textit{F3}, \textit{F4} are the fusion times in the \textit{Trip-Net}.
+
+When evaluating the \textit{GCNN} models, we take \textit{SVD} model with an optimal neighborhood size as baseline.
 \textit{NOC} and \textit{CNN} are used to verify the performance of \textit{GCNN} model.
@@
 
+In evaluating the \textit{GCNN} models, we take the \textit{SVD} model with an optimal neighborhood size as the baseline.
+\textit{NOC} and \textit{CNN} are used to check the performance of the \textit{GCNN} model.
+When evaluating the \textit{F1}-\textit{F4} models, we can take the \textit{GCNN} model as a baseline.
+
+From the table, it can be seen that all learning-based approaches achieve a better result than the \textit{SVD} approach.
+In the 30-degree error metric, the GCNN-based approach achieves 95\% accuracy, while Trip-Net is even higher and some models such as \textit{dragon} achieve 98\%.
+The best performance is 90\%, 75\%, 45\% in the $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degree error metric, respectively.
+Another notable result is the close relationship between the F3 and F4 models, which achieve very comparable performance.
+We also found that model F4 converges faster than F3 during training, but F3 ends up achieving a similar loss as model F4.
+However, using the metrics $ 30^\circ $, $ 22.5^\circ $ and $ 11.5^\circ $, we can see that the F4 model has a more stable performance with less high error normals.
+This is reasonable since the last fusion at the original resolution provides more high-resolution information to the models.
+
 %% mean metric
@@
 	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
+	\captionsetup{width=\linewidth}
+	\begin{tabular}{l | l | l l l | l l l l }
 		\toprule
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 &\textbf{ 9.77 }& 9.80 \\ 
-		\hline
-		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & \textbf{7.30} & 7.62\\ 
-		\hline
-		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 &\textbf{ 7.79} \\
-		\hline
-		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 &\textbf{ 9.39} \\
-		\hline
-		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 &\textbf{ 12.60}\\
+		Baoshanlu  		& 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 &\textbf{ 9.77 }& 9.80 \\ 
+		\hline
+		Bus 			& 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & \textbf{7.30} & 7.62\\ 
+		\hline
+		Dragon 			& 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 &\textbf{ 7.79} \\
+		\hline
+		Garfield 		& 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 &\textbf{ 9.39} \\
+		\hline
+		Washington 		& 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 &\textbf{ 12.60}\\
 		\bottomrule
 	\end{tabular}
-	\caption{Average Angle Error of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
+	\caption{Average angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
 	\label{tab:eval-mean}
@@
 	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
+	\captionsetup{width=\linewidth}
+	\begin{tabular}{l | l | l l l | l l l l }
 		\toprule
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 &\textbf{ 7.50} \\ 
-		\hline
-		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & \textbf{3.65 }& 4.47 \\ 
-		\hline
-		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 &\textbf{ 5.52} \\
-		\hline
-		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & \textbf{6.04 }\\
-		\hline
-		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 &\textbf{ 7.03 }& 7.25\\
+		Baoshanlu  		& 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 &\textbf{ 7.50} \\ 
+		\hline
+		Bus 			& 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & \textbf{3.65 }& 4.47 \\ 
+		\hline
+		Dragon 			& 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 &\textbf{ 5.52} \\
+		\hline
+		Garfield 		& 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & \textbf{6.04 }\\
+		\hline
+		Washington 		& 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 &\textbf{ 7.03 }& 7.25\\
 		\bottomrule
 	\end{tabular}
-	\caption{Median Angle Error of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
+	\caption{Median angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
 	\label{tab:eval-median}
@@
 	\centering
-	\begin{tabular}{l l | l | l l l |l l l l }
+	\captionsetup{width=\linewidth}
+	\begin{tabular}{l | l | l l l |l l l l }
 		\toprule
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 &\textbf{ 0.33 }& 0.32\\ 
-		\hline
-		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & \textbf{0.63 }& 0.55 \\ 
-		\hline
-		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 &\textbf{ 0.46}\\
-		\hline
-		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & \textbf{0.43}\\
-		\hline
-		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & \textbf{0.40 }& 0.37\\
+		Baoshanlu  		& 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 &\textbf{ 0.33 }& 0.32\\ 
+		\hline
+		Bus 			& 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & \textbf{0.63 }& 0.55 \\ 
+		\hline
+		Dragon 			& 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 &\textbf{ 0.46}\\
+		\hline
+		Garfield 		& 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & \textbf{0.43}\\
+		\hline
+		Washington 		& 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & \textbf{0.40 }& 0.37\\
 		\bottomrule
 	\end{tabular}
-	\caption{Percent of error less than 5 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
+	\caption{Percentage of error of less than 5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
 	\label{tab:eval-5d}
@@
 	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
+	\captionsetup{width=\linewidth}
+	\begin{tabular}{l | l | l l l | l l l l }
 		\toprule
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Object}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 &\textbf{ 0.69 }& \textbf{0.69}\\ 
-		\hline
-		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & \textbf{0.83 }&\textbf{ 0.83 }\\ 
-		\hline
-		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & \textbf{0.81}\\
-		\hline
-		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 &\textbf{ 0.75}\\
-		\hline
-		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & \textbf{0.65}\\
+		Baoshanlu  		& 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 &\textbf{ 0.69 }& \textbf{0.69}\\ 
+		\hline
+		Bus 			& 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & \textbf{0.83 }&\textbf{ 0.83 }\\ 
+		\hline
+		Dragon 			& 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & \textbf{0.81}\\
+		\hline
+		Garfield 		& 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 &\textbf{ 0.75}\\
+		\hline
+		Washington 		& 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & \textbf{0.65}\\
 		\bottomrule
 	\end{tabular}
-	\caption{Percent of error less than 11.5 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
+	\caption{Percentage of error of less than 11.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
 	\label{tab:eval-11d}
@@
 	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
+	\captionsetup{width=\linewidth}
+	\begin{tabular}{l | l | l l l | l l l l }
 		\toprule
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Object}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 &\textbf{ 0.92} &\textbf{ 0.92}\\ 
-		\hline
-		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & \textbf{0.94}\\ 
-		\hline
-		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & \textbf{0.95}\\
-		\hline
-		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 &\textbf{ 0.91} &\textbf{ 0.91}\\
-		\hline
-		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & \textbf{0.83} &\textbf{ 0.83}\\
+		Baoshanlu  		& 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 &\textbf{ 0.92} &\textbf{ 0.92}\\ 
+		\hline
+		Bus 			& 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & \textbf{0.94}\\ 
+		\hline
+		Dragon 			& 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & \textbf{0.95}\\
+		\hline
+		Garfield 		& 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 &\textbf{ 0.91} &\textbf{ 0.91}\\
+		\hline
+		Washington 		& 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & \textbf{0.83} &\textbf{ 0.83}\\
 		\bottomrule
 	\end{tabular}
-	\caption{Percent of error less than 22.5 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
+	\caption{Percentage of error of less than 22.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
 	\label{tab:eval-22d}
@@
 	\centering
-	\begin{tabular}{l l | l | l l l | l l l l }
+	\captionsetup{width=\linewidth}
+	\begin{tabular}{l | l | l l l | l l l l }
 		\toprule
-		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 &\textbf{ 0.97 }&\textbf{ 0.97} \\ 
-		\hline
-		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & \textbf{0.96} &\textbf{ 0.96} &\textbf{ 0.96 }\\ 
-		\hline
-		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & \textbf{0.98} \\
-		\hline
-		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & \textbf{0.95 }\\
-		\hline
-		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & \textbf{0.89} & \textbf{0.89}\\
+		Baoshanlu  		& 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 &\textbf{ 0.97 }&\textbf{ 0.97} \\ 
+		\hline
+		Bus 			& 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & \textbf{0.96} &\textbf{ 0.96} &\textbf{ 0.96 }\\ 
+		\hline
+		Dragon 			& 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & \textbf{0.98} \\
+		\hline
+		Garfield 		& 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & \textbf{0.95 }\\
+		\hline
+		Washington 		& 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & \textbf{0.89} & \textbf{0.89}\\
 		\bottomrule
 	\end{tabular}
-	\caption{Percent of error less than 30 degree of the evaluation dataset. \textit{SVD} neighbor size $ k=2 $}	
+	\caption{Percentage of error of less than 30 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
 	\label{tab:eval-30d}
@@
 
-The SVD approach can predict the normal map in a good way when the given point cloud is dense.
-As shown in Figure \ref{fig:svd-normal}.
+The \textit{SVD} approach can predict the normal map well if the given point cloud is dense.
+As shown in figure \ref{fig:svd-normal}.
 It can successfully predict the smooth surface of the dragon object, especially the flakes and the tails of the dragon.
 
-However, it failed in the areas such as hindleg, horn and the mouth, which consists mainly by sharp edges.
-This is because the neighbors points in these area do not hold the assumption of coplanarity well, the normals of these neighbors can be very different.
+However, it fails in the areas such as the hind leg, horn, and mouth, which are mainly composed of sharp edges.
+This is because the neighboring points in these areas do not hold well to the coplanarity assumption, the normals of these neighbors can be very different.
+
 \begin{figure}[th]
 	\centering
-	\includegraphics[width=.32\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
-	\includegraphics[width=.32\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
-	\includegraphics[width=.32\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}
-	\decoRule
-	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5. \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
-	\label{fig:svd-normal}
-\end{figure}
-The SVD approach is depended on a well-chosen parameter $ k $.
-Figure \ref{fig:svd-k-eval} shows the evaluation on different $ k $ values.
-When $ k=1 $, the average error of the whole image is the lowest one, most of the normals are close to the ground-truth but the outline edges, which are the areas that surface normal changed extremely sever.
-For the case $ k=2 $, the sharp edges are more smooth and cause more error, like the eyes area of the dragon.
-Compare to the first case, the outline edge error goes better.
-Most of the edge errors are reduced when $ k=2 $, since more neighbor points join the evaluation and it reduces the effect of outliers.
-However, for the area of horn outline, hindleg outline, the error goes worse.
-In this case, most of the neighbors of these points are outliers and thus failed this approach.
-$ k=3 $ and $ k=4 $ further increase the angle errors based on $ k=2 $.
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
-	\decoRule
-	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
-	\label{fig:svd-k-eval}
-\end{figure}
-
-The performance of neighbor based method is good enough for a well chosen $ k $.
-However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
-\begin{figure}[th]
-	\centering
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
-	\includegraphics[width=.24\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
-	\decoRule
-	\caption{SVD visual evaluation on a noised dragon model ($ 128\times128 $)}
-	\label{fig:svd-noise}
-\end{figure}
-
-\section{Visual Evaluation on GCNN}
-A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
-As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object.
-The image has an overall good performance on the whole object.
-A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
-In the same case, NOC model as shown in Figure \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area.
-CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
-Besides, the sharp area like the hindleg and the head area of dragon object, CNN model gives a much brighter error map (which means a higher angle error).
-Figure \ref{fig:gcnn-eval-more} shows more evaluation on GCNN model.
-
-We can get a good result from GCNN model, but from model ``Washington" we still can see it lacks the sharpness in the detail area like the face and clothes area.
-
-%% GCNN-eval
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
-		\caption{Image}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_groundtruth.png}
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_groundtruth.png}
 		\caption{GT}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_GCNN-GCNN.png}
-		\caption{Predict}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN.png}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_normal_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_error_SVD.png}
 		\caption{Error}
 	\end{subfigure}
-
 	\begin{tikzpicture}
@@
 	\end{tikzpicture}
-	\decoRule
-	\caption{GCNN visual evaluation. Window size $ 128\times128 $}
+
+	\decoRule
+	\caption{Normal map of a dragon object predicted by \textit{SVD}. k=1. (Resolution: $ 512\times 512 $) }
+	\label{fig:svd-normal}
+\end{figure}
+
+\begin{figure}[th]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/k-compare/k1.png}
+		\caption{$ k=1 $}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/k-compare/k2.png}
+		\caption{$ k=2 $}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/svd-synthetic/k-compare/k3.png}
+	\caption{$ k=3 $}
+\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/svd-synthetic/k-compare/k4.png}
+	\caption{$ k=4 $}
+\end{subfigure}
+	\begin{tikzpicture}
+	\node[text width=0.1\textwidth] at (11,-1) {90};
+	\node[inner sep=0pt] (input) at (8,-1)
+	{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+	\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Error map of \textit{SVD} with different $ k $ values. (Resolution: $ 512\times 512 $) }
+	\label{fig:svd-k-eval}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/noise/fancy_eval_0_point_cloud_noise.png}
+		\caption{Vertex}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/noise/fancy_eval_0_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/noise/fancy_eval_0_normal_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/noise/fancy_eval_0_error_SVD.png}
+		\caption{Error}
+	\end{subfigure}
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}	
+	\decoRule
+	\caption{\textit{SVD} visual evaluation on a noised dragon model, $ k=1 $, noise factor $ \mu $=50. (Resolution: $ 512\times 512 $) }
+	\label{fig:svd-noise}
+\end{figure}
+
+The SVD approach depends on a well-chosen neighborhood size $ k $.
+Figure \ref{fig:svd-k-eval} shows the evaluation for different $ k $ values.
+For $ k=1 $, the average angle error of the whole image is the smallest, most of the normals are close to the ground truth, but the outline edges, i.e., the areas where the surface normals have changed severely.
+In the $ k=2 $ case, the sharp edges are smoother and cause more error, such as the eye area of the dragon.
+Compared to the first case, the outline edge error is better.
+Most of the edge errors are reduced at $ k=2 $ because more neighbor points are included in the evaluation and the effect of outliers is reduced.
+However, in the area of the horn outline and the hindleg outline, the error becomes worse.
+In this case, most of the neighbors of these points are outliers.
+With $ k=3 $ and $ k=4 $, the average angular errors increase further compared to $ k=2 $.
+
+The performance of the neighborhood-based method is good enough for a well-chosen $ k $.
+However, in the case of a noisy point cloud as input, this approach fails because the noise does not satisfy the neighborhood assumption and also reduces the number of possible neighbors of each point for a fixed $ k $.
+See figure \ref{fig:svd-noise}.
+
+\section{Visual Evaluation on GCNN}
+A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}.
+As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object.
+The image has an overall good performance on the whole object.
+A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area.
+In the same case, NOC model as shown in Figure \ref{fig:gcnn-eval-multi-model} has an overall worse normal than GCNN model in the smooth area.
+CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN.
+Besides, the sharp area like the hindleg and the head area of dragon object, CNN model gives a much brighter error map (which means a higher angle error).
+Figure \ref{fig:gcnn-eval-more} shows more evaluation on GCNN model.
+
+We can get a good result from GCNN model, but from model ``Washington" we still can see it lacks the sharpness in the detail area like the face and clothes area.
+
+A qualitative evaluation of the object \textit{Dragon} is shown in figure \ref{fig:gcnn-eval}.
+As can be seen in the figure, the \textit{GCNN} model achieves an average angular error of 9 degrees for this object.
+The image shows an overall good performance for the whole object.
+A more detailed evaluation can be seen in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy is especially good on the smooth surface, such as the body area.
+In the same case, as shown in Figure \ref{fig:gcnn-eval-multi-model}, the \textit{NOC} model has an overall worse normal than the \textit{GCNN} model in the smooth area.
+The \textit{CNN} model retains the skip connection and thus yields a sharper result than the \textit{NOC} model, however, the smooth region of the model is still worse overall than the \textit{GCNN} model.
+In addition, the \textit{CNN} model yields a much brighter error map (implying a higher angular error) in the sharp regions such as the hind leg and the head region of the dragon object.
+Figure \ref{fig:gcnn-eval-more} shows further evaluation of the \textit{GCNN} model on other objects.
+The \textit{GCNN} model gives a good result, but for the \textit{Washington} model there is still a lack of sharpness in the detail areas such as the face and clothing.
+
+%% GCNN-eval
+\begin{figure}[H]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
+		\caption{Image}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_groundtruth.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_normal_GCNN-GCNN.png}
+		\caption{Predict}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN.png}
+		\caption{Error}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{GCNN visual evaluation. (Resolution: $ 128\times128 $)}
 	\label{fig:gcnn-eval}
@@
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{subfigure}[b]{0.18\linewidth}
@@
 	\decoRule
-	\caption{Zoom in of some regions of Dragon object (GCNN models). Window size $ 32\times32 $.}
+	\caption{Zoom in of some regions of Dragon object (GCNN models). (Resolution: $ 32\times32 $)}
 	\label{fig:gcnn-eval-synthetic-zoom-in}
@@
 	\decoRule
-	\caption{Comparison of GCNN based models.}
+	\caption{Comparison of GCNN based models. (Resolution: $ 128\times 128 $)}
 	\label{fig:gcnn-eval-multi-model}
@@
 
-As shown in figure \ref{fig:gcnn-cnn-feature map}, we also visualize the feature maps of the last gated convolution layer in the first up-sampling part for CNN and GCNN models, which corresponding the 128 feature maps with size $ 32\times 32 $ in width and height.
-The input data is also same dragon object that we used for normal visualization.
-For each feature map, we map the minimum value to the left-most color in the color bar and the maximum value to the right-most color in the color bar.
-We want to discuss the the difference of the feature maps between CNN, NOC and GCNN models.
-
-In order to see the result clearly, we use one color for the feature map visualization and use the brightness to distinguish the scale of the values, the white corresponds 1, the black corresponds 0, and the green-hue colors corresponds some values in between.
-
-From the CNN feature maps, we can see that the high value areas are usually more than one in a single feature map. Many of them have more than two bright areas. 
- For the GCNN feature maps, the brightness areas are usually concentrate only in one area or even one point.
-If we map the brightness areas to the original image, they correspond to the dense sharp edges areas, like mouse, horn, or tail of the dragon object, which is usually the hardest areas for normal estimation task.
-We suspect that these feature maps with few bright areas or only one bright area are the detail feature maps that for sharp edges inference.
-Based on this assumption, we can say that gated convolution layer describes the detail features in a more accurate way compare to standard convolution layer, since the brightness areas is smaller.
-Most of the GCNN feature maps usually has only one bright pixel with a few set of dim green pixels whereas CNN feature maps has more bright pixels with a lot of dim pixels all around the image.
-This accurate feature extraction provides our GCNN model a better performance on the detail area.
-
-Second, for the GCNN model,  we observed that some feature maps have very evenly bright areas distributed on the whole object.
-They are either overall dim or overall bright.
-Nevertheless, these feature maps are different from the detail feature maps with only few pixels with high values(brightness) but most of the other pixels with relatively low values.
-We suspect that these evenly value distributed features maps are the global feature maps that provide an over-view of the objects for a coarse prediction.
-So that they can cooperate with detail feature maps and further used to sharpen the prediction.
-It also holds for NOC model, since it does not equip with skip connections, most of the feature maps are global feature maps, so that the corresponding normal maps predicted by NOC model are more coarse than the GCNN model.
-For the CNN model, there also exists global feature maps, however, they are mostly incomplete, either missing the tails or missing the paws.
-Actually, these missing areas can usually be found in the detail feature maps.
-This also explained why the CNN detail feature maps has several bright areas in their detail feature maps.
-The detail feature maps and global feature maps are mixed together.
-And this unclear feature map extractor leads to reduce the performance on normal estimation task.
-
-%% feature maps comparison
+As shown in Figure \ref{fig:gcnn-cnn-feature map}, we visualize the feature maps of the last gated convolution layer in the first upsampling part for \textit{GCNN}, \textit{NOC} and \textit{CNN} models corresponding to the 128 feature maps with size $ 32\times 32 $ in width and height.
+The input data is also the same dragon object that we used for the normal visualization.
+For each feature map, we assign the minimum value to the leftmost color in the color bar and the maximum value to the rightmost color in the color bar.
+We want to discuss the difference of feature maps between these three models.
+
+To see the result clearly, we use green hue to visualize the feature maps and use brightness to distinguish the scale of the values: White corresponds to 1, Black corresponds to 0, and the colors with green hue correspond to some values in between.
+
 \begin{figure}[H]
 	\centering
-
-	\begin{subfigure}[b]{\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn.png}
-		\caption{CNN Feature Maps}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc.png}
-		\caption{NOC Feature Maps}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{\linewidth}
-	\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn.png}
-	\caption{GCNN Feature Maps}
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_normal_gcnn-cnn.png}
+		\caption{Normal Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_46.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_11.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_4.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_2.png}
+		\caption{Feature Map}
 	\end{subfigure}
@@
 	\decoRule
-	\caption{Feature maps of GCNN architecture based models at the first up-sampling gated convolution layer.
-All 128 feature maps are visualized for each model with normalization and filtered background.}
-	\label{fig:gcnn-cnn-feature map}
-\end{figure}
+	\caption{Some of feature maps of CNN model in up-sampling part on resolution $ 32\times32 $}
+	\label{fig:detail-feature-maps}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-noc.png}
+		\caption{Normal Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_39.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_45.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_93.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_104.png}
+		\caption{Feature Map}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {1};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
+		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Some of feature maps of NOC model in up-sampling part on resolution $ 32\times32 $}
+	\label{fig:detail-feature-maps}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-gcnn.png}
+		\caption{Normal Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_4.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_5.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_15.png}
+		\caption{Feature Map}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.19\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_127.png}
+		\caption{Feature Map}
+	\end{subfigure}
+
+	\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {1};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
+		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
+	\label{fig:detail-feature-maps}
+\end{figure}
+
+\begin{figure}[H]
+		\centering
+		\captionsetup{width=\linewidth}
+		\begin{minipage}{0.32\linewidth}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_113.png}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_102.png}
+				\end{subfigure}
+
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_65.png}
+					\caption{CNN}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_28.png}
+				\end{subfigure}
+		\end{minipage}
+		\begin{minipage}{0.32\linewidth}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_7.png}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_25.png}
+				\end{subfigure}
+
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_11.png}
+					\caption{NOC}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_127.png}
+				\end{subfigure}
+
+		\end{minipage}
+		\begin{minipage}{0.32\linewidth}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_1.png}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_9.png}
+				\end{subfigure}
+
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_24.png}
+					\caption{GCNN}
+				\end{subfigure}
+					\begin{subfigure}[t]{0.45\linewidth}
+				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_75.png}
+				\end{subfigure}
+
+		\end{minipage}
+
+		\begin{tikzpicture}
+			\node[text width=0.1\textwidth] at (11,-1) {1};
+			\node[inner sep=0pt] (input) at (8,-1)
+			{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
+			\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
+		\end{tikzpicture}
+		\decoRule
+		\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
+		\label{fig:global-feature-maps}
+\end{figure}
+
+From the CNN feature maps, we can see that the high-value areas usually represent more than one in a single feature map. Many of them have more than two bright areas. 
+In the GCNN feature maps, the bright areas are usually concentrated in only one area or even one point.
+When we map the bright areas onto the original image, they correspond to the dense, sharp areas, such as the mouse, horn, or tail of the kite object, which are usually the most difficult areas for the normal estimation task.
+We assume that these feature maps with few bright areas or only one bright area are the detail feature maps from which sharp edges can be inferred.
+Based on this assumption, we can say that the gated convolution layer describes the detail features more accurately compared to the standard convolution layer because the brightness regions are smaller.
+Most GCNN feature maps have only one bright pixel with a few green pixels, while CNN feature maps have more bright pixels with many dark pixels around the image.
+This accurate feature extraction gives our GCNN model better performance in the detailed areas.
+
+Second, with the GCNN model, we found that some feature maps have very uniformly bright areas across the entire object.
+They are either dark overall or bright overall.
+Nevertheless, these feature maps differ from the detail feature maps with only a few pixels with high values (brightness), but most other pixels with relatively low values.
+We suspect that these uniformly distributed feature maps are the global feature maps that provide an overview of the objects for rough prediction.
+Thus, they can cooperate with detailed feature maps to further refine the prediction.
+This is also true for the NOC model since it does not have skip connections and most of the feature maps are global feature maps, so the corresponding normal maps predicted by the NOC model are coarser than those of the GCNN model.
+For the CNN model, there are also global feature maps, but most of them are incomplete because either the tails or the paws are missing.
+These missing areas are usually found in the detail feature maps.
+This also explains why the CNN detail feature maps have several bright areas in their detail feature maps.
+The detail feature maps and the global feature maps are mixed together.
+And this unclear feature map extractor leads to a decrease in performance in normal estimation tasks.
 
@@
 \section{Visual Evaluation on Trip-Net}
-
-For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}.
-The Trip-Net uses illuminated information align with the geometry information achieves a sharper and more accurate result compare to the GCNN model.
+In the approach that uses an illuminated, calibrated RGBD image, the task is performed by the Trip-Net presented in \ref{sec:trip-net}.
+Based on illumination and geometry information, the Trip-Net achieves a sharper and more accurate result compared to the GCNN model.
 
@@
 \end{figure}
-
-The qualitative evaluation is shown in figure \ref{fig:trip-eval}.
-In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same.
-We also use the same input as we did in GCNN evaluation.
-The error of Trip-Net is $ 6^\circ $ whereas the GCNN is $ 9^\circ $.
+The qualitative evaluation is shown in Figure \ref{fig:trip-eval}.
+To show the effectiveness of the added illuminated information, the training settings are exactly the same for all models.
+We also use the same inputs as for the GCNN evaluation.
+The error of the Trip-Net is $ 6^\circ $, and that of the GCNN is $ 9^\circ $.
 
@@
 	\decoRule
-	\caption{Zoom in of detail regions ( $ 32\times32 $ ) of Dragon object (Trip-Net model).}
+	\caption{Zoom in of detail regions ($ 32\times32 $) of \textit{Dragon} object (Trip-Net).}
 	\label{fig:tripnet-eval-synthetic-zoom-in}
@@
 
-As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and also close to the ground-truth.
-The head region gives a sharper edge prediction.
-All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.
-
-Figure \ref{fig:tripnet-fusion-eval} compares different fusion times on Trip-Net model.
-We can see that model F1 with one fusion and and F2 with two fusions did not achieve a better result compare to GCNN model, which means the illuminated information doesn't work if we only consider the lower resolution feature maps.
-F3 model with 3 times fusion and F4 model with 4 times fusion give a much better result and also beyond the GCNN model.
-These two times fusion include high resolution features in the last up-sampling and the final output-size features before the standard convolution layers.
-We can observe the dragon scale in the figures, they are much sharper in the last two images.
+As can be seen in the Figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale of the dragon's body is much easier to see and is also closer to the ground truth.
+The head region provides a sharper edge prediction.
+All five sampled zoom-in regions in Trip-Net have better performance than GCNN.
+
+Figure \ref{fig:tripnet-fusion-eval} compares different fusion times on the Trip-Net model.
+It can be seen that the F1 with one fusion and F2 with two fusions models do not perform better compared to the GCNN model, which means that the illuminated information does not work when we consider only the lower resolution feature maps.
+The F3 model with three fusions and the F4 model with four fusions provide a much better result and also outperform the GCNN model.
+In these two fusion models, the high-resolution features are included.
+We can observe the dragon scale in the figures, it is much sharper in F3 and F4.
 
@@
 \section{Trining on Higher Resolution}
-We also trained our models on a higher resolution dataset with $ 512\times 512 $ in width and height for each scene.
-Higher resolution data gives more information about the surface feature using the same model compare to lower resolution.
-The benefit is, if we extract a fixed sized patch from the normal map, say $ 32 \times 32 $, it might correspond a hindleg area of the dragon object in $ 128\times 128 $ resolution but maybe only a toe in $ 512\times 512 $ resolution.
-Therefore if we still use the same kernel size in the network for the same dataset, (like we did with $ 3\times 3 $) the higher the resolution it has, the less area it will cover.
-Thus the surface in the same window size will more smooth and easy to be calculated the surface normal.
+We also trained our models on a higher resolution dataset with $ 512 \times 512 $ in width and height for each scene.
+Higher resolution data provides more information about surface features using the same model compared to lower resolutions.
+The advantage is that if we extract a fixed size patch from the normal map, say $32\times32$, it may correspond to a hind leg of the dragon object at a resolution of $128 \times 128$ scene, but at a resolution of $512\times 512$ scene, it may only correspond to a toe.
+Thus, if we still use the same kernel size in the network for the same data set (as in $ 3\times 3 $), the higher the resolution, the smaller the corresponding surface area.
+Thus, for the higher resolution, the surface becomes smoother and the surface normal can be computed more easily in a fixed size of area compare to lower resolution.
 This is a good thing.
-Because then we might only need to use these $ 32\times 32 $ points to calculate a toe in $ 512\times512 $ resolution image.
-But in $ 128\times128 $ resolution image, the same area $ 32\times32 $ might corresponding to entire  hindleg of the dragon object.
-In another word, we can also say that the higher resolution ``smooth" the object surface within the same size area.
-Thus the higher resolution helps the model to calculate a more accurate normal maps.
+Because then we may only need to use these $ 32\ times 32 $ points to calculate a toe in an image with $ 512\ times512 $ resolution.
+But in an image with a resolution of $ 128\times128 $, the same area $ 32\times32 $ could correspond to the entire hind leg of the dragon object.
+In other words.
+Thus, the higher resolution helps the model to compute a more accurate normal map.
 
@@
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{tabular}{l | l l l }
@@
 	\end{tabular}
-	\caption{High resolution dataset evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
+	\caption{High resolution dataset evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes. (Resolution: $ 512\times512 $)}	
 	\label{tab:high_resolution_eval}
@@
 
-Since our model is fully convolution network, the architecture keeps exactly same on the high resolution dataset.
-We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution.
-The training on high resolution network takes longer time but achieves a lower angle error.
+Since our model is a fully convolutional network, the architecture remains exactly the same on the high-resolution dataset.
+We use the same settings and the same model for training on a $ 512\times512 $ resolution dataset.
+Training with the high-resolution network takes longer, but results in a lower angular error.
 
@@
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{subfigure}[b]{0.48\linewidth}
@@
 
-A quantitative evaluation is shown in table \ref{tab:high_resolution_eval}.
-It follows the same performance ranking compares to lower resolution, which is GCNN better than SVD approach and Trip-Net slightly better than GCNN.
-The accuracy is 99 \% in the $ 30^\circ $ metric.
-In mean error metric, the error is  $ 5^\circ $.
-A qualitative evaluation is shown in figure \ref{fig:trip-eval-high-resolution}.
-We use a figure object with both smooth area (the belly and arm) and highly detailed area with sharp surface (the uneven surface of stone table) for evaluation.
-Our models gives an  $ 5^\circ $ in mean degree metric.
-
-A comparison with other models is shown in figure \ref{fig:trip-eval-compare}.
-Note that we use the same dragon object (but slightly moved the place since they have been captured in different time in high resolution dataset) for evaluation this time as a coherent comparison with low resolution dataset.
-The SVD based approach gives a good result ($ 8.88^\circ $ in mean degree metric).
-Like we discussed, the surface are relatively more smooth if we keep the same window size for normal inference.
-In the high resolution scenes, although the percentage of missing pixels in a fixed windows are remain the same compare to small resolution scenes, but the remain valid pixels in the same window size are on a relatively flat plane thus they are good enough for an accurate normal inference.
-However, as we expected, we can still see the high degree error in the sharp edges of the dragon object, like the horns and the hindleg areas as shown in \ref{fig:trip-eval-compare}.
+A quantitative evaluation is shown in Table \ref{tab:high_resolution_eval}.
+It follows the same performance ranking compared to lower resolutions, i.e.
+GCNN is better than the SVD approach and Trip-Net is slightly better than GCNN.
+The accuracy is 99\% in the $30^\circ $ metric.
+In the average error metric, the error is $ 5^\circ $.
+A qualitative evaluation is shown in Figure \ref{fig:trip-eval-high-resolution}.
+We use a figure object with smooth regions (belly and arm) and highly detailed regions with sharp surfaces (the uneven surface of the stone table) for the evaluation.
+Our models yield a $ 5^\circ $ in the middle degree of the metric.
+
+A comparison with other models is shown in Figure \ref{fig:trip-eval-compare}.
+Note that we use the same dragon object (with slightly shifted location since they were collected at different times in the high-resolution dataset) for the assessment to allow a coherent comparison with the low-resolution dataset.
+The \textit{SVD} approach yields a good result ($8.88^\circ $ in the average degree metric).
+As mentioned earlier, the surfaces are relatively smoother when we keep the same window size for normal inference.
+In the high-resolution scenes, the percentage of missing pixels in a fixed window is the same as in the low-resolution scenes, but the remaining valid pixels in the same window size are on a relatively flat plane and are therefore good enough for accurate normal inference.
+However, as expected, we can still see the high-level error in the sharp edges of the dragon object, such as the horns and the hind leg areas, as shown in Figure \ref{fig:trip-eval-compare}.
 
@@
 	\decoRule
-	\caption{Comparison on high resolution dataset ($ 512\times 512 $) .}
+	\caption{Comparison on high resolution dataset ($ 512\times 512 $).}
 	\label{fig:trip-eval-compare}
@@
 \section{Training on Real-Dataset}
-We also applied our model on a dataset that captured by a light scanner in our laboratory in order to see our model's applicability to the real-dataset.
-For the geometry information based approach, we directly use the GCNN model that trained on synthetic dataset since it only require the depth map as input, the scenarios of two dataset are the same.
-For the illuminated calibrated RGB-D image based approach, the model has to be refined based on the real-dataset, since the light intensity and position, camera matrix are different.
-We refined the Trip-Net based on a pre-trained GCNN model with the same settings in previous experiments, and observe the results.
+We also applied our model to a dataset acquired with a structured light scanner in our laboratory to test the applicability of our model to the real dataset.
+For the approach based on geometry information, we directly use the GCNN model trained on synthetic datasets since it only needs the depth map as input and the scenarios of the two datasets are the same.
+For the approach based on illuminated calibrated RGB-D images, the model needs to be refined based on the real dataset because the light intensity, position, and camera matrix are different.
+We have refined the Trip-Net based on a pre-trained GCNN model with the same settings in previous experiments.
 
@@
 	\end{tabular}
-	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes in real dataset.}	
+	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes in Real-Dataset.}	
 	\label{tab:real_eval}
@@
 
-Since in the real-dataset, we don't have a ground-truth for evaluation.
-But if we see directly from the visualization in figure \ref{fig:trip-eval-real}, we can see that Trip-Net approach has good ability to  ``mend" the missing pixels in the scenes and also gives a sharp result.
-The folds on the gowns are recognizable and even countable.
-Figure \ref{fig:real_eval_compare} compares the Trip-Net with other approaches.
-
-But we also noted that the big holes in the base stage remains in the normal maps.
-These big holes corresponds to the shinny and dark texture area, which common exist in the depth map captured by the scanners.
-Since these big holes are related with only special feature areas and also has irregular shapes, we didn't simulate this type of noise in the synthetic dataset but only with a sparse binary mask.
-Thus our models failed to mend missing big holes in the estimated normal map.
-This can be a further work of this topic, that find a way to generate high similar depth map noise to get a more robust training dataset.
+We do not have a ground truth for evaluation in the Real-Dataset.
+But if we look directly at the visualization in Figure \ref{fig:trip-eval-real}, we can see that the Trip-Net approach is well able to ``enhance'' the missing pixels in the scenes and also gives a sharp result.
+The wrinkles on the clothes are detectable and even countable.
+Figure \ref{fig:real_eval_compare} compares the trip net with other approaches.
+
+However, we also noticed that the large holes in the base level are preserved in the Normal Maps.
+These large holes correspond to the shiny and dark texture regions that are often present in the depth map captured by the scanners.
+Since these large holes are only related to specific feature areas and also have irregular shapes, we did not simulate this type of noise in the synthetic dataset, but only with a sparse binary mask.
+Therefore, our models could not fill in missing large holes in the estimated normal map.
+Further work on this topic could be to find a way to generate a very similar depth map noise to obtain a more robust training dataset.
 
@@
 	\centering
-	\begin{subfigure}[b]{0.30\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_normal_An2-real-resume-616.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.30\linewidth}
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.32\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_groundtruth.png}
@@
 	\end{subfigure}
-
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.32\linewidth}
+	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_normal_An2_no_mask.png}
+	\caption{Trip-Net}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_normal_An2-real-resume-616.png}
+		\caption{Trip-Net (No-Mask)}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.32\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_point_cloud_noise.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.32\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_img.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.20\linewidth}
+	\begin{subfigure}[b]{0.32\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_22_error_An2-real-resume.png}
@@
 	\centering
-
+	\captionsetup{width=\linewidth}
 	\begin{subfigure}[b]{0.2\linewidth}

### 2022-08-11 create_dataset_multi_lights.py

@@ -29,8 +29,8 @@ args = parser.parse_args()
 
 
 def convert2training_tensor(path, k, output_type='normal'):
-    width = 512
-    light_num = 1
+    width = 128
+    light_num = 10
     if not os.path.exists(str(path)):
         raise FileNotFoundError
     if not os.path.exists(str(path / "tensor")):
@@ -58,7 +58,8 @@ def convert2training_tensor(path, k, output_type='normal'):
         light_pos_list = []
         for i in range(light_num):
             if output_type == "normal":
-                light_posi = np.array(data[f'lightPos'])
+                # light_posi = np.array(data[f'lightPos'])
+                light_posi = np.array(data[f'lightPos{str(i)}'])
             else:
                 light_posi = np.array(data[f'lightPos{str(i)}'])
             # light_posi = np.array(data[f'lightPos'])
@@ -173,14 +174,17 @@ def convert2training_tensor(path, k, output_type='normal'):
 
 
 if args.data in ["synthetic128", "synthetic256", "synthetic512", "synthetic64"]:
-    for folder in ["baoshanlu", "bus", "dragon", "garfield", "washington"]:
+    # for folder in ["baoshanlu", "bus", "dragon", "garfield", "washington"]:
+    for folder in ["selval"]:
 
         if args.machine == "remote":
             original_folder = config.synthetic_data_dfki / args.data / folder
             dataset_folder = config.synthetic_data_noise_dfki / args.data / folder
         elif args.machine == 'local':
-            original_folder = config.synthetic_data / args.data / "seperate" / folder
-            dataset_folder = config.synthetic_data_noise_local / args.data / "seperate" / folder
+            # original_folder = config.synthetic_data / args.data / "seperate" / folder
+            original_folder = config.synthetic_data / args.data / folder
+            # dataset_folder = config.synthetic_data_noise_local / args.data / "seperate" / folder
+            dataset_folder = config.synthetic_data_noise_local / args.data / folder
         else:
             raise ValueError
 

### 2022-08-11 help_funs/worksheet.py

@@ -66,6 +66,16 @@ def visual_albedo_histo(albedo_gt):
 
 
 if __name__ == '__main__':
+    normal_file = str(config.paper_pic / "comparison_real" / "fancy_eval_20_normal_An2-real-resume-616.png")
+    gt_file = str(config.paper_pic / "comparison_real" / "fancy_eval_20_groundtruth.png")
+
+    normal = file_io.load_24bitNormal(normal_file)
+    gt = file_io.load_24bitNormal(gt_file)
+    mask = gt.sum(axis=-1) == 0
+    normal[mask] = 0
+    cv.imwrite(str(config.paper_pic / "comparison_real" / "fancy_eval_20_normal_An2_no_mask.png"),
+               cv.cvtColor(mu.visual_normal(normal, "", histogram=False), cv.COLOR_RGB2BGR))
+
     training_tensor, gt_tensor = load_a_training_tensor()
     vertex = training_tensor[:, :3, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()
     light_input = training_tensor[:, 13:16, :, :].permute(2, 3, 1, 0).squeeze(-1).numpy()

### 2022-08-11 workspace/nnnn/eval_feature_maps.py

@@ -20,7 +20,7 @@ datasize = args.datasize
 font_scale = 1
 
 # read data
-test_0 = torch.load(np.array(sorted(glob.glob(str(dataset_path / f"*_0_*"), recursive=True)))[7])  # 7
+test_0 = torch.load(np.array(sorted(glob.glob(str(dataset_path / f"*_0_*"), recursive=True)))[2])  # 7
 
 # unpack model
 test_0_tensor = test_0['input_tensor'].unsqueeze(0)
@@ -87,6 +87,12 @@ for model_idx, (name, model) in enumerate(models.items()):
     feature_map_conv1 = []
     feature_map_conv2 = []
 
+    feature_maps = []
+
+    p50 = 0
+    p75 = 0
+    p95 = 0
+
     model.normal_net.dconv1.register_forward_hook(get_activation('dconv1'))
     model.normal_net.dconv2.register_forward_hook(get_activation('dconv2'))
     model.normal_net.dconv3.register_forward_hook(get_activation('dconv3'))
@@ -144,6 +150,7 @@ for model_idx, (name, model) in enumerate(models.items()):
         feature_map[-1, :] = 255
         feature_map[:, 0] = 255
         feature_map[:, -1] = 255
+        cv.imwrite(str(folder_path / f"feature_map_{name}_{idx}.png"), cv.applyColorMap(feature_map, CV_COLOR))
         feature_map_uconv1.append(cv.applyColorMap(feature_map, CV_COLOR))
 
     act = activation['uconv2'].squeeze().to("cpu")

### 2022-08-11 paper/Chapters/Chapter06.tex
update paper

--- 2022-06-19 paper/Chapters/Chapter06.tex
@@
 %----------------------------------------------------------------------------------------
-Gated convolution neural network...
+
+In our approaches, two networks have been proposed.
+The first network called GCNN is used for the geometry information based approach, which is our baseline method.
+It is particularly well suited for semi-dense input data, which is supported by the gated convolution layer design.
+With this network, we have achieved more accurate normal inference than with a standard layered network based on the same architecture.
+We also show the effectiveness of skip connectivity in the U-Net.
+In addition, the full convolution design allows us to use images with different resolutions as input.
+
+The second network is called Trip-Net and is based on the GCNN model.
+It is designed for illumination-calibrated RGB-D image-based approaches.
+This model uses the GCNN architecture three times to process vertex map, light map and image separately.
+We have also found that 4 fusions of the 3 pipes in our models is the key to performance improvement.
+Our experiments show that the models trained on illuminated calibrated RGB-D images perform better than an approach based only on geometry information and provide more sharpness in the normal map.
+
+We also studied the performance of our models on a real dataset and compared it with traditional methods such as the SVD-based approach.
+In particular, our gated convolution layer-based model can fill in the missing pixels in the real input data and maintain an accurate normal estimate, while the optimization-based approach such as SVD cannot.
+
+We collected 55 high-resolution 3D models from the Internet and used them to create our data.
+Specifically, we use an RGB-D camera, an ambient light, and a directional light to collect thousands of scenes.
+The scene generation is simulated by the Unity game engine.
+In addition, we also simulated noise in our synthetic dataset using an uniformly distributed drop to fit our model and adopt it with semi-dense input data.
+However, for the large missing regions, we did not generate similar noise in the training set, which results in our model not being able to fill the holes in the real data.
+Exploring an algorithm to mimic sensor noise to generate more realistic data for training can be a direction for further work.

### 2022-08-11 help_funs/fm_analysis.py

@@ -1,0 +1,73 @@
+import numpy as np
+from PIL import Image
+import matplotlib.pyplot as plt
+import os.path
+from pathlib import Path
+
+path = "/Users/jing/Downloads/feature_maps/cylinder/"
+
+
+def line_chart(data, path, labels, x=None, title=None, x_scale=None, y_scale=None, y_label=None, show=False,
+               log_y=False, cla_leg=False):
+    if data.shape[1] <= 1:
+        return
+
+    if y_scale is None:
+        y_scale = [1, 1]
+    if x_scale is None:
+        x_scale = [1, 1]
+
+    for i, row in enumerate(data):
+        if x is None:
+            x = np.arange(row.shape[0]) * x_scale[1] + x_scale[0]
+        y = row
+        plt.plot(x, y, label=labels[i], lw=1)
+
+    if title is not None:
+        plt.title(title)
+
+    if y_label is not None:
+        plt.ylabel(y_label)
+
+    if log_y:
+        plt.yscale('log')
+
+    plt.legend()
+    plt.grid(True)
+
+    if not os.path.exists(str(path)):
+        os.mkdir(path)
+    plt.savefig(
+        str(Path(path) / f"{title}_{y_label}.png"))
+
+    if show:
+        plt.show()
+    if cla_leg:
+        plt.cla()
+
+
+threshold_bright = 50
+bright_percent_list = np.zeros(shape=(3, 128))
+# read a feature map
+for model_idx, prefix in enumerate(["feature_map_gcnn-noc_", "feature_map_gcnn-gcnn_", "feature_map_gcnn-cnn_"]):
+    for idx in range(128):
+        print(f"current fm idx: {idx}")
+        fm_file = path + prefix + str(idx) + ".png"
+        fm_512_img = Image.open(fm_file)
+        fm_512 = np.asarray(fm_512_img)
+
+        fm_32 = np.zeros(shape=(32, 32))
+        for row_idx in range(16):
+            for col_idx in range(16):
+                patch_3c = fm_512[row_idx * 32:(row_idx + 1) * 32, col_idx * 32:(col_idx + 1) * 32, :]
+                patch_1c = (patch_3c[:, :, 0] + patch_3c[:, :, 1] * 2 + patch_3c[:, :, 2]) / 4
+                median_value = np.median(patch_1c)
+                fm_32[row_idx, col_idx] = median_value
+        mask = fm_32 == 0
+
+        bright_pixel_percent = fm_32.sum()
[…]

### 2022-08-11 paper/Chapters/Chapter05.tex
update paper

@@
 
+\begin{flushright}
+
+\end{flushright}
 The \textit{GCNN} is the base model of the whole work.
@@
 
-As shown in Figure \ref{fig:gcnn-cnn-feature map}, we visualize the feature maps of the last gated convolution layer in the first upsampling part for \textit{GCNN}, \textit{NOC} and \textit{CNN} models corresponding to the 128 feature maps with size $ 32\times 32 $ in width and height.
-The input data is also the same dragon object that we used for the normal visualization.
-For each feature map, we assign the minimum value to the leftmost color in the color bar and the maximum value to the rightmost color in the color bar.
-We want to discuss the difference of feature maps between these three models.
-
-To see the result clearly, we use green hue to visualize the feature maps and use brightness to distinguish the scale of the values: White corresponds to 1, Black corresponds to 0, and the colors with green hue correspond to some values in between.
-
+As shown in the figure, we visualize the feature maps of the last gated convolution layer in the first upsampling part for the models \textit{GCNN}, \textit{NOC} and \textit{CNN}, which correspond to 128 feature maps with size $ 32\times 32 $ in width and height.
+The input data is also the same dragon object we used for the visualization.
+For each feature map, we assign the minimum value to the color on the far left of the color bar and the maximum value to the color on the far right of the color bar.
+We will now discuss the differences between these models.
+
+To make the result clear, we use the green hue to visualize the feature maps and the brightness to distinguish the value scale: White corresponds to 1, Black corresponds to 0, and the colors with green hue correspond to some values in between.
+
+%% CNN detail
 \begin{figure}[H]
@@
 	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_normal_gcnn-cnn.png}
+		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-cnn.png}
 		\caption{Normal Map}
@@
 	\caption{Some of feature maps of CNN model in up-sampling part on resolution $ 32\times32 $}
-	\label{fig:detail-feature-maps}
-\end{figure}
-
+	\label{fig:cnn-detail-feature-maps}
+\end{figure}
+
+%% NOC Detail
 \begin{figure}[H]
@@
 	\caption{Some of feature maps of NOC model in up-sampling part on resolution $ 32\times32 $}
-	\label{fig:detail-feature-maps}
-\end{figure}
-
+	\label{fig:noc-detail-feature-maps}
+\end{figure}
+
+We roughly distinguish feature maps into two types.
+The first type of feature maps learns the details of the target object that correspond to the feature map with sparse high values.
+In our example, the detail areas are the tail, head, paw, etc.
+Using the CNN feature maps, we could see that several detail areas in a feature map have high values.
+For example, in Figure \ref{fig:cnn-detail-feature-maps} (b), the values in the tail, hind leg, and front leg areas of the dragon object are especially high than other areas.
+These high valued areas are exactly the detailed areas and the areas with higher errors in the evaluation.
+These feature maps show that the CNN model assigns high value to several detailed parts in a single feature map.
+In the case of the NOC model, one detailed part instead of several detailed parts is usually highly valued in a single feature map, as shown in Figure \ref{fig:noc-detail-feature-maps} (e).
+We can see that the hind legs are light, while other detailed areas such as the head or tail are dark.
+The NOC model uses one feature map to deal with only one specific detailed area.
+The GCNN model follows the patterns we found in NOC, each feature map has only one specific area that is very bright, and the rest of the areas are relatively dark.
+In addition, the bright area in the GCNN model is more concentrated than in the NOC model because of the skip connection, as can be seen in Figure \ref{fig:gcnn-detail-feature-maps}.
+
+%% GCNN detail
 \begin{figure}[H]
@@
 	\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
-	\label{fig:detail-feature-maps}
-\end{figure}
-
+	\label{fig:gcnn-detail-feature-maps}
+\end{figure}
+
+%% global compare
 \begin{figure}[H]
@@
 
-From the CNN feature maps, we can see that the high-value areas usually represent more than one in a single feature map. Many of them have more than two bright areas. 
-In the GCNN feature maps, the bright areas are usually concentrated in only one area or even one point.
-When we map the bright areas onto the original image, they correspond to the dense, sharp areas, such as the mouse, horn, or tail of the kite object, which are usually the most difficult areas for the normal estimation task.
-We assume that these feature maps with few bright areas or only one bright area are the detail feature maps from which sharp edges can be inferred.
-Based on this assumption, we can say that the gated convolution layer describes the detail features more accurately compared to the standard convolution layer because the brightness regions are smaller.
-Most GCNN feature maps have only one bright pixel with a few green pixels, while CNN feature maps have more bright pixels with many dark pixels around the image.
-This accurate feature extraction gives our GCNN model better performance in the detailed areas.
-
-Second, with the GCNN model, we found that some feature maps have very uniformly bright areas across the entire object.
-They are either dark overall or bright overall.
-Nevertheless, these feature maps differ from the detail feature maps with only a few pixels with high values (brightness), but most other pixels with relatively low values.
-We suspect that these uniformly distributed feature maps are the global feature maps that provide an overview of the objects for rough prediction.
-Thus, they can cooperate with detailed feature maps to further refine the prediction.
-This is also true for the NOC model since it does not have skip connections and most of the feature maps are global feature maps, so the corresponding normal maps predicted by the NOC model are coarser than those of the GCNN model.
-For the CNN model, there are also global feature maps, but most of them are incomplete because either the tails or the paws are missing.
-These missing areas are usually found in the detail feature maps.
-This also explains why the CNN detail feature maps have several bright areas in their detail feature maps.
-The detail feature maps and the global feature maps are mixed together.
-And this unclear feature map extractor leads to a decrease in performance in normal estimation tasks.
-
-\newpage 
+The second type of feature maps learns the global features of the target object corresponding to the feature map with dense, uniformly bright values.
+This type of feature maps provides an overview of the objects for rough prediction.
+As can be seen in Figure \ref{fig:global-feature-maps}, the global feature maps have much bigger bright areas compared to the detailed feature maps.
+In the CNN model, the bright areas are seen in most parts of the object, but usually one or more specific areas are missing, such as the front or back legs.
+The global feature maps in the NOC model are either incomplete or blurry, so the global features are not learned properly.
+The GCNN model provides more complete global feature maps.
+The outline of the dragon is particularly easy to see compared to the other two models.
+
+A complete version of the feature maps in this layer is shown in Figure \ref{fig:gcnn-cnn-feature map} in Appendix \ref{AppendixC}.
+
 \section{Visual Evaluation on Trip-Net}
@@
 
-We do not have a ground truth for evaluation in the Real-Dataset.
-But if we look directly at the visualization in Figure \ref{fig:trip-eval-real}, we can see that the Trip-Net approach is well able to ``enhance'' the missing pixels in the scenes and also gives a sharp result.
-The wrinkles on the clothes are detectable and even countable.
-Figure \ref{fig:real_eval_compare} compares the trip net with other approaches.
-
-However, we also noticed that the large holes in the base level are preserved in the Normal Maps.
-These large holes correspond to the shiny and dark texture regions that are often present in the depth map captured by the scanners.
-Since these large holes are only related to specific feature areas and also have irregular shapes, we did not simulate this type of noise in the synthetic dataset, but only with a sparse binary mask.
-Therefore, our models could not fill in missing large holes in the estimated normal map.
-Further work on this topic could be to find a way to generate a very similar depth map noise to obtain a more robust training dataset.
-
-\begin{figure}[th]
+\begin{figure}[H]
 	\centering
@@
 %% real eval comparison
-\begin{figure}[th]
-	\centering
-	\captionsetup{width=\linewidth}
-	\begin{subfigure}[b]{0.2\linewidth}
+\begin{figure}[H]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.2\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.2\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.2\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
@@
 
-	\begin{subfigure}[b]{0.2\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/00008.image0.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.2\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_SVD.png}
@@
 	\end{subfigure}	
-	\begin{subfigure}[b]{0.2\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_NNNN-512.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.2\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_An2-real-resume.png}
@@
 \end{figure}
+
+We do not have a ground truth for evaluation in the Real-Dataset.
+But if we look directly at the visualization in Figure \ref{fig:trip-eval-real}, we can see that the Trip-Net approach is well able to ``enhance'' the missing pixels in the scenes and also gives a sharp result.
+The wrinkles on the clothes are detectable and even countable.
+Figure \ref{fig:real_eval_compare} compares the trip net with other approaches.
+
+However, we also noticed that the large holes in the base level are preserved in the Normal Maps.
+These large holes correspond to the shiny and dark texture regions that are often present in the depth map captured by the scanners.
+Since these large holes are only related to specific feature areas and also have irregular shapes, we did not simulate this type of noise in the synthetic dataset, but only with a sparse binary mask.
+Therefore, our models could not fill in missing large holes in the estimated normal map.
+Further work on this topic could be to find a way to generate a very similar depth map noise to obtain a more robust training dataset.

### 2022-08-12 paper/Chapters/Chapter05.tex
update paper

@@
 The advantage is that if we extract a fixed size patch from the normal map, say $32\times32$, it may correspond to a hind leg of the dragon object at a resolution of $128 \times 128$ scene, but at a resolution of $512\times 512$ scene, it may only correspond to a toe.
-Thus, if we still use the same kernel size in the network for the same data set (as in $ 3\times 3 $), the higher the resolution, the smaller the corresponding surface area.
+Thus, if we still use the same kernel size in the network for the same data set ($ 3\times 3 $), the higher the resolution, the smaller the corresponding surface area.
 Thus, for the higher resolution, the surface becomes smoother and the surface normal can be computed more easily in a fixed size of area compare to lower resolution.
 This is a good thing.
-Because then we may only need to use these $ 32\ times 32 $ points to calculate a toe in an image with $ 512\ times512 $ resolution.
+Because then we may only need to use these $ 32\times 32 $ points to calculate a toe in an image with $ 512\times512 $ resolution.
 But in an image with a resolution of $ 128\times128 $, the same area $ 32\times32 $ could correspond to the entire hind leg of the dragon object.

### 2022-08-12 paper/Chapters/Chapter06.tex
update paper

@@
 This model uses the GCNN architecture three times to process vertex map, light map and image separately.
-We have also found that 4 fusions of the 3 pipes in our models is the key to performance improvement.
-Our experiments show that the models trained on illuminated calibrated RGB-D images perform better than an approach based only on geometry information and provide more sharpness in the normal map.
+We also found that 4 fusions of the 3 pipes in our models is the key point to improve the performance.
+Based on our proposed dataset with resolution $ 128\times 128 $, the experiments show that the models trained on illuminated calibrated RGB-D images improve the accuracy by $ 11.1\% $ of the average degree error compared to the geometry information based approach, which provides more sharpness in the normal map.
 

### 2022-08-12 paper/Chapters/Chapter04.tex
update paper

@@
 	\captionsetup{width=\linewidth}
-	{\includegraphics[width=0.49\textwidth]{./Figures/Data_Extreme.png}}
-	{\includegraphics[width=0.49\textwidth]{./Figures/Data_Range.png}}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\includegraphics[width=\textwidth]{./Figures/Data_Extreme.png}
+		\caption{Extreme Values in each axis }
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\includegraphics[width=\textwidth]{./Figures/Data_Range.png}
+		\caption{Vertex Range in each axis}
+	\end{subfigure}
 	\decoRule
-	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
+	\caption{The position fluctuation of the points in 100 Vertex Maps. 
+		Left: Extreme values in 3 axes; Right: Vertex range in 3 axis.}
 	\label{fig:data_range}
@@
 \begin{table}[th]
-
 	\centering
+	\captionsetup{width=\linewidth}
 	\begin{tabular}{c | c c c}

### 2022-08-12 paper/Chapters/Chapter05.tex
update paper

@@
 	\captionsetup{width=\linewidth}
-	\begin{subfigure}[b]{0.32\linewidth}
+		\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_point_cloud_no_noise.png}
+		\caption{Vertex}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_groundtruth.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.32\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_normal_SVD.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.32\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
 		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_error_SVD.png}
@@
 	\end{subfigure}
-
-	\decoRule
-	\caption{Zoom in of some regions of Dragon object (GCNN models). (Resolution: $ 32\times32 $)}
+		\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
+	\decoRule
+	\caption{Zoom in of some regions of Dragon object based on GCNN. (Resolution: $ 32\times32 $)}
 	\label{fig:gcnn-eval-synthetic-zoom-in}
@@
 	\end{subfigure}
-
+		\begin{tikzpicture}
+		\node[text width=0.1\textwidth] at (11,-1) {90};
+		\node[inner sep=0pt] (input) at (8,-1)
+		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+	\end{tikzpicture}
 	\decoRule
@@
 
-%% CNN detail
+%% global compare
 \begin{figure}[H]
@@
 	\captionsetup{width=\linewidth}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-cnn.png}
-		\caption{Normal Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
+	\begin{minipage}{0.32\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_2.png}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_46.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
+		\end{subfigure}
+
+		\begin{subfigure}[t]{0.45\linewidth}
 			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_11.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
+			\caption{CNN}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_4.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_2.png}
-		\caption{Feature Map}
-	\end{subfigure}
+		\end{subfigure}
+	\end{minipage}
+	\begin{minipage}{0.32\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_39.png}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_45.png}
+		\end{subfigure}
+
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_93.png}
+			\caption{NOC}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_104.png}
+		\end{subfigure}
+
+	\end{minipage}
+	\begin{minipage}{0.32\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_4.png}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_5.png}
+		\end{subfigure}
+
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_15.png}
+			\caption{GCNN}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_127.png}
+		\end{subfigure}
+
+	\end{minipage}
 
@@
 	\decoRule
-	\caption{Some of feature maps of CNN model in up-sampling part on resolution $ 32\times32 $}
-	\label{fig:cnn-detail-feature-maps}
-\end{figure}
+	\caption{Some of detail feature maps of CNN, NOC, GCNN models in up-sampling part on resolution $ 32\times32 $}
+	\label{fig:detail-feature-maps}
+\end{figure}
+
+%% CNN detail
+%\begin{figure}[H]
+%	\centering
+%	\captionsetup{width=\linewidth}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-cnn.png}
+%		\caption{Normal Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_46.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_11.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_4.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_2.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	
+%	\begin{tikzpicture}
+%		\node[text width=0.1\textwidth] at (11,-1) {1};
+%		\node[inner sep=0pt] (input) at (8,-1)
+%		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
+%		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
+%	\end{tikzpicture}
+%	\decoRule
+%	\caption{Some of feature maps of CNN model in up-sampling part on resolution $ 32\times32 $}
+%	\label{fig:cnn-detail-feature-maps}
+%\end{figure}
 
 %% NOC Detail
-\begin{figure}[H]
-	\centering
-	\captionsetup{width=\linewidth}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-noc.png}
-		\caption{Normal Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_39.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_45.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_93.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_104.png}
-		\caption{Feature Map}
-	\end{subfigure}
-
-	\begin{tikzpicture}
-		\node[text width=0.1\textwidth] at (11,-1) {1};
-		\node[inner sep=0pt] (input) at (8,-1)
-		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
-		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
-	\end{tikzpicture}
-	\decoRule
-	\caption{Some of feature maps of NOC model in up-sampling part on resolution $ 32\times32 $}
-	\label{fig:noc-detail-feature-maps}
-\end{figure}
+%\begin{figure}[H]
+%	\centering
+%	\captionsetup{width=\linewidth}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-noc.png}
+%		\caption{Normal Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_39.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_45.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_93.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_104.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	
+%	\begin{tikzpicture}
+%		\node[text width=0.1\textwidth] at (11,-1) {1};
+%		\node[inner sep=0pt] (input) at (8,-1)
+%		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
+%		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
+%	\end{tikzpicture}
+%	\decoRule
+%	\caption{Some of feature maps of NOC model in up-sampling part on resolution $ 32\times32 $}
+%	\label{fig:noc-detail-feature-maps}
+%\end{figure}
+%
 
@@
 Using the CNN feature maps, we could see that several detail areas in a feature map have high values.
-For example, in Figure \ref{fig:cnn-detail-feature-maps} (b), the values in the tail, hind leg, and front leg areas of the dragon object are especially high than other areas.
+For example, if we observe one feature map in Figure \ref{fig:detail-feature-maps} (a), the values in the tail, hind leg, and front leg areas of the dragon object are especially high than other areas.
 These high valued areas are exactly the detailed areas and the areas with higher errors in the evaluation.
 These feature maps show that the CNN model assigns high value to several detailed parts in a single feature map.
-In the case of the NOC model, one detailed part instead of several detailed parts is usually highly valued in a single feature map, as shown in Figure \ref{fig:noc-detail-feature-maps} (e).
+In the case of the NOC model, one detailed part instead of several detailed parts is usually highly valued in a single feature map, as shown in Figure \ref{fig:detail-feature-maps} (b).
 We can see that the hind legs are light, while other detailed areas such as the head or tail are dark.
@@
 The GCNN model follows the patterns we found in NOC, each feature map has only one specific area that is very bright, and the rest of the areas are relatively dark.
-In addition, the bright area in the GCNN model is more concentrated than in the NOC model because of the skip connection, as can be seen in Figure \ref{fig:gcnn-detail-feature-maps}.
-
-%% GCNN detail
+In addition, the bright area in the GCNN model is more concentrated than in the NOC model because of the skip connection, as can be seen in Figure \ref{fig:detail-feature-maps} (c).
+
+%
+%%% GCNN detail
+%\begin{figure}[H]
+%	\centering
+%	\captionsetup{width=\linewidth}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-gcnn.png}
+%		\caption{Normal Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_4.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_5.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_15.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.19\linewidth}
+%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_127.png}
+%		\caption{Feature Map}
+%	\end{subfigure}
+%	
+%	\begin{tikzpicture}
+%		\node[text width=0.1\textwidth] at (11,-1) {1};
+%		\node[inner sep=0pt] (input) at (8,-1)
+%		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
+%		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
+%	\end{tikzpicture}
+%	\decoRule
+%	\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
+%	\label{fig:gcnn-detail-feature-maps}
+%\end{figure}
+%
+
+%% global compare
 \begin{figure}[H]
@@
 		\captionsetup{width=\linewidth}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-gcnn.png}
-		\caption{Normal Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_4.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_5.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_15.png}
-		\caption{Feature Map}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.19\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_127.png}
-		\caption{Feature Map}
-	\end{subfigure}
+		\begin{minipage}{0.32\linewidth}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_113.png}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_102.png}
+				\end{subfigure}
+
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_65.png}
+					\caption{CNN}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_28.png}
+				\end{subfigure}
+		\end{minipage}
+		\begin{minipage}{0.32\linewidth}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_7.png}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_25.png}
+				\end{subfigure}
+
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_11.png}
+					\caption{NOC}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_127.png}
+				\end{subfigure}
+
+		\end{minipage}
+		\begin{minipage}{0.32\linewidth}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_1.png}
+				\end{subfigure}
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_9.png}
+				\end{subfigure}
+
+				\begin{subfigure}[t]{0.45\linewidth}
+					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_24.png}
+					\caption{GCNN}
+				\end{subfigure}
+					\begin{subfigure}[t]{0.45\linewidth}
+				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_75.png}
+				\end{subfigure}
+
+		\end{minipage}
 
@@
 		\decoRule
-	\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
-	\label{fig:gcnn-detail-feature-maps}
-\end{figure}
-
-%% global compare
-\begin{figure}[H]
-		\centering
-		\captionsetup{width=\linewidth}
-		\begin{minipage}{0.32\linewidth}
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_113.png}
-				\end{subfigure}
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_102.png}
-				\end{subfigure}
-
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_65.png}
-					\caption{CNN}
-				\end{subfigure}
-				\begin{subfigure}[t]{0.45\linewidth}
-				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_28.png}
-				\end{subfigure}
-		\end{minipage}
-		\begin{minipage}{0.32\linewidth}
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_7.png}
-				\end{subfigure}
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_25.png}
-				\end{subfigure}
-
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_11.png}
-					\caption{NOC}
-				\end{subfigure}
-				\begin{subfigure}[t]{0.45\linewidth}
-				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_127.png}
-				\end{subfigure}
-
-		\end{minipage}
-		\begin{minipage}{0.32\linewidth}
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_1.png}
-				\end{subfigure}
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_9.png}
-				\end{subfigure}
-
-				\begin{subfigure}[t]{0.45\linewidth}
-					\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_24.png}
-					\caption{GCNN}
-				\end{subfigure}
-					\begin{subfigure}[t]{0.45\linewidth}
-				\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_75.png}
-				\end{subfigure}
-
-		\end{minipage}
-
-		\begin{tikzpicture}
-			\node[text width=0.1\textwidth] at (11,-1) {1};
-			\node[inner sep=0pt] (input) at (8,-1)
-			{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
-			\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
-		\end{tikzpicture}
-		\decoRule
-		\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
+		\caption{Some of global feature maps of CNN, NOC, GCNN models in up-sampling part on resolution $ 32\times32 $}
 		\label{fig:global-feature-maps}
@@
 
+%& trip-net evaluation with other models
+
+\begin{figure}[H]
+	\centering
+	\captionsetup{width=\linewidth}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
+		\caption{GT}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
+		\caption{SVD}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
+		\caption{GCNN}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.24\linewidth}
+		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
+		\caption{Trip-Net}
+	\end{subfigure}
+	\begin{tikzpicture}
+	\node[text width=0.1\textwidth] at (11,-1) {90};
+	\node[inner sep=0pt] (input) at (8,-1)
+	{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+	\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+\end{tikzpicture}
+	\decoRule
+	\caption{Comparison on high resolution dataset ($ 512\times 512 $).}
+	\label{fig:trip-eval-compare}
+\end{figure}
+
 A quantitative evaluation is shown in Table \ref{tab:high_resolution_eval}.
@@
 
-%& trip-net evaluation with other models
-
-\begin{figure}[th]
-	\centering
-	\captionsetup{width=\linewidth}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
-		\caption{GT}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
-		\caption{SVD}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
-		\caption{GCNN}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
-		\caption{Trip-Net}
-	\end{subfigure}
-	\decoRule
-	\caption{Comparison on high resolution dataset ($ 512\times 512 $).}
-	\label{fig:trip-eval-compare}
-\end{figure}
-
 \section{Training on Real-Dataset}
@@
 	\end{subfigure}	
+	\begin{tikzpicture}
+	\node[text width=0.1\textwidth] at (11,-1) {90};
+	\node[inner sep=0pt] (input) at (8,-1)
+	{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
+	\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
+\end{tikzpicture}
 	\decoRule

### 2022-08-12 paper/Chapters/Chapter05.tex
update paper

@@
 
-For the training parameters, we set the training pipeline with a batch size of 8, since we found that a higher batch size decreases the final performance.
-Adam Optimizer (\cite{adam}), learning rate starting at $ 1\times10^{-3} $, it will decrease at epoch 8 with learning decay factor 0.5.
+For the training parameters, we set the training pipeline with a batch size of 8, Adam Optimizer (\cite{adam}), learning rate starting at $ 1\times10^{-3} $, it will decrease at epoch 8 with learning decay factor 0.5.
 The model is trained using PyTorch 1.10.0a0, CUDA 11.4.1, GPU with an NVIDIA GEFORCE RTXA 6000.
-It takes 14 hours to train the GCNN and 35 hours to train the Trip-Net.
 We stop training when the angular error of the normal map stops decreasing.
 
-\begin{flushright}
-
-\end{flushright}
 The \textit{GCNN} is the base model of the whole work.
@@
 Its purpose is to show to what extent the performance of the model is improved by skipping connections.
-We use Reversed Huber Loss as a loss function during training.
+We use Huber Loss as a loss function during training.
 We have found that it gives a better final error compared to L2 loss.

### 2022-08-20 paper/Chapters/Chapter02.tex
update paper update dataset

@@
 \cite{ncnn} uses a deep learning-based approach for painting semi-dense depth maps, which mainly uses the normalized convolution proposed by \cite{nconv}.
-This approach considers a 0-1 mask to distinguish valid and invalid data points.
+This approach considers a $ 0-1 $ mask to distinguish valid and invalid data points.
 \cite{pncnn} improved this approach by proposing an input confidence estimation network to replace the binary mask with an estimated confidence mask.
@@
 
-However, these approaches mainly rely on RGB images as input for estimating the normal or the full depth map.
+However, these approaches mainly rely on RGB images as input for estimating the normal or the fully dense depth map.
 The applied scenarios are mainly indoor scenes such as bedrooms or offices, where the focus is not on the fine details of the object surface, but only on the main directions of each area, such as the directions of the floor, walls, or seats, etc as shown in Figure \ref{fig:dataset-comparison}

### 2022-08-20 paper/Chapters/Chapter05.tex
update paper update dataset

@@
 
-For the training parameters, we set the training pipeline with a batch size of 8, Adam Optimizer (\cite{adam}), learning rate starting at $ 1\times10^{-3} $, it will decrease at epoch 8 with learning decay factor 0.5.
-The model is trained using PyTorch 1.10.0a0, CUDA 11.4.1, GPU with an NVIDIA GEFORCE RTXA 6000.
+For the training parameters, we set the training pipeline with a batch size of 8, Adam Optimizer\cite{adam}, learning rate starting at $ 1\times10^{-3} $, it will decrease at epoch 8 with learning decay factor 0.5.
+The model is trained using PyTorch 1.10.0a0, CUDA 11.4.1, GPU with an NVIDIA A100 Tensor Core GPU.
 We stop training when the angular error of the normal map stops decreasing.
@@
 We score the fusion times from 1 to 4.
-For the learning rate, we initially set $ 1e-3 $.
+For the learning rate, we initially set $ 0.001 $.
 This fits the GCNN model well, but leads to a loss explosion in the trip-net.
@@
 \section{Quantitative Evaluation on 6 Metrics}
-We evaluated our models on a synthetic dataset with a resolution of $ 128 by $ 128. 
+We evaluated our models on a synthetic dataset with a resolution of $ 128 \times $ 128. 
 Based on the metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for the evaluation.
@@
 One of the advantages of the GCNN architecture is that it is robust to noisy input, so all points, including missing points in the input vertex map, are considered in the evaluation.
-We use $\tilde{\textbf{N}}$ for the estimated normal map, $ \textbf{N} $ for the ground-truth normal map, $ P $ for the \textit{set} of valid points, \textit{ValidNum} for the number of valid points.
-\textit{abs} is a function to calculate the absolute value of the given values, \textit{median} is a function to calculate the median value of a given \textit{set}.
+We use $\tilde{\textbf{N}}$ for the estimated normal map, $ \textbf{N} $ for the ground-truth normal map, $ P $ for the \textit{set} of valid points, \textit{K} for the number of valid points.
+\textit{median} is a function to calculate the median value of a given \textit{set}.
 
@@
 {1}
-{ValidNum} \cdot \sum_{i\in P}  \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| 
+{K} \cdot \sum_{i\in P}  \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| 
 \]
@@
 MED = 
-\text{Median}   \left( \Bigg\{ \left|\arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \right| \text{for}\ i \in P   \Bigg\}\right)
+\text{median}   \left( \Bigg\{ \left|\arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \right| \text{for}\ i \in P   \Bigg\}\right)
 \]
@@
 \[
-D_5 = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 5 \right)
+D_5 = \sum_{i\in P} \left( \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 5 \right)
 \]
@@
 \[ 
-E_5 = \frac{D_5}{ValidNum}\times 100\%
+E_5 = \frac{D_5}{K}\cdot 100\%
 \]
@@
 \[
-D_{11.5} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 11.5 \right)
+D_{11.5} = \sum_{i\in P} \left( \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 11.5 \right)
 \]
@@
 \[ 
-E_{11.5} = \frac{D_{11.5}}{ValidNum}\times 100\%
+E_{11.5} = \frac{D_{11.5}}{K}\cdot 100\%
 \]
@@
 \[
-D_{22.5} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 22.5 \right)
+D_{22.5} = \sum_{i\in P} \left( \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 22.5 \right)
 \]
@@
 \[ 
-E_{22.5} = \frac{D_{22.5}}{ValidNum}\times 100\%
+E_{22.5} = \frac{D_{22.5}}{K}\cdot 100\%
 \]
@@
 \[
-D_{30} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 30 \right)
+D_{30} = \sum_{i\in P} \left(\left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 30 \right)
 \]
@@
 \[ 
-E_{30} = \frac{D_{30}}{ValidNum}\times 100\%
+E_{30} = \frac{D_{30}}{K}\cdot 100\%
 \]
@@
 In the test dataset, 5 objects are considered.
-They are: \textit{Baoshanlu}, \textit{Bus}, \textit{Dragon}, \textit{Garfield} and \textit{Washington}.
+They are: \textit{Baoshanlu} (BL), \textit{Bus} (BS), \textit{Dragon} (DG), \textit{Garfield} (GF) and \textit{Washington} (WS).
 Each object has 20 scenes with a total of 100 scenes for 5 objects.
@@
 In the 30 degrees error metric, GCNN based approach achieves 95 \% accuracy whereas Trip-Net is even higher, some of the models like \textit{dragon} achieves 98\%.
-The best performance is around 90\%, 75 \%, 45 \% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metrics respectively.
+The best performance is around 90\%, 75\%, 45\% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metrics respectively.
 Another notable result is the close performance of F3 and F4 models, where they achieves a very comparable performance.
@@
 From the table, it can be seen that all learning-based approaches achieve a better result than the \textit{SVD} approach.
-In the 30-degree error metric, the GCNN-based approach achieves 95\% accuracy, while Trip-Net is even higher and some models such as \textit{dragon} achieve 98\%.
-The best performance is 90\%, 75\%, 45\% in the $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degree error metric, respectively.
-Another notable result is the close relationship between the F3 and F4 models, which achieve very comparable performance.
-We also found that model F4 converges faster than F3 during training, but F3 ends up achieving a similar loss as model F4.
-However, using the metrics $ 30^\circ $, $ 22.5^\circ $ and $ 11.5^\circ $, we can see that the F4 model has a more stable performance with less high error normals.
+In the 30-degree error metric, the GCNN-based approach achieves 93.53\% accuracy in average, while Trip-Net is 94.81\%.
+Some models such as \textit{dragon} achieve 97.61\%.
+The Trip-Net achieves around 90\%, 75\%, 45\% in the $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degree error metric, respectively.
+We also found that model F4 converges faster than less fusion models during training.
 This is reasonable since the last fusion at the original resolution provides more high-resolution information to the models.
@@
 		\toprule
-		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 &\textbf{ 9.77 }& 9.80 \\ 
-		\hline
-		Bus 			& 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & \textbf{7.30} & 7.62\\ 
-		\hline
-		Dragon 			& 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 &\textbf{ 7.79} \\
-		\hline
-		Garfield 		& 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 &\textbf{ 9.39} \\
-		\hline
-		Washington 		& 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 &\textbf{ 12.60}\\
+		BL  		& 35.66 & 11.08 & 13.13 & 13.71 & 10.14 & 10.66 & 10.66 & \textbf{10.09} \\ 
+		\hline
+		BS 			& 31.93 & 7.17 & 8.67 & 11.71 & \textbf{6.85} & 7.52 & 7.93 & 7.09 \\ 
+		\hline
+		DG 			& 39.57 & 10.58 & 15.02 & 14.78 & 10.03 & 10.34 & 8.52 & \textbf{7.58} \\
+		\hline
+		GF 		& 39.69 & 9.82 & 12.26 & 14.70 & 9.82 & 9.65 & 9.88 &\textbf{9.50} \\
+		\hline
+		WS 		& 42.83 & 13.46 & 17.60 & 17.92 & 13.42 & 13.15 & 12.81 &\textbf{12.51}\\
 		\bottomrule
@@
 		\toprule
-		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 &\textbf{ 7.50} \\ 
-		\hline
-		Bus 			& 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & \textbf{3.65 }& 4.47 \\ 
-		\hline
-		Dragon 			& 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 &\textbf{ 5.52} \\
-		\hline
-		Garfield 		& 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & \textbf{6.04 }\\
-		\hline
-		Washington 		& 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 &\textbf{ 7.03 }& 7.25\\
+		BL  		& 34.06 & 8.74 & 10.29 & 11.36 & \textbf{7.69} & 8.27 & 8.37 & 7.83 \\ 
+		\hline
+		BS 			& 34.14 & 3.54 & 4.70 & 8.55 & \textbf{3.01} & 4.01 & 4.69 & 3.56 \\ 
+		\hline
+		DG 			& 36.43 & 7.53 & 10.68 & 11.85 & 6.74 & 7.47 & 6.17 &\textbf{5.18} \\
+		\hline
+		GF 		& 37.60 & 6.14 & 8.54 & 11.71 & 6.08 & \textbf{5.86} & 6.38 & 5.96\\
+		\hline
+		WS 		& 36.89 & 7.45 & 11.19 & 12.70 & 7.43 & 7.19 & 7.28 & \textbf{6.93} \\
 		\bottomrule
@@
 		\toprule
-		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 &\textbf{ 0.33 }& 0.32\\ 
-		\hline
-		Bus 			& 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & \textbf{0.63 }& 0.55 \\ 
-		\hline
-		Dragon 			& 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 &\textbf{ 0.46}\\
-		\hline
-		Garfield 		& 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & \textbf{0.43}\\
-		\hline
-		Washington 		& 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & \textbf{0.40 }& 0.37\\
+		BL  		& 0.59\% & 24.75\% & 20.45\% & 15.86\% & \textbf{34.04\%} & 27.93\% & 26.46\% & 29.41\%\\ 
+		\hline
+		BS 			& 0.36\% & 62.28\% & 52.70\% & 24.30\% & \textbf{65.98\%} & 59.50\% &  52.56\% & 62.08\% \\ 
+		\hline
+		DG 			& 0.32\% & 31.05\% & 18.02\% & 13.64\% & 36.64\% & 30.20\% & 40.26\% &\textbf{49.04\%}\\
+		\hline
+		GF 		& 0.38\% & 43.56\% & 29.39\% & 13.78\% & 43.86\% & \textbf{44.85\%} & 40.42\% & 44.09\%\\
+		\hline
+		WS 		& 0.18\% & 37.25\% & 27.56\% & 14.42\% & 36.15\% & 38.55\% & 37.76\% & \textbf{39.15\%} \\
 		\bottomrule
@@
 		\toprule
-		\tabhead{Object}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 &\textbf{ 0.69 }& \textbf{0.69}\\ 
-		\hline
-		Bus 			& 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & \textbf{0.83 }&\textbf{ 0.83 }\\ 
-		\hline
-		Dragon 			& 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & \textbf{0.81}\\
-		\hline
-		Garfield 		& 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 &\textbf{ 0.75}\\
-		\hline
-		Washington 		& 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & \textbf{0.65}\\
+		BL  		& 3.48\% & 63.27\% & 54.23\% & 49.93\% &  66.76\% & 65.36\% & 65.12\% & \textbf{68.29\%} \\ 
+		\hline
+		BS 			& 5.19\% & 83.23\% & 79.37\% & 66.58\% & \textbf{83.62\%} & 82.43\% & 82.04\% & 83.15\%\\ 
+		\hline
+		DG 			& 2.25\% & 69.75\% & 52.93\% & 48.19\% & 72.64\% & 71.07\% & 77.83\% & \textbf{81.52\%}\\
+		\hline
+		GF 		& 2.50\% & 73.48\% & 63.11\% & 48.81\% & 73.28\% & 74.21\%  & 72.98\% &\textbf{74.48\%}\\
+		\hline
+		WS 		& 1.95\% & 62.63\% & 50.17\% & 44.74\% & 62.65\% & 63.73\% & 63.88\% & \textbf{65.07\%} \\
 		\bottomrule
 	\end{tabular}
-	\caption{Percentage of error of less than 11.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
+	\caption{Percentage of error of less than 11.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
 	\label{tab:eval-11d}
@@
 		\toprule
-		\tabhead{Object}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 &\textbf{ 0.92} &\textbf{ 0.92}\\ 
-		\hline
-		Bus 			& 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & \textbf{0.94}\\ 
-		\hline
-		Dragon 			& 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & \textbf{0.95}\\
-		\hline
-		Garfield 		& 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 &\textbf{ 0.91} &\textbf{ 0.91}\\
-		\hline
-		Washington 		& 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & \textbf{0.83} &\textbf{ 0.83}\\
+		BL  		& 18.18\% & 90.02\% & 84.28\% & 83.93\% & 90.68\% & 90.59\% & 90.96\% & \textbf{92.04\%} \\ 
+		\hline
+		BS 			& 26.26\% & 93.26\% & 91.39\% & 88.58\% & 93.25\% & 93.22\% & 93.26\% & \textbf{93.47\%}\\ 
+		\hline
+		DG 			& 13.58\% & 90.11\% & 79.72\% & 82.45\% & 90.33\% & 90.99\% & 93.95\% & \textbf{94.78\%}\\
+		\hline
+		GF 		& 13.02\% & 89.83\% & 86.63\% & 83.47\% & 89.90\% & 90.18\% & 90.46\% &\textbf{90.72\%}\\
+		\hline
+		WS 		& 14.29\% & 81.03\% & 71.81\% & 73.11\% & 81.13\% & 81.72\% & 82.68\% &\textbf{83.37\%}\\
 		\bottomrule
 	\end{tabular}
-	\caption{Percentage of error of less than 22.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
+	\caption{Percentage of error of less than 22.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
 	\label{tab:eval-22d}
@@
 		\toprule
-		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
+		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
 		\midrule
-		Baoshanlu  		& 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 &\textbf{ 0.97 }&\textbf{ 0.97} \\ 
-		\hline
-		Bus 			& 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & \textbf{0.96} &\textbf{ 0.96} &\textbf{ 0.96 }\\ 
-		\hline
-		Dragon 			& 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & \textbf{0.98} \\
-		\hline
-		Garfield 		& 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & \textbf{0.95 }\\
-		\hline
-		Washington 		& 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & \textbf{0.89} & \textbf{0.89}\\
+		BL  		& 37.22\% & 95.92\% & 92.88\% & 93.20\% & 96.28\% & 96.06\% & 96.51\% &\textbf{96.85\%} \\ 
+		\hline
+		BS 			& 43.03\% & 95.80\% & 94.38\% & 93.22\% & 95.74\% & 95.76\% & 95.86\% &\textbf{96.00\% }\\ 
+		\hline
+		DG 			& 29.87\% & 94.69\% & 87.86\% & 90.61\% & 94.61\% & 95.10\% & 97.15\% & \textbf{97.61\%} \\
+		\hline
+		GF 		& 27.03\% & 93.76\% & 91.94\% & 90.96\% & 93.75\% & 94.04\% & 94.26\% & \textbf{94.29\%}\\
+		\hline
+		WS 		& 27.67\% & 87.48\% & 80.57\% & 82.72\% & 87.80\% & 87.90\% & 89.02\% & \textbf{89.30\%}\\
 		\bottomrule
 	\end{tabular}
-	\caption{Percentage of error of less than 30 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
+	\caption{Percentage of error of less than 30 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
 	\label{tab:eval-30d}
@@
 A qualitative evaluation of the object \textit{Dragon} is shown in figure \ref{fig:gcnn-eval}.
-As can be seen in the figure, the \textit{GCNN} model achieves an average angular error of 9 degrees for this object.
+As can be seen in the figure, the GCNN model achieves an average angular error of 9 degrees for this object.
 The image shows an overall good performance for the whole object.
 A more detailed evaluation can be seen in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy is especially good on the smooth surface, such as the body area.
-In the same case, as shown in Figure \ref{fig:gcnn-eval-multi-model}, the \textit{NOC} model has an overall worse normal than the \textit{GCNN} model in the smooth area.
-The \textit{CNN} model retains the skip connection and thus yields a sharper result than the \textit{NOC} model, however, the smooth region of the model is still worse overall than the \textit{GCNN} model.
-In addition, the \textit{CNN} model yields a much brighter error map (implying a higher angular error) in the sharp regions such as the hind leg and the head region of the dragon object.
-Figure \ref{fig:gcnn-eval-more} shows further evaluation of the \textit{GCNN} model on other objects.
-The \textit{GCNN} model gives a good result, but for the \textit{Washington} model there is still a lack of sharpness in the detail areas such as the face and clothing.
+In the same case, as shown in Figure \ref{fig:gcnn-eval-multi-model}, the NOC model has an overall worse normal than the GCNN model in the smooth area.
+The CNN model retains the skip connection and thus yields a sharper result than the NOC model, however, the smooth region of the model is still worse overall than the GCNN model.
+In addition, the CNN model yields a much brighter error map (implying a higher angular error) in the sharp regions such as the hind leg and the head region of the dragon object.
+Figure \ref{fig:gcnn-eval-more} shows further evaluation of the GCNN model on other objects.
+The GCNN model gives a good result, but for the \textit{Washington} model there is still a lack of sharpness in the detail areas such as the face and clothing.
 
@@
 		\midrule
-		Mean  					& 8.88 & 5.82 & 5.33 \\ 
-		\hline
-		Median					& 3.66 & 3.98 & 3.67 \\ 
-		\hline
-		$ 5^\circ $ 			& 0.63 & 0.63 & 0.66 \\
-		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.89 & 0.91 \\
-		\hline
-		$ 22.5^\circ $ 			& 0.89 & 0.97 & 0.97 \\
-		\hline
-		$ 30^\circ $ 			& 0.92 & 0.98 & 0.99 \\
+		Mean  					& 8.88 & 5.82 & \textbf{5.33} \\ 
+		\hline
+		Median					& \textbf{3.66} & 3.98 & 3.67 \\ 
+		\hline
+		$ 5^\circ $ 			& 63\% & 63\% & \textbf{66\%} \\
+		\hline
+		$ 11.5^\circ $ 			& 79\% & 89\% & \textbf{91\%} \\
+		\hline
+		$ 22.5^\circ $ 			& 89\% & \textbf{97\%} & \textbf{97\%} \\
+		\hline
+		$ 30^\circ $ 			& 92\% & 98\% & \textbf{99\%} \\
 		\bottomrule
@@
 		\hline
-		$ 5^\circ $ 			& \textbf{0.51} & 0.44 & 0.50 \\
-		\hline
-		$ 11.5^\circ $ 			& 0.79 & 0.79 & \textbf{0.81} \\
-		\hline
-		$ 22.5^\circ $ 			& 0.93 & 0.93 & \textbf{0.94} \\
-		\hline
-		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96 \\
+		$ 5^\circ $ 			& \textbf{51\%} & 44\% & 50\% \\
+		\hline
+		$ 11.5^\circ $ 			& 79\% & 79\% & \textbf{81\%} \\
+		\hline
+		$ 22.5^\circ $ 			& 93\% & 93\% & \textbf{94\%} \\
+		\hline
+		$ 30^\circ $ 			& 96\% & 96\% & 96\% \\
 		\bottomrule
@@
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_20_groundtruth.png}
-		\caption{GT}
+		\caption{Reference}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{./Figures/comparison_real/00008.image0.png}
-		\caption{GT}
+		\caption{Reference}
 	\end{subfigure}
@@
 
-We do not have a ground truth for evaluation in the Real-Dataset.
-But if we look directly at the visualization in Figure \ref{fig:trip-eval-real}, we can see that the Trip-Net approach is well able to ``enhance'' the missing pixels in the scenes and also gives a sharp result.
+We do not have a ground truth for evaluation in the Real-Dataset but we provide a normal map that calculated from another approach as reference.
+If we look directly at the visualization in Figure \ref{fig:trip-eval-real}, we can see that the Trip-Net approach is well able to ``enhance'' the missing pixels in the scenes and also gives a sharp result.
 The wrinkles on the clothes are detectable and even countable.

### 2022-08-20 paper/Chapters/Chapter06.tex
update paper update dataset

@@
 We also found that 4 fusions of the 3 pipes in our models is the key point to improve the performance.
-Based on our proposed dataset with resolution $ 128\times 128 $, the experiments show that the models trained on illuminated calibrated RGB-D images improve the accuracy by $ 11.1\% $ of the average degree error compared to the geometry information based approach, which provides more sharpness in the normal map.
+Based on our proposed dataset with resolution $ 128\times 128 $, the experiments show that the models trained on illuminated calibrated RGB-D images improve the accuracy by $ 10.4\% $ of the average degree error compared to the geometry information based approach, which provides more sharpness in the normal map.
 

### 2022-08-20 paper/main.tex
update paper
update paper update dataset

@@
 \usepackage{pgfplots}
-\usepackage{rotating}
+\usepackage[figuresleft]{rotating}
 \usepackage{caption}
@@
 
-\begin{abstract}
-\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-In this work, a learning based approach for surface normal estimation based on illuminiated calibrated RGB-D images is proposed.
+\chapter*{Abstract}
+In this paper, a learning-based approach for surface normal estimation based on illuminated calibrated RGB-D images is proposed.
 
-This approach extends the geometry based approach by techniques of photometric stereo, which uses calibrated illuminated images for normal estimation. 
-The two types of data gives a superior performance on normal inference task.
-One of the key points of our approach is, the proposed method require only one light source for each scene capture instead of multiple light sources, which can be very easy to configure in the practice.
+This approach extends the geometry-based approach with photometric stereo analysis techniques using calibrated illuminated RGB-D images for normality estimation. 
+Based on photometric and geometric information as input, our model can improve the accuracy of the geometry-based approach on our dataset by 10\% (mean angular error).
+One of the most important points of our approach is that the proposed method requires only one light source for each scene detection instead of multiple light sources, which is very easy to configure in practice.
 
-Our model is trained on a gated convolution neural network (Trip-Net).
-The gated convolution design is intended to handle the missing pixels in the depth map, which is a common defect of the depth sensor.
-We also created a dataset of 55 point clouds called \textit{Synthetic-50-5} for training.
+Our model is trained on a neural network with gated convolution (trip-net).
+The gated convolution design is intended to handle the missing pixels in the depth map, which are a common noise of the depth sensor.
+The network has a full convolutional architecture, so it can handle data with different resolutions as input.
+The output of our model is the corresponding normal map with a 1:1 correspondence to the input data.
+To train our models, we also created a dataset of $ 55 $ highly detailed 3D objects called \textit{Synthetic-50-5}.
 We trained our model on this synthetic dataset and then applied it to a real dataset.
-Finally, a qualitative and quantitative evaluation is performed.
-
-\end{abstract}
+As our qualitative evaluation shows, the performance of the presented method can be observed especially in detailed regions.
+Finally, a quantitative evaluation with 6 metrics is performed in this thesis.
 
@@
 \include{Appendices/AppendixB}
-%\include{Appendices/AppendixC}
+\include{Appendices/AppendixC}
 \listoffigures % Prints the list of figures

### 2022-08-20 paper/presentation/template.tex
update paper update dataset

@@
 
-%\usefonttheme{default} % Typeset using the default sans serif font
-%\usefonttheme{serif} % Typeset using the default serif font (make sure a sans font isn't being set as the default font if you use this option!)
+\usefonttheme{default} % Typeset using the default sans serif font
+\usefonttheme{serif} % Typeset using the default serif font (make sure a sans font isn't being set as the default font if you use this option!)
 %\usefonttheme{structurebold} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in bold
 %\usefonttheme{structureitalicserif} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in italic serif
-\usefonttheme{structuresmallcapsserif} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in small caps serif
+%\usefonttheme{structuresmallcapsserif} % Typeset important structure text (titles, headlines, footlines, sidebar, etc) in small caps serif
 
@@
 
-%\usepackage{mathptmx} % Use the Times font for serif text
-\usepackage{palatino} % Use the Palatino font for serif text
+\usepackage{mathptmx} % Use the Times font for serif text
+%\usepackage{palatino} % Use the Palatino font for serif text
 
@@
 %\usepackage[default]{lato} % Use the Lato font for sans serif text
+
+\usepackage{tikz}
+\usepackage{tikz-network}
+\usepackage{breqn}
+\usepackage{bm}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{multirow}
+\usepackage{pdfpages}
+\usepackage{pgfplots}
+\usepackage[figuresleft]{rotating}
+\usepackage{caption}
+\captionsetup[figure]{font=normalsize,labelfont=normalsize}
+\captionsetup{justification   = raggedright,
+	singlelinecheck = false, width=\linewidth}
+\usetikzlibrary{fit}
+\usetikzlibrary{calc,patterns,angles,quotes}
+\usetikzlibrary {arrows.meta,graphs,shapes.misc}
+\usetikzlibrary {positioning}
 
@@
 	\frametitle{Surface Normal Inference}
+		\begin{figure}
+			\begin{tikzpicture} 
+				\tikzstyle{rect} = [rectangle, rounded corners, minimum width=2.5cm, minimum height=1cm,text centered, draw=black, fill=blue!20]
+				\tikzstyle{arrow} = [thick,->,>=stealth]
+				\node (img) at (0,0)  {\includegraphics[width=.25\textwidth]{./real_img.png}};
+				\node (img-t) [below of=img, yshift=-1cm] {3D Object};
+
+				\node (normal) at (6,0)
+				{\includegraphics[width=.25\textwidth]{./real_normal.png}};
+				\node (normal-t) [below of=normal, yshift=-1cm] {Normal Map};
+
+				\draw[thick, ->] (2,0) -- (4,0) node[midway, above] {$ \textbf{n} $}; %% normal
+			\end{tikzpicture}
+	\end{figure}
+\begin{itemize}
+	\item Surface normals of a scene is presented as a normal map
+	\item Surface normal is shown in RGB color
+	\item We want to find the surface normal map of the corresponding scene.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+	\frametitle{Surface Normal Inference}
+	\begin{figure}
+		\begin{tikzpicture} 
+			\tikzstyle{rect} = [rectangle, rounded corners, minimum width=2.5cm, minimum height=1cm,text centered, draw=black, fill=blue!20]
+			\tikzstyle{arrow} = [thick,->,>=stealth]
+
+			\node (img) at (0,0)  {\includegraphics[width=.2\textwidth]{./real_img.png}};
+			\node (img-t) [below of=img, yshift=-1cm] {3D Object};
+
+			\node (depth) at (3.5,0)  {\includegraphics[width=.2\textwidth]{./real_depth.png}};
+			\node (depth-t) [below of=depth, yshift=-1cm] {Depth Map};
+
+			\node (pc) at (6,-1)  {\includegraphics[width=.2\textwidth]{./real_point.png}};
+			\node (pc-t) [below of=pc, yshift=-1.5cm] {Point Cloud};
+
+			\node (normal) at (9,0) {\includegraphics[width=.2\textwidth]{./real_normal.png}};
+			\node (normal-t) [below of=normal, yshift=-1cm] {Normal Map};
+
+			\draw[thick, blue] (1.7,2) -- (1.7,-2) node[midway, above] {$ \textbf{n} $}; %% normal
+		\end{tikzpicture}
+	\end{figure}
+	\begin{itemize}
+		\item Surface normals of a scene is presented as a normal map
+		\item Surface normal is shown in RGB color
+		\item We want to find the surface normal map of the corresponding scene.
+	\end{itemize}
+
 \end{frame}
@@
 %------------------------------------------------
-
-\subsection{Figure}
-
-\begin{frame}
-	\frametitle{Figure}
-
-	\begin{figure}
-		\includegraphics[width=0.8\linewidth]{creodocs_logo.pdf}
-		\caption{Creodocs logo.}
-	\end{figure}
-\end{frame}
 

### 2022-08-20 create_dataset.py

@@ -221,6 +221,9 @@ def convert2training_tensor_resized(path, k, output_type='normal', resize_factor
         light_direction_gt[mask_gt] = 0
         light_direction[mask] = 0
 
+        import cv2 as cv
+        cv.imwrite(str(f"fancy_eval_light{item}.png"), mu.visual_light(light_direction, "", histogram=False))
+
         # albedo
         G = np.sum(gt_normal * light_direction_gt, axis=-1)
         G[mask_gt] = 0

### 2022-08-20 eval_single_obj.py

@@ -42,13 +42,13 @@ def main(models, test_folder, args, name):
         loss_list, time_list, size_list, median_loss_list, d5_list, d11_list, d22_list, d30_list = eval.eval(
             test_folder, name, model, gpu=args.gpu, data_type=args.data_type)
 
-        loss_avg[name] = ("%.2f" % (np.array(loss_list).sum() / np.array(loss_list).shape[0]))
-        time_avg[name] = ("%.2f" % (np.array(time_list)[5:].sum() / np.array(time_list)[5:].shape[0]))
-        median_avg[name] = ("%.2f" % (np.array(median_loss_list).sum() / np.array(median_loss_list).shape[0]))
-        d5_avg[name] = ("%.2f" % (1 - np.array(d5_list).sum() / np.array(d5_list).shape[0]))
-        d11_avg[name] = ("%.2f" % (1 - np.array(d11_list).sum() / np.array(d11_list).shape[0]))
-        d22_avg[name] = ("%.2f" % (1 - np.array(d22_list).sum() / np.array(d22_list).shape[0]))
-        d30_avg[name] = ("%.2f" % (1 - np.array(d30_list).sum() / np.array(d30_list).shape[0]))
+        loss_avg[name] = ("%.4f" % (np.array(loss_list).sum() / np.array(loss_list).shape[0]))
+        time_avg[name] = ("%.4f" % (np.array(time_list)[5:].sum() / np.array(time_list)[5:].shape[0]))
+        median_avg[name] = ("%.4f" % (np.array(median_loss_list).sum() / np.array(median_loss_list).shape[0]))
+        d5_avg[name] = ("%.4f" % (1 - np.array(d5_list).sum() / np.array(d5_list).shape[0]))
+        d11_avg[name] = ("%.4f" % (1 - np.array(d11_list).sum() / np.array(d11_list).shape[0]))
+        d22_avg[name] = ("%.4f" % (1 - np.array(d22_list).sum() / np.array(d22_list).shape[0]))
+        d30_avg[name] = ("%.4f" % (1 - np.array(d30_list).sum() / np.array(d30_list).shape[0]))
         losses.append(loss_list)
         times.append(time_list[5:])
         sizes.append(size_list)
@@ -92,11 +92,11 @@ if __name__ == '__main__':
     for folder_name in ["baoshanlu", "bus", "dragon", "garfield", "washington"]:
[…]

### 2022-09-14 paper/Appendices/AppendixB.tex
update paper

% Appendix A

\chapter{More Visualization} % Main appendix title

\label{AppendixB} % For referencing this appendix elsewhere, use \ref{AppendixA}

%% gcnn-Visual-more
\newpage
\begin{figure}
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_GCNN-GCNN.png}

	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
		\caption{Vertex}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_GCNN-CNN.png}
		\caption{Error}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{GCNN evaluation ($ 128\times128 $). From top to bottom: Baoshanlu, Washington statue, Bus. }
	\label{fig:gcnn-eval-more}
\end{figure}

%% Trip-Net more evaluation
\begin{figure}
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
	\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_img.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_2_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
	\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_img.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_2_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
	\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_img.png}
\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_3_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_input.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
	\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_img.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_3_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
	\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_img.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_9_error_an2-8-1000.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_input.png}
		\caption{Vertex}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
	\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_img.png}
	\caption{Image}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_GT.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_normal_an2-8-1000.png}
		\caption{Trip-Net}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_9_error_an2-8-1000.png}
		\caption{Error}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Trip-Net evaluation ($ 128\times 128 $). From top to bottom: Baoshanlu, Washington statue, Bus.}
	\label{fig:trip-net-eval-more}
\end{figure}

### 2022-09-14 paper/Appendices/AppendixC.tex
update paper

\chapter{Feature Maps Visualization} % Main appendix title
\label{AppendixC} % For referencing this appendix elsewhere, use \ref{AppendixA}

\newpage
%% feature maps comparison
\begin{figure}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn.png}
		\caption{CNN Feature Maps}
	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc.png}
		\caption{NOC Feature Maps}
	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn.png}
		\caption{GCNN Feature Maps}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {1};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
	\end{tikzpicture}
	\decoRule
	\caption{All 128 Feature maps of model GCNN, NOC, CNN at the first up-sampling. (Resolution $ 32\times 32 $)}
	\label{fig:gcnn-cnn-feature map}
\end{figure}

### 2022-09-14 paper/Chapters/Chapter05.tex
update paper

@@
 		\midrule
-		BL  		& 35.66 & 11.08 & 13.13 & 13.71 & 10.14 & 10.66 & 10.66 & \textbf{10.09} \\ 
-		\hline
-		BS 			& 31.93 & 7.17 & 8.67 & 11.71 & \textbf{6.85} & 7.52 & 7.93 & 7.09 \\ 
-		\hline
-		DG 			& 39.57 & 10.58 & 15.02 & 14.78 & 10.03 & 10.34 & 8.52 & \textbf{7.58} \\
-		\hline
-		GF 		& 39.69 & 9.82 & 12.26 & 14.70 & 9.82 & 9.65 & 9.88 &\textbf{9.50} \\
-		\hline
-		WS 		& 42.83 & 13.46 & 17.60 & 17.92 & 13.42 & 13.15 & 12.81 &\textbf{12.51}\\
+		BL  		& 22.58 & 11.08 & 13.13 & 13.71 & 10.14 & 10.66 & 10.66 & \textbf{10.09} \\ 
+		\hline
+		BS 			& 19.78 & 7.17 & 8.67 & 11.71 & \textbf{6.85} & 7.52 & 7.93 & 7.09 \\ 
+		\hline
+		DG 			& 24.66 & 10.58 & 15.02 & 14.78 & 10.03 & 10.34 & 8.52 & \textbf{7.58} \\
+		\hline
+		GF 		& 23.87 & 9.82 & 12.26 & 14.70 & 9.82 & 9.65 & 9.88 &\textbf{9.50} \\
+		\hline
+		WS 		& 26.30 & 13.46 & 17.60 & 17.92 & 13.42 & 13.15 & 12.81 &\textbf{12.51}\\
 		\bottomrule
@@
 		\midrule
-		BL  		& 34.06 & 8.74 & 10.29 & 11.36 & \textbf{7.69} & 8.27 & 8.37 & 7.83 \\ 
-		\hline
-		BS 			& 34.14 & 3.54 & 4.70 & 8.55 & \textbf{3.01} & 4.01 & 4.69 & 3.56 \\ 
-		\hline
-		DG 			& 36.43 & 7.53 & 10.68 & 11.85 & 6.74 & 7.47 & 6.17 &\textbf{5.18} \\
-		\hline
-		GF 		& 37.60 & 6.14 & 8.54 & 11.71 & 6.08 & \textbf{5.86} & 6.38 & 5.96\\
-		\hline
-		WS 		& 36.89 & 7.45 & 11.19 & 12.70 & 7.43 & 7.19 & 7.28 & \textbf{6.93} \\
+		BL  		& 14.80 & 8.74 & 10.29 & 11.36 & \textbf{7.69} & 8.27 & 8.37 & 7.83 \\ 
+		\hline
+		BS 			& 8.80 & 3.54 & 4.70 & 8.55 & \textbf{3.01} & 4.01 & 4.69 & 3.56 \\ 
+		\hline
+		DG 			& 15.42 & 7.53 & 10.68 & 11.85 & 6.74 & 7.47 & 6.17 &\textbf{5.18} \\
+		\hline
+		GF 		& 14.36 & 6.14 & 8.54 & 11.71 & 6.08 & \textbf{5.86} & 6.38 & 5.96\\
+		\hline
+		WS 		& 17.16 & 7.45 & 11.19 & 12.70 & 7.43 & 7.19 & 7.28 & \textbf{6.93} \\
 		\bottomrule
@@
 		\midrule
-		BL  		& 0.59\% & 24.75\% & 20.45\% & 15.86\% & \textbf{34.04\%} & 27.93\% & 26.46\% & 29.41\%\\ 
-		\hline
-		BS 			& 0.36\% & 62.28\% & 52.70\% & 24.30\% & \textbf{65.98\%} & 59.50\% &  52.56\% & 62.08\% \\ 
-		\hline
-		DG 			& 0.32\% & 31.05\% & 18.02\% & 13.64\% & 36.64\% & 30.20\% & 40.26\% &\textbf{49.04\%}\\
-		\hline
-		GF 		& 0.38\% & 43.56\% & 29.39\% & 13.78\% & 43.86\% & \textbf{44.85\%} & 40.42\% & 44.09\%\\
-		\hline
-		WS 		& 0.18\% & 37.25\% & 27.56\% & 14.42\% & 36.15\% & 38.55\% & 37.76\% & \textbf{39.15\%} \\
+		BL  		& 19.30\% & 24.75\% & 20.45\% & 15.86\% & \textbf{34.04\%} & 27.93\% & 26.46\% & 29.41\%\\ 
+		\hline
+		BS 			& 41.39\% & 62.28\% & 52.70\% & 24.30\% & \textbf{65.98\%} & 59.50\% &  52.56\% & 62.08\% \\ 
+		\hline
+		DG 			& 17.68\% & 31.05\% & 18.02\% & 13.64\% & 36.64\% & 30.20\% & 40.26\% &\textbf{49.04\%}\\
+		\hline
+		GF 		& 25.37\% & 43.56\% & 29.39\% & 13.78\% & 43.86\% & \textbf{44.85\%} & 40.42\% & 44.09\%\\
+		\hline
+		WS 		& 27.35\% & 37.25\% & 27.56\% & 14.42\% & 36.15\% & 38.55\% & 37.76\% & \textbf{39.15\%} \\
 		\bottomrule
@@
 		\midrule
-		BL  		& 3.48\% & 63.27\% & 54.23\% & 49.93\% &  66.76\% & 65.36\% & 65.12\% & \textbf{68.29\%} \\ 
-		\hline
-		BS 			& 5.19\% & 83.23\% & 79.37\% & 66.58\% & \textbf{83.62\%} & 82.43\% & 82.04\% & 83.15\%\\ 
-		\hline
-		DG 			& 2.25\% & 69.75\% & 52.93\% & 48.19\% & 72.64\% & 71.07\% & 77.83\% & \textbf{81.52\%}\\
-		\hline
-		GF 		& 2.50\% & 73.48\% & 63.11\% & 48.81\% & 73.28\% & 74.21\%  & 72.98\% &\textbf{74.48\%}\\
-		\hline
-		WS 		& 1.95\% & 62.63\% & 50.17\% & 44.74\% & 62.65\% & 63.73\% & 63.88\% & \textbf{65.07\%} \\
+		BL  		& 40.82\% & 63.27\% & 54.23\% & 49.93\% &  66.76\% & 65.36\% & 65.12\% & \textbf{68.29\%} \\ 
+		\hline
+		BS 			& 54.04\% & 83.23\% & 79.37\% & 66.58\% & \textbf{83.62\%} & 82.43\% & 82.04\% & 83.15\%\\ 
+		\hline
+		DG 			& 40.87\% & 69.75\% & 52.93\% & 48.19\% & 72.64\% & 71.07\% & 77.83\% & \textbf{81.52\%}\\
+		\hline
+		GF 		& 43.67\% & 73.48\% & 63.11\% & 48.81\% & 73.28\% & 74.21\%  & 72.98\% &\textbf{74.48\%}\\
+		\hline
+		WS 		& 40.47\% & 62.63\% & 50.17\% & 44.74\% & 62.65\% & 63.73\% & 63.88\% & \textbf{65.07\%} \\
 		\bottomrule
@@
 		\midrule
-		BL  		& 18.18\% & 90.02\% & 84.28\% & 83.93\% & 90.68\% & 90.59\% & 90.96\% & \textbf{92.04\%} \\ 
-		\hline
-		BS 			& 26.26\% & 93.26\% & 91.39\% & 88.58\% & 93.25\% & 93.22\% & 93.26\% & \textbf{93.47\%}\\ 
-		\hline
-		DG 			& 13.58\% & 90.11\% & 79.72\% & 82.45\% & 90.33\% & 90.99\% & 93.95\% & \textbf{94.78\%}\\
-		\hline
-		GF 		& 13.02\% & 89.83\% & 86.63\% & 83.47\% & 89.90\% & 90.18\% & 90.46\% &\textbf{90.72\%}\\
-		\hline
-		WS 		& 14.29\% & 81.03\% & 71.81\% & 73.11\% & 81.13\% & 81.72\% & 82.68\% &\textbf{83.37\%}\\
+		BL  		& 62.27\% & 90.02\% & 84.28\% & 83.93\% & 90.68\% & 90.59\% & 90.96\% & \textbf{92.04\%} \\ 
+		\hline
+		BS 			& 68.93\% & 93.26\% & 91.39\% & 88.58\% & 93.25\% & 93.22\% & 93.26\% & \textbf{93.47\%}\\ 
+		\hline
+		DG 			& 60.71\% & 90.11\% & 79.72\% & 82.45\% & 90.33\% & 90.99\% & 93.95\% & \textbf{94.78\%}\\
+		\hline
+		GF 		& 62.55\% & 89.83\% & 86.63\% & 83.47\% & 89.90\% & 90.18\% & 90.46\% &\textbf{90.72\%}\\
+		\hline
+		WS 		& 56.92\% & 81.03\% & 71.81\% & 73.11\% & 81.13\% & 81.72\% & 82.68\% &\textbf{83.37\%}\\
 		\bottomrule
@@
 		\midrule
-		BL  		& 37.22\% & 95.92\% & 92.88\% & 93.20\% & 96.28\% & 96.06\% & 96.51\% &\textbf{96.85\%} \\ 
-		\hline
-		BS 			& 43.03\% & 95.80\% & 94.38\% & 93.22\% & 95.74\% & 95.76\% & 95.86\% &\textbf{96.00\% }\\ 
-		\hline
-		DG 			& 29.87\% & 94.69\% & 87.86\% & 90.61\% & 94.61\% & 95.10\% & 97.15\% & \textbf{97.61\%} \\
-		\hline
-		GF 		& 27.03\% & 93.76\% & 91.94\% & 90.96\% & 93.75\% & 94.04\% & 94.26\% & \textbf{94.29\%}\\
-		\hline
-		WS 		& 27.67\% & 87.48\% & 80.57\% & 82.72\% & 87.80\% & 87.90\% & 89.02\% & \textbf{89.30\%}\\
+		BL  		& 73.34\% & 95.92\% & 92.88\% & 93.20\% & 96.28\% & 96.06\% & 96.51\% &\textbf{96.85\%} \\ 
+		\hline
+		BS 			& 75.14\% & 95.80\% & 94.38\% & 93.22\% & 95.74\% & 95.76\% & 95.86\% &\textbf{96.00\% }\\ 
+		\hline
+		DG 			& 68.72\% & 94.69\% & 87.86\% & 90.61\% & 94.61\% & 95.10\% & 97.15\% & \textbf{97.61\%} \\
+		\hline
+		GF 		& 70.28\% & 93.76\% & 91.94\% & 90.96\% & 93.75\% & 94.04\% & 94.26\% & \textbf{94.29\%}\\
+		\hline
+		WS 		& 64.51\% & 87.48\% & 80.57\% & 82.72\% & 87.80\% & 87.90\% & 89.02\% & \textbf{89.30\%}\\
 		\bottomrule
@@
 	\begin{subfigure}[b]{0.24\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN_9.47.png}
 		\caption{GCNN}
@@
 	\begin{subfigure}[b]{0.18\linewidth}
-		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f4.png}
+		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f4_err_6.png}
 		\caption{F4}
